### 2019-03-04 3d1d_coupled_LM.tex
Add files

% SIAM Article Template
\documentclass[r]{siamart171218}
% Packages and macros go here
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{array}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{float}
\usepackage{fullpage}
\usepackage{color}
\usepackage{enumitem}  
\usepackage{epstopdf}

% Title. If the supplement option is on, then "Supplementary Material"
% is automatically inserted before the title.
%\title{On the weak coupling of 3D and 1D second order elliptic problems}
\title{Coupling PDEs on 3D-1D domains with Lagrange multipliers}

% Authors: full names plus addresses.
\author{Miroslav Kuchta, Federica Laurino, Kent-Andre Mardal, Paolo Zunino,\thanks{Authors are listed in alphabetical order}}

\begin{document}

\maketitle

% REQUIRED
\begin{abstract}
These are personal notes written to keep track of the developments on this topic, to be kept confidential.
\end{abstract}

% REQUIRED
\begin{keywords}
elliptic problems, high dimensionality gap, essential coupling conditions, Lagrange multipliers
\end{keywords}

% REQUIRED
\begin{AMS}
n.a.
\end{AMS}

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>

% definitions here

\def\ud{u_{\odot}}
\def\vd{v_{\odot}}
\def\uf{u_{\ominus}}
\def\up{u_{\oplus}}
\def\eps{\epsilon}
\def\nn{\boldsymbol n}
\def\rr{\boldsymbol r}
\def\RR{\boldsymbol R}
\def\kk{\boldsymbol k}
\def\ss{\boldsymbol s}
\def\uu{\boldsymbol u}
\def\vv{\boldsymbol v}
\def\xx{\boldsymbol x}
\def\bu{\overline{u}}
\def\bv{\overline{v}}
\def\tu{\widetilde{u}}
\def\tv{\widetilde{v}}
\def\TT{\boldsymbol T}
\def\NN{\boldsymbol N}
\def\BB{\boldsymbol B}
\def\ttu{\widetilde{\widetilde{u}}}
\def\ttv{\widetilde{\widetilde{v}}}
\def\cv{\check{v}}
\def\mesh{{\cal T}^h}
\def\ball{{\cal B}}
\def\R{\mathbb{R}}
\def\D{\mathcal{D}}
\def\DD{\partial\mathcal{D}}
\def\trace{\overline{\mathcal{R}}}
\def\ext{\mathcal{E}}
\def\ide{\mathcal{I}}
\def\ii{\hat{\imath}}
\newcommand{\avrd}[1]{\overline{\overline{#1}}}
\newcommand{\avrc}[1]{\overline{#1}}
\newcommand{\refe}[1]{{#1}_{\mathrm{ref}}}

\newcommand{\vertiii}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 
    \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}{Property}[section]
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\section{Introduction}\label{sec:intro}

We address the geometrical configuration of the problem for a 3D coupled problem formulation based on from Dirichlet-Neumann interface conditions. Then, we apply a model reduction technique that transforms the problem into 3D-1D coupled PDEs. We develop and analyze a robust definition of the coupling operators form a 3D domain, $\Omega$, to 1D manifold, $\Lambda$, and vice versa. This is a non trivial objective because the standard trace operator form a domain $\Omega$ to a subset $\Lambda$ is not well posed if $\Lambda$ is a manifold of co-dimension two of $\Omega$.

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\section{Problem setting}\label{sec:setting}

Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set. Let $\Sigma$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Sigma}$ be the complementary set of the cylinder. We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Sigma$. We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$. We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Sigma$ and its boundary, respectively. In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach. We also assume that $\Sigma$ crosses $\Omega$ from side to side and we call $\Gamma$ the lateral (cylindrical) surface of $\Sigma$, while the upper and lower side faces of $\Sigma$ belong to $\partial\Omega$. We refer to Figure \ref{fig1} for an illustration of the notation.

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{3D-1D-simple.png}
\end{center}
\caption{Geometrical setting of the problem}
\label{fig1}
\end{figure}

We consider the problem arising from \emph{Dirichlet-Neumann} conditions. 
It consists to find $\up,\uf$ s.t.:
\begin{subequations}\label{eq:dirneu}
\begin{align}
\label{eq:dirneu1}
- \Delta \up  + \up &= f  && \text{ in } \Omega_{\oplus},\\
\label{eq:dirneu2}
- \Delta \uf  + \uf &= g  && \text{ in } \Sigma,\\
\label{eq:dirneu3}
-\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
\label{eq:dirneu4}
\uf &= \up && \text{ on }  \Gamma,\\
\label{eq:dirneu5}
\up &= 0 && \text{ on } \partial \Omega\,.
\end{align}
\end{subequations}

The objective of this work is to derive and alalyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Sigma$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$. This new problem setting will be called the \emph{reduced} problem. Form the mathematical standpoint it is more challenging than \eqref{eq:dirneu}, because it involves the coupling of 3D/1D elliptic problems.
For the model reduction process, we decompose integrals as follows, for any sufficiently regular function $w$,
\begin{equation*}
\int_\Sigma w d\omega 
= \int_\Lambda \int_{\mathcal{D}} w d\sigma ds
= \int_\Lambda |\mathcal{D}|\avrd{w} ds\,,
\quad
\int_{\Gamma} w d\sigma 
= \int_\Lambda \int_{\partial\mathcal{D}} w d\gamma ds
= \int_\Lambda  |\partial \mathcal{D}| \avrc{w} ds\,,
\end{equation*}
where $\avrd{w}, \ \avrc{w}$ denote the following mean values respectively,
\begin{equation*}
\avrd{w} = |\mathcal{D}|^{-1} \int_{\mathcal{D}} w d\sigma\,,
\quad
\avrc{w} = |\partial\mathcal{D}|^{-1} \int_{\partial\mathcal{D}} w d\gamma\,.
\end{equation*}

We apply the model reduction approach at the level of the variational formulation.
We start from the variational formulation of problem \eqref{eq:dirneu}, 
that is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Sigma\setminus\Gamma}(\Sigma), \ \lambda \in H^{-\frac12}(\partial\Sigma)$ s.t.
\begin{subequations}\label{eq:weak_dirneu}
\begin{align}
&(u_\oplus,v_\oplus)_{H^1(\Omega_\oplus)} + (u_\ominus,v_\ominus)_{H^1(\Sigma)} 
+ \langle v_\ominus - v_\oplus, \lambda \rangle_{H^{-\frac12}(\Gamma)} 
\\
\nonumber
&\qquad\qquad = (f,v_\oplus)_{L^2(\Omega_\oplus)} + (g,v_\ominus)_{L^2(\Sigma)}
\quad \forall v_\oplus \in H^1_{\partial\Omega}(\Omega_\oplus), \ v_\ominus \in H^1_{\partial\Sigma\setminus\Gamma}(\Sigma)
\\
& \langle u_\ominus - u_\oplus, \mu \rangle_{H^{-\frac12}(\Gamma)} = 0
\quad \forall  \mu \in H^{-\frac12}(\Gamma)\,,
\end{align}
\end{subequations}
where $\langle v, \mu \rangle_{H^{-\frac12}(\Gamma)}$ denotes the duality pairing between 
$ \mu \in H^{-\frac12}(\Gamma)$ and $v \in H^{\frac12}(\Gamma)$.
In this case, the additional variable $\lambda$ is equivalent to $\lambda  = - \nabla \uf \cdot \nn_\ominus$.

Using the averaging tools for the model reduction approach, we end up with a reduced problem
for the unknown $u$ defined on the entire 3D domain $\Omega$, coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$
and a Lagrange multiplier $L$ defined on $\Lambda$. In the reduced problem the multiplier assumes the following interpretation,
\begin{equation*}
L = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \nabla \uf \cdot \nn_\ominus
   = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \lambda \,.
\end{equation*}

We consider two alternative formulations. The scope of this work is to compare them, 
with the aim to determine which is the most suitable as a computational model based on 3D-1D coupled PDEs.

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\subsection{Problem 1}
The idea is to couple a 3D PDE with a 1D one, using a Lagrange multiplier space defined on a 2D surface that surrounds the 1D manifold.
Let $\langle \cdot , \cdot \rangle_\Gamma$ denote the duality pairing between 
$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$.
The problem consists to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ L \in H^{-\frac12}(\Gamma )$, such that
\begin{subequations}\label{eq:problem1}
\begin{align}
&(u,v)_{H^1(\Omega)} + |{\cal D}|(\ud,\vd)_{H^1(\Lambda)} 
+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
\\
&   \langle \Pi_1 u - \Pi_2 \ud , M \rangle_\Gamma = 0
\quad \forall M \in H^{-\frac12}(\Gamma)\,.
\end{align}
\end{subequations}
Here, $\Pi_1: H^1_0(\Omega) \rightarrow H^{\frac12}_{00}(\Gamma)$
and $\Pi_2: H^1_0(\Lambda) \rightarrow H^{\frac12}_{00}(\Gamma)$
and we remark that $\Sigma$ may be considered as a virtual surface
not necessarily of the same size as the underlying physical structure that is modeled.  
The $\Pi_1$ and $\Pi_2$ operators may be defined in terms of the averaging operators above, but may also be realized in terms of e.g. Green functions (I don't know if this is a good idea). Furthermore,  $\Gamma$ may be discretized in terms of facets neighboring $\Lambda$ and may as such not be represented as a separate structure in the implementation.

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\subsection{Problem 2}
Another form of the reduced problem uses Lagrange multipliers defined directly on the 1D manifold.
In this case, $\langle \cdot , \cdot \rangle_\Lambda$ denotes the duality pairing between 
$H^\frac12_{00}(\Lambda)$ and $H^{-\frac12}(\Lambda)$.
The problem requires to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ L \in H^{-\frac12}(\Lambda)$, such that
\begin{subequations}\label{eq:problem2}
\begin{align}
&(u,v)_{H^1(\Omega)} + |{\cal D}|(\ud,\vd)_{H^1(\Lambda)} 
+ |\partial {\cal D}| \langle \Pi_1 v - \Pi_2 \vd, L \rangle_{H^{-\frac12}(\Lambda)} 
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},V)_{L^2(\Lambda)}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
\\
&  |\partial {\cal D}| \langle \Pi_1 u -  \Pi_2 \ud, M \rangle_{H^{-\frac12}(\Lambda)} = 0
\quad \forall M \in H^{-\frac12}(\Lambda)\,.
\end{align}
\end{subequations}
We notice that all the integrals of the reduced problem are well defined because $u,v \in H^1_0(\Omega)$, 
$u,v|_{\Gamma} \in H^\frac12_{00}(\Gamma)$ and thus $\avrc{u},\avrc{v} \in H^\frac12_{00}(\Lambda)$.
More precisely, $\Pi_1 : H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda$ such that
$\Pi_1 u = \avrc{(u|_\Gamma)}$ is the combination between the trace on $\Gamma$ and the average on $\partial{\cal D}$.
The operator $\Pi_2: H^1_0(\Lambda) \rightarrow H^\frac12_{00}(\Lambda)$ is the injection form $H^1_0(\Lambda)$ and $H^\frac12_{00}(\Lambda)$.
It is apparent that problems \eqref{eq:weak_dirneu} and \eqref{eq:red_dirneu} share the same mathematical structure.
For this reason, the well-posedness of \eqref{eq:red_dirneu} can be studied in the framework of the classical theory of saddle point problems.

%Assuming now that 
%$\Pi_1: H^1(\Omega) \rightarrow H^{\frac12}(\Gamma)$ or $\Pi_2: H^1(\Gamma) \rightarrow H^{\frac12}(\Gamma)$ are isomorphisms in the sense that 
%\[
%\| \Pi_1 \|_{L(H^1(\Omega), H^{\frac12}(\Gamma))} \le C \mbox{, } 
%\| \Pi_1^{-1} \|_{L(H^{\frac12}(\Gamma), H^1(\Omega))} \le 1/c,  
%\]
%and 
%\[
%\| \Pi_2 \|_{L(H^1(\Omega), H^{\frac12}(\Gamma))} \le C \mbox{, } 
%\| \Pi_2^{-1} \|_{L(H^{\frac12}(\Gamma), H^1(\Omega))} \le 1/c .   
%\]
%We obtain the inf-sup condition as follows. Assume that $\Pi_1$ is an isomorphism then  
%we may show the inf-sup conditioning by letting $\Pi_1 \hat u = M $ and $ \hat \ud = 0$ (i.e., we need the lower bound only for one
%of the operators).  
%\begin{eqnarray}
%\sup_{u,\ud}\frac{
%\langle \Pi_1 u - \Pi_2 \ud , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
%}{(|u|_1^2 + |\ud|_1^2)^{1/2}} 
%\ge \\ 
%\frac{ \langle \Pi_1 \hat u - \Pi_2 \hat \ud , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
%}{(|\hat u|_1^2 + |\hat \ud|_1^2)^{1/2}}  \ge \\
%\frac{ \langle M , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
%}{|\Pi_1^{-1} M |_{H^1(\Omega})} \ge \\ 
%\frac{ \langle M , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
%}{| M |_{H^\frac12(\Gamma)}} \ge \\ 
%c | M |_{H^{-\frac12}(\Gamma)}  
%\end{eqnarray}
%I think the other Brezzi conditions also follows, but for the boundedness we
%would need that both $\Pi_1$ and $\Pi_2$ are bounded. Not sure I am 
%happy with the $\langle \cdot, \cdot \rangle$ notation and in particular not when we spesify the
%spaces. I would rather just say that $(\cdot, \cdot)$ denotes both the $L_2$ inner product and the
%duality pairing.  
%If we find it useful we may also  
%consider $\Pi_2: H^1(\Gamma) \rightarrow X(\Gamma)$ where $X$ may e.g. be $H^1$.  
%If so, $L, M$ in $ H^{-\frac12}(\Gamma) \cap X(\Gamma)$

\input{infsup}

\input{infsup_discrete}

\section{A benchmark problem with analytical solution}

We consider the following 3D-1D coupled problem,
\begin{subequations}\label{benchmark}
\begin{align}
\label{benchm_3d}
-\Delta u=f \quad &\text{in $\Omega$}\\
\label{benchm_1d}
-d_{zz}^2 \ud =g \quad &\text{on $\Lambda$}\\
u=0 \quad &\text{on $\partial \Omega$}\\
\label{benchm_coupl}
\ud -\avrc{u}=q \quad &\text{on $\Lambda$}
\end{align}
\end{subequations}

where $\Omega=[0,1]\times [0,1]\times [0,H]$, $\Lambda=\{x=0.5\}\times \{y=0.5\} \times [0,H] $ and
\begin{eqnarray*}
f=8\pi ^2 \sin (2\pi x) \sin (2\pi y)\\
%g=-\exp(-z)\\
%q=1+\exp(-z).
g=\frac{\pi ^2}{H^2} \sin \left(\frac{\pi z}{H}\right)\\
q=\sin \left(\frac{\pi z}{H}\right).
\end{eqnarray*}
In this case the $z$ coordinate coincides with the axial coordinate along $\Lambda$. We define $\Sigma=[0.25,0.75]\times [0.25,0.75]\times [0,H]$. The average of the 3D solution $\avrc{u}$ in \eqref{benchm_coupl} is computed on the cross section $\DD$ of the virtual interface $\Gamma=\partial \Sigma$. The exact solution of \eqref{benchmark} is given by
\begin{eqnarray}
\label{benchm_sol3d}
u=\sin (2\pi x) \sin (2\pi y)\\
\label{benchm_sol1d}
%\ud=1+\exp(-z).
\ud=\sin \left(\frac{\pi z}{H}\right) 
\end{eqnarray}
Let us notice that $\ud$ satisfies homogeneous Dirichlet conditions at the boundary of $\Lambda$.
Moreover, the solution \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfies on $\Gamma$ the relation
\begin{equation}\label{benchm_flux}
\lambda=\nabla u \cdot \textbf{n}_{\oplus}=d_z \ud n_{\oplus,z}=0,
\end{equation}
being $n_{\oplus,z}$ the $z-$component of the normal unit vector to $\Gamma$.

We prove that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of \eqref{eq:problem1} and \eqref{eq:problem2} in the simplified case in which the starting 3D-3D problem is
\begin{subequations}\label{eq:dirneu_simple}
\begin{align}
- \Delta \up  &= f  && \text{ in } \Omega_{\oplus},\\
- \Delta \uf &= g  && \text{ in } \Sigma,\\
-\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
\uf - \up &= q  && \text{ on }  \Gamma,\\
\up &= 0 && \text{ on } \partial \Omega\,.
\end{align}
\end{subequations}
instead of \eqref{eq:dirneu}. Therefore the reduced problems in the two different formulations \eqref{eq:problem1} and \eqref{eq:problem2} become respectively

\begin{subequations}\label{eq:problem1_simple}
\begin{align}
\label{eq:problem1_simple_eq1}
&(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
\\
\label{eq:problem1_simple_eq2}
&   \langle \Pi_1 u - \Pi_2 \ud , M \rangle_\Gamma =  \langle q , M \rangle_\Gamma
\quad \forall M \in H^{-\frac12}(\Gamma)\,.
\end{align}
\end{subequations}

and

\begin{subequations}\label{eq:problem2_simple}
\begin{align}
&(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
+ |\partial {\cal D}| \langle \Pi_1 v - \Pi_2 \vd, L \rangle_{H^{-\frac12}(\Lambda)} 
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},V)_{L^2(\Lambda)}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
\\
&  |\partial {\cal D}| \langle \Pi_1 u -  \Pi_2 \ud, M \rangle_{H^{-\frac12}(\Lambda)} =|\partial {\cal D}| \langle \avrc{q}, M \rangle_{H^{-\frac12}(\Lambda)}
\quad \forall M \in H^{-\frac12}(\Lambda)\,.
\end{align}
\end{subequations}

Let us prove that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of \eqref{eq:problem1_simple}. Using the integration by part formula and homogeneous boundary conditions on $\Omega$ and $\Lambda$, from \eqref{eq:problem1_simple_eq1} we have
\begin{align*}
&-(\Delta u, v)_{L^2(\Omega)} - |{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)} 
+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda).
\\
\end{align*}
Clearly, since \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d} satisfies \eqref{benchm_1d}, we have that \begin{align*}
-(\Delta u, v)_{L^2(\Omega)} =  (f,v)_{L^2(\Omega)} \\
-|{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
\end{align*}
and being $L=\lambda=0$, we can conclude that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfy \eqref{eq:problem1_simple_eq1}. The fact that the solution satisfy \eqref{eq:problem1_simple_eq2} follows from \eqref{benchm_coupl}. We can prove in the same way that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of \eqref{eq:problem2_simple}, exploiting the fact that in this case $L=\avrc{\lambda}=0$.

\begin{remark}
Let us notice that the 3D solution \eqref{benchm_sol3d} is such that $\avrc{u}=0$. Therefore in \eqref{benchmark} it is like we are solving two separated problems, one in $\Omega$ and the other on $\Lambda$.
\end{remark}
\begin{remark}
It would be interesting to make a comparison between the solution of the fully coupled 3D-3D problem \eqref{eq:dirneu} (also in the simplified case of type \eqref{eq:dirneu_simple}) and the solution of the reduced problems \eqref{eq:problem1} and \eqref{eq:problem2}. 
Therefore, we could set the values of the data of the problem such that the reduced formulation becomes non-trivial and fully coupled.
Then, we will solve both the original and reduced problem to observe the differences in the solutions and the values of the Lagrange multiplier.
\end{remark}
%\bibliographystyle{siamplain}
%\bibliography{3d1d_coupled}
\end{document}

### 2019-03-04 infsup.tex
Add files

\section{Saddle-point problem analysis}
Let us consider the general saddle point problem of the form: find $u\in X$, $p\in Q$ s.t.
\begin{eqnarray}\label{eq:saddle-point}
\begin{cases}
a(u,v)+b(v,p)=f(v)\quad &\forall v\in X\\
b(u,q)=g(q) \quad &\forall q\in M
\end{cases}
\end{eqnarray}
which embraces problems 1 and 2 described before.
For the analysis of such problems we apply the following general abstract theorem.
We denote with $A$ and $B$ the operators associated to the bilinear forms $a$ and $b$, 
namely $A: X \longrightarrow X'$ with $\langle Au,v\rangle _{X',X} = a(u,v)$ and $\langle Bv,q\rangle_{X',Q} = b(v,q)$.
\begin{theorem}[theorem 2.34 Ern-Guermond]\label{th:bnb}
Problem \eqref{eq:saddle-point} is well posed iff 
\begin{eqnarray}\label{BNB1}
\begin{cases}
\exists \alpha >0 :\, \inf_{u\in ker(B)}\sup_{v\in ker(B)} \frac{a(u,v)}{\|u\|_{X}\|v\|_{X}}\geq \alpha\\
\forall v \in ker(B), \, \left( \forall u \in ker(B),\, a(u,v)=0 \right)\implies v=0.
\end{cases}
\end{eqnarray}
and 
\begin{equation}\label{eq:infsup}
\exists \beta >0:\,\inf_{q\in Q}\sup_{v\in X} \frac{b(v,q)}{\|v\|_{X}\|q\|_{Q}}\geq \beta .
\end{equation}
\end{theorem} 
Notice that if $a$ is coercive on $ker(B)$, \eqref{BNB1} is clearly fulfilled.

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\subsection{Problem 1}
It consists to find $u \in H^1_0(\Omega),\ \ud \in H_0^1(\Lambda), \ L \in H^{-\frac12}(\Gamma )$, such that
\begin{subequations}\label{eq:red_dirneu}
\begin{align}
&(u,v)_{H^1(\Omega)} + |{\cal D}| (\ud,\vd)_{H^1(\Lambda)} 
+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma 
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}(\avrd{g},\vd)_{L^2(\Lambda)}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
\\
&   |\langle \Pi_1 u - \Pi_2 \ud , M \rangle_\Gamma = 0
\quad \forall M \in H^{-\frac12}(\Gamma)\,,
\end{align}
\end{subequations}
Here, $\Pi_1: H^1_0(\Omega) \rightarrow H^{\frac12}_{00}(\Gamma)$ is the trace operator 
while $\Pi_2$ is the uniform extension from $H^1_0(\Lambda)$ to  $H^{\frac12}_{00}(\Gamma)$. 
We notice that the trace operator is surjective from $H^1_0(\Omega)$ to $H^{\frac12}_{00}(\Gamma)$.
We apply theorem \ref{th:bnb} in the following spaces 
$X=H^1_0(\Omega) \times H^1(\Lambda)$, $Q=H^{-\frac 12}(\Gamma)$
and we prove that:
\begin{itemize}
\item $a$ coercive $\implies$ \eqref{BNB1} is fulfilled

\item We have to prove that $\forall M \in H^{-\frac 12}(\Gamma),\, \exists \beta >0$:
\begin{equation*}
\sup _{v\in H^1_0(\Omega),\, \vd \in H^1_0(\Lambda)} \frac{ \langle \Pi_1 v  - \Pi_2 \vd, M \rangle_\Gamma}{\sqrt{\|v\|^2_{H^1(\Omega)}+\|\vd \|^2_{H^1(\Lambda)}}}\geq \beta \sup_{q\in H^{\frac 12}_{00}(\Gamma)}\frac{\langle q, M\rangle}{\|q\|_{H^{\frac 12}_{00}(\Gamma)}}.
\end{equation*}
We choose $\vd \in H^1_0(\Lambda)$ such that $\Pi _2\vd =0$. Therefore,
\begin{equation*}
\sup _{v\in H^1_0(\Omega),\, \vd \in H^1_0(\Lambda)} \frac{ \langle \Pi_1 v  - \Pi_2 \vd, M \rangle_\Gamma}{\sqrt{\|v\|^2_{H^1(\Omega)}+\|\vd \|^2_{H^1(\Lambda)}}} 
\geq \sup _{v\in H^1_0(\Omega)} \frac{ \langle \Pi_1 v, M \rangle_\Gamma}{\|v\|_{H^1(\Omega)}}.
\end{equation*}

The trace operator is surjective from $H^1_0(\Omega)$ to $H^{\frac12}_{00}(\Gamma)$. Consequently, $\forall \xi \in H^{\frac 12}_{00}(\Gamma)$, we find $v$ solution of
\begin{eqnarray*}
-\Delta v&=0 \quad &\text{in }\Omega\\
v&=0 &\text{on }\partial \Omega\\
v&=\xi &\text{on } \Gamma. 
\end{eqnarray*}
We denote with $E$ the harmonic extension operator defined above.
The boundedness/stability of this operator ensures that there exists $\| E \| \in \mathbb{R}$ such that
$v=E\xi $ and $\|v \|_{H^1(\Omega)}\leq \|E\| \|\xi \|_{H^{\frac 12}_{00}(\Gamma)}$. 
Substituting in the previous inequalities we obtain
\begin{equation*}
\sup _{v\in H^1_0(\Omega)} \frac{ \langle \Pi_1 v, M \rangle_\Gamma}{\|v\|_{H^1(\Omega)}}
\geq  \sup _{\xi \in H^{\frac 12}_{00}(\Gamma )} \frac{ \langle \xi , M \rangle_\Gamma}{\|E\| \|\xi\|_{H^{\frac 12}_{00}(\Gamma)}}
= \|E\|^{-1} \|M\|_{H^{-\frac 12}(\Gamma)},
\end{equation*}
where in the last inequality we exploited the fact that $H^{-\frac 12}(\Gamma)=(H^{\frac 12 }_{00}(\Gamma))^*$.
\end{itemize}

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\subsection{Problem 2}
This problem requires to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ L \in H^{-\frac12}(\Lambda)$, such that
\begin{subequations}\label{eq:red_dirneu}
\begin{align}
&(u,v)_{H^1(\Omega)} + |{\cal D}|(U,V)_{H^1(\Lambda)} 
+ |\partial {\cal D}| \langle  \Pi_1 V - \Pi_2 v, L \rangle_\Lambda 
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},V)_{L^2(\Lambda)}
\quad \forall v \in H^1_0(\Omega), \ V \in H^1(\Lambda)
\\
&  |\partial {\cal D}| \langle \Pi_1 U - \Pi_2 u, M \rangle_\Lambda = 0
\quad \forall M \in H^{-\frac12}(\Lambda)\,.
\end{align}
\end{subequations}
Here, $\Pi_1: H^1_0(\Lambda)\rightarrow H^{\frac 12}_{00}(\Lambda)$ is the immersion operator and $\Pi_2: H^1_0(\Omega)\rightarrow H^{\frac 12}_{00}(\Lambda)$ is defined as the composition of the trace operator $T_{\Gamma}: H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ and the average operator $\bar{(\,)}:H^{\frac 12}_{00}(\Gamma) \rightarrow H^{\frac 12}_{00}(\Lambda)$, namely $\Pi_2= \bar{(\,)}\circ T_{\Gamma}$. 
First of all we prove that if $v\in H^1_0(\Omega)$, than $\Pi _2 v \in H^{\frac 12}_{00}(\Lambda)$. In particular, from standard trace theory, we have that $T_{\Gamma} v\in H^{\frac 12}_{00}(\Gamma)$, therefore we have to prove that if $v \in H^{\frac 12 }(\Gamma)$ then $\avrc{v}\in H^{\frac 12}(\Lambda)$.

\begin{lemma}\label{lemma:H12norm}
When $\Gamma$ is a cylinder, if $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}\in H_{00}^{\frac 12}(\Lambda)$.
\end{lemma}
\begin{proof}
Let us denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the laplacian on $\Gamma$, and with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $\Lambda$. In particular,
\begin{align*}
\phi _{ij}(s,\theta)=sin (i\pi s)\left( cos(j\theta)+ sin(j\theta) \right),\\
\rho_{ij}=i\pi ^2+\frac{j^2}{R^2},\\
\phi _{i}(s)=sin (i\pi s),\\
\rho _i = i\pi ^2.
\end{align*}
It is easy to verify that 
\begin{eqnarray}
\label{null_int_eigenf}
\int_0^{2\pi} \phi _{ij}(s,\theta)=0 \quad \forall j>0, \forall i \\
\label{nonull_int_eigenf}
\int_0^{2\pi} \phi _{ij}(s,\theta)= 2\pi R \, \sin(i \pi s) \quad \mbox{if } j=0, \forall i  .\\
\end{eqnarray}
Moreover we recall that $\phi_{i,j}(s,\theta)$ and $\phi _i(s)$ are orthogonal basis of $L^2(\Gamma)$ and $L^2(\Lambda)$ respectively. Therefore,
\begin{multline*}
\avrc{u}(s)=\frac{1}{2\pi R}\int_0^{2\pi} u(s,\theta)R\, d\theta
= \frac{1}{2\pi R}\int_0^{2\pi} \sum_{i,j} a_{i,j} \phi_{i,j}(s,\theta) R\, d\theta
\\= \frac{1}{2\pi R}\sum_{i,j} a_{i,j}\int_0^{2\pi}  \phi_{i,j}(s,\theta) R\, d\theta
=  \sum_{i} a_{i,0} \phi_{i}(s).
\end{multline*}
From \cite[Lemma 4.11]{c-w_h_m_2015} we have
\begin{equation}\label{H12norm_Gamma}
\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2,
\text{ with }
a_{ij}=\int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds.
\end{equation}
and 
\begin{equation*}
\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
\text{ with }
\avrc{a}_i=\int _0^1 \avrc{u}(s )\phi_{i}(s) ds.
\end{equation*}

Therefore, we have
\begin{multline*}
\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=
\sum_{i=1}^{\infty}\left( 1+ i^2\pi^2\right)^{\frac 12}\left( \int_0^1 \avrc{u}(s) sin(i\pi s)\, ds \right)^2\\
= \sum_{i=1}^{\infty} \left( 1+ i^2\pi^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^1 \sin(j\pi s) \sin(i\pi s) \, ds  \right)^2\\
= \sum_{i=1}^{\infty} \frac 14 \left( 1+ i^2\pi^2\right)^{\frac 12}a_{i,0}^2\\
\leq \sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ i^2\pi^2 + \frac{j^2}{R^2}\right)^{\frac 12} |a_{i,j}|^2 =\|u\|^2_{H^{\frac 12}(\Gamma)},
\end{multline*}

where we have used the fact that
\begin{eqnarray*}
&\int_0^1 \sin(i\pi s) \sin(j\pi s)\, ds=0 \quad \text{if $i\neq j$}\\
&\int_0^1 \sin(i\pi s) \sin(j\pi s)\, ds=\frac 12 \quad \text{if $i =j$}.
\end{eqnarray*}
\hspace*{0.9\textwidth} c.v.d.
\end{proof}

\begin{lemma}\label{lemma:H12norm_avrc}
If $\Sigma$ is a straight cylinder, 
if $u\in H^{\frac 12}_{00}(\Gamma)$ is constant on each cross section, namely $u(s,\theta)=u(s)$, then 
\begin{equation*}
\|u\|_{H^{\frac 12}_{00}(\Gamma)}=2\pi R \|u\|_{H^{\frac 12}_{00}(\Lambda)}.
\end{equation*}
\end{lemma}
\begin{proof}

From \eqref{H12norm_Gamma},
\begin{multline*}
\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2
=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ i\pi ^2+\frac{j^2}{R^2}\right)^{\frac 12}\left( \int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds \right)^2\\
=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ i\pi ^2+\frac{j^2}{R^2}\right)^{\frac 12}\left( \int _0^1 u(s) \int _0^{2\pi} \phi_{ij}\, R d\theta ds \right)^2,
\end{multline*}
and using \eqref{null_int_eigenf} and \eqref{nonull_int_eigenf}, we obtain
\begin{multline*}
\|u\|^2_{H^{\frac 12}(\Gamma)}=
\sum_{i=1}^{\infty}\left( 1+ i\pi ^2\right)^{\frac 12}\left(\int _0^1 u(s )sin (i\pi s) 2\pi R ds\right)^2\\
=4\pi ^2 R^2 \sum_{i=1}^{\infty}\left( 1+ \rho _i\right)^{\frac 12}|a_i|^2 = 4\pi ^2 R^2  \|u\|^2_{H^{\frac 12}(\Lambda)}.
\end{multline*}
\end{proof}

Then, we apply Theorem \ref{th:bnb} with the following spaces $X=H^1_0(\Omega) \times H^1_0(\Lambda)$, $Q=H^{-\frac 12}(\Lambda)$.
Let us consider $X$ equipped with the norm $\vertiii{[u,\ud ]}^2=\|u\|^2_{H^1(\Omega)} + |\D|\|\ud\|^2_{H^1(\Lambda)}$, 
$Q$ equipped with the norm
\begin{equation*}
\|M \|_{H^{-\frac 12}} := \sup_{q\in H^{\frac 12}(\Lambda)}\frac{\langle q, M\rangle}{\|q\|_{H^{\frac 12}(\Lambda)}}
\end{equation*}

Then, the following properties hold true:
\begin{itemize}
\item the form $a([u,U], [v,V])= (u,v)_{H^1(\Omega)} + |{\cal D}|(U,V)_{H^1(\Lambda)}$ is coercive 
$\implies$ \eqref{BNB1} is fulfilled. Indeed, we have,
\begin{equation*}
a([u,\ud], [u,\ud])= (u,u)_{H^1(\Omega)} + |{\cal D}|(\ud,\ud)_{H^1(\Lambda)} = \vertiii{[u,\ud]}^2\,.
\end{equation*}

\item We have that $\forall M \in H^{-\frac 12}(\Lambda),\, \exists \beta >0$:
\begin{equation*}
\sup _{v\in H^1_0(\Omega),\, V \in H^1_0(\Lambda)} \frac{ \langle  \Pi_1 V - \Pi_2 v, M \rangle_\Lambda}{\sqrt{\|v\|^2_{H^1(\Omega)}+\|V \|^2_{H^1(\Lambda)}}}
\geq \beta \sup_{q\in H^{\frac 12}(\Lambda)}\frac{\langle q, M\rangle_\Lambda}{\|q\|_{H^{\frac 12}(\Lambda)}}.
\end{equation*}
We choose $V=0$ and we obtain
\begin{equation*}
\sup _{v\in H^1_0(\Omega),\, V \in H^1_0(\Lambda)} \frac{ \langle  \Pi_1 V - \Pi_2 v, M \rangle_\Lambda}{\sqrt{\|v\|^2_{H^1(\Omega)}+\|V \|^2_{H^1(\Lambda)}}}
\geq \sup _{v\in H^1_0(\Omega)} \frac{ \langle \Pi_2 v, M \rangle_\Lambda}{\|v\|_{H^1(\Omega)}}. 
\end{equation*}

For any $q \in H^{\frac 12}_{00}(\Lambda)$, we consider its uniform extension to $\Gamma$ 
and then we consider the harmonic extension $v=E(q)\in H^1_0(\Omega)$. It follows that $\Pi_2 v=q$. Therefore, 
\begin{equation*}
\sup _{v\in H^1_0(\Omega)}  \langle \Pi_2 v, M \rangle_\Lambda \geq \sup_{q \in H^{\frac 12}_{00}(\Lambda)} \langle q, M  \rangle_\Lambda\,.
\end{equation*}
Moreover, using Lemma \ref{lemma:H12norm_avrc} we obtain
\begin{equation*}
\|v\|_{H^1_0(\Omega)}\leq \|E\| \|q\|_{H^{\frac 12}_{00}(\Gamma)}  = | \partial {\cal D} | \|E\| \|q\|_{H^{\frac 12}_{00}(\Lambda)}.
\end{equation*}
 Therefore,
\begin{multline*}
\sup _{v\in H^1_0(\Omega)} \frac{ \langle \Pi_2 v, M \rangle_\Lambda}{\|v\|_{H^1(\Omega)}}
\geq \sup _{q\in H^{\frac 12}_{00}(\Lambda)} \frac{ \langle q, M \rangle_\Lambda}{\|v\|_{H^1(\Omega)}}
\geq |\partial {\cal D}|^{-1} \|E\|^{-1} \sup _{q\in H^{\frac 12}_{00}(\Lambda)} \frac{ \langle q, M \rangle_\Lambda}{\|q\|_{H^{\frac 12}_{00}(\Lambda)}} 
\\= |\partial {\cal D}|^{-1} \|E\|^{-1} \|M\|_{H^{-\frac 12}(\Lambda)}.
\end{multline*}

\end{itemize}

\begin{remark}
The results of \eqref{lemma:H12norm} and \eqref{lemma:H12norm_avrc} can be generalized to the case of a  different geometry of $\Gamma$, for example a parallelepiped.  
\end{remark}

### 2019-03-04 infsup_discrete.tex
Add files

\section{Finite element approximation}
Let us introduce an admissibile triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{\tilde{h}}$ of $\Lambda$. We denote with $X_h(\Omega)\subset H^1_0(\Omega)$ the conforming finite element space of continuous piecewise linear functions defined on $\Omega$ and by $X_{\tilde{h}}(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise linear functions defined on $\Lambda$. Moreover, $Q_H$ denotes a suitable trial space for the lagrange multiplier $L_H$: $Q_H \subset H^{-\frac12}(\Gamma )$ in the case of Problem 1 and $Q_H \subset H^{-\frac12}(\Lambda)$ in the case of Problem 2.

\subsection{Problem 1}

\def\udh{u_{\odot_{\tilde{h}}}}
\def\vdh{v_{\odot_{\tilde{h}}}}

It consists to find $u_h \in X_h(\Omega) ,\ \udh \in X_{\tilde{h}}(\Lambda) , \ L_H \in Q_H(\Gamma) \subset H^{-\frac12}(\Gamma )$, such that
\begin{subequations}\label{eq:red_dirneu}
\begin{align}
&(u_h,v_h)_{H^1(\Omega)} + |{\cal D}| (\udh,\vdh)_{H^1(\Lambda)} 
+ \langle \Pi_1 v_h  - \Pi_2 \vdh, L_H \rangle_\Gamma 
\\
\nonumber
&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + |{\cal D}(\avrd{g},\vdh)_{L^2(\Lambda)}
\quad \forall v_h \in X_h(\Omega), \ \vdh \in X_{\tilde{h}}(\Lambda)
\\
&   \langle \Pi_1 u_h - \Pi_2 \udh , M_H \rangle_\Gamma = 0
\quad \forall M_H \in Q_H(\Gamma)\,,
\end{align}
\end{subequations}

\begin{theorem}
$\exists \gamma _1 >0$ s.t.
\begin{equation}\label{inf_sup_discrete_prob1}
\inf_{L_H \in Q_H(\Gamma)} 
\sup_{\substack{v_h \in X_h(\Omega),\\ \vdh \in X_{\tilde{h}}(\Lambda)}} \frac{ \langle \Pi_1 v_h - \Pi_2 \vdh, L_H \rangle _{\Gamma}} {\vertiii{[v_h, \vdh]} \|L_H\|_{H^{-\frac 12 }(\Gamma)}} 
\geq \gamma _1. 
\end{equation}
\end{theorem}

\begin{proof}
Let $L_H \in Q_H(\Gamma)$. As in the continuos case, let us choose $\vdh =0$, therefore 
\begin{equation*}
\sup_{\substack{v_h \in X_h(\Omega),\\ \vdh \in X_{\tilde{h}}(\Lambda)}} \frac{ \langle \Pi_1 v_h - \Pi_2 \vdh, L_H \rangle _{\Gamma}} {\vertiii{[v_h, \vdh]}}
\geq \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi_1 v_h, L_H \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}}.
\end{equation*}
Following Steinbach, Theorem 11.5, it can be shown under the following assumptions 
\begin{itemize}
\item the mesh size $h$ of the trial space $X_h(\Omega)$ is sufficiently small compared to the mesh size $H$ of $Q_H(\Gamma)$, i.e. $h \leq c_0 H$ with $c_0 < 1$, and
\item a global inverse inequality for the trial space $Q_H(\Gamma)$ holds,
\end{itemize}
that exists a positive constant $c_S$
\begin{equation}\label{infsup_tracespace}
c_S \|L_H\|_{H^{-\frac 12}(\Gamma)} \leq 
\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} \qquad \forall L_H \in Q_H(\Gamma),
\end{equation}
being $X_h(\Gamma)$ the trace space of the functions in $X_h(\Omega)$, namely the space of the restrictions of the functions in $X_h(\Omega)$ to $\Gamma$. 
Using the boundedness of the extension operator $E$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
\begin{equation*}
\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} 
\leq 
\|E\| \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle _{\Gamma} } {\|E w_h\|_{H^1(\Omega)}}.
\end{equation*}
Let $R_h: H^1(\Omega) \rightarrow X_h(\Omega)$ be a quasi interpolation operator satisfying 
\begin{equation*}
\|R_h v\|_{H^1(\Omega)} \leq c_R \|v\|_{H^1(\Omega)} \qquad \forall v \in H^1(\Omega).
\end{equation*}
Therefore, we obtain 
\begin{equation*}
\|E\| \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle _{\Gamma} } {\|E w_h\|_{H^1(\Omega)}}
\leq
\|E\| c_R \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle_{\Gamma} } {\|R_hE w_h\|_{H^1(\Omega)}}
\end{equation*}
and using \eqref{infsup_tracespace}, we have
\begin{multline}
c_S \|L_H\|_{H^{-\frac 12}(\Gamma)} 
\leq 
\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle_{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} 
\leq
\|E\| c_R \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle_{\Gamma} } {\|E w_h\|_{H^1(\Gamma)}}
\\
=
\|E\| c_R \sup_{w_h \in X_h(\Gamma)} \frac{ \langle \Pi_1 \ R_h E w_h, L_H \rangle_{\Gamma} } {\|R_h E w_h\|_{H^1(\Omega)}} 
\leq \|E\| c_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi_1 v_h, L_H \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
\end{multline}
Therefore the inf-sup condition $\eqref{inf_sup_discrete_prob1}$ holds with $\gamma_1 = c_S\|E\|^{-1} c_R^{-1}$.
\end{proof}

\subsection{Problem 2}
This problem requires to find  $u_h \in X_h(\Omega) ,\ \udh \in X_{\tilde{h}}(\Lambda), \ L_H \in Q_H(\Lambda) \subset H^{-\frac12}(\Lambda)$, such that
\begin{subequations}
\begin{align*}
&(u_h,v_h)_{H^1(\Omega)} + |{\cal D}|(\udh,\vdh)_{H^1(\Lambda)} 
+ |\partial {\cal D}| \langle  \Pi_1 \vdh - \Pi_2 v_h, L_H \rangle_\Lambda 
\\
\nonumber
&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vdh)_{L^2(\Lambda)}
\quad \forall v_h \in X_h(\Omega), \ \vdh \in X_{\tilde{h}}(\Lambda)
\\
&  |\partial {\cal D}| \langle \Pi_1 \udh - \Pi_2 u_h, M_H \rangle_\Lambda = 0
\quad \forall M_H \in Q_H(\Lambda)\,.
\end{align*}
\end{subequations}

\begin{theorem}
$\exists \gamma _2 >0$ s.t.
\begin{equation}\label{inf_sup_discrete_prob2}
\inf_{L_H \in Q_H(\Lambda)} 
\sup_{\substack{vh \in X_h(\Omega),\\ \vdh \in X_{\tilde{h}}(\Lambda)} }\frac{\langle \Pi_1 v_h - \Pi_2 \vdh, L_H \rangle _{\Lambda} } {\vertiii{[v_h, \vdh]} \|L_H\|_{H^{-\frac 12 }(\Lambda)}  } 
\geq \gamma _2. 
\end{equation}
\end{theorem}
\begin{proof}
Let $L_H$ be arbitrarly chosen in $Q_H(\Lambda)$. Again, we choose $\vdh =0$, so that \eqref{inf_sup_discrete_prob2} reduces to prove
\begin{equation*}
\gamma _2 \|L_H\|_{H^{\frac 12}(\Lambda)}
\leq 
\sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi_2 v_h , L_H \rangle _{\Lambda} } {\|v_h\|_{H^1(\Omega)} } \qquad \forall L_H \in Q_H(\Lambda).
\end{equation*}
Assume that
\begin{itemize}
\item the mesh size $h$ of the trial space $X_h(\Omega)$ is sufficiently small compared to the mesh size $H$ of $Q_H(\Lambda)$, i.e. $h \leq c_1 H$ with $c_1 < 1$,
\item a global inverse inequality for the trial space $Q_H(\Lambda)$ holds and
\item the space $X_h(\Lambda)$, defined as the space of the restrictions on $\Gamma$ of the functions in $X_h(\Omega)$ averaged on the cross section, has the approximation property, namely if $Q_h^{\sigma}$ denotes the projection from $H^\sigma (\Lambda)$ to $X_h(\Lambda)$, we have
\begin{equation*}
\|w-Q_h^{\sigma} w\|_{H^{\sigma} (\Lambda)} \leq c_A h^{s-\sigma} |w|_{H^s(\Lambda)} \qquad \forall w \in H^s(\Lambda).
\end{equation*}
(I think $X_h(\Lambda)$ concides with the space of piecewise linear continuous polinomials on $\Lambda$).
\end{itemize}
Under the previous assumptions, an inequality similar to \eqref{infsup_tracespace} holds also for $X_h(\Lambda)$. In particular, following the same proof in Steinbach, we can prove 
\begin{equation}
c_{S_2} \|L_H\|_{H^{-\frac 12}(\Lambda)} \leq 
\sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, L_H \rangle _{\Lambda} } {\|w_h\|_{H^{\frac 12}(\Lambda)}} \qquad \forall L_H \in Q_H(\Lambda).
\end{equation}
If we denote with $\mathcal{U}_E$ the uniform extension operator from $\Lambda$ to $\Gamma$, using Lemma \ref{lemma:H12norm_avrc}, we easily have for any $w_h \in H^{\frac 12}(\Lambda)$,
\begin{equation*}
\|\mathcal{U}_E w\|_{H^{\frac 12}(\Gamma)}=|\DD| \|w\|_{H^{\frac 12}(\Lambda)}.
\end{equation*}
Consequently, using again the extension operator $E$ from $H^{\frac 12}(\Omega)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1(\Omega)$ to $X_h(\Omega)$, we obtain
\begin{multline}
c_{S_2} \|L_H\|_{H^{-\frac 12}(\Lambda)} \leq 
\sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, L_H \rangle_{\Lambda} } {\|w_h\|_{H^{\frac 12}(\Lambda)}} 
\\
\leq |\DD|^{-1} \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, L_H \rangle _{\Lambda}} {\|\mathcal{U}_E w_h\|_{H^{\frac 12}(\Gamma)}} 
\leq |\DD|^{-1}\|E\| \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, L_H \rangle _{\Lambda} } {\|E \mathcal{U}_E w_h\|_{H^1(\Omega)}} 
\\
\leq |\DD|^{-1}\|E\| C_R \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, L_H \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
\\ 
=  |\DD|^{-1}\|E\| C_R \sup_{w_h \in X_h(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E w_h, L_H \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
\\
\leq |\DD|^{-1}\|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi _2  v_h, L_H \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
\end{multline}
Therefore, \eqref{inf_sup_discrete_prob2} holds with $\gamma_2=  c_{S_2} |\DD| \|E\|^{-1} C_R^{-1}$
\end{proof}

### 2019-03-05 infsup_discrete.tex
typos

@@
 Let us introduce an admissibile triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{\tilde{h}}$ of $\Lambda$.
-We denote with $X_h(\Omega)\subset H^1_0(\Omega)$ the conforming finite element space of continuous piecewise linear functions defined on $\Omega$ and by $X_{\tilde{h}}(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise linear functions defined on $\Lambda$.
-Moreover, $Q_H$ denotes a suitable trial space for the lagrange multiplier $L_H$: $Q_H \subset H^{-\frac12}(\Gamma )$ in the case of Problem 1 and $Q_H \subset H^{-\frac12}(\Lambda)$ in the case of Problem 2.
+We denote by $X_h(\Omega)\subset H^1_0(\Omega)$ the conforming finite element space of continuous piecewise linear functions defined on $\Omega$ and by $X_{\tilde{h}}(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise linear functions defined on $\Lambda$.
+Moreover, $Q_H$ denotes a suitable trial space for the lagrange multiplier $L_H$.
+In particular, $Q_H \subset H^{-\frac12}(\Gamma )$ in the case of Problem 1 and $Q_H \subset H^{-\frac12}(\Lambda)$ in the case of Problem 2.
 
@@
 \begin{equation}\label{inf_sup_discrete_prob1}
-\inf_{L_H \in Q_H(\Gamma)} 
-\sup_{\substack{v_h \in X_h(\Omega),\\ \vdh \in X_{\tilde{h}}(\Lambda)}} \frac{ \langle \Pi_1 v_h - \Pi_2 \vdh, L_H \rangle _{\Gamma}} {\vertiii{[v_h, \vdh]} \|L_H\|_{H^{-\frac 12 }(\Gamma)}} 
+\inf_{M_H \in Q_H(\Gamma)} 
+\sup_{\substack{v_h \in X_h(\Omega),\\ \vdh \in X_{\tilde{h}}(\Lambda)}} \frac{ \langle \Pi_1 v_h - \Pi_2 \vdh, M_H \rangle _{\Gamma}} {\vertiii{[v_h, \vdh]} \|M_H\|_{H^{-\frac 12 }(\Gamma)}} 
 \geq \gamma _1. 
@@
 \begin{proof}
-Let $L_H \in Q_H(\Gamma)$. As in the continuos case, let us choose $\vdh =0$, therefore 
+Let $M_H \in Q_H(\Gamma)$. As in the continuos case, let us choose $\vdh =0$, therefore 
 \begin{equation*}
-\sup_{\substack{v_h \in X_h(\Omega),\\ \vdh \in X_{\tilde{h}}(\Lambda)}} \frac{ \langle \Pi_1 v_h - \Pi_2 \vdh, L_H \rangle _{\Gamma}} {\vertiii{[v_h, \vdh]}}
-\geq \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi_1 v_h, L_H \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}}.
+\sup_{\substack{v_h \in X_h(\Omega),\\ \vdh \in X_{\tilde{h}}(\Lambda)}} \frac{ \langle \Pi_1 v_h - \Pi_2 \vdh, M_H \rangle _{\Gamma}} {\vertiii{[v_h, \vdh]}}
+\geq \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi_1 v_h, M_H \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}}.
 \end{equation*}
@@
 \begin{equation}\label{infsup_tracespace}
-c_S \|L_H\|_{H^{-\frac 12}(\Gamma)} \leq 
-\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} \qquad \forall L_H \in Q_H(\Gamma),
+c_S \|M_H\|_{H^{-\frac 12}(\Gamma)} \leq 
+\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} \qquad \forall M_H \in Q_H(\Gamma),
 \end{equation}
@@
 \begin{equation*}
-\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} 
+\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} 
 \leq 
-\|E\| \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle _{\Gamma} } {\|E w_h\|_{H^1(\Omega)}}.
+\|E\| \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|E w_h\|_{H^1(\Omega)}}.
 \end{equation*}
@@
 \begin{equation*}
-\|E\| \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle _{\Gamma} } {\|E w_h\|_{H^1(\Omega)}}
+\|E\| \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|E w_h\|_{H^1(\Omega)}}
 \leq
-\|E\| c_R \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle_{\Gamma} } {\|R_hE w_h\|_{H^1(\Omega)}}
+\|E\| c_R \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle_{\Gamma} } {\|R_hE w_h\|_{H^1(\Omega)}}
 \end{equation*}
@@
 \begin{multline}
-c_S \|L_H\|_{H^{-\frac 12}(\Gamma)} 
+c_S \|M_H\|_{H^{-\frac 12}(\Gamma)} 
 \leq 
-\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle_{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} 
+\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle_{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} 
 \leq
-\|E\| c_R \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, L_H \rangle_{\Gamma} } {\|E w_h\|_{H^1(\Gamma)}}
+\|E\| c_R \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle_{\Gamma} } {\|E w_h\|_{H^1(\Gamma)}}
 \\
 =
-\|E\| c_R \sup_{w_h \in X_h(\Gamma)} \frac{ \langle \Pi_1 \ R_h E w_h, L_H \rangle_{\Gamma} } {\|R_h E w_h\|_{H^1(\Omega)}} 
-\leq \|E\| c_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi_1 v_h, L_H \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
+\|E\| c_R \sup_{w_h \in X_h(\Gamma)} \frac{ \langle \Pi_1 \ R_h E w_h, M_H \rangle_{\Gamma} } {\|R_h E w_h\|_{H^1(\Omega)}} 
+\leq \|E\| c_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi_1 v_h, M_H \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
 \end{multline}
@@
 \begin{equation}\label{inf_sup_discrete_prob2}
-\inf_{L_H \in Q_H(\Lambda)} 
-\sup_{\substack{vh \in X_h(\Omega),\\ \vdh \in X_{\tilde{h}}(\Lambda)} }\frac{\langle \Pi_1 v_h - \Pi_2 \vdh, L_H \rangle _{\Lambda} } {\vertiii{[v_h, \vdh]} \|L_H\|_{H^{-\frac 12 }(\Lambda)}  } 
+\inf_{M_H \in Q_H(\Lambda)} 
+\sup_{\substack{vh \in X_h(\Omega),\\ \vdh \in X_{\tilde{h}}(\Lambda)} }\frac{\langle \Pi_1 v_h - \Pi_2 \vdh, M_H \rangle _{\Lambda} } {\vertiii{[v_h, \vdh]} \|M_H\|_{H^{-\frac 12 }(\Lambda)}  } 
 \geq \gamma _2. 
@@
 \begin{proof}
-Let $L_H$ be arbitrarly chosen in $Q_H(\Lambda)$. Again, we choose $\vdh =0$, so that \eqref{inf_sup_discrete_prob2} reduces to prove
+Let $M_H$ be arbitrarly chosen in $Q_H(\Lambda)$. Again, we choose $\vdh =0$, so that \eqref{inf_sup_discrete_prob2} reduces to prove
 \begin{equation*}
-\gamma _2 \|L_H\|_{H^{\frac 12}(\Lambda)}
+\gamma _2 \|M_H\|_{H^{\frac 12}(\Lambda)}
 \leq 
-\sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi_2 v_h , L_H \rangle _{\Lambda} } {\|v_h\|_{H^1(\Omega)} } \qquad \forall L_H \in Q_H(\Lambda).
+\sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi_2 v_h , M_H \rangle _{\Lambda} } {\|v_h\|_{H^1(\Omega)} } \qquad \forall M_H \in Q_H(\Lambda).
 \end{equation*}
@@
 \begin{equation}
-c_{S_2} \|L_H\|_{H^{-\frac 12}(\Lambda)} \leq 
-\sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, L_H \rangle _{\Lambda} } {\|w_h\|_{H^{\frac 12}(\Lambda)}} \qquad \forall L_H \in Q_H(\Lambda).
+c_{S_2} \|M_H\|_{H^{-\frac 12}(\Lambda)} \leq 
+\sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|w_h\|_{H^{\frac 12}(\Lambda)}} \qquad \forall M_H \in Q_H(\Lambda).
 \end{equation}
@@
 \begin{multline}
-c_{S_2} \|L_H\|_{H^{-\frac 12}(\Lambda)} \leq 
-\sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, L_H \rangle_{\Lambda} } {\|w_h\|_{H^{\frac 12}(\Lambda)}} 
+c_{S_2} \|M_H\|_{H^{-\frac 12}(\Lambda)} \leq 
+\sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle_{\Lambda} } {\|w_h\|_{H^{\frac 12}(\Lambda)}} 
 \\
-\leq |\DD|^{-1} \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, L_H \rangle _{\Lambda}} {\|\mathcal{U}_E w_h\|_{H^{\frac 12}(\Gamma)}} 
-\leq |\DD|^{-1}\|E\| \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, L_H \rangle _{\Lambda} } {\|E \mathcal{U}_E w_h\|_{H^1(\Omega)}} 
+\leq |\DD|^{-1} \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda}} {\|\mathcal{U}_E w_h\|_{H^{\frac 12}(\Gamma)}} 
+\leq |\DD|^{-1}\|E\| \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|E \mathcal{U}_E w_h\|_{H^1(\Omega)}} 
 \\
-\leq |\DD|^{-1}\|E\| C_R \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, L_H \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
+\leq |\DD|^{-1}\|E\| C_R \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
 \\ 
-=  |\DD|^{-1}\|E\| C_R \sup_{w_h \in X_h(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E w_h, L_H \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
+=  |\DD|^{-1}\|E\| C_R \sup_{w_h \in X_h(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E w_h, M_H \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
 \\
-\leq |\DD|^{-1}\|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi _2  v_h, L_H \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
+\leq |\DD|^{-1}\|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi _2  v_h, M_H \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
 \end{multline}

### 2019-04-03 infsup_discrete.tex
Discrete inf-sup same mesh for sol and mult

@@
-\section{Finite element approximation}
-Let us introduce an admissibile triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{\tilde{h}}$ of $\Lambda$.
-We denote by $X_h(\Omega)\subset H^1_0(\Omega)$ the conforming finite element space of continuous piecewise linear functions defined on $\Omega$ and by $X_{\tilde{h}}(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise linear functions defined on $\Lambda$.
-Moreover, $Q_H$ denotes a suitable trial space for the lagrange multiplier $L_H$.
+\section{Finite element approximation (Different meshes for solution and Lagrange multiplier)}
+Let us introduce an admissibile triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{h}$ of $\Lambda$.
+We denote by $X^0_h(\Omega)\subset H^1_0(\Omega)$ the conforming finite element space of continuous piecewise linear functions defined on $\Omega$ and by $X_{h}(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise linear functions defined on $\Lambda$.
+Moreover, $Q_H$ denotes a suitable trial space for the lagrange multiplier $L_H$, defined on a different triangulation of $\Gamma$ with mesh size $H$.
 In particular, $Q_H \subset H^{-\frac12}(\Gamma )$ in the case of Problem 1 and $Q_H \subset H^{-\frac12}(\Lambda)$ in the case of Problem 2.
@@
 
-\def\udh{u_{\odot_{\tilde{h}}}}
-\def\vdh{v_{\odot_{\tilde{h}}}}
-
-It consists to find $u_h \in X_h(\Omega) ,\ \udh \in X_{\tilde{h}}(\Lambda) , \ L_H \in Q_H(\Gamma) \subset H^{-\frac12}(\Gamma )$, such that
+It consists to find $u_h \in X_h(\Omega) ,\ {\ud}_h \in X_h(\Lambda) , \ L_H \in Q_H(\Gamma) \subset H^{-\frac12}(\Gamma )$, such that
 \begin{subequations}\label{eq:red_dirneu}
 \begin{align}
-&(u_h,v_h)_{H^1(\Omega)} + |{\cal D}| (\udh,\vdh)_{H^1(\Lambda)} 
-+ \langle \Pi_1 v_h  - \Pi_2 \vdh, L_H \rangle_\Gamma 
+&(u_h,v_h)_{H^1(\Omega)} + |{\cal D}| ({\ud}_h,{\vd}_h)_{H^1(\Lambda)} 
++ \langle \Pi_1 v_h  - \Pi_2 {\vd}_h, L_H \rangle_\Gamma 
 \\
 \nonumber
-&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + |{\cal D}(\avrd{g},\vdh)_{L^2(\Lambda)}
-\quad \forall v_h \in X_h(\Omega), \ \vdh \in X_{\tilde{h}}(\Lambda)
+&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + |{\cal D}|(\avrd{g},{\vd}_h)_{L^2(\Lambda)}
+\quad \forall v_h \in X_h(\Omega), \ {\vd}_h \in X_h(\Lambda)
 \\
-&   \langle \Pi_1 u_h - \Pi_2 \udh , M_H \rangle_\Gamma = 0
+&   \langle \Pi_1 u_h - \Pi_2 {\ud}_h , M_H \rangle_\Gamma = 0
 \quad \forall M_H \in Q_H(\Gamma)\,,
@@
 \inf_{M_H \in Q_H(\Gamma)} 
-\sup_{\substack{v_h \in X_h(\Omega),\\ \vdh \in X_{\tilde{h}}(\Lambda)}} \frac{ \langle \Pi_1 v_h - \Pi_2 \vdh, M_H \rangle _{\Gamma}} {\vertiii{[v_h, \vdh]} \|M_H\|_{H^{-\frac 12 }(\Gamma)}} 
+\sup_{\substack{v_h \in X_h(\Omega),\\ {\vd}_h \in X_h(\Lambda)}} \frac{ \langle \Pi_1 v_h - \Pi_2 {\vd}_h, M_H \rangle _{\Gamma}} {\vertiii{[v_h, {\vd}_h]} \|M_H\|_{H^{-\frac 12 }(\Gamma)}} 
 \geq \gamma _1. 
@@
 \begin{proof}
-Let $M_H \in Q_H(\Gamma)$. As in the continuos case, let us choose $\vdh =0$, therefore 
+Let $M_H \in Q_H(\Gamma)$. As in the continuos case, let us choose ${\vd}_h =0$, therefore 
 \begin{equation*}
-\sup_{\substack{v_h \in X_h(\Omega),\\ \vdh \in X_{\tilde{h}}(\Lambda)}} \frac{ \langle \Pi_1 v_h - \Pi_2 \vdh, M_H \rangle _{\Gamma}} {\vertiii{[v_h, \vdh]}}
+\sup_{\substack{v_h \in X_h(\Omega),\\ {\vd}_h \in X_h(\Lambda)}} \frac{ \langle \Pi_1 v_h - \Pi_2 {\vd}_h, M_H \rangle _{\Gamma}} {\vertiii{[v_h, {\vd}_h]}}
 \geq \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi_1 v_h, M_H \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}}.
 \end{equation*}
-Following Steinbach, Theorem 11.5, it can be shown under the following assumptions 
+Following \cite[Theorem 11.5]{steinbach2007numerical}, it can be shown under the following assumptions 
 \begin{itemize}
@@
 c_S \|M_H\|_{H^{-\frac 12}(\Gamma)} \leq 
-\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} \qquad \forall M_H \in Q_H(\Gamma),
+\sup_{w_h \in W_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} \qquad \forall M_H \in Q_H(\Gamma),
 \end{equation}
-being $X_h(\Gamma)$ the trace space of the functions in $X_h(\Omega)$, namely the space of the restrictions of the functions in $X_h(\Omega)$ to $\Gamma$. 
+being $W_h(\Gamma)$ the trace space of the functions in $X_h(\Omega)$, namely the space of the restrictions of the functions in $X_h(\Omega)$ to $\Gamma$. 
 Using the boundedness of the extension operator $E$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
 \begin{equation*}
-\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} 
+\sup_{w_h \in W_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} 
 \leq 
-\|E\| \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|E w_h\|_{H^1(\Omega)}}.
+\|E\| \sup_{w_h \in W_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|E w_h\|_{H^1(\Omega)}}.
 \end{equation*}
-Let $R_h: H^1(\Omega) \rightarrow X_h(\Omega)$ be a quasi interpolation operator satisfying 
+Let $R_h: H^1_0(\Omega) \rightarrow X_h(\Omega)$ be a quasi interpolation operator satisfying 
 \begin{equation*}
-\|R_h v\|_{H^1(\Omega)} \leq c_R \|v\|_{H^1(\Omega)} \qquad \forall v \in H^1(\Omega).
+\|R_h v\|_{H^1(\Omega)} \leq C_R \|v\|_{H^1(\Omega)} \qquad \forall v \in H^1_0(\Omega).
 \end{equation*}
@@
 \begin{equation*}
-\|E\| \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|E w_h\|_{H^1(\Omega)}}
+\|E\| \sup_{w_h \in W_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|E w_h\|_{H^1(\Omega)}}
 \leq
-\|E\| c_R \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle_{\Gamma} } {\|R_hE w_h\|_{H^1(\Omega)}}
+\|E\| C_R \sup_{w_h \in W_h(\Gamma)} \frac{ \langle w_h, M_H \rangle_{\Gamma} } {\|R_hE w_h\|_{H^1(\Omega)}}
 \end{equation*}
@@
 \leq 
-\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle_{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} 
+\sup_{w_h \in W_h(\Gamma)} \frac{ \langle w_h, M_H \rangle_{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} 
 \leq
-\|E\| c_R \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle_{\Gamma} } {\|E w_h\|_{H^1(\Gamma)}}
+\|E\| C_R \sup_{w_h \in W_h(\Gamma)} \frac{ \langle w_h, M_H \rangle_{\Gamma} } {\|E w_h\|_{H^1(\Gamma)}}
 \\
 =
-\|E\| c_R \sup_{w_h \in X_h(\Gamma)} \frac{ \langle \Pi_1 \ R_h E w_h, M_H \rangle_{\Gamma} } {\|R_h E w_h\|_{H^1(\Omega)}} 
-\leq \|E\| c_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi_1 v_h, M_H \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
+\|E\| C_R \sup_{w_h \in W_h(\Gamma)} \frac{ \langle \Pi_1 \ R_h E w_h, M_H \rangle_{\Gamma} } {\|R_h E w_h\|_{H^1(\Omega)}} 
+\leq \|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi_1 v_h, M_H \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
 \end{multline}
-Therefore the inf-sup condition $\eqref{inf_sup_discrete_prob1}$ holds with $\gamma_1 = c_S\|E\|^{-1} c_R^{-1}$.
+Therefore the inf-sup condition $\eqref{inf_sup_discrete_prob1}$ holds with $\gamma_1 = c_S\|E\|^{-1} C_R^{-1}$.
 \end{proof}
@@
 \subsection{Problem 2}
-This problem requires to find  $u_h \in X_h(\Omega) ,\ \udh \in X_{\tilde{h}}(\Lambda), \ L_H \in Q_H(\Lambda) \subset H^{-\frac12}(\Lambda)$, such that
+This problem requires to find  $u_h \in X_h(\Omega) ,\ {\ud}_h \in X_h(\Lambda), \ L_H \in Q_H(\Lambda) \subset H^{-\frac12}(\Lambda)$, such that
 \begin{subequations}
 \begin{align*}
-&(u_h,v_h)_{H^1(\Omega)} + |{\cal D}|(\udh,\vdh)_{H^1(\Lambda)} 
-+ |\partial {\cal D}| \langle  \Pi_1 \vdh - \Pi_2 v_h, L_H \rangle_\Lambda 
+&(u_h,v_h)_{H^1(\Omega)} + |{\cal D}|({\ud}_h,{\vd}_h)_{H^1(\Lambda)} 
++ |\partial {\cal D}| \langle  \Pi_1 {\vd}_h - \Pi_2 v_h, L_H \rangle_\Lambda 
 \\
 \nonumber
-&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vdh)_{L^2(\Lambda)}
-\quad \forall v_h \in X_h(\Omega), \ \vdh \in X_{\tilde{h}}(\Lambda)
+&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},{\vd}_h)_{L^2(\Lambda)}
+\quad \forall v_h \in X_h(\Omega), \ {\vd}_h \in X_h(\Lambda)
 \\
-&  |\partial {\cal D}| \langle \Pi_1 \udh - \Pi_2 u_h, M_H \rangle_\Lambda = 0
+&  |\partial {\cal D}| \langle \Pi_1 {\ud}_h - \Pi_2 u_h, M_H \rangle_\Lambda = 0
 \quad \forall M_H \in Q_H(\Lambda)\,.
@@
 \inf_{M_H \in Q_H(\Lambda)} 
-\sup_{\substack{vh \in X_h(\Omega),\\ \vdh \in X_{\tilde{h}}(\Lambda)} }\frac{\langle \Pi_1 v_h - \Pi_2 \vdh, M_H \rangle _{\Lambda} } {\vertiii{[v_h, \vdh]} \|M_H\|_{H^{-\frac 12 }(\Lambda)}  } 
+\sup_{\substack{vh \in X_h(\Omega),\\ {\vd}_h \in X_h(\Lambda)} }\frac{\langle \Pi_1 v_h - \Pi_2 {\vd}_h, M_H \rangle _{\Lambda} } {\vertiii{[v_h, {\vd}_h]} \|M_H\|_{H^{-\frac 12 }(\Lambda)}  } 
 \geq \gamma _2. 
@@
 \begin{proof}
-Let $M_H$ be arbitrarly chosen in $Q_H(\Lambda)$. Again, we choose $\vdh =0$, so that \eqref{inf_sup_discrete_prob2} reduces to prove
+Let $M_H$ be arbitrarly chosen in $Q_H(\Lambda)$. Again, we choose ${\vd}_h =0$, so that \eqref{inf_sup_discrete_prob2} reduces to prove
 \begin{equation*}
@@
 \item a global inverse inequality for the trial space $Q_H(\Lambda)$ holds and
-\item the space $X_h(\Lambda)$, defined as the space of the restrictions on $\Gamma$ of the functions in $X_h(\Omega)$ averaged on the cross section, has the approximation property, namely if $Q_h^{\sigma}$ denotes the projection from $H^\sigma (\Lambda)$ to $X_h(\Lambda)$, we have
+\item the space $W_h(\Lambda)$, defined as the space of the restrictions on $\Gamma$ of the functions in $X_h(\Omega)$ averaged on the cross section, has the approximation property, namely if $Q_h^{\sigma}$ denotes the projection from $H^\sigma (\Lambda)$ to $W_h(\Lambda)$, we have
 \begin{equation*}
@@
 \end{equation*}
-(I think $X_h(\Lambda)$ concides with the space of piecewise linear continuous polinomials on $\Lambda$).
+(Actually $W_h(\Lambda)$ concides with the space of piecewise linear continuous polinomials on $\Lambda$).
 \end{itemize}
-Under the previous assumptions, an inequality similar to \eqref{infsup_tracespace} holds also for $X_h(\Lambda)$. In particular, following the same proof in Steinbach, we can prove 
+Under the previous assumptions, an inequality similar to \eqref{infsup_tracespace} holds also for $W_h(\Lambda)$. In particular, following the same proof in Steinbach, we can prove 
 \begin{equation}
 c_{S_2} \|M_H\|_{H^{-\frac 12}(\Lambda)} \leq 
-\sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|w_h\|_{H^{\frac 12}(\Lambda)}} \qquad \forall M_H \in Q_H(\Lambda).
+\sup_{w_h \in W_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|w_h\|_{H^{\frac 12}(\Lambda)}} \qquad \forall M_H \in Q_H(\Lambda).
 \end{equation}
-If we denote with $\mathcal{U}_E$ the uniform extension operator from $\Lambda$ to $\Gamma$, using Lemma \ref{lemma:H12norm_avrc}, we easily have for any $w_h \in H^{\frac 12}(\Lambda)$,
+If we denote with $\mathcal{U}_E$ the uniform extension operator from $\Lambda$ to $\Gamma$, using Lemma \ref{lemma:H12norm_avrc}, we easily have for any $w \in H^{\frac 12}(\Lambda)$,
 \begin{equation*}
@@
 \end{equation*}
-Consequently, using again the extension operator $E$ from $H^{\frac 12}(\Omega)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1(\Omega)$ to $X_h(\Omega)$, we obtain
+Consequently, using again the extension operator $E$ from $H^{\frac 12}(\Omega)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_h(\Omega)$, we obtain
 \begin{multline}
 c_{S_2} \|M_H\|_{H^{-\frac 12}(\Lambda)} \leq 
-\sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle_{\Lambda} } {\|w_h\|_{H^{\frac 12}(\Lambda)}} 
+\sup_{w_h \in W_h(\Lambda)} \frac{ \langle w_h, M_H \rangle_{\Lambda} } {\|w_h\|_{H^{\frac 12}(\Lambda)}} 
 \\
-\leq |\DD|^{-1} \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda}} {\|\mathcal{U}_E w_h\|_{H^{\frac 12}(\Gamma)}} 
-\leq |\DD|^{-1}\|E\| \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|E \mathcal{U}_E w_h\|_{H^1(\Omega)}} 
+\leq |\DD| \sup_{w_h \in W_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda}} {\|\mathcal{U}_E w_h\|_{H^{\frac 12}(\Gamma)}} 
+\leq |\DD| \|E\| \sup_{w_h \in W_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|E \mathcal{U}_E w_h\|_{H^1(\Omega)}} 
 \\
-\leq |\DD|^{-1}\|E\| C_R \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
+\leq |\DD|\|E\| C_R \sup_{w_h \in W_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
 \\ 
-=  |\DD|^{-1}\|E\| C_R \sup_{w_h \in X_h(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E w_h, M_H \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
+=  |\DD| \|E\| C_R \sup_{w_h \in W_h(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E w_h, M_H \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
 \\
-\leq |\DD|^{-1}\|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi _2  v_h, M_H \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
+\leq |\DD| \|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi _2  v_h, M_H \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
 \end{multline}
-Therefore, \eqref{inf_sup_discrete_prob2} holds with $\gamma_2=  c_{S_2} |\DD| \|E\|^{-1} C_R^{-1}$
+Therefore, \eqref{inf_sup_discrete_prob2} holds with $\gamma_2=  c_{S_2} |\DD|^{-1} \|E\|^{-1} C_R^{-1}$
 \end{proof}
+
+\section{Finite element approximation (Same mesh for solution and Lagrange multiplier)}
+Let us introduce a shape-regular triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{h}$ of $\Lambda$.
+We denote by $X_{h,k}^0(\Omega)\subset H^1_0(\Omega)$ the conforming finite element space of continuous piecewise polynomials of degree $k$ defined on $\Omega$ satysfing homogeneous Dirichlet conditions on the boundary and by $X_{h,k}^0(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$, satisfying homogeneous Dirichlet conditions on $\Lambda \cap \partial \Omega$.
+Moreover, $Q_{h}$ denotes a suitable trial space for the lagrange multiplier $L_h$.
+In particular, $Q_h \subset H^{-\frac12}(\Gamma )$ in the case of Problem 1 and $Q_h \subset H^{-\frac12}(\Lambda)$ in the case of Problem 2.
+
+\subsection{Problem 1}It consists to find $u_h \in X_{h,k}^0 (\Omega) ,\ {\ud}_h \in X_{h,k}^0(\Lambda) , \ L_h \in Q_h(\Gamma) \subset H^{-\frac12}(\Gamma )$, such that
+\begin{subequations}
+\begin{align}
+&(u_h,v_h)_{H^1(\Omega)} + |{\cal D}| ({\ud}_h,{\vd}_h)_{H^1(\Lambda)} 
++ \langle \Pi_1 v_h  - \Pi_2 {\vd}_h, L_h \rangle_\Gamma 
+\\
+\nonumber
+&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + |{\cal D}(\avrd{g},{\vd}_h)_{L^2(\Lambda)}
+\quad \forall v_h \in X_{h,k}^0(\Omega), \ {\vd}_h \in X_{h,k}^0(\Lambda)
+\\
+&   \langle \Pi_1 u_h - \Pi_2 {\ud}_h , M_h \rangle_\Gamma = 0
+\quad \forall M_h \in Q_h(\Gamma)\,,
+\end{align}
+\end{subequations}
+
+Let us denote with $W_{h,k}^0(\Gamma) \subset H^{\frac 12}_{00}(\Gamma)$ the trace space of functions running in $X_{h,k}^0(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$.
+We choose $Q_h(\Gamma)=W_{h,k}^0(\Gamma)$, therefore we impose homogeneous Dirichlet boundary condition on $\partial \Omega$ also for the Lagrange multiplier.
+For this choice of $Q_h(\Gamma)$ we can prove the well-posedness of the discrete problem, as shown in the following.
+
+\begin{lemma}
+Let $P_h: H^{\frac 12}_{00} \longrightarrow W_{h,k}^0(\Gamma)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Gamma)$ by
+\begin{equation*}
+(P_h v , \psi)_\Gamma= (v, \psi)_\Gamma \qquad \forall \psi \in W_{h,k}^0(\Gamma).  
+\end{equation*} 
+Then, $P_h$ is continuous on $H^{\frac 12}_{00}(\Gamma)$, namely
+\begin{equation}\label{continuity_projoper}
+\|P_h v\|_{H^{\frac 12}_{00}(\Gamma)} \leq C \|v\|_{H^{\frac 12}_{00}(\Gamma)},
+\end{equation}
+where $C$ is a positive constant independent of $h$.
+\end{lemma}
+\begin{proof}
+We prove that $P_h$ is continuous on $L^2(\Gamma)$ and on $H^1_0(\Gamma)$ following \cite[Section 1.6.3]{MR2050138}.
+Then, the inequality \eqref{continuity_projoper} can be dirived by Hilbertian interpolation.
+For the $L^2$-continuity, we exploit the fact that, from the definition of $P_h$,
+\begin{equation*}
+(v-P_h v,P_h v)_{\Gamma}=0.
+\end{equation*} 
+Therefore, by Pythagoras identity,
+\begin{equation*}
+\|v\|^2_{L^2(\Gamma)} = \|v-P_h v\|_{L^2(\Gamma)}^2 + \|P_h v\|_{L^2(\Gamma)}^2 \geq \|P_h v\| _{L^2(\Gamma)}.
+\end{equation*}
+Let us now consider $v\in H^1_0(\Gamma)$.The Scott-Zhang interpolation operator $SZ_h$ from $H^1_0(\Gamma)$ to $W_{h,k}^0(\Gamma)$ satisfies the following inequalities,
+\begin{equation}\label{SZ_stability}
+\|SZ_h v\|_{H^1(\Gamma)} \leq C_1 \|v\|_{H^1(\Gamma)}
+\end{equation} 
+\begin{equation}\label{SZ_approx}
+\|v -SZ_h v \|_{L^2(\Gamma)}\leq C_2 h \|v\|_{H^1(\Gamma)}.
+\end{equation}
+Therefore,
+\begin{equation*}
+\begin{split}
+\|\nabla P_h v\|_{L^2(\Gamma)} 
+&\leq \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + \|\nabla SZ_h v\|_{L^2(\Gamma)}\\
+&\leq \text{ (using \eqref{SZ_stability}) } \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
+\end{split}
+\end{equation*}
+and by using the inverse inequality we obtain
+\begin{equation*}
+\begin{split}
+\|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
+&\leq \frac{C_3}{h} \|P_h v - SZ_h v\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
+&= \frac{C_3}{h} \|P_h (v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
+&\leq  \text{ (Stability of $P_h$ in $L^2$) } \frac{C_3}{h} \|v - SZ_h v\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
+&\leq \text{ (using \eqref{SZ_approx}) } \frac{C_3}{h} C_2 h  \| v\|_{H^1(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
+&\leq (C_2 C_3 +C_1) \|v\|_{H^1(\Gamma)},
+\end{split}
+\end{equation*}
+from which we obtain the continuity in $H^1_0(\Gamma)$.
+\end{proof}
+
+\begin{lemma}\label{lemma:trspace_infsup} 
+There exist a constant $\gamma >0$ such that
+\begin{equation*}
+\sup_{\substack{q_h \in W_{h,k}^0(\Gamma)}} \frac{\langle q_h , M_h \rangle}{ \|q_h\|_{H^{\frac 12}(\Gamma)}} \geq \gamma \|M_h\|_{H^{-\frac 12}(\Gamma)}.
+\end{equation*} 
+\end{lemma}
+\begin{proof}
+Let $M_h$ be in $W_{h,k}^0(\Gamma)$. From the continuous case, in particular from \eqref{inf_sup_traceop}, we have
+\begin{equation*}
+\|E\|^{-1} \|M_h\|_{H^{-\frac 12}(\Gamma)} \leq \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \Pi_1 v , M_h \rangle}{\|v\|_{H^1(\Omega)}} =\sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle T_{\Gamma} v , M_h \rangle}{\|v\|_{H^1(\Omega)}}
+\end{equation*}
+and by the trace inequality $\|T_{\Gamma}v\|_{H^\frac 12 (\Gamma)} \leq K_1 \|v\|_{H^1_0(\Omega)}$ (see \cite[7.56]{adams1975pure}), we obtain 
+\begin{equation*}
+\sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle T_{\Gamma} v , M_h \rangle}{\|v\|_{H^1(\Omega)}}
+\leq K_1 \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle T_{\Gamma} v , M_h \rangle}{ \|T_{\Gamma}v\|_{H^{\frac 12}(\Gamma)}}.
+\end{equation*}
+By the definition of $P_h$ and \eqref{continuity_projoper} 
+\begin{equation*}
+\begin{split}
+K_1 \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle T_{\Gamma} v , M_h \rangle}{ \|T_{\Gamma}v\|_{H^{\frac 12}(\Gamma)}}&= K_1 \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(T_{\Gamma} v) , M_h \rangle}{ \|T_{\Gamma}v\|_{H^{\frac 12}(\Gamma)}}\\
+&\leq  K_1 C \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(T_{\Gamma}) v , M_h \rangle}{ \|P_h(T_{\Gamma}v)\|_{H^{\frac 12}(\Gamma)}}\\
+&= K_1 C \sup_{\substack{q_h \in W_{h,k}^0(\Gamma)}} \frac{\langle q_h , M_h \rangle}{  \|q_h\|_{H^{\frac 12}(\Gamma)}}.
+\end{split}
+\end{equation*}
+\end{proof}
+
+\begin{theorem}[Discrete inf-sup] 
+$\exists \gamma _1 >0$ s.t.
+\begin{equation}\label{inf_sup_discrete_prob1}
+\inf_{M_h \in W^0_{h,k}(\Gamma)} 
+\sup_{\substack{v_h \in X^0_{h,k}(\Omega),\\ {\vd}_h \in X^0_{h,k}(\Lambda)}} \frac{ \langle \Pi_1 v_h - \Pi_2 {\vd}_h, M_h \rangle _{\Gamma}} {\vertiii{[v_h, {\vd} _h]} \|M_h\|_{H^{-\frac 12 }(\Gamma)}}
+\geq \gamma _1. 
+\end{equation}
+\end{theorem}
+
+\begin{proof}
+Let $M_h \in W^0_{h,k}$. As in the continuos case, we choose ${\vd}_h =0$ and we have
+\begin{equation*}
+\sup_{\substack{v_h \in X^0_{h,k}(\Omega),\\ {\vd}_h \in X^0_{h,k}(\Lambda)}} \frac{ \langle \Pi_1 v_h - \Pi_2 {\vd}_h, M_h \rangle _{\Gamma}} {\vertiii{[v_h,  {\vd}_h]}}
+\geq \sup_{v_h \in X^0_{h,k}(\Omega)} \frac{ \langle \Pi_1 v_h, M_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}}.
+\end{equation*}
+
+Therefore, we want to prove that there exists $\gamma _1$ such that
+\begin{equation*}
+\sup_{v_h \in X^0_{h,k}(\Omega)} \frac{ \langle \Pi_1 v_h, M_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}}=\sup_{\substack{v_h \in X^0_{h,k}(\Omega)}} \frac{\langle T_{\Gamma} v_h , M_h \rangle}{\|v_h\|_{H^1(\Omega)}} \geq \gamma_1 \|M_h\|_{H^{-\frac 12}(\Gamma)} \qquad \forall M_h \in W_{h,k}^0.
+\end{equation*}
+
+Using Lemma \ref{lemma:trspace_infsup} and the boundedness of the armonic extension operator $E$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
+\begin{equation*}
+\gamma \|M_h\|_{H^{-\frac 12}(\Gamma)} \leq  \sup_{q_h \in W_{h,k}^0(\Gamma)} \frac{ \langle q_h, M_h \rangle _{\Gamma} } {\|q_h\|_{H^{\frac 12}(\Gamma)}} 
+\leq 
+\|E\| \sup_{q_h \in W_{h,k}^0(\Gamma)} \frac{ \langle q_h, M_h \rangle _{\Gamma} } {\|Eq_h\|_{H^1(\Omega)}} .
+\end{equation*}
+Let $R_h: H^1_0(\Omega) \rightarrow X_{h,k}^0(\Omega)$ be a quasi interpolation operator satisfying 
+\begin{equation*}
+\|R_h v\|_{H^1(\Omega)} \leq C_R \|v\|_{H^1(\Omega)} \qquad \forall v \in H^1_0(\Omega).
+\end{equation*}
+Therefore, we obtain 
+\begin{equation*}
+\|E\| \sup_{q_h \in W_{h,k}^0(\Gamma)} \frac{ \langle q_h, M_h \rangle _{\Gamma} } {\|Eq_h\|_{H^1(\Omega)}} 
+\leq
+\|E\| C_R \sup_{q_h \in W_{h,k}^0(\Gamma)} \frac{ \langle q_h, M_h \rangle _{\Gamma} } {\|R_h E q_h\|_{H^1(\Omega)}}
+\end{equation*}
+and we have
+\begin{multline}
+\gamma \|M_h\|_{H^{-\frac 12}(\Gamma)} 
+\leq 
+\sup_{q_h \in W_{h,k}^0(\Gamma)} \frac{ \langle q_h, M_h \rangle_{\Gamma} } {\|q_h\|_{H^{\frac 12}(\Gamma)}} 
+\leq
+\|E\| C_R \sup_{q_h \in W_{h,k}^0(\Gamma)} \frac{ \langle q_h, M_h \rangle_{\Gamma} } {\|R_h E q_h\|_{H^1(\Gamma)}}
+\\
+=
+\|E\| C_R \sup_{q_h \in W_{h,k}^0(\Gamma)} \frac{ \langle \Pi_1 \ R_h E q_h, M_h \rangle_{\Gamma} } {\|R_h E q_h\|_{H^1(\Omega)}} 
+\leq \|E\| C_R \sup_{v_h \in X_{h,k}(\Omega)} \frac{ \langle \Pi_1 v_h, M_h \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
+\end{multline}
+Therefore the inf-sup condition $\eqref{inf_sup_discrete_prob1}$ holds with $\gamma_1 = \gamma\|E\|^{-1} C_R^{-1} $.
+\end{proof}
+
+\begin{remark} We notice that to prove the result in Lemma \ref{lemma:trspace_infsup} (and then the discrete inf-sup condition)  basically we need a projection operator $P_h: H^{\frac 12}_{00} \longrightarrow W_{h,k}^0(\Gamma)$ orthogonal in the multiplier space $Q_h(\Gamma)$, namely such that $\langle P_h v, M_h \rangle = \langle v, M_h \rangle, \, \forall M_h \in Q_h(\Gamma)$, and continuous in $H^{\frac 12}(\Gamma)$.
+Therefore, in principle different choices than $Q_h(\Lambda)=W_{h,k}^0(\Gamma)$ could be considered if we can build an operator $P_h$ satisfying these properties.
+In \cite{belgacem1999mortar} such operator $P_h$  is built for a particular choice of $Q_h(\Gamma)$ but it is not clear how they prove the $H^1$-stability inequality (and consequently the $H^{\frac 12 }$-stability) with a constant independent of the mesh size $h$...
+\end{remark}  
+\subsection{Problem 2}
+This problem requires to find  $u_h \in X^0_{h,k}(\Omega) ,\ {\ud}_h \in X^0_{h,k}(\Lambda), \ L_h \in Q_h(\Lambda) \subset H^{-\frac12}(\Lambda)$, such that
+\begin{subequations}
+\begin{align*}
+&(u_h,v_h)_{H^1(\Omega)} + |{\cal D}|({\ud}_h,{\vd}_h)_{H^1(\Lambda)} 
++ |\partial {\cal D}| \langle  \Pi_1 {\vd}_h - \Pi_2 v_h, L_h \rangle_\Lambda 
+\\
+\nonumber
+&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},{\vd}_h)_{L^2(\Lambda)}
+\quad \forall v_h \in X_h(\Omega), \ {\vd}_h \in X_h(\Lambda)
+\\
+&  |\partial {\cal D}| \langle \Pi_1 {\ud}_h - \Pi_2 u_h, M_h \rangle_\Lambda = 0
+\quad \forall M_h \in Q_h(\Lambda)\,.
+\end{align*}
+\end{subequations}
+
+We introduce the space
+$W_{h,k}^0(\Lambda) \subset H^{\frac 12} _{00} (\Lambda)$, which is the averaged trace space of functions running in $H^1_0(\Omega)$.
+It coincides with the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$ and satisfying homogeneous Dirichlet boundary condition.
+We choose $Q_h(\Lambda)=W_{h,k}^0(\Lambda)$, therefore we impose homogeneous Dirichlet boundary condition on $\Lambda \cap \partial \Omega$ also for the Lagrange multiplier.
+With this choice for $Q_h(\Lambda)$, we can prove the well-posedness of the discrete problem.
+In particular, following the same steps as for Problem 1, we can prove the following results.
+\begin{lemma}
+Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow W_{h,k}^0(\Lambda)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
+\begin{equation*}
+(P_h v , \psi)_\Lambda= (v, \psi)_\Lambda \qquad \forall \psi \in W_{h,k}^0(\Lambda).  
+\end{equation*} 
+Then, $P_h$ is continuous on $H^{\frac 12}_{00}(\Lambda)$, namely
+\begin{equation*}
+\|P_h v\|_{H^{\frac 12}_{00}(\Lambda)} \leq C \|v\|_{H^{\frac 12}_{00}(\Lambda)},
+\end{equation*}
+where $C$ is a positive constant independent of $h$.
+\end{lemma}
+
+\begin{lemma}\label{infsup_avr_trspace}
+There exist a constant $\gamma >0$ such that
+\begin{equation*}
+\sup_{\substack{q_h \in W_{h,k}^0(\Lambda)}} \frac{\langle q_h , M_h \rangle}{ \|q_h\|_{H^{\frac 12}(\Lambda)}} \geq \gamma \|M_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall M_h \in W_{h,k}^0(\Lambda).
+\end{equation*} 
+\end{lemma}
+
+\begin{theorem}[Discrete inf-sup]
+$\exists \gamma _2 >0$ s.t.
+\begin{equation}
+\inf_{M_h \in Q_h(\Lambda)} 
+\sup_{\substack{vh \in X^0_{h,k}(\Omega),\\ {\vd}_h \in X^0_{h,k}(\Lambda)} }\frac{\langle \Pi_1 v_h - \Pi_2 {\vd}_h, M_h \rangle _{\Lambda} } {\vertiii{[v_h, {\vd}_h]} \|M_h\|_{H^{-\frac 12 }(\Lambda)} }
+\geq \gamma _2. 
+\end{equation}
+\end{theorem}
+\begin{proof}
+Let $M_h$ be arbitrarly chosen in $W_{h,k}^0(\Lambda)$. Again, we choose ${\vd}_h =0$, so that the proof reduces to show that there exists $\gamma_2$ s.t.
+\begin{equation*}
+\gamma _2 \|M_h\|_{H^{-\frac 12}(\Lambda)}
+\leq 
+\sup_{v_h \in X_{h,k}^0(\Omega)} \frac{ \langle \Pi_2 v_h , M_h \rangle _{\Lambda} } {\|v_h\|_{H^1(\Omega)} } \qquad \forall M_h \in W_{h,k}^0(\Lambda).
+\end{equation*}
+Let us denote with $\mathcal{U}_E$ the uniform extension operator from $\Lambda$ to $\Gamma$. Using Lemma \ref{lemma:H12norm_avrc}, we easily have for any $w \in H^{\frac 12}(\Lambda)$,
+\begin{equation*}
+\|\mathcal{U}_E w\|_{H^{\frac 12}(\Gamma)}=|\DD| \|w\|_{H^{\frac 12}(\Lambda)}.
+\end{equation*}
+Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $E$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X^0_{h,k}(\Omega)$, we obtain
+\begin{multline}
+\gamma \|M_h\|_{H^{-\frac 12}(\Lambda)} \leq 
+\sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, M_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
+\\
+= |\DD| \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, M_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
+\leq |\DD|\|E\| \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, M_h \rangle _{\Lambda} } {\|E \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
+\\
+\leq |\DD|\|E\| C_R \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, M_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
+\\ 
+=  |\DD|\|E\| C_R \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E q_h, M_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
+\\
+\leq |\DD|\|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi _2  v_h, M_h \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
+\end{multline}
+\end{proof}

### 2019-05-04 stab/stab.tex
work on numerics report

% SIAM Article Template
\documentclass[r]{siamart171218}
% Packages and macros go here
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{array}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{float}
\usepackage{fullpage}
\usepackage{color}
\usepackage{enumitem}  
\usepackage{epstopdf}

% Title. If the supplement option is on, then "Supplementary Material"
% is automatically inserted before the title.
%\title{On the weak coupling of 3D and 1D second order elliptic problems}
\title{Coupling PDEs on XD-YD domains with Lagrange multipliers}

% Authors: full names plus addresses.
\author{Yes}

\begin{document}

\maketitle

% REQUIRED
\begin{abstract}
  This note summarizes numerical experiments investigating stabilization
  techniques for coupled multiscale problems using Lagrange multipliers. 
\end{abstract}

% REQUIRED
\begin{keywords}
No
\end{keywords}

% REQUIRED
\begin{AMS}
n.a.
\end{AMS}

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>

\newcommand{\semi}[1]{\lvert{#1}\rvert}
\newcommand{\norm}[1]{\lVert{#1}\rVert}

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}{Property}[section]
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

\section{Babu{\v s}ka problem}\label{sec:babuska}
We consider the Poisson problem with boundary conditions enforced by
Lagrange multiplier. Given bounded $\Omega\subset\mathbb{R}^2$, let $\Gamma_D$,
$\Gamma_L\subset \partial \Omega$ be such that $\semi{\Gamma_i}\neq 0$,
$i\in\left\{D, L\right\}$, $\bigcup_{i}\Gamma_i=\partial\Omega$.
We then consider the Poisson problem
\[
\begin{aligned}
-\Delta u &= f &\mbox{ in }\Omega,\\
u &= g &\mbox{ on }\Gamma_D,\\
u &= g &\mbox{ on }\Gamma_L,\\
\end{aligned}
\]
which upon introducing the Lagrange multiplier $p\in Q=(H^{1/2}_{00}(\Gamma_L))^{\prime}$
leads to a variational problem: Find $u\in V=H^1_{0, \Gamma_D}(\Omega)$,
$p\in Q$ such that
%
\begin{equation}\label{eq:bab}
  \begin{aligned}
    &\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v - \int_{\Gamma_N}h v &\forall v\in V,\\
    &\int_{\Gamma_L}q u  &\phantom{+\int_{\Omega} \nabla u\cdot \nabla v} &= \int_{\Gamma} g q &\forall q\in Q.
  \end{aligned}
\end{equation}
%

In the following experiments $\Omega=(0, 1)^2$, $\Gamma_L=\left\{(x, y)\in\partial\Omega; x=0\right\}$
while $\Gamma_D=\partial\Omega\setminus \Gamma_L$.

\subsection{Discretization by P1-P1 elements}\label{sec:p1_p1}

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{iters} & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{iters} & $\kappa$ \\
    \hline
8.84E-02 & 6.91E+00(--)   & 6.37E+00(--)   & 29 & 5.131 & 6.90E+00(--)  & 5.94E+00(--)    & 31 & 4.836\\
4.42E-02 & 3.54E+00(0.97) & 1.61E+00(1.98) & 26 & 5.176 & 3.54E+00(0.96) & 1.76E+00(1.75) & 29 & 4.846\\
2.21E-02 & 1.78E+00(0.99) & 5.45E-01(1.56) & 26 & 5.191 & 1.78E+00(0.99) & 5.95E-01(1.57) & 28 & 4.851\\
1.10E-02 & 8.93E-01(1.00) & 3.11E-01(0.81) & 25 & 5.195 & 8.93E-01(1.00) & 3.24E-01(0.88) & 26 & 4.853\\
5.52E-03 & 4.46E-01(1.00) & 2.12E-01(0.55) & 24 & 5.196 & 4.46E-01(1.00) & 2.16E-01(0.59) & 26 & 4.853\\
2.76E-03 & 2.23E-01(1.00) & 1.49E-01(0.51) & 24 & 5.196 & 2.23E-01(1.00) & 1.50E-01(0.52) & 24 & 4.854\\
1.38E-03 & 1.12E-01(1.00) & 1.06E-01(0.50) & 22 & --    & 1.12E-01(1.00) & 1.06E-01(0.51) & 22 & --   \\
    \hline
  \end{tabular}
  }
  \caption{}
  \label{tab:p1_p1}
  \end{center}
\end{table}

\subsection{Discretization by P1-P0 elements}\label{sec:p1_p0}

\begin{table}
  \begin{center}
    \footnotesize{
  \begin{tabular}{c|cc|c|c||cc|c|c}
    \hline
    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{iters} & $\kappa$
        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{iters} & $\kappa$ \\
    \hline
8.84E-02 & 6.88E+00(--)   & 2.83E+00(--)  & 26 & 4.749  & 6.91E+00(--)   & 1.17E+01(--)  & 35 & 6.940 \\
4.42E-02 & 3.54E+00(0.96) & 2.12E+00(0.42)& 28 & 4.817  & 3.54E+00(0.96) & 2.33E+00(2.33)& 35 & 6.973 \\
2.21E-02 & 1.78E+00(0.99) & 7.42E-01(1.51)& 28 & 4.840  & 1.78E+00(0.99) & 4.91E-01(2.24)& 30 & 6.987 \\
1.10E-02 & 8.93E-01(1.00) & 2.17E-01(1.78)& 25 & 4.850  & 8.93E-01(1.00) & 1.46E-01(1.75)& 28 & 6.994 \\
5.52E-03 & 4.46E-01(1.00) & 8.90E-02(1.28)& 23 & 4.853  & 4.46E-01(1.00) & 5.90E-02(1.31)& 27 & 6.996 \\
2.76E-03 & 2.23E-01(1.00) & 4.28E-02(1.06)& 23 & 4.853  & 2.23E-01(1.00) & 2.77E-02(1.09)& 26 & 6.995 \\
1.38E-03 & 1.12E-01(1.00) & 2.12E-02(1.01)& 23 & --     & 1.12E-01(1.00) & 1.36E-02(1.02)& 25 & --    \\  
    \hline
  \end{tabular}
  }
  \caption{}
  \label{tab:p1_p1}
  \end{center}
\end{table}

%\section{Coupled multiscale problem}\label{sec:coupled}
%bar

%\bibliographystyle{siamplain}
%\bibliography{3d1d_coupled}
\end{document}

### 2019-05-06 stab/stab.tex
done babuska

@@
 \usepackage{epstopdf}
+\usepackage{tikz}
 
@@
 % Authors: full names plus addresses.
-\author{Yes}
+\author{
+Miroslav Kuchta, Federica Laurino, Kent-Andre Mardal, Paolo Zunino,\thanks{Authors are listed in alphabetical order}
+}
 
@@
 \begin{keywords}
-No
+elliptic problems, high dimensionality gap, essential coupling conditions, Lagrange multipliers
 \end{keywords}
@@
 \newcommand{\norm}[1]{\lVert{#1}\rVert}
+\newcommand{\jump}[1]{\ensuremath{[\![#1]\!]} }
+\newcommand{\avg}[1]{\ensuremath{\left\{\!\left\{#1\right\}\!\right\}} }
 
@@
 \section{Babu{\v s}ka problem}\label{sec:babuska}
-We consider the Poisson problem with boundary conditions enforced by
-Lagrange multiplier. Given bounded $\Omega\subset\mathbb{R}^2$, let $\Gamma_D$,
-$\Gamma_L\subset \partial \Omega$ be such that $\semi{\Gamma_i}\neq 0$,
+Given bounded $\Omega\subset\mathbb{R}^2$, let $\Gamma_D$, $\Gamma_L \subset \partial \Omega$ be such that $\semi{\Gamma_i}\neq 0$,
 $i\in\left\{D, L\right\}$, $\bigcup_{i}\Gamma_i=\partial\Omega$.
@@
 
+% FIXME: [OK]results in -0.5 norm
+%        is 0.5 for P1 due to bcs?
+%        image of the domain for Babuska
+%        Babuska text
+%        2d-1d-1d tables
+%        2d-1d-1d domain image
+%        2d-1d-1d text
+%
+%        H(div) case code
+%        rest of it
+
 In the following experiments $\Omega=(0, 1)^2$, $\Gamma_L=\left\{(x, y)\in\partial\Omega; x=0\right\}$
-while $\Gamma_D=\partial\Omega\setminus \Gamma_L$.
+while $\Gamma_D=\partial\Omega\setminus \Gamma_L$. Letting $\Omega_h$, $\Gamma_H$
+denote respectively the discretizations of $\Omega$ and $\Gamma_L$ we shall consider
+two different geometrical settings, cf. Figure \ref{fig:domains}, (i) either
+$\Gamma_H$ is the trace mesh (on $\Gamma_L$) of $\Omega$, i.e. there is a one-to-one
+mapping between vertices/cells of the two meshes or (ii) $\Gamma_H$ is not the
+trace mesh of $\Omega$ and $\Gamma_H$ is finer relative to the trace mesh.
+We shall subsequently refer to the two cases as \emph{matching} and \emph{non-matching}.
 
-\subsection{Discretization by P1-P1 elements}\label{sec:p1_p1}
+%
+\begin{figure}[h]
+  \begin{center}
+\begin{tikzpicture}
+  \draw[black, very thick] (1,0) rectangle (4, 3);
+  \draw[black, very thick] (1,0) -- (4, 3);
+  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega_{h}$};
+
+  \node[mark size=3pt, color=black] at (1, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (1, 3) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4, 3) {\pgfuseplotmark{*}};
+
+  \draw[black, very thick] (0.5,0) -- (0.5, 3);
+  \node[opacity=0.9, left] at (0.5, 1.5) {$\Gamma_{H}$};
+
+  \node[mark size=3pt, color=black] at (0.5, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (0.5, 3) {\pgfuseplotmark{*}};
+\end{tikzpicture}
+%
+\hspace{50pt}
+%
+\begin{tikzpicture}
+  \draw[black, very thick] (1,0) rectangle (4, 3);
+  \draw[black, very thick] (1,0) -- (4, 3);
+  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega_{h}$};
+
+  \node[mark size=3pt, color=black] at (1, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (1, 3) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4, 3) {\pgfuseplotmark{*}};
+
+  \draw[black, very thick] (0.5,0) -- (0.5, 3);
+  \node[opacity=0.9, left] at (0.5, 1.5) {$\Gamma_{H}$};
+
+  \node[mark size=3pt, color=black] at (0.5, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (0.5, 1) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (0.5, 2) {\pgfuseplotmark{*}};  
+  \node[mark size=3pt, color=black] at (0.5, 3) {\pgfuseplotmark{*}};
+\end{tikzpicture}
+%
+\end{center}
+  \caption{Two different settings considered for the Babu{\v s}ka problem
+    \eqref{eq:bab}. Trace mesh (on $\Gamma_L$) of $\Omega_h$ equals (left)
+    or differs (right) from $\Gamma_H$.
+  }
+\label{fig:domains}
+\end{figure}
+
+\subsection{Discretization by P1-P1 elements}\label{sec:p1_p1} We consider
+finite element discretization of \eqref{eq:bab} in terms continuous linear
+Lagrange elements (P1) for both spaces $V$ and $Q$.
+
+\subsubsection{Matching case} We remark that Dirichlet boundary conditions
+$p=0$ on $\partial\Gamma_L$ need to be enforced on the linear system in order
+to obtain a non-singular system matrix. Then the discretization is inf-sup
+stable as can be seen in Table \ref{tab:p1_p1} by observing that the MinRes
+iterations using the Riesz map preconditioner remain bounded in the discretization
+parameter. Note that the $Q$ block of (the diagonal) preconditioner represents
+the action of the inverse of $-\Delta^{1/2}_{00}$. In particular, the fractional
+operator is based on the eigenvalue problem
+%
+\[
+\begin{aligned}
+  -\Delta p &= \lambda p &\mbox{ in }\Gamma_L,\\
+          p &= 0         &\mbox{ on }\partial\Gamma_L.
+\end{aligned}
+\]
+%
+
+\subsubsection{Non-matching case} Here $\dim Q_H$ is (considerably) larger
+than the trace space of $V_h$ and stabilization of \cite{burman2014projection}
+is needed to obtain inf-sup stability. More precisely, the discretization
+of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
+\[
+\begin{aligned}
+&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v - \int_{\Gamma_N}h v &\forall v\in V_h,\\
+  &\int_{\Gamma_L}q u  &-\gamma \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p\cdot\nabla q &= \int_{\Gamma} g q &\forall q\in Q_H.
+  \end{aligned}
+\]
+Here $\gamma$ is a stabilization parameter and we use $\gamma=1$ in the
+following. As before, Dirichlet boundary conditions $p=0$ on $\partial\Gamma_L$ are
+enforced.
+
+MinRes iteration counts with the Riesz map preconditioner are shown in
+Table \ref{tab:p1_p1}. Here, the $Q$ block of the preconditioner is
+defined as
+\[
+\langle (-\Delta_{00})^{1/2} \bullet, q\rangle + \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla \bullet \cdot\nabla q,\quad q\in Q_H.
+\]
+%
 
@@
     \hline
-    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{iters} & $\kappa$
+    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{utters} & $\kappa$
         & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{iters} & $\kappa$ \\
@@
   }
-  \caption{}
+    \caption{Approximation errors, number of preconditioner MinRes iterations (\#) and
+      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
+      with P1-P1 elements. (left) Matching case. (right) Non-matching case.}
   \label{tab:p1_p1}
@@
 \end{table}
+%
+Concerning approximation properties of the discretization, note that the error
+for the multiplier is reported in the $L^2$ norm and not the natural $H^{-1/2}$
+norm. Nevertheless, the rate seems sub-optimal. This is likely due to the fact
+that the multiplier in the manufactured test case does not satisfy the
+Dirichlet boundary conditions employed in the discrete problem.
 
 \subsection{Discretization by P1-P0 elements}\label{sec:p1_p0}
+We consider finite element discretization of \eqref{eq:bab} in terms P1 elements
+for the space $V$ while the multiplier space used piecewise constants elements
+(P0). In both the matching and non-matching case the discretization is unstable
+and inf-sup stability is obtained by using stabilization \cite{burman2014projection}.
+That is, the disretization of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
+\[
+\begin{aligned}
+&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v - \int_{\Gamma_N}h v &\forall v\in V_h,\\
+  &\int_{\Gamma_L}q u  &-\gamma \sum_{\mathcal{V}^0} \avg{H_K}^2\jump{p}\jump{q} &= \int_{\Gamma} g q &\forall q\in Q_H,
+  \end{aligned}
+\]
+where $\mathcal{V}^0$ is the set of all interior vertices of $\Gamma_H$.
+
+Table \ref{tab:p1_p0} shows stability and convergence properties of the approximation.
+Note that the error in the multiplier converges linearly, cf. $\tfrac{1}{2}$ for
+the P1-P1 discretization in Table \ref{tab:p1_p1}.
 
@@
     }
-  \caption{}
-  \label{tab:p1_p1}
+    \caption{Approximation errors, number of preconditioner MinRes iterations (\#) and
+      condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
+      with P1-P0 elements. (left) Matching case. (right) Non-matching case.}
+  \label{tab:p1_p0}
   \end{center}
@@
 
-%\section{Coupled multiscale problem}\label{sec:coupled}
-%bar
+\section{Coupled multiscale problem}\label{sec:coupled} As a stepping stone
+towards the coupled 3$d$-1$d$-1$d$ problem we consider first a coupled multiscale
+problem where the dimensionality gap is 1. Given two bounded domains $\Omega^i \subset\mathbb{R}^2$,
+$i=\left\{-, +\right\}$, let $\Gamma$ be the intersection of the domain boundaries,
+cf. Figure \ref{fig:coupled_domain}. We are then interested in solving
 
-%\bibliographystyle{siamplain}
-%\bibliography{3d1d_coupled}
+\begin{minipage}{0.47\textwidth}
+  \begin{equation}
+    \begin{aligned}
+      -\Delta u^i &= f &\mbox{ in }\Omega^{i}, i\in\left\{+, -\right\},\\
+      u^i &= g^i &\mbox{ on }\partial\Omega^{i}\setminus\Gamma,\\
+      \jump{u} &= 0 &\mbox{ on }\Gamma,\\
+      -\Delta \hat{u} + \jump{\nabla u\cdot n}&= \hat{f} &\mbox{ on }\Gamma,\\
+      \hat{u} &= \hat{g} &\mbox{ on }\partial\Gamma,\\
+      u - \hat{u} &= g&\mbox{ on }\Gamma.\\
+    \end{aligned}
+\end{equation}
+\null
+\par\xdef\tpd{\the\prevdepth}
+\end{minipage}
+\hfill
+\begin{minipage}{0.47\textwidth}
+  \begin{figure}[H]
+    \begin{center}
+\begin{tikzpicture}
+  \draw[black, very thick] (0,0) rectangle (4, 4);
+  \draw[black, very thick] (2, 0) rectangle (2, 4);
+
+  \node[fill=white, opacity=0.9] at (1, 2) {$\Omega^{-}$};
+  \node[fill=white, opacity=0.9] at (3, 2) {$\Omega^{+}$};
+
+  \draw[->, black] (2, 1) -- (3, 1);
+  \node[fill=white, opacity=0.9, above] at (2.5, 1) {$n$};
+  \node[fill=white, opacity=0.9, right] at (2.025, 2) {$\Gamma$};
+\end{tikzpicture}
+    \end{center}
+    %\vspace{-20pt}
+    \caption{Schematic domain coupled multiscale problem.}
+    \label{fig:coupled_domain}
+    %\vspace{5pt}    
+\end{figure}
+\end{minipage}
+%
+
+\bibliographystyle{siamplain}
+\bibliography{stab}
 \end{document}

### 2019-05-07 stab/stab.tex
multiscale results

@@
 \usepackage[english]{babel}
+\usepackage{fullpage}
 \usepackage{amsmath}
@@
   techniques for coupled multiscale problems using Lagrange multipliers.
+  These are personal notes written to keep track of the developments on this
+  topic, to be kept confidential.
 \end{abstract}
@@
   \begin{aligned}
-    &\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v - \int_{\Gamma_N}h v &\forall v\in V,\\
+    &\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V,\\
     &\int_{\Gamma_L}q u  &\phantom{+\int_{\Omega} \nabla u\cdot \nabla v} &= \int_{\Gamma} g q &\forall q\in Q.
@@
 %
-
-% FIXME: [OK]results in -0.5 norm
-%        is 0.5 for P1 due to bcs?
-%        image of the domain for Babuska
-%        Babuska text
-%        2d-1d-1d tables
-%        2d-1d-1d domain image
-%        2d-1d-1d text
-%
-%        H(div) case code
-%        rest of it
 
@@
 \subsubsection{Non-matching case} Here $\dim Q_H$ is (considerably) larger
-than the trace space of $V_h$ and stabilization of \cite{burman2014projection}
+than the trace space of $V_h$ and stabilization of \cite{burman2009interior}
 is needed to obtain inf-sup stability. More precisely, the discretization
 of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
-\[
+%
+\begin{equation}\label{eq:p1_stab}
 \begin{aligned}
-&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v - \int_{\Gamma_N}h v &\forall v\in V_h,\\
+&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_h,\\
   &\int_{\Gamma_L}q u  &-\gamma \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p\cdot\nabla q &= \int_{\Gamma} g q &\forall q\in Q_H.
   \end{aligned}
-\]
+\end{equation}
+%
 Here $\gamma$ is a stabilization parameter and we use $\gamma=1$ in the
-following. As before, Dirichlet boundary conditions $p=0$ on $\partial\Gamma_L$ are
-enforced.
+following. As before, the trial and test functions of the space $Q_H$ are
+constructed such that they satisfy the boundary conditions $p=0$ on $\partial\Gamma_L$.
 
 MinRes iteration counts with the Riesz map preconditioner are shown in
-Table \ref{tab:p1_p1}. Here, the $Q$ block of the preconditioner is
-defined as
+Table \ref{tab:p1_p1}. Here, the $Q$ block of the preconditioner is based
+on the inverse of the bilinear 
 \[
-\langle (-\Delta_{00})^{1/2} \bullet, q\rangle + \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla \bullet \cdot\nabla q,\quad q\in Q_H.
+\langle (-\Delta_{00})^{1/2} p, q\rangle + \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p \cdot\nabla q,\quad p, q\in Q_H.
 \]
@@
     \hline
-    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{utters} & $\kappa$
-        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{iters} & $\kappa$ \\
+    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
+        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
     \hline
@@
   }
-    \caption{Approximation errors, number of preconditioner MinRes iterations (\#) and
+    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
       condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
@@
 That is, the disretization of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
-\[
+%
+\begin{equation}\label{eq:p0_stab}
 \begin{aligned}
-&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v - \int_{\Gamma_N}h v &\forall v\in V_h,\\
+&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_h,\\
   &\int_{\Gamma_L}q u  &-\gamma \sum_{\mathcal{V}^0} \avg{H_K}^2\jump{p}\jump{q} &= \int_{\Gamma} g q &\forall q\in Q_H,
   \end{aligned}
-\]
+\end{equation}
+%
 where $\mathcal{V}^0$ is the set of all interior vertices of $\Gamma_H$.
@@
     \hline
-    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{iters} & $\kappa$
-        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & \#{iters} & $\kappa$ \\
+    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
+        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
     \hline
@@
     }
-    \caption{Approximation errors, number of preconditioner MinRes iterations (\#) and
+    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
       condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
@@
 problem where the dimensionality gap is 1. Given two bounded domains $\Omega^i \subset\mathbb{R}^2$,
-$i=\left\{-, +\right\}$, let $\Gamma$ be the intersection of the domain boundaries,
+$i\in\left\{-, +\right\}$, let $\Gamma$ be the intersection of the domain boundaries,
 cf. Figure \ref{fig:coupled_domain}. We are then interested in solving
@@
 \begin{minipage}{0.47\textwidth}
-  \begin{equation}
+  \begin{equation}\label{eq:coupled}
     \begin{aligned}
       -\Delta u^i &= f &\mbox{ in }\Omega^{i}, i\in\left\{+, -\right\},\\
-      u^i &= g^i &\mbox{ on }\partial\Omega^{i}\setminus\Gamma,\\
+      u^i &= g^i &\mbox{ on }\Gamma^i_D\partial\Omega^{i}\setminus\Gamma,\\
       \jump{u} &= 0 &\mbox{ on }\Gamma,\\
-      -\Delta \hat{u} + \jump{\nabla u\cdot n}&= \hat{f} &\mbox{ on }\Gamma,\\
+      -\Delta \hat{u} - \jump{\nabla u\cdot n}&= \hat{f} &\mbox{ on }\Gamma,\\
       \hat{u} &= \hat{g} &\mbox{ on }\partial\Gamma,\\
-      u - \hat{u} &= g&\mbox{ on }\Gamma.\\
+      u - \hat{u} &= h&\mbox{ on }\Gamma.\\
     \end{aligned}
@@
 \begin{tikzpicture}
-  \draw[black, very thick] (0,0) rectangle (4, 4);
-  \draw[black, very thick] (2, 0) rectangle (2, 4);
+  \draw[black!60!white, very thick] (0,0) rectangle (4, 4);
+  \draw[black!60!white, very thick] (2, 0) rectangle (2, 4);
 
-  \node[fill=white, opacity=0.9] at (1, 2) {$\Omega^{-}$};
-  \node[fill=white, opacity=0.9] at (3, 2) {$\Omega^{+}$};
+  \node[black!60!white, fill=white, opacity=0.9] at (1, 2) {$\Omega^{-}$};
+  \node[black!60!white, fill=white, opacity=0.9] at (3, 2) {$\Omega^{+}$};
+  \node[black!60!white, fill=white, opacity=0.9, right] at (4, 0) {$\Gamma_D$};
 
+  \draw[black, very thick] (2, 0) -- (2, 4);
   \draw[->, black] (2, 1) -- (3, 1);
@@
     %\vspace{-20pt}
-    \caption{Schematic domain coupled multiscale problem.}
+    \caption{Schematic domain of coupled multiscale problem.}
     \label{fig:coupled_domain}
@@
 %
+Let $\Omega=\Omega^{+}\cup\Omega^{-}$ and $\Gamma_D=\Gamma^{+}_D\cup\Gamma^{-}_N$.
+Introducing a Lagrange multiplier $p=\jump{\nabla\cdot n}\in Q=(H^{-1/2}_{00}(\Gamma))^{\prime}$
+the weak form of \eqref{eq:coupled} reads: Find $u\in V=H^1_{0, \Gamma_D}(\Omega)$,
+$\hat{v}\in\hat{V}=H^1_{0, \partial\Gamma}(\Gamma)$, $p\in Q$ such that
+%
+\begin{equation}\label{eq:coupled_weak}
+  \begin{aligned}
+    &\int_{\Omega}\nabla u\cdot \nabla v &\phantom{+\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &+\int{\Gamma}p v &= \int_{\Omega}f v \quad &\forall v\in V,\\
+    &\phantom{\int_{\Omega}\nabla u\cdot \nabla v} &+{\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &-\int{\Gamma}p\hat{v} &= \int_{\Gamma}\hat{f}\hat{v} \quad &\forall \hat{v}\in \hat{V},\\
+    &\int_{\Gamma}u q &-\int_{\Gamma}\hat{u}q &\phantom{-\int{\Gamma}q\hat{v}} &= \int_{\Gamma}h q \quad &\forall q\in Q.
+  \end{aligned}
+\end{equation}
+%
+\begin{figure}[h]
+  \begin{center}
+    \begin{tikzpicture}[scale=0.60]
+      % Minus
+  \draw[black, very thick] (1,0) rectangle (4, 3);
+  \draw[black, very thick] (1,0) -- (4, 3);
+  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega^{-}_{h}$};
+
+  \node[mark size=3pt, color=black] at (1, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (1, 3) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4, 3) {\pgfuseplotmark{*}};
+
+  \draw[black, thin, dotted] (4, 0) -- (4.5, 0);
+  \draw[black, thin, dotted] (4, 3) -- (4.5, 3);
+  % Center
+  \draw[black, thin, dotted] (4.5, 0) -- (5, 0);
+  \draw[black, thin, dotted] (4.5, 3) -- (5, 3);
+
+  \draw[black, very thick] (4.5,0) -- (4.5, 3);
+  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{H}$};
+
+  \node[mark size=3pt, color=black] at (4.5, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4.5, 3) {\pgfuseplotmark{*}};
+  % Right
+    \draw[black, very thick] (5,0) rectangle (8, 3);
+  \draw[black, very thick] (5,0) -- (8, 3);
+  \node[fill=white, opacity=0.9] at (6.5, 1.5) {$\Omega^{+}_{h}$};
+
+  \node[mark size=3pt, color=black] at (5, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (8, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (5, 3) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (8, 3) {\pgfuseplotmark{*}};
+\end{tikzpicture}
+    %
+    \hspace{10pt}
+    \begin{tikzpicture}[scale=0.60]
+      % Minus
+  \draw[black, very thick] (1,0) rectangle (4, 3);
+  \draw[black, very thick] (1,0) -- (4, 3);
+  \node[fill=white, opacity=0.9] at (2.75, 1.5) {$\Omega^{-}_{h}$};
+
+  \node[mark size=3pt, color=black] at (1, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (1, 3) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4, 3) {\pgfuseplotmark{*}};
+
+  \draw[black, thin, dotted] (4, 0) -- (4.5, 0);
+  \draw[black, thin, dotted] (4, 3) -- (4.5, 3);
+  % Center
+  \draw[black, thin, dotted] (4.5, 0) -- (5, 0);
+  \draw[black, thin, dotted] (4.5, 3) -- (5, 3);
+     % Center
+  \draw[black, very thick] (4.5,0) -- (4.5, 3);
+  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{H}$};
+
+  \node[mark size=3pt, color=black] at (4.5, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4.5, 1) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4.5, 2) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4.5, 3) {\pgfuseplotmark{*}};
+  % Right
+    \draw[black, very thick] (5,0) rectangle (8, 3);
+  \draw[black, very thick] (5,0) -- (8, 3);
+  \node[fill=white, opacity=0.9] at (6.5, 1.5) {$\Omega^{+}_{h}$};
+
+  \node[mark size=3pt, color=black] at (5, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (8, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (5, 3) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (8, 3) {\pgfuseplotmark{*}};
+    \end{tikzpicture}
+        %
+    \hspace{10pt}
+    \begin{tikzpicture}[scale=0.60]
+      % Minus
+  \draw[black, very thick] (0,0) rectangle (3, 3);
+  \draw[black, very thick] (0,0) -- (3, 3);
+  \node[fill=white, opacity=0.9] at (2.25, 1.5) {$\Omega^{-}_{h}$};
+
+  \node[mark size=3pt, color=black] at (0.0, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (3.0, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (0.0, 3) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (3.0, 3) {\pgfuseplotmark{*}};
+
+     % Center
+  \draw[black, very thick] (4.5,0) -- (4.5, 3);
+  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{H}$};
+
+  \node[mark size=3pt, color=black] at (4.5, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4.5, 1) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4.5, 2) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4.5, 3) {\pgfuseplotmark{*}};
+
+  \draw[black, very thick] (3,0) -- (6, 0);
+  \draw[black, very thick] (3,0) -- (6, 3);
+  \draw[black, very thick] (3,3) -- (6, 3);  
+  % Right
+    \draw[black, very thick] (6,0) rectangle (9, 3);
+  \draw[black, very thick] (6,0) -- (9, 3);
+  \node[fill=white, opacity=0.9] at (6.75, 1.5) {$\Omega^{+}_{h}$};
+
+  \node[mark size=3pt, color=black] at (6, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (9, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (6, 3) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (9, 3) {\pgfuseplotmark{*}};
+\end{tikzpicture}
+%
+\end{center}
+  \caption{Different mesh settings considered for the coupled problem
+    \eqref{eq:coupled_weak}: conforming matching, conforming non-matching,
+    non-conforming (from left to right).
+  }
+\label{fig:multi_domains}
+\end{figure}
+%
+In the following $\Omega=(0, 1)$, $\Gamma=\left\{(x, y)\in\Omega; x=\tfrac{1}{2}\right\}$
+and based on the properties of the finite element meshes $\Omega_h$, $\Gamma_H$
+we shall distinguish three different settings, cf. Figure \ref{fig:multi_domains}.
+Here, a conforming case implies that the trace mesh of $\Omega_h$ on $\Gamma$
+consists only of the existing facets of the mesh. In the conforming setting 
+we consider matching and non-matching cases as defined above. Let us also
+remark that the approximation of the space $\hat{V}$ shall always be constructed
+on the multiplier mesh $\Gamma_H$.
+
+\subsubscection{P1-P1-P1 discretization with $\Gamma$ conformity}
+
+\begin{table}
+  \begin{center}
+    \scriptsize{
+  \begin{tabular}{c|ccc|c|c||ccc|c|c}
+    \hline
+    $h$ & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
+        & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
+    \hline
+8.8E-2 & 8.8E-1(--)   & 2.0E0(--)    & 8.9E-1(--)   & 20 & 8.0 & 8.6E-1(--)   & 6.7E-1(--)   & 1.7E-1(--)   & 23 & 4.5  \\
+4.4E-2 & 4.4E-1(1.01) & 1.0E0(0.99)  & 2.1E-1(2.10) & 22 & 8.4 & 4.4E-1(0.99) & 3.4E-1(1.00) & 4.5E-2(1.89) & 25 & 4.5  \\
+2.2E-2 & 2.2E-1(1.00) & 5.0E-1(1.00) & 5.1E-2(2.03) & 22 & 8.5 & 2.2E-1(1.00) & 1.7E-1(1.00) & 1.2E-2(1.95) & 25 & 4.6  \\
+1.1E-2 & 1.1E-1(1.00) & 2.5E-1(1.00) & 1.3E-2(2.01) & 21 & 8.6 & 1.1E-1(1.00) & 8.4E-2(1.00) & 3.0E-3(1.98) & 24 & 4.7  \\
+5.5E-3 & 5.5E-2(1.00) & 1.3E-1(1.00) & 3.2E-3(2.00) & 21 & 8.7 & 5.5E-2(1.00) & 4.2E-2(1.00) & 7.5E-4(1.99) & 24 & 4.7  \\
+2.8E-3 & 2.7E-2(1.00) & 6.3E-2(1.00) & 7.9E-4(2.00) & 21 & 8.7 & 2.7E-2(1.00) & 2.1E-2(1.00) & 1.9E-4(1.99) & 22 & 4.7  \\
+1.4E-3 & 1.4E-2(1.00) & 3.1E-2(1.00) & 2.0E-4(2.00) & 21 & --  & 1.4E-2(1.00) & 1.0E-2(1.00) & 4.7E-5(2.00) & 22 & --   \\
+    \hline
+  \end{tabular}
+    }
+    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
+      condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
+      with P1-P1-P1 elements. Conforming (left) matching and (right) non-matching case.}
+  \label{tab:coupled_p1_p1}
+  \end{center}
+\end{table}
+
+% --------------------------------------------------------------------
+
+\subsubscection{P1-P1-P0 discretization with $\Gamma$ conformity}
+
+\begin{table}
+  \begin{center}
+    \scriptsize{
+  \begin{tabular}{c|ccc|c|c||ccc|c|c}
+    \hline
+    $h$ & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
+        & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
+    \hline
+8.8E-2 & 9.3E-1(--)   & 2.0E0(--)    & 2.9E0(--)    & 21 & 4.5 & 8.6E-1(--)   & 6.7E-1(--)   & 9.2E-1(--)   & 29 & 7.8\\
+4.4E-2 & 4.4E-1(1.06) & 1.0E0(0.99)  & 1.1E0(1.43)  & 28 & 4.8 & 4.4E-1(0.99) & 3.4E-1(1.00) & 3.4E-1(1.42) & 31 & 8.1\\
+2.2E-2 & 2.2E-1(1.02) & 5.0E-1(1.00) & 4.1E-1(1.39) & 28 & 5.0 & 2.2E-1(1.00) & 1.7E-1(1.00) & 1.4E-1(1.34) & 32 & 8.3\\
+1.1E-2 & 1.1E-1(1.00) & 2.5E-1(1.00) & 1.7E-1(1.28) & 27 & 5.1 & 1.1E-1(1.00) & 8.4E-2(1.00) & 5.6E-2(1.26) & 30 & 8.4\\
+5.5E-3 & 5.5E-2(1.00) & 1.3E-1(1.00) & 7.5E-2(1.19) & 27 & 5.2 & 5.5E-2(1.00) & 4.2E-2(1.00) & 2.5E-2(1.18) & 30 & 8.5\\
+2.8E-3 & 2.7E-2(1.00) & 6.3E-2(1.00) & 3.5E-2(1.11) & 27 & 5.2 & 2.7E-2(1.00) & 2.1E-2(1.00) & 1.1E-2(1.11) & 29 & 8.5\\
+1.4E-3 & 1.4E-2(1.00) & 3.1E-2(1.00) & 1.7E-2(1.07) & 27 & --  & 1.4E-2(1.00) & 1.0E-2(1.00) & 5.5E-3(1.06) & 29 & -- \\
+    \hline
+  \end{tabular}
+    }
+    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
+      condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
+      with P1-P1-P0 elements. Conforming (left) matching and (right) non-matching case.}
+  \label{tab:coupled_p1_p0}
+  \end{center}
+\end{table}
+
+% -------------------------------------------------------------------
+
+\subsubscection{Non-conforming setting}
+
+\begin{table}
+  \begin{center}
+    \scriptsize{
+  \begin{tabular}{c|ccc|c|c||ccc|c|c}
+    \hline
+    $h$ & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
+        & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
+    \hline
+8.3E-2 & 1.3E0(--)    & 7.0E-1(--)   & 1.2E0(--)    & 28 & 5.2 & 1.3E0(--)    & 7.0E-1(--)   & 1.7E0(--)     & 31 & 8.6\\   
+4.3E-2 & 8.1E-1(0.68) & 3.5E-1(1.04) & 6.4E-1(0.95) & 29 & 5.6 & 8.1E-1(0.68) & 3.5E-1(1.04) & 7.6E-1(1.18)  & 34 & 9.3\\ 
+2.2E-2 & 5.3E-1(0.62) & 1.8E-1(1.02) & 3.3E-1(0.99) & 29 & 5.8 & 5.3E-1(0.62) & 1.8E-1(1.02) & 3.6E-1(1.10)  & 34 & 9.7\\ 
+1.1E-2 & 3.6E-1(0.57) & 8.8E-2(1.01) & 1.6E-1(1.00) & 27 & 6.0 & 3.6E-1(0.57) & 8.8E-2(1.01) & 1.8E-1(1.05)  & 34 & 9.9\\ 
+5.5E-3 & 2.5E-1(0.54) & 4.4E-2(1.01) & 8.3E-2(1.00) & 27 & 6.0 & 2.5E-1(0.54) & 4.4E-2(1.01) & 8.7E-2(1.03)  & 33 & 10.0\\
+2.8E-3 & 1.7E-1(0.52) & 2.2E-2(1.00) & 4.1E-2(1.00) & 26 & 6.1 & 1.7E-1(0.52) & 2.2E-2(1.00) & 4.3E-2(1.01)  & 32 & 10.0\\
+1.4E-3 & 1.2E-1(0.51) & 1.1E-2(1.00) & 2.1E-2(1.00) & 26 & --  & 1.2E-1(0.51) & 1.1E-2(1.00) & 2.1E-2(1.01)  & 31 & 10.0\\
+    \hline
+  \end{tabular}
+    }
+    \caption{Non-conforming setting. Approximation errors, number of preconditioner MinRes iterations ($n$) and
+      condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
+      with P1-P1-P1 (left) and P1-P1-P0 (right) elements.}
+  \label{tab:coupled_non}
+  \end{center}
+\end{table}
 

### 2019-05-07 stab/stab.tex
done

@@
 \end{center}
-  \caption{Two different settings considered for the Babu{\v s}ka problem
-    \eqref{eq:bab}. Trace mesh (on $\Gamma_L$) of $\Omega_h$ equals (left)
-    or differs (right) from $\Gamma_H$.
-  }
+  \caption{Matching (left) and non-mathching (right) setting considered
+    for the Babu{\v s}ka problem.}
 \label{fig:domains}
@@
 Table \ref{tab:p1_p1}. Here, the $Q$ block of the preconditioner is based
-on the inverse of the bilinear 
+on the inverse of the bilinear form
 \[
-\langle (-\Delta_{00})^{1/2} p, q\rangle + \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p \cdot\nabla q,\quad p, q\in Q_H.
+\langle -\Delta_{00}^{1/2} p, q\rangle + \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p \cdot\nabla q,\quad p, q\in Q_H.
 \]
@@
   }
-    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
+    \caption{Approximation errors, number of preconditioned MinRes iterations ($n$) and
       condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
@@
 We consider finite element discretization of \eqref{eq:bab} in terms P1 elements
-for the space $V$ while the multiplier space used piecewise constants elements
+for the space $V$ while the multiplier space uses piecewise constants elements
 (P0). In both the matching and non-matching case the discretization is unstable
@@
     }
-    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
+    \caption{Approximation errors, number of preconditioned MinRes iterations ($n$) and
       condition number of the preconditioned problem \eqref{eq:bab} ($\kappa$) discretized
@@
       -\Delta u^i &= f &\mbox{ in }\Omega^{i}, i\in\left\{+, -\right\},\\
-      u^i &= g^i &\mbox{ on }\Gamma^i_D\partial\Omega^{i}\setminus\Gamma,\\
+      u^i &= g^i &\mbox{ on }\Gamma^i_D=\partial\Omega^{i}\setminus\Gamma,\\
       \jump{u} &= 0 &\mbox{ on }\Gamma,\\
@@
 consists only of the existing facets of the mesh. In the conforming setting 
-we consider matching and non-matching cases as defined above. Let us also
-remark that the approximation of the space $\hat{V}$ shall always be constructed
+we consider matching and non-matching cases as defined above. We remark
+that the approximation of the space $\hat{V}$ shall always be constructed
 on the multiplier mesh $\Gamma_H$.
 
-\subsubscection{P1-P1-P1 discretization with $\Gamma$ conformity}
+\subsection{P1-P1-P1 discretization with $\Gamma$ conformity}
+Let us first consider a conforming setting and an approximation of all
+the spaces involved in \eqref{eq:coupled_weak} in terms of P1 elements.
+As with the Babu{\v s}ka problem \eqref{eq:bab} the discrete multiplier
+space is such that $q=0$ on $\partial\Gamma$ for all $q\in Q_H$. In fact,
+the boundary conditions are necessary to obtain an invertible linear system.
+
+Table \ref{tab:coupled_p1_p1} summarizes the results for both matching
+and non-matching tessilations. In the latter case, a stabilization term
+\cite{burman2009interior} is added similar to \eqref{eq:p1_stab} (we set $\gamma=1$).
+In both cases the results show evidence of the inf-sup stability of the
+discretization. We note that the $L^2$ error of the multiplier converges
+quadratically; in contrast to the test problem in \eqref{eq:bab} the solution
+here \emph{does} satisfy $p=0$ on $\partial\Gamma$.
 
@@
     }
-    \caption{Approximation errors, number of preconditioner MinRes iterations ($n$) and
+    \caption{Approximation errors, number of preconditioned MinRes iterations ($n$) and
       condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
@@
 
-\subsubscection{P1-P1-P0 discretization with $\Gamma$ conformity}
+\subsection{P1-P1-P0 discretization with $\Gamma$ conformity} 
+We shall next have the multiplier space be spanned by piecewise constant
+functions. Following \eqref{eq:bab} a stabilization \cite{burman2014projection}
+is employed in both the matching and non-matching cases. Table \ref{tab:coupled_p1_p0}
+confirms that the discretization is inf-sup stable.
 
@@
 
-\subsubscection{Non-conforming setting}
+\subsection{Non-conforming setting}
+Finally a non-conforming setting is considered with P1-P1-P1 and P1-P1-P0
+discretizations. In both cases stabilization terms are employed to obtain
+inf-sup stability, cf. Table \ref{tab:coupled_non}. Note that compared to the
+conforming case the multiplier convergence with P1 elements is only linear.
+The order from the conforming case is preserved with P0 elements. Note also
+that with both elements $u_h$ converges with order $\tfrac{1}{2}$; the approximation
+struggles to capture the kink of the solution which now occurs within the finite element
+cells.
 
@@
     }
-    \caption{Non-conforming setting. Approximation errors, number of preconditioner MinRes iterations ($n$) and
+    \caption{Non-conforming setting. Approximation errors, number of preconditioned MinRes iterations ($n$) and
       condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized

### 2019-05-09 unfitted.tex
Add Burman P1-P1-P0 unfitted

\section{Unfitted P1-P1-P0 case}
\subsection{Problem 1} All the observations and the proofs are an application of \cite{burman2014} to our case. Let $\mathcal{T}^{\Omega}_h$ and  $\mathcal{T}^{\Lambda}_{h}$ denote a shape-regular triangulation  of $\Omega$ and an admissible partition  of $\Lambda$ respectively. Let us also introduce the set $\mathcal{G}_h$ of elements of $\mathcal{T}^{\Omega}_h$ intersecting the interface $\Gamma$, namely $\mathcal{G}_h=\left\{ K\in \mathcal{T}^{\Omega}_h : \, K\cap \Gamma \neq \emptyset \right\}$. For the discrete solutions $u_h$ and ${\ud}_h$ of the problem in $\Omega$ and on $\Lambda$ we choose the conforming spaces $X_{h,1}^0(\Omega)\subset H^1_0(\Omega)$ and  $X_{h,1}^0(\Lambda)\subset H^1_0(\Lambda)$ respectively. We extend the Lagrange multiplier $\lambda_h$ to the volume elements of $\mathcal{G}_h$ and we define $Q_h=\left\{\lambda_h: \, {\lambda_h}_{|K}\in P^0(K)\,  \forall K\in \mathcal{G}_h\right\}$. With this choice of the LM space, the problem is not inf-sup stable. We add a stabilization term $-s(\lambda_h, \mu_h)$ and we have
\begin{multline*}
a([u_h, {\ud}_h], [v_h, {\vd}_h]) + b([v_h, {\vd}_h], \lambda_h) + b([u_h, {\ud}_h], \mu_h) - s(\lambda_h, \mu_h)= (f, [v_h, {\vd}_h])\\
 \forall [v_h, {\vd}_h]\in X_h(\Omega)\times X_h(\Lambda) ,\, \forall \mu_h \in Q_h.
\end{multline*}
The stabilization $s(\lambda_h, \mu_h)$ is connected to a projector $\pi_L$ between $Q_h$ and a new space $L_h$ for the LM for which we can prove the inf-sup stability.\\
Therefore we have to build this new space $L_h$, prove that the inf-sup condition is fulfilled, build a projection operator $\pi_L: Q_h \rightarrow L_h$, build $s(\lambda_h, \mu_h)$ and prove that $\forall [u_h, {\ud}_h]$, there exists $\xi_h([u_h, {\ud}_h]) \in Q_h$ s.t.  
\begin{equation}\label{stab_coercivity}
a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h([u_h, {\ud}_h])) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X_h(\Omega)\times X_h(\Lambda) },
\end{equation}
\begin{equation}\label{stab_stability}
(s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[u_h, {\ud}_h]}_{X_h(\Omega)\times X_h(\Lambda) },
\end{equation}
being $\vertiii{\cdot }_{X_h(\Omega)\times X_h(\Lambda) }$ a suitable discrete norm. \\
The space $L_h$ is built as the space of $P^0$ functions defined on macro patches $\left\{ F_j \right\}_j$ of elements of $\mathcal{G}_h$. These patches are such that $diam(F_j)\leq H$ and  $jH\leq |F_j\cap \Gamma|\leq H+h$. Moreover, there exist constants $c_h$ and $c_H$ such that $c_hh\leq H \leq c_H^{-1}h$. To each patch $F_j$ we associate two shape regular macro elements $\omega_j$ and $\tilde{\omega}_j$: $\omega_j$ is built adding to $F_j \cap \Omega_{\oplus}$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$ contained in $\Omega_{\oplus}$, whereas $\tilde{\omega}_j$ is obtained adding to $F_j \cap\Sigma$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$ contained in $\Sigma$. Thanks to the shape regularity of these macro elements, we have that the following trace and Poincarè inequalites hold. For every function $v\in H^1(\omega_j)$,
\begin{equation}\label{discr_trace_ineq}
\|Tv\|_{\Gamma\cap \omega_j} \lesssim H^{-\frac 12} \|v\|_{L^2(\omega_j)}
\end{equation}
\begin{equation}\label{disc_poincare_ineq}
\|v- \pi_Lv\|_{L^2(\omega_j)} \leq c_P H \|\nabla v\|_{L^2(\omega_j)},
\end{equation}
being $\pi_L$ the projection onto piecewise constant functions on $F_j$.
The same also in $\tilde{\omega _j}$ for $v\in H^1(\tilde{\omega _j})$. This choice leads to the following stabilization 
\begin{equation*}
s(\lambda_h, \mu_h)= \sum _{K\in \mathcal{G}_h} \int_{\partial K \setminus \partial \mathcal{G}_h} h \llbracket \lambda_h \rrbracket \llbracket \mu_h \rrbracket,
\end{equation*}
being $\llbracket \lambda_h \rrbracket$ the jump of $\lambda_h$ across the internal faces of $\mathcal{G}_h$.
\subparagraph{Is $L_h$ inf-sup stable with constants independent of the cuts?} We have to prove that $\forall l_h \in L_h$, $\exists \beta >0$ s.t.
\begin{equation*}
\sup_{\substack{v_h \in X_{h,1}^0(\Omega),\\ {\vd}_h \in X_{h,1}^0(\Lambda)}} \frac{b([v_h, {\vd}_h], l_h)}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|l_h\|_{H^{-\frac 12}(\Gamma)}.
\end{equation*}
As in the continuous case, we can choose ${\vd}_h=0$ and we prove that
\begin{equation*} 
\sup_{v_h \in X_{h,1}^0(\Omega),\\ {\vd}_h \in X_{h,1}^0(\Lambda)} \frac{b([v_h, {\vd}_h], l_h)}{\vertiii{[v_h, {\vd}_h]}} \geq  \sup_{v_h \in X_{h,1}^0(\Omega)} \frac{b(v_h, l_h)}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|l_h\|_{H^{-\frac 12}(\Gamma)}, 
\end{equation*}
where $b(v_h, l_h)=(Tv_h,l_h)_{\Gamma} $ with a little abuse of notation. 
Proving the last inequality it is equivalent to find the Fortin operator $\pi_F: H^1_0(\Omega) \rightarrow X_{h,1}^0(\Omega)$, such that 
\begin{equation*}
b(v-\pi_F v, l_h)=0, \quad \forall v\in H^1_0(\Omega), \, l_h \in L_h
\end{equation*} 
and
\begin{equation*}
\|\pi_F v\|_{H^1(\Omega)}\lesssim \|v\|_{H^1(\Omega)}.
\end{equation*} 
We define
\begin{equation*}
\pi_F v = I_h v + \sum _j \alpha _j \varphi _j \qquad \text{with }\alpha_j =\frac{\int_{F_j \cap \Gamma}T(v-I_hv)}{\int_{F_j \cap \Gamma}T\varphi _j}
\end{equation*}
and $\varphi_j \in X_{h,1}^0(\Omega)$ s.t. supp$(\varphi_j)\subset \bar{\omega}_j$, $\varphi_j =0$ on $\partial \omega _j$ and 
\begin{equation*}
 \int_{F_j\cap \Gamma}T\varphi_j=O(H) \text{ and } \|\nabla \varphi\|_{L^2(\omega _j)}=O(1). 
\end{equation*}
This construction is always possible provided $H$ is sufficiently larger that $h$ (usually $H=3h$).
Then $b(v-\pi_F v, l_h)=0 \, \forall l_h$ follows by construction. Indeed:
\begin{multline*}
b(v-\pi_F v, l_h)= \int_{\Gamma} T(v-\pi_Fv)l_h = \sum _j \int_{F_j\cap \Gamma} \left[ T(v-I_hv)-\sum _i \alpha_i T\varphi _i \right]l_h \\
=(\text{supp} \varphi \subset \omega_j) \sum _j \int{F_j\cap \Gamma} \left[ T(v-I_hv)-\alpha_j T\varphi _j \right]l_h\\
=\sum _j \int_{F_j\cap \Gamma} T(v-I_hv) l_h - \frac{\int_{F_j\cap \Gamma} T(v-I_hv)}{\int_{F_j\cap \Gamma}T\varphi_j} \int_{F_j\cap \Gamma}T\varphi _jl_h\\ 
=(\text{using $l_h$ constant on $F_j\cap \Gamma$})\,0.
\end{multline*}
Concerning the continuity of $\pi_F$, we have
\begin{multline*}
\|\nabla \pi_F v \|_{L^2(\Omega)} \leq \|\nabla I_h v\|_{L^2(\Omega)} + \sum_j|\alpha_j|\|\nabla \varphi _j\|_{L^2(\bar{\omega}_j)}
\\
(\text{stability of }I_h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \sum_j|\alpha_j|\|\nabla \varphi _j\|_{L^2(\bar{\omega}_j)}
\\
\left(\text{using }\|\nabla \varphi\|=O(1)\right) \lesssim \|\nabla  v\|_{L^2(\Omega)} + \sum_j \frac{\left|\int_{F_j\cap \Gamma} T(v-I_h v)\right|}{\left|\int_{F_j\cap \Gamma}T\varphi _j\right|}
\\
\left(\text{since }\left|\int_{F_j\cap \Gamma}T\varphi _j\right|=O(H)\right) \lesssim  \|\nabla  v\|_{L^2(\Omega)} + \frac 1H \sum_j \left|\int_{F_j\cap \Gamma} T(v-I_h v)\right| 
\\
(\text{H\"older}) \lesssim  \|\nabla  v\|_{L^2(\Omega)} + \frac 1H \sum_j |F_j\cap \Gamma|^{\frac 12} \left(\int_{F_j\cap \Gamma} (T(v-I_h v))^2\right)^{\frac 12}
\\
(\text{being }|F_j\cap \Gamma| \leq H+h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H^{\frac 12}} \sum_j  \| v-I_h v\|_{F_j\cap \Gamma} 
\\
\left(\text{trace inequality} \right)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H} \sum_j  \| v-I_h v\|_{L^2(\omega_j)} \lesssim \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H}  \| v-I_h v\|_{L^2(\Omega)} 
\\
(\text{approximation properties of }I_h)\lesssim \|\nabla  v\|_{L^2(\Omega)}.
\end{multline*}

\subparagraph{Satisfaction of the assumptions of the 
abstract analysis} 
We have to prove \eqref{stab_coercivity} and \eqref{stab_stability}.
We choose the following discrete norm
\begin{equation*}
\vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_h(\Lambda) }
= \|u_h\|^2_{H^1(\Omega)}+|D|\|{\ud}_h\|^2_{H^1(\Lambda)} + \|u_h - {\ud}_h\|^2_{\frac 12, h, \Gamma},
\end{equation*}
where $\|u_h - {\ud}_h\|^2_{\frac 12, h, \Gamma} = \|h^{\frac 12} (u_h - {\ud}_h)\|^2_{L^2(\Gamma)} $.
Concerning the coercivity property \eqref{stab_coercivity}, we have to show that $\forall [u_h, {\ud}_h]$, there esists $\xi_h$ s.t.
\begin{equation*}
(u_h,u_h)_{H^1(\Omega)}+ |D|({\ud}_h, {\ud}_h)_{H^1(\Lambda)} +  (Tu_h -  \mathcal{U}_E {\ud}_h, \xi_h)_{\Gamma} \geq \alpha_{\xi}(\|u_h\|^2_{H^1(\Omega)}+|D|\|{\ud}_h\|^2_{H^1(\Lambda)}+ \|u_h - {\ud}_h\|^2_{\frac 12, h, \Gamma}).
\end{equation*}
We choose 
\begin{equation*}
{\xi_h}_{|F_j\cap \Gamma}=\delta \frac 1H \pi_L(u_h-{\ud}_h) \qquad \text{with } \pi_L(u_h-{\ud}_h) =\frac{1}{|F_j\cap \Gamma|}\int_{F_j\cap \Gamma} Tu_h-\mathcal{U}_E {\ud}_h.
\end{equation*}
Actually, $\xi_h\in L_h \subset Q_h$. Then,
\begin{multline*}
\left( Tu_h - \mathcal{U}_E{\ud}_h, \xi _h \right)_{\Gamma} 
= \sum_j \int_{F_j\cap \Gamma} ( Tu_h - \mathcal{U}_E{\ud}_h)\xi_h
\\
= \delta \frac{1}{H} \sum_j \int_{F_j\cap \Gamma} ( Tu_h - \mathcal{U}_E{\ud}_h) \pi_L(u_h - {\ud}_h)
\\
=\delta \frac{1}{H} \sum_j \int_{F_j\cap \Gamma}  (\pi_L(u_h - {\ud}_h))^2
\\
=\delta \frac{1}{H} \sum_j \left(\|(\pi_L - \mathcal{I})(u_h-{\ud}_h)\|^2_{L^2(F_j\cap \Gamma)}  + \|u_h-{\ud}_h\|^2_{L^2(F_j\cap \Gamma)} \right)
\\
\geq -\delta \frac 1H \sum_j \|(\pi_L - \mathcal{I})u_h\|^2_{L^2(F_j\cap \Gamma)}
- \delta \frac 1H \sum_j \|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(F_j\cap \Gamma)} 
+ \delta \frac 1H \sum_j \|u_h-{\ud}_h\|^2_{L^2(F_j\cap \Gamma)}
\\
\geq -\delta \sum_j c_P^2 \|\nabla u_h\|^2_{L^2(\omega_j)}
- \delta \sum_j c_P^2 \|\nabla  \mathcal{U}_E u_h\|^2_{L^2(\tilde{\omega}_j)}
+ \delta \frac 1H \sum_j \|u_h-{\ud}_h\|^2_{L^2(F_j\cap \Gamma)}
\\
(\text{since }c_H H \leq h ) \leq -\delta c_P^2 \|\nabla u_h\|^2_{L^2(\Omega)} - \delta c_P^2 |\D|\|\nabla {\ud}_h\|^2_{L^2(\Lambda)} + \delta c_H \|u_h-{\ud}_h\|^2_{\frac 12,h,\Gamma}. 
\end{multline*}
With a little abuse of notation we are denoting with $\mathcal{U}_E$ both the uniform extension to $\Gamma$ and $\tilde{\omega}_j$. Therefore, we obtain
\begin{multline*}
a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h([u_h, {\ud}_h]))
\geq \\
(1-\delta c_P^2) \|\nabla u_h\|^2_{L^2(\Omega)} + (1- \delta c_P^2) |\D|\|\nabla {\ud}_h\|^2_{L^2(\Lambda)}
+\delta c_H \|u_h-{\ud}_h\|^2_{\frac 12,h,\Gamma}
\end{multline*}
and choosing $\delta=\frac{1}{2c_P^2}$ we obtain the coercivity inequality.\\
Concerning the stability inequality, the proof is analogous to the one in \cite{burman2014}.

### 2019-05-09 stab/stab.tex

@@
 In the following experiments $\Omega=(0, 1)^2$, $\Gamma_L=\left\{(x, y)\in\partial\Omega; x=0\right\}$
-while $\Gamma_D=\partial\Omega\setminus \Gamma_L$. Letting $\Omega_h$, $\Gamma_H$
+while $\Gamma_D=\partial\Omega\setminus \Gamma_L$. Letting $\Omega_H$, $\Gamma_h$
 denote respectively the discretizations of $\Omega$ and $\Gamma_L$ we shall consider
 two different geometrical settings, cf. Figure \ref{fig:domains}, (i) either
-$\Gamma_H$ is the trace mesh (on $\Gamma_L$) of $\Omega$, i.e. there is a one-to-one
-mapping between vertices/cells of the two meshes or (ii) $\Gamma_H$ is not the
-trace mesh of $\Omega$ and $\Gamma_H$ is finer relative to the trace mesh.
+$\Gamma_h$ is the trace mesh (on $\Gamma_L$) of $\Omega$, i.e. there is a one-to-one
+mapping between vertices/cells of the two meshes or (ii) $\Gamma_h$ is not the
+trace mesh of $\Omega$ and $\Gamma_h$ is finer relative to the trace mesh.
 We shall subsequently refer to the two cases as \emph{matching} and \emph{non-matching}.
@@
   \draw[black, very thick] (1,0) -- (4, 3);
-  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega_{h}$};
+  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega_{H}$};
 
@@
   \draw[black, very thick] (0.5,0) -- (0.5, 3);
-  \node[opacity=0.9, left] at (0.5, 1.5) {$\Gamma_{H}$};
+  \node[opacity=0.9, left] at (0.5, 1.5) {$\Gamma_{h}$};
 
@@
 
-\subsubsection{Non-matching case} Here $\dim Q_H$ is (considerably) larger
-than the trace space of $V_h$ and stabilization of \cite{burman2009interior}
+\subsubsection{Non-matching case} Here $\dim Q_h$ is (considerably) larger
+than the trace space of $V_H$ and stabilization of \cite{burman2009interior}
 is needed to obtain inf-sup stability. More precisely, the discretization
-of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
+of \eqref{eq:bab} reads: Find $u\in V_H$, $q\in Q_h$ such that
 %
@@
 \begin{aligned}
-&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_h,\\
-  &\int_{\Gamma_L}q u  &-\gamma \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p\cdot\nabla q &= \int_{\Gamma} g q &\forall q\in Q_H.
+&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_H,\\
+  &\int_{\Gamma_L}q u  &-\gamma \sum_{K\in\Gamma_h}\int_{K} h_K^3\nabla p\cdot\nabla q &= \int_{\Gamma} g q &\forall q\in Q_h.
   \end{aligned}
@@
 Here $\gamma$ is a stabilization parameter and we use $\gamma=1$ in the
-following. As before, the trial and test functions of the space $Q_H$ are
+following. As before, the trial and test functions of the space $Q_h$ are
 constructed such that they satisfy the boundary conditions $p=0$ on $\partial\Gamma_L$.
@@
 \[
-\langle -\Delta_{00}^{1/2} p, q\rangle + \sum_{K\in\Gamma_H}\int_{K} H_K^3\nabla p \cdot\nabla q,\quad p, q\in Q_H.
+\langle -\Delta_{00}^{1/2} p, q\rangle + \sum_{K\in\Gamma_h}\int_{K} h_K^3\nabla p \cdot\nabla q,\quad p, q\in Q_h.
 \]
@@
     \hline
-    $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
-        & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
+    $h$ & $\norm{u-u_H}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
+        & $\norm{u-u_H}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
     \hline
@@
 and inf-sup stability is obtained by using stabilization \cite{burman2014projection}.
-That is, the disretization of \eqref{eq:bab} reads: Find $u\in V_h$, $q\in Q_H$ such that
+That is, the disretization of \eqref{eq:bab} reads: Find $u\in V_H$, $q\in Q_h$ such that
 %
@@
 \begin{aligned}
-&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_h,\\
-  &\int_{\Gamma_L}q u  &-\gamma \sum_{\mathcal{V}^0} \avg{H_K}^2\jump{p}\jump{q} &= \int_{\Gamma} g q &\forall q\in Q_H,
+&\int_{\Omega} \nabla u\cdot \nabla v &+ \int_{\Gamma_L}p v &= \int_{\Omega} f v &\forall v\in V_H,\\
+  &\int_{\Gamma_L}q u  &-\gamma \sum_{\mathcal{V}^0} \avg{h_K}^2\jump{p}\jump{q} &= \int_{\Gamma} g q &\forall q\in Q_h,
   \end{aligned}
@@
 %
-where $\mathcal{V}^0$ is the set of all interior vertices of $\Gamma_H$.
+where $\mathcal{V}^0$ is the set of all interior vertices of $\Gamma_h$.
 
@@
   \node[black!60!white, fill=white, opacity=0.9] at (3, 2) {$\Omega^{+}$};
-  \node[black!60!white, fill=white, opacity=0.9, right] at (4, 0) {$\Gamma_D$};
+  \node[black!60!white, opacity=0.9, right] at (4, 0) {$\Gamma_D$};
 
@@
 Let $\Omega=\Omega^{+}\cup\Omega^{-}$ and $\Gamma_D=\Gamma^{+}_D\cup\Gamma^{-}_N$.
-Introducing a Lagrange multiplier $p=\jump{\nabla\cdot n}\in Q=(H^{-1/2}_{00}(\Gamma))^{\prime}$
+Introducing a Lagrange multiplier $p=\jump{\nabla u \cdot n}\in Q=(H^{-1/2}_{00}(\Gamma))^{\prime}$
 the weak form of \eqref{eq:coupled} reads: Find $u\in V=H^1_{0, \Gamma_D}(\Omega)$,
@@
   \draw[black, very thick] (1,0) -- (4, 3);
-  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega^{-}_{h}$};
+  \node[fill=white, opacity=0.9] at (2.5, 1.5) {$\Omega^{-}_{H}$};
 
@@
   \draw[black, very thick] (4.5,0) -- (4.5, 3);
-  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{H}$};
+  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{h}$};
 
@@
   \draw[black, very thick] (5,0) -- (8, 3);
-  \node[fill=white, opacity=0.9] at (6.5, 1.5) {$\Omega^{+}_{h}$};
+  \node[fill=white, opacity=0.9] at (6.5, 1.5) {$\Omega^{+}_{H}$};
 
@@
   \draw[black, very thick] (1,0) -- (4, 3);
-  \node[fill=white, opacity=0.9] at (2.75, 1.5) {$\Omega^{-}_{h}$};
+  \node[fill=white, opacity=0.9] at (2.75, 1.5) {$\Omega^{-}_{H}$};
 
@@
   \draw[black, very thick] (0,0) -- (3, 3);
-  \node[fill=white, opacity=0.9] at (2.25, 1.5) {$\Omega^{-}_{h}$};
+  \node[fill=white, opacity=0.9] at (2.25, 1.5) {$\Omega^{-}_{H}$};
 
@@
   \draw[black, very thick] (6,0) -- (9, 3);
-  \node[fill=white, opacity=0.9] at (6.75, 1.5) {$\Omega^{+}_{h}$};
+  \node[fill=white, opacity=0.9] at (6.75, 1.5) {$\Omega^{+}_{H}$};
 
@@
 In the following $\Omega=(0, 1)$, $\Gamma=\left\{(x, y)\in\Omega; x=\tfrac{1}{2}\right\}$
-and based on the properties of the finite element meshes $\Omega_h$, $\Gamma_H$
+and based on the properties of the finite element meshes $\Omega_H$, $\Gamma_h$
 we shall distinguish three different settings, cf. Figure \ref{fig:multi_domains}.
-Here, a conforming case implies that the trace mesh of $\Omega_h$ on $\Gamma$
+Here, a conforming case implies that the trace mesh of $\Omega_H$ on $\Gamma$
 consists only of the existing facets of the mesh. In the conforming setting 
@@
 that the approximation of the space $\hat{V}$ shall always be constructed
-on the multiplier mesh $\Gamma_H$.
+on the multiplier mesh $\Gamma_h$.
 
@@
 As with the Babu{\v s}ka problem \eqref{eq:bab} the discrete multiplier
-space is such that $q=0$ on $\partial\Gamma$ for all $q\in Q_H$. In fact,
+space is such that $q=0$ on $\partial\Gamma$ for all $q\in Q_h$. In fact,
 the boundary conditions are necessary to obtain an invertible linear system.
@@
     \hline
-    $h$ & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
-        & $\norm{u-u_h}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
+    $h$ & $\norm{u-u_H}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$
+        & $\norm{u-u_H}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$ \\
     \hline

### 2019-05-17 unfitted.tex
Unfitted problem 2

@@
 \subsection{Problem 1} All the observations and the proofs are an application of \cite{burman2014} to our case.
-Let $\mathcal{T}^{\Omega}_h$ and  $\mathcal{T}^{\Lambda}_{h}$ denote a shape-regular triangulation  of $\Omega$ and an admissible partition  of $\Lambda$ respectively.
+Let $\mathcal{T}^{\Omega}_h$ and  $\mathcal{T}^{\Lambda}_{h'}$ denote a shape-regular triangulation  of $\Omega$ and an admissible partition  of $\Lambda$ respectively.
 Let us also introduce the set $\mathcal{G}_h$ of elements of $\mathcal{T}^{\Omega}_h$ intersecting the interface $\Gamma$, namely $\mathcal{G}_h=\left\{ K\in \mathcal{T}^{\Omega}_h : \, K\cap \Gamma \neq \emptyset \right\}$.
@@
 \begin{equation*}
-\sup_{\substack{v_h \in X_{h,1}^0(\Omega),\\ {\vd}_h \in X_{h,1}^0(\Lambda)}} \frac{b([v_h, {\vd}_h], l_h)}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|l_h\|_{H^{-\frac 12}(\Gamma)}.
+\sup_{\substack{v_h \in X_{h,1}^0(\Omega),\\ {\vd}_h \in X_{h',1}^0(\Lambda)}} \frac{b([v_h, {\vd}_h], l_h)}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|l_h\|_{H^{-\frac 12}(\Gamma)}.
 \end{equation*}
@@
 \vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_h(\Lambda) }
-= \|u_h\|^2_{H^1(\Omega)}+|D|\|{\ud}_h\|^2_{H^1(\Lambda)} + \|u_h - {\ud}_h\|^2_{\frac 12, h, \Gamma},
+= \|u_h\|^2_{H^1(\Omega)}+|D|\|{\ud}_h\|^2_{H^1(\Lambda)} + \|u_h - {\ud}_h\|^2_{-\frac 12, h, \Gamma},
 \end{equation*}
-where $\|u_h - {\ud}_h\|^2_{\frac 12, h, \Gamma} = \|h^{\frac 12} (u_h - {\ud}_h)\|^2_{L^2(\Gamma)} $.
+where $\|u_h - {\ud}_h\|^2_{-\frac 12, h, \Gamma} = \|h^{\frac 12} (u_h - {\ud}_h)\|^2_{L^2(\Gamma)} $.
 Concerning the coercivity property \eqref{stab_coercivity}, we have to show that $\forall [u_h, {\ud}_h]$, there esists $\xi_h$ s.t.
 \begin{equation*}
-(u_h,u_h)_{H^1(\Omega)}+ |D|({\ud}_h, {\ud}_h)_{H^1(\Lambda)} +  (Tu_h -  \mathcal{U}_E {\ud}_h, \xi_h)_{\Gamma} \geq \alpha_{\xi}(\|u_h\|^2_{H^1(\Omega)}+|D|\|{\ud}_h\|^2_{H^1(\Lambda)}+ \|u_h - {\ud}_h\|^2_{\frac 12, h, \Gamma}).
+(u_h,u_h)_{H^1(\Omega)}+ |D|({\ud}_h, {\ud}_h)_{H^1(\Lambda)} +  (Tu_h -  \mathcal{U}_E {\ud}_h, \xi_h)_{\Gamma} \geq \alpha_{\xi}(\|u_h\|^2_{H^1(\Omega)}+|D|\|{\ud}_h\|^2_{H^1(\Lambda)}+ \|u_h - {\ud}_h\|^2_{-\frac 12, h, \Gamma}).
 \end{equation*}
@@
 \\
-(\text{since }c_H H \leq h ) \leq -\delta c_P^2 \|\nabla u_h\|^2_{L^2(\Omega)} - \delta c_P^2 |\D|\|\nabla {\ud}_h\|^2_{L^2(\Lambda)} + \delta c_H \|u_h-{\ud}_h\|^2_{\frac 12,h,\Gamma}. 
+(\text{since }c_H H \leq h ) \leq -\delta c_P^2 \|\nabla u_h\|^2_{L^2(\Omega)} - \delta c_P^2 |\D|\|\nabla {\ud}_h\|^2_{L^2(\Lambda)} + \delta c_H \|u_h-{\ud}_h\|^2_{--\frac 12,h,\Gamma}. 
 \end{multline*}
@@
 (1-\delta c_P^2) \|\nabla u_h\|^2_{L^2(\Omega)} + (1- \delta c_P^2) |\D|\|\nabla {\ud}_h\|^2_{L^2(\Lambda)}
-+\delta c_H \|u_h-{\ud}_h\|^2_{\frac 12,h,\Gamma}
++\delta c_H \|u_h-{\ud}_h\|^2_{-\frac 12,h,\Gamma}
 \end{multline*}
@@
 Concerning the stability inequality, the proof is analogous to the one in \cite{burman2014}.
+
+\subsection{Problem 2} In the case of Problem 2 we consider $Q_h=\{\lambda_{h} : \lambda_h \in P^0(K) \forall K \in \mathcal{T}^{\Lambda}_{h'}\}$, namely the multiplier lives on the same mesh used for the 1D solution ${\ud}_h$.
+Notice that in this case we suppose that the mesh sizes of the 3D mesh $	\mathcal{T}^{\Omega}_h$ and the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different, in particular we suppose the 1D mesh is finer.
+With this choice the problem is not inf-sup stable, therefore we add a stabilization term as in the case of Problem 1.
+Again, we have to build a new space $L_h$, prove that the inf-sup condition is fulfilled, build a projection operator $\pi_L: Q_h \rightarrow L_h$, build $s(\lambda_h, \mu_h)$ and prove that $\forall [u_h, {\ud}_h]$, there exists $\xi_h([u_h, {\ud}_h]) \in Q_h$ s.t.
+\eqref{stab_coercivity} and \eqref{stab_stability} holds.
+We recall that in the case of problem 2,
+\begin{equation*}
+b([u_h, {\ud}_h], \lambda _h) = |\DD|\left(\avrc{T u_h} - {\ud}_h, \lambda _h\right)_{\Lambda}.
+\end{equation*}
+Let us consider macro patches $\left\{ F_j \right\}_j$ of elements of the 3D mesh $\mathcal{T}_h^{\Omega}$ intersecting the 1D manifold $\Lambda$.
+These patches are such that $diam(F_j)\leq H$ and  $jH\leq |F_j\cap \Gamma|\leq H+h$, where $H$ is sufficiently larger than $h$.
+Moreover, there exist constants $c_h$ and $c_H$ such that $c_hh\leq H \leq c_H^{-1}h$.
+We make the following technical assumption: $\Gamma \subset \bigcup _{j} F_j$.
+We define the space $L_h$ as the space of functions which are $P^0$ on each intersection $F_j\cap \Lambda$.
+Moreover, we associate to each patch $F_j$ a shape regular macro elements $\omega_j$, which is built adding to $F_j$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$.
+Thanks to the shape regularity of these macro elements, again we have that the discrete trace and Poincarè inequalites hold.
+Moreover $\forall u_h \in X_h^\Omega$ we have the following average inequality
+\begin{equation*}
+\sum _j |\DD| \|\avrc{T u_h}\|^2_{L^2(F_j \cap \Lambda)} \leq \sum _j \|\avrc{T u_h}\|^2_{L^2(F_j\cap \Lambda)}.
+\end{equation*}
+{\color{red} I think this inequality is valid but only globally.
+Indeed locally it is not guaranteed that the portion of $\Gamma$ corresponding to $F_j \cap \Lambda$ is contained in $F_j \cap \Gamma$}.
+\\
+We define $\pi_L$ as the projection onto piecewise constant functions on $F_j\cap \Lambda$. This choice leads to the following stabilization 
+\begin{equation*}
+s(\lambda_h, \mu_h)= \sum _{K\in \mathcal{T}_{h'}^{\Lambda}} \int_{\partial K} h \llbracket \lambda_h \rrbracket \llbracket \mu_h \rrbracket,
+\end{equation*}
+being $\llbracket \lambda_h \rrbracket$ the jump of $\lambda_h$ across the internal faces of $\mathcal{T}_{h'}^{\Lambda}$.
+
+\subparagraph{Is $L_h$ inf-sup stable with constants independent of the cuts?} We have to prove that $\forall l_h \in L_h$, $\exists \beta >0$ s.t.
+\begin{equation*}
+\sup_{\substack{v_h \in X_{h,1}^0(\Omega),\\ {\vd}_h \in X_{h',1}^0(\Lambda)}} \frac{|\DD|\left(\avrc{T v_h} - {\vd}_h, l _h\right)_{\Lambda}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|l_h\|_{H^{-\frac 12}(\Lambda)}.
+\end{equation*}
+As in the continuous case, we can choose ${\vd}_h=0$ and we prove that
+\begin{equation*} 
+\sup_{v_h \in X_{h,1}^0(\Omega)} \frac{|\DD|\left(\avrc{T v_h} , l _h\right)_{\Lambda}}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|l_h\|_{H^{-\frac 12}(\Lambda)}.
+\end{equation*} 
+Proving the last inequality it is equivalent to find the Fortin operator $\pi_F: H^1_0(\Omega) \rightarrow X_{h,1}^0(\Omega)$, such that 
+\begin{equation*}
+|\DD|\left(\avrc{T v} - \avrc{T \pi _F v}  , l _h\right)_{\Lambda}=0, \quad \forall v\in H^1_0(\Omega), \, l_h \in L_h
+\end{equation*} 
+and
+\begin{equation*}
+\|\pi_F v\|_{H^1(\Omega)}\lesssim \|v\|_{H^1(\Omega)}.
+\end{equation*}
+
+We define
+\begin{equation*}
+\pi_F v = I_h v + \sum _j \alpha _j \varphi _j \qquad \text{with }\alpha_j =\frac{\int_{F_j \cap \Lambda}|\DD| (\avrc{Tv}-\avrc{TI_hv})}{\int_{F_j \cap \Lambda}|\DD|\avrc{T\varphi _j}}
+\end{equation*}
+and $\varphi_j \in X_{h,1}^0(\Omega)$ s.t. supp$(\varphi_j)\subset \bar{\omega}_j$, $\varphi_j =0$ on $\partial \omega _j$ and 
+\begin{equation*}
+ \int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}=O(H) \text{ and } \|\nabla \varphi\|_{L^2(\omega _j)}=O(1). 
+\end{equation*}
+This construction is always possible provided $H$ is sufficiently larger that $h$.
+Then we have
+\begin{multline*}
+|\DD|\left(\avrc{T v} - \avrc{T \pi _F v}  , l _h\right)_{\Lambda} 
+= \sum _j \int_{F_j\cap \Lambda} |\DD |\left[ \avrc{Tv}-\avrc{TI_hv}-\sum _i \alpha_i \avrc{T\varphi _i} \right]l_h \\
+=(\text{supp} \varphi \subset \omega_j) \sum _j \int_{F_j\cap \Lambda}|\DD| \left[ \avrc{Tv}-\avrc{TI_hv}-\alpha_j \avrc{T\varphi _j} \right]l_h\\
+=\sum _j \int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{T I_h v}) l_h - \frac{\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})}{\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}} \int_{F_j\cap \Lambda} |\DD|\avrc{T\varphi _j}l_h\\
+=(\text{using $l_h$ constant on $F_j\cap \Lambda$})\,0.
+\end{multline*}
+Concerning the continuity of $\pi_F$, we have
+\begin{multline*}
+\|\nabla \pi_F v \|_{L^2(\Omega)} \leq \|\nabla I_h v\|_{L^2(\Omega)} + \sum_j|\alpha_j|\|\nabla \varphi _j\|_{L^2(\bar{\omega}_j)}\\
+(\text{stability of }I_h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \sum_j|\alpha_j|\|\nabla \varphi _j\|_{L^2(\bar{\omega}_j)}
+\\
+\left(\text{using }\|\nabla \varphi\|=O(1)\right) \lesssim \|\nabla  v\|_{L^2(\Omega)} + \sum_j \frac{\left|\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})\right|}{\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}}
+\\
+\left(\text{since }\left|\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}\right|=O(H)\right) \lesssim  \|\nabla  v\|_{L^2(\Omega)} + \frac 1H \sum_j \left|\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})\right|
+\\
+(\text{H\"older}) \lesssim  \|\nabla  v\|_{L^2(\Omega)} + \frac 1H \sum_j |F_j\cap \Lambda|^{\frac 12} \left(\int_{F_j\cap \Lambda} |\DD|^2(\avrc{Tv}-\avrc{TI_hv})^2\right)^{\frac 12}
+\\
+(\text{being }|F_j\cap \Lambda| \leq H+h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H^{\frac 12}} \sum_j  |\DD|\| \avrc{Tv}-\avrc{TI_hv}\|_{L^2(F_j\cap \Lambda)}
+\\
+(\text{average inequality}) \lesssim \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H^{\frac 12}} \sum_j |\DD|^{\frac 12} \| T(v-I_hv)\|_{L^2(F_j\cap \Gamma)}  
+\\
+\left(\text{trace inequality} \right)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H} \sum_j  \| v-I_h v\|_{L^2(\omega_j)} \lesssim \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H}  \| v-I_h v\|_{L^2(\Omega)}
+\\
+(\text{approximation properties of }I_h)\lesssim \|\nabla  v\|_{L^2(\Omega)}.
+\end{multline*}
+
+\subparagraph{Satisfaction of the assumptions of the 
+abstract analysis} 
+We have to prove \eqref{stab_coercivity} and \eqref{stab_stability}.
+We choose the following discrete norm
+\begin{equation*}
+\vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_{h'}(\Lambda) }
+= \|u_h\|^2_{H^1(\Omega)}+|D|\|{\ud}_h\|^2_{H^1(\Lambda)} + |\DD|\|\avrc{Tu_h} - {\ud}_h\|^2_{-\frac 12, h, \Lambda},
+\end{equation*}
+where $|\DD|\|\avrc{Tu_h} - {\ud}_h\|^2_{-\frac 12, h, \Lambda} = |\DD|\|h^{\frac 12} (\avrc{Tu_h} - {\ud}_h)\|^2_{L^2(\Lambda)} $.
+Concerning the coercivity property \eqref{stab_coercivity}, we have to show that $\forall [u_h, {\ud}_h]$, there esists $\xi_h \in Q_h$ s.t.
+\begin{multline*}
+(u_h,u_h)_{H^1(\Omega)}+ |D|({\ud}_h, {\ud}_h)_{H^1(\Lambda)} +  |\DD| (\avrc{Tu_h} - {\ud}_h, \xi_h)_{\Lambda} \\
+\geq \alpha_{\xi}(\|u_h\|^2_{H^1(\Omega)}+|D|\|{\ud}_h\|^2_{H^1(\Lambda)}+ |\DD|\|\avrc{Tu_h} - {\ud}_h\|^2_{-\frac 12, h, \Lambda}.
+\end{multline*}
+We choose 
+\begin{equation*}
+{\xi_h}_{|F_j\cap \Lambda}=\delta \frac 1H \pi_L(\avrc{Tu_h}-{\ud}_h) \qquad \text{with } \pi_L(\avrc{Tu_h}-{\ud}_h) =\frac{1}{|F_j\cap \Lambda|}\int_{F_j\cap \Lambda} \avrc{Tu_h}- {\ud}_h.
+\end{equation*}
+Actually, $\xi_h\in L_h \subset Q_h$. Then,
+\begin{multline*}
+|\DD|\left( \avrc{Tu_h} - {\ud}_h, \xi _h \right)_{\Lambda} 
+= \sum_j \int_{F_j\cap \Lambda} |\DD|( \avrc{Tu_h} - {\ud}_h)\xi_h
+\\
+= \delta \frac{1}{H} \sum_j \int_{F_j\cap \Lambda}|\DD| (\pi_L( \avrc{Tu_h} - {\ud}_h) )^2
+\\
+\geq -\delta \frac 1H \sum_j|\DD| \|(\pi_L - \mathcal{I})\avrc{Tu_h}\|^2_{L^2(F_j\cap \Lambda)}
+- \delta \frac 1H \sum_j |\DD|\|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(F_j\cap \Lambda)}
+\\ 
++ \delta \frac 1H \sum_j |\DD|\|\avrc{Tu_h}-{\ud}_h\|^2_{L^2(F_j\cap \Lambda)}. 
+\end{multline*}
+For the first term we have
+\begin{multline*}
+\sum _j |\DD| \|(\pi_L - \mathcal{I})\avrc{Tu_h}\|^2_{L^2(F_j\cap \Lambda)} =\int _{F_j \cap \Lambda} |\DD| (\pi_L \avrc{Tu_h}- \avrc{Tu_h})^2
+\\
+(\text{Average inequality)} \leq \sum _j  \int_{F_j \cap \Gamma} (\pi_L \avrc{Tu_h} -Tu_h)^2 
+\\
+(\text{trace inequality}) \leq \sum _j  \frac 1H \int_{\omega_j}(\pi_L \avrc{Tu_h} - u_h)^2 
+\\ 
+(\text{Poincare})\leq \sum _j  H c_P ^2 \|\nabla u_h\|^2_{L^2(\omega _j)}.
+\end{multline*}
+For the second term we have
+\begin{multline*}
+\sum _j |\DD|\|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(F_j\cap \Lambda)} = \sum _j \int_{F_j\cap \Lambda} |\DD| (\pi_L {\ud}_h -{\ud}_h)^2
+\\
+(\text{poincare })\leq \sum _j  H^2 c_P^2 \int_{F_j\cap \Lambda} |\DD|(\nabla {\ud}_h)^2
+\\
+(\text{since $H$ is fixed, we can find a constant s.t. } H|\DD| \lesssim |\D|) \lesssim \sum _j H c_P^2 |\D| \int_{F_j\cap \Lambda} (\nabla {\ud}_h)^2 
+\\
+\lesssim \sum _j H c_P^2 |\D| \|\nabla {\ud}_h\|^2_{L^2(F_j\cap \Lambda)}.
+\end{multline*}
+Therefore, we obtain
+\begin{multline*}
+a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h([u_h, {\ud}_h]))
+\geq \\
+(1-\delta c_P^2) \|\nabla u_h\|^2_{L^2(\Omega)} + (1- \delta c_P^2) |\D|\|\nabla {\ud}_h\|^2_{L^2(\Lambda)}
++\delta c_H |\DD| \|\avrc{Tu_h}-{\ud}_h\|^2_{-\frac 12,h,\Lambda}
+\end{multline*}
+and choosing $\delta=\frac{1}{2c_P^2}$ we obtain the coercivity inequality.\\
+Concerning the stability inequality, the proof is analogous to the one in \cite{burman2014}.

### 2019-05-21 unfitted.tex
Techincal assumption

@@
 Let us consider macro patches $\left\{ F_j \right\}_j$ of elements of the 3D mesh $\mathcal{T}_h^{\Omega}$ intersecting the 1D manifold $\Lambda$.
-These patches are such that $diam(F_j)\leq H$ and  $jH\leq |F_j\cap \Gamma|\leq H+h$, where $H$ is sufficiently larger than $h$.
+These patches are such that and  $jH\leq |F_j\cap \Lambda|\leq H+h$, where $H$ is sufficiently larger than $h$.
 Moreover, there exist constants $c_h$ and $c_H$ such that $c_hh\leq H \leq c_H^{-1}h$.
-We make the following technical assumption: $\Gamma \subset \bigcup _{j} F_j$.
 We define the space $L_h$ as the space of functions which are $P^0$ on each intersection $F_j\cap \Lambda$.
-Moreover, we associate to each patch $F_j$ a shape regular macro elements $\omega_j$, which is built adding to $F_j$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$.
+Moreover, we associate to each patch $F_j$ a shape regular macro elements $\omega_j$, which is built adding to $F_j$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$.We make the following technical assumption: $\Gamma \subset \bigcup _{j} \omega_j$.
 Thanks to the shape regularity of these macro elements, again we have that the discrete trace and Poincarè inequalites hold.
@@
 \begin{equation*}
-\sum _j |\DD| \|\avrc{T u_h}\|^2_{L^2(F_j \cap \Lambda)} \leq \sum _j \|\avrc{T u_h}\|^2_{L^2(F_j\cap \Lambda)}.
+\sum _j |\DD| \|\avrc{T u_h}\|^2_{L^2(F_j \cap \Lambda)} \leq \sum _j \|T u_h\|^2_{L^2(\omega_j\cap \Gamma)}.
 \end{equation*}
 {\color{red} I think this inequality is valid but only globally.
-Indeed locally it is not guaranteed that the portion of $\Gamma$ corresponding to $F_j \cap \Lambda$ is contained in $F_j \cap \Gamma$}.
+Indeed locally it is not guaranteed that the portion of $\Gamma$ corresponding to $F_j \cap \Lambda$ is contained in $\omega _j \cap \Gamma$}.
 \\
@@
 \\
-(\text{average inequality}) \lesssim \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H^{\frac 12}} \sum_j |\DD|^{\frac 12} \| T(v-I_hv)\|_{L^2(F_j\cap \Gamma)}  
+(\text{average inequality}) \lesssim \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H^{\frac 12}} \sum_j |\DD|^{\frac 12} \| T(v-I_hv)\|_{L^2(\omega _j\cap \Gamma)}  
 \\
@@
 \\
-(\text{Average inequality)} \leq \sum _j  \int_{F_j \cap \Gamma} (\pi_L \avrc{Tu_h} -Tu_h)^2 
+(\text{Average inequality)} \leq \sum _j  \int_{\omega _j \cap \Gamma} (\pi_L \avrc{Tu_h} -Tu_h)^2 
 \\

### 2019-05-21 stab/stab.tex
the discrete coupled surface formulation

@@
 }
+
+\newcommand{\Miro}[1]{\textcolor{cyan}{Miro: #1}}
 
@@
   \begin{aligned}
-    &\int_{\Omega}\nabla u\cdot \nabla v &\phantom{+\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &+\int{\Gamma}p v &= \int_{\Omega}f v \quad &\forall v\in V,\\
-    &\phantom{\int_{\Omega}\nabla u\cdot \nabla v} &+{\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &-\int{\Gamma}p\hat{v} &= \int_{\Gamma}\hat{f}\hat{v} \quad &\forall \hat{v}\in \hat{V},\\
+    &\int_{\Omega}\nabla u\cdot \nabla v &\phantom{+\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &+\int_{\Gamma} p v &= \int_{\Omega}f v \quad &\forall v\in V,\\
+    &\phantom{\int_{\Omega}\nabla u\cdot \nabla v} &+{\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &-\int_{\Gamma} p\hat{v} &= \int_{\Gamma}\hat{f}\hat{v} \quad &\forall \hat{v}\in \hat{V},\\
     &\int_{\Gamma}u q &-\int_{\Gamma}\hat{u}q &\phantom{-\int{\Gamma}q\hat{v}} &= \int_{\Gamma}h q \quad &\forall q\in Q.
@@
 
+% --------------------------------------------------------------------
+
+\section{Coupled multiscale problem in 3 mesh formulation}\label{sec:coupled_3}
+The discrete formulations thus far concerned only two meshes, $\Omega_H$ and $\Gamma_h$,
+and are in this sense similar to Problem 2 of the 3$d$-1$d$ problem. Here we
+shall consider a 2$d$ ``analogue'' of Problem 1. In particular the reduced
+domain and the coupling/Lagrange multiplier domain shall be different.
+
+Let us recall that in Problem 1 (of the coupled 3$d$-1$d$ problem) the coupling surface $\Gamma$ isn't necessarily
+identical/related to the cylindrical surface whose centerline is the reduced
+domain $\Gamma$. We propose to take advantage of the fact that (to certain extent?)
+the surface may be chosen freely in the following construction which automatically
+satisfies the requirement of conformity of the triangulation of $\Omega$ to the
+multiplier surface.
+
+Let $\Omega_H$, $\Gamma_h$ be the two \emph{independent} discretizations of the
+bulk and the centerline. In particular, $\Gamma_h$ is not assumed to consist only
+of the edges of the tetrahedra in $\Omega_H$. However, we assume that the $\Gamma_h$
+is finer than $\Omega_H$ restricted to the line. Next, let $\mathcal{K}_H$ be
+the set of all tetrahedra in $\Omega_H$ intersected by elements of $\Gamma_h$.
+Finally, the coupling surface $\omega_H$ shall consist of those facets
+of elements in $\mathcal{K}_H$ which are \emph{not} intersected by the curve.
+The process in the 2$d$ setting of Figure \ref{fig:coupled_domain} is shown
+in Figure \ref{fig:mesh3}. We remark that the coupling surface changes with
+discretization.
+
+%
+\begin{figure}[h]
+  \begin{center}
+    \begin{tikzpicture}[scale=0.60]
+      % Minus
+  \draw[black, very thick] (0,0) rectangle (3, 3);
+  \draw[black, very thick] (0,0) -- (3, 3);
+  \node[left] at (0, 1.5) {$\Omega^{-}_{H}$};
+
+  \node[mark size=3pt, color=black] at (0.0, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (3.0, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (0.0, 3) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (3.0, 3) {\pgfuseplotmark{*}};
+
+     % Center
+  \draw[black, very thick] (4.5,0) -- (4.5, 3);
+  \node[opacity=0.9, below] at (4.5, 0) {$\Gamma_{h}$};
+
+  \node[mark size=3pt, color=black] at (4.5, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4.5, 1) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4.5, 2) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (4.5, 3) {\pgfuseplotmark{*}};
+
+  \draw[black, very thick] (3,0) -- (6, 0);
+  \draw[black, very thick] (3,0) -- (6, 3);
+  \draw[black, very thick] (3,3) -- (6, 3);  
+  % Right
+    \draw[black, very thick] (6,0) rectangle (9, 3);
+  \draw[black, very thick] (6,0) -- (9, 3);
+  \node[right] at (9, 1.5) {$\Omega^{+}_{H}$};
+
+  \node[mark size=3pt, color=black] at (6, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (9, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (6, 3) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=black] at (9, 3) {\pgfuseplotmark{*}};
+
+  \draw[blue, very thick] (3,0) -- (3, 3);
+  \draw[blue, very thick] (6,0) -- (6, 3);
+  \node[mark size=3pt, color=blue] at (6, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=blue] at (6, 3) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=blue] at (3, 0) {\pgfuseplotmark{*}};
+  \node[mark size=3pt, color=blue] at (3, 3) {\pgfuseplotmark{*}};
+
+  \node[below] at (3, 0) {$\omega_{H}$};
+  \node[below] at (6, 0) {$\omega_{H}$};
+
+  \end{tikzpicture}
+    \end{center}
+  \caption{Coupling surface $\omega_H$ consists of facets of elements
+  of $\Omega_H$ not intersected by $\Gamma_h$.}
+    \label{fig:mesh3}
+\end{figure}
+
+To investigate the idea we consider the multiscale problem \eqref{eq:coupled_weak}.
+Note that its left hand side defines an operator
+%
+\[
+\begin{pmatrix}
+  A & & T^{\prime}\\
+  & \hat{A} & -I\\
+  T & -I & 0\\
+\end{pmatrix},
+\]
+where $A$, $\hat{A}$ are the Laplacians on $\Omega$ and $\Gamma$ respectively
+and $T$, $I$ are the trace and identity operators. Let now $V_H=H^{1}_0(\Omega)$,
+$\hat{V}_h=H^{1}_0(\Gamma_h)$, $Q=(H^{-1/2}_{00}(\omega_H))^{\prime}$. We shall
+consider a modified problem defined by operator
+%
+\begin{equation}\label{eq:mesh3}
+\begin{pmatrix}
+  A & & T^{\prime}\\
+  & \hat{A} & -E^{\prime}_{\omega}\\
+  T_{\omega} & -E_{\omega} & 0\\
+\end{pmatrix},
+\end{equation}
+%
+with $T_{\omega}: V\rightarrow Q^{\prime}$ (trace) and $E_{\omega}: \hat{V}\rightarrow Q^{\prime}$
+(extension)
+\[
+\langle T_{\Omega} u, q\rangle = \int_{\omega_H} uq, \quad\quad
+%
+\langle E_{\Omega} \hat{u}, q\rangle = \int_{\omega_H} \hat{u} q.
+\]
+%
+
+In the following experiments we investigate stability and approximation
+properties of \eqref{eq:mesh3}. To this end we consider a Riesz map preconditioner
+based on spaces $V$, $\hat{V}$ and $Q$ and the manufactured test cased from \S \ref{sec:coupled}.
+The spaces are all discretized with P1 elements and we have $H=3h$. As before, we enforce boundary
+conditions on $Q$. The extension operator is defined as extension by constant
+from the nearest degree of freedom of $\hat{V}$.
+
+\begin{table}
+  \begin{center}
+    \scriptsize{
+  \begin{tabular}{c|ccc|c|c}
+    \hline
+    $h$ & $\norm{u-u_H}_1$ & $\norm{\hat{u}-\hat{u}_h}_1$ & $\norm{p-p_h}_0$ & $n$ & $\kappa$\\
+    \hline
+8.58E-2 & 1.49E0(--)    & 6.74E-1(--)   & 7.22E0(--)   & 31 & 13   \\
+4.35E-2 & 9.89E-1(0.60) & 3.46E-1(0.98) & 7.59E0(-0.07)& 40 & 22 \\
+2.19E-2 & 6.66E-1(0.58) & 1.74E-1(1.00) & 7.37E0(0.04) & 48 & 41 \\
+1.10E-2 & 4.57E-1(0.55) & 8.75E-2(1.00) & 7.25E0(0.02) & 58 & 79 \\
+5.51E-3 & 3.17E-1(0.53) & 4.37E-2(1.00) & 7.14E0(0.02) & 75 & 154 \\
+2.76E-3 & 2.22E-1(0.52) & 2.18E-2(1.00) & 7.09E0(0.01) & 75 & 304 \\
+1.38E-3 & 1.56E-1(0.51) & 1.09E-2(1.00) & 7.06E0(0.01) & 77 & -- \\
+    \hline
+  \end{tabular}
+    }
+    \caption{Three mesh formulation. Approximation errors, number of preconditioned MinRes iterations ($n$) and
+      condition number of the preconditioned problem \eqref{eq:coupled_weak} ($\kappa$) discretized
+      with P1-P1-P1 elements.}
+  \label{tab:mesh3}
+  \end{center}
+\end{table}
+%
+
+Table \ref{tab:mesh3} summarizes the preliminary results. With the exception of the multiplier
+convergence in all the variables can be seen. However, we recall that the
+true solution is here defined as $\jump{\nabla u\cdot n}$ on $\Gamma$ while
+the discrete one lives on $\omega_H$ so there is at the very least some
+geometrical error. Observing the condition numbers we also see that the
+formulation is unstable.
+
+\subsection{TODO}
+\begin{itemize}
+\item Build \eqref{eq:mesh3} for just half of the domain, so $\omega_H$ is connected
+\item How is this problem related 2$d$-2$d$-2$d$ problem with ``thin'' (middle) domain
+  which becomes $\Gamma$?
+\item What are then the approximation properties?
+\item Stabilization
+\end{itemize}
+
 \bibliographystyle{siamplain}

### 2019-05-28 benchmark.tex
Updates

--- 2019-03-04 3d1d_coupled_LM.tex
@@
-% SIAM Article Template
-\documentclass[r]{siamart171218}
-% Packages and macros go here
-\usepackage[english]{babel}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{array}
-\usepackage{graphicx}
-\usepackage{epsfig}
-\usepackage{float}
-\usepackage{fullpage}
-\usepackage{color}
-\usepackage{enumitem}  
-\usepackage{epstopdf}
-
-% Title. If the supplement option is on, then "Supplementary Material"
-% is automatically inserted before the title.
-%\title{On the weak coupling of 3D and 1D second order elliptic problems}
-\title{Coupling PDEs on 3D-1D domains with Lagrange multipliers}
-
-% Authors: full names plus addresses.
-\author{Miroslav Kuchta, Federica Laurino, Kent-Andre Mardal, Paolo Zunino,\thanks{Authors are listed in alphabetical order}}
-
-\begin{document}
-
-\maketitle
-
-% REQUIRED
-\begin{abstract}
-These are personal notes written to keep track of the developments on this topic, to be kept confidential.
-\end{abstract}
-
-% REQUIRED
-\begin{keywords}
-elliptic problems, high dimensionality gap, essential coupling conditions, Lagrange multipliers
-\end{keywords}
-
-% REQUIRED
-\begin{AMS}
-n.a.
-\end{AMS}
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-
-% definitions here
-
-\def\ud{u_{\odot}}
-\def\vd{v_{\odot}}
-\def\uf{u_{\ominus}}
-\def\up{u_{\oplus}}
-\def\eps{\epsilon}
-\def\nn{\boldsymbol n}
-\def\rr{\boldsymbol r}
-\def\RR{\boldsymbol R}
-\def\kk{\boldsymbol k}
-\def\ss{\boldsymbol s}
-\def\uu{\boldsymbol u}
-\def\vv{\boldsymbol v}
-\def\xx{\boldsymbol x}
-\def\bu{\overline{u}}
-\def\bv{\overline{v}}
-\def\tu{\widetilde{u}}
-\def\tv{\widetilde{v}}
-\def\TT{\boldsymbol T}
-\def\NN{\boldsymbol N}
-\def\BB{\boldsymbol B}
-\def\ttu{\widetilde{\widetilde{u}}}
-\def\ttv{\widetilde{\widetilde{v}}}
-\def\cv{\check{v}}
-\def\mesh{{\cal T}^h}
-\def\ball{{\cal B}}
-\def\R{\mathbb{R}}
-\def\D{\mathcal{D}}
-\def\DD{\partial\mathcal{D}}
-\def\trace{\overline{\mathcal{R}}}
-\def\ext{\mathcal{E}}
-\def\ide{\mathcal{I}}
-\def\ii{\hat{\imath}}
-\newcommand{\avrd}[1]{\overline{\overline{#1}}}
-\newcommand{\avrc}[1]{\overline{#1}}
-\newcommand{\refe}[1]{{#1}_{\mathrm{ref}}}
-
-\newcommand{\vertiii}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 
-    \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
-
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{prop}{Property}[section]
-\theoremstyle{remark}
-\newtheorem{remark}{Remark}[section]
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\section{Introduction}\label{sec:intro}
-
-We address the geometrical configuration of the problem for a 3D coupled problem formulation based on from Dirichlet-Neumann interface conditions.
-Then, we apply a model reduction technique that transforms the problem into 3D-1D coupled PDEs.
-We develop and analyze a robust definition of the coupling operators form a 3D domain, $\Omega$, to 1D manifold, $\Lambda$, and vice versa.
-This is a non trivial objective because the standard trace operator form a domain $\Omega$ to a subset $\Lambda$ is not well posed if $\Lambda$ is a manifold of co-dimension two of $\Omega$.
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\section{Problem setting}\label{sec:setting}
-
-Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set.
-Let $\Sigma$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Sigma}$ be the complementary set of the cylinder.
-We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Sigma$.
-We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$.
-We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Sigma$ and its boundary, respectively.
-In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach.
-We also assume that $\Sigma$ crosses $\Omega$ from side to side and we call $\Gamma$ the lateral (cylindrical) surface of $\Sigma$, while the upper and lower side faces of $\Sigma$ belong to $\partial\Omega$.
-We refer to Figure \ref{fig1} for an illustration of the notation.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.5\textwidth]{3D-1D-simple.png}
-\end{center}
-\caption{Geometrical setting of the problem}
-\label{fig1}
-\end{figure}
-
-We consider the problem arising from \emph{Dirichlet-Neumann} conditions. 
-It consists to find $\up,\uf$ s.t.:
-\begin{subequations}\label{eq:dirneu}
-\begin{align}
-\label{eq:dirneu1}
-- \Delta \up  + \up &= f  && \text{ in } \Omega_{\oplus},\\
-\label{eq:dirneu2}
-- \Delta \uf  + \uf &= g  && \text{ in } \Sigma,\\
-\label{eq:dirneu3}
--\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
-\label{eq:dirneu4}
-\uf &= \up && \text{ on }  \Gamma,\\
-\label{eq:dirneu5}
-\up &= 0 && \text{ on } \partial \Omega\,.
-\end{align}
-\end{subequations}
-
-The objective of this work is to derive and alalyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Sigma$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$.
-This new problem setting will be called the \emph{reduced} problem.
-Form the mathematical standpoint it is more challenging than \eqref{eq:dirneu}, because it involves the coupling of 3D/1D elliptic problems.
-For the model reduction process, we decompose integrals as follows, for any sufficiently regular function $w$,
-\begin{equation*}
-\int_\Sigma w d\omega 
-= \int_\Lambda \int_{\mathcal{D}} w d\sigma ds
-= \int_\Lambda |\mathcal{D}|\avrd{w} ds\,,
-\quad
-\int_{\Gamma} w d\sigma 
-= \int_\Lambda \int_{\partial\mathcal{D}} w d\gamma ds
-= \int_\Lambda  |\partial \mathcal{D}| \avrc{w} ds\,,
-\end{equation*}
-where $\avrd{w}, \ \avrc{w}$ denote the following mean values respectively,
-\begin{equation*}
-\avrd{w} = |\mathcal{D}|^{-1} \int_{\mathcal{D}} w d\sigma\,,
-\quad
-\avrc{w} = |\partial\mathcal{D}|^{-1} \int_{\partial\mathcal{D}} w d\gamma\,.
-\end{equation*}
-
-We apply the model reduction approach at the level of the variational formulation.
-We start from the variational formulation of problem \eqref{eq:dirneu}, 
-that is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Sigma\setminus\Gamma}(\Sigma), \ \lambda \in H^{-\frac12}(\partial\Sigma)$ s.t.
-\begin{subequations}\label{eq:weak_dirneu}
-\begin{align}
-&(u_\oplus,v_\oplus)_{H^1(\Omega_\oplus)} + (u_\ominus,v_\ominus)_{H^1(\Sigma)} 
-+ \langle v_\ominus - v_\oplus, \lambda \rangle_{H^{-\frac12}(\Gamma)} 
-\\
-\nonumber
-&\qquad\qquad = (f,v_\oplus)_{L^2(\Omega_\oplus)} + (g,v_\ominus)_{L^2(\Sigma)}
-\quad \forall v_\oplus \in H^1_{\partial\Omega}(\Omega_\oplus), \ v_\ominus \in H^1_{\partial\Sigma\setminus\Gamma}(\Sigma)
-\\
-& \langle u_\ominus - u_\oplus, \mu \rangle_{H^{-\frac12}(\Gamma)} = 0
-\quad \forall  \mu \in H^{-\frac12}(\Gamma)\,,
-\end{align}
-\end{subequations}
-where $\langle v, \mu \rangle_{H^{-\frac12}(\Gamma)}$ denotes the duality pairing between 
-$ \mu \in H^{-\frac12}(\Gamma)$ and $v \in H^{\frac12}(\Gamma)$.
-In this case, the additional variable $\lambda$ is equivalent to $\lambda  = - \nabla \uf \cdot \nn_\ominus$.
-
-Using the averaging tools for the model reduction approach, we end up with a reduced problem
-for the unknown $u$ defined on the entire 3D domain $\Omega$, coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$
-and a Lagrange multiplier $L$ defined on $\Lambda$. In the reduced problem the multiplier assumes the following interpretation,
-\begin{equation*}
-L = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \nabla \uf \cdot \nn_\ominus
-   = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \lambda \,.
-\end{equation*}
-
-We consider two alternative formulations. The scope of this work is to compare them, 
-with the aim to determine which is the most suitable as a computational model based on 3D-1D coupled PDEs.
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\subsection{Problem 1}
-The idea is to couple a 3D PDE with a 1D one, using a Lagrange multiplier space defined on a 2D surface that surrounds the 1D manifold.
-Let $\langle \cdot , \cdot \rangle_\Gamma$ denote the duality pairing between 
-$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$.
-The problem consists to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ L \in H^{-\frac12}(\Gamma )$, such that
-\begin{subequations}\label{eq:problem1}
-\begin{align}
-&(u,v)_{H^1(\Omega)} + |{\cal D}|(\ud,\vd)_{H^1(\Lambda)} 
-+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
-\\
-&   \langle \Pi_1 u - \Pi_2 \ud , M \rangle_\Gamma = 0
-\quad \forall M \in H^{-\frac12}(\Gamma)\,.
-\end{align}
-\end{subequations}
-Here, $\Pi_1: H^1_0(\Omega) \rightarrow H^{\frac12}_{00}(\Gamma)$
-and $\Pi_2: H^1_0(\Lambda) \rightarrow H^{\frac12}_{00}(\Gamma)$
-and we remark that $\Sigma$ may be considered as a virtual surface
-not necessarily of the same size as the underlying physical structure that is modeled.  
-The $\Pi_1$ and $\Pi_2$ operators may be defined in terms of the averaging operators above, but may also be realized in terms of e.g.
-Green functions (I don't know if this is a good idea).
-Furthermore,  $\Gamma$ may be discretized in terms of facets neighboring $\Lambda$ and may as such not be represented as a separate structure in the implementation.
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\subsection{Problem 2}
-Another form of the reduced problem uses Lagrange multipliers defined directly on the 1D manifold.
-In this case, $\langle \cdot , \cdot \rangle_\Lambda$ denotes the duality pairing between 
-$H^\frac12_{00}(\Lambda)$ and $H^{-\frac12}(\Lambda)$.
-The problem requires to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ L \in H^{-\frac12}(\Lambda)$, such that
-\begin{subequations}\label{eq:problem2}
-\begin{align}
-&(u,v)_{H^1(\Omega)} + |{\cal D}|(\ud,\vd)_{H^1(\Lambda)} 
-+ |\partial {\cal D}| \langle \Pi_1 v - \Pi_2 \vd, L \rangle_{H^{-\frac12}(\Lambda)} 
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},V)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
-\\
-&  |\partial {\cal D}| \langle \Pi_1 u -  \Pi_2 \ud, M \rangle_{H^{-\frac12}(\Lambda)} = 0
-\quad \forall M \in H^{-\frac12}(\Lambda)\,.
-\end{align}
-\end{subequations}
-We notice that all the integrals of the reduced problem are well defined because $u,v \in H^1_0(\Omega)$, 
-$u,v|_{\Gamma} \in H^\frac12_{00}(\Gamma)$ and thus $\avrc{u},\avrc{v} \in H^\frac12_{00}(\Lambda)$.
-More precisely, $\Pi_1 : H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda$ such that
-$\Pi_1 u = \avrc{(u|_\Gamma)}$ is the combination between the trace on $\Gamma$ and the average on $\partial{\cal D}$.
-The operator $\Pi_2: H^1_0(\Lambda) \rightarrow H^\frac12_{00}(\Lambda)$ is the injection form $H^1_0(\Lambda)$ and $H^\frac12_{00}(\Lambda)$.
-It is apparent that problems \eqref{eq:weak_dirneu} and \eqref{eq:red_dirneu} share the same mathematical structure.
-For this reason, the well-posedness of \eqref{eq:red_dirneu} can be studied in the framework of the classical theory of saddle point problems.
-
-%Assuming now that 
-%$\Pi_1: H^1(\Omega) \rightarrow H^{\frac12}(\Gamma)$ or $\Pi_2: H^1(\Gamma) \rightarrow H^{\frac12}(\Gamma)$ are isomorphisms in the sense that 
-%\[
-%\| \Pi_1 \|_{L(H^1(\Omega), H^{\frac12}(\Gamma))} \le C \mbox{, } 
-%\| \Pi_1^{-1} \|_{L(H^{\frac12}(\Gamma), H^1(\Omega))} \le 1/c,  
-%\]
-%and 
-%\[
-%\| \Pi_2 \|_{L(H^1(\Omega), H^{\frac12}(\Gamma))} \le C \mbox{, } 
-%\| \Pi_2^{-1} \|_{L(H^{\frac12}(\Gamma), H^1(\Omega))} \le 1/c .   
-%\]
-%We obtain the inf-sup condition as follows. Assume that $\Pi_1$ is an isomorphism then  
-%we may show the inf-sup conditioning by letting $\Pi_1 \hat u = M $ and $ \hat \ud = 0$ (i.e., we need the lower bound only for one
-%of the operators).  
-%\begin{eqnarray}
-%\sup_{u,\ud}\frac{
-%\langle \Pi_1 u - \Pi_2 \ud , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
-%}{(|u|_1^2 + |\ud|_1^2)^{1/2}} 
-%\ge \\ 
-%\frac{ \langle \Pi_1 \hat u - \Pi_2 \hat \ud , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
-%}{(|\hat u|_1^2 + |\hat \ud|_1^2)^{1/2}}  \ge \\
-%\frac{ \langle M , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
-%}{|\Pi_1^{-1} M |_{H^1(\Omega})} \ge \\ 
-%\frac{ \langle M , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
-%}{| M |_{H^\frac12(\Gamma)}} \ge \\ 
-%c | M |_{H^{-\frac12}(\Gamma)}  
-%\end{eqnarray}
-%I think the other Brezzi conditions also follows, but for the boundedness we
-%would need that both $\Pi_1$ and $\Pi_2$ are bounded. Not sure I am 
-%happy with the $\langle \cdot, \cdot \rangle$ notation and in particular not when we spesify the
-%spaces. I would rather just say that $(\cdot, \cdot)$ denotes both the $L_2$ inner product and the
-%duality pairing.  
-%If we find it useful we may also  
-%consider $\Pi_2: H^1(\Gamma) \rightarrow X(\Gamma)$ where $X$ may e.g. be $H^1$.  
-%If so, $L, M$ in $ H^{-\frac12}(\Gamma) \cap X(\Gamma)$
-
-\input{infsup}
-
-\input{infsup_discrete}
-
 \section{A benchmark problem with analytical solution}
@@
 \end{remark}
-%\bibliographystyle{siamplain}
-%\bibliography{3d1d_coupled}
-\end{document}

### 2019-07-05 3d1d_coupled_LM.tex
Discrete inf-sup same mesh for sol and mult

@@
 \usepackage{epstopdf}
+\usepackage{stmaryrd}
 
@@
 \def\vd{v_{\odot}}
+\def\ld{\lambda_{\odot}}
+\def\md{\mu_{\odot}}
+\def\lld{l_{\odot}}
 \def\uf{u_{\ominus}}
@@
 Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set.
-Let $\Sigma$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Sigma}$ be the complementary set of the cylinder.
-We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Sigma$.
+Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Omega_\ominus}$ be the complementary set of the cylinder.
+We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Omega_\ominus$.
 We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$.
-We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Sigma$ and its boundary, respectively.
-In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach.
-We also assume that $\Sigma$ crosses $\Omega$ from side to side and we call $\Gamma$ the lateral (cylindrical) surface of $\Sigma$, while the upper and lower side faces of $\Sigma$ belong to $\partial\Omega$.
+We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Omega_\ominus$ and its boundary, respectively.
+%In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach. 
+We also assume that $\Omega_\ominus$ crosses $\Omega$ from side to side and we call $\Gamma$ the lateral (cylindrical) surface of $\Omega_\ominus$, while the upper and lower side faces of $\Omega_\ominus$ belong to $\partial\Omega$.
 We refer to Figure \ref{fig1} for an illustration of the notation.
@@
 \label{eq:dirneu2}
-- \Delta \uf  + \uf &= g  && \text{ in } \Sigma,\\
+- \Delta \uf  + \uf &= g  && \text{ in } \Omega_\ominus,\\
 \label{eq:dirneu3}
@@
 
-The objective of this work is to derive and alalyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Sigma$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$.
+The objective of this work is to derive and alalyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Omega_\ominus$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$.
 This new problem setting will be called the \emph{reduced} problem.
@@
 \begin{equation*}
-\int_\Sigma w d\omega 
+\int_{\Omega_\ominus} w d\omega 
 = \int_\Lambda \int_{\mathcal{D}} w d\sigma ds
@@
 We start from the variational formulation of problem \eqref{eq:dirneu}, 
-that is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Sigma\setminus\Gamma}(\Sigma), \ \lambda \in H^{-\frac12}(\partial\Sigma)$ s.t.
+that is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus), \ \lambda \in H^{-\frac12}(\partial\Omega_\ominus)$ s.t.
 \begin{subequations}\label{eq:weak_dirneu}
 \begin{align}
-&(u_\oplus,v_\oplus)_{H^1(\Omega_\oplus)} + (u_\ominus,v_\ominus)_{H^1(\Sigma)} 
-+ \langle v_\ominus - v_\oplus, \lambda \rangle_{H^{-\frac12}(\Gamma)} 
+&(u_\oplus,v_\oplus)_{H^1(\Omega_\oplus)} + (u_\ominus,v_\ominus)_{H^1(\Omega_\ominus)} 
++ \langle  v_\oplus - v_\ominus, \lambda \rangle_{H^{-\frac12}(\Gamma)} 
 \\
 \nonumber
-&\qquad\qquad = (f,v_\oplus)_{L^2(\Omega_\oplus)} + (g,v_\ominus)_{L^2(\Sigma)}
-\quad \forall v_\oplus \in H^1_{\partial\Omega}(\Omega_\oplus), \ v_\ominus \in H^1_{\partial\Sigma\setminus\Gamma}(\Sigma)
+&\qquad\qquad = (f,v_\oplus)_{L^2(\Omega_\oplus)} + (g,v_\ominus)_{L^2(\Omega_\ominus)}
+\quad \forall v_\oplus \in H^1_{\partial\Omega}(\Omega_\oplus), \ v_\ominus \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus)
 \\
-& \langle u_\ominus - u_\oplus, \mu \rangle_{H^{-\frac12}(\Gamma)} = 0
+& \langle u_\oplus - u_\ominus, \mu \rangle_{H^{-\frac12}(\Gamma)} = 0
 \quad \forall  \mu \in H^{-\frac12}(\Gamma)\,,
@@
 $ \mu \in H^{-\frac12}(\Gamma)$ and $v \in H^{\frac12}(\Gamma)$.
-In this case, the additional variable $\lambda$ is equivalent to $\lambda  = - \nabla \uf \cdot \nn_\ominus$.
+In this case, the additional variable $\lambda$ is equivalent to $\lambda  =  \nabla \uf \cdot \nn_\ominus$.
 
-Using the averaging tools for the model reduction approach, we end up with a reduced problem
+Using the averaging tools for the model reduction approach, we end up with two different formulations of a reduced problem
 for the unknown $u$ defined on the entire 3D domain $\Omega$, coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$
-and a Lagrange multiplier $L$ defined on $\Lambda$. In the reduced problem the multiplier assumes the following interpretation,
-\begin{equation*}
-L = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \nabla \uf \cdot \nn_\ominus
-   = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \lambda \,.
-\end{equation*}
+and a Lagrange multiplier defined either on $\Gamma$ (problem 1) or on $\Lambda$ (problem 2). 
+%In the reduced problem the multiplier assumes the following interpretation,
+%\begin{equation*}
+%L = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \nabla \uf \cdot \nn_\ominus
+%   = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \lambda \,.
+%\end{equation*}
 
-We consider two alternative formulations. The scope of this work is to compare them, 
+%We consider two alternative formulations.
+The scope of this work is to compare them, 
 with the aim to determine which is the most suitable as a computational model based on 3D-1D coupled PDEs.
@@
 % >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\subsection{Problem 1}
-The idea is to couple a 3D PDE with a 1D one, using a Lagrange multiplier space defined on a 2D surface that surrounds the 1D manifold.
+\subsection{Topological model reduction}
+\subsubsection*{Model reduction of the problem on $\Omega_{\ominus}$}
+
+We apply the averaging technique to equation \eqref{eq:dirneu2}.
+In particular, we consider an arbitrary portion $\mathcal{P}$ of the cylinder $\Omega_\ominus$, with lateral surface $\Gamma _{\mathcal{P}}$ and bounded by two perpendicular sections to $\Lambda$, namely $\mathcal{D}(s_1), \ \mathcal{D}(s_2)$ with $s_1<s_2$.
+We have,
+\begin{multline*}
+\int_{\mathcal{P}} -\Delta \uf + \uf d\omega =
+-\int_{\partial \mathcal{P}} \nabla \uf \cdot \nn_{\ominus} \, d\sigma  + \int_{\mathcal{P}}\uf d\omega=
+\\
+ \int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma -  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma -  \int_{\Gamma_{\mathcal{P}}} \nabla \uf \cdot \nn_{\ominus} d\sigma +\int_{\mathcal{P}}\uf d\omega
+\end{multline*}
+By the fundamental theorem of integral calculus combined with the Reynolds transport Theorem, 
+%where $d_s |\partial\mathcal{D}(s)|$ is the rate at which the cross section changes size,
+being $\nu$ the normal component of the velocity of the boundary, 
+we have,
+%\begin{multline*}
+%-\int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma +  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma 
+%= \int_{s_1}^{s_2} d_s \int_{\mathcal{D}(s)}  \partial_s \uf d\sigma ds
+%\\
+%= \int_{s_1}^{s_2} \int_{\mathcal{D}(s)} \partial^2_{ss} \uf d\sigma ds + \int_{s_1}^{s_2} \int_{\partial\mathcal{D}(s)} \nu \partial_s \uf d\gamma ds
+%\\
+%= \int_{s_1}^{s_2} \left[ |\mathcal{D}(s)| d^2_{ss} \avrd{u}_{\ominus}  + |\partial\mathcal{D}(s)| \nu  d_s \avrc{u}_{\ominus} \right] ds.
+%\end{multline*}
+
+\begin{equation*}
+\begin{split}
+\int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma -  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma 
+&= -\int_{s_1}^{s_2} d_s \int_{\mathcal{D}(s)}  \partial_s \uf d\sigma ds
+\\
+&= -\int_{s_1}^{s_2} d_{ss}^2 \int_{\D(s)} u_{\ominus} \, d\sigma \, ds +  \int_{s_1}^{s_2} d_s \left( \int_{\DD(s)} \nu u_{\ominus} \, d\gamma \right) ds\,,
+\end{split}
+\end{equation*}
+and assuming that $\D(s)$  can not change shape, we have
+\begin{equation*}
+\begin{split}
+-\int_{s_1}^{s_2} d_{ss}^2 \int_{\D(s)} u_{\ominus} \, d\sigma \, ds + \int_{s_1}^{s_2} d_s \left( \int_{\DD(s)} \nu u_{\ominus} \, d\gamma \right)\, ds
+&=-\int_{s_1}^{s_2} \left[d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) -  d_s(  \nu |\DD(s)| \avrc{u}_{\ominus} ) \right] \, ds
+\\
+&=-\int_{s_1}^{s_2} \left[d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) -  d_s\left(d_s(|\D(s)|) \avrc{u}_{\ominus} \right) \right] \, ds.
+\end{split}
+\end{equation*}
+Moreover, we have
+\begin{equation*}
+\int_{\Gamma_{\mathcal{P}}} \nabla \uf \cdot \nn_{\ominus} d\sigma =  \int_{\Gamma_{\mathcal{P}}} \lambda \, d\sigma
+=  \int_{s_1}^{s_2} \int_{\partial\mathcal{D}(s)} \lambda d\gamma \, ds 
+= \int_{s_1}^{s_2} |\DD| \avrc{\lambda} \,ds\,.
+\end{equation*}
+From the combination of all the above terms with the right hand side, we obtain that the solution $\uf$ of \eqref{eq:dirneu2} satisfies,
+\begin{equation*}
+\int_{s_1}^{s_2} \left[ 
+-d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) +  d_s\left(d_s(|\D(s)|) \avrc{u}_{\ominus}\right) + |\D(s)|\avrd{u}_{\ominus} 
+- |\partial\mathcal{D}(s)| \avrc{\lambda} 
+\right] \, ds = \int_{s_1}^{s_2} |\mathcal{D}(s)| \avrd{g}\, ds \,.
+\end{equation*}
+Since the choice of the points $s_1,s_2$ is arbitrary, we conclude that the following equation holds true,
+\begin{equation}\label{eq:averaged_f}
+-d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) +  d_s\left(d_s(|\D(s)|) \avrc{u}_{\ominus}\right) + |\D(s)|\avrd{u}_{\ominus} 
+- |\partial\mathcal{D}(s)| \avrc{\lambda}
+= |\mathcal{D}(s)| \avrd{g} \quad \text{on} \ \Lambda\,,
+\end{equation}
+which is complemented by the following conditions at the boundary of $\Lambda$,
+\begin{equation}\label{eq:averaged_f_boundary}
+|\D(s)| d_s \avrd{u}_{\ominus} = 0, \quad d_s |\D(s)| = 0, \quad \text{on} \quad s=0,S.
+\end{equation}
+Then, we consider variational formulation of the averaged equation \eqref{eq:averaged_f}.
+After multiplication by a test function $\vd \in H^1(\Lambda)$, integration on $\Lambda$ and suitable application of integration by parts, we obtain,
+\begin{multline*}
+\int_\Lambda d_s (|\D(s)| \avrd{u}_{\ominus} ) d_s \vd \, ds - d_s (|\D(s)| \avrd{u}_{\ominus} ) \vd |_{s=0}^{s=S}
+- \int_\Lambda (d_s |\D(s)|)\avrc{u}_{\ominus} d_s \vd \, ds + (d_s |\D(s)|) \avrc{u}_{\ominus} \vd |_{s=0}^{s=S}
+\\
++\int_\Lambda |\D(s)| \avrd{u_\ominus} \vd - \int_\Lambda |\DD(s)| \avrc{\lambda} \vd \, ds
+= \int_\Lambda |\D(s)| \avrd{g} V\, ds\,.
+\end{multline*}
+Using boundary conditions, 
+the identity $d_s (|\D(s)| \avrd{u}_{\ominus} ) = |\D(s)| d_s \avrd{u}_{\ominus} + d_s (|\D(s)|) \avrd{u}_{\ominus}$
+and reminding that $d_s |\D(s)|)/|\DD(s)| = \nu$,
+we obtain,
+\begin{equation}\label{eq:averaged_f_weak}
+(d_s \avrd{u}_{\ominus}, d_s \vd )_{\Lambda,|\D|} 
++ ( \nu (\avrd{u}_{\ominus} - \avrc{u}_{\ominus}), d_s \vd)_{\Lambda,|\DD|} +(\avrd{u_\ominus}, \vd)_{\Lambda, |\D|}
+- (\avrc{\lambda},\vd)_{\Lambda,|\DD|}
+= (\avrd{g},V)_{\Lambda,|\D|}\,.
+\end{equation}
+where we have introduced the following weighted inner product notation,
+\begin{equation*}
+(\ud,\vd)_{\Lambda,w} = \int_0^S w(s) \ud(s) \vd(s) ds\,.
+\end{equation*}
+Let us now formulate the modelling assumption that allows us to reduce equation \eqref{eq:averaged_f_weak} to a solvable one-dimensional (1D) model.
+More precisely, we assume that:
+\begin{description}
+\item[A1] the function $\uf$ has a \emph{uniform profile} on each cross section $\mathcal{D}(s)$, namely $\uf(r,s,t) = \ud(s)$.
+\end{description}
+Therefore, observing that $\ud=\avrc{u}_{\ominus}=\avrd{u}_{\ominus}$, problem \eqref{eq:averaged_f_weak} consists to find $\ud \in H^1(\Lambda)$ such that
+\begin{equation}\label{eq:1Ddirneu_weak}
+ (d_s \ud, d_s \ud)_{\Lambda,|\mathcal{D}|} 
++(\ud, \vd)_{\Lambda, |\D|}
+-(\avrc{\lambda},\vd)_{\Lambda, |\DD|}
+=  (\avrd{g},\vd)_{\Lambda, |\mathcal{D}|}
+\quad \forall \vd \in H^1(\Lambda)\,.
+\end{equation}
+
+\subsubsection*{Topological model reduction of the problem on $\Omega_{\oplus}$}
+We focus here on the subproblem of \eqref{eq:dirneu1} related to $\Omega_{\oplus}$.
+We multiply both sides of \eqref{eq:dirneu1} by a test function $v\in H^1_0(\Omega)$ and integrate on $\Omega_\oplus$. Integrating by parts and using boundary and interface conditions, we obtain
+\begin{equation*}
+\begin{split}
+\int_{\Omega _{\oplus}}fv\,d\omega&=
+\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\omega -\int _{\partial \Omega _{\oplus}}\nabla \up \cdot \nn_{\oplus} v\,d\sigma + \int_{\Omega_{\oplus}} \up v
+\\
+&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega -\int_{\Gamma} \nabla \up \cdot \nn_{\oplus} v + \int_{\Omega_{\oplus}} \up v
+\\
+&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega +\int_{\Gamma} \lambda v + \int_{\Omega_{\oplus}} \up v.
+\end{split}
+\end{equation*} 
+Then, we make the following modelling assumptions:
+\begin{description}
+\item[A2] we identify the domain $\Omega_{\oplus}$ with the entire $\Omega$, 
+and we correspondingly omit the subscript $\oplus$ to the functions defined on $\Omega_{\oplus}$,
+namely
+\begin{equation*}
+\int_{\Omega_{\oplus}} u_\oplus\, d\omega \simeq \int_{\Omega} u\, d\omega\,.
+\end{equation*}
+\end{description}
+Therefore, we obtain 
+\begin{equation*}
+(\nabla u ,\nabla v)_{\Omega} +(u,v)_{\Omega}+(\lambda, v)_{\Gamma}  =(f,v)_{\Omega}
+\end{equation*}
+and combining with \eqref{eq:1Ddirneu_weak} we obtain the first formulation of the reduced problem.
+
+\subsubsection*{Problem 1 (3D-1D-3D)}
 Let $\langle \cdot , \cdot \rangle_\Gamma$ denote the duality pairing between 
-$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$.
-The problem consists to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ L \in H^{-\frac12}(\Gamma )$, such that
+$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$. The problem consists to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac12}(\Gamma )$, such that
 \begin{subequations}\label{eq:problem1}
 \begin{align}
-&(u,v)_{H^1(\Omega)} + |{\cal D}|(\ud,\vd)_{H^1(\Lambda)} 
-+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
+&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
++ \langle T v  - \mathcal{U}_E \vd, \lambda \rangle_\Gamma
 \\
 \nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
+&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
 \quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
 \\
-&   \langle \Pi_1 u - \Pi_2 \ud , M \rangle_\Gamma = 0
-\quad \forall M \in H^{-\frac12}(\Gamma)\,.
+&   \langle T u - \mathcal{U}_E \ud , \mu \rangle_\Gamma = 0
+\quad \forall \mu \in H^{-\frac12}(\Gamma)\,.
 \end{align}
 \end{subequations}
-Here, $\Pi_1: H^1_0(\Omega) \rightarrow H^{\frac12}_{00}(\Gamma)$
-and $\Pi_2: H^1_0(\Lambda) \rightarrow H^{\frac12}_{00}(\Gamma)$
-and we remark that $\Sigma$ may be considered as a virtual surface
-not necessarily of the same size as the underlying physical structure that is modeled.  
-The $\Pi_1$ and $\Pi_2$ operators may be defined in terms of the averaging operators above, but may also be realized in terms of e.g.
+Here, $T:H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ denotes the trace operator on $\Gamma$ and $\mathcal{U}_E: H^1_0(\Lambda) \rightarrow H^1_{0}(\Gamma)$ denotes the uniform extension from $\Lambda$ to $\Gamma$.
+The idea is then to couple a 3D PDE with a 1D one, using a Lagrange multiplier space defined on a 2D surface that surrounds the 1D manifold.\\
+
+%Here, $\Pi_1: H^1_0(\Omega) \rightarrow H^{\frac12}_{00}(\Gamma)$
+%and $\Pi_2: H^1_0(\Lambda) \rightarrow H^{\frac12}_{00}(\Gamma)$
+%and we remark that $\Sigma$ may be considered as a virtual surface
+%not necessarily of the same size as the underlying physical structure that is modeled.  
+%The $\Pi_1$ and $\Pi_2$ operators may be defined in terms of the averaging operators above, but may also be realized in terms of e.g.
 Green functions (I don't know if this is a good idea).
@@
 % >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\subsection{Problem 2}
-Another form of the reduced problem uses Lagrange multipliers defined directly on the 1D manifold.
-In this case, $\langle \cdot , \cdot \rangle_\Lambda$ denotes the duality pairing between 
+Now, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-3D to a 3D-1D-1D formulation. 
+To this purpose, let us write the lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
+\begin{equation*}
+\lambda=\avrc{\lambda}+\tilde{\lambda}, \qquad v=\avrc{v}+\tilde{v},
+\quad \text{on} \ \partial\mathcal{D}(s)\,,
+\end{equation*}
+where $\avrc{\tilde{\lambda}}=\avrc{\tilde{v}}=0$. 
+Therefore, using the coordinates system $(r,s,t)$ on $\Gamma$, we have
+\begin{equation*}
+\int_{\Gamma}\lambda v\, d\sigma
+=\int _{\Lambda}  \int_{\partial\mathcal{D}(s)} (\avrc{\lambda}+\tilde{\lambda})(\avrc{v}+\tilde{v})d\gamma ds
+= \int_{\Lambda}|\partial\mathcal{D}(s)| \avrc{\lambda}\avrc{v}\,ds+\int_{\Lambda}  \int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v}d\gamma ds\,.
+\end{equation*}
+
+Then, we make the following modelling assumptions:
+\begin{description}
+\item[A3] we assume that the product of fluctuations is small, namely
+\begin{equation*}
+\int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v} d\gamma \simeq 0\,
+\end{equation*}
+\end{description}
+and we obtain 
+\begin{equation*}
+(\nabla u ,\nabla v)_{\Omega} +(u,v)_{\Omega}+(\avrc \lambda, \avrc v)_{\Lambda , |\DD|}  =(f,v)_{\Omega},
+\end{equation*}
+which, combined with \eqref{eq:1Ddirneu_weak} leads to the second formulation of the reduced problem.
+
+\subsection{Problem 2 (3D-1D-1D)}
+Let $\langle \cdot , \cdot \rangle_\Lambda$ denote the duality pairing between 
 $H^\frac12_{00}(\Lambda)$ and $H^{-\frac12}(\Lambda)$.
-The problem requires to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ L \in H^{-\frac12}(\Lambda)$, such that
+The problem requires to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
 \begin{subequations}\label{eq:problem2}
 \begin{align}
-&(u,v)_{H^1(\Omega)} + |{\cal D}|(\ud,\vd)_{H^1(\Lambda)} 
-+ |\partial {\cal D}| \langle \Pi_1 v - \Pi_2 \vd, L \rangle_{H^{-\frac12}(\Lambda)} 
+&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
++  \langle \avrc{T v} - \vd, \ld \rangle_{H^{-\frac12}(\Lambda), |\DD|} 
 \\
 \nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},V)_{L^2(\Lambda)}
+&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
 \quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
 \\
-&  |\partial {\cal D}| \langle \Pi_1 u -  \Pi_2 \ud, M \rangle_{H^{-\frac12}(\Lambda)} = 0
-\quad \forall M \in H^{-\frac12}(\Lambda)\,.
+&   \langle \avrc{T u} -   \ud, \md \rangle_{H^{-\frac12}(\Lambda),|\DD|} = 0
+\quad \forall \md \in H^{-\frac12}(\Lambda)\,.
 \end{align}
@@
 We notice that all the integrals of the reduced problem are well defined because $u,v \in H^1_0(\Omega)$, 
-$u,v|_{\Gamma} \in H^\frac12_{00}(\Gamma)$ and thus $\avrc{u},\avrc{v} \in H^\frac12_{00}(\Lambda)$.
-More precisely, $\Pi_1 : H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda$ such that
-$\Pi_1 u = \avrc{(u|_\Gamma)}$ is the combination between the trace on $\Gamma$ and the average on $\partial{\cal D}$.
-The operator $\Pi_2: H^1_0(\Lambda) \rightarrow H^\frac12_{00}(\Lambda)$ is the injection form $H^1_0(\Lambda)$ and $H^\frac12_{00}(\Lambda)$.
+$Tu, \ Tv \in H^\frac12_{00}(\Gamma)$ and thus $\avrc{Tu},\avrc{Tv} \in H^\frac12_{00}(\Lambda)$, as shown in the following lemma.
+%More precisely, $\Pi_1 : H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda$ such that
+%$\Pi_1 u = \avrc{(u|_\Gamma)}$ is the combination between the trace on $\Gamma$ and the average on $\partial{\cal D}$.
+%The operator $\Pi_2: H^1_0(\Lambda) \rightarrow H^\frac12_{00}(\Lambda)$ is the injection form $H^1_0(\Lambda)$ and $H^\frac12_{00}(\Lambda)$.
+
+\begin{lemma}\label{lemma:H12norm}
+{\color{red}TO DO: generalize to not uniform $\DD$} 
+When $\Gamma$ is a cylinder, if $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}\in H_{00}^{\frac 12}(\Lambda)$.
+Moreover, if $u\in H^{\frac 12}_{00}(\Gamma)$ is constant on each cross section, namely $u(s,\theta)=u(s)$, then
+\begin{equation*}
+\|u\|_{H^{\frac 12}_{00}(\Gamma)}=2\pi R \|u\|_{H^{\frac 12}_{00}(\Lambda)}.
+\end{equation*}
+\end{lemma}
+\begin{proof}
+Let us denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the laplacian on $\Gamma$, and with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $\Lambda$.
+In particular,
+\begin{align*}
+\phi _{ij}(s,\theta)=sin (i\pi s)\left( cos(j\theta)+ sin(j\theta) \right),\\
+\rho_{ij}=i\pi ^2+\frac{j^2}{R^2},\\
+\phi _{i}(s)=sin (i\pi s),\\
+\rho _i = i\pi ^2.
+\end{align*}
+It is easy to verify that 
+\begin{eqnarray}
+\label{null_int_eigenf}
+\int_0^{2\pi} \phi _{ij}(s,\theta)=0 \quad \forall j>0, \forall i \\
+\label{nonull_int_eigenf}
+\int_0^{2\pi} \phi _{ij}(s,\theta)= 2\pi R \, \sin(i \pi s) \quad \mbox{if } j=0, \forall i  .\\
+\end{eqnarray}
+Moreover we recall that $\phi_{i,j}(s,\theta)$ and $\phi _i(s)$ are orthogonal basis of $L^2(\Gamma)$ and $L^2(\Lambda)$ respectively. Therefore,
+\begin{multline*}
+\avrc{u}(s)=\frac{1}{2\pi R}\int_0^{2\pi} u(s,\theta)R\, d\theta
+= \frac{1}{2\pi R}\int_0^{2\pi} \sum_{i,j} a_{i,j} \phi_{i,j}(s,\theta) R\, d\theta
+\\= \frac{1}{2\pi R}\sum_{i,j} a_{i,j}\int_0^{2\pi}  \phi_{i,j}(s,\theta) R\, d\theta
+=  \sum_{i} a_{i,0} \phi_{i}(s).
+\end{multline*}
+From \cite[Lemma 4.11]{chandler2015interpolation} we have
+\begin{equation}\label{H12norm_Gamma}
+\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2,
+\text{ with }
+a_{ij}=\int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds.
+\end{equation}
+and 
+\begin{equation*}
+\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
+\text{ with }
+\avrc{a}_i=\int _0^1 \avrc{u}(s )\phi_{i}(s) ds.
+\end{equation*}
+
+Therefore, we have
+\begin{multline*}
+\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=
+\sum_{i=1}^{\infty}\left( 1+ i^2\pi^2\right)^{\frac 12}\left( \int_0^1 \avrc{u}(s) sin(i\pi s)\, ds \right)^2\\
+= \sum_{i=1}^{\infty} \left( 1+ i^2\pi^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^1 \sin(j\pi s) \sin(i\pi s) \, ds  \right)^2\\
+= \sum_{i=1}^{\infty} \frac 14 \left( 1+ i^2\pi^2\right)^{\frac 12}a_{i,0}^2\\
+\leq \sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ i^2\pi^2 + \frac{j^2}{R^2}\right)^{\frac 12} |a_{i,j}|^2 =\|u\|^2_{H^{\frac 12}(\Gamma)},
+\end{multline*}
+
+where we have used the fact that
+\begin{eqnarray*}
+&\int_0^1 \sin(i\pi s) \sin(j\pi s)\, ds=0 \quad \text{if $i\neq j$}\\
+&\int_0^1 \sin(i\pi s) \sin(j\pi s)\, ds=\frac 12 \quad \text{if $i =j$}.
+\end{eqnarray*}
+Moreover, in the case in which $u$ is constant on each cross section, from \eqref{H12norm_Gamma} we have
+\begin{multline*}
+\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2
+=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ i\pi ^2+\frac{j^2}{R^2}\right)^{\frac 12}\left( \int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds \right)^2\\
+=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ i\pi ^2+\frac{j^2}{R^2}\right)^{\frac 12}\left( \int _0^1 u(s) \int _0^{2\pi} \phi_{ij}\, R d\theta ds \right)^2,
+\end{multline*}
+and using \eqref{null_int_eigenf} and \eqref{nonull_int_eigenf}, we obtain
+\begin{multline*}
+\|u\|^2_{H^{\frac 12}(\Gamma)}=
+\sum_{i=1}^{\infty}\left( 1+ i\pi ^2\right)^{\frac 12}\left(\int _0^1 u(s )sin (i\pi s) 2\pi R ds\right)^2\\
+=4\pi ^2 R^2 \sum_{i=1}^{\infty}\left( 1+ \rho _i\right)^{\frac 12}|a_i|^2 = 4\pi ^2 R^2  \|u\|^2_{H^{\frac 12}(\Lambda)}.
+\end{multline*}
+\hspace*{0.9\textwidth} c.v.d.
+\end{proof}
+
+\begin{remark}
+The results of \eqref{lemma:H12norm}  can be generalized to the case of a  different geometry of $\Gamma$, for example a parallelepiped.  
+\end{remark}
+
 It is apparent that problems \eqref{eq:weak_dirneu} and \eqref{eq:red_dirneu} share the same mathematical structure.
@@
 
-\input{infsup}
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+%Analysis of the continuous problem 
+\input{infsup_continuous}
 
-\input{infsup_discrete}
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+%Analysis of the discrete problem in the case in which the LM lives on the coarser mesh w.r.t the trace mesh deriving from the 3D mesh
 
-\section{A benchmark problem with analytical solution}
+%\input{infsup_discrete_coarserLM}
 
-We consider the following 3D-1D coupled problem,
-\begin{subequations}\label{benchmark}
-\begin{align}
-\label{benchm_3d}
--\Delta u=f \quad &\text{in $\Omega$}\\
-\label{benchm_1d}
--d_{zz}^2 \ud =g \quad &\text{on $\Lambda$}\\
-u=0 \quad &\text{on $\partial \Omega$}\\
-\label{benchm_coupl}
-\ud -\avrc{u}=q \quad &\text{on $\Lambda$}
-\end{align}
-\end{subequations}
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+%Analysis of the discrete problem in the case in which the LM lives on the the trace mesh deriving from the 3D mesh (conforming to the interface cylinder \Gamma)
 
-where $\Omega=[0,1]\times [0,1]\times [0,H]$, $\Lambda=\{x=0.5\}\times \{y=0.5\} \times [0,H] $ and
-\begin{eqnarray*}
-f=8\pi ^2 \sin (2\pi x) \sin (2\pi y)\\
-%g=-\exp(-z)\\
-%q=1+\exp(-z).
-g=\frac{\pi ^2}{H^2} \sin \left(\frac{\pi z}{H}\right)\\
-q=\sin \left(\frac{\pi z}{H}\right).
-\end{eqnarray*}
-In this case the $z$ coordinate coincides with the axial coordinate along $\Lambda$.
-We define $\Sigma=[0.25,0.75]\times [0.25,0.75]\times [0,H]$.
-The average of the 3D solution $\avrc{u}$ in \eqref{benchm_coupl} is computed on the cross section $\DD$ of the virtual interface $\Gamma=\partial \Sigma$.
-The exact solution of \eqref{benchmark} is given by
-\begin{eqnarray}
-\label{benchm_sol3d}
-u=\sin (2\pi x) \sin (2\pi y)\\
-\label{benchm_sol1d}
-%\ud=1+\exp(-z).
-\ud=\sin \left(\frac{\pi z}{H}\right) 
-\end{eqnarray}
-Let us notice that $\ud$ satisfies homogeneous Dirichlet conditions at the boundary of $\Lambda$.
-Moreover, the solution \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfies on $\Gamma$ the relation
-\begin{equation}\label{benchm_flux}
-\lambda=\nabla u \cdot \textbf{n}_{\oplus}=d_z \ud n_{\oplus,z}=0,
-\end{equation}
-being $n_{\oplus,z}$ the $z-$component of the normal unit vector to $\Gamma$.
+\input{infsup_discrete_conformingLM}
 
-We prove that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of \eqref{eq:problem1} and \eqref{eq:problem2} in the simplified case in which the starting 3D-3D problem is
-\begin{subequations}\label{eq:dirneu_simple}
-\begin{align}
-- \Delta \up  &= f  && \text{ in } \Omega_{\oplus},\\
-- \Delta \uf &= g  && \text{ in } \Sigma,\\
--\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
-\uf - \up &= q  && \text{ on }  \Gamma,\\
-\up &= 0 && \text{ on } \partial \Omega\,.
-\end{align}
-\end{subequations}
-instead of \eqref{eq:dirneu}. Therefore the reduced problems in the two different formulations \eqref{eq:problem1} and \eqref{eq:problem2} become respectively
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+%Analysis of the discrete problem in the case in which we have a non conforming 3D mesh (just in the case of formulation 2 3D-1D-1D)
 
-\begin{subequations}\label{eq:problem1_simple}
-\begin{align}
-\label{eq:problem1_simple_eq1}
-&(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
-+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
-\\
-\label{eq:problem1_simple_eq2}
-&   \langle \Pi_1 u - \Pi_2 \ud , M \rangle_\Gamma =  \langle q , M \rangle_\Gamma
-\quad \forall M \in H^{-\frac12}(\Gamma)\,.
-\end{align}
-\end{subequations}
+\input{unfitted_prob2}
 
-and
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 
-\begin{subequations}\label{eq:problem2_simple}
-\begin{align}
-&(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
-+ |\partial {\cal D}| \langle \Pi_1 v - \Pi_2 \vd, L \rangle_{H^{-\frac12}(\Lambda)} 
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},V)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
-\\
-&  |\partial {\cal D}| \langle \Pi_1 u -  \Pi_2 \ud, M \rangle_{H^{-\frac12}(\Lambda)} =|\partial {\cal D}| \langle \avrc{q}, M \rangle_{H^{-\frac12}(\Lambda)}
-\quad \forall M \in H^{-\frac12}(\Lambda)\,.
-\end{align}
-\end{subequations}
-
-Let us prove that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of \eqref{eq:problem1_simple}.
-Using the integration by part formula and homogeneous boundary conditions on $\Omega$ and $\Lambda$, from \eqref{eq:problem1_simple_eq1} we have
-\begin{align*}
-&-(\Delta u, v)_{L^2(\Omega)} - |{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)} 
-+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda).
-\\
-\end{align*}
-Clearly, since \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d} satisfies \eqref{benchm_1d}, we have that \begin{align*}
--(\Delta u, v)_{L^2(\Omega)} =  (f,v)_{L^2(\Omega)} \\
--|{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
-\end{align*}
-and being $L=\lambda=0$, we can conclude that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfy \eqref{eq:problem1_simple_eq1}.
-The fact that the solution satisfy \eqref{eq:problem1_simple_eq2} follows from \eqref{benchm_coupl}.
-We can prove in the same way that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of \eqref{eq:problem2_simple}, exploiting the fact that in this case $L=\avrc{\lambda}=0$.
-
-\begin{remark}
-Let us notice that the 3D solution \eqref{benchm_sol3d} is such that $\avrc{u}=0$.
-Therefore in \eqref{benchmark} it is like we are solving two separated problems, one in $\Omega$ and the other on $\Lambda$.
-\end{remark}
-\begin{remark}
-It would be interesting to make a comparison between the solution of the fully coupled 3D-3D problem \eqref{eq:dirneu} (also in the simplified case of type \eqref{eq:dirneu_simple}) and the solution of the reduced problems \eqref{eq:problem1} and \eqref{eq:problem2}.
-Therefore, we could set the values of the data of the problem such that the reduced formulation becomes non-trivial and fully coupled.
-Then, we will solve both the original and reduced problem to observe the differences in the solutions and the values of the Lagrange multiplier.
-\end{remark}
-%\bibliographystyle{siamplain}
-%\bibliography{3d1d_coupled}
+\input{benchmark}
+%-----------------
+\bibliographystyle{siamplain}
+\bibliography{3d1d_coupled}
 \end{document}

### 2019-07-05 infsup_discrete_conformingLM.tex

\section{Finite element approximation}
The discrete equivalent of \eqref{eq:saddle-point} reads as finding $u_h\in X_h\subset X$, $\lambda_h\in Q_h\subset Q$ s.t.
\begin{eqnarray}\label{eq:saddle-point_discrete}
\begin{cases}
a(u_h,v_h)+b(v_h,\lambda_h)=c(v_h)\quad &\forall v_h\in X_h\\
b(u_h,\mu_h)=d(\mu_h) \quad &\forall \mu_h\in Q_h.
\end{cases}
\end{eqnarray}

{\color{red} Define Bh, etc}

\begin{theorem}[Ern-Guermond 2.42]
Problem \eqref{eq:saddle-point_discrete} is well-posed if and only if 
\begin{equation}\label{BNB1_discrete}
\exists \alpha_h >0 :\, \inf_{u_h\in ker(B_h)}\sup_{v_h\in ker(B_h)} \frac{a(u_h,v_h)}{\|u_h\|_{X}\|v_h\|_{X}}\geq \alpha_h
\end{equation}
and 
\begin{equation}\label{eq:infsup_discrete}
\exists \beta_h >0:\,\inf_{\mu_h\in Q_h}\sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}\|\mu_h\|_{Q}}\geq \beta_h .
\end{equation}
\end{theorem}
Let us notice that for both problem 1 and problem 2 the bilinear form $a(\cdot, \cdot)$ is coercive as stated in Lemmas \eqref{lemma:prob1_coercivity} and \eqref{lemma:prob2_coercivity}. Consequently, \eqref{BNB1_discrete} is automatically satisfied, being $\alpha_h$ the coercivity constant.\\

Let us introduce a shape-regular triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{h}$ of $\Lambda$. 
We analyze two different cases: the one in which the 3D mesh is conforming to the interface $\Gamma$, namely the set of the intersections of the 3D elements of $\mathcal{T}^{\Omega}_h$ with $\Gamma$ is constituted by facets of such elements, and the non conforming case, namely the 3D elements of $\mathcal{T}^{\Omega}_h$ 'cut' the interface $\Gamma$.

\subsection{$\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}

\subsubsection{Problem 1}
We denote by $X_{h,k}^0(\Omega)\subset H^1_0(\Omega)$ the conforming finite element space of continuous piecewise polynomials of degree $k$ defined on $\Omega$ satisfying homogeneous Dirichlet conditions on the boundary and by $X_{h,k}^0(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$, satisfying homogeneous Dirichlet conditions on $\Lambda \cap \partial \Omega$. 
%Moreover, $Q_{h}$ denotes a suitable trial space for the lagrange multiplier $\lambda_h$. In particular, $Q_h \subset H^{-\frac12}(\Gamma )$ in the case of Problem 1 and $Q_h \subset H^{-\frac12}(\Lambda)$ in the case of Problem 2.
Problem 1 consists to find $u_h \in X_{h,k}^0 (\Omega) ,\ {\ud}_h \in X_{h,k}^0(\Lambda) , \lambda_h \in Q_h(\Gamma) \subset H^{-\frac12}(\Gamma )$, such that
\begin{subequations}
\begin{align}
&(u_h,v_h)_{H^1(\Omega)} + ({\ud}_h,{\vd}_h)_{H^1(\Lambda),|\D|} 
+ \langle T v_h  - \mathcal{U}_E {\vd}_h, \lambda_h \rangle_\Gamma 
\\
\nonumber
&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda),|\D|}
\quad \forall v_h \in X_{h,k}^0(\Omega), \ {\vd}_h \in X_{h,k}^0(\Lambda)
\\
&   \langle T u_h - \mathcal{U} {\ud}_h , \mu_h \rangle_\Gamma = 0
\quad \forall \mu_h \in Q_h(\Gamma)\,,
\end{align}
\end{subequations}
The space $Q_h(\Gamma)$ must be suitably chosen such that \eqref{eq:infsup_discrete} holds. Let us denote with $W_{h,k}^0(\Gamma) \subset H^{\frac 12}_{00}(\Gamma)$ the trace space of functions running in $X_{h,k}^0(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$. We choose $Q_h(\Gamma)=W_{h,k}^0(\Gamma)$, therefore we impose homogeneous Dirichlet boundary condition on $\partial \Omega$ also for the Lagrange multiplier. For this choice of $Q_h(\Gamma)$ we can prove the well-posedness of the discrete problem, as shown in the following.

\begin{lemma}
Let $P_h: H^{\frac 12}_{00}(\Gamma) \longrightarrow W_{h,k}^0(\Gamma)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Gamma)$ by
\begin{equation*}
(P_h v , \psi)_\Gamma= (v, \psi)_\Gamma \qquad \forall \psi \in W_{h,k}^0(\Gamma).  
\end{equation*} 
Then, $P_h$ is continuous on $H^{\frac 12}_{00}(\Gamma)$, namely
\begin{equation}\label{continuity_projoper}
\|P_h v\|_{H^{\frac 12}(\Gamma)} \leq C \|v\|_{H^{\frac 12}(\Gamma)},
\end{equation}
where $C$ is a positive constant independent of $h$.
\end{lemma}
\begin{proof}
We prove that $P_h$ is continuous on $L^2(\Gamma)$ and on $H^1_0(\Gamma)$ following \cite[Section 1.6.3]{MR2050138}.  Then, the inequality \eqref{continuity_projoper} can be dirived by Hilbertian interpolation. For the $L^2$-continuity, we exploit the fact that, from the definition of $P_h$,
\begin{equation*}
(v-P_h v,P_h v)_{\Gamma}=0.
\end{equation*} 
Therefore, by Pythagoras identity,
\begin{equation*}
\|v\|^2_{L^2(\Gamma)} = \|v-P_h v\|_{L^2(\Gamma)}^2 + \|P_h v\|_{L^2(\Gamma)}^2 \geq \|P_h v\| _{L^2(\Gamma)}.
\end{equation*}
Let us now consider $v\in H^1_0(\Gamma)$.The Scott-Zhang interpolation operator $SZ_h$ from $H^1_0(\Gamma)$ to $W_{h,k}^0(\Gamma)$ satisfies the following inequalities,
\begin{equation}\label{SZ_stability}
\|SZ_h v\|_{H^1(\Gamma)} \leq C_1 \|v\|_{H^1(\Gamma)}
\end{equation} 
\begin{equation}\label{SZ_approx}
\|v -SZ_h v \|_{L^2(\Gamma)}\leq C_2 h \|v\|_{H^1(\Gamma)}.
\end{equation}
Therefore,
\begin{equation*}
\begin{split}
\|\nabla P_h v\|_{L^2(\Gamma)} 
&\leq \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + \|\nabla SZ_h v\|_{L^2(\Gamma)}\\
&\leq \text{ (using \eqref{SZ_stability}) } \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
\end{split}
\end{equation*}
and by using the inverse inequality we obtain
\begin{equation*}
\begin{split}
\|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
&\leq \frac{C_3}{h} \|P_h v - SZ_h v\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
&= \frac{C_3}{h} \|P_h (v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
&\leq  \text{ (Stability of $P_h$ in $L^2$) } \frac{C_3}{h} \|v - SZ_h v\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
&\leq \text{ (using \eqref{SZ_approx}) } \frac{C_3}{h} C_2 h  \| v\|_{H^1(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
&\leq (C_2 C_3 +C_1) \|v\|_{H^1(\Gamma)},
\end{split}
\end{equation*}
from which we obtain the continuity in $H^1_0(\Gamma)$.\\
{\color{red} I would skip this proof and just leave the citation}
\end{proof}

\begin{lemma}\label{lemma:trspace_infsup} 
There exist a constant $\gamma >0$ such that
\begin{equation*}
\sup_{\substack{q_h \in W_{h,k}^0(\Gamma)}} \frac{\langle q_h , \mu_h \rangle}{ \|q_h\|_{H^{\frac 12}(\Gamma)}} \geq \gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)}.
\end{equation*} 
\end{lemma}
\begin{proof}
Let $\mu_h$ be in $Q_h(\Gamma)$. From the continuous case, in particular from \eqref{infsup_traceop}, we have
\begin{equation*}
\|\mathcal{E}\|^{-1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle Tv , \mu_h \rangle}{\|v\|_{H^1(\Omega)}} 
\end{equation*}
and by the trace inequality $\|Tv\|_{H^\frac 12 (\Gamma)} \leq C_T \|v\|_{H^1(\Omega)}$ (see \cite[7.56]{adams1975pure}), we obtain 
\begin{equation*}
\sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle T v , \mu_h \rangle}{\|v\|_{H^1(\Omega)}}
\leq C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle T v , \mu_h \rangle}{ \|Tv\|_{H^{\frac 12}(\Gamma)}}.
\end{equation*}
By the definition of $P_h$ and \eqref{continuity_projoper} 
\begin{equation*}
\begin{split}
C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle T v , \mu_h \rangle}{ \|Tv\|_{H^{\frac 12}(\Gamma)}}&= C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(T v) , \mu_h \rangle}{ \|Tv\|_{H^{\frac 12}(\Gamma)}}\\
&\leq  C_T C \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(T v) , \mu_h \rangle}{ \|P_h(Tv)\|_{H^{\frac 12}(\Gamma)}}\\
&= C_T C \sup_{\substack{q_h \in W_{h,k}^0(\Gamma)}} \frac{\langle q_h , \mu_h \rangle}{  \|q_h\|_{H^{\frac 12}(\Gamma)}}.
\end{split}
\end{equation*}
\end{proof}

\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds, namely 
$\exists \beta_{h,1} >0$ s.t.
\begin{equation}\label{inf_sup_discrete_prob1}
\inf_{\mu_h \in Q_h(\Gamma)} 
\sup_{\substack{v_h \in X^0_{h,k}(\Omega),\\ {\vd}_h \in X^0_{h,k}(\Lambda)}} \frac{ \langle T v_h - \mathcal{U}_E {\vd}_h, \mu_h \rangle _{\Gamma}} {\vertiii{[v_h, {\vd} _h]} \|\mu_h\|_{H^{-\frac 12 }(\Gamma)}} 
\geq \beta_{h,1}. 
\end{equation}
\end{theorem}

\begin{proof}
Let $\mu_h \in Q_h(\Gamma)$. As in the continuos case, we choose ${\vd}_h =0$ and we have
\begin{equation*}
\sup_{\substack{v_h \in X^0_{h,k}(\Omega),\\ {\vd}_h \in X^0_{h,k}(\Lambda)}} \frac{ \langle T v_h - \mathcal{U}_E {\vd}_h, \mu_h \rangle _{\Gamma}} {\vertiii{[v_h,  {\vd}_h]}}
\geq \sup_{v_h \in X^0_{h,k}(\Omega)} \frac{ \langle T v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}}.
\end{equation*}

Therefore, we want to prove that there exists $\beta_{h,1}$ such that
\begin{equation*}
\sup_{v_h \in X^0_{h,k}(\Omega)} \frac{ \langle T v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}} \geq \beta_{h,1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \qquad \forall \mu_h \in Q_h(\Gamma).
\end{equation*}

Using Lemma \ref{lemma:trspace_infsup} and the boundedness of the armonic extension operator $\mathcal{E}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
\begin{equation*}
\gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq  \sup_{q_h \in Q_h(\Gamma)} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|q_h\|_{H^{\frac 12}(\Gamma)}} 
\leq 
\|\mathcal{E}\| \sup_{q_h \in Q_h(\Gamma)} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{E}q_h\|_{H^1(\Omega)}} .
\end{equation*}
Let $R_h: H^1_0(\Omega) \rightarrow X_{h,k}^0(\Omega)$ be a quasi interpolation operator satisfying 
\begin{equation*}
\|R_h v\|_{H^1(\Omega)} \leq C_R \|v\|_{H^1(\Omega)} \qquad \forall v \in H^1_0(\Omega).
\end{equation*}
Therefore, we obtain 
\begin{equation*}
\|\mathcal{E}\| \sup_{q_h \in Q_h(\Gamma)} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{E}q_h\|_{H^1(\Omega)}} 
\leq
\|\mathcal{E}\| C_R \sup_{q_h \in Q_h(\Gamma)} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|R_h \mathcal{E} q_h\|_{H^1(\Omega)}}
\end{equation*}
and we have
\begin{multline}
\gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)} 
\leq 
\sup_{q_h \in Q_h(\Gamma)} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|q_h\|_{H^{\frac 12}(\Gamma)}} 
\leq
\|\mathcal{E}\| C_R \sup_{q_h \in Q_h(\Gamma)} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{E} q_h\|_{H^1(\Gamma)}}
\\
=
\|\mathcal{E}\| C_R \sup_{q_h \in Q_h(\Gamma)} \frac{ \langle T \ R_h E q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{E} q_h\|_{H^1(\Omega)}} 
\leq \|\mathcal{E}\| C_R \sup_{v_h \in X_{h,k}(\Omega)} \frac{ \langle T v_h, \mu_h \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
\end{multline}
Therefore the inf-sup condition $\eqref{inf_sup_discrete_prob1}$ holds with $\beta_{h,1} = \gamma \|\mathcal{E}\|^{-1} C_R^{-1} $.
\end{proof}
{\color{red}
\begin{remark} We notice that to prove the result in Lemma \ref{lemma:trspace_infsup} (and then the discrete inf-sup condition)  basically we need a projection operator $P_h: H^{\frac 12}_{00} \longrightarrow W_{h,k}^0(\Gamma)$ orthogonal in the multiplier space $Q_h(\Gamma)$, namely such that $\langle P_h v, \mu_h \rangle = \langle v, \mu_h \rangle, \, \forall \mu_h \in Q_h(\Gamma)$, and continuous in $H^{\frac 12}(\Gamma)$. Therefore, in principle different choices than $Q_h(\Lambda)=W_{h,k}^0(\Gamma)$ could be considered if we can build an operator $P_h$ satisfying these properties. In \cite{belgacem1999mortar} such operator $P_h$  is built for a particular choice of $Q_h(\Gamma)$ but it is not clear how they prove the $H^1$-stability inequality (and consequently the $H^{\frac 12 }$-stability) with a constant independent of the mesh size $h$...
\end{remark}  
}
\subsubsection{Problem 2}
This problem requires to find  $u_h \in X^0_{h,k}(\Omega) ,\ {\ud}_h \in X^0_{h,k}(\Lambda), \ {\ld}_h \in Q_h(\Lambda) \subset H^{-\frac12}(\Lambda)$, such that
\begin{subequations}
\begin{align}\label{eq:prob2_discrete}
&(u_h,v_h)_{H^1(\Omega)} + ({\ud}_h,{\vd}_h)_{H^1(\Lambda), |{\cal D}|} 
+  \langle  \avrc{Tv_h} -  {\vd}_h, {\ld}_h \rangle_{\Lambda, |\DD|} 
\\
\nonumber
&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda), |{\cal D}|}
\quad \forall v_h \in X_h(\Omega), \ {\vd}_h \in X_h(\Lambda)
\\
&  \langle \avrc{T u_h} - {\ud}_h, {\md}_h \rangle_{\Lambda,| \DD| } = 0
\quad \forall {\md}_h \in Q_h(\Lambda)\,.
\end{align}
\end{subequations}

We introduce the space
$W_{h,k}^0(\Lambda) \subset H^{\frac 12} _{00} (\Lambda)$, which is the averaged trace space of functions running in $H^1_0(\Omega)$. It coincides with the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$ and satisfying homogeneous Dirichlet boundary condition. {\color{red} (Add assumptions..)}
We choose $Q_h(\Lambda)=W_{h,k}^0(\Lambda)$, therefore we impose homogeneous Dirichlet boundary condition on $\Lambda \cap \partial \Omega$ also for the Lagrange multiplier. With this choice for $Q_h(\Lambda)$, we can prove the well-posedness of the discrete problem. In particular, following the same steps as for Problem 1, we can prove the following results.
\begin{lemma}
Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow W_{h,k}^0(\Lambda)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
\begin{equation*}
(P_h v , \psi)_\Lambda= (v, \psi)_\Lambda \qquad \forall \psi \in W_{h,k}^0(\Lambda).  
\end{equation*} 
Then, $P_h$ is continuous on $H^{\frac 12}_{00}(\Lambda)$, namely
\begin{equation*}
\|P_h v\|_{H^{\frac 12}_{00}(\Lambda)} \leq C \|v\|_{H^{\frac 12}_{00}(\Lambda)},
\end{equation*}
where $C$ is a positive constant independent of $h$.
\end{lemma}

\begin{lemma}\label{infsup_avr_trspace}
There exist a constant $\gamma >0$ such that
\begin{equation*}
\sup_{\substack{q_h \in W_{h,k}^0(\Lambda)}} \frac{\langle q_h , \mu_h \rangle}{ \|q_h\|_{H^{\frac 12}(\Lambda)}} \geq \gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall \mu_h \in W_{h,k}^0(\Lambda).
\end{equation*} 
\end{lemma}

\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds, namely 
$\exists \beta_{h,2} >0$ s.t.
\begin{equation}
\inf_{\mu_h \in Q_h(\Lambda)} 
\sup_{\substack{v_h \in X^0_{h,k}(\Omega),\\ {\vd}_h \in X^0_{h,k}(\Lambda)} }\frac{\langle \avrc{Tv_h} -  {\vd}_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\vertiii{[v_h, {\vd}_h]} \|{\md}_h\|_{H^{-\frac 12 }(\Lambda)} } 
\geq \beta_{h,2}. 
\end{equation}
\end{theorem}
\begin{proof}
Let ${\md}_h$ be arbitrarly chosen in $Q_h(\Lambda)$. Again, we choose ${\vd}_h =0$, so that the proof reduces to show that there exists $\beta_{h,2}$ such that
\begin{equation*}
\sup_{v_h \in X_{h,k}^0(\Omega)} \frac{ \langle \avrc{T v_h} , {\md}_h \rangle _{\Lambda,|\DD|} } {\|v_h\|_{H^1(\Omega)} }\geq \beta_{h,2} \|{\md}_h\|_{H^{-\frac 12}(\Lambda)}\ \qquad \forall {\md}_h \in Q_h(\Lambda).
\end{equation*}
Let us denote with $\mathcal{U}_E$ the uniform extension operator from $\Lambda$ to $\Gamma$. Using Lemma \ref{H12norm_Gamma}, we easily have for any $w \in H^{\frac 12}(\Lambda)$,\\
{\color{red} TO DO: generalize to non constant $\DD$}
\begin{equation*}
\|\mathcal{U}_E w\|_{H^{\frac 12}(\Gamma)}=|\DD| \|w\|_{H^{\frac 12}(\Lambda)}.
\end{equation*}
Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $E$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X^0_{h,k}(\Omega)$, we obtain
\begin{multline}
\gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \leq 
\sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
\\
= |\DD| \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
\leq |\DD|\|E\| \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda} } {\|E \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
\\
\leq |\DD|\|E\| C_R \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
\\ 
=  |\DD|\|E\| C_R \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E q_h, \mu_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
\\
\leq |\DD|\|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi _2  v_h, \mu_h \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
\end{multline}

%\begin{equation*}
%\|\mathcal{U}_E w\|_{H^{\frac 12}(\Gamma)}\lesssim \|w\|_{H^{\frac 12}(\Lambda)}.
%\end{equation*}
%Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{E}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X^0_{h,k}(\Omega)$, we obtain
%\begin{multline}
%\gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \leq 
%\sup_{q_h \in Q_h(\Lambda)} \frac{ \langle q_h, {\md}_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
%\\
%\lesssim \sup_{q_h \in Q_h(\Lambda)} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
%\lesssim \|\mathcal{E}\| \sup_{q_h \in Q_h(\Lambda)} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda} } {\|\mathcal{E} \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
%\\
%\lesssim \|\mathcal{E}\| C_R \sup_{q_h \in Q_h(\Lambda)} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
%\\ 
%\lesssim\|\mathcal{E}\| C_R \sup_{q_h \in Q_h(\Lambda)} \frac{ \langle \avrc{TR_h E \mathcal{U}_E q_h}, {\md}_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
%\\
%\lesssim\|\mathcal{E}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \avrc{T v_h}, {\md}_h \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
%\end{multline}

\end{proof}

{\color{red}
*******************extension to non uniform $|\DD|$
}
\begin{lemma}
Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow W_{h,k}^0(\Lambda)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
\begin{equation*}
(P_h v , \psi)_{\Lambda,|\DD|}= (v, \psi)_{\Lambda , |\DD|} \qquad \forall \psi \in W_{h,k}^0(\Lambda).  
\end{equation*} 
Then, $P_h$ is continuous on $H^{\frac 12}_{00}(\Lambda)$, namely
\begin{equation*}
\|P_h v\|_{H^{\frac 12}(\Lambda),|\DD|} \leq C \|v\|_{H^{\frac 12}(\Lambda),|\DD|},
\end{equation*}
where $C$ is a positive constant independent of $h$.
\end{lemma}

\begin{lemma}\label{infsup_avr_trspace}
There exist a constant $\gamma >0$ such that
\begin{equation*}
\sup_{\substack{q_h \in W_{h,k}^0(\Lambda)}} \frac{\langle q_h , {\md}_h \rangle_{\Lambda, |\DD|}}{ \|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} \geq \gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall {\md}_h \in W_{h,k}^0(\Lambda).
\end{equation*} 
\end{lemma}

\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds, namely 
$\exists \beta_{h,2} >0$ s.t.
\begin{equation}
\inf_{\mu_h \in Q_h(\Lambda)} 
\sup_{\substack{v_h \in X^0_{h,k}(\Omega),\\ {\vd}_h \in X^0_{h,k}(\Lambda)} }\frac{\langle \avrc{Tv_h} -  {\vd}_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\vertiii{[v_h, {\vd}_h]} \|{\md}_h\|_{H^{-\frac 12 }(\Lambda)} } 
\geq \beta_{h,2}. 
\end{equation}
\end{theorem}
\begin{proof}
Let ${\md}_h$ be arbitrarly chosen in $Q_h(\Lambda)$. Again, we choose ${\vd}_h =0$, so that the proof reduces to show that there exists $\beta_{h,2}$ such that
\begin{equation*}
\sup_{v_h \in X_{h,k}^0(\Omega)} \frac{ \langle \avrc{T v_h} , {\md}_h \rangle _{\Lambda,|\DD|} } {\|v_h\|_{H^1(\Omega)} }\geq \beta_{h,2} \|{\md}_h\|_{H^{-\frac 12}(\Lambda)}\ \qquad \forall {\md}_h \in Q_h(\Lambda).
\end{equation*}
Let us denote with $\mathcal{U}_E$ the uniform extension operator from $\Lambda$ to $\Gamma$. {\color{red}We notice that for any $w \in H^{\frac 12}(\Lambda)$,
\begin{equation*}
\|\mathcal{U}_E w\|_{H^{\frac 12}(\Gamma)}= \|w\|_{H^{\frac 12}(\Lambda),|\DD|}.
\end{equation*}
}
Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{E}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X^0_{h,k}(\Omega)$, we obtain
\begin{multline}
\gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \leq 
\sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} 
\\
=  \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
\leq \|\mathcal{E}\| \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|\mathcal{E} \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
\\
\leq \|\mathcal{E}\| C_R \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
\\ 
=  \|\mathcal{E}\| C_R \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle 	\avrc{T  R_h E \mathcal{U}_E q_h}, \mu_h \rangle _{\Lambda,|\DD|}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
\\
\leq \|\mathcal{E}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \avrc{T v_h}, \mu_h \rangle _{\Lambda,|\DD|}} {\|v_h\|_{H^1(\Omega)}}. 
\end{multline}

\end{proof}

### 2019-07-05 lm3d1d_vs1/infsup.tex

--- 2019-03-04 infsup.tex
@@
 a(u,v)+b(v,p)=f(v)\quad &\forall v\in X\\
-b(u,q)=g(q) \quad &\forall q\in M
+b(u,q)=g(q) \quad &\forall q\in Q
 \end{cases}
@@
 \nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}(\avrd{g},\vd)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
+&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}|(\avrd{g},\vd)_{L^2(\Lambda)}
+\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
 \\
-&   |\langle \Pi_1 u - \Pi_2 \ud , M \rangle_\Gamma = 0
+&   \langle \Pi_1 u - \Pi_2 \ud , M \rangle_\Gamma = 0
 \quad \forall M \in H^{-\frac12}(\Gamma)\,,
@@
 We apply theorem \ref{th:bnb} in the following spaces 
-$X=H^1_0(\Omega) \times H^1(\Lambda)$, $Q=H^{-\frac 12}(\Gamma)$
-and we prove that:
+$X=H^1_0(\Omega) \times H^1_0(\Lambda)$, $Q=H^{-\frac 12}(\Gamma)$, where $X$  is equipped with the norm $\vertiii{[u,\ud ]}^2=\|u\|^2_{H^1(\Omega)} + |\D|\|\ud\|^2_{H^1(\Lambda)}$. We prove that:
 \begin{itemize}
@@
 \begin{equation*}
-\sup _{v\in H^1_0(\Omega),\, \vd \in H^1_0(\Lambda)} \frac{ \langle \Pi_1 v  - \Pi_2 \vd, M \rangle_\Gamma}{\sqrt{\|v\|^2_{H^1(\Omega)}+\|\vd \|^2_{H^1(\Lambda)}}}\geq \beta \sup_{q\in H^{\frac 12}_{00}(\Gamma)}\frac{\langle q, M\rangle}{\|q\|_{H^{\frac 12}_{00}(\Gamma)}}.
+\sup _{v\in H^1_0(\Omega),\, \vd \in H^1_0(\Lambda)} \frac{ \langle \Pi_1 v  - \Pi_2 \vd, M \rangle_\Gamma}{\vertiii{[v, \vd]}}\geq \beta \sup_{q\in H^{\frac 12}(\Gamma)}\frac{\langle q, M\rangle}{\|q\|_{H^{\frac 12}(\Gamma)}}.
 \end{equation*}
@@
 \begin{equation*}
-\sup _{v\in H^1_0(\Omega),\, \vd \in H^1_0(\Lambda)} \frac{ \langle \Pi_1 v  - \Pi_2 \vd, M \rangle_\Gamma}{\sqrt{\|v\|^2_{H^1(\Omega)}+\|\vd \|^2_{H^1(\Lambda)}}} 
+\sup _{v\in H^1_0(\Omega),\, \vd \in H^1_0(\Lambda)} \frac{ \langle \Pi_1 v  - \Pi_2 \vd, M \rangle_\Gamma}{\vertiii{[v, \vd]}} 
 \geq \sup _{v\in H^1_0(\Omega)} \frac{ \langle \Pi_1 v, M \rangle_\Gamma}{\|v\|_{H^1(\Omega)}}.
@@
 
-The trace operator is surjective from $H^1_0(\Omega)$ to $H^{\frac12}_{00}(\Gamma)$. Consequently, $\forall \xi \in H^{\frac 12}_{00}(\Gamma)$, we find $v$ solution of
+The trace operator is surjective from $H^1_0(\Omega)$ to $H^{\frac12}_{00}(\Gamma)$. Indeed, $\forall \xi \in H^{\frac 12}_{00}(\Gamma)$, we  can find $v$ solution of
 \begin{eqnarray*}
@@
 The boundedness/stability of this operator ensures that there exists $\| E \| \in \mathbb{R}$ such that
-$v=E\xi $ and $\|v \|_{H^1(\Omega)}\leq \|E\| \|\xi \|_{H^{\frac 12}_{00}(\Gamma)}$. 
+$v=E(\xi) $ and $\|v \|_{H^1(\Omega)}\leq \|E\| \|\xi \|_{H^{\frac 12}_{00}(\Gamma)}$. 
 Substituting in the previous inequalities we obtain
-\begin{equation*}
+\begin{equation}\label{infsup_traceop}
 \sup _{v\in H^1_0(\Omega)} \frac{ \langle \Pi_1 v, M \rangle_\Gamma}{\|v\|_{H^1(\Omega)}}
@@
 = \|E\|^{-1} \|M\|_{H^{-\frac 12}(\Gamma)},
-\end{equation*}
+\end{equation}
 where in the last inequality we exploited the fact that $H^{-\frac 12}(\Gamma)=(H^{\frac 12 }_{00}(\Gamma))^*$. 
@@
 \begin{align}
-&(u,v)_{H^1(\Omega)} + |{\cal D}|(U,V)_{H^1(\Lambda)} 
-+ |\partial {\cal D}| \langle  \Pi_1 V - \Pi_2 v, L \rangle_\Lambda 
+&(u,v)_{H^1(\Omega)} + |{\cal D}|(\ud,\vd)_{H^1(\Lambda)} 
++ |\partial {\cal D}| \langle  \Pi_1 \vd - \Pi_2 v, L \rangle_\Lambda 
 \\
@@
 &\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},V)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ V \in H^1(\Lambda)
+\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
 \\
-&  |\partial {\cal D}| \langle \Pi_1 U - \Pi_2 u, M \rangle_\Lambda = 0
+&  |\partial {\cal D}| \langle \Pi_1 \ud - \Pi_2 u, M \rangle_\Lambda = 0
 \quad \forall M \in H^{-\frac12}(\Lambda)\,.
@@
 Here, $\Pi_1: H^1_0(\Lambda)\rightarrow H^{\frac 12}_{00}(\Lambda)$ is the immersion operator and $\Pi_2: H^1_0(\Omega)\rightarrow H^{\frac 12}_{00}(\Lambda)$ is defined as the composition of the trace operator $T_{\Gamma}: H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ and the average operator $\bar{(\,)}:H^{\frac 12}_{00}(\Gamma) \rightarrow H^{\frac 12}_{00}(\Lambda)$, namely $\Pi_2= \bar{(\,)}\circ T_{\Gamma}$.
-First of all we prove that if $v\in H^1_0(\Omega)$, than $\Pi _2 v \in H^{\frac 12}_{00}(\Lambda)$.
-In particular, from standard trace theory, we have that $T_{\Gamma} v\in H^{\frac 12}_{00}(\Gamma)$, therefore we have to prove that if $v \in H^{\frac 12 }(\Gamma)$ then $\avrc{v}\in H^{\frac 12}(\Lambda)$.
+First of all we prove that if $u\in H^1_0(\Omega)$, than $\Pi _2 u \in H^{\frac 12}_{00}(\Lambda)$.
+In particular, from standard trace theory, we have that $T_{\Gamma} u\in H^{\frac 12}_{00}(\Gamma)$, therefore we have to prove that if $u \in H^{\frac 12 }_{00}(\Gamma)$ then $\avrc{u}\in H^{\frac 12}_{00}(\Lambda)$.
 
@@
 \end{multline*}
-From \cite[Lemma 4.11]{c-w_h_m_2015} we have
+From \cite[Lemma 4.11]{chandler2015interpolation} we have
 \begin{equation}\label{H12norm_Gamma}
@@
 Then, we apply Theorem \ref{th:bnb} with the following spaces $X=H^1_0(\Omega) \times H^1_0(\Lambda)$, $Q=H^{-\frac 12}(\Lambda)$.
-Let us consider $X$ equipped with the norm $\vertiii{[u,\ud ]}^2=\|u\|^2_{H^1(\Omega)} + |\D|\|\ud\|^2_{H^1(\Lambda)}$, 
+Let us consider $X$ equipped again with the norm $\vertiii{[u,\ud ]}^2=\|u\|^2_{H^1(\Omega)} + |\D|\|\ud\|^2_{H^1(\Lambda)}$, 
 $Q$ equipped with the norm
@@
 \begin{itemize}
-\item the form $a([u,U], [v,V])= (u,v)_{H^1(\Omega)} + |{\cal D}|(U,V)_{H^1(\Lambda)}$ is coercive 
+\item the form $a([u,\ud], [v,\vd])= (u,v)_{H^1(\Omega)} + |{\cal D}|(\ud,\vd)_{H^1(\Lambda)}$ is coercive 
 $\implies$ \eqref{BNB1} is fulfilled. Indeed, we have,
@@
 \begin{equation*}
-\sup _{v\in H^1_0(\Omega),\, V \in H^1_0(\Lambda)} \frac{ \langle  \Pi_1 V - \Pi_2 v, M \rangle_\Lambda}{\sqrt{\|v\|^2_{H^1(\Omega)}+\|V \|^2_{H^1(\Lambda)}}}
+\sup _{v\in H^1_0(\Omega),\, \vd \in H^1_0(\Lambda)} \frac{ \langle  \Pi_1 \vd - \Pi_2 v, M \rangle_\Lambda}{\sqrt{\|v\|^2_{H^1(\Omega)}+|\D| \|\vd \|^2_{H^1(\Lambda)}}}
 \geq \beta \sup_{q\in H^{\frac 12}(\Lambda)}\frac{\langle q, M\rangle_\Lambda}{\|q\|_{H^{\frac 12}(\Lambda)}}.
 \end{equation*}
-We choose $V=0$ and we obtain
+We choose $\vd=0$ and we obtain
 \begin{equation*}
-\sup _{v\in H^1_0(\Omega),\, V \in H^1_0(\Lambda)} \frac{ \langle  \Pi_1 V - \Pi_2 v, M \rangle_\Lambda}{\sqrt{\|v\|^2_{H^1(\Omega)}+\|V \|^2_{H^1(\Lambda)}}}
+\sup _{v\in H^1_0(\Omega),\, \vd \in H^1_0(\Lambda)} \frac{ \langle  \Pi_1 \vd - \Pi_2 v, M \rangle_\Lambda}{\sqrt{\|v\|^2_{H^1(\Omega)}+|\D|\|\vd \|^2_{H^1(\Lambda)}}}
 \geq \sup _{v\in H^1_0(\Omega)} \frac{ \langle \Pi_2 v, M \rangle_\Lambda}{\|v\|_{H^1(\Omega)}}. 
@@
 
-For any $q \in H^{\frac 12}_{00}(\Lambda)$, we consider its uniform extension to $\Gamma$ 
+For any $q \in H^{\frac 12}_{00}(\Lambda)$, we consider its uniform extension to $\Gamma$ (we denote it again with $q$) 
 and then we consider the harmonic extension $v=E(q)\in H^1_0(\Omega)$. It follows that $\Pi_2 v=q$. Therefore, 

### 2019-07-05 unfitted_prob1.tex

--- 2019-05-09 unfitted.tex
@@
-\section{Unfitted P1-P1-P0 case}
+\section{Unfitted P1-P1-P0}
 \subsection{Problem 1} All the observations and the proofs are an application of \cite{burman2014} to our case.
-Let $\mathcal{T}^{\Omega}_h$ and  $\mathcal{T}^{\Lambda}_{h}$ denote a shape-regular triangulation  of $\Omega$ and an admissible partition  of $\Lambda$ respectively.
+Let $\mathcal{T}^{\Omega}_h$ and  $\mathcal{T}^{\Lambda}_{h'}$ denote a shape-regular triangulation  of $\Omega$ and an admissible partition  of $\Lambda$ respectively.
 Let us also introduce the set $\mathcal{G}_h$ of elements of $\mathcal{T}^{\Omega}_h$ intersecting the interface $\Gamma$, namely $\mathcal{G}_h=\left\{ K\in \mathcal{T}^{\Omega}_h : \, K\cap \Gamma \neq \emptyset \right\}$.
@@
 The space $L_h$ is built as the space of $P^0$ functions defined on macro patches $\left\{ F_j \right\}_j$ of elements of $\mathcal{G}_h$.
-These patches are such that $diam(F_j)\leq H$ and  $jH\leq |F_j\cap \Gamma|\leq H+h$.
+These patches are such that $diam(F_j)\leq H$ and  $H\leq |F_j\cap \Gamma|\leq H+h$.
 Moreover, there exist constants $c_h$ and $c_H$ such that $c_hh\leq H \leq c_H^{-1}h$.

### 2019-07-05 unfitted_prob2.tex

\subsection{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$}
We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_h$ cut the interface $\Gamma$. It is easy to understand that the formulation of Problem 2 is more suitable. 
{\color{red} Add more details, we can refer also to cutFEM (Burman, Massing etc.) explaining the limitation of that approach (network case for example).}\\
Therefore we focus on the analysis of Problem 2.

\subsubsection{Problem 2} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X^0_{h,1}(\Omega)$ and $X^0_{h,1}(\Lambda)$, see the previous subsection for the definition. Concerning the multiplier space, we make the following choice, $Q_h(\Lambda)=\{{\ld}_h : {\ld}_h \in P^0(K) \forall K \in \mathcal{T}^{\Lambda}_{h'}\}$, namely the multiplier lives on the same mesh used for the 1D solution ${\ud}_h$. Notice that in this case we suppose that the mesh sizes of the 3D mesh $	\mathcal{T}^{\Omega}_h$ and the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different, in particular we suppose the 1D mesh is finer. With this choice the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s({\ld}_h, {\md}_h)$ to \eqref{eq:prob2_discrete} following the approach introduce in \cite{burman2014}. In particular, we build a new multiplier space $L_h(\Lambda)$ for which the discrete inf-sup condition is fulfilled and we build a projection operator $\pi_L: Q_h(\Lambda) \rightarrow L_h(\Lambda)$. Based on this projection operator, we build the stabilization term $s({\ld}_h, {\md}_h)$ and prove that $\forall [u_h, {\ud}_h]$, there exists $\xi_h([u_h, {\ud}_h]) \in Q_h(\Lambda)$ s.t.  
\begin{equation}\label{stab_coercivity}
a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h([u_h, {\ud}_h])) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X^0_{h,1}(\Omega)\times X^0_{h,1}(\Lambda) },
\end{equation}
\begin{equation}\label{stab_stability}
(s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[u_h, {\ud}_h]}_{X^0_{h,1}(\Omega)\times X^0_{h,1}(\Lambda) },
\end{equation}
being $\vertiii{[\cdot \, ,\, \cdot] }_{X^0_{h,1}(\Omega)\times X^0_{h,1}(\Lambda) }$ a suitable discrete norm. \\

We recall that in the case of Problem 2, 
\begin{equation*}
b([u_h, {\ud}_h], {\ld}_h) = \left(\avrc{T u_h} - {\ud}_h, {\ld}_h\right)_{\Lambda,|\DD|}.
\end{equation*}
The construction of the inf-sup stable space $L_h(\Lambda)$ is based on assembling the elements of the 3D mesh $\mathcal{T}_h^{\Omega}$ intersecting the 1D manifold $\Lambda$ into macro patches $\left\{ F_j \right\}_j$. These patches are such that and  $H\leq |F_j\cap \Lambda|\leq H+h$, where $H$ is sufficiently larger than $h$. Moreover,  we assume there exist constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$. We define the space $L_h(\Lambda)$ as the space of functions which are $P^0$ on each intersection $F_j\cap \Lambda$. Moreover, we associate to each patch $F_j$ a shape regular macro elements $\omega_j$, which is built adding to $F_j$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$. We make the following technical assumption: $\Gamma \subset \bigcup _{j} \omega_j$. Thanks to the shape regularity of these macro elements,  we have that the discrete trace and Poincarè inequalites hold. More precisely, for every function $v\in H^1(\omega_j)$,
\begin{equation}\label{discr_trace_ineq}
\|Tv\|_{\Gamma\cap \omega_j} \lesssim H^{-\frac 12} \|v\|_{L^2(\omega_j)}
\end{equation}
\begin{equation}\label{disc_poincare_ineq}
\|v- \pi_Lv\|_{L^2(\omega_j)} \leq c_P H \|\nabla v\|_{L^2(\omega_j)},
\end{equation}
where $\pi_L$ is defined as the projection onto piecewise constant functions on $F_j\cap \Lambda$.
 Moreover $\forall u_h \in X_h^\Omega$ we have the following average inequality 
\begin{equation*}
\sum _j \|\avrc{T u_h}\|^2_{L^2(F_j \cap \Lambda),|\DD| } \leq \sum _j \|T u_h\|^2_{L^2(\omega_j\cap \Gamma)}.
\end{equation*}
{\color{red} I think this inequality is valid but only globally. Indeed locally it is not guaranteed that the portion of $\Gamma$ corresponding to $F_j \cap \Lambda$ is contained in $\omega _j \cap \Gamma$}. \\
These choices lead to the following stabilization 
\begin{equation*}
s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{T}_{h'}^{\Lambda}} \int_{\partial K} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
\end{equation*}
being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{T}_{h'}^{\Lambda}$.
\begin{lemma}
The space $L_h$ inf-sup stable, namely $\forall {\lld}_h \in L_h(\Lambda)$, $\exists \beta >0$ s.t.
\begin{equation*}
\sup_{\substack{v_h \in X_{h,1}^0(\Omega),\\ {\vd}_h \in X_{h',1}^0(\Lambda)}} \frac{\left(\avrc{T v_h} - {\vd}_h, {\lld} _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|{\lld}_h\|_{H^{-\frac 12}(\Lambda)}.
\end{equation*} 
and the constant is independent of the cuts. 
\end{lemma}
\begin{proof}
% We have to prove that $\exists \beta >0$ such that $\forall l_h \in L_h$,
%\begin{equation*}
%\sup_{\substack{v_h \in X_{h,1}^0(\Omega),\\ {\vd}_h \in X_{h',1}^0(\Lambda)}} \frac{\left(\avrc{T v_h} - {\vd}_h, l _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|l_h\|_{H^{-\frac 12}(\Lambda)}.
%\end{equation*}
As in the continuous case, we can choose ${\vd}_h=0$ and we prove that
\begin{equation*} 
\sup_{v_h \in X_{h,1}^0(\Omega)} \frac{\left(\avrc{T v_h} ,{\lld}_h\right)_{\Lambda, |\DD|}}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|{\lld}_h\|_{H^{-\frac 12}(\Lambda)}.
\end{equation*} 
Proving the last inequality it is equivalent to find the Fortin operator $\pi_F: H^1_0(\Omega) \rightarrow X_{h,1}^0(\Omega)$, such that 
\begin{equation*}
\left(\avrc{T v} - \avrc{T \pi _F v}  , {\lld}_h\right)_{\Lambda, |\DD|}=0, \quad \forall v\in H^1_0(\Omega), \, {\lld}_h \in L_h(\Lambda)
\end{equation*} 
and
\begin{equation*}
\|\pi_F v\|_{H^1(\Omega)}\lesssim \|v\|_{H^1(\Omega)}.
\end{equation*}

We define
\begin{equation*}
\pi_F v = I_h v + \sum _j \alpha _j \varphi _j \qquad \text{with }\alpha_j =\frac{\int_{F_j \cap \Lambda}|\DD| (\avrc{Tv}-\avrc{TI_hv})}{\int_{F_j \cap \Lambda}|\DD|\avrc{T\varphi _j}}
\end{equation*}
and $\varphi_j \in X_{h,1}^0(\Omega)$ s.t. supp$(\varphi_j)\subset \bar{\omega}_j$, $\varphi_j =0$ on $\partial \omega _j$ and 
\begin{equation*}
 \int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}=O(H) \text{ and } \|\nabla \varphi\|_{L^2(\omega _j)}=O(1). 
\end{equation*}
This construction is always possible provided $H$ is sufficiently larger that $h$.
Then we have
\begin{multline*}
\left(\avrc{T v} - \avrc{T \pi _F v}  , {\lld}_h\right)_{\Lambda, |\DD|} 
= \sum _j \int_{F_j\cap \Lambda} |\DD |\left[ \avrc{Tv}-\avrc{TI_hv}-\sum _i \alpha_i \avrc{T\varphi _i} \right]{\lld}_h \\
=(\text{supp} \varphi \subset \omega_j) \sum _j \int_{F_j\cap \Lambda}|\DD| \left[ \avrc{Tv}-\avrc{TI_hv}-\alpha_j \avrc{T\varphi _j} \right]{\lld}_h\\
=\sum _j \int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{T I_h v}) {\lld}_h - \frac{\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})}{\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}} \int_{F_j\cap \Lambda} |\DD|\avrc{T\varphi _j}{\lld}_h\\ 
=(\text{using $l_h$ constant on $F_j\cap \Lambda$})\,0.
\end{multline*}
Concerning the continuity of $\pi_F$, we have
\begin{multline*}
\|\nabla \pi_F v \|_{L^2(\Omega)} \leq \|\nabla I_h v\|_{L^2(\Omega)} + \left(\sum_j|\alpha_j|^2\|\nabla \varphi _j\|^2_{L^2(\bar{\omega}_j)}\right)^{\frac 12}\\
(\text{stability of }I_h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \left(\sum_j|\alpha_j|^2\|\nabla \varphi _j\|^2_{L^2(\bar{\omega}_j)}\right)^{\frac 12}
\end{multline*}
and for the second term we have
\begin{multline*}
\sum_j|\alpha_j|^2\|\nabla \varphi _j\|^2_{L^2(\bar{\omega}_j)}\leq
\\
\left(\text{using }\|\nabla \varphi _j\|=O(1)\right) \lesssim  \sum_j \frac{\left(\left|\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})\right|\right)^2}{\left(\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}\right)^2}
\\
\left(\text{since }\left|\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}\right|=O(H)\right) \lesssim \frac {1}{H^2} \sum_j \left(\left|\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})\right| \right)^2
\\
(\text{Jensen}) \lesssim  \frac {1}{H^2} \sum_j |F_j\cap \Lambda| \int_{F_j\cap \Lambda} |\DD|^2(\avrc{Tv}-\avrc{TI_hv})^2
\\
(\text{being }|F_j\cap \Lambda| \leq H+h)\lesssim  \frac {1}{H} \sum_j \| \avrc{Tv}-\avrc{TI_hv}\|^2_{L^2(F_j\cap \Lambda), |\DD|}
\\
(\text{average inequality}) \lesssim  \frac {1}{H} \sum_j \| T(v-I_hv)\|^2_{L^2(\omega _j\cap \Gamma)}  
\\
\left(\text{trace inequality} \right)\lesssim  \frac {1}{H^2} \sum_j  \| v-I_h v\|^2_{L^2(\omega_j)} \lesssim  \frac {1}{H^2}  \| v-I_h v\|^2_{L^2(\Omega)} 
\\
(\text{approximation properties of }I_h)\lesssim \|\nabla  v\|^2_{L^2(\Omega)}
\end{multline*}
and the continuity of $\pi_F$ follows.
\end{proof}

%\subparagraph{Satisfaction of the assumptions of the 
%abstract analysis}
We choose the following discrete norm
\begin{equation*}
\vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_{h'}(\Lambda) }
= \|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|} + \|\avrc{Tu_h} - {\ud}_h\|^2_{-\frac 12, h, \Lambda, |\DD|},
\end{equation*}
where $\|\avrc{Tu_h} - {\ud}_h\|^2_{-\frac 12, h, \Lambda, |\DD|} = \|h^{\frac 12} (\avrc{Tu_h} - {\ud}_h)\|^2_{L^2(\Lambda), |\DD|} $. Then, we have the following lemma. 
\begin{lemma}
The inequalities \eqref{stab_coercivity} and \eqref{stab_stability} hold.
\end{lemma}
\begin{proof} 
Concerning the coercivity property \eqref{stab_coercivity}, we have to show that $\forall [u_h, {\ud}_h]$, there esists $\xi_h \in Q_h(\Lambda)$ s.t.
\begin{multline*}
(u_h,u_h)_{H^1(\Omega)}+ ({\ud}_h, {\ud}_h)_{H^1(\Lambda), |\D|} +   (\avrc{Tu_h} - {\ud}_h, \xi_h)_{\Lambda,|\DD|} \\
\geq \alpha_{\xi}(\|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|}+ \|\avrc{Tu_h} - {\ud}_h\|^2_{-\frac 12, h, \Lambda, |\DD|}.
\end{multline*}
We choose 
\begin{equation*}
{\xi_h}_{|F_j\cap \Lambda}=\delta \frac 1H \pi_L(\avrc{Tu_h}-{\ud}_h) \qquad \text{with } \pi_L(\avrc{Tu_h}-{\ud}_h) =\frac{1}{|\Gamma_{F_j\cap \Lambda}|}\int_{F_j\cap \Lambda}|\DD| (\avrc{Tu_h}- {\ud}_h),
\end{equation*}
being $\Gamma_{F_j\cap \Lambda}$ the portion of $\Gamma$ with centerline $F_j\cap \Lambda$. 
Actually, $\xi_h\in L_h(\Lambda) \subset Q_h(\Lambda)$. Then,
\begin{multline*}
\left( \avrc{Tu_h} - {\ud}_h, \xi _h \right)_{\Lambda,|\DD|} 
= \sum_j \int_{F_j\cap \Lambda} |\DD|( \avrc{Tu_h} - {\ud}_h)\xi_h
\\
= \delta \frac{1}{H} \sum_j \int_{F_j\cap \Lambda}|\DD| (\pi_L( \avrc{Tu_h} - {\ud}_h) )^2
\\
(\text{orthogonality of $\pi_L$}) =  \delta \frac{1}{H} \|(\pi_L-\mathcal{I})(\avrc{Tu_h} - {\ud}_h)\|^2_{L^2(F_j\cap \Lambda),|\DD|} + \delta \frac{1}{H} \|\avrc{Tu_h} - {\ud}_h\|^2_{L^2(F_j\cap \Lambda),|\DD|}
\\ 
\geq -\delta \frac 1H \sum_j \|(\pi_L - \mathcal{I})\avrc{Tu_h}\|^2_{L^2(F_j\cap \Lambda), |\DD|}
- \delta \frac 1H \sum_j \|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(F_j\cap \Lambda),|\DD|}
\\ 
+ \delta \frac 1H \sum_j \|\avrc{Tu_h}-{\ud}_h\|^2_{L^2(F_j\cap \Lambda),|\DD|}. 
\end{multline*}
For the first term we have
\begin{multline*}
\sum _j  \|(\pi_L - \mathcal{I})\avrc{Tu_h}\|^2_{L^2(F_j\cap \Lambda),|\DD|} =\sum _j \int _{F_j \cap \Lambda} |\DD| (\pi_L \avrc{Tu_h}- \avrc{Tu_h})^2
\\
(\text{Average inequality)} \leq \sum _j  \int_{\omega _j \cap \Gamma} (\pi_L \avrc{Tu_h} -Tu_h)^2 
\\
(\text{trace inequality}) \leq \sum _j  \frac 1H \int_{\omega_j}(\pi_L \avrc{Tu_h} - u_h)^2 
\\ 
(\text{Poincare, see \cite[Corollary B.65]{MR2050138}})\leq \sum _j  H c_P ^2 \|\nabla u_h\|^2_{L^2(\omega _j)}.
\end{multline*}
For the second term we have
\begin{multline*}
\sum _j \|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(F_j\cap \Lambda),|\DD|} = \sum _j \int_{F_j\cap \Lambda} |\DD| (\pi_L {\ud}_h -{\ud}_h)^2
\\
(\text{Poincare, \cite[Corollary B.65]{MR2050138}})\lesssim \sum _j  H^2 c_P^2 \int_{F_j\cap \Lambda} |\DD|(\nabla {\ud}_h)^2
\\
(\text{since $H$ is fixed, we can find a constant s.t. } H|\DD| \lesssim |\D|) \lesssim \sum _j H c_P^2  \int_{F_j\cap \Lambda} |\D|(\nabla {\ud}_h)^2 
\\
\lesssim \sum _j H c_P^2  \|\nabla {\ud}_h\|^2_{L^2(F_j\cap \Lambda),|\D|}.
\end{multline*}
{\color{red} N.B. we are using a kind of weigthed Poincare inequality, check... I think it should work because I can do something like this
\begin{multline*}
\int_{F_j \cap \Lambda} |\DD| u^2 \leq 
max |\DD| \int_{F_j \cap \Lambda} u^2 \leq
max |\DD| \int_{F_j \cap \Lambda} (\nabla u)^2 =
\frac{max |\DD|}{min|\DD|} min|\DD| \int_{F_j \cap \Lambda} u^2 \leq\\
\frac{max |\DD|}{min|\DD|}  \int_{F_j \cap \Lambda} |\DD| u^2 
\end{multline*}
}\\
Therefore, we obtain
\begin{multline*}
a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h([u_h, {\ud}_h]))
\geq \\
(1-\delta c_P^2) \|\nabla u_h\|^2_{L^2(\Omega)} + (1- \delta c_P^2) \|\nabla {\ud}_h\|^2_{L^2(\Lambda), |\D|}
+\delta c_H  \|\avrc{Tu_h}-{\ud}_h\|^2_{-\frac 12,h,\Lambda, |\DD|}
\end{multline*}
and choosing $\delta=\frac{1}{2c_P^2}$ we obtain the coercivity inequality.\\
Concerning the stability inequality \eqref{stab_stability}, the proof is analogous to the one in \cite{burman2014}.
\end{proof}

### 2019-07-05 infsup_discrete_conformingLM.tex
update

@@
 
-{\color{red} Define Bh, etc}
+{\color{red} Define Bh, etc}\\
+The well posedness of such problem is governed by the classical inf-sup theory in Banach spaces. The main result is reported below.
 
-\begin{theorem}[Ern-Guermond 2.42]
+\begin{corollary}{\cite[Theorem 2.42]{MR2050138}}
 Problem \eqref{eq:saddle-point_discrete} is well-posed if and only if 
@@
 \end{equation}
-\end{theorem}
+\end{corollary}
+This corollary is the discrete counterpart of Theorem \ref{th:bnb} where at the discrete level condition \eqref{BNB1_discrete} implies both of \eqref{BNB1}.
+Conversely, \eqref{eq:infsup_discrete} does not follow from the conformity of the finte element spaces and it must be analysed independetly of \eqref{eq:infsup}.
 Let us notice that for both problem 1 and problem 2 the bilinear form $a(\cdot, \cdot)$ is coercive as stated in Lemmas \eqref{lemma:prob1_coercivity} and \eqref{lemma:prob2_coercivity}.
@@
 Let us introduce a shape-regular triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{h}$ of $\Lambda$. 
-We analyze two different cases: the one in which the 3D mesh is conforming to the interface $\Gamma$, namely the set of the intersections of the 3D elements of $\mathcal{T}^{\Omega}_h$ with $\Gamma$ is constituted by facets of such elements, and the non conforming case, namely the 3D elements of $\mathcal{T}^{\Omega}_h$ 'cut' the interface $\Gamma$.
+We analyze two different cases: the one in which the 3D mesh is conforming to the interface $\Gamma$, namely the set of the intersections of the 3D elements of $\mathcal{T}^{\Omega}_h$ with $\Gamma$ is constituted by facets of such elements, and the non conforming case, namely the interface $\Gamma$ cuts the mesh arbitrarly.
 
@@
 \subsubsection{Problem 1}
-We denote by $X_{h,k}^0(\Omega)\subset H^1_0(\Omega)$ the conforming finite element space of continuous piecewise polynomials of degree $k$ defined on $\Omega$ satisfying homogeneous Dirichlet conditions on the boundary and by $X_{h,k}^0(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$, satisfying homogeneous Dirichlet conditions on $\Lambda \cap \partial \Omega$.
+We denote by $X_{h,0}^k(\Omega)\subset H^1_0(\Omega)$, with $k>0$, the conforming finite element space of continuous piecewise polynomials of degree $k$ defined on $\Omega$ satisfying homogeneous Dirichlet conditions on the boundary and by $X_{h,0}^k(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$, satisfying homogeneous Dirichlet conditions on $\Lambda \cap \partial \Omega$.
 %Moreover, $Q_{h}$ denotes a suitable trial space for the lagrange multiplier $\lambda_h$.
 In particular, $Q_h \subset H^{-\frac12}(\Gamma )$ in the case of Problem 1 and $Q_h \subset H^{-\frac12}(\Lambda)$ in the case of Problem 2.
-Problem 1 consists to find $u_h \in X_{h,k}^0 (\Omega) ,\ {\ud}_h \in X_{h,k}^0(\Lambda) , \lambda_h \in Q_h(\Gamma) \subset H^{-\frac12}(\Gamma )$, such that
+Problem 1 consists to find $u_h \in X_{h,0}^k (\Omega) ,\, {\ud}_h \in X_{h,0}^k(\Lambda) ,\, \lambda_h \in Q_h \subset H^{-\frac12}(\Gamma )$, such that
 \begin{subequations}
@@
 &\qquad\qquad= (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda),|\D|}
-\quad \forall v_h \in X_{h,k}^0(\Omega), \ {\vd}_h \in X_{h,k}^0(\Lambda)
+\quad \forall v_h \in X_{h,0}^k(\Omega), \ {\vd}_h \in X_{h,0}^k(\Lambda)
 \\
 &   \langle T u_h - \mathcal{U} {\ud}_h , \mu_h \rangle_\Gamma = 0
-\quad \forall \mu_h \in Q_h(\Gamma)\,,
+\quad \forall \mu_h \in Q_h\,,
 \end{align}
 \end{subequations}
-The space $Q_h(\Gamma)$ must be suitably chosen such that \eqref{eq:infsup_discrete} holds.
-Let us denote with $W_{h,k}^0(\Gamma) \subset H^{\frac 12}_{00}(\Gamma)$ the trace space of functions running in $X_{h,k}^0(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$.
-We choose $Q_h(\Gamma)=W_{h,k}^0(\Gamma)$, therefore we impose homogeneous Dirichlet boundary condition on $\partial \Omega$ also for the Lagrange multiplier.
-For this choice of $Q_h(\Gamma)$ we can prove the well-posedness of the discrete problem, as shown in the following.
+The space $Q_h$ must be suitably chosen such that \eqref{eq:infsup_discrete} holds.
+{\color{red}For this purpose we define conformity conditios between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$ with $\Gamma$.
+MOre precisely we require that the intersection of $\mathcal{T}^{\Omega}_h$ and $\Gamma$ is amde of entire faces of elemets $K \in \mathcal{T}^{\Omega}_h$.
+Furthermore we also set a restriction between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$.
+We want that the intersection of $\Gamma$ with any orthogonal plane to $\Lambda$ that crosses $\Lambda$ at the nodes of $\mathcal{T}^{\Lambda}_h$, consists of entire edges of $\mathcal{T}^{\Omega}_h$.
+Namely the intersection of $\Gamma$ with orthogonal planes to $\Lambda$ is conformal with $\mathcal{T}^{\Lambda}_h$.} Let us denote with $W_{h,0}^k(\Gamma) \subset H^{\frac 12}_{00}(\Gamma)$ the trace space of functions running in $X_{h,0}^k(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$.
+We choose $Q_h=W_{h,0}^k(\Gamma)$, therefore we impose homogeneous Dirichlet boundary condition on $\partial \Omega$ also for the Lagrange multiplier.
+For this choice of $Q_h$ we can prove the well-posedness of the discrete problem, as shown in the following.
 
 \begin{lemma}
-Let $P_h: H^{\frac 12}_{00}(\Gamma) \longrightarrow W_{h,k}^0(\Gamma)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Gamma)$ by
+Let $P_h: H^{\frac 12}_{00}(\Gamma) \longrightarrow W_{h,0}^k(\Gamma)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Gamma)$ by
 \begin{equation*}
-(P_h v , \psi)_\Gamma= (v, \psi)_\Gamma \qquad \forall \psi \in W_{h,k}^0(\Gamma).  
+(P_h v , \psi_h)_\Gamma= (v, \psi_h)_\Gamma \qquad \forall \psi_h \in W_{h,0}^k(\Gamma).  
 \end{equation*} 
@@
 \begin{equation*}
-\|v\|^2_{L^2(\Gamma)} = \|v-P_h v\|_{L^2(\Gamma)}^2 + \|P_h v\|_{L^2(\Gamma)}^2 \geq \|P_h v\| _{L^2(\Gamma)}.
+\|v\|^2_{L^2(\Gamma)} = \|v-P_h v\|_{L^2(\Gamma)}^2 + \|P_h v\|_{L^2(\Gamma)}^2 \geq \|P_h v\|^2 _{L^2(\Gamma)}.
 \end{equation*}
-Let us now consider $v\in H^1_0(\Gamma)$.The Scott-Zhang interpolation operator $SZ_h$ from $H^1_0(\Gamma)$ to $W_{h,k}^0(\Gamma)$ satisfies the following inequalities,
+Let us now consider $v\in H^1_0(\Gamma)$.The Scott-Zhang interpolation operator $SZ_h$ from $H^1_0(\Gamma)$ to $W_{h,0}^k(\Gamma)$ satisfies the following inequalities,
 \begin{equation}\label{SZ_stability}
@@
 \end{equation}
-Therefore,
+Therefore, using \eqref{SZ_stability},
 \begin{equation*}
@@
 &\leq \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + \|\nabla SZ_h v\|_{L^2(\Gamma)}\\
-&\leq \text{ (using \eqref{SZ_stability}) } \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
+&\leq  \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
 \end{split}
@@
 \begin{lemma}\label{lemma:trspace_infsup} 
-There exist a constant $\gamma >0$ such that
+There exists a constant $\gamma >0$ such that for any $\mu_h\in Q_h$
 \begin{equation*}
-\sup_{\substack{q_h \in W_{h,k}^0(\Gamma)}} \frac{\langle q_h , \mu_h \rangle}{ \|q_h\|_{H^{\frac 12}(\Gamma)}} \geq \gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)}.
+\sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , \mu_h \rangle}{ \|q_h\|_{H^{\frac 12}(\Gamma)}} \geq \gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)}.
 \end{equation*} 
@@
 \begin{proof}
-Let $\mu_h$ be in $Q_h(\Gamma)$. From the continuous case, in particular from \eqref{infsup_traceop}, we have
+Let $\mu_h$ be in $Q_h$. From the continuous case, in particular from \eqref{infsup_traceop}, we have
 \begin{equation*}
@@
 &\leq  C_T C \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(T v) , \mu_h \rangle}{ \|P_h(Tv)\|_{H^{\frac 12}(\Gamma)}}\\
-&= C_T C \sup_{\substack{q_h \in W_{h,k}^0(\Gamma)}} \frac{\langle q_h , \mu_h \rangle}{  \|q_h\|_{H^{\frac 12}(\Gamma)}}.
+&= C_T C \sup_{\substack{q_h \in W_{h,0}^k(\Gamma)}} \frac{\langle q_h , \mu_h \rangle}{  \|q_h\|_{H^{\frac 12}(\Gamma)}}.
 \end{split}
@@
 \begin{equation}\label{inf_sup_discrete_prob1}
-\inf_{\mu_h \in Q_h(\Gamma)} 
-\sup_{\substack{v_h \in X^0_{h,k}(\Omega),\\ {\vd}_h \in X^0_{h,k}(\Lambda)}} \frac{ \langle T v_h - \mathcal{U}_E {\vd}_h, \mu_h \rangle _{\Gamma}} {\vertiii{[v_h, {\vd} _h]} \|\mu_h\|_{H^{-\frac 12 }(\Gamma)}}
+\inf_{\mu_h \in Q_h} 
+\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)}} \frac{ \langle T v_h - \mathcal{U}_E {\vd}_h, \mu_h \rangle _{\Gamma}} {\vertiii{[v_h, {\vd} _h]} \|\mu_h\|_{H^{-\frac 12 }(\Gamma)}}
 \geq \beta_{h,1}. 
@@
 \begin{proof}
-Let $\mu_h \in Q_h(\Gamma)$. As in the continuos case, we choose ${\vd}_h =0$ and we have
+Let $\mu_h \in Q_h$. As in the continuos case, we choose ${\vd}_h =0$ and we have
 \begin{equation*}
-\sup_{\substack{v_h \in X^0_{h,k}(\Omega),\\ {\vd}_h \in X^0_{h,k}(\Lambda)}} \frac{ \langle T v_h - \mathcal{U}_E {\vd}_h, \mu_h \rangle _{\Gamma}} {\vertiii{[v_h,  {\vd}_h]}}
-\geq \sup_{v_h \in X^0_{h,k}(\Omega)} \frac{ \langle T v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}}.
+\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)}} \frac{ \langle T v_h - \mathcal{U}_E {\vd}_h, \mu_h \rangle _{\Gamma}} {\vertiii{[v_h,  {\vd}_h]}}
+\geq \sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle T v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}}.
 \end{equation*}
@@
 \begin{equation*}
-\sup_{v_h \in X^0_{h,k}(\Omega)} \frac{ \langle T v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}} \geq \beta_{h,1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \qquad \forall \mu_h \in Q_h(\Gamma).
+\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle T v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}} \geq \beta_{h,1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \qquad \forall \mu_h \in Q_h.
 \end{equation*}
 
-Using Lemma \ref{lemma:trspace_infsup} and the boundedness of the armonic extension operator $\mathcal{E}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
+Using Lemma \ref{lemma:trspace_infsup} and the boundedness of the armonic extension operator $\mathcal{E}$ from $H^{\frac 12}_{00}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
 \begin{equation*}
-\gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq  \sup_{q_h \in Q_h(\Gamma)} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|q_h\|_{H^{\frac 12}(\Gamma)}} 
+\gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq  \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|q_h\|_{H^{\frac 12}(\Gamma)}} 
 \leq 
-\|\mathcal{E}\| \sup_{q_h \in Q_h(\Gamma)} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{E}q_h\|_{H^1(\Omega)}} .
+\|\mathcal{E}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{E}q_h\|_{H^1(\Omega)}} .
 \end{equation*}
-Let $R_h: H^1_0(\Omega) \rightarrow X_{h,k}^0(\Omega)$ be a quasi interpolation operator satisfying 
+Let $R_h: H^1_0(\Omega) \rightarrow X_{h,0}^k(\Omega)$ be a quasi interpolation operator satisfying 
 \begin{equation*}
@@
 \begin{equation*}
-\|\mathcal{E}\| \sup_{q_h \in Q_h(\Gamma)} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{E}q_h\|_{H^1(\Omega)}} 
+\|\mathcal{E}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{E}q_h\|_{H^1(\Omega)}} 
 \leq
-\|\mathcal{E}\| C_R \sup_{q_h \in Q_h(\Gamma)} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|R_h \mathcal{E} q_h\|_{H^1(\Omega)}}
+\|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|R_h \mathcal{E} q_h\|_{H^1(\Omega)}}
 \end{equation*}
@@
 \leq 
-\sup_{q_h \in Q_h(\Gamma)} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|q_h\|_{H^{\frac 12}(\Gamma)}} 
+\sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|q_h\|_{H^{\frac 12}(\Gamma)}} 
 \leq
-\|\mathcal{E}\| C_R \sup_{q_h \in Q_h(\Gamma)} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{E} q_h\|_{H^1(\Gamma)}}
+\|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{E} q_h\|_{H^1(\Gamma)}}
 \\
 =
-\|\mathcal{E}\| C_R \sup_{q_h \in Q_h(\Gamma)} \frac{ \langle T \ R_h E q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{E} q_h\|_{H^1(\Omega)}} 
+\|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle T \ R_h E q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{E} q_h\|_{H^1(\Omega)}} 
 \leq \|\mathcal{E}\| C_R \sup_{v_h \in X_{h,k}(\Omega)} \frac{ \langle T v_h, \mu_h \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
@@
 {\color{red}
-\begin{remark} We notice that to prove the result in Lemma \ref{lemma:trspace_infsup} (and then the discrete inf-sup condition)  basically we need a projection operator $P_h: H^{\frac 12}_{00} \longrightarrow W_{h,k}^0(\Gamma)$ orthogonal in the multiplier space $Q_h(\Gamma)$, namely such that $\langle P_h v, \mu_h \rangle = \langle v, \mu_h \rangle, \, \forall \mu_h \in Q_h(\Gamma)$, and continuous in $H^{\frac 12}(\Gamma)$.
-Therefore, in principle different choices than $Q_h(\Lambda)=W_{h,k}^0(\Gamma)$ could be considered if we can build an operator $P_h$ satisfying these properties.
-In \cite{belgacem1999mortar} such operator $P_h$  is built for a particular choice of $Q_h(\Gamma)$ but it is not clear how they prove the $H^1$-stability inequality (and consequently the $H^{\frac 12 }$-stability) with a constant independent of the mesh size $h$...
+\begin{remark} We notice that to prove the result in Lemma \ref{lemma:trspace_infsup} (and then the discrete inf-sup condition)  basically we need a projection operator $P_h: H^{\frac 12}_{00} \longrightarrow W_{h,0}^k(\Gamma)$ orthogonal in the multiplier space $Q_h$, namely such that $\langle P_h v, \mu_h \rangle = \langle v, \mu_h \rangle, \, \forall \mu_h \in Q_h$, and continuous in $H^{\frac 12}(\Gamma)$.
+Therefore, in principle different choices than $Q_h=W_{h,0}^k(\Gamma)$ could be considered if we can build an operator $P_h$ satisfying these properties.
+In \cite{belgacem1999mortar} such operator $P_h$  is built for a particular choice of $Q_h$ but it is not clear how they prove the $H^1$-stability inequality (and consequently the $H^{\frac 12 }$-stability) with a constant independent of the mesh size $h$...
 \end{remark}  
@@
 \subsubsection{Problem 2}
-This problem requires to find  $u_h \in X^0_{h,k}(\Omega) ,\ {\ud}_h \in X^0_{h,k}(\Lambda), \ {\ld}_h \in Q_h(\Lambda) \subset H^{-\frac12}(\Lambda)$, such that
+This problem requires to find  $u_h \in X_{h,0}^k(\Omega) ,\ {\ud}_h \in X_{h,0}^k(\Lambda), \ {\ld}_h \in Q_h \subset H^{-\frac12}(\Lambda)$, such that
 \begin{subequations}
@@
 &  \langle \avrc{T u_h} - {\ud}_h, {\md}_h \rangle_{\Lambda,| \DD| } = 0
-\quad \forall {\md}_h \in Q_h(\Lambda)\,.
+\quad \forall {\md}_h \in Q_h\,.
 \end{align}
@@
 We introduce the space
-$W_{h,k}^0(\Lambda) \subset H^{\frac 12} _{00} (\Lambda)$, which is the averaged trace space of functions running in $H^1_0(\Omega)$.
+$W_{h,0}^k(\Lambda) \subset H^{\frac 12} _{00} (\Lambda)$, which is the averaged trace space of functions running in $H^1_0(\Omega)$.
 It coincides with the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$ and satisfying homogeneous Dirichlet boundary condition.
 {\color{red} (Add assumptions..)}
-We choose $Q_h(\Lambda)=W_{h,k}^0(\Lambda)$, therefore we impose homogeneous Dirichlet boundary condition on $\Lambda \cap \partial \Omega$ also for the Lagrange multiplier.
-With this choice for $Q_h(\Lambda)$, we can prove the well-posedness of the discrete problem.
+We choose $Q_h=W_{h,0}^k(\Lambda)$, therefore we impose homogeneous Dirichlet boundary condition on $\Lambda \cap \partial \Omega$ also for the Lagrange multiplier.
+With this choice for $Q_h$, we can prove the well-posedness of the discrete problem.
 In particular, following the same steps as for Problem 1, we can prove the following results.
 \begin{lemma}
-Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow W_{h,k}^0(\Lambda)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
+Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow W_{h,0}^k(\Lambda)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
 \begin{equation*}
-(P_h v , \psi)_\Lambda= (v, \psi)_\Lambda \qquad \forall \psi \in W_{h,k}^0(\Lambda).  
+(P_h v , \psi)_\Lambda= (v, \psi)_\Lambda \qquad \forall \psi \in W_{h,0}^k(\Lambda).  
 \end{equation*} 
@@
 \begin{equation*}
-\sup_{\substack{q_h \in W_{h,k}^0(\Lambda)}} \frac{\langle q_h , \mu_h \rangle}{ \|q_h\|_{H^{\frac 12}(\Lambda)}} \geq \gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall \mu_h \in W_{h,k}^0(\Lambda).
+\sup_{\substack{q_h \in W_{h,0}^k(\Lambda)}} \frac{\langle q_h , \mu_h \rangle}{ \|q_h\|_{H^{\frac 12}(\Lambda)}} \geq \gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall \mu_h \in W_{h,0}^k(\Lambda).
 \end{equation*} 
@@
 \begin{equation}
-\inf_{\mu_h \in Q_h(\Lambda)} 
-\sup_{\substack{v_h \in X^0_{h,k}(\Omega),\\ {\vd}_h \in X^0_{h,k}(\Lambda)} }\frac{\langle \avrc{Tv_h} -  {\vd}_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\vertiii{[v_h, {\vd}_h]} \|{\md}_h\|_{H^{-\frac 12 }(\Lambda)} }
+\inf_{\mu_h \in Q_h} 
+\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)} }\frac{\langle \avrc{Tv_h} -  {\vd}_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\vertiii{[v_h, {\vd}_h]} \|{\md}_h\|_{H^{-\frac 12 }(\Lambda)} }
 \geq \beta_{h,2}. 
@@
 \begin{proof}
-Let ${\md}_h$ be arbitrarly chosen in $Q_h(\Lambda)$. Again, we choose ${\vd}_h =0$, so that the proof reduces to show that there exists $\beta_{h,2}$ such that
+Let ${\md}_h$ be arbitrarly chosen in $Q_h$. Again, we choose ${\vd}_h =0$, so that the proof reduces to show that there exists $\beta_{h,2}$ such that
 \begin{equation*}
-\sup_{v_h \in X_{h,k}^0(\Omega)} \frac{ \langle \avrc{T v_h} , {\md}_h \rangle _{\Lambda,|\DD|} } {\|v_h\|_{H^1(\Omega)} }\geq \beta_{h,2} \|{\md}_h\|_{H^{-\frac 12}(\Lambda)}\ \qquad \forall {\md}_h \in Q_h(\Lambda).
+\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \avrc{T v_h} , {\md}_h \rangle _{\Lambda,|\DD|} } {\|v_h\|_{H^1(\Omega)} }\geq \beta_{h,2} \|{\md}_h\|_{H^{-\frac 12}(\Lambda)}\ \qquad \forall {\md}_h \in Q_h.
 \end{equation*}
@@
 \end{equation*}
-Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $E$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X^0_{h,k}(\Omega)$, we obtain
+Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $E$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
 \begin{multline}
 \gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \leq 
-\sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
+\sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
 \\
-= |\DD| \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
-\leq |\DD|\|E\| \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda} } {\|E \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
+= |\DD| \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
+\leq |\DD|\|E\| \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda} } {\|E \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
 \\
-\leq |\DD|\|E\| C_R \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
+\leq |\DD|\|E\| C_R \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
 \\ 
-=  |\DD|\|E\| C_R \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E q_h, \mu_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
+=  |\DD|\|E\| C_R \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E q_h, \mu_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
 \\
@@
 %\end{equation*}
-%Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{E}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X^0_{h,k}(\Omega)$, we obtain
+%Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{E}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
 %\begin{multline}
 %\gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \leq 
-%\sup_{q_h \in Q_h(\Lambda)} \frac{ \langle q_h, {\md}_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
+%\sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
 %\\
-%\lesssim \sup_{q_h \in Q_h(\Lambda)} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
-%\lesssim \|\mathcal{E}\| \sup_{q_h \in Q_h(\Lambda)} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda} } {\|\mathcal{E} \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
+%\lesssim \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
+%\lesssim \|\mathcal{E}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda} } {\|\mathcal{E} \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
 %\\
-%\lesssim \|\mathcal{E}\| C_R \sup_{q_h \in Q_h(\Lambda)} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
+%\lesssim \|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
 %\\ 
-%\lesssim\|\mathcal{E}\| C_R \sup_{q_h \in Q_h(\Lambda)} \frac{ \langle \avrc{TR_h E \mathcal{U}_E q_h}, {\md}_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
+%\lesssim\|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle \avrc{TR_h E \mathcal{U}_E q_h}, {\md}_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
 %\\
@@
 \begin{lemma}
-Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow W_{h,k}^0(\Lambda)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
+Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow W_{h,0}^k(\Lambda)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
 \begin{equation*}
-(P_h v , \psi)_{\Lambda,|\DD|}= (v, \psi)_{\Lambda , |\DD|} \qquad \forall \psi \in W_{h,k}^0(\Lambda).  
+(P_h v , \psi)_{\Lambda,|\DD|}= (v, \psi)_{\Lambda , |\DD|} \qquad \forall \psi \in W_{h,0}^k(\Lambda).  
 \end{equation*} 
@@
 \begin{equation*}
-\sup_{\substack{q_h \in W_{h,k}^0(\Lambda)}} \frac{\langle q_h , {\md}_h \rangle_{\Lambda, |\DD|}}{ \|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} \geq \gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall {\md}_h \in W_{h,k}^0(\Lambda).
+\sup_{\substack{q_h \in W_{h,0}^k(\Lambda)}} \frac{\langle q_h , {\md}_h \rangle_{\Lambda, |\DD|}}{ \|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} \geq \gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall {\md}_h \in W_{h,0}^k(\Lambda).
 \end{equation*} 
@@
 }
-Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{E}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X^0_{h,k}(\Omega)$, we obtain
+Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{E}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
 \begin{multline}
 \gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \leq 
-\sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} 
+\sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} 
 \\
-=  \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
-\leq \|\mathcal{E}\| \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|\mathcal{E} \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
+=  \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
+\leq \|\mathcal{E}\| \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|\mathcal{E} \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
 \\
-\leq \|\mathcal{E}\| C_R \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
+\leq \|\mathcal{E}\| C_R \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
 \\ 
-=  \|\mathcal{E}\| C_R \sup_{q_h \in W_{h,k}^0(\Lambda)} \frac{ \langle 	\avrc{T  R_h E \mathcal{U}_E q_h}, \mu_h \rangle _{\Lambda,|\DD|}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
+=  \|\mathcal{E}\| C_R \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle 	\avrc{T  R_h E \mathcal{U}_E q_h}, \mu_h \rangle _{\Lambda,|\DD|}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
 \\

### 2019-07-08 infsup_discrete_conformingLM.tex
update

@@
 \end{eqnarray}
-
-{\color{red} Define Bh, etc}\\
+Let $B_h: Q'_h \longrightarrow Q_h$ be the operator induced by $b$ such that $\langle B_h v_h,\mu _h\rangle_{Q'_h,Q_h} = b(v_h,\mu _h)$.
 The well posedness of such problem is governed by the classical inf-sup theory in Banach spaces. The main result is reported below.
@@
 \subsection{$\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}
-
+ We first analyze the case in which the 3D mesh is conforming to the interface $\Gamma$.
+With this aim, we define conformity conditions between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$ with $\Gamma$.
+More precisely we require that the intersection of $\mathcal{T}^{\Omega}_h$ and $\Gamma$ is made of entire faces of elemets $K \in \mathcal{T}^{\Omega}_h$.
+Furthermore we also set a restriction between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$.
+We want that the intersection of $\Gamma$ with any orthogonal plane to $\Lambda$ that crosses $\Lambda$ at the nodes of $\mathcal{T}^{\Lambda}_h$, consists of entire edges of $\mathcal{T}^{\Omega}_h$.
+Namely the intersection of $\Gamma$ with orthogonal planes to $\Lambda$ is conformal with $\mathcal{T}^{\Lambda}_h$.
 \subsubsection{Problem 1}
@@
 &(u_h,v_h)_{H^1(\Omega)} + ({\ud}_h,{\vd}_h)_{H^1(\Lambda),|\D|} 
-+ \langle T v_h  - \mathcal{U}_E {\vd}_h, \lambda_h \rangle_\Gamma 
++ \langle \trace v_h  - \mathcal{E}_{\Lambda} {\vd}_h, \lambda_h \rangle_\Gamma 
 \\
@@
 \\
-&   \langle T u_h - \mathcal{U} {\ud}_h , \mu_h \rangle_\Gamma = 0
+&   \langle \trace u_h - \mathcal{E}_{\Lambda} {\ud}_h , \mu_h \rangle_\Gamma = 0
 \quad \forall \mu_h \in Q_h\,,
@@
 The space $Q_h$ must be suitably chosen such that \eqref{eq:infsup_discrete} holds.
-{\color{red}For this purpose we define conformity conditios between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$ with $\Gamma$.
-MOre precisely we require that the intersection of $\mathcal{T}^{\Omega}_h$ and $\Gamma$ is amde of entire faces of elemets $K \in \mathcal{T}^{\Omega}_h$.
-Furthermore we also set a restriction between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$.
-We want that the intersection of $\Gamma$ with any orthogonal plane to $\Lambda$ that crosses $\Lambda$ at the nodes of $\mathcal{T}^{\Lambda}_h$, consists of entire edges of $\mathcal{T}^{\Omega}_h$.
-Namely the intersection of $\Gamma$ with orthogonal planes to $\Lambda$ is conformal with $\mathcal{T}^{\Lambda}_h$.} Let us denote with $W_{h,0}^k(\Gamma) \subset H^{\frac 12}_{00}(\Gamma)$ the trace space of functions running in $X_{h,0}^k(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$.
+Let us denote with $W_{h,0}^k(\Gamma) \subset H^{\frac 12}_{00}(\Gamma)$ the trace space of functions running in $X_{h,0}^k(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$.
 We choose $Q_h=W_{h,0}^k(\Gamma)$, therefore we impose homogeneous Dirichlet boundary condition on $\partial \Omega$ also for the Lagrange multiplier.
@@
 \begin{lemma}
-Let $P_h: H^{\frac 12}_{00}(\Gamma) \longrightarrow W_{h,0}^k(\Gamma)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Gamma)$ by
+Let $P_h: H^{\frac 12}_{00}(\Gamma) \longrightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Gamma)$ by
 \begin{equation*}
-(P_h v , \psi_h)_\Gamma= (v, \psi_h)_\Gamma \qquad \forall \psi_h \in W_{h,0}^k(\Gamma).  
+(P_h v , \psi_h)_\Gamma= (v, \psi_h)_\Gamma \qquad \forall \psi_h \in Q_h.  
 \end{equation*} 
@@
 \end{equation*}
-Let us now consider $v\in H^1_0(\Gamma)$.The Scott-Zhang interpolation operator $SZ_h$ from $H^1_0(\Gamma)$ to $W_{h,0}^k(\Gamma)$ satisfies the following inequalities,
+Let us now consider $v\in H^1_0(\Gamma)$.The Scott-Zhang interpolation operator $SZ_h$ from $H^1_0(\Gamma)$ to $Q_h$ satisfies the following inequalities,
 \begin{equation}\label{SZ_stability}
@@
 from which we obtain the continuity in $H^1_0(\Gamma)$.\\
-{\color{red} I would skip this proof and just leave the citation}
 \end{proof}
-
 \begin{lemma}\label{lemma:trspace_infsup} 
@@
 \begin{equation*}
-\|\mathcal{E}\|^{-1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle Tv , \mu_h \rangle}{\|v\|_{H^1(\Omega)}} 
+\|\mathcal{E}_\Omega\|^{-1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{\|v\|_{H^1(\Omega)}} 
 \end{equation*}
-and by the trace inequality $\|Tv\|_{H^\frac 12 (\Gamma)} \leq C_T \|v\|_{H^1(\Omega)}$ (see \cite[7.56]{adams1975pure}), we obtain 
+and by the trace inequality $\|\trace v\|_{H^\frac 12 (\Gamma)} \leq C_T \|v\|_{H^1(\Omega)}$ (see \cite[7.56]{adams1975pure}), we obtain 
 \begin{equation*}
-\sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle T v , \mu_h \rangle}{\|v\|_{H^1(\Omega)}}
-\leq C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle T v , \mu_h \rangle}{ \|Tv\|_{H^{\frac 12}(\Gamma)}}.
+\sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{\|v\|_{H^1(\Omega)}}
+\leq C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{ \|\trace v\|_{H^{\frac 12}(\Gamma)}}.
 \end{equation*}
@@
 \begin{split}
-C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle T v , \mu_h \rangle}{ \|Tv\|_{H^{\frac 12}(\Gamma)}}&= C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(T v) , \mu_h \rangle}{ \|Tv\|_{H^{\frac 12}(\Gamma)}}\\
-&\leq  C_T C \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(T v) , \mu_h \rangle}{ \|P_h(Tv)\|_{H^{\frac 12}(\Gamma)}}\\
-&= C_T C \sup_{\substack{q_h \in W_{h,0}^k(\Gamma)}} \frac{\langle q_h , \mu_h \rangle}{  \|q_h\|_{H^{\frac 12}(\Gamma)}}.
+C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{ \|\trace v\|_{H^{\frac 12}(\Gamma)}}&= C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(\trace v) , \mu_h \rangle}{ \|\trace v\|_{H^{\frac 12}(\Gamma)}}\\
+&\leq  C_T C \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(\trace v) , \mu_h \rangle}{ \|P_h(\trace v)\|_{H^{\frac 12}(\Gamma)}}\\
+&= C_T C \sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , \mu_h \rangle}{  \|q_h\|_{H^{\frac 12}(\Gamma)}}.
 \end{split}
@@
 \inf_{\mu_h \in Q_h} 
-\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)}} \frac{ \langle T v_h - \mathcal{U}_E {\vd}_h, \mu_h \rangle _{\Gamma}} {\vertiii{[v_h, {\vd} _h]} \|\mu_h\|_{H^{-\frac 12 }(\Gamma)}}
+\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)}} \frac{ \langle \trace v_h - \ext {\vd}_h, \mu_h \rangle _{\Gamma}} {\vertiii{[v_h, {\vd} _h]} \|\mu_h\|_{H^{-\frac 12 }(\Gamma)}}
 \geq \beta_{h,1}. 
@@
 \begin{equation*}
-\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)}} \frac{ \langle T v_h - \mathcal{U}_E {\vd}_h, \mu_h \rangle _{\Gamma}} {\vertiii{[v_h,  {\vd}_h]}}
-\geq \sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle T v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}}.
+\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)}} \frac{ \langle \trace v_h - \ext {\vd}_h, \mu_h \rangle _{\Gamma}} {\vertiii{[v_h,  {\vd}_h]}}
+\geq \sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \trace v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}}.
 \end{equation*}
@@
 \begin{equation*}
-\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle T v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}} \geq \beta_{h,1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \qquad \forall \mu_h \in Q_h.
+\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \trace v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}} \geq \beta_{h,1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \qquad \forall \mu_h \in Q_h.
 \end{equation*}
 
-Using Lemma \ref{lemma:trspace_infsup} and the boundedness of the armonic extension operator $\mathcal{E}$ from $H^{\frac 12}_{00}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
+Using Lemma \ref{lemma:trspace_infsup} and the boundedness of the armonic extension operator $\mathcal{E}_{\Omega}$ from $H^{\frac 12}_{00}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
 \begin{equation*}
@@
 \leq 
-\|\mathcal{E}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{E}q_h\|_{H^1(\Omega)}} .
+\|\mathcal{E}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{E}_\Omega q_h\|_{H^1(\Omega)}} .
 \end{equation*}
@@
 \begin{equation*}
-\|\mathcal{E}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{E}q_h\|_{H^1(\Omega)}} 
+\|\mathcal{E}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{E}_{\Omega}q_h\|_{H^1(\Omega)}} 
 \leq
-\|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|R_h \mathcal{E} q_h\|_{H^1(\Omega)}}
+\|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|R_h \mathcal{E}_{\Omega} q_h\|_{H^1(\Omega)}}
 \end{equation*}
@@
 \leq
-\|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{E} q_h\|_{H^1(\Gamma)}}
+\|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{E}_{\Omega} q_h\|_{H^1(\Gamma)}}
 \\
 =
-\|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle T \ R_h E q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{E} q_h\|_{H^1(\Omega)}} 
-\leq \|\mathcal{E}\| C_R \sup_{v_h \in X_{h,k}(\Omega)} \frac{ \langle T v_h, \mu_h \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
+\|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle \trace R_h  \mathcal{E}_{\Omega}q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{E}_{\Omega} q_h\|_{H^1(\Omega)}} 
+\leq \|\mathcal{E}_{\Omega}\| C_R \sup_{v_h \in X_{h,k}(\Omega)} \frac{ \langle \trace v_h, \mu_h \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
 \end{multline}
-Therefore the inf-sup condition $\eqref{inf_sup_discrete_prob1}$ holds with $\beta_{h,1} = \gamma \|\mathcal{E}\|^{-1} C_R^{-1} $.
+Therefore the inf-sup condition $\eqref{inf_sup_discrete_prob1}$ holds with $\beta_{h,1} = \gamma \|\mathcal{E}_{\Omega}\|^{-1} C_R^{-1} $.
 \end{proof}
-{\color{red}
+
 \begin{remark} We notice that to prove the result in Lemma \ref{lemma:trspace_infsup} (and then the discrete inf-sup condition)  basically we need a projection operator $P_h: H^{\frac 12}_{00} \longrightarrow W_{h,0}^k(\Gamma)$ orthogonal in the multiplier space $Q_h$, namely such that $\langle P_h v, \mu_h \rangle = \langle v, \mu_h \rangle, \, \forall \mu_h \in Q_h$, and continuous in $H^{\frac 12}(\Gamma)$.
 Therefore, in principle different choices than $Q_h=W_{h,0}^k(\Gamma)$ could be considered if we can build an operator $P_h$ satisfying these properties.
-In \cite{belgacem1999mortar} such operator $P_h$  is built for a particular choice of $Q_h$ but it is not clear how they prove the $H^1$-stability inequality (and consequently the $H^{\frac 12 }$-stability) with a constant independent of the mesh size $h$...
+In \cite{belgacem1999mortar} such operator $P_h$  is built for a particular choice of $Q_h$ but it is not clear how to prove the $H^1$-stability inequality (and consequently the $H^{\frac 12 }$-stability) with a constant independent of the mesh size $h$.
 \end{remark}
-}
+
 \subsubsection{Problem 2}
@@
 &(u_h,v_h)_{H^1(\Omega)} + ({\ud}_h,{\vd}_h)_{H^1(\Lambda), |{\cal D}|} 
-+  \langle  \avrc{Tv_h} -  {\vd}_h, {\ld}_h \rangle_{\Lambda, |\DD|} 
++  \langle  \mtrace v_h -  {\vd}_h, {\ld}_h \rangle_{\Lambda, |\DD|} 
 \\
@@
 \\
-&  \langle \avrc{T u_h} - {\ud}_h, {\md}_h \rangle_{\Lambda,| \DD| } = 0
+&  \langle \mtrace u_h - {\ud}_h, {\md}_h \rangle_{\Lambda,| \DD| } = 0
 \quad \forall {\md}_h \in Q_h\,.
@@
 It coincides with the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$ and satisfying homogeneous Dirichlet boundary condition.
-{\color{red} (Add assumptions..)}
 We choose $Q_h=W_{h,0}^k(\Lambda)$, therefore we impose homogeneous Dirichlet boundary condition on $\Lambda \cap \partial \Omega$ also for the Lagrange multiplier.
@@
 In particular, following the same steps as for Problem 1, we can prove the following results.
+
+%**** uniform \DD
+%\begin{lemma}
+%Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
+%\begin{equation*}
+%(P_h v , \psi)_\Lambda= (v, \psi)_\Lambda \qquad \forall \psi \in Q_h.  
+%\end{equation*} 
+%Then, $P_h$ is continuous on $H^{\frac 12}_{00}(\Lambda)$, namely
+%\begin{equation*}
+%\|P_h v\|_{H^{\frac 12}_{00}(\Lambda)} \leq C \|v\|_{H^{\frac 12}_{00}(\Lambda)},
+%\end{equation*}
+%where $C$ is a positive constant independent of $h$.
+%\end{lemma}
+%
+%\begin{lemma}\label{infsup_avr_trspace}
+%There exist a constant $\gamma >0$ such that
+%\begin{equation*}
+%\sup_{\substack{q_h \in W_{h,0}^k(\Lambda)}} \frac{\langle q_h , \mu_h \rangle}{ \|q_h\|_{H^{\frac 12}(\Lambda)}} \geq \gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall \mu_h \in Q_h.
+%\end{equation*} 
+%\end{lemma}
+%
+%\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds, namely 
+%$\exists \beta_{h,2} >0$ s.t.
+%\begin{equation}
+%\inf_{\mu_h \in Q_h} 
+%\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)} }\frac{\langle \mtrace v_h -  {\vd}_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\vertiii{[v_h, {\vd}_h]} \|{\md}_h\|_{H^{-\frac 12 }(\Lambda)} }
+%\geq \beta_{h,2}. 
+%\end{equation}
+%\end{theorem}
+%\begin{proof}
+%Let ${\md}_h$ be arbitrarly chosen in $Q_h$. Again, we choose ${\vd}_h =0$, so that the proof reduces to show that there exists $\beta_{h,2}$ such that
+%\begin{equation*}
+%\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \mtrace v_h , {\md}_h \rangle _{\Lambda,|\DD|} } {\|v_h\|_{H^1(\Omega)} }\geq \beta_{h,2} \|{\md}_h\|_{H^{-\frac 12}(\Lambda)}\ \qquad \forall {\md}_h \in Q_h.
+%\end{equation*}
+%Let us denote with $\ext$ the uniform extension operator from $\Lambda$ to $\Gamma$. Using Lemma \ref{H12norm_Gamma}, we easily have for any $w \in H^{\frac 12}(\Lambda)$,\\
+%{\color{red} TO DO: generalize to non constant $\DD$}
+%\begin{equation*}
+%\|\mathcal{U}_E w\|_{H^{\frac 12}(\Gamma)}=|\DD| \|w\|_{H^{\frac 12}(\Lambda)}.
+%\end{equation*}
+%Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $E$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
+%\begin{multline}
+%\gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \leq 
+%\sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
+%\\
+%= |\DD| \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
+%\leq |\DD|\|E\| \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda} } {\|E \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
+%\\
+%\leq |\DD|\|E\| C_R \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
+%\\ 
+%=  |\DD|\|E\| C_R \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E q_h, \mu_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
+%\\
+%\leq |\DD|\|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi _2  v_h, \mu_h \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
+%\end{multline}
+%
+%%\begin{equation*}
+%%\|\mathcal{U}_E w\|_{H^{\frac 12}(\Gamma)}\lesssim \|w\|_{H^{\frac 12}(\Lambda)}.
+%%\end{equation*}
+%%Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{E}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
+%%\begin{multline}
+%%\gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \leq 
+%%\sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
+%%\\
+%%\lesssim \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
+%%\lesssim \|\mathcal{E}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda} } {\|\mathcal{E} \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
+%%\\
+%%\lesssim \|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
+%%\\ 
+%%\lesssim\|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle \avrc{TR_h E \mathcal{U}_E q_h}, {\md}_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
+%%\\
+%%\lesssim\|\mathcal{E}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \avrc{T v_h}, {\md}_h \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
+%%\end{multline}
+%
+%\end{proof}
+%
+
+%*******************extension to non uniform $|\DD|$
+
 \begin{lemma}
-Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow W_{h,0}^k(\Lambda)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
+Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
 \begin{equation*}
-(P_h v , \psi)_\Lambda= (v, \psi)_\Lambda \qquad \forall \psi \in W_{h,0}^k(\Lambda).  
-\end{equation*} 
-Then, $P_h$ is continuous on $H^{\frac 12}_{00}(\Lambda)$, namely
-\begin{equation*}
-\|P_h v\|_{H^{\frac 12}_{00}(\Lambda)} \leq C \|v\|_{H^{\frac 12}_{00}(\Lambda)},
-\end{equation*}
-where $C$ is a positive constant independent of $h$.
-\end{lemma}
-
-\begin{lemma}\label{infsup_avr_trspace}
-There exist a constant $\gamma >0$ such that
-\begin{equation*}
-\sup_{\substack{q_h \in W_{h,0}^k(\Lambda)}} \frac{\langle q_h , \mu_h \rangle}{ \|q_h\|_{H^{\frac 12}(\Lambda)}} \geq \gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall \mu_h \in W_{h,0}^k(\Lambda).
-\end{equation*} 
-\end{lemma}
-
-\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds, namely 
-$\exists \beta_{h,2} >0$ s.t.
-\begin{equation}
-\inf_{\mu_h \in Q_h} 
-\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)} }\frac{\langle \avrc{Tv_h} -  {\vd}_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\vertiii{[v_h, {\vd}_h]} \|{\md}_h\|_{H^{-\frac 12 }(\Lambda)} }
-\geq \beta_{h,2}. 
-\end{equation}
-\end{theorem}
-\begin{proof}
-Let ${\md}_h$ be arbitrarly chosen in $Q_h$. Again, we choose ${\vd}_h =0$, so that the proof reduces to show that there exists $\beta_{h,2}$ such that
-\begin{equation*}
-\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \avrc{T v_h} , {\md}_h \rangle _{\Lambda,|\DD|} } {\|v_h\|_{H^1(\Omega)} }\geq \beta_{h,2} \|{\md}_h\|_{H^{-\frac 12}(\Lambda)}\ \qquad \forall {\md}_h \in Q_h.
-\end{equation*}
-Let us denote with $\mathcal{U}_E$ the uniform extension operator from $\Lambda$ to $\Gamma$. Using Lemma \ref{H12norm_Gamma}, we easily have for any $w \in H^{\frac 12}(\Lambda)$,\\
-{\color{red} TO DO: generalize to non constant $\DD$}
-\begin{equation*}
-\|\mathcal{U}_E w\|_{H^{\frac 12}(\Gamma)}=|\DD| \|w\|_{H^{\frac 12}(\Lambda)}.
-\end{equation*}
-Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $E$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
-\begin{multline}
-\gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \leq 
-\sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
-\\
-= |\DD| \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
-\leq |\DD|\|E\| \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda} } {\|E \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
-\\
-\leq |\DD|\|E\| C_R \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
-\\ 
-=  |\DD|\|E\| C_R \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E q_h, \mu_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
-\\
-\leq |\DD|\|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi _2  v_h, \mu_h \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
-\end{multline}
-
-%\begin{equation*}
-%\|\mathcal{U}_E w\|_{H^{\frac 12}(\Gamma)}\lesssim \|w\|_{H^{\frac 12}(\Lambda)}.
-%\end{equation*}
-%Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{E}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
-%\begin{multline}
-%\gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \leq 
-%\sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
-%\\
-%\lesssim \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
-%\lesssim \|\mathcal{E}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda} } {\|\mathcal{E} \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
-%\\
-%\lesssim \|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
-%\\ 
-%\lesssim\|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle \avrc{TR_h E \mathcal{U}_E q_h}, {\md}_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
-%\\
-%\lesssim\|\mathcal{E}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \avrc{T v_h}, {\md}_h \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
-%\end{multline}
-
-\end{proof}
-
-{\color{red}
-*******************extension to non uniform $|\DD|$
-}
-\begin{lemma}
-Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow W_{h,0}^k(\Lambda)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
-\begin{equation*}
-(P_h v , \psi)_{\Lambda,|\DD|}= (v, \psi)_{\Lambda , |\DD|} \qquad \forall \psi \in W_{h,0}^k(\Lambda).  
+(P_h v , \psi)_{\Lambda,|\DD|}= (v, \psi)_{\Lambda , |\DD|} \qquad \forall \psi \in Q_h.  
 \end{equation*} 
@@
 \begin{equation*}
-\sup_{\substack{q_h \in W_{h,0}^k(\Lambda)}} \frac{\langle q_h , {\md}_h \rangle_{\Lambda, |\DD|}}{ \|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} \geq \gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall {\md}_h \in W_{h,0}^k(\Lambda).
+\sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , {\md}_h \rangle_{\Lambda, |\DD|}}{ \|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} \geq \gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall {\md}_h \in Q_h.
 \end{equation*} 
@@
 \inf_{\mu_h \in Q_h} 
-\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)} }\frac{\langle \avrc{Tv_h} -  {\vd}_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\vertiii{[v_h, {\vd}_h]} \|{\md}_h\|_{H^{-\frac 12 }(\Lambda)} }
+\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)} }\frac{\langle \mtrace v_h -  {\vd}_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\vertiii{[v_h, {\vd}_h]} \|{\md}_h\|_{H^{-\frac 12 }(\Lambda)} }
 \geq \beta_{h,2}. 
@@
 \begin{equation*}
-\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \avrc{T v_h} , {\md}_h \rangle _{\Lambda,|\DD|} } {\|v_h\|_{H^1(\Omega)} }\geq \beta_{h,2} \|{\md}_h\|_{H^{-\frac 12}(\Lambda)}\ \qquad \forall {\md}_h \in Q_h.
+\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \mtrace v_h , {\md}_h \rangle _{\Lambda,|\DD|} } {\|v_h\|_{H^1(\Omega)} }\geq \beta_{h,2} \|{\md}_h\|_{H^{-\frac 12}(\Lambda)}\ \qquad \forall {\md}_h \in Q_h.
 \end{equation*}
-Let us denote with $\mathcal{U}_E$ the uniform extension operator from $\Lambda$ to $\Gamma$. {\color{red}We notice that for any $w \in H^{\frac 12}(\Lambda)$,
+From Lemma \ref{lemma:H12norm} and its corollaries, for any $w \in H^{\frac 12}(\Lambda)$,
 \begin{equation*}
-\|\mathcal{U}_E w\|_{H^{\frac 12}(\Gamma)}= \|w\|_{H^{\frac 12}(\Lambda),|\DD|}.
+\|\ext w\|_{H^{\frac 12}(\Gamma)}= \|w\|_{H^{\frac 12}(\Lambda),|\DD|}.
 \end{equation*}
-}
-Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{E}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
+
+Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{E}_{\Omega}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
 \begin{multline}
 \gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \leq 
-\sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} 
+\sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} 
 \\
-=  \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
-\leq \|\mathcal{E}\| \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|\mathcal{E} \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
+=  \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|\ext q_h\|_{H^{\frac 12}(\Gamma)}} 
+\leq \|\mathcal{E}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|\mathcal{E}_{\Omega} \ext q_h\|_{H^1(\Omega)}} 
 \\
-\leq \|\mathcal{E}\| C_R \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
+\leq \|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|R_h \mathcal{E}_{\Omega} \ext q_h\|_{H^1(\Omega)}}
 \\ 
-=  \|\mathcal{E}\| C_R \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle 	\avrc{T  R_h E \mathcal{U}_E q_h}, \mu_h \rangle _{\Lambda,|\DD|}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
+=  \|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle 	\mtrace R_h \mathcal{E}_{\Omega} \ext q_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|R_h \mathcal{E}_{\Omega} \ext w_h\|_{H^1(\Omega)}}
 \\
-\leq \|\mathcal{E}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \avrc{T v_h}, \mu_h \rangle _{\Lambda,|\DD|}} {\|v_h\|_{H^1(\Omega)}}. 
+\leq \|\mathcal{E}_{\Omega}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \mtrace v_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|v_h\|_{H^1(\Omega)}}. 
 \end{multline}

### 2019-07-22 3d1d_coupled_LM.tex

@@
 \usepackage{stmaryrd}
+\usepackage{tikz, subfigure}
 
@@
 \def\DD{\partial\mathcal{D}}
-\def\trace{\overline{\mathcal{R}}}
-\def\ext{\mathcal{E}}
+\def\trace{{\mathcal{T}_\Gamma}}
+\def\mtrace{{\overline{\mathcal{T}}_\Lambda}}
+\def\ext{\mathcal{E}_\Gamma}
 \def\ide{\mathcal{I}}
@@
 Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set.
-Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Omega_\ominus}$ be the complementary set of the cylinder.
+Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Omega}_\ominus$ be the complementary set of the cylinder.
 We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Omega_\ominus$.
 We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$.
-We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Omega_\ominus$ and its boundary, respectively.
+We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Omega_\ominus$ and its boundary, respectively, and we assume that $\min |\D (s)| >0$, where $|\D (s)|$ is the measure of $\D (s)$.
 %In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach. 
@@
 
-The objective of this work is to derive and alalyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Omega_\ominus$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$.
+The objective of this work is to derive and analyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Omega_\ominus$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$.
 This new problem setting will be called the \emph{reduced} problem.
@@
 
-Using the averaging tools for the model reduction approach, we end up with two different formulations of a reduced problem
+Using a model reduction approach based on averaging, we end up with two different formulations of a reduced problem
 for the unknown $u$ defined on the entire 3D domain $\Omega$, coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$
 and a Lagrange multiplier defined either on $\Gamma$ (problem 1) or on $\Lambda$ (problem 2). 
-%In the reduced problem the multiplier assumes the following interpretation,
-%\begin{equation*}
-%L = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \nabla \uf \cdot \nn_\ominus
-%   = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \lambda \,.
-%\end{equation*}
-
-%We consider two alternative formulations.
-The scope of this work is to compare them, 
-with the aim to determine which is the most suitable as a computational model based on 3D-1D coupled PDEs.
+The scope of this work is to compare them, with the aim to determine which is the most suitable to set up a computational model for 3D-1D coupled PDEs.
 
@@
 By the fundamental theorem of integral calculus combined with the Reynolds transport Theorem, 
-%where $d_s |\partial\mathcal{D}(s)|$ is the rate at which the cross section changes size,
-being $\nu$ the normal component of the velocity of the boundary, 
-we have,
-%\begin{multline*}
-%-\int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma +  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma 
-%= \int_{s_1}^{s_2} d_s \int_{\mathcal{D}(s)}  \partial_s \uf d\sigma ds
-%\\
-%= \int_{s_1}^{s_2} \int_{\mathcal{D}(s)} \partial^2_{ss} \uf d\sigma ds + \int_{s_1}^{s_2} \int_{\partial\mathcal{D}(s)} \nu \partial_s \uf d\gamma ds
-%\\
-%= \int_{s_1}^{s_2} \left[ |\mathcal{D}(s)| d^2_{ss} \avrd{u}_{\ominus}  + |\partial\mathcal{D}(s)| \nu  d_s \avrc{u}_{\ominus} \right] ds.
-%\end{multline*}
-
+being $\nu$ the normal deformation of the boundary along $(0,S)$, we have,
 \begin{equation*}
@@
 \begin{equation}\label{eq:1Ddirneu_weak}
- (d_s \ud, d_s \ud)_{\Lambda,|\mathcal{D}|} 
+ (d_s \ud, d_s \vd)_{\Lambda,|\mathcal{D}|} 
 +(\ud, \vd)_{\Lambda, |\D|}
@@
 
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 \subsubsection*{Topological model reduction of the problem on $\Omega_{\oplus}$}
@@
 &(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
-+ \langle T v  - \mathcal{U}_E \vd, \lambda \rangle_\Gamma
++ \langle \trace v  - \ext \vd, \lambda \rangle_\Gamma
 \\
@@
 \\
-&   \langle T u - \mathcal{U}_E \ud , \mu \rangle_\Gamma = 0
+&   \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0
 \quad \forall \mu \in H^{-\frac12}(\Gamma)\,.
@@
 \end{subequations}
-Here, $T:H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ denotes the trace operator on $\Gamma$ and $\mathcal{U}_E: H^1_0(\Lambda) \rightarrow H^1_{0}(\Gamma)$ denotes the uniform extension from $\Lambda$ to $\Gamma$.
-The idea is then to couple a 3D PDE with a 1D one, using a Lagrange multiplier space defined on a 2D surface that surrounds the 1D manifold.\\
-
-%Here, $\Pi_1: H^1_0(\Omega) \rightarrow H^{\frac12}_{00}(\Gamma)$
-%and $\Pi_2: H^1_0(\Lambda) \rightarrow H^{\frac12}_{00}(\Gamma)$
-%and we remark that $\Sigma$ may be considered as a virtual surface
-%not necessarily of the same size as the underlying physical structure that is modeled.  
-%The $\Pi_1$ and $\Pi_2$ operators may be defined in terms of the averaging operators above, but may also be realized in terms of e.g.
-Green functions (I don't know if this is a good idea).
-Furthermore,  $\Gamma$ may be discretized in terms of facets neighboring $\Lambda$ and may as such not be represented as a separate structure in the implementation.
+Here, $\trace:H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ denotes the trace operator from $\Omega$ to $\Gamma$ and $\ext: H^1_0(\Lambda) \rightarrow H^1_{0}(\Gamma)$ denotes the uniform extension from $\Lambda$ to $\Gamma$.
 
 % >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-Now, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-3D to a 3D-1D-1D formulation. 
-To this purpose, let us write the lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
+Now, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-2D formulation
+involving sub-problems on $\Omega$ and $\Lambda$ and coupling operators defined on $\Gamma$
+to a 3D-1D-1D formulation where the coupling terms are set on $\Lambda$. 
+To this purpose, let us write the Lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
 \begin{equation*}
@@
 where $\avrc{\tilde{\lambda}}=\avrc{\tilde{v}}=0$. 
-Therefore, using the coordinates system $(r,s,t)$ on $\Gamma$, we have
+Therefore, the coupling term on $\Gamma$ can be decomposed as,
 \begin{equation*}
@@
 &(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
-+  \langle \avrc{T v} - \vd, \ld \rangle_{H^{-\frac12}(\Lambda), |\DD|} 
++  \langle \mtrace v - \vd, \ld \rangle_{H^{-\frac12}(\Lambda), |\DD|} 
 \\
@@
 &\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
+\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)\,,
 \\
-&   \langle \avrc{T u} -   \ud, \md \rangle_{H^{-\frac12}(\Lambda),|\DD|} = 0
-\quad \forall \md \in H^{-\frac12}(\Lambda)\,.
+&   \langle \mtrace u -   \ud, \md \rangle_{H^{-\frac12}(\Lambda),|\DD|} = 0
+\quad \forall \md \in H^{-\frac12}(\Lambda)\,,
 \end{align}
 \end{subequations}
-We notice that all the integrals of the reduced problem are well defined because $u,v \in H^1_0(\Omega)$, 
-$Tu, \ Tv \in H^\frac12_{00}(\Gamma)$ and thus $\avrc{Tu},\avrc{Tv} \in H^\frac12_{00}(\Lambda)$, as shown in the following lemma.
-%More precisely, $\Pi_1 : H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda$ such that
-%$\Pi_1 u = \avrc{(u|_\Gamma)}$ is the combination between the trace on $\Gamma$ and the average on $\partial{\cal D}$.
-%The operator $\Pi_2: H^1_0(\Lambda) \rightarrow H^\frac12_{00}(\Lambda)$ is the injection form $H^1_0(\Lambda)$ and $H^\frac12_{00}(\Lambda)$.
+where $\mtrace$ denotes the composition of operators $\trace \circ \avrc{(\cdot)}$.
+We notice that all the integrals of the reduced problem are well defined because 
+$\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$ as shown in the following lemma.
+
+%\begin{lemma}\label{lemma:H12norm}
+%{\color{red}TO DO: generalize to not uniform $\DD$} 
+%When $\Gamma$ is a cylinder, if $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}\in H_{00}^{\frac 12}(\Lambda)$.
+Moreover, if $u\in H^{\frac 12}_{00}(\Gamma)$ is constant on each cross section, namely $u(s,\theta)=u(s)$, then
+%\begin{equation*}
+%\|u\|_{H^{\frac 12}_{00}(\Gamma)}=2\pi R \|u\|_{H^{\frac 12}_{00}(\Lambda)}.
+%\end{equation*}
+%\end{lemma}
+%\begin{proof}
+%Let us denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the laplacian on $\Gamma$, and with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $\Lambda$.
+In particular,
+%\begin{align*}
+%\phi _{ij}(s,\theta)=sin (i\pi s)\left( cos(j\theta)+ sin(j\theta) \right),\\
+%\rho_{ij}=i\pi ^2+\frac{j^2}{R^2},\\
+%\phi _{i}(s)=sin (i\pi s),\\
+%\rho _i = i\pi ^2.
+%\end{align*}
+%It is easy to verify that 
+%\begin{eqnarray}
+%\label{null_int_eigenf}
+%\int_0^{2\pi} \phi _{ij}(s,\theta)=0 \quad \forall j>0, \forall i \\
+%\label{nonull_int_eigenf}
+%\int_0^{2\pi} \phi _{ij}(s,\theta)= 2\pi R \, \sin(i \pi s) \quad \mbox{if } j=0, \forall i  .\\
+%\end{eqnarray}
+%Moreover we recall that $\phi_{i,j}(s,\theta)$ and $\phi _i(s)$ are orthogonal basis of $L^2(\Gamma)$ and $L^2(\Lambda)$ respectively. Therefore,
+%\begin{multline*}
+%\avrc{u}(s)=\frac{1}{2\pi R}\int_0^{2\pi} u(s,\theta)R\, d\theta
+%= \frac{1}{2\pi R}\int_0^{2\pi} \sum_{i,j} a_{i,j} \phi_{i,j}(s,\theta) R\, d\theta
+%\\= \frac{1}{2\pi R}\sum_{i,j} a_{i,j}\int_0^{2\pi}  \phi_{i,j}(s,\theta) R\, d\theta
+%=  \sum_{i} a_{i,0} \phi_{i}(s).
+%\end{multline*}
+%From \cite[Lemma 4.11]{chandler2015interpolation} we have
+%\begin{equation}\label{H12norm_Gamma}
+%\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2,
+%\text{ with }
+%a_{ij}=\int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds.
+%\end{equation}
+%and 
+%\begin{equation*}
+%\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
+%\text{ with }
+%\avrc{a}_i=\int _0^1 \avrc{u}(s )\phi_{i}(s) ds.
+%\end{equation*}
+%
+%Therefore, we have
+%\begin{multline*}
+%\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=
+%\sum_{i=1}^{\infty}\left( 1+ i^2\pi^2\right)^{\frac 12}\left( \int_0^1 \avrc{u}(s) sin(i\pi s)\, ds \right)^2\\
+%= \sum_{i=1}^{\infty} \left( 1+ i^2\pi^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^1 \sin(j\pi s) \sin(i\pi s) \, ds  \right)^2\\
+%= \sum_{i=1}^{\infty} \frac 14 \left( 1+ i^2\pi^2\right)^{\frac 12}a_{i,0}^2\\
+%\leq \sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ i^2\pi^2 + \frac{j^2}{R^2}\right)^{\frac 12} |a_{i,j}|^2 =\|u\|^2_{H^{\frac 12}(\Gamma)},
+%\end{multline*}
+%
+%where we have used the fact that
+%\begin{eqnarray*}
+%&\int_0^1 \sin(i\pi s) \sin(j\pi s)\, ds=0 \quad \text{if $i\neq j$}\\
+%&\int_0^1 \sin(i\pi s) \sin(j\pi s)\, ds=\frac 12 \quad \text{if $i =j$}.
+%\end{eqnarray*}
+%Moreover, in the case in which $u$ is constant on each cross section, from \eqref{H12norm_Gamma} we have
+%\begin{multline*}
+%\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2
+%=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ i\pi ^2+\frac{j^2}{R^2}\right)^{\frac 12}\left( \int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds \right)^2\\
+%=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ i\pi ^2+\frac{j^2}{R^2}\right)^{\frac 12}\left( \int _0^1 u(s) \int _0^{2\pi} \phi_{ij}\, R d\theta ds \right)^2,
+%\end{multline*}
+%and using \eqref{null_int_eigenf} and \eqref{nonull_int_eigenf}, we obtain
+%\begin{multline*}
+%\|u\|^2_{H^{\frac 12}(\Gamma)}=
+%\sum_{i=1}^{\infty}\left( 1+ i\pi ^2\right)^{\frac 12}\left(\int _0^1 u(s )sin (i\pi s) 2\pi R ds\right)^2\\
+%=4\pi ^2 R^2 \sum_{i=1}^{\infty}\left( 1+ \rho _i\right)^{\frac 12}|a_i|^2 = 4\pi ^2 R^2  \|u\|^2_{H^{\frac 12}(\Lambda)}.
+%\end{multline*}
+%\hspace*{0.9\textwidth} c.v.d.
+%\end{proof}
+%\begin{remark}
+%The results of \eqref{lemma:H12norm}  can be generalized to the case of a  different geometry of $\Gamma$, for example a parallelepiped.  
+%\end{remark}
 
 \begin{lemma}\label{lemma:H12norm}
-{\color{red}TO DO: generalize to not uniform $\DD$} 
-When $\Gamma$ is a cylinder, if $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}\in H_{00}^{\frac 12}(\Lambda)$.
-Moreover, if $u\in H^{\frac 12}_{00}(\Gamma)$ is constant on each cross section, namely $u(s,\theta)=u(s)$, then
+Let $\Gamma$ be a tensor product domain, $\Gamma= (0,X) \times (0,Y)$.
+For any regular $u(x,y)$ in $\Gamma$, let $\avrc{u}(x)=\frac 1Y \int _0^Y u(x,y)\, dy$.
+Then, for any $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}(x)\in H_{00}^{\frac 12}((0,X))$.
+Moreover, if $u(x,y)\in H^{\frac 12}_{00}(\Gamma)$ is constant with respect to $y$, namely $u(x,y)=u(x)$, then 
 \begin{equation*}
-\|u\|_{H^{\frac 12}_{00}(\Gamma)}=2\pi R \|u\|_{H^{\frac 12}_{00}(\Lambda)}.
+\|u\|_{H^{\frac 12}_{00}(\Gamma)}=Y \|u\|_{H^{\frac 12}_{00}(0,X)}.
 \end{equation*}
@@
 \begin{proof}
-Let us denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the laplacian on $\Gamma$, and with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $\Lambda$.
+Let us consider the eigenvalue problems for the Laplace operator on $\Gamma$ with homogeneous Dirichlet conditions at $x=0,\, X$ and periodic boundary conditions at $y=0,\, Y$ and on $(0,X)$ with homogeneous Dirichlet conditions.
+Let us denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the laplacian on $\Gamma$, and with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $(0,X)$.
 In particular,
 \begin{align*}
-\phi _{ij}(s,\theta)=sin (i\pi s)\left( cos(j\theta)+ sin(j\theta) \right),\\
-\rho_{ij}=i\pi ^2+\frac{j^2}{R^2},\\
-\phi _{i}(s)=sin (i\pi s),\\
-\rho _i = i\pi ^2.
+\phi _{ij}(x,y)=\sin \left(\frac{i\pi x}{X}\right)\left( cos\left(\frac{j2\pi y}{Y}\right)+ sin	\left(\frac{j2\pi y}{Y}\right) \right),\\
+\rho_{ij}=\left(\frac{i\pi}{X}\right) ^2+\left(\frac{j2\pi}{Y}\right)^2,\\
+\phi _{i}(x)=\sin \left(\frac{i\pi x}{X}\right),\\
+\rho _i = \left(\frac{i\pi}{X}\right) ^2.
 \end{align*}
@@
 \label{null_int_eigenf}
-\int_0^{2\pi} \phi _{ij}(s,\theta)=0 \quad \forall j>0, \forall i \\
+\int_0^{Y} \phi _{ij}(x,y)=0 \quad \forall j>0, \forall i \\
 \label{nonull_int_eigenf}
-\int_0^{2\pi} \phi _{ij}(s,\theta)= 2\pi R \, \sin(i \pi s) \quad \mbox{if } j=0, \forall i  .\\
+\int_0^{Y} \phi _{ij}(x,y)= Y \, \sin\left(\frac{i\pi x}{X}\right) \quad \mbox{if } j=0, \forall i  .\\
 \end{eqnarray}
-Moreover we recall that $\phi_{i,j}(s,\theta)$ and $\phi _i(s)$ are orthogonal basis of $L^2(\Gamma)$ and $L^2(\Lambda)$ respectively. Therefore,
+Moreover we recall that $\phi_{i,j}(x,y)$ and $\phi _i(x)$ are orthogonal basis of $L^2(\Gamma)$ and $L^2(0,X)$ respectively. Therefore,
 \begin{multline*}
-\avrc{u}(s)=\frac{1}{2\pi R}\int_0^{2\pi} u(s,\theta)R\, d\theta
-= \frac{1}{2\pi R}\int_0^{2\pi} \sum_{i,j} a_{i,j} \phi_{i,j}(s,\theta) R\, d\theta
-\\= \frac{1}{2\pi R}\sum_{i,j} a_{i,j}\int_0^{2\pi}  \phi_{i,j}(s,\theta) R\, d\theta
-=  \sum_{i} a_{i,0} \phi_{i}(s).
+\avrc{u}(x)=\frac{1}{Y}\int_0^{Y} u(x,y)\, dy
+= \frac{1}{Y}\int_0^{Y} \sum_{i,j} a_{i,j} \phi_{i,j}(x,y) \, dy
+\\= \frac{1}{Y}\sum_{i,j} a_{i,j}\int_0^{Y}  \phi_{i,j}(x,y) \, dy
+=  \sum_{i} a_{i,0} \phi_{i}(x).
 \end{multline*}
@@
 \text{ with }
-a_{ij}=\int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds.
+a_{ij}=\int _0^X\int _0^{Y} u(x,y )\phi_{ij} (x,y)dy dx.
 \end{equation}
@@
 \begin{equation*}
-\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
+\|\avrc{u}\|^2_{H^{\frac 12}(0,X)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
 \text{ with }
-\avrc{a}_i=\int _0^1 \avrc{u}(s )\phi_{i}(s) ds.
+\avrc{a}_i=\int _0^X \avrc{u}(x )\phi_{i}(x) dx.
 \end{equation*}
@@
 \begin{multline*}
-\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=
-\sum_{i=1}^{\infty}\left( 1+ i^2\pi^2\right)^{\frac 12}\left( \int_0^1 \avrc{u}(s) sin(i\pi s)\, ds \right)^2\\
-= \sum_{i=1}^{\infty} \left( 1+ i^2\pi^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^1 \sin(j\pi s) \sin(i\pi s) \, ds  \right)^2\\
-= \sum_{i=1}^{\infty} \frac 14 \left( 1+ i^2\pi^2\right)^{\frac 12}a_{i,0}^2\\
-\leq \sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ i^2\pi^2 + \frac{j^2}{R^2}\right)^{\frac 12} |a_{i,j}|^2 =\|u\|^2_{H^{\frac 12}(\Gamma)},
+\|\avrc{u}\|^2_{H^{\frac 12}(0,X)}=
+\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \int_0^X \avrc{u}(x) \sin\left(\frac{i\pi x}{X}\right)\, dx \right)^2\\
+= \sum_{i=1}^{\infty} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^1 \sin\left(\frac{j\pi x}{X}\right) \sin\left(\frac{i\pi x}{X}\right) \, dx  \right)^2\\
+= \sum_{i=1}^{\infty} \frac{X^2}{4} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}a_{i,0}^2\\
+\leq \frac{X^2}{4}\sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12} |a_{i,j}|^2 =\frac{X^2}{4}\|u\|^2_{H^{\frac 12}(\Gamma)},
 \end{multline*}
@@
 \begin{eqnarray*}
-&\int_0^1 \sin(i\pi s) \sin(j\pi s)\, ds=0 \quad \text{if $i\neq j$}\\
-&\int_0^1 \sin(i\pi s) \sin(j\pi s)\, ds=\frac 12 \quad \text{if $i =j$}.
+&\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=0 \quad \text{if $i\neq j$}\\
+&\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=\frac X2 \quad \text{if $i =j$}.
 \end{eqnarray*}
-Moreover, in the case in which $u$ is constant on each cross section, from \eqref{H12norm_Gamma} we have
+Moreover, in the case in which $u$ is constant with respect to $y$, from \eqref{H12norm_Gamma} we have
 \begin{multline*}
-\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2
-=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ i\pi ^2+\frac{j^2}{R^2}\right)^{\frac 12}\left( \int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds \right)^2\\
-=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ i\pi ^2+\frac{j^2}{R^2}\right)^{\frac 12}\left( \int _0^1 u(s) \int _0^{2\pi} \phi_{ij}\, R d\theta ds \right)^2,
+\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2\\
+=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12}\left( \int _0^X\int _0^Y u(x,y )\phi_{ij}(x,y) \,dy\,dx \right)^2\\
+=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12}\left( \int _0^X u(x) \int _0^Y \phi_{ij}(x,y)\,  dy dx \right)^2,
 \end{multline*}
@@
 \|u\|^2_{H^{\frac 12}(\Gamma)}=
-\sum_{i=1}^{\infty}\left( 1+ i\pi ^2\right)^{\frac 12}\left(\int _0^1 u(s )sin (i\pi s) 2\pi R ds\right)^2\\
-=4\pi ^2 R^2 \sum_{i=1}^{\infty}\left( 1+ \rho _i\right)^{\frac 12}|a_i|^2 = 4\pi ^2 R^2  \|u\|^2_{H^{\frac 12}(\Lambda)}.
+\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left(\int _0^X Yu(x)\, \sin\left(\frac{i\pi x}{X}\right) dx\right)^2\\
+=Y^2 \sum_{i=1}^{\infty}\left( 1+ \rho _i\right)^{\frac 12}|a_i|^2 = Y^2  \|u\|^2_{H^{\frac 12}(0,X)}.
 \end{multline*}
-\hspace*{0.9\textwidth} c.v.d.
 \end{proof}
 
-\begin{remark}
-The results of \eqref{lemma:H12norm}  can be generalized to the case of a  different geometry of $\Gamma$, for example a parallelepiped.  
-\end{remark}
+\begin{corollary}
+Let $\Gamma$ be the lateral surface of a prism with $N$ faces $\Gamma_i$, $i=1, \dots, N$, with $\Gamma_i=(0,X_i)\times(0,S)$.
+For any $u\in H^{\frac 12}_{00}(\Gamma)$, let $\avrc{u}(s)= \frac{1}{\sum_i{|X_i|}}\sum_{i=1}^N \int_0^{X_i} u(x,s)\, dx$.
+Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$.
+\end{corollary}
 
-It is apparent that problems \eqref{eq:weak_dirneu} and \eqref{eq:red_dirneu} share the same mathematical structure.
-For this reason, the well-posedness of \eqref{eq:red_dirneu} can be studied in the framework of the classical theory of saddle point problems.
+\begin{corollary}
+Let $\Gamma$ be the lateral surface of a cylinder of radius $R$.
+Let $u\in H^{\frac 12}_{00}(\Gamma)$ and let $\avrc{u}(s)= \frac{1}{2\pi R} \int_0^{2\pi} u(s,\theta)R\, d\theta$.
+Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$.
+\end{corollary}
+
+The well-posedness of $\eqref{eq:problem1}$ and $\eqref{eq:problem2}$ can be studied in the framework of the classical theory of saddle point problems as shown in the following.
+
+%It is apparent that problems \eqref{eq:weak_dirneu} and \eqref{eq:red_dirneu} share the same mathematical structure.
+%For this reason, the well-posedness of \eqref{eq:red_dirneu} can be studied in the framework of the classical theory of saddle point problems.
 

### 2019-07-22 graphics/gamma_generated.tex

%\documentclass[tikz,border=3mm]{standalone}
%\usetikzlibrary{calc}
%\usetikzlibrary{shapes, snakes, patterns, arrows}
%\begin{document}

\begin{tikzpicture}[scale=0.7, every node/.style={scale=0.7}]
\pgfmathsetmacro{\factor}{1/sqrt(2)};

\coordinate  (A) at (-2.5,1.5,-2.1*\factor);
\coordinate  (B) at (3.8,4,0*\factor);
\coordinate  (C) at (3.6,-2,2*\factor);
\coordinate  (D) at (6.5,2.7,8*\factor);
\draw[thick, black,    fill=white!90!gray, opacity=1] (A) --(B)--(C)--cycle;
\draw[ thick,black,  fill=gray!60!, opacity=0.7] (D) --(B)--(C)--cycle;
\draw[thick,gray!60!] (D) --(A);
\node [font=\Large, right] at (3.5, -2.5) {$\omega_j $};

%cylinder Gamma
%\draw[dashed, very thick] (1, 5) ellipse (1.5 and 0.3);
%\draw[dashed, very thick] (1, -3) ellipse (1.5 and 0.3);
\draw[black, very  thick] (-0.5, 2.55) -- (-0.5, 5);
\draw[black, very thick, opacity=.2] (-0.5, 2.55) -- (-0.5, 0.75);
\draw[black, very  thick] (-0.5, 0.75) -- (-0.5, -3); 
\draw[ very thick] (2.5, 5) -- (2.5, 3.55);
\draw[ very thick, opacity =0.2] (2.5, 3.55) -- (2.5, -2);
\draw[very thick] (2.5, -2) -- (2.5, -3);
\node [font=\Large, right] at (-1.2, 4.5) {$\Gamma$};

%centerline \Lambda
\draw[very thick] (1, 5) -- (1, 3.05);
\draw[red, very thick, opacity=.6] (1, 3.05) -- (1, -0.65);
\draw[very thick, ]  (1, -0.65) -- (1, -3);
\node [font=\Large, right] at (1.1, 3.8) {$\Lambda$};
\node [font=\Large, right, red] at (1, 0.4) {$\omega _j \cap \Lambda$};

\draw[dashed, very thick, purple, opacity=.4] (1, 3.05) ellipse (1.5 and 0.3);
\draw[dashed, very thick, purple, opacity=.4] (1, -0.65) ellipse (1.5 and 0.3);

\fill [purple, opacity=0.3]  (-0.5, -0.65) arc (180:360:1.5 and 0.3) -- (2.5, 3.05) arc (0:180:1.5 and -0.3);
\node [font=\Large, right, purple] at (-2, 0) {$\Gamma_{\omega_j \cap \Lambda}$};

\end{tikzpicture}

%\end{document}

### 2019-07-22 unfitted_prob2.tex

@@
+\def\patch{\omega _j}
 \subsection{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$}
 We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_h$ cut the interface $\Gamma$. It is easy to understand that the formulation of Problem 2 is more suitable. 
-{\color{red} Add more details, we can refer also to cutFEM (Burman, Massing etc.) explaining the limitation of that approach (network case for example).}\\
+%{\color{red} Add more details, we can refer also to cutFEM (Burman, Massing etc.) explaining the limitation of that approach (network case for example).}\\
 Therefore we focus on the analysis of Problem 2.
 
-\subsubsection{Problem 2} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X^0_{h,1}(\Omega)$ and $X^0_{h,1}(\Lambda)$, see the previous subsection for the definition.
-Concerning the multiplier space, we make the following choice, $Q_h(\Lambda)=\{{\ld}_h : {\ld}_h \in P^0(K) \forall K \in \mathcal{T}^{\Lambda}_{h'}\}$, namely the multiplier lives on the same mesh used for the 1D solution ${\ud}_h$.
-Notice that in this case we suppose that the mesh sizes of the 3D mesh $	\mathcal{T}^{\Omega}_h$ and the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different, in particular we suppose the 1D mesh is finer.
-With this choice the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s({\ld}_h, {\md}_h)$ to \eqref{eq:prob2_discrete} following the approach introduce in \cite{burman2014}.
-In particular, we build a new multiplier space $L_h(\Lambda)$ for which the discrete inf-sup condition is fulfilled and we build a projection operator $\pi_L: Q_h(\Lambda) \rightarrow L_h(\Lambda)$.
-Based on this projection operator, we build the stabilization term $s({\ld}_h, {\md}_h)$ and prove that $\forall [u_h, {\ud}_h]$, there exists $\xi_h([u_h, {\ud}_h]) \in Q_h(\Lambda)$ s.t.
+\subsubsection{Problem 2} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X_{h,0}^1(\Omega)$ and $X_{h,0}^1(\Lambda)$, see the previous subsection for the definition.
+Notice that in this case we suppose that the mesh sizes of the 3D mesh $\mathcal{T}^{\Omega}_h$ and the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different, in particular we suppose the 1D mesh is finer.
+Concerning the multiplier space, let $\mathcal{G}_h = \{K \in \mathcal{T}^{\Omega}_h: \, K\cap \Lambda \neq \emptyset\}$, namely the set of the 3D elements which intersect $\Lambda$, and let us define $Q_h=\{{\ld}_h : {\ld}_h \in P^0(K) \, \forall K \in \mathcal{G}_h\}$.
+We notice that we are extending the multiplier to the 3D elements: equivalenty we could have defined $\lambda_h$ as a piecewise constant function on $K\cap \Lambda$ for any $K \in \mathcal{G}_h$, but we use this trick so that we do not need to consider the 1D mesh given by the intersection of the elements of $\mathcal{G}_h$ with $\Lambda$.
+With this choice the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s({\ld}_h, {\md}_h)$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}.
+In particular, we build a new multiplier space $L_h$ for which the discrete inf-sup condition is fulfilled and we build a projection operator $\pi_L: Q_h \rightarrow L_h$ such that for any $[v, \vd] \in X $
+\begin{equation}\label{condition_pi_L}
+b([v, \vd], {\ld}_h - \pi_L {\ld}_h) \lesssim \vertiii{[v,\vd]}\|{\ld}_h - \pi_L {\ld}_h\|_{L_h},
+\end{equation}
+where for $X$ and $\vertiii{[\cdot, \cdot]}$ we use the definitions of section $3.2$ and $\|\cdot \|_{L_h}$ denotes a suitable discrete norm on $L_h$. Then, the following lemma holds
+\begin{lemma}\cite[Lemma2.1]{burman2014}
+Under the previous assumption, $\forall {\ld}_h \in Q_h$,
+\begin{equation*}
+\|{\ld}_h\|_{H^{-\frac 12}(\Lambda)} \lesssim \sup_{\substack{v_h \in X_{h,0}^1(\Omega)\\ {\vd}_h \in X_{h,0}^1(\Lambda)}} \frac{b([v_h, {\vd}_h], {\ld}_h)}{\vertiii{[v_h, {\vd}_h]}} + \|{\ld}_h - \pi_L {\ld}_h\|_{L_h}
+\end{equation*}
+\end{lemma}
+ Based on this projection operator, we build the stabilization term $s({\ld}_h, {\md}_h)$ satisfying
+ \begin{equation*}
+ \|{\ld}_h- \pi_L {\ld}_h\|_{L_h} \lesssim s({\ld}_h, {\ld}_h)
+\end{equation*}  and prove that $\forall [u_h, {\ud}_h]$, there exists $\xi_h([u_h, {\ud}_h]) \in Q_h$ s.t.
 \begin{equation}\label{stab_coercivity}
-a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h([u_h, {\ud}_h])) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X^0_{h,1}(\Omega)\times X^0_{h,1}(\Lambda) },
+a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h([u_h, {\ud}_h])) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) },
 \end{equation}
 \begin{equation}\label{stab_stability}
-(s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[u_h, {\ud}_h]}_{X^0_{h,1}(\Omega)\times X^0_{h,1}(\Lambda) },
+(s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) },
 \end{equation}
-being $\vertiii{[\cdot \, ,\, \cdot] }_{X^0_{h,1}(\Omega)\times X^0_{h,1}(\Lambda) }$ a suitable discrete norm. \\
+being $\vertiii{[\cdot \, ,\, \cdot] }_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) }$ a suitable discrete norm. Then, the stabilized problem 
+\begin{multline}\label{eq:prob2_stabilized}
+a([u_h, {\ud}_h], [v_h, {\vd}_h]) +
+b([v_h, {\vd}_h], {\ld}_h) +\\
+b([u_h, {\ud}_h], {\md}_h) 
+- s({\ld}_h, {\md}_h) = c(v_h) + d({\md}_h)\\
+  \qquad \forall [v_h, {\vd}_h] \in {X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda), \, \forall \md}_h \in Q_h
+\end{multline}
+is well posed thanks to the following lemma.
+\begin{lemma}\cite[Lemma2.3]{burman2014}
+Under the previous assumptions, system \eqref{eq:prob2_stabilized} admits a unique solution $\{[u_h, {\ud}_h], {\ld}_h \}$.
+\end{lemma}
 
@@
 \begin{equation*}
-b([u_h, {\ud}_h], {\ld}_h) = \left(\avrc{T u_h} - {\ud}_h, {\ld}_h\right)_{\Lambda,|\DD|}.
+b([u_h, {\ud}_h], {\ld}_h) = \left(\mtrace u_h - {\ud}_h, {\ld}_h\right)_{\Lambda,|\DD|}.
 \end{equation*}
-The construction of the inf-sup stable space $L_h(\Lambda)$ is based on assembling the elements of the 3D mesh $\mathcal{T}_h^{\Omega}$ intersecting the 1D manifold $\Lambda$ into macro patches $\left\{ F_j \right\}_j$.
-These patches are such that and  $H\leq |F_j\cap \Lambda|\leq H+h$, where $H$ is sufficiently larger than $h$.
-Moreover,  we assume there exist constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$.
-We define the space $L_h(\Lambda)$ as the space of functions which are $P^0$ on each intersection $F_j\cap \Lambda$.
-Moreover, we associate to each patch $F_j$ a shape regular macro elements $\omega_j$, which is built adding to $F_j$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$.
-We make the following technical assumption: $\Gamma \subset \bigcup _{j} \omega_j$.
-Thanks to the shape regularity of these macro elements,  we have that the discrete trace and Poincarè inequalites hold.
-More precisely, for every function $v\in H^1(\omega_j)$,
+The construction of the inf-sup stable space $L_h$ is based on macro elements of diameter $H$, where $H$ is sufficiently larger than $h$.
+In particular, we assume that there exists positive constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$, with $c_h$ is sufficiently large.
+The space is constructed assembling the 3D elements of $\mathcal{G}_h$ into macro patches $ \patch $ such that $H \leq |\patch\cap \Lambda|\leq cH$.
+Namely, $\patch=\cup _{i=0}^{M_j} K_i$, where $K_i \in \mathcal{G}_h$ and $M_j$ is uniformly bounded in $j$ by some $M\in \mathbb{N}$ and $H=\min_{j}|\patch\cap \Lambda|$.
+We assume that the interiors of the patches $\patch$ are  disjoint.
+We define
+\begin{equation*}
+L_h=\left\{{\lld }_h: \, {\lld }_h\in P^0(\patch)\, \forall j \right\}.
+\end{equation*}
+
+%figure extended patch
+\begin{figure}\label{fig:patch}
+\center
+\input{./graphics/ext_patch}
+\caption{Extended patches $\omega_j$.}
+\end{figure}
+
+Moreover, we associate to each patch $\patch$ a shape-regular extended patch, still denoted by $\omega_j$ for notational simplicity, which is built adding to $\patch$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$ and we assume that the interiors of the new extended patches $\omega _j$ are still disjoint (see Figure \ref{fig:patch}).
+Here we are using the classical definition of shape-regularity, see for example \cite{MR2050138}, namely there exist a constant $C>0$ such that for any $\omega_j$, $\frac{\tilde{\rho}_j}{\bar{\rho}_j}\leq C$, being $\tilde{\rho}_j$ the diameter of $\omega_j$ and $\bar{\rho}_j$ the diameter of the largest ball that can be inscribed in $\omega_j$.
+The extended patches $\omega _j$ are built such that they fulfill the conditions meas$(\patch)=\mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda}\cap \omega_j)=O(H)$, where $\Gamma_{\patch\cap \Lambda}$ is the portion of $\Gamma$ with centerline $\patch\cap \Lambda$.
+See Figure \ref{fig:gamma_generated} for a representation in the simple case in which $\omega _j$ is composed just by one tetrahedron.
+The latter assumption is required to ensure that the intersection of $\Gamma_{\patch\cap \Lambda}$ and $\omega_j$ is not too small and it will be needed later on to prove the inf-sup stability of the space $L_h$ in Lemma \ref{lemma:Lh_infsup}.
+We equipe the space $L_h$ with the discrete norm
+\begin{equation*}
+\|\lld \|_{L_h} = \|\lld \|_{-\frac 12, h, \Lambda} = \|h^{\frac 12} \  \lld \|_{L^2(\Lambda)}.
+\end{equation*}
+As shown in \cite[Section III]{burman2014}, we can always choose $\pi_L$ as the $L_2$ orthogonal projection operator from $\Lambda_h$ to $L_h$ in order to satisfy \eqref{condition_pi_L} and then in practice replace it with any interpolation $\tilde{\pi}_L$ of $\Lambda_h$ in $L_h$.
+In particular, we define $\forall \lambda_h \in \Lambda_h$,
+\begin{equation*}
+\tilde{\pi}_L {\ld}_{ _{|\patch}} = N_j^{-1} \sum_{\substack{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset}} {\ld}_{|K_i} \qquad \text{for all $\omega_j$,} 
+\end{equation*}
+being $N_j$ the cardinality of the set $\{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset\}$. These choice leads to the following stabilization 
+\begin{equation*}
+s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
+\end{equation*}
+being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{G}_h$.
+
+\begin{figure}\label{fig:gamma_generated}
+\centering
+\subfigure[$\Gamma_{\omega_j \cap \Lambda}$]
+{
+\input{./graphics/gamma_generated}
+}
+\qquad \qquad
+\subfigure[ $\Gamma_{\omega_j \cap \Lambda} \cap \omega_j$]{
+\input{./graphics/intersection}
+}
+\caption{$\Gamma_{\omega_j \cap \Lambda}$, the portion of $\Gamma$ generated by $\omega_j \cap \Lambda$ in (a) and the intersection between $\Gamma_{\omega_j \cap \Lambda}$ and $\omega_j$ in (b).
+Here for simplicity $\omega_j$ is represented as a single tetrahedron but actually it is a collection of tetrahedra as shown in Figure \ref{fig:patch}.}
+\end{figure}
+Thanks to the shape regularity of these extended patches, we have that the following discrete trace and Poincarè-type inequalites hold. More precisely, for any function $v\in H^1(\omega_j)$, 
 \begin{equation}\label{discr_trace_ineq}
-\|Tv\|_{\Gamma\cap \omega_j} \lesssim H^{-\frac 12} \|v\|_{L^2(\omega_j)}
+\|\trace v\|_{L^2(\Gamma\cap \omega_j)} \lesssim H^{-\frac 12} \|v\|_{L^2(\omega_j)}
 \end{equation}
 \begin{equation}\label{disc_poincare_ineq}
-\|v- \pi_Lv\|_{L^2(\omega_j)} \leq c_P H \|\nabla v\|_{L^2(\omega_j)},
+\|v- \mathcal{E}_{\patch} \pi_L\mtrace v\|_{L^2(\omega_j)} \leq c_P H \|\nabla v\|_{L^2(\omega_j)},
 \end{equation}
-where $\pi_L$ is defined as the projection onto piecewise constant functions on $F_j\cap \Lambda$.
- Moreover $\forall u_h \in X_h^\Omega$ we have the following average inequality 
+%where $\pi_L$ is a projection operator onto piecewise constant functions on $\patch\cap \Lambda$. In particular, for any $w \in L^2(\Lambda)$, we define
+where for any $w \in L^1(\Lambda)$, $ \mathcal{E}_{\patch}\pi_Lw \in L_h$ and with a little abuse of notation we denote as $\pi_L$ the operator
 \begin{equation*}
-\sum _j \|\avrc{T u_h}\|^2_{L^2(F_j \cap \Lambda),|\DD| } \leq \sum _j \|T u_h\|^2_{L^2(\omega_j\cap \Gamma)}.
+\pi_Lw_{|\patch \cap \Lambda} =\frac{1}{|\Gamma_{\patch\cap \Lambda}|}\int_{\patch\cap \Lambda}|\DD| w\quad \forall j,
 \end{equation*}   
-{\color{red} I think this inequality is valid but only globally.
-Indeed locally it is not guaranteed that the portion of $\Gamma$ corresponding to $F_j \cap \Lambda$ is contained in $\omega _j \cap \Gamma$}.
+whereas the operator $\mathcal{E}_{\patch}$ simply extends the constant $\pi_L\mtrace v_{|\patch \cap \Lambda}$ to $\omega _j$.
+Moreover $\forall u_h \in X^1_{h,0}(\Omega)$ we have the following average inequality 
+\begin{equation*}
+\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| } \leq \sum _j \|\trace  u_h\|^2_{L^2(\omega_j\cap \Gamma)}.
+\end{equation*}
+Indeed, by the definition of $\mtrace$ and Jensen inequality, we have
+\begin{multline*}
+\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| }
+= \sum _j\int_{\patch \cap \Lambda} |\DD| \mtrace u_h^2 
 \\
-These choices lead to the following stabilization 
+= \int_{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \trace u_h \right)^2
+\\
+(\text{Jensen})\leq \int_{\Lambda} \int_{\DD} (\trace u_h)^2
+= \int_{\Gamma} (\trace u_h)^2
+\\
+(\patch \cap \Gamma \text{ partition of } \Gamma)= \sum _j \int_{\patch \cap \Gamma} (\trace u_h)^2
+= \sum _j \|\trace u_h\|^2_{L^2(\patch \cap \Gamma)}.
+\end{multline*}
+
+\begin{lemma}\label{lemma:Lh_infsup}
+The space $L_h$ is inf-sup stable, namely $\forall {\lld}_h \in L_h$, $\exists \beta >0$ s.t.
 \begin{equation*}
-s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{T}_{h'}^{\Lambda}} \int_{\partial K} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
-\end{equation*}
-being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{T}_{h'}^{\Lambda}$.
-\begin{lemma}
-The space $L_h$ inf-sup stable, namely $\forall {\lld}_h \in L_h(\Lambda)$, $\exists \beta >0$ s.t.
-\begin{equation*}
-\sup_{\substack{v_h \in X_{h,1}^0(\Omega),\\ {\vd}_h \in X_{h',1}^0(\Lambda)}} \frac{\left(\avrc{T v_h} - {\vd}_h, {\lld} _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|{\lld}_h\|_{H^{-\frac 12}(\Lambda)}.
+\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\lld} _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|{\lld}_h\|_{H^{-\frac 12}(\Lambda)}.
 \end{equation*} 
@@
 %\begin{equation*}
-%\sup_{\substack{v_h \in X_{h,1}^0(\Omega),\\ {\vd}_h \in X_{h',1}^0(\Lambda)}} \frac{\left(\avrc{T v_h} - {\vd}_h, l _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|l_h\|_{H^{-\frac 12}(\Lambda)}.
+%\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',1}^0(\Lambda)}} \frac{\left(\avrc{T v_h} - {\vd}_h, l _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|l_h\|_{H^{-\frac 12}(\Lambda)}.
 %\end{equation*}
@@
 \begin{equation*} 
-\sup_{v_h \in X_{h,1}^0(\Omega)} \frac{\left(\avrc{T v_h} ,{\lld}_h\right)_{\Lambda, |\DD|}}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|{\lld}_h\|_{H^{-\frac 12}(\Lambda)}.
+\sup_{v_h \in X_{h,0}^1(\Omega)} \frac{\left(\mtrace v_h ,{\lld}_h\right)_{\Lambda, |\DD|}}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|{\lld}_h\|_{H^{-\frac 12}(\Lambda)}.
 \end{equation*} 
-Proving the last inequality it is equivalent to find the Fortin operator $\pi_F: H^1_0(\Omega) \rightarrow X_{h,1}^0(\Omega)$, such that 
+Proving the last inequality it is equivalent to find the Fortin operator $\pi_F: H^1_0(\Omega) \rightarrow X_{h,0}^1(\Omega)$, such that 
 \begin{equation*}
-\left(\avrc{T v} - \avrc{T \pi _F v}  , {\lld}_h\right)_{\Lambda, |\DD|}=0, \quad \forall v\in H^1_0(\Omega), \, {\lld}_h \in L_h(\Lambda)
+\left(\mtrace v - \mtrace \pi _F v  , {\lld}_h\right)_{\Lambda, |\DD|}=0, \quad \forall v\in H^1_0(\Omega), \, {\lld}_h \in L_h
 \end{equation*} 
@@
 \begin{equation*}
-\pi_F v = I_h v + \sum _j \alpha _j \varphi _j \qquad \text{with }\alpha_j =\frac{\int_{F_j \cap \Lambda}|\DD| (\avrc{Tv}-\avrc{TI_hv})}{\int_{F_j \cap \Lambda}|\DD|\avrc{T\varphi _j}}
+\pi_F v = I_h v + \sum _j \alpha _j \varphi _j \qquad \text{with }\alpha_j =\frac{\int_{\patch \cap \Lambda}|\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch \cap \Lambda}|\DD|\mtrace \varphi _j}
 \end{equation*}
-and $\varphi_j \in X_{h,1}^0(\Omega)$ s.t. supp$(\varphi_j)\subset \bar{\omega}_j$, $\varphi_j =0$ on $\partial \omega _j$ and 
-\begin{equation*}
- \int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}=O(H) \text{ and } \|\nabla \varphi\|_{L^2(\omega _j)}=O(1). 
-\end{equation*}
-This construction is always possible provided $H$ is sufficiently larger that $h$.
+where $I_h: H^1(\Omega) \rightarrow X_{h,0}^1$ denotes an $H^1(\Omega)$-stable interpolant
+and $\varphi_j \in X_{h,0}^1(\Omega)$ is such that supp$(\varphi_j)\subset \omega_j$, supp$(\trace \varphi _j) \subset \Gamma_{\patch\cap \Lambda}\cap \omega_j$, $\varphi_j =0$ on $\partial \omega _j$ and
+\begin{equation}\label{phi_properties}
+\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j=O(H) \text{ and } \|\nabla \varphi _j\|_{L^2(\omega _j)}=O(1). 
+\end{equation}
+We notice that supp$(\trace \varphi_j) \subset \Gamma_{\patch\cap \Lambda}\cap \omega_j$ ensures that $\mtrace \varphi_j \subset \omega_j\cap \Lambda$.
+Therefore, since for construction the interiors of $\omega_j\cap \Lambda$  are disjoint and $\varphi _j = 0 $ on $\partial \omega_j$,  the functions $\mtrace \varphi_j\, \forall j$ have all disjoint supports.
+This construction is always possible since meas$(\patch) = \mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda} \cap \omega_j)=\mathcal{O}(H)$, provided $H$ is sufficiently larger that $h$.
+Indeed, this guarantees that the functions $\varphi _j$ and their traces $\trace \varphi _j$ have a sufficiently large support so that they can be built in order to satisfy \eqref{phi_properties}.
 Then we have
 \begin{multline*}
-\left(\avrc{T v} - \avrc{T \pi _F v}  , {\lld}_h\right)_{\Lambda, |\DD|} 
-= \sum _j \int_{F_j\cap \Lambda} |\DD |\left[ \avrc{Tv}-\avrc{TI_hv}-\sum _i \alpha_i \avrc{T\varphi _i} \right]{\lld}_h \\
-=(\text{supp} \varphi \subset \omega_j) \sum _j \int_{F_j\cap \Lambda}|\DD| \left[ \avrc{Tv}-\avrc{TI_hv}-\alpha_j \avrc{T\varphi _j} \right]{\lld}_h\\
-=\sum _j \int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{T I_h v}) {\lld}_h - \frac{\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})}{\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}} \int_{F_j\cap \Lambda} |\DD|\avrc{T\varphi _j}{\lld}_h\\
-=(\text{using $l_h$ constant on $F_j\cap \Lambda$})\,0.
+\left(\mtrace v - \mtrace \pi _F v  , {\lld}_h\right)_{\Lambda, |\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD |\left[ \mtrace v-\mtrace I_h v-\sum _i \alpha_i \mtrace \varphi _i \right]{\lld}_h \\
+(\text{supp} (\mtrace \varphi _i )\subset \omega _i\cap \Lambda \, \forall i)  =\sum _j \int_{\patch\cap \Lambda}|\DD| \left[ \mtrace v-\mtrace I_h v-\alpha_j \mtrace \varphi _j \right]{\lld}_h\\
+=\sum _j \int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\lld}_h - \frac{\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi _j} \int_{\patch\cap \Lambda} |\DD|\mtrace \varphi _j{\lld}_h\\
+(\text{using $l_h$ constant on $\patch\cap \Lambda$})=0.
 \end{multline*}
-Concerning the continuity of $\pi_F$, we have
+Concerning the continuity of $\pi_F$, we exploit the assumptions that the interiors of $\patch$ are disjoint and supp$(\varphi _j) \subset \patch$ and we have
 \begin{multline*}
-\|\nabla \pi_F v \|_{L^2(\Omega)} \leq \|\nabla I_h v\|_{L^2(\Omega)} + \left(\sum_j|\alpha_j|^2\|\nabla \varphi _j\|^2_{L^2(\bar{\omega}_j)}\right)^{\frac 12}\\
-(\text{stability of }I_h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \left(\sum_j|\alpha_j|^2\|\nabla \varphi _j\|^2_{L^2(\bar{\omega}_j)}\right)^{\frac 12}
+\|\nabla \pi_F v \|_{L^2(\Omega)} \leq \|\nabla I_h v\|_{L^2(\Omega)} + \left(\sum_j\alpha_j^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\right)^{\frac 12}\\
+(\text{stability of }I_h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \left(\sum_j\alpha_j^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\right)^{\frac 12}
 \end{multline*}
-and for the second term we have
+and for the second term 
 \begin{multline*}
-\sum_j|\alpha_j|^2\|\nabla \varphi _j\|^2_{L^2(\bar{\omega}_j)}\leq
+\sum_j \alpha_j ^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\leq
 \\
-\left(\text{using }\|\nabla \varphi _j\|=O(1)\right) \lesssim  \sum_j \frac{\left(\left|\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})\right|\right)^2}{\left(\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}\right)^2}
+\left(\text{using }\|\nabla \varphi _j\|_{{L^2(\omega_j)}}=O(1)\right) \lesssim  \sum_j \frac{\left(\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)\right)^2}{\left(\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j \right)^2}
 \\
-\left(\text{since }\left|\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}\right|=O(H)\right) \lesssim \frac {1}{H^2} \sum_j \left(\left|\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})\right| \right)^2
+\left(\text{since }\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j=O(H)\right) \lesssim \frac {1}{H^2} \sum_j \left(\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_hv)\right)^2
 \\
-(\text{Jensen}) \lesssim  \frac {1}{H^2} \sum_j |F_j\cap \Lambda| \int_{F_j\cap \Lambda} |\DD|^2(\avrc{Tv}-\avrc{TI_hv})^2
+(\text{Jensen}) \lesssim  \frac {1}{H^2} \sum_j |\patch\cap \Lambda| \int_{\patch\cap \Lambda} |\DD|^2(\mtrace v-\mtrace I_h v)^2
 \\
-(\text{being }|F_j\cap \Lambda| \leq H+h)\lesssim  \frac {1}{H} \sum_j \| \avrc{Tv}-\avrc{TI_hv}\|^2_{L^2(F_j\cap \Lambda), |\DD|}
+(\text{being }|\patch\cap \Lambda| \leq cH)\lesssim  \frac {1}{H} \sum_j \| \mtrace (v-I_h v)\|^2_{L^2(\patch\cap \Lambda), |\DD|}
 \\
-(\text{average inequality}) \lesssim  \frac {1}{H} \sum_j \| T(v-I_hv)\|^2_{L^2(\omega _j\cap \Gamma)}  
+(\text{average inequality}) \lesssim  \frac {1}{H} \sum_j \| \trace(v-I_h v)\|^2_{L^2(\omega _j\cap \Gamma)}  
 \\
@@
 \vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_{h'}(\Lambda) }
-= \|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|} + \|\avrc{Tu_h} - {\ud}_h\|^2_{-\frac 12, h, \Lambda, |\DD|},
+= \|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|} + \|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|},
 \end{equation*}
-where $\|\avrc{Tu_h} - {\ud}_h\|^2_{-\frac 12, h, \Lambda, |\DD|} = \|h^{\frac 12} (\avrc{Tu_h} - {\ud}_h)\|^2_{L^2(\Lambda), |\DD|} $. Then, we have the following lemma. 
+where $\|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|} = \|h^{-\frac 12} (\mtrace u_h - {\ud}_h)\|^2_{L^2(\Lambda), |\DD|} $. Then, we have the following lemma. 
 \begin{lemma}
@@
 \begin{proof} 
-Concerning the coercivity property \eqref{stab_coercivity}, we have to show that $\forall [u_h, {\ud}_h]$, there esists $\xi_h \in Q_h(\Lambda)$ s.t.
+Concerning the coercivity property \eqref{stab_coercivity}, we have to show that $\forall [u_h, {\ud}_h]$, there esists $\xi_h \in Q_h$ s.t.
 \begin{multline*}
-(u_h,u_h)_{H^1(\Omega)}+ ({\ud}_h, {\ud}_h)_{H^1(\Lambda), |\D|} +   (\avrc{Tu_h} - {\ud}_h, \xi_h)_{\Lambda,|\DD|} \\
-\geq \alpha_{\xi}(\|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|}+ \|\avrc{Tu_h} - {\ud}_h\|^2_{-\frac 12, h, \Lambda, |\DD|}.
+(u_h,u_h)_{H^1(\Omega)}+ ({\ud}_h, {\ud}_h)_{H^1(\Lambda), |\D|} +   (\mtrace u_h - {\ud}_h, \xi_h)_{\Lambda,|\DD|} \\
+\geq \alpha_{\xi}(\|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|}+ \|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|}.
 \end{multline*}
@@
 \begin{equation*}
-{\xi_h}_{|F_j\cap \Lambda}=\delta \frac 1H \pi_L(\avrc{Tu_h}-{\ud}_h) \qquad \text{with } \pi_L(\avrc{Tu_h}-{\ud}_h) =\frac{1}{|\Gamma_{F_j\cap \Lambda}|}\int_{F_j\cap \Lambda}|\DD| (\avrc{Tu_h}- {\ud}_h),
+{\xi_h}_{|\patch\cap \Lambda}=\delta \frac 1H \pi_L(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}
 \end{equation*}
-being $\Gamma_{F_j\cap \Lambda}$ the portion of $\Gamma$ with centerline $F_j\cap \Lambda$. 
-Actually, $\xi_h\in L_h(\Lambda) \subset Q_h(\Lambda)$. Then,
+and we recall that 
+\begin{equation*}
+\pi_L(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}=\frac{1}{|\Gamma_{\patch\cap \Lambda}|}\int_{\patch\cap \Lambda}|\DD| (\mtrace u_h- {\ud}_h).
+\end{equation*} 
+Actually, $\mathcal{E}_{\patch}\xi_h\in L_h \subset Q_h$. Then,
 \begin{multline*}
-\left( \avrc{Tu_h} - {\ud}_h, \xi _h \right)_{\Lambda,|\DD|} 
-= \sum_j \int_{F_j\cap \Lambda} |\DD|( \avrc{Tu_h} - {\ud}_h)\xi_h
+\left( \mtrace u_h - {\ud}_h, \xi _h \right)_{\Lambda,|\DD|} 
+= \sum_j \int_{\patch\cap \Lambda} |\DD|(\mtrace u_h - {\ud}_h)\xi_h
 \\
-= \delta \frac{1}{H} \sum_j \int_{F_j\cap \Lambda}|\DD| (\pi_L( \avrc{Tu_h} - {\ud}_h) )^2
+(\text{definition of $\xi_h$})= \delta \frac{1}{H}\sum_j \pi_L( \mtrace u_h - {\ud}_h)\int_{\patch\cap \Lambda} |\DD|(\mtrace u_h - {\ud}_h)
 \\
-(\text{orthogonality of $\pi_L$}) =  \delta \frac{1}{H} \|(\pi_L-\mathcal{I})(\avrc{Tu_h} - {\ud}_h)\|^2_{L^2(F_j\cap \Lambda),|\DD|} + \delta \frac{1}{H} \|\avrc{Tu_h} - {\ud}_h\|^2_{L^2(F_j\cap \Lambda),|\DD|}
+= \delta \frac{1}{H} \sum_j \int_{\patch\cap \Lambda}|\DD| (\pi_L( \mtrace u_h - {\ud}_h) )^2
 \\
-\geq -\delta \frac 1H \sum_j \|(\pi_L - \mathcal{I})\avrc{Tu_h}\|^2_{L^2(F_j\cap \Lambda), |\DD|}
-- \delta \frac 1H \sum_j \|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(F_j\cap \Lambda),|\DD|}
+(\text{orthogonality of $\pi_L$}) = - \delta \frac{1}{H} \|(\pi_L-\mathcal{I})(\mtrace u_h - {\ud}_h)\|^2_{L^2(\patch\cap \Lambda),|\DD|} + \delta \frac{1}{H} \|\mtrace u_h - {\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|}
 \\ 
-+ \delta \frac 1H \sum_j \|\avrc{Tu_h}-{\ud}_h\|^2_{L^2(F_j\cap \Lambda),|\DD|}. 
+\geq -2\delta \frac 1H \sum_j \|(\pi_L - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda), |\DD|}
+-2 \delta \frac 1H \sum_j \|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|}
+\\ 
++ \delta \frac 1H \sum_j \|\mtrace u_h-{\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|}. 
 \end{multline*}
@@
 \begin{multline*}
-\sum _j  \|(\pi_L - \mathcal{I})\avrc{Tu_h}\|^2_{L^2(F_j\cap \Lambda),|\DD|} =\sum _j \int _{F_j \cap \Lambda} |\DD| (\pi_L \avrc{Tu_h}- \avrc{Tu_h})^2
+\sum _j  \|(\pi_L - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} =\sum _j \int _{\patch \cap \Lambda} |\DD| (\pi_L \mtrace u_h- \mtrace u_h)^2
 \\
-(\text{Average inequality)} \leq \sum _j  \int_{\omega _j \cap \Gamma} (\pi_L \avrc{Tu_h} -Tu_h)^2 
+(\text{Average inequality)} \leq \sum _j  \int_{\omega _j \cap \Gamma} (\ext \pi_L \mtrace u_h -\trace u_h)^2 
 \\
-(\text{trace inequality}) \leq \sum _j  \frac 1H \int_{\omega_j}(\pi_L \avrc{Tu_h} - u_h)^2 
+(\text{trace inequality}) \leq \sum _j  \frac 1H \int_{\omega_j}(\mathcal{E}_{\patch} \pi_L \mtrace u_h - u_h)^2 
 \\ 
@@
 \begin{multline*}
-\sum _j \|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(F_j\cap \Lambda),|\DD|} = \sum _j \int_{F_j\cap \Lambda} |\DD| (\pi_L {\ud}_h -{\ud}_h)^2
+\sum _j \|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD| (\pi_L {\ud}_h -{\ud}_h)^2
 \\
-(\text{Poincare, \cite[Corollary B.65]{MR2050138}})\lesssim \sum _j  H^2 c_P^2 \int_{F_j\cap \Lambda} |\DD|(\nabla {\ud}_h)^2
+(\text{Poincare, \cite[Corollary B.65]{MR2050138}})\lesssim \sum _j  H^2 c_P^2 \int_{\patch\cap \Lambda} |\DD|(\nabla {\ud}_h)^2
 \\
-(\text{since $H$ is fixed, we can find a constant s.t. } H|\DD| \lesssim |\D|) \lesssim \sum _j H c_P^2  \int_{F_j\cap \Lambda} |\D|(\nabla {\ud}_h)^2 
+(\text{since $H$ is fixed, we can find a constant s.t. } H|\DD| \lesssim |\D|) \lesssim \sum _j H c_P^2  \int_{\patch\cap \Lambda} |\D|(\nabla {\ud}_h)^2 
 \\
-\lesssim \sum _j H c_P^2  \|\nabla {\ud}_h\|^2_{L^2(F_j\cap \Lambda),|\D|}.
+\lesssim \sum _j H c_P^2  \|\nabla {\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\D|}.
 \end{multline*}
-{\color{red} N.B. we are using a kind of weigthed Poincare inequality, check... I think it should work because I can do something like this
-\begin{multline*}
-\int_{F_j \cap \Lambda} |\DD| u^2 \leq 
-max |\DD| \int_{F_j \cap \Lambda} u^2 \leq
-max |\DD| \int_{F_j \cap \Lambda} (\nabla u)^2 =
-\frac{max |\DD|}{min|\DD|} min|\DD| \int_{F_j \cap \Lambda} u^2 \leq\\
-\frac{max |\DD|}{min|\DD|}  \int_{F_j \cap \Lambda} |\DD| u^2 
-\end{multline*}
-}\\
+%{\color{red} N.B. we are using a kind of weigthed Poincare inequality, check... I think it should work because I can do something like this
+%\begin{multline*}
+%\int_{\patch \cap \Lambda} |\DD| u^2 \leq 
+%max |\DD| \int_{\patch \cap \Lambda} u^2 \leq
+%max |\DD| \int_{\patch \cap \Lambda} (\nabla u)^2 =
+%\frac{max |\DD|}{min|\DD|} min|\DD| \int_{\patch \cap \Lambda} (\nabla u)^2 \leq\\
+%\frac{max |\DD|}{min|\DD|}  \int_{\patch \cap \Lambda} |\DD| (\nabla u)^2 
+%\end{multline*}
+%}\\
 Therefore, we obtain
@@
 \geq \\
-(1-\delta c_P^2) \|\nabla u_h\|^2_{L^2(\Omega)} + (1- \delta c_P^2) \|\nabla {\ud}_h\|^2_{L^2(\Lambda), |\D|}
-+\delta c_H  \|\avrc{Tu_h}-{\ud}_h\|^2_{-\frac 12,h,\Lambda, |\DD|}
+(1-2\delta c_P^2) \|\nabla u_h\|^2_{L^2(\Omega)} + (1- 2\delta c_P^2) \|\nabla {\ud}_h\|^2_{L^2(\Lambda), |\D|}
++\delta c_H  \|\mtrace u_h-{\ud}_h\|^2_{\frac 12,h,\Lambda, |\DD|}
 \end{multline*}
-and choosing $\delta=\frac{1}{2c_P^2}$ we obtain the coercivity inequality.\\
+and choosing $\delta=\frac{1}{4c_P^2}$ we obtain the coercivity inequality.\\
 Concerning the stability inequality \eqref{stab_stability}, the proof is analogous to the one in \cite{burman2014}.
 \end{proof}
+
+\begin{remark}
+We notice that if we choose $Q_h=X_{h',0}^1(\Lambda)$, the constant in the inf-sup inequality  \eqref{eq:infsup_discrete} depends on the mesh size $h'$. Indeed,
+\begin{multline}
+\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\lld} _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}}
+\geq \sup_{\substack{{\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(- {\vd}_h, {\lld} _h\right)_{\Lambda, |\DD|}}{\|{\vd}_h\|_{H^1(\Lambda)}}
+\geq \frac{{\|\lld} _h\|^2_{L^2(\Lambda)}}{\|{\vd}_h\|_{H^1(\Lambda)}} \\
+( \text{inverse inequality} )\geq \frac{{h'}^2}{c_I} \|{\lld}_h\|_{L^2(\Lambda)}
+\geq  \frac{{h'}^2}{c_I} \|{\lld}_h\|_{H^{-\frac 12},(\Lambda)}
+\end{multline}
+being $c_I$ the constant in the inverse inequality
+\begin{equation*}
+\|{\lld}_h\|_{H^1(\Lambda)} \leq \frac{c_I} {{h'}^2} \|{\lld}_h\|_{L^2(\Lambda)}. 
+\end{equation*}
+\end{remark}

### 2019-08-01 solver/img/conform.tex
work on solver note

\documentclass{standalone}

\usepackage{tikz}
\usetikzlibrary{shapes, snakes, patterns, arrows}
\usetikzlibrary{calc}

\begin{document}

\begin{tikzpicture}[scale=0.60]
      % Minus
  \draw[black] (0, 0) rectangle (3, 3);
  \draw[black] (0, 0) -- (3, 3);
  \node[mark size=3pt, color=black] at (0, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (3, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (0, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (3, 3) {\pgfuseplotmark{*}};

  \draw[black] (6, 0) rectangle (9, 3);
  \draw[black] (6, 0) -- (9, 3);
  \node[mark size=3pt, color=black] at (6, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (9, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (6, 3) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=black] at (9, 3) {\pgfuseplotmark{*}};

  \draw[green!50!black, very thick] (3, 0) -- (3, 3);
  \draw[green!50!black, very thick] (6, 0) -- (6, 3);
  \draw[green!50!black, very thick] (4.5, 0) -- (4.5, 3);
  %\node[green!50!black, below] at (4.5, 0) {$\Gamma$};

  \draw[white!50!blue, very thick] (4, 0) -- (4, 3);
  \node[mark size=3pt, color=white!50!blue] at (4, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=white!50!blue] at (4, 3) {\pgfuseplotmark{*}};
  \draw[thin, black, dashed] (4, 1) -- (4.5, 1);
  \draw[thin, black, dashed] (4, 2) -- (4.5, 2);
  %\node[white!50!blue, above] at (4, 3) {$\hat{\Gamma}_h$};

  \draw[white!50!red, very thick] (5, 0) -- (5, 3);
  \node[mark size=3pt, color=white!50!red] at (5, 0) {\pgfuseplotmark{*}};
  \node[mark size=3pt, color=white!50!red] at (5, 3) {\pgfuseplotmark{*}};
  \draw[thin, black, dashed] (5, 1) -- (4.5, 1);
  \draw[thin, black, dashed] (5, 2) -- (4.5, 2);
  %\node[white!50!red, above] at (5, 3) {${\Gamma}_h$};
\end{tikzpicture}

\end{document}

### 2019-08-01 solver/problem_omega.tex
work on solver note

\begin{table}
    \scriptsize{% (i)
  \begin{center}
    \begin{tabular}{c|cccc||cc}
      \hline
      \multirow{2}{*}{$h/H$} & \multicolumn{4}{c||}{$\mathcal{B}$} & \multicolumn{2}{c}{$\mathcal{B}_{h}$}\\
      \cline{2-7}
      & $\norm{u-u_h}_1$ & $\norm{\lambda-\lambda_h}_0$ & \# & $\kappa$ & \# & $\kappa$\\
      \hline
1        & 8.62E-1(--)  & 1.04E0(--)    &   21 & 7.8  & 24 & 20.9 \\
$2^{-1}$ & 4.4E-1(0.99) & 3.8E-1(1.46)  & 24   & 7.9  & 41 & 21.1 \\
$2^{-2}$ & 2.2E-1(1.00) & 1.4E-1(1.49)  & 22   & 7.9  & 46 & 21.2 \\
$2^{-3}$ & 1.1E-1(1.00) & 4.8E-2(1.50)  & 22   & --   & 47 & --   \\
$2^{-4}$ & 5.5E-2(1.00) & 1.7E-2(1.50)  & 21   & --   & 48 & --   \\
$2^{-5}$ & 2.7E-2(1.00) & 6.0E-3(1.50)  & 21   & --   & 45 & --   \\
\hline
  \end{tabular}
  \end{center}
    }
    \vspace{5pt}
  \scriptsize{%(ii)
    \begin{minipage}{0.49\textwidth}
  \begin{center}
    \begin{tabular}{c|cccc||cc}
      \hline
      \multirow{2}{*}{$h/H$} & \multicolumn{4}{c||}{$\mathcal{B}$} & \multicolumn{2}{c}{$\mathcal{B}_{h}$}\\
      \cline{2-7}
      & $\norm{u-u_h}_1$ & $\norm{\lambda-\lambda_h}_0$ & \# & $\kappa$ & \# & $\kappa$\\
      \hline
1       & 8.6E-1(--) & 5.4E-1(--)    & 29 & 6.5 & 25 & 16.9\\
$2^{-1}$ & 4.3E-1(0.98) & 2.3E-1(1.20)& 29 & 6.6 & 31 & 17.7\\
$2^{-2}$ & 2.2E-1(1.00) & 1.0E-1(1.19)& 28 & 6.6 & 34 & 18.1\\
$2^{-3}$ & 1.1E-1(1.00) & 4.7E-2(1.13)& 28 & --   & 37 & --   \\
$2^{-4}$ & 5.5E-2(1.00) & 2.2E-2(1.08)& 28 & --   & 37 & --   \\
$2^{-5}$ & 2.7E-2(1.00) & 1.1E-2(1.04)& 27 & --   & 37 & --   \\
\hline
  \end{tabular}
  \end{center}
  \end{minipage}
  }
    \scriptsize{%(iii)
    \begin{minipage}{0.49\textwidth}
  \begin{center}
    \begin{tabular}{c|cccc||cc}
      \hline
      \multirow{2}{*}{$h/H$} & \multicolumn{4}{c||}{$\mathcal{B}$} & \multicolumn{2}{c}{$\mathcal{B}_{h}$}\\
      \cline{2-7}
      & $\norm{u-u_h}_1$ & $\norm{\lambda-\lambda_h}_0$ & \# & $\kappa$ & \# & $\kappa$\\
      \hline
1       & 8.6E-1(--) & 5.4E-1(--)  & 31 & 6.7 & 21 & 2.5\\
$2^{-1}$ & 4.3E-1(0.98) & 2.3E-1(1.20)& 32 & 6.6 & 21 & 2.5\\
$2^{-2}$ & 2.2E-1(1.00) & 1.0E-1(1.19)& 31 & 6.6 & 21 & 2.5\\
$2^{-3}$ & 1.1E-1(1.00) & 4.7E-2(1.13)& 30 & --  & 20 & --  \\
$2^{-4}$ & 5.5E-2(1.00) & 2.2E-2(1.08)& 28 & --  & 20 & --  \\
$2^{-5}$ & 2.7E-2(1.00) & 1.1E-2(1.04)& 28 & --  & 18 & --  \\
      \hline
  \end{tabular}
  \end{center}
  \end{minipage}
    }
    \vspace{5pt}
    \\
  \scriptsize{%(iv)
    \begin{minipage}{0.49\textwidth}
  \begin{center}
    \begin{tabular}{c|cccc}
      \hline
      \multirow{2}{*}{$h/H$} & \multicolumn{4}{c|}{$\mathcal{B}$}\\
      \cline{2-5}
      & $\norm{u-u_h}_1$ & $\norm{\lambda-\lambda_h}_0$ & \# & $\kappa$\\
      \hline
1       & 1.7E0(--)    & 2.0E0(--)    & 22 &4.5\\
$2^{-1}$ & 1.0E0(0.71)  & 1.2E0(0.71)  & 27 &5.1\\
$2^{-2}$ & 5.9E-1(0.78) & 7.7E-1(0.69) & 29 &5.4\\
$2^{-3}$ & 3.3E-1(0.85) & 4.9E-1(0.64) & 29 &-- \\
$2^{-4}$ & 1.7E-1(0.91) & 3.3E-1(0.59) & 28 &-- \\
$2^{-5}$ & 9.1E-2(0.95) & 2.2E-1(0.55) & 26 &-- \\
      \hline
  \end{tabular}
  \end{center}
  \end{minipage}
  }
  \scriptsize{%(iv)
    \begin{minipage}{0.49\textwidth}
  \begin{center}
    \begin{tabular}{c|cccc}
      \hline
      \multirow{2}{*}{$h/H$} & \multicolumn{4}{c|}{$\mathcal{B}$}\\
      \cline{2-5}
      & $\norm{u-u_h}_1$ & $\norm{\lambda-\lambda_h}_0$ & \# & $\kappa$\\
      \hline
1       & 2.0E0(--) & 1.3E0(--)        & 24 & 5.8\\
$2^{-1}$ & 1.4E0(0.53) & 7.0E-1(0.93)   & 29 & 7.1\\
$2^{-2}$ & 9.1E-1(0.62) & 3.5E-1(1.02)  & 34 & 8.0\\
$2^{-3}$ & 5.7E-1(0.68) & 1.6E-1(1.08)  & 36 & -- \\
$2^{-4}$ & 3.5E-1(0.71) & 7.9E-2(1.05)  & 36 & -- \\
$2^{-5}$ & 2.2E-1(0.69) & 4.3E-2(0.89)  & 34 & -- \\
      \hline
  \end{tabular}
  \end{center}
  \end{minipage}
  }
%%%%%%%%%%%%%
  \caption{}
  \label{}
\end{table}

### 2019-08-01 solver/solver.tex
work on solver note

% SIAM Article Template
\documentclass[r]{siamart171218}
% Packages and macros go here
\usepackage[english]{babel}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{array}
\usepackage{epsfig}
\usepackage{float}
\usepackage{fullpage}
\usepackage{color}
\usepackage{enumitem}  
\usepackage{epstopdf}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{standalone}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{color}

\usepackage{ifpdf}
\ifpdf
\DeclareGraphicsRule{*}{mps}{*}{}
\fi

\DeclareRobustCommand{\figlegend}[1]{%
  \raisebox{0.5ex}{
    \tikz[]{%
      \fill[very thick, color=#1] (0, 0) rectangle (0.3, 0.1);
    }%
  }
}
% Title. If the supplement option is on, then "Supplementary Material"
% is automatically inserted before the title.
%\title{On the weak coupling of 3D and 1D second order elliptic problems}
\title{Notes on robust solvers for systems of coupled multiscale PDEs}

% Authors: full names plus addresses.
\author{
Miroslav Kuchta, Federica Laurino, Kent-Andre Mardal, Paolo Zunino,\thanks{Authors are listed in alphabetical order}
}

\newcommand{\Miro}[1]{\textcolor{cyan}{Miro: #1}}

\begin{document}

\maketitle

% REQUIRED
\begin{abstract}
  We summarize numerical experiments related to the task of developing
  mesh and parameter indepent solvers for the 3$d$-1$d$ coupled diffusion problems.
  These are personal notes written to keep track of the developments on this
  topic and are to be kept confidential.
\end{abstract}

% REQUIRED
\begin{keywords}
elliptic problems, high dimensionality gap, essential coupling conditions, Lagrange multipliers
\end{keywords}

% REQUIRED
\begin{AMS}
n.a.
\end{AMS}

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>

\newcommand{\semi}[1]{\lvert{#1}\rvert}
\newcommand{\norm}[1]{\lVert{#1}\rVert}
\newcommand{\jump}[1]{\ensuremath{[\![#1]\!]} }
\newcommand{\avg}[1]{\ensuremath{\left\{\!\left\{#1\right\}\!\right\}} }
\def\ud{u_{\odot}}
\def\vd{v_{\odot}}
\def\ld{\lambda_{\odot}}
\def\md{\mu_{\odot}}
\def\lld{l_{\odot}}
\def\uf{u_{\ominus}}
\def\up{u_{\oplus}}
\def\eps{\epsilon}
\def\nn{\boldsymbol n}
\def\rr{\boldsymbol r}
\def\RR{\boldsymbol R}
\def\kk{\boldsymbol k}
\def\ss{\boldsymbol s}
\def\uu{\boldsymbol u}
\def\vv{\boldsymbol v}
\def\xx{\boldsymbol x}
\def\bu{\overline{u}}
\def\bv{\overline{v}}
\def\tu{\widetilde{u}}
\def\tv{\widetilde{v}}
\def\TT{\boldsymbol T}
\def\NN{\boldsymbol N}
\def\BB{\boldsymbol B}
\def\ttu{\widetilde{\widetilde{u}}}
\def\ttv{\widetilde{\widetilde{v}}}
\def\cv{\check{v}}
\def\mesh{{\cal T}^h}
\def\ball{{\cal B}}
\def\R{\mathbb{R}}
\def\D{\mathcal{D}}
\def\DD{\partial\mathcal{D}}
\def\trace{{\mathcal{T}_\Gamma}}
\def\mtrace{{\overline{\mathcal{T}}_\Lambda}}
\def\ext{\mathcal{E}_\Gamma}
\def\ide{\mathcal{I}}
\def\ii{\hat{\imath}}
\newcommand{\avrd}[1]{\overline{\overline{#1}}}
\newcommand{\avrc}[1]{\overline{#1}}
\newcommand{\refe}[1]{{#1}_{\mathrm{ref}}}

\newcommand{\vertiii}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 
    \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}{Property}[section]
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

\section{Introduction}\label{sec:intro}

Let $\langle \cdot , \cdot \rangle_\Lambda$ denote the duality pairing between 
$H^\frac12_{00}(\Lambda)$ and $H^{-\frac12}(\Lambda)$. This note concerns robust
solvers for the problem:
Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
\begin{subequations}\label{eq:problem2}
\begin{align}
&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
+  \langle \mtrace v - \vd, \ld \rangle_{H^{-\frac12}(\Lambda), |\DD|} 
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)\,,
\\
&   \langle \mtrace u -   \ud, \md \rangle_{H^{-\frac12}(\Lambda),|\DD|} = 0
\quad \forall \md \in H^{-\frac12}(\Lambda)\,,
\end{align}
\end{subequations}
where $\mtrace$ denotes the composition of operators $\avrc{(\cdot)} \circ \trace $.
In particular, we aim at devising algorithms that are robust with respect to
the averaging radius in $\mtrace$.

The (continuous) problem \eqref{eq:problem2} is well posed, in particular
the Lagrange multiplier $\md$ exists in a suitable fractional Sobolev space on
$\Lambda$. Following operator preconditioning framework \cite{mardal2011preconditioning} preconditioners
for the problem rely on fractional Sobolev norms. At the moment the stability
of the discrete problem can be shown using the Lagrange multiplier defined
in the space of piecewise constant functions over the collection of tetrahedra
(of the 3$d$ mesh) that are intersected by $\Lambda$. However, it is not clear
how fractional Sobolev norms on such a space should be constructed (in contrast
to the case where the multiplier is defined on $\Lambda$). We shall therefore
establish the preconditioners for the \emph{discrete} problem using different
norms than those used in the analysis of the \emph{continuous} one.

As a stepping stone to \eqref{eq:problem2} we shall consider a related
2$d$-1$d$ problem\\
%Stong
\begin{minipage}{0.57\textwidth}
  \begin{equation}\label{eq:coupled}
    \begin{aligned}
      -\Delta u^i &= f &\mbox{ in }\Omega^{i}, i\in\left\{+, -\right\},\\
      \jump{u} &= 0 &\mbox{ on }\Gamma,\\
      -\Delta \hat{u} +\hat{u} - \jump{\nabla u\cdot n}&= \hat{f} &\mbox{ on }\Gamma,\\
      \epsilon u - \hat{u} &= h&\mbox{ on }\Gamma.\\
    \end{aligned}
\end{equation}
\null
\par\xdef\tpd{\the\prevdepth}
\end{minipage}
\hfill
\begin{minipage}{0.37\textwidth}
  \begin{figure}[H]
    \begin{center}
\begin{tikzpicture}
  \node[black, fill=white, opacity=0.9] at (1, 2) {$\Omega^{-}$};
  \node[black, fill=white, opacity=0.9] at (3, 2) {$\Omega^{+}$};

  % Boundaries
  \draw[red!60!white] (0, 0) -- (0, 4);
  \draw[red!60!white] (4, 0) -- (4, 4);
  \node[red!60!white, opacity=0.9, right] at (4, 1) {$\Gamma_D$};

  \draw[blue!60!white] (0, 0) -- (4, 0);
  \draw[blue!60!white] (0, 4) -- (4, 4);
  \node[blue!60!white, opacity=0.9, below] at (3, 0) {$\Gamma_N$};

  \draw[black, very thick] (2, 0) -- (2, 4);
  \draw[->, black] (2, 1) -- (3, 1);
  \node[fill=white, opacity=0.9, above] at (2.5, 1) {$n$};
  \node[fill=white, opacity=0.9, right] at (2.025, 2) {$\Gamma$};
\end{tikzpicture}
    \end{center}
    %\vspace{-20pt}
    \caption{Schematic domain of coupled multiscale problem.}
    \label{fig:coupled_domain}
    %\vspace{5pt}    
\end{figure}
\end{minipage}
%
Here \eqref{eq:coupled} shall be equipped with Dirichlet boundary conditions
(for $u^i$) on $\Gamma_D$, while Neumann conditions are used on $\Gamma_N$
(for both the unknowns). Note that the role of constant parameter $\epsilon$ is similar
to that of averaging radius in \eqref{eq:problem2}.

Let $\Omega=\Omega^{+}\cup\Omega^{-}$. Introducing a Lagrange multiplier
$p=\epsilon^{-1}\jump{\nabla u \cdot n}\in Q=H^{-1/2}(\Gamma)$
the weak form of \eqref{eq:coupled} reads: Find $u\in V=H^1_{0, \Gamma_D}(\Omega)$,
$\hat{v}\in\hat{V}=H^1(\Gamma)$, $p\in Q$ such that
%
\begin{equation}\label{eq:coupled_weak}
  \begin{aligned}
    &\int_{\Omega}\nabla u\cdot \nabla v &\phantom{+\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &+\epsilon\int_{\Gamma} p v &= \int_{\Omega}f v \quad &\forall v\in V,\\
    &\phantom{\int_{\Omega}\nabla u\cdot \nabla v} &+{\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v} + \hat{u}\hat{v}} &-\int_{\Gamma} p\hat{v} &= \int_{\Gamma}\hat{f}\hat{v} \quad &\forall \hat{v}\in \hat{V},\\
    &\epsilon\int_{\Gamma}u q &-\int_{\Gamma}\hat{u}q &\phantom{-\int{\Gamma}q\hat{v}} &= \int_{\Gamma}h q \quad &\forall q\in Q.
  \end{aligned}
\end{equation}

In the following it will be convenient to work with the operator form of
\eqref{eq:coupled_weak}. In particular the left-hand-side defines an operator
%
\begin{equation}\label{eq:operator2d}
  \mathcal{A} = \begin{pmatrix}
    -\Delta_{\Omega} & & -\epsilon T^{\prime}\\
    & -\Delta_{\Gamma} + I & I\\
    -\epsilon T & I & \\
  \end{pmatrix} =
  \begin{pmatrix}
    A_2 &  & B_2'\\
    & A_1 & -B_1'\\
    B_2 & -B_1 & \\
   \end{pmatrix}.
\end{equation}
In \cite{kuchta2016preconditioners} it is shown that $\mathcal{A}$ is an
isomorphism from $W$ to its dual space where
\[
W=H^1(\Omega)_{0, \Gamma_D}\times H^1{(\Gamma)}\times(\epsilon H^{-1/2}(\Gamma)\cap H^{-1}(\Gamma)).
\]
It is further shown that discretization in terms of continuous linear Lagrange
elements (P1) for all the unknowns is inf-sup stable and in turn the diagonal operator
\begin{equation}\label{eq:P1_precond}
\mathcal{B}=\text{diag}(-\Delta_{\Omega}, -\Delta_{\Gamma}+I, \epsilon^2(-\Delta_{\Gamma})^{-1/2}+(-\Delta_{\Gamma}+I)^{-1})^{-1}
\end{equation}
is a robust preconditioner for $\mathcal{A}$. For the sake of completness
(and verifying the implementation) Table \ref{tab:P1} shows the number of
MinRes iterations and condition numbers of the preconditioned problem for
different levels of refinements and values of the parameter $\epsilon$. The
stability is evident.
%
\begin{table}
    \footnotesize{
      \begin{minipage}{0.49\textwidth}
          \begin{center}
            \begin{tabular}{c|cccc} \hline
              \multirow{2}{*}{$\epsilon$} & \multicolumn{4}{c}{$h$}\\
              \cline{2-5}
 &   $2^{-2}$  & $2^{-3}$ & $2^{-4}$ & $2^{-5}$   \\  
\hline
$10^{6}$ &	7.73&	7.82&	7.86&	7.87\\
$10^{4}$ &	7.73&	7.82&	7.86&	7.87\\
$10^{2}$   &	7.73&	7.82&	7.86&	7.87\\
1     &	7.39&	7.79&	8.01&	8.13\\
$10^{-2}$  &	2.62&	2.63&	2.63&	2.65\\
$10^{-4}$ &	2.62&	2.62&	2.62&	2.62\\
$10^{-6}$ &	2.62&	2.62&	2.62&	2.62\\
\hline
\end{tabular}
\end{center}
      \end{minipage}
    }
          \footnotesize{
            \begin{minipage}{0.49\textwidth}
              \begin{center}
            \begin{tabular}{c|cccccc} \hline
              \multirow{2}{*}{$\epsilon$} & \multicolumn{6}{c}{$h$}\\
              \cline{2-7}
 &   $2^{-3}$ & $2^{-4}$ & $2^{-5}$ & $2^{-6}$ & $2^{-7}$ & $2^{-8}$  \\  
              \hline
$10^{6}$ & 21 & 22 & 22 & 21 & 21 & 19\\
$10^{4}$ & 21 & 22 & 22 & 21 & 21 & 19\\
$10^{2}$ & 21 & 22 & 22 & 21 & 21 & 19\\
1 & 24 & 28 & 26 & 26 & 27 & 25\\
$10^{-2}$ & 10 & 10 & 10 & 12 & 13 & 14\\
$10^{-4}$ & 6 & 6 & 6 & 6 & 7 & 7\\
$10^{-6}$ & 4 & 4 & 4 & 4 & 4 & 4\\
\hline
\end{tabular}                
              \end{center}
        \end{minipage}
      }
          \caption{
            Problem \eqref{eq:coupled_weak} discretized with P1 elements.
            Condition number (left) and iterations counts (right) using
            preconditioner \eqref{eq:P1_precond}.
          }
          \label{tab:P1} 
%\label{table1}
\end{table}

Preconditioner \eqref{eq:P1_precond} was derived under the assumption that
the finite element mesh $\Gamma_h$ of $\Gamma$ consists of facets of the finite
element mesh $\Omega_h$ of $\Omega$, see also Figure \ref{fig:domains} (i). This
assumption is too limiting; for practical purposes the meshes should be independent
and a more common case is that the trace mesh of $\Omega_h$ on $\Gamma$ is coarser
than $\Gamma_h$. In the following we shall pursue formulations (and corresponding
solvers) of \eqref{eq:coupled_weak} which allow for different meshes and resolutions.
Our ultimate goal is a stable formulation in which the multiplier is not defined
on $\Gamma_h$ but rather on cells of $\Omega_h$ intersected by the curve, cf. Figure
\ref{fig:domains} (iv) and (v).
%
\begin{figure}
  \begin{center}
    \includegraphics[width=0.4\textwidth]{./img/conform.tex}\\

  \includegraphics[width=0.4\textwidth]{./img/conform_fine.tex}\hfill
  \includegraphics[width=0.4\textwidth]{./img/cut_fine.tex}\\
  \includegraphics[width=0.4\textwidth]{./img/nocut_lm2d.tex}\hfill
    \includegraphics[width=0.4\textwidth]{./img/cut_lm2d.tex}
  \end{center}
  \caption{Schematic geometric setting and discretization of mutliscale problems.
    Position of interface $\Gamma$ is denoted by \figlegend{green!50!black}. Meshes
    underlying discrete approximation spaces $\hat{V}_h$ and $Q_h$ of $\hat{V}$ and $Q$ are denoted respectively
    by \figlegend{white!50!blue} and \figlegend{white!50!red}. Geometric correspondence
    is signified by dashed line. Cases: (i) trace mesh of $V_h$ is used for $\hat{V}_h$ and $Q_h$,
    (ii) $\Gamma$ does not intersect $\Omega_h $ cell interiors, (iii) $\Gamma$ does
    intersect cell interiors, (iv) as (ii) with $Q_h$ defined on intersected cells and
    (v) as (iii) with $Q_h$ defined on intersected cells.
  }
 \label{fig:domains}
\end{figure}

The rest of the report is structured as follows. Considering \eqref{eq:operator2d}
we first treat the problems related to domains $\Omega$, i.e. $\mathcal{A}_2=\left[A_2, B_2'; B_2, 0\right]$,
and $\Gamma$, i.e. $\mathcal{A}_1=\left[A_1, B_1'; B_1, 0\right]$, individually\footnote{This is done for
clarity of exposition, to better fix the ideas and debugging}. More precisely, in
\S\ref{sec:problem_omega} a set of preconditioners for different formulations of the Babu{\v s}ka
problem is presented culminating in a formulation having the discrete Lagrange multiplier on the
cut cells. In \S\ref{sec:problem_gamma} we deal with instabities in $\mathcal{A}_1$ which arise
due to choices of discretization of the Lagrange multiplier space in $\mathcal{A}_2$. Finally in
\S\ref{sec:coupled} the insights from individual problems are combined to yield robust solvers
for the coupled problem.

\section{Coupling 2$d$-1$d$}\label{sec:problem_omega}
\input{problem_omega}

\section{Coupling 1$d$-1$d$}\label{sec:problem_gamma}
\input{problem_gamma}

\section{Coupling 2$d$-1$d$-1$d$}\label{sec:coupled}
\input{coupled}

\bibliographystyle{siamplain}
\bibliography{solver}
\end{document}

### 2019-08-02 solver/problem_omega.tex
A2 done

@@
+With Figure \ref{fig:coupled_domain} in mind we wish to solve the 2$d$-1$d$
+coupled problem: Find $u\in V=H^1_{0, \Gamma_{D}}(\Omega)$,
+$p\in Q=H^{-1/2}(\Gamma)$ such that
+ %
+\begin{equation}\label{eq:A2}
+\begin{aligned}
+  &\int_{\Omega}\nabla u\cdot\nabla v\,\mathrm{d}x + &{\int_{\Gamma}p v} &= \int_{\Omega}f v\,\mathrm{d}x\quad\forall v\in V,\\
+  &{\int_{\Gamma}q u\,\mathrm{d}s} + &\phantom{\int{\Gamma}p v} &= \int_{\Gamma}g q\,\mathrm{d}s\quad\forall q\in Q.\\
+\end{aligned},
+\quad\mbox{or equivalently}\quad
+\mathcal{A}_2\begin{pmatrix}
+u\\
+p\\
+\end{pmatrix} = L.
+\end{equation}
+%
+It can be seen that $\mathcal{A}_2$ is an isomorphism from $W=V\times Q$
+to $W^{'}$ and in turn by \cite{mardal2011preconditioning} operator
+\[
+\mathcal{B}_2=\text{diag}(-\Delta_{\Omega}, (-\Delta_{\Gamma}+I)^{-1/2})^{-1}
+\]
+is a cannonical preconditioner for $\mathcal{A}_2$. Considering first the
+case (i) from Figure \ref{fig:domains}, i.e. trace mesh of $\Omega_h$ is
+$\Gamma_h$ and using (stable) P1-P1 discretization Table \ref{tab:A2} shows
+the both the condition number and the number of MinRes iterations of $\mathcal{B}_2\mathcal{A}_2$
+are bounded.
+
+In order to arrive at the formulation where the discrete multiplier space
+$Q_h$ is setup on the $\Gamma$-intersected cells of $\Omega_h$ let us first
+consider an intermediate formulation with a piecewise constant (P0) multiplier defined
+on $\Gamma_h$, cf. Figure \ref{fig:domains} (ii) and (iii). It is well known, e.g.
+\cite[Ch 11.3]{steinbach2007numerical}, that if trace mesh of $\Omega_h$ is $\Gamma_h$ then P1-P0 discretization is
+unstable. However the pair is stable if $\Gamma_h$ is coarser than the trace
+mesh or a stabilization is employed. In the application we have in mind
+the mesh of $\Omega$ is in general coarser than that of $\Gamma$ and thus
+stabilized formulation are of interest. To highlight the difference in resolution
+between the meshes we shall use different subscripts, i.e. $\Omega_H$ and
+$\Gamma_h$. We remark that stabilization for piecewise linear Lagrange multipliers
+(on $\Gamma$) is discussed in \cite{burman2009interior}.
+
+Let $V_H=V_H(\Omega_H)$, $Q_h=Q_h(\Gamma_h)$ be the finite element approximations
+of $V$ and $Q$ in terms of P1 and P0 elements respectively. Following \cite{burman2014projection}
+the stabilized formulation of \eqref{eq:A2} reads: Find $u \in V_H$ and
+$p \in Q_h$ such that
+%
+\[
+\begin{aligned}
+  &\int_{\Omega}\nabla u\cdot\nabla v\,\mathrm{d}x + &{\int_{\Gamma}p v\,\mathrm{d}s} &= \int_{\Omega}f v\,\mathrm{d}x\quad\forall v\in V_H,\\
+  &{\int_{\Gamma}q u\,\mathrm{d}s} + &-\sum_{F\in\mathcal{F}}\int_{F}h^2\jump{p}\jump{q} \mathrm{d}s &= \int_{\Gamma}g q\,\mathrm{d}s\quad\forall q\in Q_h,\\
+\end{aligned},
+\quad\mbox{or equivalently}\quad
+\mathcal{A}_{2, \Gamma_h}\begin{pmatrix}u\\p\\\end{pmatrix} = L.
+\]
+%
+Here $\mathcal{F}$ is the union of internal and $\Gamma_N$-intersecting
+facets of $\Gamma_h$. A possible preconditioner for $\mathcal{A}_{2,\Gamma_h}$,
+which is based on the mapping properties of the continuous problem is a Riesz
+map with respect to the inner product in induced by $\mathcal{B}^{-1}_{2, \Gamma_h}$
+\[
+\langle
+\mathcal{B}^{-1}_{2, \Gamma_h}\begin{pmatrix}u\\p\end{pmatrix},
+  \begin{pmatrix}v\\q\end{pmatrix}
+\rangle
+    =
+    \int_{\Omega}\nabla u\cdot\nabla v\,\mathrm{d}x + \langle(-\Delta_{\Gamma}+I)^{-1/2}p, q\rangle
+    + \sum_{F\in\mathcal{F}}\int_{F}h^2\jump{p}\jump{q} \mathrm{d}s.
+\]
+Robustness of the preconditioner can be seen in Table \ref{tab:A2} in both
+the case where $\Gamma_h$ does not and does intersect the cell interior of $\Omega_h$ (cases
+(iii) and (iv) in Figure \ref{fig:domains}). A potential difficulty with
+$\mathcal{B}_{2, \Gamma_h}$ is, however, its generalization of the call of $Q_h$ defined
+on intersected cells (interiors). In particular, the fractional norm can be
+an problematic. To avoid the issue, we therefore consider an alternative
+preconditioner based on \cite[\S 4.A]{burman2014projection}
+\[
+\langle
+\tilde{\mathcal{B}}^{-1}_{2, \Gamma_h}\begin{pmatrix}u\\p\end{pmatrix},
+  \begin{pmatrix}v\\q\end{pmatrix}
+\rangle
+    =
+    \int_{\Omega}\nabla u\cdot\nabla v\,\mathrm{d}x + \int_{\Gamma}h^{-1}u v\,\mathrm{d}s + \int_{\Gamma} h p q\,\mathrm{d}s
+    + \sum_{F\in\mathcal{F}}\int_{F}h^2\jump{p}\jump{q} \mathrm{d}s.
+\]
+Note that the fractional norm on the multiplier has been replaced by the $h$-weighted
+$L^2$ norm. Furthermore, there is an additional control of the trace of $u$ on
+the curve by $h^{-1}$-weighted $L^2$ norm. We remark that \cite{burman2014projection} proves
+the inf-sup condition for $\mathcal{A}_{2, \Gamma_h}$ using the norms on $V_H$ and
+$Q_h$ as follows
+\[
+\norm{u}^2_{V_H} = \norm{\semi{\nabla u}}^2_0 + \int_{\Gamma}h^{-1} u v\,\mathrm{d}s
+\quad\mbox{and}\quad
+\norm{p}_{Q_h} = \norm{h^{1/2} p}_0.
+\]
+
+Robustness of the preconditioner is
+shown in Table \ref{tab:A2}; in the cut case (iii) the preconditioner is more
+efficinet than $\mathcal{B}_{2, \Gamma_h}$. We remark that the error convergence
+of $\norm{u-u_H}_1$ is reduced in this case due to the fact that the kink
+of the solution cannot be captured within the element.
+
+Finally, we extend $\mathcal{A}_{2, \Gamma_h}$ to the formulation with Lagrange
+mutliplier on the intersected elements. To this end, let $\mathcal{S}_H$ denote
+elements of $\Omega_H$ intersected by $\Gamma_h$. The space $Q_H$ now consists
+of piecewise constants on $\mathcal{S}_H$. Following \cite[\S 4.B]{burman2014projection}
+we consider problem: Find $u\in V_H$, $p\in  Q_H$ such that
+%
+\[
+\begin{aligned}
+  &\int_{\Omega}\nabla u\cdot\nabla v\,\mathrm{d}x + &{\int_{\Gamma}p v\,\mathrm{d}s} &= \int_{\Omega}f v\,\mathrm{d}x\quad\forall v\in V_H,\\
+  &{\int_{\Gamma}q u\,\mathrm{d}s} + &-\sum_{F\in\partial\mathcal{S}}\int_{F}H\jump{p}\jump{q} \mathrm{d}s &= \int_{\Gamma}g q\,\mathrm{d}s\quad\forall q\in Q_H,\\
+\end{aligned},
+\quad\mbox{or equivalently}\quad
+\mathcal{A}_{2, \Omega_H}\begin{pmatrix}u\\p\\\end{pmatrix} = L.
+\]
+%
+Here $\partial\mathcal{S}$ denotes interior and Neumann boundary intersecting
+facets of $\mathcal{S}$. We remark that the norms for the inf-sup condition (shown
+in \cite{burman2014projection} of $\mathcal{A}_{2, \Omega_H}$ are identical to $\mathcal{A}_{2, \Gamma_g}$.
+
+Note that the stabilization is newly applied on edges
+(points previously in $\mathcal{A}_{2, \Gamma_h}$) and relative to $\mathcal{A}_{2, \Gamma_h}$
+we componsate for the increased dimensionality of the facets by decreasing
+the exponent of the $H$-weight. In a similar manner
+the preconditioner $\tilde{\mathcal{B}}_{2, \Gamma_h}$ can be generalized
+yielding $\tilde{\mathcal{B}}_{2, \Omega_H}$
+\[
+\langle
+\tilde{\mathcal{B}}^{-1}_{2, \Omega_H}\begin{pmatrix}u\\p\end{pmatrix},
+  \begin{pmatrix}v\\q\end{pmatrix}
+\rangle
+    =
+    \int_{\Omega}\nabla u\cdot\nabla v\,\mathrm{d}x + \int_{\Gamma}h^{-1}u v\,\mathrm{d}s + \int_{\Gamma} h p q\,\mathrm{d}s
+    + \sum_{F\in\partial\mathcal{S}}\int_{F}H\jump{p}\jump{q} \mathrm{d}s.
+\]
+In Table \ref{tab:A2} we observe that MinRes iterations with
+$\tilde{\mathcal{B}}_{2, \Omega_H}\mathcal{A}_{2, \Omega_H}$ are bounded. The decreasing
+increments of the condition numbers suggest that $\kappa$ is bounded as well.
+
 \begin{table}
@@
   \begin{center}
-    \begin{tabular}{c|cccc||cc}
+    \begin{tabular}{c|cccc}%||cc}
       \hline
-      \multirow{2}{*}{$h/H$} & \multicolumn{4}{c||}{$\mathcal{B}$} & \multicolumn{2}{c}{$\mathcal{B}_{h}$}\\
-      \cline{2-7}
-      & $\norm{u-u_h}_1$ & $\norm{\lambda-\lambda_h}_0$ & \# & $\kappa$ & \# & $\kappa$\\
+      \multirow{2}{*}{$\frac{H}{H_0}$} & \multicolumn{4}{c}{$\mathcal{B}_2$}\\ %& \multicolumn{2}{c}{$\mathcal{B}_{h}$}\\
+      \cline{2-5}
+      & $\norm{u-u_H}_1$ & $\norm{\lambda-\lambda_H}_0$ & \#\\% & $\kappa$ & \# & $\kappa$\\
       \hline
-1        & 8.62E-1(--)  & 1.04E0(--)    &   21 & 7.8  & 24 & 20.9 \\
-$2^{-1}$ & 4.4E-1(0.99) & 3.8E-1(1.46)  & 24   & 7.9  & 41 & 21.1 \\
-$2^{-2}$ & 2.2E-1(1.00) & 1.4E-1(1.49)  & 22   & 7.9  & 46 & 21.2 \\
-$2^{-3}$ & 1.1E-1(1.00) & 4.8E-2(1.50)  & 22   & --   & 47 & --   \\
-$2^{-4}$ & 5.5E-2(1.00) & 1.7E-2(1.50)  & 21   & --   & 48 & --   \\
-$2^{-5}$ & 2.7E-2(1.00) & 6.0E-3(1.50)  & 21   & --   & 45 & --   \\
+1        & 8.62E-1(--)  & 1.04E0(--)    &   21 & 7.8\\ % & 24 & 20.9 \\
+$2^{-1}$ & 4.4E-1(0.99) & 3.8E-1(1.46)  & 24   & 7.9\\ % & 41 & 21.1 \\
+$2^{-2}$ & 2.2E-1(1.00) & 1.4E-1(1.49)  & 22   & 7.9\\ % & 46 & 21.2 \\
+$2^{-3}$ & 1.1E-1(1.00) & 4.8E-2(1.50)  & 22   & -- \\ % & 47 & --   \\
+$2^{-4}$ & 5.5E-2(1.00) & 1.7E-2(1.50)  & 21   & -- \\ % & 48 & --   \\
+$2^{-5}$ & 2.7E-2(1.00) & 6.0E-3(1.50)  & 21   & -- \\ % & 45 & --   \\
 \hline
@@
       \hline
-      \multirow{2}{*}{$h/H$} & \multicolumn{4}{c||}{$\mathcal{B}$} & \multicolumn{2}{c}{$\mathcal{B}_{h}$}\\
+      \multirow{2}{*}{$\frac{H}{H_0}$} & \multicolumn{4}{c||}{$\mathcal{B}_{2, \Gamma_h}$} & \multicolumn{2}{c}{$\tilde{\mathcal{B}}_{2, \Gamma_h}$}\\
       \cline{2-7}
-      & $\norm{u-u_h}_1$ & $\norm{\lambda-\lambda_h}_0$ & \# & $\kappa$ & \# & $\kappa$\\
+      & $\norm{u-u_H}_1$ & $\norm{\lambda-\lambda_h}_0$ & \# & $\kappa$ & \# & $\kappa$\\
       \hline
@@
       \hline
-      \multirow{2}{*}{$h/H$} & \multicolumn{4}{c||}{$\mathcal{B}$} & \multicolumn{2}{c}{$\mathcal{B}_{h}$}\\
+      \multirow{2}{*}{$\frac{H}{H_0}$} & \multicolumn{4}{c||}{$\mathcal{B}_{2, \Gamma_h}$} & \multicolumn{2}{c}{$\tilde{\mathcal{B}}_{2, \Gamma_h}$}\\
       \cline{2-7}
-      & $\norm{u-u_h}_1$ & $\norm{\lambda-\lambda_h}_0$ & \# & $\kappa$ & \# & $\kappa$\\
+      & $\norm{u-u_H}_1$ & $\norm{\lambda-\lambda_h}_0$ & \# & $\kappa$ & \# & $\kappa$\\
       \hline
-1       & 8.6E-1(--) & 5.4E-1(--)  & 31 & 6.7 & 21 & 2.5\\
-$2^{-1}$ & 4.3E-1(0.98) & 2.3E-1(1.20)& 32 & 6.6 & 21 & 2.5\\
-$2^{-2}$ & 2.2E-1(1.00) & 1.0E-1(1.19)& 31 & 6.6 & 21 & 2.5\\
-$2^{-3}$ & 1.1E-1(1.00) & 4.7E-2(1.13)& 30 & --  & 20 & --  \\
-$2^{-4}$ & 5.5E-2(1.00) & 2.2E-2(1.08)& 28 & --  & 20 & --  \\
-$2^{-5}$ & 2.7E-2(1.00) & 1.1E-2(1.04)& 28 & --  & 18 & --  \\
+1       & 1.3E0(--)   & 1.7E0(--)    & 31 & 6.7 & 21 & 2.5\\
+$2^{-1}$ &8.2E-1(0.68) & 9.2E-1(0.92)  & 32 & 6.6 & 21 & 2.5\\
+$2^{-2}$ &5.4E-1(0.63) & 4.6E-1(1.00)  & 31 & 6.6 & 21 & 2.5\\
+$2^{-3}$ &3.6E-1(0.58) & 2.3E-1(1.01)  & 30 & --  & 20 & --  \\
+$2^{-4}$ &2.5E-1(0.54) & 1.1E-1(1.01)  & 28 & --  & 20 & --  \\
+$2^{-5}$ &1.7E-1(0.52) & 5.7E-2(1.01)  & 28 & --  & 18 & --  \\
       \hline
@@
       \hline
-      \multirow{2}{*}{$h/H$} & \multicolumn{4}{c|}{$\mathcal{B}$}\\
+      \multirow{2}{*}{$\frac{H}{H_0}$} & \multicolumn{4}{c}{$\mathcal{B}$}\\
       \cline{2-5}
@@
 %%%%%%%%%%%%%
-  \caption{}
-  \label{}
+  \caption{Iteration counts (\#) and condition numbers ($\kappa$) of different
+    formulations of \eqref{eq:A2}, $H_0=2^{-4}$ and $h=H/3$.
+    The cases correspond to setups (i)-(v) from Figure \ref{fig:domains}.
+    First row (i) with $\mathcal{A}_2$. Second row (ii) and (iii) with
+    $\mathcal{A}_{2, \Gamma_h}$. Third row (iv) and (v) with $\mathcal{A}_{2, \Omega_H}$.
+  }
+  \label{tab:A2}
 \end{table}

### 2019-08-02 solver/solver.tex
A2 done

@@
 
+\newcommand{\MK}[1]{\textcolor{cyan}{#1}}
+
 \newcommand{\semi}[1]{\lvert{#1}\rvert}
@@
 \newcommand{\avg}[1]{\ensuremath{\left\{\!\left\{#1\right\}\!\right\}} }
+
 \def\ud{u_{\odot}}
@@
   % Boundaries
-  \draw[red!60!white] (0, 0) -- (0, 4);
-  \draw[red!60!white] (4, 0) -- (4, 4);
+  \draw[very thick, red!60!white] (0, 0) -- (0, 4);
+  \draw[very thick,red!60!white] (4, 0) -- (4, 4);
   \node[red!60!white, opacity=0.9, right] at (4, 1) {$\Gamma_D$};
 
-  \draw[blue!60!white] (0, 0) -- (4, 0);
-  \draw[blue!60!white] (0, 4) -- (4, 4);
+  \draw[very thick, blue!60!white] (0, 0) -- (4, 0);
+  \draw[very thick, blue!60!white] (0, 4) -- (4, 4);
   \node[blue!60!white, opacity=0.9, below] at (3, 0) {$\Gamma_N$};
@@
   \begin{aligned}
-    &\int_{\Omega}\nabla u\cdot \nabla v &\phantom{+\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &+\epsilon\int_{\Gamma} p v &= \int_{\Omega}f v \quad &\forall v\in V,\\
-    &\phantom{\int_{\Omega}\nabla u\cdot \nabla v} &+{\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v} + \hat{u}\hat{v}} &-\int_{\Gamma} p\hat{v} &= \int_{\Gamma}\hat{f}\hat{v} \quad &\forall \hat{v}\in \hat{V},\\
-    &\epsilon\int_{\Gamma}u q &-\int_{\Gamma}\hat{u}q &\phantom{-\int{\Gamma}q\hat{v}} &= \int_{\Gamma}h q \quad &\forall q\in Q.
+    &\int_{\Omega}\nabla u\cdot \nabla v\,\mathrm{d}x &\phantom{+\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &+\epsilon\int_{\Gamma} p v\,\mathrm{d}s &= \int_{\Omega}f v\,\mathrm{d}x \quad &\forall v\in V,\\
+    &\phantom{\int_{\Omega}\nabla u\cdot \nabla v} &+{\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v} + \hat{u}\hat{v}\,\mathrm{d}x} &-\int_{\Gamma} p\hat{v}\,\mathrm{d}s &= \int_{\Gamma}\hat{f}\hat{v}\,\mathrm{d}s \quad &\forall \hat{v}\in \hat{V},\\
+    &\epsilon\int_{\Gamma}u q\,\mathrm{d}s &-\int_{\Gamma}\hat{u}q\,\mathrm{d}s &\phantom{-\int{\Gamma}q\hat{v}} &= \int_{\Gamma}h q\,\mathrm{d}s \quad &\forall q\in Q.
   \end{aligned}
@@
     -\Delta_{\Omega} & & -\epsilon T^{\prime}\\
-    & -\Delta_{\Gamma} + I & I\\
-    -\epsilon T & I & \\
+    & -\Delta_{\Gamma} + I & -I\\
+    -\epsilon T & -I & \\
   \end{pmatrix} =
@@
 (and verifying the implementation) Table \ref{tab:P1} shows the number of
-MinRes iterations and condition numbers of the preconditioned problem for
-different levels of refinements and values of the parameter $\epsilon$. The
+MinRes iterations and condition numbers\footnote{
+  Unless specified otherwise all the experiments are done on $\Omega$ a unit square
+  triangulated in $2N^2$ isosceles triangles. MinRes iterations are always started
+  from a random initial vector and terminate one the relative preconditioned residual
+  norm is reduced by factor $10^{8}$. Condition numbers of the preconditioned problem
+  are computed by direct solvers, i.e. from the full spectrum.
+} of the preconditioned problem for
+different levels of refinement and values of the parameter $\epsilon$. The
 stability is evident.
@@
   \end{center}
-  \caption{Schematic geometric setting and discretization of mutliscale problems.
+  \caption{Schematic geometric setting and discretization of multiscale problems.
     Position of interface $\Gamma$ is denoted by \figlegend{green!50!black}. Meshes
@@
 and $\Gamma$, i.e. $\mathcal{A}_1=\left[A_1, B_1'; B_1, 0\right]$, individually\footnote{This is done for
-clarity of exposition, to better fix the ideas and debugging}. More precisely, in
+clarity of exposition, to better fix the ideas and debugging.}. More precisely, in
 \S\ref{sec:problem_omega} a set of preconditioners for different formulations of the Babu{\v s}ka
@@
 
-\section{Coupling 2$d$-1$d$}\label{sec:problem_omega}
+\section{Preconditioning $\mathcal{A}_2$}\label{sec:problem_omega}
 \input{problem_omega}
 
-\section{Coupling 1$d$-1$d$}\label{sec:problem_gamma}
+\section{Preconditioning $\mathcal{A}_1$}\label{sec:problem_gamma}
 \input{problem_gamma}
 
-\section{Coupling 2$d$-1$d$-1$d$}\label{sec:coupled}
+\section{Preconditioning coupled problem}\label{sec:coupled}
 \input{coupled}

### 2019-08-02 solver/problem_gamma.tex
work on A1

Let $V=H^1{(\Gamma)}$ We consider the minimization problem
\[
\min_{u\in V}\quad\norm{u}^2_1 - \int_{\Gamma}f u\,\mathrm{d}x\quad\mbox{subject to}\quad
u-g\mbox{ in }\Gamma.
\]
Denoting $p$ the Lagrange multiplier for the constraint the extremal points
of the related Lagrangian are found as a solution to
%
\begin{equation}\label{eq:A1}
\begin{pmatrix}f\\g\end{pmatrix}=
\mathcal{A}_1\begin{pmatrix}u\\p\end{pmatrix}=
%
\begin{pmatrix}
  -\Delta + I & I\\
  I           &  \\
\end{pmatrix}
\begin{pmatrix}u\\p\end{pmatrix}.
\end{equation}
%
Setting $Q=H^{-1}(\Gamma)$, the operator $\mathcal{A}_1:W\rightarrow W^{\prime}$
can be seen to be an isomorphism with $W=V\times Q$. In particular the inf-sup
condition holds with constant 1 (by definition of the $H^{-1}$ norm).

While it can be easily seen that P1-P1 discretization is inf-sup stable for
the problem the pair which we are interested in is P1-P0 as piece-wise constant
elements were used in the previous section. We recall that stable P1-P1 discretization
for $\mathcal{A}_2$ (using different meshes for $\Omega$, $\Gamma$ is also possible,
cf. \cite{burman2009interior}, however, it is not clear how to extend this result
to 3$d$-1$d$ problem \eqref{eq:problem2}.

To illustrate that P1-P0 is not inf-sup stable for $\mathcal{A}_1$ consider
a uniform mesh $\Gamma_h$ and for simplicity assume homogeneous Dirichlet
boundary conditions on $V$. Let $\text{mid}_{K}$ be the midpoint of $K\in\Gamma_h$.
Then 
\[
\int_{\Gamma} p v = \sum_{K\in{\Gamma}_h}p(\text{mid}_{K})v(\text{mid}_{K})
\]
and it can be seen that a ``checker-board'' function $p$ renders the integral
zero, that is, the inf-sup condition does not hold.

Let $C$ be the constant from the inf-sup condition of $\mathcal{A}_2$. 
Since $\mathcal{A}_1$ is only a sub-problem of \eqref{eq:operator2d} the
inf-sup condition for the operator of the coupled problem can be obtained as
\[
\sup_{(v,\hat{v})\in V\times \hat{V}}\frac{\int_{\Gamma}(v-\hat{v}) p}{\norm{(v,\hat{v})}_{V\times \hat{V}}}
\geq
\sup_{v\in V}\frac{\int_{\Gamma}v p}{\norm{v}_{V}}
\geq
C\norm{p}_Q.
\]
If we apply similar argument to the discrete inf-sup condition it seems
that the unstable discretization of $\mathcal{A}_1$ does not present issue.
We shall now give an example which demonstrates that for \emph{robust} preconditioning
the inf-sup condition should be established in the (intersection) space in which \emph{both}
subproblems are inf-sup stable.

\begin{example}[Stokes problem]\label{ex:stokes}
  Consider the problem of finding $u_1$, $u_2$, $p$ satisfying
  \[
  \begin{aligned}
  -\Delta u_1 -\epsilon\nabla p &= f_1\mbox{ in }\Omega,\\
  -\Delta u_2 + \nabla p &= f_2\mbox{ in }\Omega,\\
  \nabla\cdot(\epsilon u_1 - u_2) &= g\mbox{ in }\Omega.
  \end{aligned}
  \]
  We shall assume that the $u_1=0$, $u_2=0$ on $\Gamma_D\subset\partial\Omega$
  and $\semi{\Gamma_D}\neq\semi{\partial\Omega}$. Let now $V_1=H^{1}_{0, \Gamma_D}(\Omega)$,
  $V_2=H^{1}_{0, \Gamma_D}(\Omega)$ and $Q=L^2(\Omega)$. Then the operator defined 
  by the weak form of the problem
  \[
  \mathcal{A}=\begin{pmatrix}
  -\Delta & & -\epsilon\nabla\\
  & -\Delta & \nabla\\
  \epsilon\nabla\cdot & -\nabla\cdot & \\
  \end{pmatrix}: V_1\times V_2\times Q \rightarrow (V_1\times V_2\times Q)^{\prime}
  \]
  is an isomorphism. However, with these spaces the Riesz map preconditioner
  is not parameter robust. Instead $Q=\epsilon L^2(\Omega)\cap L^2{(\Omega)}$
  shall be used.

  To illustrate the issue with unstable discretization
  let $V_1$ be discretized by P2 elements while $V_2$ uses P1 elements. As
  P1 elements are used for $Q$ the first Stokes problem is stable while the
  latter one is not. We shall first consider
  \[
  \mathcal{B}=\text{diag}(-\Delta, -\Delta, (\epsilon^2+1)I)^{-1}
  \]
  as a preconditioner for $\mathcal{A}$.

  Table \ref{tab:stokes} shows that
  iterations are stable when $\epsilon\gg 1$ while they are unbounded for
  $\epsilon<1$. A heuristic explanation for
  the observation can based on Schur complement reasoning. Indeed the
  Schur complement of $\mathcal{A}_h$ consists of two parts corresponding
  to the two Stokes problems
  \[
  S = \epsilon^2\nabla_h\cdot(-\Delta_h)^{-1}\nabla_h + \nabla_h\cdot(-\Delta_h)^{-1}\nabla_h.
  \]
  Owing the discrete inf-sup condition the spectrum of the first part is
  bounded by $\epsilon^2 I_h$ for all $h$. However, for the second component
  a similar bound does not hold (as the corresponding discretization is unstable)
  and this part can become dominant for small $\epsilon$.

  To obtain parameter robustness we consider a stabilized formulation
  of the Stokes problem in which $\gamma \Delta p = 0$ is added to the
  divergence constraint (with Dirichlet boundary conditions for $p$ on
  $\partial\Omega\setminus \Gamma_D$) and $\gamma$ depends on the square
  of the mesh size, see also \cite[\S 7]{mardal2011preconditioning}. As
  a preconditioner for the stabilized operator we then consider
  \[
  \mathcal{B}_s=\text{diag}(-\Delta, -\Delta, (\epsilon^2+1)I-\beta\Delta)^{-1}.
  \]
  Table \ref{tab:stokes} confirms robustness of the preconditioner. We remark
  that the stabilizing term has little effect on approximation properties
  of the formulation.

  \begin{table}
      \scriptsize{
    \begin{minipage}{0.49\textwidth}
  \begin{center}
    \begin{tabular}{c|ccccc}
      \hline
      \multirow{2}{*}{$\epsilon$} & \multicolumn{5}{c}{$h$}\\
      \cline{2-6}
 &   $2^{-3}$  & $2^{-4}$ & $2^{-5}$ & $2^{-6}$ & $2^{-7}$  \\  
\hline
$10^{6}$ & 54 & 57 & 59 & 59 & 96\\
$10^{4}$ & 121 & 116 & 113 & 107 & 109\\
$10^{2}$ & 100 & 86 & 69 & 121 & 172\\
1 & 177 & 244 & 287 & 311 & 329\\
$2^{-1}$ & 231 & 303 & 372 & 415 & 500\\
$2^{-2}$ & 350 & 453 & 500 & 500 & 500\\
$10^{-1}$ & 500 & 500 & 500 & 500 & 500\\
\hline
  \end{tabular}
  \end{center}
  \end{minipage}
      }
            \scriptsize{
    \begin{minipage}{0.49\textwidth}
  \begin{center}
    \begin{tabular}{c|cccccc}
      \hline
      \multirow{2}{*}{$\epsilon$} & \multicolumn{5}{c}{$h$}\\
      \cline{2-6}
 &   $2^{-3}$  & $2^{-4}$ & $2^{-5}$ & $2^{-6}$ & $2^{-7}$  \\  
\hline
$10^{6}$ & 51 & 54 & 55 & 57 & 58\\
$10^{4}$ & 51 & 54 & 55 & 57 & 58\\
$10^{2}$ & 51 & 54 & 56 & 57 & 58\\
1 & 36 & 42 & 47 & 49 & 50\\
$10^{-2}$ & 32 & 38 & 44 & 47 & 49\\
$10^{-4}$ & 32 & 38 & 44 & 47 & 49\\
$10^{-6}$ & 32 & 38 & 44 & 47 & 49\\
\hline
  \end{tabular}
  \end{center}
  \end{minipage}
  }
    \caption{Iteration counts for the Stokes problem. (left) Formulation without
      stabilization using preconditioner $\mathcal{B}$. (right) Stabilized
      formulation with preconditioner $\mathcal{B}_s$. Maximum number of
    iterations allowed is 500.}
  \label{tab:stokes}
  \end{table}
\end{example}

Example \ref{ex:stokes} motivates the need to find a stabilizing term
for the P1-P0 discretization of $\mathcal{A}_1$. In addition, the stabilization
should be consisten so that to not ruin the approximation properties of the
formulation.

### 2019-08-02 solver/problem_omega.tex
work on A1

@@
       \hline
-      \multirow{2}{*}{$\frac{H}{H_0}$} & \multicolumn{4}{c}{$\mathcal{B}$}\\
+      \multirow{2}{*}{$\frac{H}{H_0}$} & \multicolumn{4}{c}{$\mathcal{B}_{2, \Omega_H}$}\\
       \cline{2-5}
@@
 \end{table}
+
+At this point we have at our disposal an efficient solver for $\mathcal{A}_2$,
+that is a 2$d$-1$d$ subcomponent of the coupled problem \eqref{eq:coupled_weak}.
+We now turn attention to the 1$d$-1$d$ component; the idea being that the solver
+for the coupled problem in some sense consists of solvers for $\mathcal{A}_2$ and
+$\mathcal{A}_1$.

### 2019-08-02 solver/problem_gamma.tex
update

@@
 \min_{u\in V}\quad\norm{u}^2_1 - \int_{\Gamma}f u\,\mathrm{d}x\quad\mbox{subject to}\quad
-u-g\mbox{ in }\Gamma.
+u=g\mbox{ in }\Gamma.
 \]
@@
 for the P1-P0 discretization of $\mathcal{A}_1$. In addition, the stabilization
-should be consisten so that to not ruin the approximation properties of the
+should be consistent so as to not ruin the approximation properties of the
 formulation.
+
+\subsection{Stabilized $\mathcal{A}_1$} We construct the stabilizing term
+based on two observations. (i) In \S\ref{sec:problem_omega} the stabilization
+for $p\in Q_h\subset H^{-1/2}$ in takes the form the facet integral with integrand $h^{2}\jump{p}\jump{q}$.
+(ii) For P0 element $-\Delta_h$ is spectrally equivalent to operator involving
+facet integrals with integrand $h^{-1}\jump{p}\jump{q}$. In turn we assume
+that the stabilization for $H^s$ norms takes the form $h^{p}\jump{p}\jump{q}$
+and by interpolation from (i) and (ii) $p=-2s+1$. Thus the stabilizing term for $H^{-1}$ shall
+involve the cube of the mesh size and we consider a discrete formulation of \eqref{eq:A1}
+in terms of the operator
+%
+\[
+\langle\mathcal{A}_{1, h}\begin{pmatrix}u\\p\end{pmatrix},
+  \begin{pmatrix}v\\q\end{pmatrix}
+    \rangle
+    =
+    \int_{\Gamma}\nabla u\cdot\nabla v+uv\,\mathrm{d}x+\int_{\Gamma}uq + vp\,\mathrm{d}x-
+    \sum_{F\in\mathcal{F}}h^3\jump{p}\jump{q}\,\mathrm{d}s.
+\]
+The preconditioner for $\mathcal{A}_{1, h}$ is then the Riesz mapping which
+includes the negative stabilized term
+\[
+\langle\mathcal{B}^{-1}_{1, h}\begin{pmatrix}u\\p\end{pmatrix},
+  \begin{pmatrix}v\\q\end{pmatrix}
+    \rangle
+    =
+    \int_{\Gamma}\nabla u\cdot\nabla v+uv\,\mathrm{d}x+
+    \langle(-\Delta+I)^{-1}p, q\rangle+
+    \sum_{F\in\mathcal{F}}h^3\jump{p}\jump{q}\,\mathrm{d}s.
+\]
+
+Table \ref{tab:A1} shows error convergence of the proposed formulation
+together with the condition number of the preconditioner problem. We remark
+that the manufactured solution on the unit interval has $g=0$ so that $p=f=\cos(\pi x)$
+and $u=0$ is the solution. It can be seen that the formulation is stable and
+yields converging solutions.
+
+\begin{table}
+  \footnotesize{
+    \begin{center}
+      \begin{tabular}{c|cc|c}
+        \hline
+        $h$ & $\norm{u-u_h}_1$ & $\norm{p-p_h}_0$ & $\kappa$ \\
+        \hline
+% 2.50E-01& 6.4083E-02(--)  & 2.4243E-01(--)  & 2.65607  \\
+% 1.25E-01& 5.5055E-03(3.54)& 8.0279E-02(1.59)& 2.66149  \\
+% 6.25E-02& 3.5103E-04(3.97)& 4.0044E-02(1.00)& 2.66364  \\
+% 3.12E-02& 2.1949E-05(4.00)& 2.0040E-02(1.00)& 2.66582  \\
+ 1.56E-02& 1.3715E-06(4.00)& 1.0020E-02(1.00)& 2.66592  \\
+ 7.81E-03& 8.5716E-08(4.00)& 5.0100E-03(1.00)& 2.66596  \\
+ 3.91E-03& 5.3572E-09(4.00)& 2.5050E-03(1.00)& 2.66599  \\
+ 1.95E-03& 3.3482E-10(4.00)& 1.2525E-03(1.00)& 2.66599  \\
+ 9.77E-04& 2.0926E-11(4.00)& 6.2625E-04(1.00)& 2.66599  \\
+ 4.88E-04& 1.3079E-12(4.00)& 3.1312E-04(1.00)& 2.66575  \\
+        \hline
+      \end{tabular}
+    \end{center}
+  }
+  \caption{Conditioning and approximation properties of stabilized
+    formulation of \eqref{eq:A1} using P1-P0 elements.
+  }
+  \label{tab:A1}
+\end{table}

### 2019-08-03 solver/problem_gamma.tex
typos

@@
 for $\mathcal{A}_2$ (using different meshes for $\Omega$, $\Gamma$ is also possible,
-cf. \cite{burman2009interior}, however, it is not clear how to extend this result
+cf. \cite{burman2009interior}), however, it is not clear how to extend this result
 to 3$d$-1$d$ problem \eqref{eq:problem2}.
@@
   $\epsilon<1$. A heuristic explanation for
-  the observation can based on Schur complement reasoning. Indeed the
+  the observation can be based on Schur complement reasoning. Indeed the
   Schur complement of $\mathcal{A}_h$ consists of two parts corresponding
@@
   \]
-  Owing the discrete inf-sup condition the spectrum of the first part is
+  Owing to the discrete inf-sup condition the spectrum of the first part is
   bounded by $\epsilon^2 I_h$ for all $h$. However, for the second component
@@
 based on two observations. (i) In \S\ref{sec:problem_omega} the stabilization
-for $p\in Q_h\subset H^{-1/2}$ in takes the form the facet integral with integrand $h^{2}\jump{p}\jump{q}$.
-(ii) For P0 element $-\Delta_h$ is spectrally equivalent to operator involving
+for $p\in Q_h\subset H^{-1/2}$ takes the form of the facet integral with integrand $h^{2}\jump{p}\jump{q}$.
+(ii) For P0 elements $-\Delta_h$ is spectrally equivalent to operator involving
 facet integrals with integrand $h^{-1}\jump{p}\jump{q}$. In turn we assume
@@
 Table \ref{tab:A1} shows error convergence of the proposed formulation
-together with the condition number of the preconditioner problem. We remark
+together with the condition number of the preconditioned problem. We remark
 that the manufactured solution on the unit interval has $g=0$ so that $p=f=\cos(\pi x)$

### 2019-08-03 solver/problem_omega.tex
typos

@@
 $\Gamma_h$ and using (stable) P1-P1 discretization Table \ref{tab:A2} shows
-the both the condition number and the number of MinRes iterations of $\mathcal{B}_2\mathcal{A}_2$
+that both the condition number and the number of MinRes iterations of $\mathcal{B}_2\mathcal{A}_2$
 are bounded.
@@
 the mesh of $\Omega$ is in general coarser than that of $\Gamma$ and thus
-stabilized formulation are of interest. To highlight the difference in resolution
+stabilized formulation is of interest. To highlight the difference in resolution
 between the meshes we shall use different subscripts, i.e. $\Omega_H$ and
@@
 (iii) and (iv) in Figure \ref{fig:domains}). A potential difficulty with
-$\mathcal{B}_{2, \Gamma_h}$ is, however, its generalization of the call of $Q_h$ defined
+$\mathcal{B}_{2, \Gamma_h}$ is, however, its generalization to the case of $Q_h$ defined
 on intersected cells (interiors). In particular, the fractional norm can be
-an problematic. To avoid the issue, we therefore consider an alternative
+problematic. To avoid the issue, we therefore consider an alternative
 preconditioner based on \cite[\S 4.A]{burman2014projection}
@@
 \[
-\norm{u}^2_{V_H} = \norm{\semi{\nabla u}}^2_0 + \int_{\Gamma}h^{-1} u v\,\mathrm{d}s
+\norm{u}^2_{V_H} = \norm{\nabla u}^2_0 + \int_{\Gamma}h^{-1} u v\,\mathrm{d}s
 \quad\mbox{and}\quad
@@
 shown in Table \ref{tab:A2}; in the cut case (iii) the preconditioner is more
-efficinet than $\mathcal{B}_{2, \Gamma_h}$. We remark that the error convergence
+efficient than $\mathcal{B}_{2, \Gamma_h}$. We remark that the error convergence
 of $\norm{u-u_H}_1$ is reduced in this case due to the fact that the kink
@@
 facets of $\mathcal{S}$. We remark that the norms for the inf-sup condition (shown
-in \cite{burman2014projection} of $\mathcal{A}_{2, \Omega_H}$ are identical to $\mathcal{A}_{2, \Gamma_g}$.
+in \cite{burman2014projection} of $\mathcal{A}_{2, \Omega_H}$) are identical to $\mathcal{A}_{2, \Gamma_g}$.
 
@@
   \caption{Iteration counts (\#) and condition numbers ($\kappa$) of different
-    formulations of \eqref{eq:A2}, $H_0=2^{-4}$ and $h=H/3$.
+    preconditioned formulations of \eqref{eq:A2}, $H_0=2^{-4}$ and $h=H/3$.
     The cases correspond to setups (i)-(v) from Figure \ref{fig:domains}.

### 2019-09-25 3d1d_coupled_LM.tex
Adding Paolo's corrections

@@
 Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set.
-Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Omega}_\ominus$ be the complementary set of the cylinder.
-We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Omega_\ominus$.
+Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and let $\Omega_\oplus = \Omega \setminus \overline{\Omega}_\ominus$ be the complementary set of the cylinder.
+We also introduce the set $\Lambda$, a 1D manifold that represents the centerline of $\Omega_\ominus$.
 We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$.
@@
 This new problem setting will be called the \emph{reduced} problem.
-Form the mathematical standpoint it is more challenging than \eqref{eq:dirneu}, because it involves the coupling of 3D/1D elliptic problems.
+Form the mathematical standpoint it is more challenging than \eqref{eq:dirneu}, because it involves the coupling of 3D/1D elliptic problems.\\
+
 For the model reduction process, we decompose integrals as follows, for any sufficiently regular function $w$,
@@
 and a Lagrange multiplier defined either on $\Gamma$ (problem 1) or on $\Lambda$ (problem 2). 
-The scope of this work is to compare them, with the aim to determine which is the most suitable to set up a computational model for 3D-1D coupled PDEs.
+The scope of this work is to compare them, with the aim to determine which is the most suitable to set up a computational model for 3D-1D PDEs coupled with Dirichlet-Neumann constraint.
 
@@
 \\
-+\int_\Lambda |\D(s)| \avrd{u_\ominus} \vd - \int_\Lambda |\DD(s)| \avrc{\lambda} \vd \, ds
++\int_\Lambda |\D(s)| \avrd{u}_\ominus \vd - \int_\Lambda |\DD(s)| \avrc{\lambda} \vd \, ds
 = \int_\Lambda |\D(s)| \avrd{g} V\, ds\,.
@@
 (d_s \avrd{u}_{\ominus}, d_s \vd )_{\Lambda,|\D|} 
-+ ( \nu (\avrd{u}_{\ominus} - \avrc{u}_{\ominus}), d_s \vd)_{\Lambda,|\DD|} +(\avrd{u_\ominus}, \vd)_{\Lambda, |\D|}
++ ( \nu (\avrd{u}_{\ominus} - \avrc{u}_{\ominus}), d_s \vd)_{\Lambda,|\DD|} +(\avrd{u}_\ominus, \vd)_{\Lambda, |\D|}
 - (\avrc{\lambda},\vd)_{\Lambda,|\DD|}
@@
 
-\subsubsection*{Problem 1 (3D-1D-3D)}
+\subsubsection*{Problem 1 (3D-2D-1D)}
 Let $\langle \cdot , \cdot \rangle_\Gamma$ denote the duality pairing between 
-$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$. The problem consists to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac12}(\Gamma )$, such that
+$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$. The problem consists to find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac12}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
 \begin{subequations}\label{eq:problem1}
@@
 \end{subequations}
-Here, $\trace:H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ denotes the trace operator from $\Omega$ to $\Gamma$ and $\ext: H^1_0(\Lambda) \rightarrow H^1_{0}(\Gamma)$ denotes the uniform extension from $\Lambda$ to $\Gamma$.
+Here, $\trace:H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ denotes the trace operator from $\Omega$ to $\Gamma$ and $\ext: H^1_0(\Lambda) \rightarrow H^1_{0}(\Gamma)$ denotes the uniform extension from $\Lambda$ to $\Gamma$ and we exploited the fact that
+\begin{equation*}
+\left( \avrc{\lambda}, \vd \right)_{\Lambda, |\DD|} 
+= \int _{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \lambda \, d\gamma \right) \vd \, ds 
+= (\lambda, \ext \vd)_{\Gamma}.
+\end{equation*}
 
 % >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-Now, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-2D formulation
+Now, we apply a topological model reduction of the interface conditions, namely we go from a 3D-2D-1D formulation
 involving sub-problems on $\Omega$ and $\Lambda$ and coupling operators defined on $\Gamma$
@@
 \end{description}
-and we obtain 
-\begin{equation*}
-(\nabla u ,\nabla v)_{\Omega} +(u,v)_{\Omega}+(\avrc \lambda, \avrc v)_{\Lambda , |\DD|}  =(f,v)_{\Omega},
-\end{equation*}
-which, combined with \eqref{eq:1Ddirneu_weak} leads to the second formulation of the reduced problem.
+and the term $\left(\trace v, \lambda \right)_{\Gamma}$ becomes $\left( \mtrace v, \avrc{\lambda} \right)_{\Lambda, |\DD|}$, where $\mtrace$ denotes the composition of operators $\trace \circ \avrc{(\cdot)}$.
+Combined with \eqref{eq:1Ddirneu_weak}, this leads to the second formulation of the reduced problem.
 
-\subsection{Problem 2 (3D-1D-1D)}
+\subsubsection*{Problem 2 (3D-1D-1D)}
 Let $\langle \cdot , \cdot \rangle_\Lambda$ denote the duality pairing between 
@@
 We notice that all the integrals of the reduced problem are well defined because 
-$\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$ as shown in the following lemma.
+$\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$ as shown in the following.\\
 
@@
 
+From the theory of interpolation of Sobolev spaces  illustrated in \cite{chandler2015interpolation}, we can define the fractional norms $\|\cdot \|_{H^{\frac 12}(\Gamma)}$ and $\|\cdot \|_{H^{\frac 12}(\Lambda)}$ as functions of the eigenvalues and eigenfunctions of the Laplacian on $\Gamma$ and $\Lambda$ respectively.
+In particular, from \cite[Lemma 4.11]{chandler2015interpolation}, if we denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the Laplacian on $\Gamma$ with homogeneous Dirichlet condition at the boundary, for any function $u \in H^{\frac 12}_{00}(\Gamma)$ we have
+\begin{equation}\label{eq:fracnorm_gamma}
+\|u\|_{H^{\frac 12}(\Gamma)}=\left(\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2\right)^{\frac 12},
+\text{ with }
+a_{ij}=\left( u,\phi _{ij} \right)_{\Gamma}.
+\end{equation}
+Similarly, denoting with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the Laplacian on $\Lambda$ with homogenous Dirichlet boundary conditions, if $u \in H^{\frac 12}(\Lambda)$ we have
+\begin{equation}\label{eq:fracnorm_lambda}
+\|u\|_{H^{\frac 12}_{00}(\Lambda)}=\left(\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|a_i|^2\right)^{\frac 12},
+\text{ with }
+a_i=\left(u, \phi _i \right)_{\Lambda}.
+\end{equation}
+In the same way, we can define the equivalent weighted norm in $H^{\frac 12}_{00}(\Lambda)$
+\begin{equation}\label{eq:weightfracnorm}
+\|u\|_{H^{\frac 12}_{00}(\Lambda), |\DD|}=\left(\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|a_i|^2\right)^{\frac 12},
+\text{ with }
+a_i=\left(u, \phi _i \right)_{\Lambda, |\DD|}.
+\end{equation}
+
 \begin{lemma}\label{lemma:H12norm}
@@
 \begin{proof}
-Let us consider the eigenvalue problems for the Laplace operator on $\Gamma$ with homogeneous Dirichlet conditions at $x=0,\, X$ and periodic boundary conditions at $y=0,\, Y$ and on $(0,X)$ with homogeneous Dirichlet conditions.
-Let us denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the laplacian on $\Gamma$, and with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $(0,X)$.
+In order to apply \eqref{eq:fracnorm_gamma} and \eqref{eq:fracnorm_lambda}, let us consider the eigenvalue problems for the Laplace operator on $\Gamma$ with homogeneous Dirichlet conditions at $x=0,\, X$ and periodic boundary conditions at $y=0,\, Y$.
+Let us also consider the Laplace eigeinproblem on $(0,X)$ with homogeneous Dirichlet conditions.
+Let us denote as $\phi _{ij}(x,y)$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the Laplacian on $\Gamma$, and with $\phi _i(x)$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $(0,X)$.
 In particular,
@@
 \label{nonull_int_eigenf}
-\int_0^{Y} \phi _{ij}(x,y)= Y \, \sin\left(\frac{i\pi x}{X}\right) \quad \mbox{if } j=0, \forall i  .\\
+\int_0^{Y} \phi _{ij}(x,y)= Y \, \sin\left(\frac{i\pi x}{X}\right) \quad \mbox{if } j=0, \forall i  .
 \end{eqnarray}
-Moreover we recall that $\phi_{i,j}(x,y)$ and $\phi _i(x)$ are orthogonal basis of $L^2(\Gamma)$ and $L^2(0,X)$ respectively. Therefore,
+Moreover we recall that $\phi_{i,j}(x,y)$ and $\phi _i(x)$ form an orthogonal basis of $L^2(\Gamma)$ and $L^2(0,X)$ respectively. Therefore,
 \begin{multline*}
@@
 \end{multline*}
-From \cite[Lemma 4.11]{chandler2015interpolation} we have
-\begin{equation}\label{H12norm_Gamma}
-\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2,
-\text{ with }
-a_{ij}=\int _0^X\int _0^{Y} u(x,y )\phi_{ij} (x,y)dy dx.
-\end{equation}
-and 
-\begin{equation*}
-\|\avrc{u}\|^2_{H^{\frac 12}(0,X)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
-\text{ with }
-\avrc{a}_i=\int _0^X \avrc{u}(x )\phi_{i}(x) dx.
-\end{equation*}
+%From \cite[Lemma 4.11]{chandler2015interpolation} we have
+%\begin{equation}\label{H12norm_Gamma}
+%\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2,
+%\text{ with }
+%a_{ij}=\int _0^X\int _0^{Y} u(x,y )\phi_{ij} (x,y)dy dx.
+%\end{equation}
+%and 
+%\begin{equation*}
+%\|\avrc{u}\|^2_{H^{\frac 12}(0,X)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
+%\text{ with }
+%\avrc{a}_i=\int _0^X \avrc{u}(x )\phi_{i}(x) dx.
+%\end{equation*}
 
-Therefore, we have
+From \eqref{eq:fracnorm_lambda} we have
 \begin{multline*}
-\|\avrc{u}\|^2_{H^{\frac 12}(0,X)}=
-\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \int_0^X \avrc{u}(x) \sin\left(\frac{i\pi x}{X}\right)\, dx \right)^2\\
-= \sum_{i=1}^{\infty} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^1 \sin\left(\frac{j\pi x}{X}\right) \sin\left(\frac{i\pi x}{X}\right) \, dx  \right)^2\\
+\|\avrc{u}\|^2_{H^{\frac 12}(0,X)}
+=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}a_i^2\\
+=\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \int_0^X \avrc{u}(x) \sin\left(\frac{i\pi x}{X}\right)\, dx \right)^2\\
+= \sum_{i=1}^{\infty} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^X \sin\left(\frac{j\pi x}{X}\right) \sin\left(\frac{i\pi x}{X}\right) \, dx  \right)^2\\
 = \sum_{i=1}^{\infty} \frac{X^2}{4} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}a_{i,0}^2\\
@@
 \end{multline*}
-
 where we have used the fact that
@@
 &\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=0 \quad \text{if $i\neq j$}\\
-&\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=\frac X2 \quad \text{if $i =j$}.
+&\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=\frac X2 \quad \text{if $i =j$}
 \end{eqnarray*}
-Moreover, in the case in which $u$ is constant with respect to $y$, from \eqref{H12norm_Gamma} we have
+and we have applied \eqref{eq:fracnorm_gamma} in the last equality.
+Moreover, in the case in which $u$ is constant with respect to $y$, we have
 \begin{multline*}
@@
 
-\begin{corollary}
-Let $\Gamma$ be the lateral surface of a prism with $N$ faces $\Gamma_i$, $i=1, \dots, N$, with $\Gamma_i=(0,X_i)\times(0,S)$.
+%\begin{corollary}
+%Let $\Gamma$ be the lateral surface of a prism with $N$ faces $\Gamma_i$, $i=1, \dots, N$, with $\Gamma_i=(0,X_i)\times(0,S)$.
 For any $u\in H^{\frac 12}_{00}(\Gamma)$, let $\avrc{u}(s)= \frac{1}{\sum_i{|X_i|}}\sum_{i=1}^N \int_0^{X_i} u(x,s)\, dx$.
-Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$.
-\end{corollary}
+Then $\avrc{u}\in H^{\frac 12}_{00}(0,S )$ {\color{red} and there exists a constant $C_\Gamma$ such that
+%\begin{equation*}
+%\|\avrc{u}\|_{H^{\frac 12}(0,S)} \leq C_\Gamma \|u\|_{H^{\frac 12}(\Gamma)}.
+%\end{equation*}
+%}
+%\end{corollary}
 
@@
 Let $u\in H^{\frac 12}_{00}(\Gamma)$ and let $\avrc{u}(s)= \frac{1}{2\pi R} \int_0^{2\pi} u(s,\theta)R\, d\theta$.
-Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$.
+Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$ and there exists a constant $C_\Gamma$ such that
+\begin{equation*}
+\|\avrc{u}\|_{H^{\frac 12}(0,S)} \leq C_\Gamma \|u\|_{H^{\frac 12}(\Gamma)}.
+\end{equation*}
+\end{corollary}
+
+\begin{corollary}
+Let $\Gamma$ be the lateral surface of a generalized cylinder, being $\DD(s)$ the boundary of the cross section and $\Lambda$ its centerline.
+Let $u\in H^{\frac 12}_{00}(\Gamma)$ and let $\avrc{u}(s)= \frac{1}{|\DD(s)|} \int_{\DD} u \,d\gamma$.
+Then $\avrc{u}\in H^{\frac 12}_{00}(\Lambda)$  and there exists a constant $C_\Gamma$ such that
+\begin{equation*}
+\|\avrc{u}\|_{H^{\frac 12}(\Lambda), |\DD|} \leq C_\Gamma \|u\|_{H^{\frac 12}(\Gamma)}.
+\end{equation*}
 \end{corollary}

### 2019-10-18 code/test.sh
tests

@@ -1,0 +1,8 @@
+#! /bin/bash
+
+script=`ls test_*.py`
+for i in $script
+do
+    echo ">>>>>>>>>>>>>" $i "<<<<<<<<<<<<<<";
+    python $i;
+done

### 2019-10-18 code/test_cross_avg.py

@@ -1,0 +1,93 @@
+# Gamma as straight line {0.5}x{0.5}x(0, 1)
+# Omega as [0, 1]^2
+#
+# I consider q from the benchmark q = sin(pi*z/H)
+
+from weak_bcs.burman.generation import line_mesh, line, StraightLineMesh
+from dolfin import *
+from xii import *
+from xii.assembler.average_matrix import average_matrix
+import numpy as np
+
+
+def test_vol_approx(n, f, true=None):
+    '''Volume integral (for benchmark problem)'''
+    omega = UnitCubeMesh(n, n, 2*n)
+
+    A = np.array([0.5, 0.5, 0.0])
+    B = np.array([0.5, 0.5, 1.0])             
+    gamma = StraightLineMesh(A, B, 2*n)
+
+    V3 = FunctionSpace(omega, 'CG', 1)
+    V1 = FunctionSpace(gamma, 'CG', 1)
+
+    f3 = interpolate(f, V3)
+
+    shape = Square(P=lambda x: np.array([0.25, 0.25, x[2]]),
+                   degree=10)
+
+    Pi = average_matrix(V3, V1, shape=shape)
+    x = Pi*f3.vector()
+    f1 = Function(V1, x)
+
+    if true is None:
+        true = f
+    error = sqrt(abs(assemble(inner(true - f1, true - f1)*dx)))
+
+    return gamma.hmin(), error, f1
+
+# --------------------------------------------------------------------
+
+if __name__ == '__main__':
+    from test_surf_avg import analyze_convergence
+    from functools import partial
+    import sympy as sp
+
+    ns = (4, 8, 16, 32)
+    
+    # Convergence to 'identity'
+    f = Expression('sin(pi*x[2])', degree=5)
+    get_error = partial(test_vol_approx, f=f, true=f)
+    rate, error = analyze_convergence(ns, get_error)[2:]
+    assert rate > 1
+    
+    # Should be exact right away
+    f = Expression('2*x[2]', degree=5)
+    get_error = partial(test_vol_approx, f=f, true=f)
+    rate, error = analyze_convergence(ns, get_error)[2:]
+    assert error < 1E-12
+
+    # The exact solution in 3d has Avg(u) != 0
+    f = Expression('sin(2*pi*x[0])*sin(2*pi*x[1])', degree=5)
+
+    x = sp.Symbol('x')
[…]

### 2019-10-18 code/test_ext.py

@@ -1,0 +1,76 @@
+# Gamma as straight line {0.5}x{0.5}x(0, 1)
+# Omega as [0, 1]^2
+#
+# I consider q from the benchmark q = sin(pi*z/H)
+
+from weak_bcs.burman.generation import line_mesh, line, StraightLineMesh
+from dolfin import *
+from xii import *
+from xii.assembler.extension_matrix import uniform_extension_matrix
+import numpy as np
+
+set_log_level(WARNING)
+
+
+def test_ext(n, f, true=None):
+    '''Surface integral (for benchmark problem)'''
+    omega = UnitCubeMesh(n, n, 2*n)
+
+    A = np.array([0.5, 0.5, 0.0])
+    B = np.array([0.5, 0.5, 1.0])             
+    lmbda = StraightLineMesh(A, B, 2*n)  # The curve
+
+    # Coupling surface
+    walls = ['near((x[0]-0.25)*(x[0]-0.75), 0) && ((0.25-tol) < x[1]) && ((0.75+tol) > x[1])',
+             'near((x[1]-0.25)*(x[1]-0.75), 0) && ((0.25-tol) < x[0]) && ((0.75+tol) > x[0])']
+    walls = ['( %s )' % w for w in walls]
+    
+    chi = CompiledSubDomain(' || '.join(walls), tol=1E-10)
+    surfaces = MeshFunction('size_t', omega, 2, 0)
+    chi.mark(surfaces, 1)
+
+    gamma = EmbeddedMesh(surfaces, 1)
+
+    V3 = FunctionSpace(omega, 'CG', 1)
+    V2 = FunctionSpace(gamma, 'CG', 1)
+    V1 = FunctionSpace(lmbda, 'CG', 1)
+
+    # What we want to extend
+    f1 = interpolate(f, V1)
+
+    E = uniform_extension_matrix(V1, V2)
+    x = E*f1.vector()
+    f2 = Function(V2, x)
+
+    if true is None:
+        true = f
+    error = sqrt(abs(assemble(inner(true - f2, true - f2)*dx)))
+
+    return gamma.hmin(), error, f2
+
+# --------------------------------------------------------------------
+
+if __name__ == '__main__':
+    from test_surf_avg import analyze_convergence
+    from functools import partial
+    import sympy as sp
+
+    ns = (4, 8, 16, 32)
+    
+    # Exact
+    f = Constant(1)
+    get_error = partial(test_ext, f=f, true=f)
[…]

### 2019-10-18 code/test_surf_avg.py

@@ -1,0 +1,104 @@
+# Gamma as straight line {0.5}x{0.5}x(0, 1)
+# Omega as [0, 1]^2
+#
+# I consider q from the benchmark q = sin(pi*z/H)
+
+from weak_bcs.burman.generation import line_mesh, line, StraightLineMesh
+from dolfin import *
+from xii import *
+from xii.assembler.average_matrix import average_matrix
+import numpy as np
+
+
+def analyze_convergence(ns, get_error):
+    '''get_error: n -> h, e'''
+    her = []  # h error rate
+    for n in ns:
+        h, e, f = get_error(n)
+
+        if her:
+            h0, e0, _ = her[-1]
+            rate = np.log(e/e0)/np.log(h/h0)
+        else:
+            rate = np.nan
+
+        print 'n(%g) -> %g %g [%g]' % (n, h, e, rate)
+        her.append([h, e, rate])
+    # Final fit
+    h, e, _ = np.array(her).T
+
+    rate, _ = np.polyfit(np.log(h), np.log(e), deg=1)
+    print 'Final rate %g \n' % rate
+    
+    return her, f, rate, np.mean(e)
+
+
+def test_surf_approx(n, f, true=None):
+    '''Surface integral (for benchmark problem)'''
+    omega = UnitCubeMesh(n, n, 2*n)
+
+    A = np.array([0.5, 0.5, 0.0])
+    B = np.array([0.5, 0.5, 1.0])             
+    gamma = StraightLineMesh(A, B, 2*n)
+
+    V3 = FunctionSpace(omega, 'CG', 1)
+    V1 = FunctionSpace(gamma, 'CG', 1)
+
+    f3 = interpolate(f, V3)
+
+    shape = SquareRim(P=lambda x: np.array([0.25, 0.25, x[2]]),
+                      degree=10)
+
+    Pi = average_matrix(V3, V1, shape=shape)
+    x = Pi*f3.vector()
+
+    f1 = Function(V1, x)
+
+    if true is None:
+        true = f
+    error = sqrt(abs(assemble(inner(true - f1, true - f1)*dx)))
+
+    return gamma.hmin(), error, f1
+
+# --------------------------------------------------------------------
+
+if __name__ == '__main__':
+    from functools import partial
+    import sympy as sp
+
+    ns = (4, 8, 16, 32)
+    
+    # Convergence to 'identity'
+    f = Expression('sin(pi*x[2])', degree=5)
[…]

### 2019-10-18 code/test_identity.py
more tests

@@ -1,24 +1,23 @@
-# Gamma as straight line {0.5}x{0.5}x(0, 1)
-# Omega as [0, 1]^2
-#
-# I consider q from the benchmark q = sin(pi*z/H)
+# If I extend 1d to 2d (then 3d) and reduce back to 1d do I get the same
 
 from weak_bcs.burman.generation import line_mesh, line, StraightLineMesh
 from dolfin import *
 from xii import *
 from xii.assembler.extension_matrix import uniform_extension_matrix
+from xii.assembler.average_matrix import average_matrix
 import numpy as np
 
 set_log_level(WARNING)
 
 
-def test_ext(n, f, true=None):
+def test_id(n, f, align=True):
     '''Surface integral (for benchmark problem)'''
     omega = UnitCubeMesh(n, n, 2*n)
 
     A = np.array([0.5, 0.5, 0.0])
-    B = np.array([0.5, 0.5, 1.0])             
-    lmbda = StraightLineMesh(A, B, 2*n)  # The curve
+    B = np.array([0.5, 0.5, 1.0])
+
+    lmbda = StraightLineMesh(A, B, 2*n if align else n)  # The curve
 
     # Coupling surface
     walls = ['near((x[0]-0.25)*(x[0]-0.75), 0) && ((0.25-tol) < x[1]) && ((0.75+tol) > x[1])',
@@ -37,16 +36,36 @@ def test_ext(n, f, true=None):
 
     # What we want to extend
     f1 = interpolate(f, V1)
-
+    # To 2d
     E = uniform_extension_matrix(V1, V2)
     x = E*f1.vector()
     f2 = Function(V2, x)
+    # Extend to 3d by harmonic extension
+    u, v = TrialFunction(V3), TestFunction(V3)
+    a, L = inner(grad(u), grad(v))*dx, inner(Constant(0), v)*dx
+    bcs = [DirichletBC(V3, f, 'on_boundary'),
+           DirichletBC(V3, f, surfaces, 1)]
 
-    if true is None:
-        true = f
-    error = sqrt(abs(assemble(inner(true - f2, true - f2)*dx)))
+    A, b = assemble_system(a, L, bcs)
+    f3 = Function(V3)
+    
+    solver = KrylovSolver('cg', 'hypre_amg')
+    solver.parameters['relative_tolerance'] = 1E-13
+    
+    solver.solve(A, f3.vector(), b)
 
-    return gamma.hmin(), error, f2
[…]

### 2019-10-18 code/test_trace.py

@@ -1,24 +1,20 @@
 # Gamma as straight line {0.5}x{0.5}x(0, 1)
 # Omega as [0, 1]^2
 #
-# I consider q from the benchmark q = sin(pi*z/H)
+# Things for formulation with the multiplier on surface
 
-from weak_bcs.burman.generation import line_mesh, line, StraightLineMesh
+
 from dolfin import *
 from xii import *
-from xii.assembler.extension_matrix import uniform_extension_matrix
+from xii.assembler.trace_matrix import trace_mat_no_restrict
 import numpy as np
 
 set_log_level(WARNING)
 
 
-def test_ext(n, f, true=None):
+def test_trace(n, f, true=None):
     '''Surface integral (for benchmark problem)'''
-    omega = UnitCubeMesh(n, n, 2*n)
-
-    A = np.array([0.5, 0.5, 0.0])
-    B = np.array([0.5, 0.5, 1.0])             
-    lmbda = StraightLineMesh(A, B, 2*n)  # The curve
+    omega = UnitCubeMesh(n, n, n)
 
     # Coupling surface
     walls = ['near((x[0]-0.25)*(x[0]-0.75), 0) && ((0.25-tol) < x[1]) && ((0.75+tol) > x[1])',
@@ -33,13 +29,12 @@ def test_ext(n, f, true=None):
 
     V3 = FunctionSpace(omega, 'CG', 1)
     V2 = FunctionSpace(gamma, 'CG', 1)
-    V1 = FunctionSpace(lmbda, 'CG', 1)
 
     # What we want to extend
-    f1 = interpolate(f, V1)
+    f3 = interpolate(f, V3)
 
-    E = uniform_extension_matrix(V1, V2)
-    x = E*f1.vector()
+    T = PETScMatrix(trace_mat_no_restrict(V3, V2))
+    x = T*f3.vector()
     f2 = Function(V2, x)
 
     if true is None:
@@ -59,20 +54,24 @@ if __name__ == '__main__':
     
     # Exact
     f = Constant(1)
-    get_error = partial(test_ext, f=f, true=f)
+    get_error = partial(test_trace, f=f, true=f)
     rate, error = analyze_convergence(ns, get_error)[2:]
     assert error < 1E-12
 
-    # Exact
-    f = Expression('x[2]', degree=5)
-    get_error = partial(test_ext, f=f, true=f)
+    # Exact as we have P1
+    f = Expression('x[0] - x[1] + 2*x[2]', degree=2)
[…]

### 2019-10-18 code/test_Pi_coupling.py
Pi okay

@@ -1,0 +1,112 @@
+# (Pi u_3d, u_1d)_Gamma integrals
+
+from weak_bcs.burman.generation import line_mesh, line, StraightLineMesh
+from dolfin import *
+from xii import *
+from xii.assembler.average_matrix import average_matrix
+import numpy as np
+
+
+def test_Pi(n, f3, f1, Pi_f3):
+    '''(Pi u_3d, u_1d)_Gamma.'''
+    # True here is the reduced one
+    omega = UnitCubeMesh(n, n, 2*n)
+
+    A = np.array([0.5, 0.5, 0.0])
+    B = np.array([0.5, 0.5, 1.0])             
+    gamma = StraightLineMesh(A, B, 2*n)
+
+    V3 = FunctionSpace(omega, 'CG', 1)
+    V1 = FunctionSpace(gamma, 'CG', 1)
+
+    u3 = TrialFunction(V3)
+    v1 = TestFunction(V1)
+
+    shape = SquareRim(P=lambda x: np.array([0.25, 0.25, x[2]]),
+                      degree=10)
+
+    dx_ = Measure('dx', domain=gamma)
+    a = inner(Average(u3, gamma, shape=shape), v1)*dx_
+
+    A = ii_assemble(a)
+
+    # Now check action
+    f3h = interpolate(f3, V3)
+    x = A*f3h.vector()
+
+    f1h = interpolate(f1, V1)
+    Pi_f = Function(V1, x)
+    result = f1h.vector().inner(x)
+
+    true = assemble(inner(Pi_f3, f1)*dx_)
+    
+    error = abs(true - result)
+
+    return gamma.hmin(), error, Pi_f
+
+# --------------------------------------------------------------------
+
+if __name__ == '__main__':
+    from test_surf_avg import analyze_convergence
+    from functools import partial
+    import sympy as sp
+
+    ns = (4, 8, 16, 32)
+    
+    # Exact, exact
+    f3, f1 = Constant(2), Constant(3)
+    get_error = partial(test_Pi, f3=f3, f1=f1, Pi_f3=f3)
+    rate, error = analyze_convergence(ns, get_error)[2:]
+    assert error < 1E-12
+
+    # Exact, exact
+    f3, f1 = Expression('x[2]', degree=3), Expression('x[2]', degree=3)
[…]

### 2019-10-18 code/test_ET_coupling.py
coupling tests

@@ -1,0 +1,79 @@
+# (E u_1d, T u_3d)_Gamma integrals
+
+from weak_bcs.burman.generation import line_mesh, line, StraightLineMesh
+from dolfin import *
+from xii import *
+import numpy as np
+
+
+def test_ET(n, f3, f1):
+    '''(E u_1d, T u_3d)_Gamma.'''
+    # True here is the reduced one
+    omega = UnitCubeMesh(n, n, 2*n)
+
+    # Coupling surface
+    walls = ['near((x[0]-0.25)*(x[0]-0.75), 0) && ((0.25-tol) < x[1]) && ((0.75+tol) > x[1])',
+             'near((x[1]-0.25)*(x[1]-0.75), 0) && ((0.25-tol) < x[0]) && ((0.75+tol) > x[0])']
+    walls = ['( %s )' % w for w in walls]
+    
+    chi = CompiledSubDomain(' || '.join(walls), tol=1E-10)
+    surfaces = MeshFunction('size_t', omega, 2, 0)
+    chi.mark(surfaces, 1)
+
+    gamma = EmbeddedMesh(surfaces, 1)
+
+    A = np.array([0.5, 0.5, 0.0])
+    B = np.array([0.5, 0.5, 1.0])             
+    lmbda = StraightLineMesh(A, B, 2*n)  # The curve
+
+    V3 = FunctionSpace(omega, 'CG', 1)
+    V2 = FunctionSpace(gamma, 'CG', 2)
+    V1 = FunctionSpace(lmbda, 'CG', 1)
+    
+    u1 = TrialFunction(V1)
+    v3 = TestFunction(V3)
+
+    dx_ = Measure('dx', domain=gamma)
+    a = inner(Extension(u1, gamma, 'uniform'), Trace(v3, gamma))*dx_
+
+    A = ii_assemble(a)
+
+    # Now check action
+    f1h = interpolate(f1, V1)
+    x = A*f1h.vector()
+
+    f3h = interpolate(f3, V3)
+    result = f3h.vector().inner(x)
+
+    true = assemble(inner(f3, f1)*dx_)
+
+    error = abs(true - result)
+
+    return gamma.hmin(), error, f3h
+
+# --------------------------------------------------------------------
+
+if __name__ == '__main__':
+    from test_surf_avg import analyze_convergence
+    from functools import partial
+    import sympy as sp
+
+    ns = (4, 8, 16, 32)
+    
+    # Exact, exact
[…]

### 2019-10-18 code/test_E_coupling.py

@@ -1,0 +1,85 @@
+# (E u_1d, u_2d)_Gamma integrals
+
+from weak_bcs.burman.generation import line_mesh, line, StraightLineMesh
+from dolfin import *
+from xii import *
+import numpy as np
+
+
+def test_E(n, f2, f1):
+    '''(E u_1d, u_2d)_Gamma.'''
+    # True here is the reduced one
+    omega = UnitCubeMesh(n, n, 2*n)
+
+    # Coupling surface
+    walls = ['near((x[0]-0.25)*(x[0]-0.75), 0) && ((0.25-tol) < x[1]) && ((0.75+tol) > x[1])',
+             'near((x[1]-0.25)*(x[1]-0.75), 0) && ((0.25-tol) < x[0]) && ((0.75+tol) > x[0])']
+    walls = ['( %s )' % w for w in walls]
+    
+    chi = CompiledSubDomain(' || '.join(walls), tol=1E-10)
+    surfaces = MeshFunction('size_t', omega, 2, 0)
+    chi.mark(surfaces, 1)
+
+    gamma = EmbeddedMesh(surfaces, 1)
+
+    A = np.array([0.5, 0.5, 0.0])
+    B = np.array([0.5, 0.5, 1.0])             
+    lmbda = StraightLineMesh(A, B, 2*n)  # The curve
+
+    V3 = FunctionSpace(omega, 'CG', 1)
+    V2 = FunctionSpace(gamma, 'CG', 1)
+    V1 = FunctionSpace(lmbda, 'CG', 1)
+    
+    u1 = TrialFunction(V1)
+    v2 = TestFunction(V2)
+
+    dx_ = Measure('dx', domain=gamma)
+    a = inner(Extension(u1, gamma, 'uniform'), v2)*dx_
+
+    A = ii_assemble(a)
+
+    # Now check action
+    f1h = interpolate(f1, V1)
+    x = A*f1h.vector()
+
+    f2h = interpolate(f2, V2)
+    result = f2h.vector().inner(x)
+
+    true = assemble(inner(f2, f1)*dx_)
+
+    error = abs(true - result)
+
+    return gamma.hmin(), error, Function(V2, x)
+
+# --------------------------------------------------------------------
+
+if __name__ == '__main__':
+    from test_surf_avg import analyze_convergence
+    from functools import partial
+    import sympy as sp
+
+    ns = (4, 8, 16, 32)
+    
+    # Exact, exact
[…]

### 2019-10-18 code/test_Pi_coupling.py

@@ -3,7 +3,6 @@
 from weak_bcs.burman.generation import line_mesh, line, StraightLineMesh
 from dolfin import *
 from xii import *
-from xii.assembler.average_matrix import average_matrix
 import numpy as np
 
 

### 2019-10-18 code/test_T_coupling.py

@@ -1,0 +1,74 @@
+# (T u_3d, u_2d)_Gamma integrals
+
+from dolfin import *
+from xii import *
+import numpy as np
+
+
+def test_T(n, f3, f2):
+    '''(T u_3d, u_2d)_Gamma.'''
+    # True here is the reduced one
+    omega = UnitCubeMesh(n, n, 2*n)
+
+    # Coupling surface
+    walls = ['near((x[0]-0.25)*(x[0]-0.75), 0) && ((0.25-tol) < x[1]) && ((0.75+tol) > x[1])',
+             'near((x[1]-0.25)*(x[1]-0.75), 0) && ((0.25-tol) < x[0]) && ((0.75+tol) > x[0])']
+    walls = ['( %s )' % w for w in walls]
+    
+    chi = CompiledSubDomain(' || '.join(walls), tol=1E-10)
+    surfaces = MeshFunction('size_t', omega, 2, 0)
+    chi.mark(surfaces, 1)
+
+    gamma = EmbeddedMesh(surfaces, 1)
+
+    V3 = FunctionSpace(omega, 'CG', 1)
+    V2 = FunctionSpace(gamma, 'CG', 1)
+
+    u3 = TrialFunction(V3)
+    v2 = TestFunction(V2)
+
+    dx_ = Measure('dx', domain=gamma)
+    a = inner(Trace(u3, gamma), v2)*dx_
+
+    A = ii_assemble(a)
+
+    # Now check action
+    f3h = interpolate(f3, V3)
+    x = A*f3h.vector()
+
+    f2h = interpolate(f2, V2)
+    result = f2h.vector().inner(x)
+
+    true = assemble(inner(f2, f3)*dx_)
+    
+    error = abs(true - result)
+
+    return gamma.hmin(), error, Function(V2, x)
+
+# --------------------------------------------------------------------
+
+if __name__ == '__main__':
+    from test_surf_avg import analyze_convergence
+    from functools import partial
+    import sympy as sp
+
+    ns = (4, 8, 16, 32)
+    
+    # Exact, exact
+    f3, f2 = Constant(2), Constant(3)
+    get_error = partial(test_T, f3=f3, f2=f2)
+    rate, error = analyze_convergence(ns, get_error)[2:]
+    assert error < 1E-12
+
+    # Exact, exact
+    f3 = Expression('x[0] - x[2] + 2*x[1]', degree=3)
[…]

### 2019-10-18 code/test_surf_avg.py

@@ -8,6 +8,7 @@ from dolfin import *
 from xii import *
 from xii.assembler.average_matrix import average_matrix
 import numpy as np
+import warnings
 
 
 def analyze_convergence(ns, get_error):
@@ -18,7 +19,10 @@ def analyze_convergence(ns, get_error):
 
         if her:
             h0, e0, _ = her[-1]
-            rate = np.log(e/e0)/np.log(h/h0)
+            try:
+                rate = np.log(e/e0)/np.log(h/h0)
+            except ZeroDivisionError:
+                rate = np.nan
         else:
             rate = np.nan
 
@@ -27,8 +31,9 @@ def analyze_convergence(ns, get_error):
     # Final fit
     h, e, _ = np.array(her).T
 
-    rate, _ = np.polyfit(np.log(h), np.log(e), deg=1)
-    print 'Final rate %g \n' % rate
+    with warnings.catch_warnings('error'):
+        rate, _ = np.polyfit(np.log(h), np.log(e), deg=1)
+        print 'Final rate %g \n' % rate
     
     return her, f, rate, np.mean(e)
 

### 2019-10-18 code/test_subdomain_solvers.py
check components

@@ -1,0 +1,71 @@
+from weak_bcs.burman.generation import StraightLineMesh
+from dolfin import *
+import numpy as np
+
+
+def poisson_3d(n, u_true, f):
+    '''3d part of benchmark'''
+    mesh = UnitCubeMesh(n, n, n)
+
+    V = FunctionSpace(mesh, 'CG', 1)
+    bc = DirichletBC(V, u_true, 'on_boundary')
+    
+    u, v = TrialFunction(V), TestFunction(V)
+    a = inner(grad(u), grad(v))*dx
+    L = inner(f, v)*dx
+
+    A, b = assemble_system(a, L, bc)
+
+    solver = KrylovSolver('cg', 'amg')
+    solver.parameters['relative_tolerance'] = 1E-13
+
+    uh = Function(V)
+    solver.solve(A, uh.vector(), b)
+    
+    return mesh.hmin(), errornorm(u_true, uh, 'H1'), uh
+
+
+def poisson_1d(n, u_true, f):
+    '''1d part of benchmark'''
+    A, B = np.array([0.5, 0.5, 0]), np.array([0.5, 0.5, 1])
+    mesh = StraightLineMesh(A, B, n)
+
+    V = FunctionSpace(mesh, 'CG', 1)
+    bc = DirichletBC(V, u_true, 'on_boundary')
+    
+    u, v = TrialFunction(V), TestFunction(V)
+    a = inner(grad(u), grad(v))*dx
+    L = inner(f, v)*dx
+
+    A, b = assemble_system(a, L, bc)
+
+    solver = KrylovSolver('cg', 'amg')
+    solver.parameters['relative_tolerance'] = 1E-13
+
+    uh = Function(V)
+    solver.solve(A, uh.vector(), b)
+
+    return mesh.hmin(), errornorm(u_true, uh, 'H1'), uh
+
+# --------------------------------------------------------------------
+
+if __name__ == '__main__':
+    from test_surf_avg import analyze_convergence
+    from functools import partial
+
+
+    ns = (4, 8, 16, 32)
+    # 3d
+    u3d = Expression('sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)
+    f3d = Expression('(8*pi*pi)*sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)    
+    get_error = partial(poisson_3d, f=f3d, u_true=u3d)
+    rate, error = analyze_convergence(ns, get_error)[2:]
[…]

### 2019-10-18 src_lm3d1d/poisson_3d.py
update

@@ -1,0 +1,57 @@
+from dolfin import *
+from xii import *
+from weak_bcs.utils import block_form, MMSData, H1_norm
+from block import block_mat, block_vec
+import numpy as np
+
+
+def setup_mms(params):
+    '''Manufactured solution'''
+    
+    u3d = Expression('sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)
+    f3d = Expression('(8*pi*pi)*sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)    
+
+    return MMSData(solution=[u3d], rhs=[f3d], subdomains=['on_boundary'],normals=None)
+
+
+def setup_problem(n, mms, params):
+    '''Poisson solver'''
+    mesh = UnitCubeMesh(n, n, n)
+    
+    V = FunctionSpace(mesh, 'CG', 1)
+
+    # Just one
+    boundaries = MeshFunction('size_t', mesh, 2, 0)
+    for tag, subd in enumerate(mms.subdomains, 1):
+        CompiledSubDomain(subd, tol=1E-10).mark(boundaries, tag)
+
+    u_true,  = mms.solution
+    bc = DirichletBC(V, u_true, boundaries, 1)
+
+    f, = mms.rhs
+    
+    u, v = TrialFunction(V), TestFunction(V)
+    a = inner(grad(u), grad(v))*dx
+    L = inner(f, v)*dx
+
+    A, b = assemble_system(a, L, bc)
+
+    return block_mat([[A]]), block_vec([b]), [V]
+
+
+def setup_error_monitor(mms_data, params):
+    '''We look at H1 norm'''
+    # Error of the passed wh
+    
+    def get_error(wh, u_exact=mms_data.solution[0]):
+        # We look at the H1 error for velocity
+        uh, = wh
+
+        return (H1_norm(u_exact, uh), )
+    # Pretty print
+    error_types = ('|u|_1', )
+    
+    return get_error, error_types
+
+# How is the problem parametrized
+PARAMETERS = ('mu', )

### 2019-10-18 src_lm3d1d/coupled_lm1.py
line multiplier

@@ -1,0 +1,159 @@
+# Formulation with the multiplier on the curve
+from dolfin import *
+from xii import *
+from weak_bcs.utils import block_form, MMSData, H1_norm, Hs0_norm, matrix_fromHs
+from hsmg.hseig import Hs0Norm
+from block.algebraic.petsc import LU, AMG
+from block import block_mat, block_vec
+import numpy as np
+
+
+def setup_mms(params):
+    '''Manufactured solution from notes'''
+    
+    u3d = Expression('sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)
+    f3d = Expression('(8*pi*pi)*sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)
+
+    f1d = Expression('pi*pi*sin(pi*x[2])', degree=4)
+    u1d = Expression('sin(pi*x[2])', degree=4)
+
+    p = Expression('0', degree=4)  # The multiplier
+
+    return MMSData(solution=[u3d, u1d, p],
+                   rhs=[(f3d, f1d, u1d), (u3d, u1d, p)],
+                   subdomains=[], normals=None)
+
+
+def setup_problem(n, mms, params):
+    '''Poisson solver'''
+    mesh = UnitCubeMesh(n, n, n)
+
+
+    '''Coupled 3d-1d with 1d Lagrange multiplier'''
+    # NOTE: inborg distinguishes between parallel and not parallel hmin
+    omega = UnitCubeMesh(n, n, n)
+
+    A, B = np.array([0.5, 0.5, 0]), np.array([0.5, 0.5, 1])
+    gamma = StraightLineMesh(A, B, n)
+
+    # The poisson problem
+    V3 = FunctionSpace(omega, 'CG', 1)
+    V1 = FunctionSpace(gamma, 'CG', 1)
+    Q = FunctionSpace(gamma, 'CG', 1)
+    
+    W = [V3, V1, Q]
+
+    u3, u1, p = map(TrialFunction, W)
+    v3, v1, q = map(TestFunction, W)
+
+    # The size of averaging square is 0.5
+    alen = 0.5
+    avg_shape = SquareRim(lambda x: np.array([0.25, 0.25, x[-1]]), degree=10)
+
+    # Setup bounding curve
+    Pi_u3, Pi_v3 = (Average(f, gamma, avg_shape) for f in (u3, v3))
+
+    # Cell integral of Qspace
+    dx_ = Measure('dx', domain=gamma)
+    avg_len = Constant(4*alen)
[…]

### 2019-10-18 src_lm3d1d/coupled_lm1.py
lm2 does not converge - work cut out...

@@ -25,10 +25,6 @@ def setup_mms(params):
 
 
 def setup_problem(n, mms, params):
-    '''Poisson solver'''
-    mesh = UnitCubeMesh(n, n, n)
-
-
     '''Coupled 3d-1d with 1d Lagrange multiplier'''
     # NOTE: inborg distinguishes between parallel and not parallel hmin
     omega = UnitCubeMesh(n, n, n)
@@ -77,7 +73,7 @@ def setup_problem(n, mms, params):
     # Account for reduction from volume to line
     avg_shape = Square(lambda x: np.array([0.25, 0.25, x[-1]]), degree=10)
     # NOTE: Avg only works with functions so need to interpolate it
-    V3h = FunctionSpace(mesh, 'CG', 2)
+    V3h = FunctionSpace(omega, 'CG', 2)
     f1h = interpolate(f1, V3h)
     L[1] = avg_area*inner(Average(f1h, gamma, avg_shape), v1)*dx_
 
@@ -112,7 +108,7 @@ def setup_error_monitor(mms_data, params):
         # is expensive so wi reduce order then
         degree_rise = 1 if u3h.function_space().dim() < 2E6 else 0
         # NOTE: the error is interpolated to P2 disc, or P1 disc
-        return (H1_norm(u1, u1h, degree_rise=degree_rise),
+        return (H1_norm(u3, u3h, degree_rise=degree_rise),
                 H1_norm(u1, u1h, degree_rise=1),  
                 Hs0Norm(p, ph))
     # Pretty print

### 2019-10-18 src_lm3d1d/coupled_lm2.py

@@ -1,0 +1,114 @@
+# Formulation with the multiplier on the surface
+from dolfin import *
+from xii import *
+from weak_bcs.utils import block_form, MMSData, H1_norm, Hs0_norm, matrix_fromHs
+import src_lm3d1d.coupled_lm1 as lm1
+from hsmg.hseig import Hs0Norm
+from block.algebraic.petsc import LU, AMG
+from block import block_mat, block_vec
+import numpy as np
+
+# NOTE: - integrate only outside
+#       - adjust mesh to have really R small (modelling error)
+#         (THIS MIGHT REQUIRE CHANGING THE SOLUTION TO HAVE THE PROPERTIES
+#          OF THE ORIGINAL ONE)
+#
+#       - make HsNorm use our eigh
+
+def setup_problem(n, mms, params):
+    '''Coupled 3d-1d with 2d Lagrange multiplier'''
+    # NOTE: inborg distinguishes between parallel and not parallel hmin
+    omega = UnitCubeMesh(n, n, n)
+
+    size = params.size
+    # Coupling surface
+    walls = ['near((x[0]-L)*(x[0]-H), 0) && ((L-tol) < x[1]) && ((H+tol) > x[1])',
+             'near((x[1]-L)*(x[1]-H), 0) && ((L-tol) < x[0]) && ((H+tol) > x[0])']
+    walls = ['( %s )' % w for w in walls]
+    
+    chi = CompiledSubDomain(' || '.join(walls), tol=1E-10, L=0.5-size, H=0.5+size)
+    surfaces = MeshFunction('size_t', omega, 2, 0)
+    chi.mark(surfaces, 1)
+
+    gamma = EmbeddedMesh(surfaces, 1)
+
+    # Centerline
+    A, B = np.array([0.5, 0.5, 0]), np.array([0.5, 0.5, 1])
+    lmbda = StraightLineMesh(A, B, n)  
+
+    # The poisson problem
+    V3 = FunctionSpace(omega, 'CG', 1)
+    V1 = FunctionSpace(lmbda, 'CG', 1)
+    Q = FunctionSpace(gamma, 'CG', 1)
+    
+    W = [V3, V1, Q]
+
+    u3, u1, p = map(TrialFunction, W)
+    v3, v1, q = map(TestFunction, W)
+
+    Tu3, Tv3 = (Trace(f, gamma) for f in (u3, v3))
+    Eu1, Ev1 = (Extension(f, gamma, type='uniform') for f in (u1, v1))
+    
[…]

### 2019-10-19 src_lm3d1d/coupled_lm1.py
update

@@ -1,7 +1,7 @@
 # Formulation with the multiplier on the curve
 from dolfin import *
 from xii import *
-from weak_bcs.utils import block_form, MMSData, H1_norm, Hs0_norm, matrix_fromHs
+from weak_bcs.utils import block_form, MMSData, H1_norm, L2_norm
 from hsmg.hseig import Hs0Norm
 from block.algebraic.petsc import LU, AMG
 from block import block_mat, block_vec
@@ -21,7 +21,7 @@ def setup_mms(params):
 
     return MMSData(solution=[u3d, u1d, p],
                    rhs=[(f3d, f1d, u1d), (u3d, u1d, p)],
-                   subdomains=[], normals=None)
+                   subdomains=[], normals=[])
 
 
 def setup_problem(n, mms, params):
@@ -97,22 +97,29 @@ def setup_error_monitor(mms_data, params):
     '''We look at H1, H1, Hs norm'''
     # Error of the passed wh
     
-    def get_error(wh, w=mms_data.solution):
+    def get_error(wh, mms=mms_data):
         # We look at the H1 error for velocity
-        u3, u1, p = w
+        u3, u1, p = mms.solution
         u3h, u1h, ph = wh
 
-        Hs0Norm = Hs0_norm(s=-0.5)
+        # Passing the HsNorm from preconditioner so that we don't compute
+        # eigenvalues twice
+        Hs0Norm = mms.normals.pop()
+        # e*H*e ie (e, e)_H
+        e = interpolate(p, ph.function_space()).vector()
+        e.axpy(-1, ph.vector())
 
+        e = np.sqrt(e.inner(Hs0Norm*e))
         # On big meshes constructing the error for interpolation space
         # is expensive so wi reduce order then
         degree_rise = 1 if u3h.function_space().dim() < 2E6 else 0
         # NOTE: the error is interpolated to P2 disc, or P1 disc
         return (H1_norm(u3, u3h, degree_rise=degree_rise),
-                H1_norm(u1, u1h, degree_rise=1),  
-                Hs0Norm(p, ph))
+                H1_norm(u1, u1h),  
+                e,
+                L2_norm(p, ph))
     # Pretty print
-    error_types = ('|u3|_1', '|u1|_1', '|p|_{-1/2}')
[…]

### 2019-10-19 src_lm3d1d/coupled_lm2.py

@@ -8,19 +8,13 @@ from block.algebraic.petsc import LU, AMG
 from block import block_mat, block_vec
 import numpy as np
 
-# NOTE: - integrate only outside
-#       - adjust mesh to have really R small (modelling error)
-#         (THIS MIGHT REQUIRE CHANGING THE SOLUTION TO HAVE THE PROPERTIES
-#          OF THE ORIGINAL ONE)
-#
-#       - make HsNorm use our eigh
 
 def setup_problem(n, mms, params):
     '''Coupled 3d-1d with 2d Lagrange multiplier'''
     # NOTE: inborg distinguishes between parallel and not parallel hmin
     omega = UnitCubeMesh(n, n, n)
 
-    size = params.size
+    size = 0.25
     # Coupling surface
     walls = ['near((x[0]-L)*(x[0]-H), 0) && ((L-tol) < x[1]) && ((H+tol) > x[1])',
              'near((x[1]-L)*(x[1]-H), 0) && ((L-tol) < x[0]) && ((H+tol) > x[0])']
@@ -80,7 +74,7 @@ def setup_problem(n, mms, params):
     f1h = interpolate(f1, V3h)
     L[1] = avg_area*inner(Average(f1h, lmbda, avg_shape), v1)*dl
 
-    L[2] = inner(-fI, q)*dx_
+    L[2] = inner(fI, q)*dx_
     
     # Homog everywhere
     V3_bcs = [DirichletBC(V3, g3, 'on_boundary')]
@@ -95,8 +89,23 @@ def setup_problem(n, mms, params):
 
     return A, b, W
 
-# Generic wrt implementation :)
-setup_mms = lm1.setup_mms
+
+def setup_mms(params):
+    '''Manufactured solution from notes'''
+    
+    u3d = Expression('sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)
+    f3d = Expression('(8*pi*pi)*sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)
+
+    u1d = Expression('sin(pi*x[2])', degree=4)
+    f1d = Expression('pi*pi*sin(pi*x[2])', degree=4)
+
+    p = Expression('0', degree=4)  # The multiplier
+    fLM = Expression('sin(2*pi*x[0])*sin(2*pi*x[1]) - sin(pi*x[2])', degree=4)
+
+    return MMSData(solution=[u3d, u1d, p],
[…]

### 2019-10-19 benchmark.tex
update

@@
+% SIAM Article Template
+\documentclass[r]{siamart171218}
+% Packages and macros go here
+\usepackage[english]{babel}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsfonts}
+\usepackage{array}
+\usepackage{graphicx}
+\usepackage{epsfig}
+\usepackage{float}
+\usepackage{fullpage}
+\usepackage{color}
+\usepackage{enumitem}  
+\usepackage{epstopdf}
+\usepackage{stmaryrd}
+
+% Title. If the supplement option is on, then "Supplementary Material"
+% is automatically inserted before the title.
+%\title{On the weak coupling of 3D and 1D second order elliptic problems}
+\title{Coupling PDEs on 3D-1D domains with Lagrange multipliers}
+
+% Authors: full names plus addresses.
+\author{Miroslav Kuchta, Federica Laurino, Kent-Andre Mardal, Paolo Zunino,\thanks{Authors are listed in alphabetical order}}
+
+\begin{document}
+
+\maketitle
+
+% REQUIRED
+\begin{abstract}
+These are personal notes written to keep track of the developments on this topic, to be kept confidential.
+\end{abstract}
+
+% REQUIRED
+\begin{keywords}
+elliptic problems, high dimensionality gap, essential coupling conditions, Lagrange multipliers
+\end{keywords}
+
+% REQUIRED
+\begin{AMS}
+n.a.
+\end{AMS}
+
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+
+% definitions here
+
+\def\ud{u_{\odot}}
+\def\vd{v_{\odot}}
+\def\uf{u_{\ominus}}
+\def\up{u_{\oplus}}
+\def\eps{\epsilon}
+\def\nn{\boldsymbol n}
+\def\rr{\boldsymbol r}
+\def\RR{\boldsymbol R}
+\def\kk{\boldsymbol k}
+\def\ss{\boldsymbol s}
+\def\uu{\boldsymbol u}
+\def\vv{\boldsymbol v}
+\def\xx{\boldsymbol x}
+\def\bu{\overline{u}}
+\def\bv{\overline{v}}
+\def\tu{\widetilde{u}}
+\def\tv{\widetilde{v}}
+\def\TT{\boldsymbol T}
+\def\NN{\boldsymbol N}
+\def\BB{\boldsymbol B}
+\def\ttu{\widetilde{\widetilde{u}}}
+\def\ttv{\widetilde{\widetilde{v}}}
+\def\cv{\check{v}}
+\def\mesh{{\cal T}^h}
+\def\ball{{\cal B}}
+\def\R{\mathbb{R}}
+\def\D{\mathcal{D}}
+\def\DD{\partial\mathcal{D}}
+\def\trace{\overline{\mathcal{R}}}
+\def\ext{\mathcal{E}}
+\def\ide{\mathcal{I}}
+\def\ii{\hat{\imath}}
+\newcommand{\avrd}[1]{\overline{\overline{#1}}}
+\newcommand{\avrc}[1]{\overline{#1}}
+\newcommand{\refe}[1]{{#1}_{\mathrm{ref}}}
+
+\newcommand{\vertiii}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 
+    \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
+
+\newtheorem{thm}{Theorem}[section]
+\newtheorem{prop}{Property}[section]
+\theoremstyle{remark}
+\newtheorem{remark}{Remark}[section]
+
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 \section{A benchmark problem with analytical solution}
 
-We consider the following 3D-1D coupled problem,
+Let $\Omega=[0,1]\times [0,1]\times [0,1]$, \\$\Lambda=\{x=\tfrac{1}{2}\}\times \{y=\tfrac{1}{2}\} \times [0,1] $
+and $\Sigma=[\tfrac{1}{4}, \tfrac{3}{4}]\times [\tfrac{1}{4}, \tfrac{3}{4}]\times [0, 1]$.
+Finally we let $\DD$ be the cross section of the virtual interface $\Gamma=\partial \Sigma$.
+As a benchmark problem for the two formulations we consider the following coupled problems
+%
 \begin{subequations}\label{benchmark}
@@
 -d_{zz}^2 \ud =g \quad &\text{on $\Lambda$}\\
-u=0 \quad &\text{on $\partial \Omega$}\\
-\label{benchm_coupl}
-\ud -\avrc{u}=q \quad &\text{on $\Lambda$}
+u=h \quad &\text{on $\partial \Omega$},
 \end{align}
 \end{subequations}
-
-where $\Omega=[0,1]\times [0,1]\times [0,H]$, $\Lambda=\{x=0.5\}\times \{y=0.5\} \times [0,H] $ and
+where for formulation \eqref{eq:problem1} the mix-dimensional coupling constraint reads
+\begin{equation}
+  \label{eq:couple_1}
+\mathcal{T}_{\Gamma}u - \mathcal{E}_{\Gamma}\ud = q_1\quad\text{ on }\Gamma,
+\end{equation}
+while for \eqref{eq:problem2} we set
+\begin{equation}
+    \label{eq:couple_2}
+\avrc{u} - \ud = q_2\quad\text{ on }\Lambda.
+\end{equation}
+%
+In \eqref{benchmark} the right-hand side data shall be defined as 
 \begin{eqnarray*}
 f=8\pi ^2 \sin (2\pi x) \sin (2\pi y)\\
-%g=-\exp(-z)\\
-%q=1+\exp(-z).
-g=\frac{\pi ^2}{H^2} \sin \left(\frac{\pi z}{H}\right)\\
-q=\sin \left(\frac{\pi z}{H}\right).
+g={\pi ^2}\sin \left({\pi z}\right)\\
+h=\sin (2\pi x) \sin (2\pi y)\\
+q_1=\sin (2\pi x) \sin (2\pi y) - \sin \left({\pi z}\right)\\.
+q_2=\sin \left({\pi z}\right)\\.
 \end{eqnarray*}
-In this case the $z$ coordinate coincides with the axial coordinate along $\Lambda$.
-We define $\Sigma=[0.25,0.75]\times [0.25,0.75]\times [0,H]$.
-The average of the 3D solution $\avrc{u}$ in \eqref{benchm_coupl} is computed on the cross section $\DD$ of the virtual interface $\Gamma=\partial \Sigma$.
-The exact solution of \eqref{benchmark} is given by
+
+The exact solution of \eqref{benchmark}, regardless of the coupling constraing,
+is given by
+%
 \begin{eqnarray}
@@
 \end{eqnarray}
+%
 Let us notice that $\ud$ satisfies homogeneous Dirichlet conditions at the boundary of $\Lambda$.
@@
 
-We prove that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of \eqref{eq:problem1} and \eqref{eq:problem2} in the simplified case in which the starting 3D-3D problem is
+We prove that \eqref{benchmark} with the couplin \eqref{eq:couple2 } is solution
+of \eqref{eq:problem2} in the simplified case in which the starting 3D-3D problem is
 \begin{subequations}\label{eq:dirneu_simple}
@@
 \uf - \up &= q  && \text{ on }  \Gamma,\\
-\up &= 0 && \text{ on } \partial \Omega\,.
+\up &= h && \text{ on } \partial \Omega.
 \end{align}
 \end{subequations}
-instead of \eqref{eq:dirneu}. Therefore the reduced problems in the two different formulations \eqref{eq:problem1} and \eqref{eq:problem2} become respectively
-
-\begin{subequations}\label{eq:problem1_simple}
-\begin{align}
-\label{eq:problem1_simple_eq1}
-&(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
-+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
-\\
-\label{eq:problem1_simple_eq2}
-&   \langle \Pi_1 u - \Pi_2 \ud , M \rangle_\Gamma =  \langle q , M \rangle_\Gamma
-\quad \forall M \in H^{-\frac12}(\Gamma)\,.
-\end{align}
-\end{subequations}
-
-and
+instead of \eqref{eq:dirneu}. Therefore the reduced problem in \eqref{eq:problem2} becomes
 
@@
 
-Let us prove that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of \eqref{eq:problem1_simple}.
-Using the integration by part formula and homogeneous boundary conditions on $\Omega$ and $\Lambda$, from \eqref{eq:problem1_simple_eq1} we have
-\begin{align*}
-&-(\Delta u, v)_{L^2(\Omega)} - |{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)} 
-+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda).
-\\
-\end{align*}
-Clearly, since \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d} satisfies \eqref{benchm_1d}, we have that \begin{align*}
--(\Delta u, v)_{L^2(\Omega)} =  (f,v)_{L^2(\Omega)} \\
--|{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
-\end{align*}
-and being $L=\lambda=0$, we can conclude that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfy \eqref{eq:problem1_simple_eq1}.
+%% Let us prove that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of
+%% \eqref{eq:problem2_simple}. Using the integration by part formula and homogeneous
+%% boundary conditions on $\Omega$ and $\Lambda$, from \eqref{eq:problem1_simple_eq1} we have
+%% \begin{align*}
+%% &-(\Delta u, v)_{L^2(\Omega)} - |{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)} 
+%% + \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
+%% \\
+%% \nonumber
+%% &\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
+%% \quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda).
+%% \\
+%% \end{align*}
+%% Clearly, since \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d} satisfies \eqref{benchm_1d}, we have that \begin{align*}
+%% -(\Delta u, v)_{L^2(\Omega)} =  (f,v)_{L^2(\Omega)} \\
+%% -|{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
+%% \end{align*}
+%% and being $L=\lambda=0$, we can conclude that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfy \eqref{eq:problem1_simple_eq1}.
 The fact that the solution satisfy \eqref{eq:problem1_simple_eq2} follows from \eqref{benchm_coupl}.
@@
 
-\begin{remark}
-Let us notice that the 3D solution \eqref{benchm_sol3d} is such that $\avrc{u}=0$.
+%% \begin{remark}
+%% Let us notice that the 3D solution \eqref{benchm_sol3d} is such that $\avrc{u}=0$.
 Therefore in \eqref{benchmark} it is like we are solving two separated problems, one in $\Omega$ and the other on $\Lambda$.
-\end{remark}
-\begin{remark}
-It would be interesting to make a comparison between the solution of the fully coupled 3D-3D problem \eqref{eq:dirneu} (also in the simplified case of type \eqref{eq:dirneu_simple}) and the solution of the reduced problems \eqref{eq:problem1} and \eqref{eq:problem2}.
-Therefore, we could set the values of the data of the problem such that the reduced formulation becomes non-trivial and fully coupled.
-Then, we will solve both the original and reduced problem to observe the differences in the solutions and the values of the Lagrange multiplier.
-\end{remark}
+%% \end{remark}
+%% \begin{remark}
+%% It would be interesting to make a comparison between the solution of the fully coupled 3D-3D problem \eqref{eq:dirneu} (also in the simplified case of type \eqref{eq:dirneu_simple}) and the solution of the reduced problems \eqref{eq:problem1} and \eqref{eq:problem2}.
+%% Therefore, we could set the values of the data of the problem such that the reduced formulation becomes non-trivial and fully coupled.
+%% Then, we will solve both the original and reduced problem to observe the differences in the solutions and the values of the Lagrange multiplier.
+%% \end{remark}
+
+%-----------------
+\bibliographystyle{siamplain}
+\bibliography{3d1d_coupled}
+\end{document}

### 2019-10-19 lm3d1d_vs1/3d1d_coupled_LM.tex
Updates
update

--- 2019-03-04 3d1d_coupled_LM.tex
@@
 \def\ud{u_{\odot}}
+\def\udh{u_{\odot, h}}
 \def\vd{v_{\odot}}
@@
 \newcommand{\refe}[1]{{#1}_{\mathrm{ref}}}
+\newcommand{\norm}[1]{\lVert{#1}\rVert}
 
@@
 
-We consider the following 3D-1D coupled problem,
+Let $\Omega=[0,1]^3$, $\Lambda=\{x=\tfrac{1}{2}\}\times \{y=\tfrac{1}{2}\} \times [0,1] $
+and $\Sigma=[\tfrac{1}{4}, \tfrac{3}{4}]\times [\tfrac{1}{4}, \tfrac{3}{4}]\times [0, 1]$.
+Finally we let $\DD$ be the cross section of the virtual interface $\Gamma=\partial \Sigma$.
+As a benchmark for the two formulations we consider the following coupled problems
+%
 \begin{subequations}\label{benchmark}
@@
 -d_{zz}^2 \ud =g \quad &\text{on $\Lambda$}\\
-u=0 \quad &\text{on $\partial \Omega$}\\
-\label{benchm_coupl}
-\ud -\avrc{u}=q \quad &\text{on $\Lambda$}
+u=h \quad &\text{on $\partial \Omega$},
 \end{align}
 \end{subequations}
+where for formulation \eqref{eq:problem1} the mix-dimensional coupling constraint reads
+\begin{equation}
+  \label{eq:couple_1}
+\mathcal{T}_{\Gamma}u - \mathcal{E}_{\Gamma}\ud = q_1\quad\text{ on }\Gamma,
+\end{equation}
+while for \eqref{eq:problem2} we set
+\begin{equation}
+    \label{eq:couple_2}
+\avrc{u} - \ud = q_2\quad\text{ on }\Lambda.
+\end{equation}
+%
+In \eqref{benchmark}-\eqref{eq:couple_2} the right-hand side data shall be defined as 
+\begin{eqnarray*}
+  &f=8\pi ^2 \sin (2\pi x) \sin (2\pi y)\quad &g={\pi ^2}\sin \left({\pi z}\right)\quad h=\sin (2\pi x) \sin (2\pi y)\\
+  &q_1=\sin (2\pi x) \sin (2\pi y) - \sin \left({\pi z}\right)\quad &q_2=\sin \left({\pi z}\right).
+\end{eqnarray*}
 
-where $\Omega=[0,1]\times [0,1]\times [0,H]$, $\Lambda=\{x=0.5\}\times \{y=0.5\} \times [0,H] $ and
-\begin{eqnarray*}
-f=8\pi ^2 \sin (2\pi x) \sin (2\pi y)\\
-%g=-\exp(-z)\\
-%q=1+\exp(-z).
-g=\frac{\pi ^2}{H^2} \sin \left(\frac{\pi z}{H}\right)\\
-q=\sin \left(\frac{\pi z}{H}\right).
-\end{eqnarray*}
-In this case the $z$ coordinate coincides with the axial coordinate along $\Lambda$.
-We define $\Sigma=[0.25,0.75]\times [0.25,0.75]\times [0,H]$.
-The average of the 3D solution $\avrc{u}$ in \eqref{benchm_coupl} is computed on the cross section $\DD$ of the virtual interface $\Gamma=\partial \Sigma$.
-The exact solution of \eqref{benchmark} is given by
+The exact solution of \eqref{benchmark}, regardless of the coupling constraint,
+is given by
+%
 \begin{eqnarray}
@@
 %\ud=1+\exp(-z).
-\ud=\sin \left(\frac{\pi z}{H}\right) 
+\ud=\sin \left(\frac{\pi z}{H}\right).
 \end{eqnarray}
+%
 Let us notice that $\ud$ satisfies homogeneous Dirichlet conditions at the boundary of $\Lambda$.
@@
 \end{equation}
-being $n_{\oplus,z}$ the $z-$component of the normal unit vector to $\Gamma$.
+with $n_{\oplus,z}$ the $z-$component of the normal unit vector to $\Gamma$.
 
-We prove that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of \eqref{eq:problem1} and \eqref{eq:problem2} in the simplified case in which the starting 3D-3D problem is
+We prove that \eqref{benchmark} is solution of \eqref{eq:problem2} in the
+simplified case in which the starting 3D-3D problem is
 \begin{subequations}\label{eq:dirneu_simple}
@@
 -\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
-\uf - \up &= q  && \text{ on }  \Gamma,\\
-\up &= 0 && \text{ on } \partial \Omega\,.
+\uf - \up &= q_i  && \text{ on }  \Gamma,\\
+\up &= h && \text{ on } \partial \Omega.
 \end{align}
 \end{subequations}
-instead of \eqref{eq:dirneu}. Therefore the reduced problems in the two different formulations \eqref{eq:problem1} and \eqref{eq:problem2} become respectively
-
+instead of \eqref{eq:dirneu}. Therefore the reduced problem in \eqref{eq:problem1} and
+\eqref{eq:problem2} become respectively
+%
 \begin{subequations}\label{eq:problem1_simple}
@@
 &(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
-+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
++ \langle \mathcal{T}_{\Gamma} v  - \mathcal{E}_{\Gamma} \vd, L \rangle_\Gamma
 \\
@@
 &\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
+\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
 \\
 \label{eq:problem1_simple_eq2}
-&   \langle \Pi_1 u - \Pi_2 \ud , M \rangle_\Gamma =  \langle q , M \rangle_\Gamma
+&   \langle \mathcal{T}_{\Gamma} u - \mathcal{E}_{\Gamma} \ud , M \rangle_\Gamma =  \langle q_1 , M \rangle_\Gamma
 \quad \forall M \in H^{-\frac12}(\Gamma)\,.
@@
 \end{subequations}
-
 and
-
 \begin{subequations}\label{eq:problem2_simple}
   \begin{align}
+    \label{eq:problem2_simple_eq1}
 &(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
-+ |\partial {\cal D}| \langle \Pi_1 v - \Pi_2 \vd, L \rangle_{H^{-\frac12}(\Lambda)} 
++ |{\partial \cal D}| \langle \avrc{v} - \vd, L \rangle_{H^{-\frac12}(\Lambda)} 
 \\
@@
 \\
-&  |\partial {\cal D}| \langle \Pi_1 u -  \Pi_2 \ud, M \rangle_{H^{-\frac12}(\Lambda)} =|\partial {\cal D}| \langle \avrc{q}, M \rangle_{H^{-\frac12}(\Lambda)}
+\label{eq:problem2_simple_eq2}
+&  |\partial {\cal D}| \langle \avrc{u} -  ud, M \rangle_{H^{-\frac12}(\Lambda)} =
+|\partial {\cal D}| \langle \avrc{q_2}, M \rangle_{H^{-\frac12}(\Lambda)}
 \quad \forall M \in H^{-\frac12}(\Lambda)\,.
@@
 
-Let us prove that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of \eqref{eq:problem1_simple}.
-Using the integration by part formula and homogeneous boundary conditions on $\Omega$ and $\Lambda$, from \eqref{eq:problem1_simple_eq1} we have
+Let us prove that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of
+\eqref{eq:problem2_simple}. Using the integration by part formula and homogeneous
+boundary conditions on $\Omega$ and $\Lambda$, from \eqref{eq:problem2_simple_eq1} we have
 \begin{align*}
 &-(\Delta u, v)_{L^2(\Omega)} - |{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)} 
-+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
++ |{\cal D}|\langle \avrc{v}  - \vd, L \rangle_\Lambda
 \\
@@
 \end{align*}
-Clearly, since \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d} satisfies \eqref{benchm_1d}, we have that \begin{align*}
+Since $L=\avrc{\lambda}=0$ and \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d}
+satisfies \eqref{benchm_1d}, we have that
+\begin{align*}
 -(\Delta u, v)_{L^2(\Omega)} =  (f,v)_{L^2(\Omega)} \\
--|{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
+-|{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)},
 \end{align*}
-and being $L=\lambda=0$, we can conclude that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfy \eqref{eq:problem1_simple_eq1}.
-The fact that the solution satisfy \eqref{eq:problem1_simple_eq2} follows from \eqref{benchm_coupl}.
-We can prove in the same way that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of \eqref{eq:problem2_simple}, exploiting the fact that in this case $L=\avrc{\lambda}=0$.
+Thus \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfy \eqref{eq:problem2_simple_eq1}.
+The fact that the solution satisfy \eqref{eq:problem2_simple_eq2} follows from \eqref{eq:couple_2}.
 
-\begin{remark}
-Let us notice that the 3D solution \eqref{benchm_sol3d} is such that $\avrc{u}=0$.
+We can prove in a similar way that \eqref{benchm_sol3d}-\eqref{benchm_sol1d}, with $L=\lambda=0$
+satisfy \eqref{eq:problem1_simple}. Note in particular that $q_1$ is such that
+$\mathcal{T}_{\Gamma}u - \mathcal{E}_{\Gamma}\ud = q_1$ on $\Gamma$.
+
+\subsection{Numerical experiments} Using the benchmark problem \eqref{benchmark}
+we now investigate convergence properties of the two formulations. To this
+end we consider a \emph{uniform} tessilation of $\mathcal{T}^{Omega}_h$ of $\Omega$ consisting of
+equal-sized tetrahedra with edge length $h$. Further, the discretization shall be
+geometrically \emph{conforming} to both $\Lambda$ and $\Gamma$ such that
+the tessilations $\mathcal{T}^{\Gamma}_h$, $\mathcal{T}^{\Lambda}_h$ are made up
+of facets and edges of $\mathcal{T}^{\Omega}_h$ respectively, cf. Figure \textbf{TODO}
+for illustration.
+
+Formulations \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} shall
+be discretized using contiuous Lagrange element of order 1 ($P_1$) for all the spaces
+involved. We recall that since are investigating the conforming case, the tripplet
+$P_1$-$P_1$-$P_1$ satisfies
+the discrete inf-sup condition. The resulting linear systems are solved
+using the minimal residual method (MinRes) with stopping criterion requiring the relative
+preconditioned residual norm to be less than $10^{-12}$. As the preconditioner
+we use (approximate) the Riesz mapping with respect to the inner products of
+the spaces in which the two formulations were proved to be well posed.
+In particular, the preconditioner for the Lagrange multiplier relies on
+(the inverse of) the fractional Laplacian $-\Delta^{-1/2}$ on $\Gamma$ for
+\eqref{eq:problem1_simple} and $\Lambda$ for \eqref{eq:problem2_simple}.
+We remark that the size of the linear systems on the finest meshes considered
+here prevents the use direct solvers. Therefore iterative solvers were necessary.
+
+Considering uniform refinements of the initial mesh, Table \ref{tab:error_conform}
+lists the errors of formulations \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}
+on the benchmark problem. It can be seen the error in $u$ and $\ud$ in $H^1$ norm
+converges linearly (as can be expected due to $P_1$ element discretization).
+Moreover, the error of the Lagrange multiplier approximation in $H^{-1/2}$ norm
+decreases quadratically. In the light of $P_1$ discretization this rate appears
+superconvergent. We speculate that the result is (i) due to the fact that the
+exact solution is particularly simple, $L=0$, and (ii) the fact that the error
+is interpolated into the same finite element as the approximation $L_h$. We remark
+that for $u$ and $\ud$ the error is interpolated into FE space of piecewise
+quadratic \emph{discontinous} functions. Evaluating the fractional norm in higher
+order discontinous spaces is prohibitively costly. \textbf{Should we try for line formulation
+where  this is okay?}
+%
+\begin{table}
+  \scriptsize{
+    \begin{minipage}{0.49\textwidth}
+  \begin{center}
+    \begin{tabular}{c|ccc}
+      \hline
+    $h$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{L-L_H}_{-1/2,\Gamma}$\\
+      \hline
+4.3E-1 & 3.4E0(--) & 5.3E-1(--) & 2.9E0(--)\\
+2.2E-1 & 1.7E0(0.99) & 2.6E-1(1.06) & 6.1E-1(2.25)\\
+1.1E-1 & 8.7E-1(0.99) & 1.3E-1(1.02) & 1.4E-1(2.13)\\
+5.4E-2 & 4.4E-1(1.00) & 6.3E-2(1.00) & 3.4E-2(2.03)\\
+2.7E-2 & 2.2E-1(1.00) & 3.1E-2(1.00) & 8.6E-3(2.00)\\
+\hline
+  \end{tabular}
+  \end{center}
+  \end{minipage}
+    }
+    \vspace{5pt}
+  \scriptsize{%(ii)
+    \begin{minipage}{0.49\textwidth}
+      \begin{center}
+        \begin{tabular}{c|ccc}
+      \hline
+    $h$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{L-L_H}_{-1/2, \Lambda}$\\
+      \hline
+4.3E-1 & 3.1E0(--) & 5.4E-1(--) & 4.3E-2(--)\\
+2.2E-1 & 1.7E0(0.87) & 2.6E-1(1.06) & 1.1E-2(1.99)\\
+1.1E-1 & 8.6E-1(0.96) & 1.3E-1(1.02) & 2.7E-3(2.01)\\
+5.4E-2 & 4.4E-1(0.99) & 6.3E-2(1.00) & 6.7E-4(2.00)\\
+2.7E-2 & 2.2E-1(1.00) & 3.1E-2(1.00) & 1.7E-4(2.01)\\
+\hline
+  \end{tabular}
+  \end{center}
+  \end{minipage}
+  }
+  \caption{Error convergence of \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}
+    on a benchmark problem \eqref{benchmark}. Continuous linear Lagrange
+    elements are used.
+  }
+  \label{tab:error_conform}
+\end{table}
+
+In Table \ref{tab:error_conform} one can observe that the two formulations
+yield practically identical approximations of $u$ and $\ud$. However, the solution
+cost of the two approaches differs. In Table \ref{tab:cost} we summarize the
+size of the linear systems solved at each level of refinement and the time
+for the iterative solver to converge. Let as first note that the proposed
+preconditioners seem robust with respect to discretization parameter as
+the iteration counts are clearly bounded. We then see that the solution
+time for \eqref{eq:problem1_simple} is up to 2 times longer compared to
+\eqref{eq:problem2_simple}. This is in addition to the higher setup costs
+of the preconditioner which in our implementation involve solving an eigenvalue
+problem for the fractional Laplacian. Therefore it is advantageous to keep
+the multiplier space as small as possible.
+
+\begin{table}
+  \scriptsize{
+  \begin{center}
+    \begin{tabular}{c|cc|ccc|ccc}
+      \hline
+      $h$ & $\dim{V_h}$ & $\dim{V_{\odot, h}}$ & $\dim{Q^{\Gamma}_h}$ & $\#$ & $T\left[s\right]$ & $\dim{Q^{\Lambda}_h}$ & $\#$ & $T\left[s\right]$\\
+      \hline
+4.33E-01 &125    &5  &40    &27 &0.03  &5  &9  &0.01\\
+2.17E-01 &729    &9  &144   &55 &0.10  &9  &19 &0.02\\
+1.08E-01 &4913   &17 &544   &62 &0.25  &17 &36 &0.14\\
+5.41E-02 &35937  &33 &2112  &64 &1.97  &33 &42 &1.08\\
+2.71E-02 &274625 &65 &8320  &64 &18.01 &65 &36 &8.24\\
+\hline
+    \end{tabular}
+    \end{center}
+    }
+  \caption{Cost comparison of the two formulations. Number of MinRes iterations
+    is denoted by $\#$. Time till convergence of the iterative solver (excluding the setup) is shown
+    as $T$.
+  }
+\label{tab:cost}
+\end{table}
+
+\textbf{Some plots of the solutions}
+
+%\eqref{benchm_sol3d}-\eqref{benchm_sol1d}
+
+%% \begin{remark}
+%% Let us notice that the 3D solution \eqref{benchm_sol3d} is such that $\avrc{u}=0$.
 Therefore in \eqref{benchmark} it is like we are solving two separated problems, one in $\Omega$ and the other on $\Lambda$.
-\end{remark}
-\begin{remark}
-It would be interesting to make a comparison between the solution of the fully coupled 3D-3D problem \eqref{eq:dirneu} (also in the simplified case of type \eqref{eq:dirneu_simple}) and the solution of the reduced problems \eqref{eq:problem1} and \eqref{eq:problem2}.
-Therefore, we could set the values of the data of the problem such that the reduced formulation becomes non-trivial and fully coupled.
-Then, we will solve both the original and reduced problem to observe the differences in the solutions and the values of the Lagrange multiplier.
-\end{remark}
-%\bibliographystyle{siamplain}
-%\bibliography{3d1d_coupled}
+%% \end{remark}
+%% \begin{remark}
+%% It would be interesting to make a comparison between the solution of the fully coupled 3D-3D problem \eqref{eq:dirneu} (also in the simplified case of type \eqref{eq:dirneu_simple}) and the solution of the reduced problems \eqref{eq:problem1} and \eqref{eq:problem2}.
+%% Therefore, we could set the values of the data of the problem such that the reduced formulation becomes non-trivial and fully coupled.
+%% Then, we will solve both the original and reduced problem to observe the differences in the solutions and the values of the Lagrange multiplier.
+%% \end{remark}
+
+\input{unfitted}
+%-----------------
+\bibliographystyle{siamplain}
+\bibliography{3d1d_coupled}
 \end{document}

### 2019-10-19 lm3d1d_vs1/3d1d_coupled_LM.tex
update

@@
 decreases quadratically. In the light of $P_1$ discretization this rate appears
-superconvergent. We speculate that the result is (i) due to the fact that the
-exact solution is particularly simple, $L=0$, and (ii) the fact that the error
-is interpolated into the same finite element as the approximation $L_h$. We remark
-that for $u$ and $\ud$ the error is interpolated into FE space of piecewise
-quadratic \emph{discontinous} functions. Evaluating the fractional norm in higher
-order discontinous spaces is prohibitively costly. \textbf{Should we try for line formulation
-where  this is okay?}
+superconvergent. We speculate that the result is due to the fact that the
+exact solution is particularly simple, $L=0$. In case of the results for
+\eqref{eq:problem1_simple} the rate can also be due to the fact that the
+error is interpolated into the same finite element as the approximation $L_h$.
+We remark that for $u$ and $\ud$ the error is interpolated into FE space of piecewise
+quadratic \emph{discontinous} functions. For \eqref{eq:problem2_simple} we
+evaluate the fractional norm and interpolate the error using piecewise continuous
+cubic functions. Evaluating the fractional norm in higher order spaces
+for formulation with the multiplier space on $\Gamma$ is prohibitively costly.
+
 %
@@
       \hline
-4.3E-1 & 3.1E0(--) & 5.4E-1(--) & 4.3E-2(--)\\
-2.2E-1 & 1.7E0(0.87) & 2.6E-1(1.06) & 1.1E-2(1.99)\\
-1.1E-1 & 8.6E-1(0.96) & 1.3E-1(1.02) & 2.7E-3(2.01)\\
-5.4E-2 & 4.4E-1(0.99) & 6.3E-2(1.00) & 6.7E-4(2.00)\\
-2.7E-2 & 2.2E-1(1.00) & 3.1E-2(1.00) & 1.7E-4(2.01)\\
+4.3E-1 & 3.1E0(--)    & 5.4E-1(--)   & 4.4E-2(--)   \\
+2.2E-1 & 1.7E0(0.87)  & 2.6E-1(1.06) & 1.1E-2(2.01) \\
+1.1E-1 & 8.6E-1(0.96) & 1.3E-1(1.02) & 2.7E-3(2.01) \\
+5.4E-2 & 4.4E-1(0.99) & 6.3E-2(1.00) & 6.7E-4(2.01) \\
+2.7E-2 & 2.2E-1(1.00) & 3.1E-2(1.00) & 1.7E-4(2.01) \\
+1.4E-2 & 1.1E-1(1.00) & 1.6E-2(1.00) & 4.1E-5(2.01) \\
 \hline
@@
 the iteration counts are clearly bounded. We then see that the solution
-time for \eqref{eq:problem1_simple} is up to 2 times longer compared to
+time for \eqref{eq:problem1_simple} is about 2 times longer compared to
 \eqref{eq:problem2_simple}. This is in addition to the higher setup costs
@@
 problem for the fractional Laplacian. Therefore it is advantageous to keep
-the multiplier space as small as possible.
-
+the multiplier space as small as possible. Let us remark that the missing
+results for \eqref{eq:problem1_simple} in Table \ref{tab:cost} and \ref{tab:error_conform}
+are due to the memory limitations which we encouter when solving the eigenvalue problem
+for Laplacian, which for $h=1.35E-02$ includes cca 32 thousand eigenvalues.
+%
 \begin{table}
@@
 2.71E-02 &274625 &65 &8320  &64 &18.01 &65 &36 &8.24\\
+1.35E-02 &--     &-- &--    &-- &--    &129 &31 &61.37\\
 \hline

### 2019-10-19 src_lm3d1d/coupled_lm1.py

@@ -102,14 +102,15 @@ def setup_error_monitor(mms_data, params):
         u3, u1, p = mms.solution
         u3h, u1h, ph = wh
 
-        # Passing the HsNorm from preconditioner so that we don't compute
-        # eigenvalues twice
-        Hs0Norm = mms.normals.pop()
+        # On a finer mesh
+        Q = FunctionSpace(ph.function_space().mesh(), 'CG', 3)
+        Hs = Hs0Norm(Q, s=-0.5, bcs=DirichletBC(Q, Constant(0), 'on_boundary'))
+        
         # e*H*e ie (e, e)_H
-        e = interpolate(p, ph.function_space()).vector()
-        e.axpy(-1, ph.vector())
+        e = interpolate(p, Q).vector()
+        e.axpy(-1, interpolate(ph, Q).vector())
 
-        e = np.sqrt(e.inner(Hs0Norm*e))
+        e = np.sqrt(e.inner(Hs*e))
         # On big meshes constructing the error for interpolation space
         # is expensive so wi reduce order then
         degree_rise = 1 if u3h.function_space().dim() < 2E6 else 0

### 2019-10-19 src_lm3d1d/coupled_lm2.py

@@ -106,7 +106,37 @@ def setup_mms(params):
                    rhs=[(f3d, f1d, fLM), (u3d, u1d, p)],
                    subdomains=[], normals=[])
 
-setup_error_monitor = lm1.setup_error_monitor
+def setup_error_monitor(mms_data, params):
+    '''We look at H1, H1, Hs norm'''
+    # Error of the passed wh
+    
+    def get_error(wh, mms=mms_data):
+        # We look at the H1 error for velocity
+        u3, u1, p = mms.solution
+        u3h, u1h, ph = wh
+
+        # Passing the HsNorm from preconditioner so that we don't compute
+        # eigenvalues twice
+        Hs0Norm = mms.normals.pop()
+        # e*H*e ie (e, e)_H
+        e = interpolate(p, ph.function_space()).vector()
+        e.axpy(-1, ph.vector())
+
+        e = np.sqrt(e.inner(Hs0Norm*e))
+        # On big meshes constructing the error for interpolation space
+        # is expensive so wi reduce order then
+        degree_rise = 1 if u3h.function_space().dim() < 2E6 else 0
+        # NOTE: the error is interpolated to P2 disc, or P1 disc
+        return (H1_norm(u3, u3h, degree_rise=degree_rise),
+                H1_norm(u1, u1h),  
+                e,
+                L2_norm(p, ph))
+    # Pretty print
+    error_types = ('|u3|_1', '|u1|_1', '|p|_{-1/2}', '|p|_0')
+    
+    return get_error, error_types
+
+
 cannonical_inner_product = lm1.cannonical_inner_product
 cannonical_riesz_map = lm1.cannonical_riesz_map
 

### 2019-10-20 lm3d1d_vs1/3d1d_coupled_LM.tex
typos and mesh for the benchmark

@@
 \begin{eqnarray*}
-  &f=8\pi ^2 \sin (2\pi x) \sin (2\pi y)\quad &g={\pi ^2}\sin \left({\pi z}\right)\quad h=\sin (2\pi x) \sin (2\pi y)\\
-  &q_1=\sin (2\pi x) \sin (2\pi y) - \sin \left({\pi z}\right)\quad &q_2=\sin \left({\pi z}\right).
+  &f=8\pi ^2 \sin (2\pi x) \sin (2\pi y),\quad &g={\pi ^2}\sin \left({\pi z}\right),\quad h=\sin (2\pi x) \sin (2\pi y),\\
+  &q_1=\sin (2\pi x) \sin (2\pi y) - \sin \left({\pi z}\right),\quad &q_2=-\sin \left({\pi z}\right).
 \end{eqnarray*}
@@
 %\ud=1+\exp(-z).
-\ud=\sin \left(\frac{\pi z}{H}\right).
+\ud=\sin \left({\pi z}\right).
 \end{eqnarray}
@@
 \label{eq:problem2_simple_eq2}
-&  |\partial {\cal D}| \langle \avrc{u} -  ud, M \rangle_{H^{-\frac12}(\Lambda)} =
+&  |\partial {\cal D}| \langle \avrc{u} -  \ud, M \rangle_{H^{-\frac12}(\Lambda)} =
 |\partial {\cal D}| \langle \avrc{q_2}, M \rangle_{H^{-\frac12}(\Lambda)}
@@
 -(\Delta u, v)_{L^2(\Omega)} =  (f,v)_{L^2(\Omega)} \\
--|{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)},
+-|{\partial \cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)},
 \end{align*}
@@
 we now investigate convergence properties of the two formulations. To this
-end we consider a \emph{uniform} tessilation of $\mathcal{T}^{Omega}_h$ of $\Omega$ consisting of
-equal-sized tetrahedra with edge length $h$. Further, the discretization shall be
+end we consider a \emph{uniform} tessilation of $\mathcal{T}^{\Omega}_h$ of $\Omega$ consisting of
+tetrahedra with diameter $h$. Further, the discretization shall be
 geometrically \emph{conforming} to both $\Lambda$ and $\Gamma$ such that
 the tessilations $\mathcal{T}^{\Gamma}_h$, $\mathcal{T}^{\Lambda}_h$ are made up
-of facets and edges of $\mathcal{T}^{\Omega}_h$ respectively, cf. Figure \textbf{TODO}
+of facets and edges of $\mathcal{T}^{\Omega}_h$ respectively, cf. Figure \ref{fig:mesh}
 for illustration.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.5\textwidth]{./conform_mesh.pdf}
+    \caption{$\Lambda$ and $\Gamma$ conforming discretization of $\Omega$
+      used for \eqref{eq:problem1_simple}. For \eqref{eq:problem2_simple}
+      only conformity to $\Lambda$ is needed.
+    }
+    \label{fig:mesh}
+  \end{center}
+\end{figure}
 
@@
 be discretized using contiuous Lagrange element of order 1 ($P_1$) for all the spaces
-involved. We recall that since are investigating the conforming case, the tripplet
+involved. We recall that since are are investigating the conforming case, the tripplet
 $P_1$-$P_1$-$P_1$ satisfies
@@
 preconditioned residual norm to be less than $10^{-12}$. As the preconditioner
-we use (approximate) the Riesz mapping with respect to the inner products of
+we use the (approximate) Riesz mapping with respect to the inner products of
 the spaces in which the two formulations were proved to be well posed.
@@
 \eqref{eq:problem1_simple} the rate can also be due to the fact that the
-error is interpolated into the same finite element as the approximation $L_h$.
+error is interpolated into the same finite element space as the approximation $L_h$.
 We remark that for $u$ and $\ud$ the error is interpolated into FE space of piecewise
@@
       \hline
-    $h$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{L-L_H}_{-1/2,\Gamma}$\\
+    $h$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{L-L_h}_{-1/2,\Gamma}$\\
       \hline
@@
       \hline
-    $h$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{L-L_H}_{-1/2, \Lambda}$\\
+    $h$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{L-L_h}_{-1/2, \Lambda}$\\
       \hline
@@
 size of the linear systems solved at each level of refinement and the time
-for the iterative solver to converge. Let as first note that the proposed
+for the iterative solver to converge. Let us first note that the proposed
 preconditioners seem robust with respect to discretization parameter as
@@
 problem for the fractional Laplacian. Therefore it is advantageous to keep
-the multiplier space as small as possible. Let us remark that the missing
+the multiplier space as small as possible. We remark that the missing
 results for \eqref{eq:problem1_simple} in Table \ref{tab:cost} and \ref{tab:error_conform}
-are due to the memory limitations which we encouter when solving the eigenvalue problem
-for Laplacian, which for $h=1.35E-02$ includes cca 32 thousand eigenvalues.
+are due to the memory limitations which we encounter when solving the eigenvalue problem
+for the Laplacian, which for finest mesh involves cca 32 thousand eigenvalues.
 %

### 2019-10-20 src_lm3d1d/poisson_1d.py

@@ -1,0 +1,68 @@
+from dolfin import *
+from xii import *
+from weak_bcs.utils import block_form, MMSData, H1_norm
+from block import block_mat, block_vec
+import numpy as np
+
+
+def setup_mms(params):
+    '''Manufactured solution'''
+    
+    u3d = Expression('sin(2*pi*x[0])', degree=4)
+    f3d = Expression('(4*pi*pi)*sin(2*pi*x[0])', degree=4)    
+
+    return MMSData(solution=[u3d], rhs=[f3d], subdomains=['on_boundary'],normals=None)
+
+
+def setup_problem(n, mms, params):
+    '''Poisson solver'''
+    mesh = UnitIntervalMesh(n)
+    
+    V = FunctionSpace(mesh, 'CG', 1)
+
+    # Just one
+    boundaries = MeshFunction('size_t', mesh, 0, 0)
+    for tag, subd in enumerate(mms.subdomains, 1):
+        CompiledSubDomain(subd, tol=1E-10).mark(boundaries, tag)
+
+    u_true,  = mms.solution
+    bc = DirichletBC(V, u_true, boundaries, 1)
+
+    f, = mms.rhs
+    
+    u, v = TrialFunction(V), TestFunction(V)
+    a = inner(grad(u), grad(v))*dx
+    L = inner(f, v)*dx
+
+    A, b = assemble_system(a, L, bc)
+
+    return block_mat([[A]]), block_vec([b]), [V]
+
+
+def setup_error_monitor(mms_data, params):
+    '''We look at H1 norm'''
+    # Error of the passed wh
+    
+    def get_error(wh, u_exact=mms_data.solution[0]):
+        # We look at the H1 error for velocity
+        uh, = wh
+
+        V = uh.function_space()
+        V = FunctionSpace(V.mesh(), 'CG', V.ufl_element().degree()+2)
+        u, v = TrialFunction(V), TestFunction(V)
+        a, L = inner(grad(u), grad(v))*dx, inner(Constant(0), v)*dx
+        A, _ = assemble_system(a, L, bcs=DirichletBC(V, Constant(0), 'on_boundary'))
+
+        e = interpolate(u_exact, V).vector()
+        e.axpy(-1, interpolate(uh, V).vector())
+
+        error = sqrt(e.inner(A*e))
+        
+        return (error, )
+    # Pretty print
+    error_types = ('|u|_1', )
+    
+    return get_error, error_types
+
+# How is the problem parametrized
+PARAMETERS = ('mu', )

### 2019-10-20 benchmark.tex
Plots num sol

--- 2019-05-28 benchmark.tex
@@
 -d_{zz}^2 \ud =g \quad &\text{on $\Lambda$}\\
-u=0 \quad &\text{on $\partial \Omega$}\\
-\label{benchm_coupl}
-\ud -\avrc{u}=q \quad &\text{on $\Lambda$}
+u=h \quad &\text{on $\partial \Omega$},
 \end{align}
 \end{subequations}
+where for formulation \eqref{eq:problem1} the mix-dimensional coupling constraint reads
+\begin{equation}
+  \label{eq:couple_1}
+\mathcal{T}_{\Gamma}u - \mathcal{E}_{\Gamma}\ud = q_1\quad\text{ on }\Gamma,
+\end{equation}
+while for \eqref{eq:problem2} we set
+\begin{equation}
+    \label{eq:couple_2}
+\avrc{u} - \ud = q_2\quad\text{ on }\Lambda.
+\end{equation}
+%
+In \eqref{benchmark}-\eqref{eq:couple_2} the right-hand side data shall be defined as 
+\begin{eqnarray*}
+  &f=8\pi ^2 \sin (2\pi x) \sin (2\pi y),\quad &g={\pi ^2}\sin \left({\pi z}\right),\quad h=\sin (2\pi x) \sin (2\pi y),\\
+  &q_1=\sin (2\pi x) \sin (2\pi y) - \sin \left({\pi z}\right),\quad &q_2=-\sin \left({\pi z}\right).
+\end{eqnarray*}
 
-where $\Omega=[0,1]\times [0,1]\times [0,H]$, $\Lambda=\{x=0.5\}\times \{y=0.5\} \times [0,H] $ and
-\begin{eqnarray*}
-f=8\pi ^2 \sin (2\pi x) \sin (2\pi y)\\
-%g=-\exp(-z)\\
-%q=1+\exp(-z).
-g=\frac{\pi ^2}{H^2} \sin \left(\frac{\pi z}{H}\right)\\
-q=\sin \left(\frac{\pi z}{H}\right).
-\end{eqnarray*}
-In this case the $z$ coordinate coincides with the axial coordinate along $\Lambda$.
-We define $\Sigma=[0.25,0.75]\times [0.25,0.75]\times [0,H]$.
-The average of the 3D solution $\avrc{u}$ in \eqref{benchm_coupl} is computed on the cross section $\DD$ of the virtual interface $\Gamma=\partial \Sigma$.
-The exact solution of \eqref{benchmark} is given by
+The exact solution of \eqref{benchmark}, regardless of the coupling constraint,
+is given by
+%
 \begin{eqnarray}
@@
 %\ud=1+\exp(-z).
-\ud=\sin \left(\frac{\pi z}{H}\right) 
+\ud=\sin \left({\pi z}\right).
 \end{eqnarray}
+%
 Let us notice that $\ud$ satisfies homogeneous Dirichlet conditions at the boundary of $\Lambda$.
@@
 \\
-&  |\partial {\cal D}| \langle \Pi_1 u -  \Pi_2 \ud, M \rangle_{H^{-\frac12}(\Lambda)} =|\partial {\cal D}| \langle \avrc{q}, M \rangle_{H^{-\frac12}(\Lambda)}
+\label{eq:problem2_simple_eq2}
+&  |\partial {\cal D}| \langle \avrc{u} -  \ud, M \rangle_{H^{-\frac12}(\Lambda)} =
+|\partial {\cal D}| \langle \avrc{q_2}, M \rangle_{H^{-\frac12}(\Lambda)}
 \quad \forall M \in H^{-\frac12}(\Lambda)\,.
@@
 \end{align*}
-Clearly, since \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d} satisfies \eqref{benchm_1d}, we have that \begin{align*}
+Since $L=\avrc{\lambda}=0$ and \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d}
+satisfies \eqref{benchm_1d}, we have that
+\begin{align*}
 -(\Delta u, v)_{L^2(\Omega)} =  (f,v)_{L^2(\Omega)} \\
--|{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
+-|{\partial \cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)},
 \end{align*}
-and being $L=\lambda=0$, we can conclude that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfy \eqref{eq:problem1_simple_eq1}.
-The fact that the solution satisfy \eqref{eq:problem1_simple_eq2} follows from \eqref{benchm_coupl}.
-We can prove in the same way that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is solution of \eqref{eq:problem2_simple}, exploiting the fact that in this case $L=\avrc{\lambda}=0$.
+Thus \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfy \eqref{eq:problem2_simple_eq1}.
+The fact that the solution satisfy \eqref{eq:problem2_simple_eq2} follows from \eqref{eq:couple_2}.
 
-\begin{remark}
-Let us notice that the 3D solution \eqref{benchm_sol3d} is such that $\avrc{u}=0$.
+We can prove in a similar way that \eqref{benchm_sol3d}-\eqref{benchm_sol1d}, with $L=\lambda=0$
+satisfy \eqref{eq:problem1_simple}. Note in particular that $q_1$ is such that
+$\mathcal{T}_{\Gamma}u - \mathcal{E}_{\Gamma}\ud = q_1$ on $\Gamma$.
+
+\subsection{Numerical experiments} Using the benchmark problem \eqref{benchmark}
+we now investigate convergence properties of the two formulations. To this
+end we consider a \emph{uniform} tessilation of $\mathcal{T}^{\Omega}_h$ of $\Omega$ consisting of
+tetrahedra with diameter $h$. Further, the discretization shall be
+geometrically \emph{conforming} to both $\Lambda$ and $\Gamma$ such that
+the tessilations $\mathcal{T}^{\Gamma}_h$, $\mathcal{T}^{\Lambda}_h$ are made up
+of facets and edges of $\mathcal{T}^{\Omega}_h$ respectively, cf. Figure \ref{fig:mesh}
+for illustration.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.5\textwidth]{./graphics/conform_mesh.pdf}
+    \caption{$\Lambda$ and $\Gamma$ conforming discretization of $\Omega$
+      used for \eqref{eq:problem1_simple}. For \eqref{eq:problem2_simple}
+      only conformity to $\Lambda$ is needed.
+    }
+    \label{fig:mesh}
+  \end{center}
+\end{figure}
+
+Formulations \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} shall
+be discretized using contiuous Lagrange element of order 1 ($P_1$) for all the spaces
+involved. We recall that since are are investigating the conforming case, the tripplet
+$P_1$-$P_1$-$P_1$ satisfies
+the discrete inf-sup condition. The resulting linear systems are solved
+using the minimal residual method (MinRes) with stopping criterion requiring the relative
+preconditioned residual norm to be less than $10^{-12}$. As the preconditioner
+we use the (approximate) Riesz mapping with respect to the inner products of
+the spaces in which the two formulations were proved to be well posed.
+In particular, the preconditioner for the Lagrange multiplier relies on
+(the inverse of) the fractional Laplacian $-\Delta^{-1/2}$ on $\Gamma$ for
+\eqref{eq:problem1_simple} and $\Lambda$ for \eqref{eq:problem2_simple}.
+We remark that the size of the linear systems on the finest meshes considered
+here prevents the use direct solvers.
+Therefore iterative solvers were necessary.
+We plot the numerical solution of problem \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} in Figure \ref{fig:sol_benchm1} and \ref{fig:sol_benchm2}, respectively.
+
+\begin{figure}
+\centering
+\includegraphics[width = 0.9\textwidth]{./graphics/mfs_LM2d}
+\caption{Numerical solution of problem \eqref{eq:problem1_simple}: functions $u_h$ and $\udh$ on the left and the Lagrance multiplier $\lambda_h$ on the right.}\label{fig:sol_benchm1}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width = 0.9\textwidth]{./graphics/mfs_LM1d}
+\caption{Numerical solution of problem \eqref{eq:problem2_simple}: functions $u_h$ and $\udh$ on the left and the Lagrance multiplier ${\ld}_h$ on the right.}\label{fig:sol_benchm2}
+\end{figure}
+
+Considering uniform refinements of the initial mesh, Table \ref{tab:error_conform}
+lists the errors of formulations \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}
+on the benchmark problem. It can be seen the error in $u$ and $\ud$ in $H^1$ norm
+converges linearly (as can be expected due to $P_1$ element discretization).
+Moreover, the error of the Lagrange multiplier approximation in $H^{-1/2}$ norm
+decreases quadratically. In the light of $P_1$ discretization this rate appears
+superconvergent. We speculate that the result is due to the fact that the
+exact solution is particularly simple, $L=0$. In case of the results for
+\eqref{eq:problem1_simple} the rate can also be due to the fact that the
+error is interpolated into the same finite element space as the approximation $L_h$.
+We remark that for $u$ and $\ud$ the error is interpolated into FE space of piecewise
+quadratic \emph{discontinous} functions. For \eqref{eq:problem2_simple} we
+evaluate the fractional norm and interpolate the error using piecewise continuous
+cubic functions. Evaluating the fractional norm in higher order spaces
+for formulation with the multiplier space on $\Gamma$ is prohibitively costly.
+
+%
+\begin{table}
+  \scriptsize{
+    \begin{minipage}{0.49\textwidth}
+  \begin{center}
+    \begin{tabular}{c|ccc}
+      \hline
+    $h$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{L-L_h}_{-1/2,\Gamma}$\\
+      \hline
+4.3E-1 & 3.4E0(--) & 5.3E-1(--) & 2.9E0(--)\\
+2.2E-1 & 1.7E0(0.99) & 2.6E-1(1.06) & 6.1E-1(2.25)\\
+1.1E-1 & 8.7E-1(0.99) & 1.3E-1(1.02) & 1.4E-1(2.13)\\
+5.4E-2 & 4.4E-1(1.00) & 6.3E-2(1.00) & 3.4E-2(2.03)\\
+2.7E-2 & 2.2E-1(1.00) & 3.1E-2(1.00) & 8.6E-3(2.00)\\
+\hline
+  \end{tabular}
+  \end{center}
+  \end{minipage}
+    }
+    \vspace{5pt}
+  \scriptsize{%(ii)
+    \begin{minipage}{0.49\textwidth}
+      \begin{center}
+        \begin{tabular}{c|ccc}
+      \hline
+    $h$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{L-L_h}_{-1/2, \Lambda}$\\
+      \hline
+4.3E-1 & 3.1E0(--)    & 5.4E-1(--)   & 4.4E-2(--)   \\
+2.2E-1 & 1.7E0(0.87)  & 2.6E-1(1.06) & 1.1E-2(2.01) \\
+1.1E-1 & 8.6E-1(0.96) & 1.3E-1(1.02) & 2.7E-3(2.01) \\
+5.4E-2 & 4.4E-1(0.99) & 6.3E-2(1.00) & 6.7E-4(2.01) \\
+2.7E-2 & 2.2E-1(1.00) & 3.1E-2(1.00) & 1.7E-4(2.01) \\
+1.4E-2 & 1.1E-1(1.00) & 1.6E-2(1.00) & 4.1E-5(2.01) \\
+\hline
+  \end{tabular}
+  \end{center}
+  \end{minipage}
+  }
+  \caption{Error convergence of \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}
+    on a benchmark problem \eqref{benchmark}. Continuous linear Lagrange
+    elements are used.
+  }
+  \label{tab:error_conform}
+\end{table}
+
+In Table \ref{tab:error_conform} one can observe that the two formulations
+yield practically identical approximations of $u$ and $\ud$. However, the solution
+cost of the two approaches differs. In Table \ref{tab:cost} we summarize the
+size of the linear systems solved at each level of refinement and the time
+for the iterative solver to converge. Let us first note that the proposed
+preconditioners seem robust with respect to discretization parameter as
+the iteration counts are clearly bounded. We then see that the solution
+time for \eqref{eq:problem1_simple} is about 2 times longer compared to
+\eqref{eq:problem2_simple}. This is in addition to the higher setup costs
+of the preconditioner which in our implementation involve solving an eigenvalue
+problem for the fractional Laplacian. Therefore it is advantageous to keep
+the multiplier space as small as possible. We remark that the missing
+results for \eqref{eq:problem1_simple} in Table \ref{tab:cost} and \ref{tab:error_conform}
+are due to the memory limitations which we encounter when solving the eigenvalue problem
+for the Laplacian, which for finest mesh involves cca 32 thousand eigenvalues.
+%
+\begin{table}
+  \scriptsize{
+  \begin{center}
+    \begin{tabular}{c|cc|ccc|ccc}
+      \hline
+      $h$ & $\dim{V_h}$ & $\dim{V_{\odot, h}}$ & $\dim{Q^{\Gamma}_h}$ & $\#$ & $T\left[s\right]$ & $\dim{Q^{\Lambda}_h}$ & $\#$ & $T\left[s\right]$\\
+      \hline
+4.33E-01 &125    &5  &40    &27 &0.03  &5  &9  &0.01\\
+2.17E-01 &729    &9  &144   &55 &0.10  &9  &19 &0.02\\
+1.08E-01 &4913   &17 &544   &62 &0.25  &17 &36 &0.14\\
+5.41E-02 &35937  &33 &2112  &64 &1.97  &33 &42 &1.08\\
+2.71E-02 &274625 &65 &8320  &64 &18.01 &65 &36 &8.24\\
+1.35E-02 &--     &-- &--    &-- &--    &129 &31 &61.37\\
+\hline
+    \end{tabular}
+    \end{center}
+    }
+  \caption{Cost comparison of the two formulations. Number of MinRes iterations
+    is denoted by $\#$. Time till convergence of the iterative solver (excluding the setup) is shown
+    as $T$.
+  }
+\label{tab:cost}
+\end{table}
+
+%\begin{remark}
+%Let us notice that the 3D solution \eqref{benchm_sol3d} is such that $\avrc{u}=0$.
 Therefore in \eqref{benchmark} it is like we are solving two separated problems, one in $\Omega$ and the other on $\Lambda$.
-\end{remark}
-\begin{remark}
-It would be interesting to make a comparison between the solution of the fully coupled 3D-3D problem \eqref{eq:dirneu} (also in the simplified case of type \eqref{eq:dirneu_simple}) and the solution of the reduced problems \eqref{eq:problem1} and \eqref{eq:problem2}.
-Therefore, we could set the values of the data of the problem such that the reduced formulation becomes non-trivial and fully coupled.
-Then, we will solve both the original and reduced problem to observe the differences in the solutions and the values of the Lagrange multiplier.
-\end{remark}
+%\end{remark}
+%\begin{remark}
+%It would be interesting to make a comparison between the solution of the fully coupled 3D-3D problem \eqref{eq:dirneu} (also in the simplified case of type \eqref{eq:dirneu_simple}) and the solution of the reduced problems \eqref{eq:problem1} and \eqref{eq:problem2}.
+%Therefore, we could set the values of the data of the problem such that the reduced formulation becomes non-trivial and fully coupled.
+%Then, we will solve both the original and reduced problem to observe the differences in the solutions and the values of the Lagrange multiplier.
+%\end{remark}

### 2019-10-20 benchmark.tex
consistent notation

@@
   \label{eq:couple_1}
-\mathcal{T}_{\Gamma}u - \mathcal{E}_{\Gamma}\ud = q_1\quad\text{ on }\Gamma,
+\trace{u} - \ext{\ud} = q_1\quad\text{ on }\Gamma,
 \end{equation}
@@
 %
-In \eqref{benchmark}-\eqref{eq:couple_2} the right-hand side data shall be defined as 
+In \eqref{benchmark}-\eqref{eq:couple_2} the right-hand sides shall be defined as 
 \begin{eqnarray*}
@@
 \begin{equation}\label{benchm_flux}
-\lambda=\nabla u \cdot \textbf{n}_{\oplus}=d_z \ud n_{\oplus,z}=0,
+L=\nabla u \cdot \textbf{n}_{\oplus}=d_z \ud n_{\oplus,z}=0,
 \end{equation}
@@
 &(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
-+ \langle \mathcal{T}_{\Gamma} v  - \mathcal{E}_{\Gamma} \vd, L \rangle_\Gamma
++ \langle \trace{v}  - \ext{\vd}, \lambda \rangle_\Gamma
 \\
@@
 \label{eq:problem1_simple_eq2}
-&   \langle \mathcal{T}_{\Gamma} u - \mathcal{E}_{\Gamma} \ud , M \rangle_\Gamma =  \langle q_1 , M \rangle_\Gamma
-\quad \forall M \in H^{-\frac12}(\Gamma)\,.
+&   \langle \trace{u} - \ext{\ud} , \mu \rangle_\Gamma =  \langle q_1 , \mu \rangle_\Gamma
+\quad \forall \mu \in H^{-\frac12}(\Gamma)\,.
 \end{align}
@@
 &(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
-+ |{\partial \cal D}| \langle \avrc{v} - \vd, L \rangle_{H^{-\frac12}(\Lambda)} 
++ |{\partial \cal D}| \langle \avrc{v} - \vd, \ld \rangle_{H^{-\frac12}(\Lambda)} 
 \\
 \nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},V)_{L^2(\Lambda)}
+&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g}, \vd)_{L^2(\Lambda)}
 \quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
@@
 \label{eq:problem2_simple_eq2}
-&  |\partial {\cal D}| \langle \avrc{u} -  \ud, M \rangle_{H^{-\frac12}(\Lambda)} =
-|\partial {\cal D}| \langle \avrc{q_2}, M \rangle_{H^{-\frac12}(\Lambda)}
-\quad \forall M \in H^{-\frac12}(\Lambda)\,.
+&  |\partial {\cal D}| \langle \avrc{u} -  \ud, \md \rangle_{H^{-\frac12}(\Lambda)} =
+|\partial {\cal D}| \langle \avrc{q_2}, \md \rangle_{H^{-\frac12}(\Lambda)}
+\quad \forall \md \in H^{-\frac12}(\Lambda)\,.
 \end{align}
@@
 &-(\Delta u, v)_{L^2(\Omega)} - |{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)} 
-+ |{\cal D}|\langle \avrc{v}  - \vd, L \rangle_\Lambda
++ |{\cal D}|\langle \avrc{v}  - \vd, \ld \rangle_\Lambda
 \\
@@
 &\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda).
+\quad \forall v \in H^1_0(\Omega), \vd \in H^1(\Lambda).
 \\
 \end{align*}
-Since $L=\avrc{\lambda}=0$ and \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d}
+Since $\ld=\avrc{L}=0$ and \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d}
 satisfies \eqref{benchm_1d}, we have that
@@
 
-We can prove in a similar way that \eqref{benchm_sol3d}-\eqref{benchm_sol1d}, with $L=\lambda=0$
+We can prove in a similar way that \eqref{benchm_sol3d}-\eqref{benchm_sol1d}, with $\lambda=0$
 satisfy \eqref{eq:problem1_simple}. Note in particular that $q_1$ is such that
-$\mathcal{T}_{\Gamma}u - \mathcal{E}_{\Gamma}\ud = q_1$ on $\Gamma$.
+$\trace{u} - \ext{\ud} = q_1$ on $\Gamma$.
 
@@
     \caption{$\Lambda$ and $\Gamma$ conforming discretization of $\Omega$
-      used for \eqref{eq:problem1_simple}. For \eqref{eq:problem2_simple}
-      only conformity to $\Lambda$ is needed.
+      used for \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}.
     }
@@
 be discretized using contiuous Lagrange element of order 1 ($P_1$) for all the spaces
-involved. We recall that since are are investigating the conforming case, the tripplet
+involved. We recall that since we are investigating the conforming case, the tripplet
 $P_1$-$P_1$-$P_1$ satisfies
@@
 We remark that the size of the linear systems on the finest meshes considered
-here prevents the use direct solvers.
-Therefore iterative solvers were necessary.
-We plot the numerical solution of problem \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} in Figure \ref{fig:sol_benchm1} and \ref{fig:sol_benchm2}, respectively.
+here prevents the use direct solvers. Therefore iterative solvers were necessary.
+We plot the numerical solution of problem \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} in
+Figure \ref{fig:sol_benchm1} and \ref{fig:sol_benchm2}, respectively.
 
@@
   \begin{center}
-    \begin{tabular}{c|ccc}
+    \begin{tabular}{l|lll}
       \hline
-    $h$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{L-L_h}_{-1/2,\Gamma}$\\
+    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\lambda-\lambda_h}_{-1/2,\Gamma}$\\
       \hline
-4.3E-1 & 3.4E0(--) & 5.3E-1(--) & 2.9E0(--)\\
-2.2E-1 & 1.7E0(0.99) & 2.6E-1(1.06) & 6.1E-1(2.25)\\
-1.1E-1 & 8.7E-1(0.99) & 1.3E-1(1.02) & 1.4E-1(2.13)\\
-5.4E-2 & 4.4E-1(1.00) & 6.3E-2(1.00) & 3.4E-2(2.03)\\
-2.7E-2 & 2.2E-1(1.00) & 3.1E-2(1.00) & 8.6E-3(2.00)\\
+4  & 3.4E0(--) & 5.3E-1(--) & 2.9E0(--)\\
+8  & 1.7E0(0.99) & 2.6E-1(1.06) & 6.1E-1(2.25)\\
+16 & 8.7E-1(0.99) & 1.3E-1(1.02) & 1.4E-1(2.13)\\
+32 & 4.4E-1(1.00) & 6.3E-2(1.00) & 3.4E-2(2.03)\\
+64 & 2.2E-1(1.00) & 3.1E-2(1.00) & 8.6E-3(2.00)\\
 \hline
@@
       \begin{center}
-        \begin{tabular}{c|ccc}
+        \begin{tabular}{l|lll}
       \hline
-    $h$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{L-L_h}_{-1/2, \Lambda}$\\
+    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{-1/2, \Lambda}$\\
       \hline
-4.3E-1 & 3.1E0(--)    & 5.4E-1(--)   & 4.4E-2(--)   \\
-2.2E-1 & 1.7E0(0.87)  & 2.6E-1(1.06) & 1.1E-2(2.01) \\
-1.1E-1 & 8.6E-1(0.96) & 1.3E-1(1.02) & 2.7E-3(2.01) \\
-5.4E-2 & 4.4E-1(0.99) & 6.3E-2(1.00) & 6.7E-4(2.01) \\
-2.7E-2 & 2.2E-1(1.00) & 3.1E-2(1.00) & 1.7E-4(2.01) \\
-1.4E-2 & 1.1E-1(1.00) & 1.6E-2(1.00) & 4.1E-5(2.01) \\
+4   & 3.1E0(--)    & 5.4E-1(--)   & 4.4E-2(--)   \\
+8   & 1.7E0(0.87)  & 2.6E-1(1.06) & 1.1E-2(2.01) \\
+16  & 8.6E-1(0.96) & 1.3E-1(1.02) & 2.7E-3(2.01) \\
+32  & 4.4E-1(0.99) & 6.3E-2(1.00) & 6.7E-4(2.01) \\
+64  & 2.2E-1(1.00) & 3.1E-2(1.00) & 1.7E-4(2.01) \\
+128 & 1.1E-1(1.00) & 1.6E-2(1.00) & 4.1E-5(2.01) \\
 \hline
@@
   \begin{center}
-    \begin{tabular}{c|cc|ccc|ccc}
+    \begin{tabular}{l|ll|lll|lll}
       \hline
-      $h$ & $\dim{V_h}$ & $\dim{V_{\odot, h}}$ & $\dim{Q^{\Gamma}_h}$ & $\#$ & $T\left[s\right]$ & $\dim{Q^{\Lambda}_h}$ & $\#$ & $T\left[s\right]$\\
+      $h^{-1}$ & $\dim{X^1_{h, 0}(\Omega)}$ & $\dim{X^1_{h, 0}(\Lambda)}$ & $\dim{Q_h(\Gamma)}$ & $\#$ & $T\left[s\right]$ & $\dim{Q_h(\Lambda)}$ & $\#$ & $T\left[s\right]$\\
       \hline
-4.33E-01 &125    &5  &40    &27 &0.03  &5  &9  &0.01\\
-2.17E-01 &729    &9  &144   &55 &0.10  &9  &19 &0.02\\
-1.08E-01 &4913   &17 &544   &62 &0.25  &17 &36 &0.14\\
-5.41E-02 &35937  &33 &2112  &64 &1.97  &33 &42 &1.08\\
-2.71E-02 &274625 &65 &8320  &64 &18.01 &65 &36 &8.24\\
-1.35E-02 &--     &-- &--    &-- &--    &129 &31 &61.37\\
+4   &125     &5   &40    &27 &0.03  &5   &9  &0.01\\
+8   &729     &9   &144   &55 &0.10  &9   &19 &0.02\\
+16  &4913    &17  &544   &62 &0.25  &17  &36 &0.14\\
+32  &35937   &33  &2112  &64 &1.97  &33  &42 &1.08\\
+64  &274625  &65  &8320  &64 &18.01 &65  &36 &8.24\\
+128 &2146947 &129 &--    &-- &--    &129 &31 &61.37\\
 \hline

### 2019-10-20 benchmark.tex
typos

@@
 \begin{equation}\label{benchm_flux}
-L=\nabla u \cdot \textbf{n}_{\oplus}=d_z \ud n_{\oplus,z}=0,
+\lambda=\nabla u \cdot \textbf{n}_{\oplus}=d_z \ud n_{\oplus,z}=0,
 \end{equation}
@@
 \end{align*}
-Since $\ld=\avrc{L}=0$ and \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d}
+Since $\ld=\avrc{\lambda}=0$ and \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d}
 satisfies \eqref{benchm_1d}, we have that
@@
 superconvergent. We speculate that the result is due to the fact that the
-exact solution is particularly simple, $L=0$. In case of the results for
+exact solution is particularly simple, $\lambda=0$. In case of the results for
 \eqref{eq:problem1_simple} the rate can also be due to the fact that the
-error is interpolated into the same finite element space as the approximation $L_h$.
+error is interpolated into the same finite element space as the approximation $Q_h$.
 We remark that for $u$ and $\ud$ the error is interpolated into FE space of piecewise

### 2019-10-20 benchmark.tex
revert to L

--- 2019-10-20 benchmark.tex
@@
 superconvergent. We speculate that the result is due to the fact that the
-exact solution is particularly simple, $L=0$. In case of the results for
+exact solution is particularly simple, $\lambda=\ld=0$. In case of the results for
 \eqref{eq:problem1_simple} the rate can also be due to the fact that the
-error is interpolated into the same finite element space as the approximation $L_h$.
+error is interpolated into the same finite element space as the approximation $Q_h$.
 We remark that for $u$ and $\ud$ the error is interpolated into FE space of piecewise

### 2019-12-06 src_lm3d1d/coupled_lm1.py
update

@@ -1,7 +1,8 @@
 # Formulation with the multiplier on the curve
 from dolfin import *
 from xii import *
-from weak_bcs.utils import block_form, MMSData, H1_norm, L2_norm
+from weak_bcs.utils import block_form, MMSData, H1_norm, L2_norm, matrix_fromHs
+from xii.linalg.matrix_utils import identity_matrix
 from hsmg.hseig import Hs0Norm
 from block.algebraic.petsc import LU, AMG
 from block import block_mat, block_vec
@@ -105,7 +106,10 @@ def setup_error_monitor(mms_data, params):
         # On a finer mesh
         Q = FunctionSpace(ph.function_space().mesh(), 'CG', 3)
         Hs = Hs0Norm(Q, s=-0.5, bcs=DirichletBC(Q, Constant(0), 'on_boundary'))
-        
+
+        # A U = M U Lambda
+        # Hs = M * U * Lambda^{-0.5} * (M*U).T
+
         # e*H*e ie (e, e)_H
         e = interpolate(p, Q).vector()
         e.axpy(-1, interpolate(ph, Q).vector())
@@ -157,14 +161,50 @@ def cannonical_riesz_map(W, mms, params, AA):
     return B
 
 
+def withL2_inner_product(W, mms, params, AA):
+    '''Inner product of alpha*H1 x beta*H1 x H-0.5'''
+    V3, V1, Q = W
+    # Extact Vi norms from system
+    V3_inner = AA[0][0]
+    V1_inner = AA[1][1]
+
+    p, q = TrialFunction(Q), TestFunction(Q)
+    Q_inner = assemble(inner(p, q)*dx)
+
+    B = block_diag_mat([V3_inner, V1_inner, Q_inner])
+
+    return B
+
+
+def withL2_riesz_map(W, mms, params, AA):
+    '''Riesz map wrt. inner product of alpha*H1 x beta*H1 x H-0.5'''
+    V3, V1, Q = W
+    # Extact Vi norms from system
+    V3_inner = AA[0][0]
+    V1_inner = AA[1][1]
+    Q_inner = AA[2][2]
+
+    B = block_diag_mat([AMG(V3_inner), AMG(V1_inner), AMG(Q_inner)])
+
+    return B
+
+
+def just_identity(W, mms, params, AA, Z):
+    '''1'''
+    return identity_matrix(W)
+
 # --------------------------------------------------------------------
 
 # The idea now that we register the inner product so that from outside
[…]

### 2019-12-06 src_lm3d1d/coupled_lm2.py

@@ -1,7 +1,7 @@
 # Formulation with the multiplier on the surface
 from dolfin import *
 from xii import *
-from weak_bcs.utils import block_form, MMSData, H1_norm, Hs0_norm, matrix_fromHs
+from weak_bcs.utils import block_form, MMSData, H1_norm, Hs0_norm, matrix_fromHs, L2_norm
 import src_lm3d1d.coupled_lm1 as lm1
 from hsmg.hseig import Hs0Norm
 from block.algebraic.petsc import LU, AMG
@@ -115,6 +115,10 @@ def setup_error_monitor(mms_data, params):
         u3, u1, p = mms.solution
         u3h, u1h, ph = wh
 
+        # X = ph.function_space()
+        # bcs = DirichletBC(X, Constant(0), 'on_boundary').get_boundary_values().keys()
+        # print np.linalg.norm(ph.vector().get_local()[bcs], np.inf)
+
         # Passing the HsNorm from preconditioner so that we don't compute
         # eigenvalues twice
         Hs0Norm = mms.normals.pop()
@@ -140,14 +144,23 @@ def setup_error_monitor(mms_data, params):
 cannonical_inner_product = lm1.cannonical_inner_product
 cannonical_riesz_map = lm1.cannonical_riesz_map
 
+withL2_inner_product = lm1.withL2_inner_product
+withL2_riesz_map = lm1.withL2_riesz_map
+
+just_identity = lm1.just_identity
+
 # --------------------------------------------------------------------
 
 # The idea now that we register the inner product so that from outside
 # of the module they are accessible without referring to them by name
-W_INNER_PRODUCTS = {0: cannonical_inner_product}
+W_INNER_PRODUCTS = {0: cannonical_inner_product,
+                    1: withL2_inner_product,
+                    2: just_identity}
 
 # And we do the same for preconditioners / riesz maps
-W_RIESZ_MAPS = {0: cannonical_riesz_map}
+W_RIESZ_MAPS = {0: cannonical_riesz_map,
+                1: withL2_riesz_map,
+                2: just_identity}
 
 # How is the problem parametrized
 PARAMETERS = ('size', )

### 2019-12-06 src_lm3d1d/coupled_1_lm3d_align.py
update

@@ -1,0 +1,191 @@
+# Formulation with the multiplier on the curve
+from dolfin import *
+from xii import *
+from weak_bcs.utils import (block_form, MMSData, H1_norm, L2_norm, matrix_fromHs,
+                            mat_add)
+
+import src_lm3d1d.coupled_lm1 as lm1
+from line_cut import curve_cover
+from hsmg.hseig import Hs0Norm, HsNorm
+from block.algebraic.petsc import LU, AMG
+from block import block_mat, block_vec
+import numpy as np
+
+
+def setup_mms(params):
+    '''Manufactured solution from notes'''
+    
+    u3d = Expression('sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)
+    f3d = Expression('(8*pi*pi)*sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)
+
+    f1d = Expression('pi*pi*sin(pi*x[2])', degree=4)
+    u1d = Expression('sin(pi*x[2])', degree=4)
+
+    p = Expression('0', degree=4)  # The multiplier
+
+    return MMSData(solution=[u3d, u1d, p],
+                   rhs=[(f3d, f1d, u1d), (u3d, u1d, p)],
+                   subdomains=[], normals=[])
+
+
+def setup_problem(n, mms, params):
+    '''Coupled 3d-1d with 1d Lagrange multiplier'''
+    # NOTE: inborg distinguishes between parallel and not parallel hmin
+    omega = UnitCubeMesh(n, n, n)
+
+    A, B = np.array([0.5, 0.5, 0]), np.array([0.5, 0.5, 1])
+    gamma = StraightLineMesh(A, B, 3*n)
+
+    cut_cells = curve_cover(gamma, omega, tol=1E-10)
+    omega_subdomains = MeshFunction('size_t', omega, omega.topology().dim(), 0)
+    omega_subdomains.array()[cut_cells] = 1
+
+    lm_gamma = EmbeddedMesh(omega_subdomains, 1)
+    File('x.pvd') << omega
+    File('y.pvd') << lm_gamma
+    
+    # The poisson problem
+    V3 = FunctionSpace(omega, 'CG', 1)
+    V1 = FunctionSpace(gamma, 'CG', 1)
+    Q = FunctionSpace(lm_gamma, 'DG', 0)
+    
+    W = [V3, V1, Q]
+
+    u3, u1, p = map(TrialFunction, W)
[…]

### 2019-12-06 src_lm3d1d/coupled_1_lm3d_noalign.py

@@ -1,0 +1,191 @@
+# Formulation with the multiplier on the curve
+from dolfin import *
+from xii import *
+from weak_bcs.utils import (block_form, MMSData, H1_norm, L2_norm, matrix_fromHs,
+                            mat_add)
+
+import src_lm3d1d.coupled_lm1 as lm1
+from line_cut import curve_cover
+from hsmg.hseig import Hs0Norm, HsNorm
+from block.algebraic.petsc import LU, AMG
+from block import block_mat, block_vec
+import numpy as np
+
+
+def setup_mms(params):
+    '''Manufactured solution from notes'''
+    
+    u3d = Expression('sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)
+    f3d = Expression('(8*pi*pi)*sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)
+
+    f1d = Expression('pi*pi*sin(pi*x[2])', degree=4)
+    u1d = Expression('sin(pi*x[2])', degree=4)
+
+    p = Expression('0', degree=4)  # The multiplier
+
+    return MMSData(solution=[u3d, u1d, p],
+                   rhs=[(f3d, f1d, u1d), (u3d, u1d, p)],
+                   subdomains=[], normals=[])
+
+
+def setup_problem(n, mms, params):
+    '''Coupled 3d-1d with 1d Lagrange multiplier'''
+    # NOTE: inborg distinguishes between parallel and not parallel hmin
+    omega = UnitCubeMesh(n+1, n+1, n)
+
+    A, B = np.array([0.5, 0.5, 0]), np.array([0.5, 0.5, 1])
+    gamma = StraightLineMesh(A, B, 3*n)
+
+    cut_cells = curve_cover(gamma, omega, tol=1E-10)
+    omega_subdomains = MeshFunction('size_t', omega, omega.topology().dim(), 0)
+    omega_subdomains.array()[cut_cells] = 1
+
+    lm_gamma = EmbeddedMesh(omega_subdomains, 1)
+    File('x.pvd') << omega
+    File('y.pvd') << lm_gamma
+    
+    # The poisson problem
+    V3 = FunctionSpace(omega, 'CG', 1)
+    V1 = FunctionSpace(gamma, 'CG', 1)
+    Q = FunctionSpace(lm_gamma, 'DG', 0)
+    
+    W = [V3, V1, Q]
+
+    u3, u1, p = map(TrialFunction, W)
[…]

### 2019-12-06 src_lm3d1d/line_cut.py

@@ -1,0 +1,247 @@
+from collections import deque
+import networkx as nx
+import dolfin as df
+import numpy as np
+import itertools
+import operator
+
+# ---
+# Once we have a marked volume in the mesh we want to clasify interior
+# and exterior facets for the purpose of penalizing jumps and what not
+def build_graph(mesh, volume_cells):
+    '''
+    Graph representation of cell-cell connectivity over facets. In graph 
+    cell is a node; common facet between cells mounts to an edge. Edges 
+    can be clasified during graph building: those connected to just one 
+    cell are guaranteed to exterior.
+    '''
+    assert isinstance(volume_cells, set)
+    
+    assert mesh.mpi_comm().tompi4py().size == 1  # Only serial
+    
+    cdim = mesh.topology().dim()
+    fdim = cdim - 1
+
+    mesh.init(cdim, fdim)
+    mesh.init(fdim, cdim)
+
+    f2c, c2f = mesh.topology()(fdim, cdim), mesh.topology()(cdim, fdim)
+
+    G = nx.Graph()
+    volume_facets = np.unique(np.hstack(map(c2f, volume_cells)))
+
+    vc = set(volume_cells)
+
+    interiors, exteriors = [], []
+    for f in volume_facets:
+        cells = f2c(f)
+
+        # Definitely an exterior
+        if len(cells) == 1:
+            exteriors.append(f)
+        else:
+            # We are always after a subset
+            if set(cells) <= volume_cells:
+                G.add_edges_from(itertools.combinations(cells, 2))
+                interiors.append(f)
+            else:
+                exteriors.append(f)
+
+    return (interiors, exteriors), G
+
+
+def ie_facets_volume(mesh, volume_cells):
+    '''Interior, exterior facets of the marked volume (for each connected component)'''
+    _, G = build_graph(mesh, volume_cells)
+
+    ccs = nx.connected_components(G)
+
+    interiors, exteriors = [], []
+    for cc in ccs:
+        (i, e), _ = build_graph(mesh, cc)
+        interiors.append(i)
+        exteriors.append(e)
+
+    return interiors, exteriors
+
+# ---
+# Some CGAL like functionality where, unlike with dolfin, I can control
+# tolerance for what is 0
+def norm(vec):
+    '''Handle cross product'''
+    if not vec.shape:  # Scalar
[…]

### 2019-12-07 benchmark.tex
forgot L
progress on nonconf results

@@
 -d_{zz}^2 \ud =g \quad &\text{on $\Lambda$}\\
-u=h \quad &\text{on $\partial \Omega$},
+u=u_b \quad &\text{on $\partial \Omega$},
 \end{align}
@@
 \begin{eqnarray*}
-  &f=8\pi ^2 \sin (2\pi x) \sin (2\pi y),\quad &g={\pi ^2}\sin \left({\pi z}\right),\quad h=\sin (2\pi x) \sin (2\pi y),\\
+  &f=8\pi ^2 \sin (2\pi x) \sin (2\pi y),\quad &g={\pi ^2}\sin \left({\pi z}\right),\quad u_b=\sin (2\pi x) \sin (2\pi y),\\
   &q_1=\sin (2\pi x) \sin (2\pi y) - \sin \left({\pi z}\right),\quad &q_2=-\sin \left({\pi z}\right).
@@
 
-We can prove in a similar way that \eqref{benchm_sol3d}-\eqref{benchm_sol1d}, with $\lambda=0$
+We can prove in a similar way that \eqref{benchm_sol3d}-\eqref{benchm_sol1d}, with $\lambda=L=0$
 satisfy \eqref{eq:problem1_simple}. Note in particular that $q_1$ is such that
@@
 
-\subsection{Numerical experiments} Using the benchmark problem \eqref{benchmark}
-we now investigate convergence properties of the two formulations. To this
-end we consider a \emph{uniform} tessilation of $\mathcal{T}^{\Omega}_h$ of $\Omega$ consisting of
-tetrahedra with diameter $h$. Further, the discretization shall be
-geometrically \emph{conforming} to both $\Lambda$ and $\Gamma$ such that
-the tessilations $\mathcal{T}^{\Gamma}_h$, $\mathcal{T}^{\Lambda}_h$ are made up
-of facets and edges of $\mathcal{T}^{\Omega}_h$ respectively, cf. Figure \ref{fig:mesh}
+\subsection{Numerical experiments. $\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$.}\label{sec:experiment_conform}
+Using the benchmark problem \eqref{benchmark} we now investigate convergence
+properties of the two formulations. To this end we consider a \emph{uniform} tessilation
+of $\mathcal{T}^{\Omega}_h$ of $\Omega$ consisting of tetrahedra with diameter $h$.
+Further, the discretization shall be geometrically \emph{conforming} to both $\Lambda$
+and $\Gamma$ such that the tessilations $\mathcal{T}^{\Gamma}_h$, $\mathcal{T}^{\Lambda}_h$
+are made up of facets and edges of $\mathcal{T}^{\Omega}_h$ respectively, cf. Figure \ref{fig:mesh}
 for illustration.
@@
 using the minimal residual method (MinRes) with stopping criterion requiring the relative
-preconditioned residual norm to be less than $10^{-12}$. As the preconditioner
-we use the (approximate) Riesz mapping with respect to the inner products of
+preconditioned residual norm to be less than $10^{-8}$. Following operator
+preconditioning technique \cite{mardal2011preconditioning} we use as preconditioners
+the (approximate) Riesz mapping with respect to the inner products of
 the spaces in which the two formulations were proved to be well posed.
@@
 \eqref{eq:problem1_simple} and $\Lambda$ for \eqref{eq:problem2_simple}.
-We remark that the size of the linear systems on the finest meshes considered
-here prevents the use direct solvers. Therefore iterative solvers were necessary.
+In both cases the fractional Laplacian was realized by spectral decomposition
+\cite{kuchta2016preconditioners}.
+%We remark that the size of the linear systems on the finest meshes considered
+%here prevents the use direct solvers. Therefore iterative solvers were necessary.
 We plot the numerical solution of problem \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} in
@@
 superconvergent. We speculate that the result is due to the fact that the
-exact solution is particularly simple, $\lambda=\ld=0$. In case of the results for
-\eqref{eq:problem1_simple} the rate can also be due to the fact that the
-error is interpolated into the same finite element space as the approximation $Q_h$.
+exact solution is particularly simple, $\lambda=\ld=0$.
+%In case of the results for
+%\eqref{eq:problem1_simple} the rate can also be due to the fact that the
+%error is interpolated into the same finite element space as the approximation $Q_h$.
 We remark that for $u$ and $\ud$ the error is interpolated into FE space of piecewise
@@
 
+For the sake of comparison with non-conforming formulation of \eqref{eq:problem2} from
+\S\ref{sec:unfit2} Table \ref{tab:error_conform} also
+lists the error of the Lagrange multiplier in the $L^2$ norm. Here, quadratic convergence is observed
+for \eqref{eq:problem2_simple}. For \eqref{eq:problem1_simple} the rate between 1.5 and 2.
 %
@@
   \scriptsize{
-    \begin{minipage}{0.49\textwidth}
   \begin{center}
-    \begin{tabular}{l|lll}
+    \begin{tabular}{l|llll}
       \hline
-    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\lambda-\lambda_h}_{-1/2,\Gamma}$\\
+    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\lambda-\lambda_h}_{-1/2,\Gamma}$ & $\norm{\lambda-\lambda_h}_{0,\Gamma}$\\
       \hline
-4  & 3.4E0(--) & 5.3E-1(--) & 2.9E0(--)\\
-8  & 1.7E0(0.99) & 2.6E-1(1.06) & 6.1E-1(2.25)\\
-16 & 8.7E-1(0.99) & 1.3E-1(1.02) & 1.4E-1(2.13)\\
-32 & 4.4E-1(1.00) & 6.3E-2(1.00) & 3.4E-2(2.03)\\
-64 & 2.2E-1(1.00) & 3.1E-2(1.00) & 8.6E-3(2.00)\\
+4  & 3.4E0(--)    & 5.3E-1(--)   & 2.9E0(--)    &8.7E0(--)    \\
+8  & 1.7E0(0.99)  & 2.6E-1(1.06) & 6.1E-1(2.25) &1.9E0(2.21)  \\
+16 & 8.7E-1(0.99) & 1.3E-1(1.02) & 1.4E-1(2.13) &4.7E-1(1.99) \\
+32 & 4.4E-1(1.00) & 6.3E-2(1.00) & 3.4E-2(2.03) &1.3E-1(1.80) \\
+64 & 2.2E-1(1.00) & 3.1E-2(1.00) & 8.6E-3(2.00) &4.2E-2(1.68) \\
+\midrule
+$h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{-1/2, \Lambda}$ & $\norm{\ld-\ldh}_{0, \Lambda}$\\
+\hline
+4   & 3.1E0(--)    & 5.4E-1(--)   & 4.4E-2(--)   & 7.8E-2(--)  \\
+8   & 1.7E0(0.87)  & 2.6E-1(1.06) & 1.1E-2(2.01) & 1.9E-2(2.01)\\
+16  & 8.6E-1(0.96) & 1.3E-1(1.02) & 2.7E-3(2.01) & 4.8E-3(2.02)\\
+32  & 4.4E-1(0.99) & 6.3E-2(1.00) & 6.7E-4(2.01) & 1.2E-3(2.01)\\
+64  & 2.2E-1(1.00) & 3.1E-2(1.00) & 1.7E-4(2.01) & 3.0E-4(2.01)\\
+128 & 1.1E-1(1.00) & 1.6E-2(1.00) & 4.1E-5(2.01) & 7.4E-5(2.00)\\
 \hline
@@
   \end{center}
-  \end{minipage}
-    }
-    \vspace{5pt}
-  \scriptsize{%(ii)
-    \begin{minipage}{0.49\textwidth}
-      \begin{center}
-        \begin{tabular}{l|lll}
-      \hline
-    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{-1/2, \Lambda}$\\
-      \hline
-4   & 3.1E0(--)    & 5.4E-1(--)   & 4.4E-2(--)   \\
-8   & 1.7E0(0.87)  & 2.6E-1(1.06) & 1.1E-2(2.01) \\
-16  & 8.6E-1(0.96) & 1.3E-1(1.02) & 2.7E-3(2.01) \\
-32  & 4.4E-1(0.99) & 6.3E-2(1.00) & 6.7E-4(2.01) \\
-64  & 2.2E-1(1.00) & 3.1E-2(1.00) & 1.7E-4(2.01) \\
-128 & 1.1E-1(1.00) & 1.6E-2(1.00) & 4.1E-5(2.01) \\
-\hline
-  \end{tabular}
-  \end{center}
-  \end{minipage}
   }
@@
 \end{table}
+
+\subsection{Numerical experiments. $\mathcal{T}^{\Omega}_h$ non-conforming to $\Gamma$}\label{sec:experiment_nonconform}
+Using benchmark problem \eqref{benchmark} we finally consider \eqref{eq:problem2} in the
+setting of \S \ref{sec:unfit2}. To this end we let $\mathcal{T}^{\Omega}_h$ be a uniform
+tessilation of $\Omega$ such that no cell $\mathcal{T}^{\Omega}_h$ has any edge
+lying on $\Gamma$. Further we let $h^{\prime}=h/3$ in $\mathcal{T}^{\Gamma}_{h^{\prime}}$,
+cf. Figure \ref{fig:unfit}.\\
+
+\begin{table}
+%%   %%%
+\begin{minipage}[b]{0.45\linewidth}
+ \centering
+ \includegraphics[width=\textwidth]{graphics/nonconform_mesh.pdf}
+ \vspace{-20pt}
+ \captionof{figure}{
+   Sample discretization of the benchmark geometry in the non-conforming case. 
+ }
+\label{fig:unfit}
+\end{minipage}
+\hspace{5pt}
+%%%
+    \begin{minipage}[b]{0.48\linewidth}
+      %%%
+  \scriptsize{
+  \begin{center}
+    \begin{tabular}{l|lll}
+      \hline
+    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{0,\mathcal{G}_h}$\\
+      \hline
+5   & 2.6E0(--)    & 2.3E-1(--)   & 3.0E-2(--)\\
+9   & 1.5E0(0.84)  & 9.4E-2(1.42) & 6.9E-3(2.34)\\
+17  & 8.1E-1(0.94) & 4.3E-2(1.18) & 1.5E-3(2.35)\\
+33  & 4.2E-1(0.98) & 2.1E-2(1.06) & 2.0E-4(2.96)\\
+65  & 2.1E-1(0.99) & 1.1E-2(1.02) & 3.3E-5(2.67)\\
+129 & 1.1E-1(1.00) & 5.2E-3(1.01) & 4.9E-6(2.74)\\
+\hline
+    \end{tabular}
+  \end{center}    
+}    
+  \captionof{table}{
+    Error convergence of \eqref{eq:problem2_simple} on a benchmark problem \eqref{benchmark} in case
+    $\mathcal{T}^{\Omega}_h$ does not conform to $\Gamma$.}
+  \label{tab:unfit}    
+  \end{minipage}
+\end{table}
+
+Using discretization in terms of $P_1$-$P_1$-$P_0$ element Table \ref{tab:unfit}
+lists the error of the stabilized formulation \eqref{eq:problem2}. A linear
+convergence in the $H^1$ norm can be observed in the error of $u$ and $\ud$.
+For simplicity the convergence of the multiplier is measured in the $L^2$ norm
+on $\mathcal{G}_h$ (instead of the $H^{-1/2}(\Gamma)$ norm used in the analysis).
+Then, convergence exceeding order 2 can be observed, however, the rates are rather
+unstable.
 

### 2019-12-07 unfitted_prob2.tex
progress on nonconf results

@@
 \def\patch{\omega _j}
-\subsection{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$}
+\subsection{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$}\label{sec:unfit2}
 We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_h$ cut the interface $\Gamma$. It is easy to understand that the formulation of Problem 2 is more suitable. 

### 2019-12-07 src_lm3d1d/coupled_lm1_neumann.py
swithc to L2 norm

@@ -1,11 +1,7 @@
 # Formulation with the multiplier on the curve
 from dolfin import *
 from xii import *
-from weak_bcs.utils import (block_form, MMSData, H1_norm, L2_norm, matrix_fromHs,
-                            mat_add)
-
-import src_lm3d1d.coupled_lm1 as lm1
-from line_cut import curve_cover
+from weak_bcs.utils import block_form, MMSData, H1_norm, L2_norm
 from hsmg.hseig import Hs0Norm, HsNorm
 from block.algebraic.petsc import LU, AMG
 from block import block_mat, block_vec
@@ -15,11 +11,11 @@ import numpy as np
 def setup_mms(params):
     '''Manufactured solution from notes'''
     
-    u3d = Expression('sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)
-    f3d = Expression('(8*pi*pi)*sin(2*pi*x[0])*sin(2*pi*x[1])', degree=4)
+    u3d = Expression('cos(2*pi*x[0])*cos(2*pi*x[1])', degree=4)
+    f3d = Expression('(8*pi*pi)*cos(2*pi*x[0])*cos(2*pi*x[1])', degree=4)
 
-    f1d = Expression('pi*pi*sin(pi*x[2])', degree=4)
-    u1d = Expression('sin(pi*x[2])', degree=4)
+    f1d = Expression('pi*pi*cos(pi*x[2])', degree=4)
+    u1d = Expression('cos(pi*x[2])', degree=4)
 
     p = Expression('0', degree=4)  # The multiplier
 
@@ -31,24 +27,15 @@ def setup_mms(params):
 def setup_problem(n, mms, params):
     '''Coupled 3d-1d with 1d Lagrange multiplier'''
     # NOTE: inborg distinguishes between parallel and not parallel hmin
-    omega = UnitCubeMesh(n+1, n+1, n)
+    omega = UnitCubeMesh(n, n, n)
 
     A, B = np.array([0.5, 0.5, 0]), np.array([0.5, 0.5, 1])
-    gamma = StraightLineMesh(A, B, 3*n)
-    #mms.subdomains.append(gamma)
-    
-    cut_cells = curve_cover(gamma, omega, tol=1E-10)
-    omega_subdomains = MeshFunction('size_t', omega, omega.topology().dim(), 0)
-    omega_subdomains.array()[cut_cells] = 1
+    gamma = StraightLineMesh(A, B, n)
 
[…]

### 2019-12-07 src_lm3d1d/coupled_lm2_neumann.py

@@ -1,0 +1,195 @@
+
+
+# Formulation with the multiplier on the surface
+from dolfin import *
+from xii import *
+from weak_bcs.utils import block_form, MMSData, H1_norm, Hs0_norm, matrix_fromHs, L2_norm
+import src_lm3d1d.coupled_lm1 as lm1
+from hsmg.hseig import Hs0Norm, HsNorm
+from block.algebraic.petsc import LU, AMG
+from block import block_mat, block_vec
+import numpy as np
+
+
+def setup_problem(n, mms, params):
+    '''Coupled 3d-1d with 2d Lagrange multiplier'''
+    # NOTE: inborg distinguishes between parallel and not parallel hmin
+    omega = UnitCubeMesh(n, n, n)
+
+    size = 0.25
+    # Coupling surface
+    walls = ['near((x[0]-L)*(x[0]-H), 0) && ((L-tol) < x[1]) && ((H+tol) > x[1])',
+             'near((x[1]-L)*(x[1]-H), 0) && ((L-tol) < x[0]) && ((H+tol) > x[0])']
+    walls = ['( %s )' % w for w in walls]
+    
+    chi = CompiledSubDomain(' || '.join(walls), tol=1E-10, L=0.5-size, H=0.5+size)
+    surfaces = MeshFunction('size_t', omega, 2, 0)
+    chi.mark(surfaces, 1)
+
+    wall = CompiledSubDomain('near(x[0]*(1-x[0])*x[1]*(1-x[1]), 0)')
+    wall.mark(surfaces, 2)
+    
+    # File('surface.pvd') << surfaces
+    gamma = EmbeddedMesh(surfaces, 1)
+
+    # Centerline
+    A, B = np.array([0.5, 0.5, 0]), np.array([0.5, 0.5, 1])
+    lmbda = StraightLineMesh(A, B, n)  
+
+    # The poisson problem
+    V3 = FunctionSpace(omega, 'CG', 1)
+    V1 = FunctionSpace(lmbda, 'CG', 1)
+    Q = FunctionSpace(gamma, 'CG', 1)
+    
+    W = [V3, V1, Q]
+
+    u3, u1, p = map(TrialFunction, W)
+    v3, v1, q = map(TestFunction, W)
+
+    Tu3, Tv3 = (Trace(f, gamma) for f in (u3, v3))
+    Eu1, Ev1 = (Extension(f, gamma, type='uniform') for f in (u1, v1))
+    
[…]

### 2019-12-07 src_lm3d1d/foo.py

@@ -1,0 +1,44 @@
+from line_cut import curve_cover
+import numpy as np
+from dolfin import *
+from xii import *
+
+n = 4
+
+omega = UnitCubeMesh(3, 3, n)
+
+A, B = np.array([0.5, 0.5, 0]), np.array([0.5, 0.5, 1])
+gamma = StraightLineMesh(A, B, 3*n+1)
+
+cut_cells = curve_cover(gamma, omega, tol=1E-10)
+omega_subdomains = MeshFunction('size_t', omega, omega.topology().dim(), 0)
+omega_subdomains.array()[cut_cells] = 1
+
+lm_gamma = EmbeddedMesh(omega_subdomains, 1)
+File('omega_subdomains.pvd') << omega_subdomains
+
+Q = FunctionSpace(lm_gamma, 'DG', 0)
+print Q.dim()
+p, q = TrialFunction(Q), TestFunction(Q)
+
+circle = None#Circle(1E-10, 12)
+Tp, Tq = Average(p, gamma, circle), Average(q, gamma, circle)
+
+dx_ = Measure('dx', domain=gamma)
+m = inner(Tp, Tq)*dx_
+
+X, y, Z = map(ii_convert, ii_assemble(m).chain)
+
+x = Function(Q).vector()
+for i in range(Q.dim()):
+    x.set_local(np.eye(Q.dim())[i])
+
+    print (Z*x).norm('l2')
+    #< 1E-13:
+    #    omega_subdomains[int(cut_cells[i])] = 2
+    #    print '!'
+    #x *= 0.
+print Z.array()
+
+print np.sort(np.linalg.eigvalsh(y.array()))
+print np.sort(np.linalg.eigvalsh(ii_convert(ii_assemble(m)).array()))

### 2019-12-07 src_lm3d1d/foo_2d.py

@@ -1,0 +1,41 @@
+from line_cut import curve_cover
+import numpy as np
+from dolfin import *
+from xii import *
+
+n = 4
+
+omega = UnitSquareMesh(n+1, n+1)
+
+A, B = np.array([0.5, 0.0]), np.array([0.5, 1])
+gamma = StraightLineMesh(A, B, 3*n)
+
+cut_cells = curve_cover(gamma, omega, tol=1E-10)
+omega_subdomains = MeshFunction('size_t', omega, omega.topology().dim(), 0)
+omega_subdomains.array()[cut_cells] = 1
+
+File('cut_2d.pvd') << omega_subdomains
+
+
+lm_gamma = EmbeddedMesh(omega_subdomains, 1)
+
+Q = FunctionSpace(lm_gamma, 'DG', 0)
+
+p, q = TrialFunction(Q), TestFunction(Q)
+Tp, Tq = Trace(p, gamma), Trace(q, gamma)
+
+dx_ = Measure('dx', domain=gamma)
+m = inner(Tp, Tq)*dx_
+
+X, y, Z = map(ii_convert, ii_assemble(m).chain)
+
+x = Function(Q).vector()
+for i in range(Q.dim()):
+    x.set_local(np.eye(Q.dim())[i])
+
+    if (Z*x).norm('l2') < 1E-13:
+        omega_subdomains[int(cut_cells[i])] = 2
+        print '!'
+    x *= 0.
+
+File('cut_2d.pvd') << omega_subdomains

### 2019-12-07 benchmark.tex
update

@@
 
-\subsection{Numerical experiments. $\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$.}\label{sec:experiment_conform}
+\subsection{Numerical experiments. $\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}\label{sec:experiment_conform}
 Using the benchmark problem \eqref{benchmark} we now investigate convergence
@@
 
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.5\textwidth]{./graphics/conform_mesh.pdf}
-    \caption{$\Lambda$ and $\Gamma$ conforming discretization of $\Omega$
+\begin{table}
+%%   %%%
+\begin{minipage}[b]{0.35\linewidth}
+ \centering
+ \includegraphics[width=\textwidth]{graphics/conform_mesh.pdf}
+ \vspace{-20pt}
+ \captionof{figure}{
+$\Lambda$ and $\Gamma$ conforming discretization of $\Omega$
    used for \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}.   
@@
 \label{fig:mesh}
+\end{minipage}
+\hspace{2pt}
+\begin{minipage}[b]{0.63\textwidth}
+  \scriptsize{
+  \begin{center}
+    \begin{tabular}{l|llll}
+      \toprule
+    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\lambda-\lambda_h}_{-\tfrac{1}{2},\Gamma}$ & $\norm{\lambda-\lambda_h}_{0,\Gamma}$\\
+      \hline
+4  & 3.4E0(--)    & 5.3E-1(--)   & 2.9E0(--)    &8.7E0(--)    \\
+8  & 1.7E0(0.99)  & 2.6E-1(1.06) & 6.1E-1(2.25) &1.9E0(2.21)  \\
+16 & 8.7E-1(0.99) & 1.3E-1(1.02) & 1.4E-1(2.13) &4.7E-1(1.99) \\
+32 & 4.4E-1(1.00) & 6.3E-2(1.00) & 3.4E-2(2.03) &1.3E-1(1.80) \\
+64 & 2.2E-1(1.00) & 3.1E-2(1.00) & 8.6E-3(2.00) &4.2E-2(1.68) \\
+\midrule
+$h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-u_{\odot, h^{\prime}}}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{-\tfrac{1}{2}, \Lambda}$ & $\norm{\ld-\ldh}_{0, \Lambda}$\\
+\hline
+4   & 3.1E0(--)    & 5.4E-1(--)   & 4.4E-2(--)   & 7.8E-2(--)  \\
+8   & 1.7E0(0.87)  & 2.6E-1(1.06) & 1.1E-2(2.01) & 1.9E-2(2.01)\\
+16  & 8.6E-1(0.96) & 1.3E-1(1.02) & 2.7E-3(2.01) & 4.8E-3(2.02)\\
+32  & 4.4E-1(0.99) & 6.3E-2(1.00) & 6.7E-4(2.01) & 1.2E-3(2.01)\\
+64  & 2.2E-1(1.00) & 3.1E-2(1.00) & 1.7E-4(2.01) & 3.0E-4(2.01)\\
+128 & 1.1E-1(1.00) & 1.6E-2(1.00) & 4.1E-5(2.01) & 7.4E-5(2.00)\\
+\bottomrule
+  \end{tabular}
   \end{center}
-\end{figure}
+  }
+  \captionof{table}{Error convergence of \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}
+    on a benchmark problem \eqref{benchmark}. Continuous linear Lagrange
+    elements are used.
+  }
+  \label{tab:error_conform}
+  \end{minipage}
+\end{table}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width = 0.9\textwidth]{./graphics/mfs_LM1d}
-\caption{Numerical solution of problem \eqref{eq:problem2_simple}: functions $u_h$ and $\udh$ on the left and the Lagrance multiplier ${\ld}_h$ on the right.}\label{fig:sol_benchm2}
-\end{figure}
-
 Considering uniform refinements of the initial mesh, Table \ref{tab:error_conform}
@@
 
+\begin{figure}
+\centering
+\includegraphics[width = 0.9\textwidth]{./graphics/mfs_LM1d}
+\caption{Numerical solution of problem \eqref{eq:problem2_simple}: functions $u_h$ and $\udh$ on the left and the Lagrance multiplier ${\ld}_h$ on the right.}\label{fig:sol_benchm2}
+\end{figure}
+
 For the sake of comparison with non-conforming formulation of \eqref{eq:problem2} from
@@
 for \eqref{eq:problem2_simple}. For \eqref{eq:problem1_simple} the rate between 1.5 and 2.
-%
-\begin{table}
-  \scriptsize{
-  \begin{center}
-    \begin{tabular}{l|llll}
-      \hline
-    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\lambda-\lambda_h}_{-1/2,\Gamma}$ & $\norm{\lambda-\lambda_h}_{0,\Gamma}$\\
-      \hline
-4  & 3.4E0(--)    & 5.3E-1(--)   & 2.9E0(--)    &8.7E0(--)    \\
-8  & 1.7E0(0.99)  & 2.6E-1(1.06) & 6.1E-1(2.25) &1.9E0(2.21)  \\
-16 & 8.7E-1(0.99) & 1.3E-1(1.02) & 1.4E-1(2.13) &4.7E-1(1.99) \\
-32 & 4.4E-1(1.00) & 6.3E-2(1.00) & 3.4E-2(2.03) &1.3E-1(1.80) \\
-64 & 2.2E-1(1.00) & 3.1E-2(1.00) & 8.6E-3(2.00) &4.2E-2(1.68) \\
-\midrule
-$h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{-1/2, \Lambda}$ & $\norm{\ld-\ldh}_{0, \Lambda}$\\
-\hline
-4   & 3.1E0(--)    & 5.4E-1(--)   & 4.4E-2(--)   & 7.8E-2(--)  \\
-8   & 1.7E0(0.87)  & 2.6E-1(1.06) & 1.1E-2(2.01) & 1.9E-2(2.01)\\
-16  & 8.6E-1(0.96) & 1.3E-1(1.02) & 2.7E-3(2.01) & 4.8E-3(2.02)\\
-32  & 4.4E-1(0.99) & 6.3E-2(1.00) & 6.7E-4(2.01) & 1.2E-3(2.01)\\
-64  & 2.2E-1(1.00) & 3.1E-2(1.00) & 1.7E-4(2.01) & 3.0E-4(2.01)\\
-128 & 1.1E-1(1.00) & 1.6E-2(1.00) & 4.1E-5(2.01) & 7.4E-5(2.00)\\
-\hline
-  \end{tabular}
-  \end{center}
-  }
-  \caption{Error convergence of \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}
-    on a benchmark problem \eqref{benchmark}. Continuous linear Lagrange
-    elements are used.
-  }
-  \label{tab:error_conform}
-\end{table}
 
 \subsection{Numerical experiments. $\mathcal{T}^{\Omega}_h$ non-conforming to $\Gamma$}\label{sec:experiment_nonconform}
-Using benchmark problem \eqref{benchmark} we finally consider \eqref{eq:problem2} in the
+Using benchmark problem \eqref{benchmark} we consider \eqref{eq:problem2} in the
 setting of \S \ref{sec:unfit2}. To this end we let $\mathcal{T}^{\Omega}_h$ be a uniform
 tessilation of $\Omega$ such that no cell $\mathcal{T}^{\Omega}_h$ has any edge
-lying on $\Gamma$. Further we let $h^{\prime}=h/3$ in $\mathcal{T}^{\Gamma}_{h^{\prime}}$,
-cf. Figure \ref{fig:unfit}.\\
+lying on $\Lambda$. Further we let $h^{\prime}=h/3$ in $\mathcal{T}^{\Lambda}_{h^{\prime}}$,
+cf. Figure \ref{fig:unfit}.
+
+Using discretization in terms of $P_1$-$P_1$-$P_0$ element Table \ref{tab:error_unfit}
+lists the error of the stabilized formulation of \eqref{eq:problem2}. A linear
+convergence in the $H^1$ norm can be observed in the error of $u$ and $\ud$. We
+remark that the norms were computed as in \S\ref{sec:experiment_conform}. For simplicity
+the convergence of the multiplier is measured in the $L^2$ norm
+on $\mathcal{G}_h$ (instead of the $H^{-1/2}(\Gamma)$ norm used in the analysis).
+Then, convergence exceeding order 2 can be observed, however, the rates are rather
+unstable.
 
@@
 %%   %%%
-\begin{minipage}[b]{0.45\linewidth}
+\begin{minipage}[b]{0.35\linewidth}
  \centering
@@
 \end{minipage}
-\hspace{5pt}
+\hspace{2pt}
 %%%
-    \begin{minipage}[b]{0.48\linewidth}
+    \begin{minipage}[b]{0.62\linewidth}
       %%%
@@
     \begin{tabular}{l|lll}
-      \hline
+      \toprule
     $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{0,\mathcal{G}_h}$\\
@@
 129 & 1.1E-1(1.00) & 5.2E-3(1.01) & 4.9E-6(2.74)\\
-\hline
+\bottomrule
     \end{tabular}
@@
     Error convergence of \eqref{eq:problem2_simple} on a benchmark problem \eqref{benchmark} in case
-    $\mathcal{T}^{\Omega}_h$ does not conform to $\Gamma$.}
-  \label{tab:unfit}    
+    $\mathcal{T}^{\Omega}_h$ does not conform to $\Lambda$.}
+  \label{tab:error_unfit}    
   \end{minipage}
@@
 
-Using discretization in terms of $P_1$-$P_1$-$P_0$ element Table \ref{tab:unfit}
-lists the error of the stabilized formulation \eqref{eq:problem2}. A linear
-convergence in the $H^1$ norm can be observed in the error of $u$ and $\ud$.
-For simplicity the convergence of the multiplier is measured in the $L^2$ norm
-on $\mathcal{G}_h$ (instead of the $H^{-1/2}(\Gamma)$ norm used in the analysis).
-Then, convergence exceeding order 2 can be observed, however, the rates are rather
-unstable.
+\subsection{Comparison}
+In Tables \ref{tab:error_conform}, \ref{tab:error_unfit} one can observe that 
+all the formulations yield practically identically accurate approximations of $u$.
+Futher, compared to the conforming case, the stabilized formulation \eqref{eq:problem2}
+results in a greater accuracy of $u_{\cdot, h}$ as the underlying mesh $\mathcal{T}^{\Lambda}_{h}$ is
+here finer. Due to the different definitions in the three formulations, comparision of the Lagrange
+multiplier convergence is not straightforward. We therefore limit ourselves to a
+comment that in the $L^2$ norm all the formulations yield faster than linear convergence.
 
-In Table \ref{tab:error_conform} one can observe that the two formulations
-yield practically identical approximations of $u$ and $\ud$. However, the solution
+However, the solution
 cost of the two approaches differs. In Table \ref{tab:cost} we summarize the
@@
       \hline
-4   &125     &5   &40    &27 &0.03  &5   &9  &0.01\\
-8   &729     &9   &144   &55 &0.10  &9   &19 &0.02\\
-16  &4913    &17  &544   &62 &0.25  &17  &36 &0.14\\
-32  &35937   &33  &2112  &64 &1.97  &33  &42 &1.08\\
-64  &274625  &65  &8320  &64 &18.01 &65  &36 &8.24\\
+4   &125     &5   &40    & &0.03  &5   &9  &0.01\\
+8   &729     &9   &144   & &0.10  &9   &19 &0.02\\
+16  &4913    &17  &544   & &0.25  &17  &36 &0.14\\
+32  &35937   &33  &2112  & &1.97  &33  &42 &1.08\\
+64  &274625  &65  &8320  & &18.01 &65  &36 &8.24\\
 128 &2146947 &129 &--    &-- &--    &129 &31 &61.37\\

### 2019-12-07 appendix.tex
all results in

\section{System sizes in benchmark formulations}\label{sec:appendix}
Below we list dimensions of the finite element spaces used to discretize
formualations \eqref{eq:problem1}, \eqref{eq:problem2} and stabilized
\eqref{eq:problem2} on different levels of refinement.

\begin{center}
  \scriptsize{
    \begin{tabular}{l|lll|lll|lll}
      \toprule
      \multirow{2}{*}{$l$} & \multicolumn{3}{c|}{\eqref{eq:problem1}} & \multicolumn{3}{c|}{\eqref{eq:problem2}} & \multicolumn{3}{c}{ Stabilized \eqref{eq:problem2}}\\
      \cline{2-10}
      & $\lvert X^1_{h, 0}(\Omega) \rvert$ & $\lvert X^1_{h, 0}(\Lambda) \rvert$ & $\lvert Q_h(\Gamma) \rvert$ &
      $\lvert X^1_{h, 0}(\Omega) \rvert$ & $\lvert X^1_{h, 0}(\Lambda) \rvert$ & $\lvert Q_h(\Lambda) \rvert$ &
      $\lvert X^1_{h, 0}(\Omega) \rvert$ & $\lvert X^1_{h^{\prime}, 0}(\Lambda) \rvert$ & $\lvert Q_h(\mathcal{G}_h) \rvert$\\
      \hline
     1& 125    & 5  & 40   & 125     & 5   & 5   & 180     & 13  & 24  \\
     2& 729    & 9  & 144  & 729     & 9   & 9   & 900     & 25  & 48  \\
     3& 4913   & 17 & 544  & 4913    & 17  & 17  & 5508    & 49  & 96  \\
     4& 35937  & 33 & 2112 & 35937   & 33  & 33  & 38148   & 97  & 192 \\
     5& 274625 & 65 & 8320 & 274625  & 65  & 65  & 283140  & 193 & 384 \\
     6& --     & -- & -    & 2146689 & 129 & 129 & 2180100 & 385 & 768 \\
      \bottomrule
    \end{tabular}
    }
    \end{center}

### 2019-12-07 benchmark.tex
all results in

@@
 
-Formulations \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} shall
-be discretized using contiuous Lagrange element of order 1 ($P_1$) for all the spaces
-involved. We recall that since we are investigating the conforming case, the tripplet
-$P_1$-$P_1$-$P_1$ satisfies
-the discrete inf-sup condition. The resulting linear systems are solved
-using the minimal residual method (MinRes) with stopping criterion requiring the relative
-preconditioned residual norm to be less than $10^{-8}$. Following operator
-preconditioning technique \cite{mardal2011preconditioning} we use as preconditioners
-the (approximate) Riesz mapping with respect to the inner products of
-the spaces in which the two formulations were proved to be well posed.
-In particular, the preconditioner for the Lagrange multiplier relies on
-(the inverse of) the fractional Laplacian $-\Delta^{-1/2}$ on $\Gamma$ for
-\eqref{eq:problem1_simple} and $\Lambda$ for \eqref{eq:problem2_simple}.
-In both cases the fractional Laplacian was realized by spectral decomposition
-\cite{kuchta2016preconditioners}.
-%We remark that the size of the linear systems on the finest meshes considered
-%here prevents the use direct solvers. Therefore iterative solvers were necessary.
-We plot the numerical solution of problem \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} in
-Figure \ref{fig:sol_benchm1} and \ref{fig:sol_benchm2}, respectively.
-
-\begin{figure}
-\centering
-\includegraphics[width = 0.9\textwidth]{./graphics/mfs_LM2d}
-\caption{Numerical solution of problem \eqref{eq:problem1_simple}: functions $u_h$ and $\udh$ on the left and the Lagrance multiplier $\lambda_h$ on the right.}\label{fig:sol_benchm1}
-\end{figure}
-
-Considering uniform refinements of the initial mesh, Table \ref{tab:error_conform}
+Considering inf-sup stable discretization in terms of continuous linear Lagrange
+($P_1$) elements (for all the spaces), Table \ref{tab:error_conform}
 lists the errors of formulations \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}
@@
 %error is interpolated into the same finite element space as the approximation $Q_h$.
-We remark that for $u$ and $\ud$ the error is interpolated into FE space of piecewise
-quadratic \emph{discontinous} functions. For \eqref{eq:problem2_simple} we
+We remark that for $u$ and $\ud$ the error is interpolated into the finite element space of
+piecewise quadratic \emph{discontinous} functions. For \eqref{eq:problem2_simple} we
 evaluate the fractional norm and interpolate the error using piecewise continuous
-cubic functions. Evaluating the fractional norm in higher order spaces
-for formulation with the multiplier space on $\Gamma$ is prohibitively costly.
+cubic functions. This is due to the fact that evaluating the fractional norm in higher order spaces
+for on $\Gamma$ is prohibitively costly. For the sake of comparison with non-conforming formulation of \eqref{eq:problem2} from
+\S\ref{sec:unfit2} Table \ref{tab:error_conform} also
+lists the error of the Lagrange multiplier in the $L^2$ norm. Here, quadratic convergence is observed
+for \eqref{eq:problem2_simple}. For \eqref{eq:problem1_simple} the rate between 1.5 and 2.
+
+We plot the numerical solution of problem \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} in
+Figure \ref{fig:sol_benchm1} and \ref{fig:sol_benchm2}, respectively.
+
+\begin{figure}
+\centering
+\includegraphics[width = 0.9\textwidth]{./graphics/mfs_LM2d}
+\caption{Numerical solution of problem \eqref{eq:problem1_simple}: functions $u_h$ and $\udh$ on the left and the Lagrance multiplier $\lambda_h$ on the right.}\label{fig:sol_benchm1}
+\end{figure}
 
@@
 \end{figure}
-
-For the sake of comparison with non-conforming formulation of \eqref{eq:problem2} from
-\S\ref{sec:unfit2} Table \ref{tab:error_conform} also
-lists the error of the Lagrange multiplier in the $L^2$ norm. Here, quadratic convergence is observed
-for \eqref{eq:problem2_simple}. For \eqref{eq:problem1_simple} the rate between 1.5 and 2.
 
@@
 remark that the norms were computed as in \S\ref{sec:experiment_conform}. For simplicity
-the convergence of the multiplier is measured in the $L^2$ norm
-on $\mathcal{G}_h$ (instead of the $H^{-1/2}(\Gamma)$ norm used in the analysis).
-Then, convergence exceeding order 2 can be observed, however, the rates are rather
-unstable.
+the convergence of the multiplier is measured in the $L^2$ norm rather then the $H^{-1/2}(\Gamma)$
+norm used in the analysis. Then, convergence exceeding order 1.5 can be observed, however,
+the rates are rather unstable.
+
+\miro{The solution is plotted in ..... I guess there should be some zoom in on the
+cut cells.}
 
@@
       \toprule
-    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{0,\mathcal{G}_h}$\\
+    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{0,\Lambda}$\\
       \hline
-5   & 2.6E0(--)    & 2.3E-1(--)   & 3.0E-2(--)\\
-9   & 1.5E0(0.84)  & 9.4E-2(1.42) & 6.9E-3(2.34)\\
-17  & 8.1E-1(0.94) & 4.3E-2(1.18) & 1.5E-3(2.35)\\
-33  & 4.2E-1(0.98) & 2.1E-2(1.06) & 2.0E-4(2.96)\\
-65  & 2.1E-1(0.99) & 1.1E-2(1.02) & 3.3E-5(2.67)\\
-129 & 1.1E-1(1.00) & 5.2E-3(1.01) & 4.9E-6(2.74)\\
+5   & 2.6E0(--)    & 2.3E-1(--)   & 1.7E-1(--) \\ 
+9   & 1.5E0(0.84)  & 9.4E-2(1.42) & 7.1E-2(1.36)\\
+17  & 8.1E-1(0.94) & 4.3E-2(1.18) & 2.9E-2(1.37)\\
+33  & 4.2E-1(0.98) & 2.1E-2(1.06) & 7.9E-3(1.91)\\
+65  & 2.1E-1(0.99) & 1.1E-2(1.02) & 2.6E-3(1.64)\\
+129 & 1.1E-1(1.00) & 5.2E-3(1.01) & 8.5E-4(1.61)\\
 \bottomrule
@@
 
-However, the solution
-cost of the two approaches differs. In Table \ref{tab:cost} we summarize the
-size of the linear systems solved at each level of refinement and the time
-for the iterative solver to converge. Let us first note that the proposed
-preconditioners seem robust with respect to discretization parameter as
-the iteration counts are clearly bounded. We then see that the solution
-time for \eqref{eq:problem1_simple} is about 2 times longer compared to
-\eqref{eq:problem2_simple}. This is in addition to the higher setup costs
+In order to discuss solution cost of the formulations we consider 
+the resulting preconditioned linear systems. In particular, we shall compare
+spectral condition numbers and the time to convergence of the preconditioned
+minimal residual (MinRes) solver with the with stopping criterion requiring
+the relative preconditioned residual norm to be less than $10^{-8}$. We remark
+that we shall ignore the setup cost of the precondtioner.
+
+Following operator preconditioning technique \cite{mardal2011preconditioning} we
+use as preconditioners for \eqref{eq:problem1} and \eqref{eq:problem2} in the
+conforming case the (approximate) Riesz mapping with respect to the inner products of
+the spaces in which the two formulations were proved to be well posed.
+In particular, the preconditioner for the Lagrange multiplier relies on
+(the inverse of) the fractional Laplacian $-\Delta^{-1/2}$ on $\Gamma$ for
+\eqref{eq:problem1_simple} and $\Lambda$ for \eqref{eq:problem2_simple}.
+In both cases the fractional Laplacian was realized by spectral decomposition
+\cite{kuchta2016preconditioners}.
+
+For the unfitted stabilized \eqref{eq:problem2} the Lagrange multiplier preconditioner
+uses a Riesz map with respect to the inner product due to $L^2(\mathcal{G}_h)$ and
+the stabilization \eqref{eq:stab}, i.e.
+\[
+({\ld}_h, {\md}_h) \mapsto \sum _{K\in \mathcal{G}_h}\int_{K}{\ld}_h {\md}_h + \sum _{K\in \mathcal{G}_h} \int_{\partial K \setminus \partial \mathcal{G}_h} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket.
+\]
+This simple choice does not yield bounded
+iterations. However, establishing a robust precondtioner in this case 
+is beyond the scope of the paper and shall be pursued in the future works.
+
+In Table \ref{tab:cost} we compare solution time, number of iterations and
+condition numbers of the (linear systems due to the) three formulations.
+Let us first note that the proposed preconditioners for \eqref{eq:problem1} and
+\eqref{eq:problem2} in the conforming case seem robust with respect to discretization
+parameter as the iteration counts and condition numbers are bounded in $h$.
+We then see that the solution time for \eqref{eq:problem1_simple} is about 2 times
+longer compared to \eqref{eq:problem2_simple}. This is in addition to the higher setup costs
 of the preconditioner which in our implementation involve solving an eigenvalue
@@
 are due to the memory limitations which we encounter when solving the eigenvalue problem
-for the Laplacian, which for finest mesh involves cca 32 thousand eigenvalues.
+for the Laplacian, which for finest mesh involves cca 32 thousand eigenvalues, cf. Appendix \ref{sec:appendix}.
 %
+
+Due to the missing proper preconditioner for the Lagrange multiplier block the
+number of iterations in the third, unfitted formulation can be seen to approximatly
+double on refinement.
+
 \begin{table}
@@
   \begin{center}
-    \begin{tabular}{l|ll|lll|lll}
+    \begin{tabular}{l|lll|lll|lll}
+      \toprule
+      \multirow{2}{*}{$l$} & \multicolumn{3}{c|}{\eqref{eq:problem1}} & \multicolumn{3}{c|}{\eqref{eq:problem2}} & \multicolumn{3}{c}{ Stabilized \eqref{eq:problem2}}\\
+      \cline{2-10}
+      & \# & $T\left[s\right]$ & $\kappa$ & \# & $T\left[s\right]$ & $\kappa$ & \# & $T\left[s\right]$ & $\kappa$\\
       \hline
-      $h^{-1}$ & $\dim{X^1_{h, 0}(\Omega)}$ & $\dim{X^1_{h, 0}(\Lambda)}$ & $\dim{Q_h(\Gamma)}$ & $\#$ & $T\left[s\right]$ & $\dim{Q_h(\Lambda)}$ & $\#$ & $T\left[s\right]$\\
-      \hline
-4   &125     &5   &40    & &0.03  &5   &9  &0.01\\
-8   &729     &9   &144   & &0.10  &9   &19 &0.02\\
-16  &4913    &17  &544   & &0.25  &17  &36 &0.14\\
-32  &35937   &33  &2112  & &1.97  &33  &42 &1.08\\
-64  &274625  &65  &8320  & &18.01 &65  &36 &8.24\\
-128 &2146947 &129 &--    &-- &--    &129 &31 &61.37\\
-\hline
+      1 & 20 & 0.03  & 15.56 & 9  & 0.02  & 3.04 & 21  & 0.01   & 9.70 \\
+      2 & 35 & 0.06  & 16.28 & 17 & 0.03  & 4.67 & 31  & 0.03   & 15.87\\
+      3 & 38 & 0.14  & 16.64 & 22 & 0.06  & 6.25 & 53  & 0.15   & 32.93\\
+      4 & 39 & 1.70  & 16.75 & 24 & 0.89  & 7.03 & 110 & 4.54   & 61.48\\
+      5 & 38 & 12.04 & 16.78 & 20 & 5.21  & 5.02 & 232 & 59.43  & 94.25\\
+      6 & -- & --    & --    & 17 & 28.77 & --   & 507 & 832.90 & --   \\
+      \bottomrule
     \end{tabular}
@@
     }
-  \caption{Cost comparison of the two formulations. Number of MinRes iterations
-    is denoted by $\#$. Time till convergence of the iterative solver (excluding the setup) is shown
-    as $T$.
+  \caption{Cost comparison of the formulations across refinement levels $l$.
+    Number of MinRes iterations and the conditioned number of the preconditioned
+    problem is denoted by $\#$ and $\kappa$ respectively. Time till convergence
+    of the iterative solver (excluding the setup) is shown as $T$.
   }

### 2019-12-07 unfitted.tex
all results in

@@
 The same also in $\tilde{\omega _j}$ for $v\in H^1(\tilde{\omega _j})$. This choice leads to the following stabilization 
-\begin{equation*}
+\begin{equation}\label{eq:stab}
 s(\lambda_h, \mu_h)= \sum _{K\in \mathcal{G}_h} \int_{\partial K \setminus \partial \mathcal{G}_h} h \llbracket \lambda_h \rrbracket \llbracket \mu_h \rrbracket,
-\end{equation*}
+\end{equation}
 being $\llbracket \lambda_h \rrbracket$ the jump of $\lambda_h$ across the internal faces of $\mathcal{G}_h$.
@@
 Let us consider macro patches $\left\{ F_j \right\}_j$ of elements of the 3D mesh $\mathcal{T}_h^{\Omega}$ intersecting the 1D manifold $\Lambda$.
-These patches are such that and  $jH\leq |F_j\cap \Lambda|\leq H+h$, where $H$ is sufficiently larger than $h$.
+These patches are such that and  $H\leq |F_j\cap \Lambda|\leq H+h$, where $H$ is sufficiently larger than $h$.
 Moreover, there exist constants $c_h$ and $c_H$ such that $c_hh\leq H \leq c_H^{-1}h$.
@@
 \begin{multline*}
-\|\nabla \pi_F v \|_{L^2(\Omega)} \leq \|\nabla I_h v\|_{L^2(\Omega)} + \sum_j|\alpha_j|\|\nabla \varphi _j\|_{L^2(\bar{\omega}_j)}\\
-(\text{stability of }I_h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \sum_j|\alpha_j|\|\nabla \varphi _j\|_{L^2(\bar{\omega}_j)}
+\|\nabla \pi_F v \|_{L^2(\Omega)} \leq \|\nabla I_h v\|_{L^2(\Omega)} + \left(\sum_j|\alpha_j|^2\|\nabla \varphi _j\|^2_{L^2(\bar{\omega}_j)}\right)^{\frac 12}\\
+(\text{stability of }I_h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \left(\sum_j|\alpha_j|^2\|\nabla \varphi _j\|^2_{L^2(\bar{\omega}_j)}\right)^{\frac 12}
+\end{multline*}
+and for the second term we have
+\begin{multline*}
+\sum_j|\alpha_j|^2\|\nabla \varphi _j\|^2_{L^2(\bar{\omega}_j)}\leq
 \\
-\left(\text{using }\|\nabla \varphi\|=O(1)\right) \lesssim \|\nabla  v\|_{L^2(\Omega)} + \sum_j \frac{\left|\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})\right|}{\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}}
+\left(\text{using }\|\nabla \varphi _j\|=O(1)\right) \lesssim  \sum_j \frac{\left(\left|\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})\right|\right)^2}{\left(\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}\right)^2}
 \\
-\left(\text{since }\left|\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}\right|=O(H)\right) \lesssim  \|\nabla  v\|_{L^2(\Omega)} + \frac 1H \sum_j \left|\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})\right|
+\left(\text{since }\left|\int_{F_j\cap \Lambda}|\DD|\avrc{T\varphi_j}\right|=O(H)\right) \lesssim \frac {1}{H^2} \sum_j \left(\left|\int_{F_j\cap \Lambda} |\DD| (\avrc{Tv}-\avrc{TI_hv})\right| \right)^2
 \\
-(\text{H\"older}) \lesssim  \|\nabla  v\|_{L^2(\Omega)} + \frac 1H \sum_j |F_j\cap \Lambda|^{\frac 12} \left(\int_{F_j\cap \Lambda} |\DD|^2(\avrc{Tv}-\avrc{TI_hv})^2\right)^{\frac 12}
+(\text{Jensen}) \lesssim  \frac {1}{H^2} \sum_j |F_j\cap \Lambda| \int_{F_j\cap \Lambda} |\DD|^2(\avrc{Tv}-\avrc{TI_hv})^2
 \\
-(\text{being }|F_j\cap \Lambda| \leq H+h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H^{\frac 12}} \sum_j  |\DD|\| \avrc{Tv}-\avrc{TI_hv}\|_{L^2(F_j\cap \Lambda)}
+(\text{being }|F_j\cap \Lambda| \leq H+h)\lesssim  \frac {1}{H} \sum_j \| \avrc{Tv}-\avrc{TI_hv}\|^2_{L^2(F_j\cap \Lambda), |\DD|}
 \\
-(\text{average inequality}) \lesssim \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H^{\frac 12}} \sum_j |\DD|^{\frac 12} \| T(v-I_hv)\|_{L^2(\omega _j\cap \Gamma)}  
+(\text{average inequality}) \lesssim  \frac {1}{H} \sum_j \| T(v-I_hv)\|^2_{L^2(\omega _j\cap \Gamma)}  
 \\
-\left(\text{trace inequality} \right)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H} \sum_j  \| v-I_h v\|_{L^2(\omega_j)} \lesssim \|\nabla  v\|_{L^2(\Omega)} + \frac {1}{H}  \| v-I_h v\|_{L^2(\Omega)}
+\left(\text{trace inequality} \right)\lesssim  \frac {1}{H^2} \sum_j  \| v-I_h v\|^2_{L^2(\omega_j)} \lesssim  \frac {1}{H^2}  \| v-I_h v\|^2_{L^2(\Omega)} 
 \\
-(\text{approximation properties of }I_h)\lesssim \|\nabla  v\|_{L^2(\Omega)}.
+(\text{approximation properties of }I_h)\lesssim \|\nabla  v\|^2_{L^2(\Omega)}
 \end{multline*}
+and the continuity of $\pi_F$ follows.
 

### 2019-12-07 benchmark.tex
update

@@
 Following operator preconditioning technique \cite{mardal2011preconditioning} we
-use as preconditioners for \eqref{eq:problem1} and \eqref{eq:problem2} in the
+propose as preconditioners for \eqref{eq:problem1} and \eqref{eq:problem2} in the
 conforming case the (approximate) Riesz mapping with respect to the inner products of
@@
 \eqref{eq:problem1_simple} and $\Lambda$ for \eqref{eq:problem2_simple}.
-In both cases the fractional Laplacian was realized by spectral decomposition
-\cite{kuchta2016preconditioners}.
+A detailed analysis of the preconditioners will be presented in a separate
+work. We remark that in both cases the fractional Laplacian was here realized
+by spectral decomposition \cite{kuchta2016preconditioners}.
 

### 2019-12-07 src_lm3d1d/foo.py

@@ -27,18 +27,35 @@ Tp, Tq = Average(p, gamma, circle), Average(q, gamma, circle)
 dx_ = Measure('dx', domain=gamma)
 m = inner(Tp, Tq)*dx_
 
-X, y, Z = map(ii_convert, ii_assemble(m).chain)
+M = ii_convert(ii_assemble(m)).array()
 
-x = Function(Q).vector()
-for i in range(Q.dim()):
-    x.set_local(np.eye(Q.dim())[i])
+X = FunctionSpace(gamma, 'DG', 0)
+x, y = Function(Q), Function(Q)
 
-    print (Z*x).norm('l2')
-    #< 1E-13:
-    #    omega_subdomains[int(cut_cells[i])] = 2
-    #    print '!'
-    #x *= 0.
-print Z.array()
+# This shows the problem
+M0 = np.zeros_like(M)
+for i in range(len(M0)):
+    x.vector().set_local(np.eye(Q.dim())[i])
+    x_ = interpolate(x, X)    
+    for j in range(len(M0)):
+        y.vector().set_local(np.eye(Q.dim())[j])
+        y_ = interpolate(y, X)
+        M0[i, j] = assemble(inner(x_, y_)*dx)
 
-print np.sort(np.linalg.eigvalsh(y.array()))
-print np.sort(np.linalg.eigvalsh(ii_convert(ii_assemble(m)).array()))
+print np.linalg.cond(M0)
+
+# X, y, Z = map(ii_convert, ii_assemble(m).chain)
+
+# x = Function(Q).vector()
+# for i in range(Q.dim()):
+#     x.set_local(np.eye(Q.dim())[i])
+
+#     print (Z*x).norm('l2')
+#     #< 1E-13:
+#     #    omega_subdomains[int(cut_cells[i])] = 2
+#     #    print '!'
+#     #x *= 0.
+# print Z.array()
+
+# print np.sort(np.linalg.eigvalsh(y.array()))
+# print np.sort(np.linalg.eigvalsh(ii_convert(ii_assemble(m)).array()))

### 2019-12-07 src_lm3d1d/poisson_3d.py

@@ -2,6 +2,7 @@ from dolfin import *
 from xii import *
 from weak_bcs.utils import block_form, MMSData, H1_norm
 from block import block_mat, block_vec
+from block.algebraic.petsc import AMG
 import numpy as np
 
 
@@ -55,3 +56,32 @@ def setup_error_monitor(mms_data, params):
 
 # How is the problem parametrized
 PARAMETERS = ('mu', )
+
+# --------------------------------------------------------------------
+
+if __name__ == '__main__':
+    from petsc4py import PETSc
+    from IPython import embed
+    
+    for n in [4*2**i for i in range(6)]:
+        mms = setup_mms(None)
+
+        A, b, V = setup_problem(n, mms, params=None)
+        A = A[0][0]
+        b = b[0]
+        V = V[0]
+
+        solver = PETScKrylovSolver('cg', 'hypre_amg')
+        solver.set_operators(A, A)
+
+        solver.parameters['relative_tolerance'] = 1E-8
+
+        ksp = solver.ksp()
+        # ksp.setComputeEigenvalues(1)
+
+        x = Function(V).vector()
+
+        timer = Timer('ksp')
+        niters = solver.solve(x, b)
+        print V.dim(), niters, timer.stop()
+        # print ksp.computeEigenvalues()

### 2019-12-07 src_lm3d1d/poisson_3d.py
only time iters

@@ -67,21 +67,33 @@ if __name__ == '__main__':
         mms = setup_mms(None)
 
         A, b, V = setup_problem(n, mms, params=None)
-        A = A[0][0]
-        b = b[0]
+        A = as_backend_type(A[0][0]).mat()
+        b = as_backend_type(b[0]).vec()
         V = V[0]
 
-        solver = PETScKrylovSolver('cg', 'hypre_amg')
-        solver.set_operators(A, A)
+        ksp = PETSc.KSP().create()
+        ksp.setType('cg')
+        ksp.setOperators(A)
+        ksp.setConvergenceHistory()
+        ksp.setNormType(PETSc.KSP.NormType.NORM_PRECONDITIONED)
 
-        solver.parameters['relative_tolerance'] = 1E-8
+        pc = ksp.getPC()
+        pc.setType('hypre')
+        pc.setOperators(A, A)
+        pc.setUp()
+        
+        # User configs
+        opts = PETSc.Options()
+        opts.setValue('ksp_rtol', 1E-8)
+        opts.setValue('ksp_atol', 1E-20)
+        opts.setValue('ksp_monitor_true_residual', None)
+        ksp.setFromOptions()
+        
+        x = A.createVecLeft()
+        dt = Timer('ksp')
+        ksp.solve(b, x)
+        dt = dt.stop()
 
-        ksp = solver.ksp()
-        # ksp.setComputeEigenvalues(1)
+        niters = ksp.getIterationNumber()
 
-        x = Function(V).vector()
-
-        timer = Timer('ksp')
-        niters = solver.solve(x, b)
-        print V.dim(), niters, timer.stop()
-        # print ksp.computeEigenvalues()
+        print V.dim(), '%.2f' % dt, niters

### 2019-12-07 benchmark.tex
relative to cg

@@
 the relative preconditioned residual norm to be less than $10^{-8}$. We remark
-that we shall ignore the setup cost of the precondtioner.
+that we shall ignore the setup cost of the preconditioner.
 
@@
 We then see that the solution time for \eqref{eq:problem1_simple} is about 2 times
-longer compared to \eqref{eq:problem2_simple}. This is in addition to the higher setup costs
-of the preconditioner which in our implementation involve solving an eigenvalue
-problem for the fractional Laplacian. Therefore it is advantageous to keep
+longer compared to \eqref{eq:problem2_simple} which is about 4 times more expensive
+than the solution of the Poisson problem \eqref{benchm_3d}. This is in addition to the
+higher setup costs of the preconditioner which in our implementation involve solving
+an eigenvalue problem for the fractional Laplacian. Therefore it is advantageous to keep
 the multiplier space as small as possible. We remark that the missing
@@
   \begin{center}
-    \begin{tabular}{l|lll|lll|lll}
+    \begin{tabular}{l|lll|lll|lll|ll}
       \toprule
-      \multirow{2}{*}{$l$} & \multicolumn{3}{c|}{\eqref{eq:problem1}} & \multicolumn{3}{c|}{\eqref{eq:problem2}} & \multicolumn{3}{c}{ Stabilized \eqref{eq:problem2}}\\
-      \cline{2-10}
-      & \# & $T\left[s\right]$ & $\kappa$ & \# & $T\left[s\right]$ & $\kappa$ & \# & $T\left[s\right]$ & $\kappa$\\
+      \multirow{2}{*}{$l$} & \multicolumn{3}{c|}{\eqref{eq:problem1}} & \multicolumn{3}{c|}{\eqref{eq:problem2}} & \multicolumn{3}{c|}{ Stabilized \eqref{eq:problem2}} & \multicolumn{2}{c}{\eqref{benchm_3d}}\\
+      \cline{2-12}
+      & \# & $T\left[s\right]$ & $\kappa$ & \# & $T\left[s\right]$ & $\kappa$ & \# & $T\left[s\right]$ & $\kappa$ & \# & $T\left[s\right]$\\
       \hline
-      1 & 20 & 0.03  & 15.56 & 9  & 0.02  & 3.04 & 21  & 0.01   & 9.70 \\
-      2 & 35 & 0.06  & 16.28 & 17 & 0.03  & 4.67 & 31  & 0.03   & 15.87\\
-      3 & 38 & 0.14  & 16.64 & 22 & 0.06  & 6.25 & 53  & 0.15   & 32.93\\
-      4 & 39 & 1.70  & 16.75 & 24 & 0.89  & 7.03 & 110 & 4.54   & 61.48\\
-      5 & 38 & 12.04 & 16.78 & 20 & 5.21  & 5.02 & 232 & 59.43  & 94.25\\
-      6 & -- & --    & --    & 17 & 28.77 & --   & 507 & 832.90 & --   \\
+      1 & 20 & 0.03  & 15.56 & 9  & 0.02  & 3.04 & 21  & 0.01   & 9.70  &3 & $<0.01$\\ 
+      2 & 35 & 0.06  & 16.28 & 17 & 0.03  & 4.67 & 31  & 0.03   & 15.87 &4 & $<0.01$\\ 
+      3 & 38 & 0.14  & 16.64 & 22 & 0.06  & 6.25 & 53  & 0.15   & 32.93 &5 & 0.01   \\ 
+      4 & 39 & 1.70  & 16.75 & 24 & 0.89  & 7.03 & 110 & 4.54   & 61.48 &5 & 0.12   \\ 
+      5 & 38 & 12.04 & 16.78 & 20 & 5.21  & 5.02 & 232 & 59.43  & 94.25 &5 & 0.90  \\ 
+      6 & -- & --    & --    & 17 & 28.77 & --   & 507 & 832.90 & --    &6 & 7.75  \\ 
       \bottomrule
@@
     problem is denoted by $\#$ and $\kappa$ respectively. Time till convergence
-    of the iterative solver (excluding the setup) is shown as $T$.
+    of the iterative solver (excluding the setup) is shown as $T$. Results of algebraic
+    multigrid preconditioned conjugate gradient method for 3D Poisson are shown
+    in the last 2 columns.
   }

### 2019-12-08 benchmark.tex
consistency in caption Tab5.3

@@
   \caption{Cost comparison of the formulations across refinement levels $l$.
-    Number of MinRes iterations and the conditioned number of the preconditioned
+    Number of Krylov (preconditioned conjugate gradient for \eqref{benchm_3d},
+    MinRes otherwise) iterations and the conditioned number of the preconditioned
     problem is denoted by $\#$ and $\kappa$ respectively. Time till convergence
-    of the iterative solver (excluding the setup) is shown as $T$. Results of algebraic
-    multigrid preconditioned conjugate gradient method for 3D Poisson are shown
-    in the last 2 columns.
+    of the iterative solver (excluding the setup) is shown as $T$. 
   }

### 2019-12-13 unfitted_prob2.tex
all results in
1st revision unfitted analysis

--- 2019-07-22 unfitted_prob2.tex
@@
 \def\patch{\omega _j}
-\subsection{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$}
-We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_h$ cut the interface $\Gamma$. It is easy to understand that the formulation of Problem 2 is more suitable. 
+\subsection{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$} \label{sec:unfit2}
+We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_h$ cut the interface $\Gamma$. The formulation of Problem 2 is more suitable for this purpose. 
 %{\color{red} Add more details, we can refer also to cutFEM (Burman, Massing etc.) explaining the limitation of that approach (network case for example).}\\
@@
 
-\subsubsection{Problem 2} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X_{h,0}^1(\Omega)$ and $X_{h,0}^1(\Lambda)$, see the previous subsection for the definition.
-Notice that in this case we suppose that the mesh sizes of the 3D mesh $\mathcal{T}^{\Omega}_h$ and the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different, in particular we suppose the 1D mesh is finer.
-Concerning the multiplier space, let $\mathcal{G}_h = \{K \in \mathcal{T}^{\Omega}_h: \, K\cap \Lambda \neq \emptyset\}$, namely the set of the 3D elements which intersect $\Lambda$, and let us define $Q_h=\{{\ld}_h : {\ld}_h \in P^0(K) \, \forall K \in \mathcal{G}_h\}$.
-We notice that we are extending the multiplier to the 3D elements: equivalenty we could have defined $\lambda_h$ as a piecewise constant function on $K\cap \Lambda$ for any $K \in \mathcal{G}_h$, but we use this trick so that we do not need to consider the 1D mesh given by the intersection of the elements of $\mathcal{G}_h$ with $\Lambda$.
-With this choice the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s({\ld}_h, {\md}_h)$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}.
-In particular, we build a new multiplier space $L_h$ for which the discrete inf-sup condition is fulfilled and we build a projection operator $\pi_L: Q_h \rightarrow L_h$ such that for any $[v, \vd] \in X $
+\subsubsection{Problem 2} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X_{h,0}^1(\Omega)$ and $X_{h,0}^1(\Lambda)$.
+Notice that in this case we assume that the mesh sizes of the 3D mesh $\mathcal{T}^{\Omega}_h$ and the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different, in particular we assume the 1D mesh is finer.
+Concerning the multiplier space, let $\mathcal{G}_h = \{K \in \mathcal{T}^{\Omega}_h: \, K\cap \Lambda \neq \emptyset\}$, namely $\mathcal{G}_h$ is the set of the 3D elements which intersect $\Lambda$.
+Then we define $Q_h=\{{\ld}_h : {\ld}_h \in P^0(K) \, \forall K \in \mathcal{G}_h\}$.
+We notice that we are extending the multiplier to the 3D elements so that we do not need to consider the 1D mesh given by the intersection of the elements of $\mathcal{T}^{\Omega}_h$ with $\mathcal{T}^{\Lambda}_{h'}$.
+With this choice of multipliers the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s({\ld}_h, {\md}_h)$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}.
+The stabilization operator is based on a new multiplier space $L_H$ for which the discrete inf-sup condition is fulfilled and a projection operator $\pi_L: Q_h \rightarrow L_H$ such that for any $[v, \vd] \in X $
 \begin{equation}\label{condition_pi_L}
-b([v, \vd], {\ld}_h - \pi_L {\ld}_h) \lesssim \vertiii{[v,\vd]}\|{\ld}_h - \pi_L {\ld}_h\|_{L_h},
+b([v, \vd], {\ld}_h - \pi_L {\ld}_h) \lesssim \vertiii{[v,\vd]}\|{\ld}_h - \pi_L {\ld}_h\|_{L_H},
 \end{equation}
-where for $X$ and $\vertiii{[\cdot, \cdot]}$ we use the definitions of section $3.2$ and $\|\cdot \|_{L_h}$ denotes a suitable discrete norm on $L_h$. Then, the following lemma holds
+where for $X$ and $\vertiii{[\cdot, \cdot]}$ we use the definitions of section $3.2$ and $\|\cdot \|_{L_H}$ denotes a suitable discrete norm on $L_H$.
+Then, the following relaxed form of the inf-sup condition is satisfied,
 \begin{lemma}\cite[Lemma2.1]{burman2014}
@@
 \begin{equation*}
-\|{\ld}_h\|_{H^{-\frac 12}(\Lambda)} \lesssim \sup_{\substack{v_h \in X_{h,0}^1(\Omega)\\ {\vd}_h \in X_{h,0}^1(\Lambda)}} \frac{b([v_h, {\vd}_h], {\ld}_h)}{\vertiii{[v_h, {\vd}_h]}} + \|{\ld}_h - \pi_L {\ld}_h\|_{L_h}
+\|{\ld}_h\|_{H^{-\frac 12}(\Lambda)} \lesssim \sup_{\substack{v_h \in X_{h,0}^1(\Omega)\\ {\vd}_h \in X_{h,0}^1(\Lambda)}} \frac{b([v_h, {\vd}_h], {\ld}_h)}{\vertiii{[v_h, {\vd}_h]}} + \|{\ld}_h - \pi_L {\ld}_h\|_{L_H}.
 \end{equation*}
@@
  \begin{equation*}
- \|{\ld}_h- \pi_L {\ld}_h\|_{L_h} \lesssim s({\ld}_h, {\ld}_h)
-\end{equation*}  and prove that $\forall [u_h, {\ud}_h]$, there exists $\xi_h([u_h, {\ud}_h]) \in Q_h$ s.t.
+ \|{\ld}_h- \pi_L {\ld}_h\|_{L_H} \lesssim s({\ld}_h, {\ld}_h)
+\end{equation*}  and prove that $\forall [u_h, {\ud}_h]$, there exists a function $\xi_h\in Q_h$ depending on $[u_h, {\ud}_h]$, namely $\xi_h=\xi_h([u_h, {\ud}_h])$, s.t.
 \begin{equation}\label{stab_coercivity}
-a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h([u_h, {\ud}_h])) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) },
+a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) },
 \end{equation}
@@
 \end{equation}
-being $\vertiii{[\cdot \, ,\, \cdot] }_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) }$ a suitable discrete norm. Then, the stabilized problem 
+being $\vertiii{[\cdot \, ,\, \cdot] }_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) }$ a suitable discrete norm.
+Then, the final objective of this section is to prove that the stabilized version of the 3D-1D-1D problem, precisely,
 \begin{multline}\label{eq:prob2_stabilized}
@@
 \end{multline}
-is well posed thanks to the following lemma.
-\begin{lemma}\cite[Lemma2.3]{burman2014}
-Under the previous assumptions, system \eqref{eq:prob2_stabilized} admits a unique solution $\{[u_h, {\ud}_h], {\ld}_h \}$.
-\end{lemma}
-
+is well posed.
+%\begin{lemma}\cite[Lemma2.3]{burman2014}
+%Under the previous assumptions, system \eqref{eq:prob2_stabilized} admits a unique solution $\{[u_h, {\ud}_h], {\ld}_h \}$.
+%\end{lemma}
+In what follows we discuss the definition of the space $L_H$, the projector $\pi_L$ and the stabilization operator such that lemmas 2.1 and 2.3 of \cite{burman2014} can be applied to problem \eqref{eq:prob2_stabilized}.
 We recall that in the case of Problem 2, 
@@
 \end{equation*}
-The construction of the inf-sup stable space $L_h$ is based on macro elements of diameter $H$, where $H$ is sufficiently larger than $h$.
-In particular, we assume that there exists positive constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$, with $c_h$ is sufficiently large.
-The space is constructed assembling the 3D elements of $\mathcal{G}_h$ into macro patches $ \patch $ such that $H \leq |\patch\cap \Lambda|\leq cH$.
-Namely, $\patch=\cup _{i=0}^{M_j} K_i$, where $K_i \in \mathcal{G}_h$ and $M_j$ is uniformly bounded in $j$ by some $M\in \mathbb{N}$ and $H=\min_{j}|\patch\cap \Lambda|$.
+The construction of the inf-sup stable space $L_H$ is based on macro elements of diameter $H$, where $H$ is sufficiently large.
+In particular, we assume that there exists positive constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$.
+The space is constructed assembling the 3D elements of $\mathcal{G}_h$ into macro patches $ \patch $ such that $H \leq |\patch\cap \Lambda|\leq cH$, with $c\geq 1$.
+Let $M_j$ be the number of elements of the patch $\omega_j$, namely, $\patch=\cup _{i=0}^{M_j} K_i$, where $K_i \in \mathcal{G}_h$, $M_j$ is uniformly bounded in $j$ by some $M\in \mathbb{N}$ and $H=\min_{j}|\patch\cap \Lambda|$.
 We assume that the interiors of the patches $\patch$ are  disjoint.
@@
 \begin{equation*}
-L_h=\left\{{\lld }_h: \, {\lld }_h\in P^0(\patch)\, \forall j \right\}.
+L_H=\left\{{\lld }_H: \, {\lld }_H\in P^0(\patch)\, \forall j \right\}.
 \end{equation*}
@@
 Here we are using the classical definition of shape-regularity, see for example \cite{MR2050138}, namely there exist a constant $C>0$ such that for any $\omega_j$, $\frac{\tilde{\rho}_j}{\bar{\rho}_j}\leq C$, being $\tilde{\rho}_j$ the diameter of $\omega_j$ and $\bar{\rho}_j$ the diameter of the largest ball that can be inscribed in $\omega_j$.
-The extended patches $\omega _j$ are built such that they fulfill the conditions meas$(\patch)=\mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda}\cap \omega_j)=O(H)$, where $\Gamma_{\patch\cap \Lambda}$ is the portion of $\Gamma$ with centerline $\patch\cap \Lambda$.
+The extended patches $\omega _j$ are built such that they fulfill the conditions meas$(\patch)=\mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda}\cap \omega_j)=\mathcal{O}(H)$, where $\Gamma_{\patch\cap \Lambda}$ is the portion of $\Gamma$ with centerline $\patch\cap \Lambda$.
 See Figure \ref{fig:gamma_generated} for a representation in the simple case in which $\omega _j$ is composed just by one tetrahedron.
-The latter assumption is required to ensure that the intersection of $\Gamma_{\patch\cap \Lambda}$ and $\omega_j$ is not too small and it will be needed later on to prove the inf-sup stability of the space $L_h$ in Lemma \ref{lemma:Lh_infsup}.
-We equipe the space $L_h$ with the discrete norm
+The latter assumption is required to ensure that the intersection of $\Gamma_{\patch\cap \Lambda}$ and $\omega_j$ is not too small and it will be needed later on to prove the inf-sup stability of the space $L_H$ in Lemma \ref{lemma:Lh_infsup}.
+We introduce the following discrete norms
 \begin{equation*}
-\|\lld \|_{L_h} = \|\lld \|_{-\frac 12, h, \Lambda} = \|h^{\frac 12} \  \lld \|_{L^2(\Lambda)}.
+\|\, \lambda \,\|_{\pm \frac 12, h, \Lambda} = \|h^{\mp\frac 12} \lambda\|_{L^2(\Lambda)},
 \end{equation*}
-As shown in \cite[Section III]{burman2014}, we can always choose $\pi_L$ as the $L_2$ orthogonal projection operator from $\Lambda_h$ to $L_h$ in order to satisfy \eqref{condition_pi_L} and then in practice replace it with any interpolation $\tilde{\pi}_L$ of $\Lambda_h$ in $L_h$.
+recalling that $h$ is the mesh size of $\mathcal{T}^\Omega_{h}$. We equipe the space $X_h(\Omega)\times X_{h'}(\Lambda)$ with the discrete norm
+\begin{equation*}
+\vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_{h'}(\Lambda) }
+= \|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|} + \|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|},
+\end{equation*}
+and the space $L_H$ with the norm 
+\begin{equation*}
+\|{\lld}_H \|_{L_H} = \|{\lld}_H \|_{-\frac 12, h, \Lambda}.
+\end{equation*}
+As shown in \cite[Section III]{burman2014}, we can always choose $\pi_L$ as the $L_2$ orthogonal projection operator from $\Lambda_h$ to $L_H$ in order to satisfy \eqref{condition_pi_L} and then in practice replace it with any interpolation $\tilde{\pi}_L$ of $\Lambda_h$ in $L_H$.
 In particular, we define $\forall \lambda_h \in \Lambda_h$,
 \begin{equation*}
-\tilde{\pi}_L {\ld}_{ _{|\patch}} = N_j^{-1} \sum_{\substack{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset}} {\ld}_{|K_i} \qquad \text{for all $\omega_j$,} 
+\tilde{\pi}_L {\ld}_{ _{|\patch}} = M^{-1} \sum_{\substack{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset}} {\ld}_{|K_i} \qquad \text{for all $\omega_j$,} 
 \end{equation*}
-being $N_j$ the cardinality of the set $\{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset\}$. These choice leads to the following stabilization 
-\begin{equation*}
+being $M$ the cardinality of the set $\{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset\}$. These choices lead to the following stabilization 
+\begin{equation}\label{eq:stab}
 s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
-\end{equation*}
+\end{equation}
 being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{G}_h$.
@@
 \begin{equation}\label{disc_poincare_ineq}
-\|v- \mathcal{E}_{\patch} \pi_L\mtrace v\|_{L^2(\omega_j)} \leq c_P H \|\nabla v\|_{L^2(\omega_j)},
+\|v- \mathcal{E}_{\patch} \pi_L\mtrace v\|_{L^2(\omega_j)} \leq c_P H \|\nabla v\|_{L^2(\omega_j)}.
 \end{equation}
 %where $\pi_L$ is a projection operator onto piecewise constant functions on $\patch\cap \Lambda$. In particular, for any $w \in L^2(\Lambda)$, we define
-where for any $w \in L^1(\Lambda)$, $ \mathcal{E}_{\patch}\pi_Lw \in L_h$ and with a little abuse of notation we denote as $\pi_L$ the operator
-\begin{equation*}
+For any $w \in L^2(\Lambda)$ we have that $ \mathcal{E}_{\patch}\pi_Lw \in L_H$, where with a little abuse of notation we denote as $\pi_L$ the operator
+\begin{equation}\label{eq:projector}
 \pi_Lw_{|\patch \cap \Lambda} =\frac{1}{|\Gamma_{\patch\cap \Lambda}|}\int_{\patch\cap \Lambda}|\DD| w\quad \forall j,
-\end{equation*}   
+\end{equation}   
 whereas the operator $\mathcal{E}_{\patch}$ simply extends the constant $\pi_L\mtrace v_{|\patch \cap \Lambda}$ to $\omega _j$.
 Moreover $\forall u_h \in X^1_{h,0}(\Omega)$ we have the following average inequality 
-\begin{equation*}
-\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| } \leq \sum _j \|\trace  u_h\|^2_{L^2(\omega_j\cap \Gamma)}.
-\end{equation*}
-Indeed, by the definition of $\mtrace$ and Jensen inequality, we have
-\begin{multline*}
+%\begin{equation*}
+%\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| } \leq \sum _j \|\trace  u_h\|^2_{L^2(\omega_j\cap \Gamma)}.
+%\end{equation*}
+which is a consequence of the definition of $\mtrace$ and Jensen inequality,
+\begin{multline}\label{eq:avrg_ineq}
 \sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| }
 = \sum _j\int_{\patch \cap \Lambda} |\DD| \mtrace u_h^2 
+= \int_{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \trace u_h \right)^2
+\leq \int_{\Lambda} \int_{\DD} (\trace u_h)^2
 \\
-= \int_{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \trace u_h \right)^2
-\\
-(\text{Jensen})\leq \int_{\Lambda} \int_{\DD} (\trace u_h)^2
 = \int_{\Gamma} (\trace u_h)^2
-\\
-(\patch \cap \Gamma \text{ partition of } \Gamma)= \sum _j \int_{\patch \cap \Gamma} (\trace u_h)^2
+= \sum _j \int_{\patch \cap \Gamma} (\trace u_h)^2
 = \sum _j \|\trace u_h\|^2_{L^2(\patch \cap \Gamma)}.
-\end{multline*}
-
+\end{multline}
+To prove that \eqref{eq:prob2_stabilized} is well posed, we proceed through three main steps.
+The first step consists of showing that the space $L_H$ is inf-sup stable.
+This result is addressed in the following lemma.
 \begin{lemma}\label{lemma:Lh_infsup}
-The space $L_h$ is inf-sup stable, namely $\forall {\lld}_h \in L_h$, $\exists \beta >0$ s.t.
+The space $L_H$ is inf-sup stable, namely $\forall {\lld}_H \in L_H$, $\exists \beta >0$ s.t.
 \begin{equation*}
-\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\lld} _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|{\lld}_h\|_{H^{-\frac 12}(\Lambda)}.
+\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\lld} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|{\lld}_H\|_{H^{-\frac 12}(\Lambda)}.
 \end{equation*} 
-and the constant is independent of the cuts. 
 \end{lemma}
@@
 \begin{equation*} 
-\sup_{v_h \in X_{h,0}^1(\Omega)} \frac{\left(\mtrace v_h ,{\lld}_h\right)_{\Lambda, |\DD|}}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|{\lld}_h\|_{H^{-\frac 12}(\Lambda)}.
+\sup_{v_h \in X_{h,0}^1(\Omega)} \frac{\left(\mtrace v_h ,{\lld}_H\right)_{\Lambda, |\DD|}}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|{\lld}_H\|_{H^{-\frac 12}(\Lambda)}.
 \end{equation*} 
@@
 \begin{equation*}
-\left(\mtrace v - \mtrace \pi _F v  , {\lld}_h\right)_{\Lambda, |\DD|}=0, \quad \forall v\in H^1_0(\Omega), \, {\lld}_h \in L_h
+\left(\mtrace v - \mtrace \pi _F v  , {\lld}_H\right)_{\Lambda, |\DD|}=0, \quad \forall v\in H^1_0(\Omega), \, {\lld}_H \in L_H
 \end{equation*} 
 and
-\begin{equation*}
+\begin{equation}\label{eq:cont_Fortin}
 \|\pi_F v\|_{H^1(\Omega)}\lesssim \|v\|_{H^1(\Omega)}.
-\end{equation*}
+\end{equation}
 
@@
 \begin{equation}\label{phi_properties}
-\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j=O(H) \text{ and } \|\nabla \varphi _j\|_{L^2(\omega _j)}=O(1). 
+\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j=\mathcal{O}(H) \text{ and } \|\nabla \varphi _j\|_{L^2(\omega _j)}=\mathcal{O}(1). 
 \end{equation}
@@
 \begin{multline*}
-\left(\mtrace v - \mtrace \pi _F v  , {\lld}_h\right)_{\Lambda, |\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD |\left[ \mtrace v-\mtrace I_h v-\sum _i \alpha_i \mtrace \varphi _i \right]{\lld}_h \\
-(\text{supp} (\mtrace \varphi _i )\subset \omega _i\cap \Lambda \, \forall i)  =\sum _j \int_{\patch\cap \Lambda}|\DD| \left[ \mtrace v-\mtrace I_h v-\alpha_j \mtrace \varphi _j \right]{\lld}_h\\
-=\sum _j \int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\lld}_h - \frac{\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi _j} \int_{\patch\cap \Lambda} |\DD|\mtrace \varphi _j{\lld}_h\\
-(\text{using $l_h$ constant on $\patch\cap \Lambda$})=0.
+\left(\mtrace v - \mtrace \pi _F v  , {\lld}_H\right)_{\Lambda, |\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD |\left[ \mtrace v-\mtrace I_h v-\sum _i \alpha_i \mtrace \varphi _i \right]{\lld}_H \\
+(\text{supp} (\mtrace \varphi _i )\subset \omega _i\cap \Lambda \, \forall i)  =\sum _j \int_{\patch\cap \Lambda}|\DD| \left[ \mtrace v-\mtrace I_h v-\alpha_j \mtrace \varphi _j \right]{\lld}_H\\
+=\sum _j \int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\lld}_H - \frac{\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi _j} \int_{\patch\cap \Lambda} |\DD|\mtrace \varphi _j{\lld}_H\\
+(\text{using ${\lld}_H$ constant on $\patch\cap \Lambda$})=0.
 \end{multline*}
@@
 \\
-\left(\text{using }\|\nabla \varphi _j\|_{{L^2(\omega_j)}}=O(1)\right) \lesssim  \sum_j \frac{\left(\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)\right)^2}{\left(\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j \right)^2}
+\left(\text{using }\|\nabla \varphi _j\|_{{L^2(\omega_j)}}=\mathcal{O}(1)\right) \lesssim  \sum_j \frac{\left(\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)\right)^2}{\left(\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j \right)^2}
 \\
@@
 \\
-(\text{average inequality}) \lesssim  \frac {1}{H} \sum_j \| \trace(v-I_h v)\|^2_{L^2(\omega _j\cap \Gamma)}  
+(\text{average inequality \eqref{eq:avrg_ineq}} ) \lesssim  \frac {1}{H} \sum_j \| \trace(v-I_h v)\|^2_{L^2(\omega _j\cap \Gamma)}  
 \\
-\left(\text{trace inequality} \right)\lesssim  \frac {1}{H^2} \sum_j  \| v-I_h v\|^2_{L^2(\omega_j)} \lesssim  \frac {1}{H^2}  \| v-I_h v\|^2_{L^2(\Omega)} 
+\left(\text{trace inequality \eqref{discr_trace_ineq}} \right)\lesssim  \frac {1}{H^2} \sum_j  \| v-I_h v\|^2_{L^2(\omega_j)} \lesssim  \frac {1}{H^2}  \| v-I_h v\|^2_{L^2(\Omega)} 
 \\
@@
 and the continuity of $\pi_F$ follows.
+We notice that the constant in the inequality \eqref{eq:cont_Fortin} is independent of how $\Lambda$  is cut by the elements of the mesh $\mathcal{T}_h^{\Omega}$.
 \end{proof}
@@
 %abstract analysis}
-We choose the following discrete norm
+
+The second step of the stability analysis of the stabilized 3D-1D-1D scheme, namely  \eqref{eq:prob2_stabilized}, consists of showing that \eqref{stab_coercivity} and \eqref{stab_stability} are satisfied.
+In particular, we consider the projection operator defined in \eqref{eq:projector} and the stabilization operator \eqref{eq:stab}.
+Also, the function $\xi_h([u_h, {\ud}_h])$ is defined as follows
 \begin{equation*}
-\vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_{h'}(\Lambda) }
-= \|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|} + \|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|},
+{\xi_h}_{|\patch\cap \Lambda}=\delta \frac 1H \pi_L(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}.
 \end{equation*}
-where $\|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|} = \|h^{-\frac 12} (\mtrace u_h - {\ud}_h)\|^2_{L^2(\Lambda), |\DD|} $. Then, we have the following lemma. 
+Then the following result holds true. 
 \begin{lemma}
-The inequalities \eqref{stab_coercivity} and \eqref{stab_stability} hold.
+The inequalities \eqref{stab_coercivity} and \eqref{stab_stability} are satisfied (under the previous assumptions).
 \end{lemma}
@@
 Concerning the coercivity property \eqref{stab_coercivity}, we have to show that $\forall [u_h, {\ud}_h]$, there esists $\xi_h \in Q_h$ s.t.
-\begin{multline*}
-(u_h,u_h)_{H^1(\Omega)}+ ({\ud}_h, {\ud}_h)_{H^1(\Lambda), |\D|} +   (\mtrace u_h - {\ud}_h, \xi_h)_{\Lambda,|\DD|} \\
-\geq \alpha_{\xi}(\|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|}+ \|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|}.
-\end{multline*}
-We choose 
 \begin{equation*}
-{\xi_h}_{|\patch\cap \Lambda}=\delta \frac 1H \pi_L(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}
+(u_h,u_h)_{H^1(\Omega)}+ ({\ud}_h, {\ud}_h)_{H^1(\Lambda), |\D|} +   (\mtrace u_h - {\ud}_h, \xi_h)_{\Lambda,|\DD|} \geq \alpha_{\xi}\vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_{h'}(\Lambda) }.
 \end{equation*}
-and we recall that 
-\begin{equation*}
-\pi_L(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}=\frac{1}{|\Gamma_{\patch\cap \Lambda}|}\int_{\patch\cap \Lambda}|\DD| (\mtrace u_h- {\ud}_h).
-\end{equation*} 
-Actually, $\mathcal{E}_{\patch}\xi_h\in L_h \subset Q_h$. Then,
+Using the definitions of $\pi_L$ and $\xi_h([u_h, {\ud}_h])$ previously presented and recalling that $\mathcal{E}_{\patch}\xi_h\in L_H \subset Q_h$, we obtain
 \begin{multline*}
@@
 \\
-= \delta \frac{1}{H} \sum_j \int_{\patch\cap \Lambda}|\DD| (\pi_L( \mtrace u_h - {\ud}_h) )^2
+\left(|\Gamma_{\omega_j \cap \Lambda}| = \int_{\omega_j \cap \Lambda}|\DD|\right)= \delta \frac{1}{H} \sum_j \int_{\patch\cap \Lambda}|\DD| (\pi_L( \mtrace u_h - {\ud}_h) )^2
 \\
@@
 \end{multline*}
-For the first term we have
+For the first term, we introduce the uniform extension operator  $\mathcal{E}_{\Gamma}$ from $\omega_j \cap \Lambda$ to the subset of $\Gamma$ with centerline $\omega_j \cap \Lambda$ and we have
 \begin{multline*}
@@
 \\
-(\text{Average inequality)} \leq \sum _j  \int_{\omega _j \cap \Gamma} (\ext \pi_L \mtrace u_h -\trace u_h)^2 
+(\text{Average inequality \eqref{eq:avrg_ineq}}) \leq \sum _j  \int_{\omega _j \cap \Gamma} (\ext \pi_L \mtrace u_h -\trace u_h)^2 
 \\
-(\text{trace inequality}) \leq \sum _j  \frac 1H \int_{\omega_j}(\mathcal{E}_{\patch} \pi_L \mtrace u_h - u_h)^2 
+(\text{trace inequality \eqref{discr_trace_ineq}}) \leq \sum _j  \frac 1H \int_{\omega_j}(\mathcal{E}_{\patch} \pi_L \mtrace u_h - u_h)^2 
 \\ 
@@
 \end{multline*}
-and choosing $\delta=\frac{1}{4c_P^2}$ we obtain the coercivity inequality.\\
+and choosing $\delta=\frac{1}{4c_P^2}$ we obtain the desired inequality.\\
 Concerning the stability inequality \eqref{stab_stability}, the proof is analogous to the one in \cite{burman2014}.
@@
 \begin{multline}
-\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\lld} _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}}
-\geq \sup_{\substack{{\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(- {\vd}_h, {\lld} _h\right)_{\Lambda, |\DD|}}{\|{\vd}_h\|_{H^1(\Lambda)}}
-\geq \frac{{\|\lld} _h\|^2_{L^2(\Lambda)}}{\|{\vd}_h\|_{H^1(\Lambda)}} \\
-( \text{inverse inequality} )\geq \frac{{h'}^2}{c_I} \|{\lld}_h\|_{L^2(\Lambda)}
-\geq  \frac{{h'}^2}{c_I} \|{\lld}_h\|_{H^{-\frac 12},(\Lambda)}
+\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\lld} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}}
+\geq \sup_{\substack{{\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(- {\vd}_h, {\lld} _H\right)_{\Lambda, |\DD|}}{\|{\vd}_h\|_{H^1(\Lambda)}}
+\geq \frac{{\|\lld} _H\|^2_{L^2(\Lambda)}}{\|{\vd}_h\|_{H^1(\Lambda)}} \\
+( \text{inverse inequality} )\geq \frac{{h'}^2}{c_I} \|{\lld}_H\|_{L^2(\Lambda)}
+\geq  \frac{{h'}^2}{c_I} \|{\lld}_H\|_{H^{-\frac 12},(\Lambda)}
 \end{multline}
@@
 \begin{equation*}
-\|{\lld}_h\|_{H^1(\Lambda)} \leq \frac{c_I} {{h'}^2} \|{\lld}_h\|_{L^2(\Lambda)}. 
+\|{\lld}_H\|_{H^1(\Lambda)} \leq \frac{c_I} {{h'}^2} \|{\lld}_H\|_{L^2(\Lambda)}. 
 \end{equation*}

### 2020-01-09 3d1d_coupled_LM.tex
Plots num sol
progress on nonconf results
update
all results in
Paolo's revision sections 2-3

--- 2019-07-05 3d1d_coupled_LM.tex
@@
 \usepackage{stmaryrd}
+\usepackage{tikz, subfigure}
+\usepackage{booktabs}  % for tables
+\usepackage{capt-of}
+\usepackage{multirow}
+\usepackage[displaymath, mathlines]{lineno}
 
+\newcommand{\miro}[1]{{\color{cyan}#1}}
 % Title. If the supplement option is on, then "Supplementary Material"
@@
 \begin{document}
+\linenumbers
 
@@
 \begin{abstract}
-These are personal notes written to keep track of the developments on this topic, to be kept confidential.
+Manuscript in preparation, to be kept confidential.
 \end{abstract}
@@
 \def\ld{\lambda_{\odot}}
+\def\udh{u_{\odot h}}
+\def\vdh{v_{\odot h}}
+\def\ldh{\lambda_{\odot h}}
 \def\md{\mu_{\odot}}
@@
 
-Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set.
-Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Omega_\ominus}$ be the complementary set of the cylinder.
-We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Omega_\ominus$.
-We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$.
-We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Omega_\ominus$ and its boundary, respectively.
-%In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach. 
-We also assume that $\Omega_\ominus$ crosses $\Omega$ from side to side and we call $\Gamma$ the lateral (cylindrical) surface of $\Omega_\ominus$, while the upper and lower side faces of $\Omega_\ominus$ belong to $\partial\Omega$.
-We refer to Figure \ref{fig1} for an illustration of the notation.
+In this section we fist provide the main notation and definitions to set up the problem.
+In particular, we address the geometry of the domain, which is equivalent to the one addressed in previous works of the authors \cite{laurino_m2an},
+and we define the functional spaces and related operators necessary for a rigorous problem formulation and analysis.
+Finally, the section ends with the formal derivation of the problem, 
+based on averaging techniques applied to a fully three-dimensional model in the geometrical setting defined before.
+
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\subsection{Geometry of the problem}
+The domain is denoted as $\Omega$ is convex and composed by two parts, 
+$\Omega_{\ominus}$ and $\Omega_{\oplus}:=\Omega\setminus\overline{\Omega}_{\ominus}$. 
+Let $\Omega_{\ominus}$ be a \emph{generalized cylinder}, 
+that is the swept volume of a two dimensional set moved along a curve in the three-dimensional space, see for example \cite{MR1940257}.
+We also assume that $\Omega_{\ominus}$ crosses $\Omega$ from side to side, and we call $\Gamma$ the lateral surface of $\Omega_{\ominus}$, 
+while the upper and lower faces of $\Omega_{\ominus}$ belong to $\partial\Omega$. 
+Let $\boldsymbol \lambda(s) = [\xi(s), \tau(s), \zeta(s)], \ s\in(0,S)$ be a $\mathcal{C}^2$-regular curve in the three-dimensional space.
+For simplicity, let us assume that $\|\boldsymbol \lambda^\prime(s)\|=1$ such that the arc-length and the coordinate $s$ coincide.
+Let $\Lambda = \{\boldsymbol \lambda(s), \ s\in(0,S)\}$ be the centerline of the cylinder. 
+According to the geometrical setting, we will denote with $v,\,v_\oplus,\,v_\ominus,\,\vd$,
+functions defined on $\Omega,\,\Omega_{\oplus},\,\Omega_{\ominus},\,\Lambda$, respectively.
+We refer to Figure \ref{fig1} for a sketch of the domains.
+
+Let $\TT,\NN,\BB$ be the Frenet frame related to the curve.
+Let $\mathcal{D}(s) = [x(r,t),y(r,t)]: (0,R(s))\times(0,T(s)) \rightarrow \R^2$ be a parametrization of the cross section.
+Let us assume that $\mathcal{D}(s)$ is convex for any $s \in (0,S)$. The cross section can change size along $\Lambda$ but not shape.
+Let us also parametrize the boundary of the cross section as $\partial\mathcal{D}(s) = [\partial x(r,t),\partial y(r,t)]: (0,R(s))\times(0,T(s)) \rightarrow \R^2$,
+and let us assume that $\partial\mathcal{D}(s)$ is a piecewise $\mathcal{C}^2$-regular curve.
+Then, the generalized cylinder $\Omega_{\ominus}$ can be defined as follows
+\begin{equation*}
+\Omega_{\ominus} = \{ \boldsymbol \lambda(s) + x(r,t) \NN(s) + y(r,t) \BB(s), \ r \in (0,R(s)),\ s \in (0,S), \ t \in (0,T(s))\}\,,
+\end{equation*}
+and the lateral boundary is
+\begin{equation*}
+\Gamma = \{ \boldsymbol \lambda(s) + \partial x(r,t) \NN(s) + \partial y(r,t) \BB(s), \ r \in (0,R(s)),\ s \in (0,S), \ t \in (0,T(s))\}\,.
+\end{equation*}
+Let $|\cdot|$ denote the Lebesgue measure of a set. If $|\mathcal{D}(0)|, \ |\mathcal{D}(S)| >0$ then $\Omega_{\ominus}$ has \emph{top} and \emph{bottom} boundaries,
+which belong to $\partial\Omega$.
+
+Thanks to the  geometrical structure of the generalized cylinder, 
+for any sufficiently regular function $w$ we decompose integrals as follows
+and we define the corresponding averages $\avrc{w},\,\avrd{w}$,
+\begin{gather*}
+\int_{\Omega_{\ominus}} w d\omega 
+= \int_\Lambda \int_{\mathcal{D}(s)} w d\sigma ds
+= \int_\Lambda |\mathcal{D}(s)|\avrd{w}(s) ds\,,
+\ \textrm{where} \ \avrd{w}(s) = |\mathcal{D}(s)|^{-1} \int_{\mathcal{D}(s)} w d\sigma\,,
+\\
+\int_{\partial\Omega_{\ominus}} w d\sigma 
+= \int_\Lambda \int_{\partial\mathcal{D}(s)} w d\gamma ds
+= \int_\Lambda  |\partial \mathcal{D}(s)| \avrc{w}(s) ds\,,
+\ \textrm{where} \ \avrc{w}(s) = |\partial\mathcal{D}(s)|^{-1} \int_{\partial\mathcal{D}(s)} w d\gamma\,,
+\end{gather*}
+being $d\omega, \ d\sigma, \ d\gamma$ the generic volume, surface and curvilinear Lebesgue measures.
+Analogously, for functions defined on $\Lambda$ and $\Omega_\ominus$ respectively, 
+we define as $d_s$ and $\partial_s$ the ordinary and partial derivative with respect to the arclength.
+
+This work is based on the assumption that \emph{the transversal diameter of $\Omega_{\ominus}$ is small compared to the diameter of $\Omega$}. 
+Let $d= \max_{s \in (0,S)} \mathrm{diam}(\D(s))$ be the largest diameter of the cross sections of $\Omega_{\ominus}$, that is the transversal diameter of $\Omega_{\ominus}$.
+The central assumption of this work is that $d \ll \mathrm{diam}(\Omega)$.
+Let us now scale the domains $\Omega$ and $\Omega_{\ominus}$.
+Let $\chi_{\Omega}(\xx) = \xx / \mathrm{diam}(\Omega)$ be a scaling function and let be $\Omega_\chi = \chi_{\Omega}(\Omega), \ {\Omega_{\ominus}}_\chi =  \chi_{\Omega}(\Omega_{\ominus})$ be the scaled domains.
+The previous assumption implies that for the scaled domains $\epsilon = d_\chi = d/\mathrm{diam}(\Omega)$
+is such that $0 < \epsilon \ll 1$. For simplicity of notation, and without loss of generality, form now on we will implicitly refer to the scaled domains dropping the subindex $\chi$.
 
@@
 
-We consider the problem arising from \emph{Dirichlet-Neumann} conditions. 
-It consists to find $\up,\uf$ s.t.:
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\subsection{Functional setting and preliminary results}
+
+Let $D$ be a generic regular bounded domain in $\R^3$. 
+Let $X$ be a Hilbert space defined on $D$.
+Let $(\cdot,\cdot)_X$ denote the inner product of $X$.
+Let $(\cdot,\cdot)_L^2(D)$,  $(\cdot,\cdot)_D$ or simply $(\cdot,\cdot)$ be the $L^2(D)$ inner product on $D$.
+For the domain $\Lambda$ we will use the following notation for the weighted inner product,
+\begin{equation*}
+(\ud,\vd)_{\Lambda,w} = \int_0^S w(s) \ud(s) \vd(s) ds\,.
+\end{equation*}
+Given an Hilbert space $X$ and its dual $X^*$, the duality pairing between the two is denoted as $\langle\cdot,\cdot\rangle$.
+When needed, the integration weights will be also applied to the duality product.
+
+We will use the standard notation $H^q(D)$ to denote the Sobolev space of functions on $D$ with all derivatives up to the order $q$ in $L^2(D)$.
+The corresponding norm is $\|\cdot\|_{H^q(D)}$ and the seminorm is $\vert\cdot\vert_{H^q(D)}$.
+The space $H^q_0(D)$ represents the closure in $H^q(D)$ of smooth functions with compact support in $D$.
+
+Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. 
+We denote with $\mathcal{T}: H^q(D) \rightarrow H^{q-\frac12}(\Sigma)$ the trace operator from $D$ to $\Sigma$.
+For the purpose of this work we will extensively use traces on $\Gamma$ of functions defined on $\Omega$. Such operator will be denoted with $\trace$. 
+The operator obtained form the combination of the average operator $\avrc{(\cdot)}$ with the trace on $\Gamma$ will be denoted with $\mtrace = \avrc{(\cdot)} \circ \trace$,
+as it maps functions on $\Omega$ to functions on $\Lambda$.
+
+Fractional Sobolev spaces arising from the application of the trace operator are particularly important in this work.
+For example the trace space on $\Gamma$ of $H^1_0(\Omega)$ will be be extensively used for this study.
+We denote this space as $H^{\frac12}_{00}(\Gamma) = \trace H^1_0(\Omega)$.
+It can be interpreted as the subspace of $H^{\frac12}(\Gamma)$ of functions with continuous extension by zero outside $\Gamma$.
+We remark that $(H^{\frac12}_{00}(D))^* = H^{-\frac12}(D)$ with $D=\Gamma,\Lambda$.
+We will see later that functions belonging to $H^{\frac12}_{00}(\Lambda)$ are generated from the application of $\mtrace$ to $H^1_0(\Omega)$.
+
+In what follows we will also use the uniform extension to $\Omega_{\ominus}$ of functions defined on $\Lambda$.
+Namely, given $\vd(s)$ we define $\mathcal{E}_{\Omega_{\ominus}}$ as $\mathcal{E}_{\Omega_{\ominus}}\vd(s,r,t)=\vd(s)$.
+Then, taking the trace on $\Gamma$ of the extended function we obtain an extension map from $\Lambda$ to $\Gamma$, denoted as $\ext$.
+We observe that $\ext: H^\frac12_0(\Lambda) \rightarrow H^\frac12_{00}(\Gamma)$ satisfies the following property
+\begin{equation}\label{eq:ext}
+\langle \mtrace u, \vd \rangle_{\Lambda, |\DD|} 
+= \int _{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \trace u \, d\gamma \right) \vd \, ds 
+= \langle \trace u, \ext \vd\rangle_{\Gamma}\,,
+\end{equation} 
+which shows that the average and the uniform extension operator commute.
+
+From the theory of interpolation of Sobolev spaces we define the fractional norms $\|\cdot \|_{H^{\frac 12}_{00}(\Gamma)}$ and $\|\cdot \|_{H^{\frac 12}_{00}(\Lambda)}$ as functions of the eigenvalues and eigenfunctions of the Laplacian on $\Gamma$ and $\Lambda$ respectively, see for example \cite{MR0350177,MR2328004}.
+We denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the Laplacian on $\Gamma$ with homogeneous Dirichlet condition at the boundary.
+Then, the norms of $H^{\frac 12}_{00}(\Gamma),\,H^{\frac 12}_{00}(\Lambda)$ and the corresponding dual norms are defined as
+\begin{equation}\label{eq:fracnorm_gamma}
+\|u\|_{H^{\frac 12}_{00}(\Gamma)}=\left(\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2\right)^{\frac 12}
+\ \text{with} \ a_{ij}=\left( u,\phi _{ij} \right)_{\Gamma};
+\quad
+\| v \|_{H^{-\frac 12}(\Gamma)} = \sup_{u\in H^{\frac 12}_{00}(\Gamma)}\frac{\langle u, v \rangle_\Gamma}{\|u\|_{H^{\frac 12}_{00}(\Gamma)}}\,.
+\end{equation}
+Similarly, denoting with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the Laplacian on $\Lambda$ with homogenous Dirichlet boundary conditions, if $u \in H^{\frac 12}(\Lambda)$ we have
+\begin{equation}\label{eq:fracnorm_lambda}
+\|u\|_{H^{\frac 12}_{00}(\Lambda)}=\left(\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|a_i|^2\right)^{\frac 12}
+\ \text{with} \ a_i=\left(u, \phi _i \right)_{\Lambda};
+\quad
+\| v \|_{H^{-\frac 12}(\Lambda)} = \sup_{u\in H^{\frac 12}_{00}(\Lambda)}\frac{\langle u, v \rangle_\Lambda}{\|u\|_{H^{\frac 12}_{00}(\Lambda)}}\,.
+\end{equation}
+We define the equivalent weighted norm in $H^{\frac 12}_{00}(\Lambda)$ in the same way,
+\begin{equation}\label{eq:weightfracnorm}
+\|u\|_{H^{\frac 12}_{00}(\Lambda), |\DD|}=\left(\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|a_i|^2\right)^{\frac 12},
+\ \text{with} a_i=\left(u, \phi _i \right)_{\Lambda, |\DD|};
+\quad
+\| v \|_{H^{-\frac 12}(\Lambda)} = \sup_{u\in H^{\frac 12}_{00}(\Lambda)}\frac{\langle u, v \rangle_{\Lambda, |\DD|}}{\|u\|_{H^{\frac 12}_{00}(\Lambda), |\DD|}}\,.
+\end{equation}
+
+We conclude this section with the analysis of a fundamental property for the problem formulation that we will address.
+It consists in the characterization of the regularity of the operator $\mtrace$.
+More precisely we aim to show that $\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$.
+This is a consequence of the following lemma.
+
+\input{preliminary_results.tex}
+
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\subsection{Problem formulation}
+We consider the problem arising from \emph{Dirichlet-Neumann} conditions. Find $\up,\uf$ s.t.:
 \begin{subequations}\label{eq:dirneu}
@@
 
-The objective of this work is to derive and alalyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Omega_\ominus$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$.
-This new problem setting will be called the \emph{reduced} problem.
-Form the mathematical standpoint it is more challenging than \eqref{eq:dirneu}, because it involves the coupling of 3D/1D elliptic problems.
-For the model reduction process, we decompose integrals as follows, for any sufficiently regular function $w$,
-\begin{equation*}
-\int_{\Omega_\ominus} w d\omega 
-= \int_\Lambda \int_{\mathcal{D}} w d\sigma ds
-= \int_\Lambda |\mathcal{D}|\avrd{w} ds\,,
-\quad
-\int_{\Gamma} w d\sigma 
-= \int_\Lambda \int_{\partial\mathcal{D}} w d\gamma ds
-= \int_\Lambda  |\partial \mathcal{D}| \avrc{w} ds\,,
-\end{equation*}
-where $\avrd{w}, \ \avrc{w}$ denote the following mean values respectively,
-\begin{equation*}
-\avrd{w} = |\mathcal{D}|^{-1} \int_{\mathcal{D}} w d\sigma\,,
-\quad
-\avrc{w} = |\partial\mathcal{D}|^{-1} \int_{\partial\mathcal{D}} w d\gamma\,.
-\end{equation*}
+We observe that the coupling constraints defined on $\Gamma$ involve \emph{essential}-type conditions.
+To address such conditions at the level of the variational formulation, we adopt the method of Lagrange multipliers,
+which has been widely used for this purpose since the origin of the finite element method, \cite{MR359352}.
+We remark that this case is substantially different from the one previously addressed in \cite{laurino_m2an}.
 
-We apply the model reduction approach at the level of the variational formulation.
-We start from the variational formulation of problem \eqref{eq:dirneu}, 
-that is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus), \ \lambda \in H^{-\frac12}(\partial\Omega_\ominus)$ s.t.
+The variational formulation of problem \eqref{eq:dirneu}
+is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus), \ \lambda \in H^{-\frac12}(\partial\Omega_\ominus)$ s.t.
 \begin{subequations}\label{eq:weak_dirneu}
@@
 &(u_\oplus,v_\oplus)_{H^1(\Omega_\oplus)} + (u_\ominus,v_\ominus)_{H^1(\Omega_\ominus)} 
-+ \langle  v_\oplus - v_\ominus, \lambda \rangle_{H^{-\frac12}(\Gamma)} 
++ \langle  v_\oplus - v_\ominus, \lambda \rangle_{\Gamma} 
 \\
@@
 \\
-& \langle u_\oplus - u_\ominus, \mu \rangle_{H^{-\frac12}(\Gamma)} = 0
+& \langle u_\oplus - u_\ominus, \mu \rangle_{\Gamma} = 0
 \quad \forall  \mu \in H^{-\frac12}(\Gamma)\,,
@@
 \end{subequations}
-where $\langle v, \mu \rangle_{H^{-\frac12}(\Gamma)}$ denotes the duality pairing between 
-$ \mu \in H^{-\frac12}(\Gamma)$ and $v \in H^{\frac12}(\Gamma)$.
-In this case, the additional variable $\lambda$ is equivalent to $\lambda  =  \nabla \uf \cdot \nn_\ominus$.
+%where $\langle v, \mu \rangle_{H^{-\frac12}(\Gamma)}$ denotes the duality pairing between 
+%$ \mu \in H^{-\frac12}(\Gamma)$ and $v \in H^{\frac12}(\Gamma)$.
+In this case, $\lambda$ is the Lagrange multiplier and it is equivalent to $\nabla \uf \cdot \nn_\ominus$.
 
-Using the averaging tools for the model reduction approach, we end up with two different formulations of a reduced problem
-for the unknown $u$ defined on the entire 3D domain $\Omega$, coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$
-and a Lagrange multiplier defined either on $\Gamma$ (problem 1) or on $\Lambda$ (problem 2). 
-%In the reduced problem the multiplier assumes the following interpretation,
-%\begin{equation*}
-%L = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \nabla \uf \cdot \nn_\ominus
-%   = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \lambda \,.
-%\end{equation*}
+The objective of this work is to derive and analyze a simplified version of problem \eqref{eq:weak_dirneu}, where the domain $\Omega_\ominus$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$.
+This new problem setting will be called the \emph{reduced} problem.
+Form the mathematical standpoint it is more challenging than \eqref{eq:weak_dirneu}, because it involves the coupling of 3D/1D elliptic problems.
+We end up with two different formulations of a reduced problem for the unknown $u$ defined on the entire 3D domain $\Omega$, 
+coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$ and a Lagrange multiplier defined either on $\Gamma$ (problem 1) or on $\Lambda$ (problem 2). 
+The scope of this work is to analyze and compare the two alternatives,
+with the aim to determine which is the most suitable to set up a computational model for 3D-1D PDEs coupled with Dirichlet-Neumann constraint.
 
-%We consider two alternative formulations.
-The scope of this work is to compare them, 
-with the aim to determine which is the most suitable as a computational model based on 3D-1D coupled PDEs.
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 \subsection{Topological model reduction}
@@
 \end{equation}
-where we have introduced the following weighted inner product notation,
-\begin{equation*}
-(\ud,\vd)_{\Lambda,w} = \int_0^S w(s) \ud(s) \vd(s) ds\,.
-\end{equation*}
 Let us now formulate the modelling assumption that allows us to reduce equation \eqref{eq:averaged_f_weak} to a solvable one-dimensional (1D) model.
-More precisely, we assume that:
-\begin{description}
-\item[A1] the function $\uf$ has a \emph{uniform profile} on each cross section $\mathcal{D}(s)$, namely $\uf(r,s,t) = \ud(s)$.
-\end{description}
-Therefore, observing that $\ud=\avrc{u}_{\ominus}=\avrd{u}_{\ominus}$, problem \eqref{eq:averaged_f_weak} consists to find $\ud \in H^1(\Lambda)$ such that
+More precisely, we assume that the function $\uf$ has a \emph{uniform profile} on each cross section $\mathcal{D}(s)$, namely $\uf(r,s,t) = \ud(s)$.
+Therefore, observing that $\ud=\avrc{u}_{\ominus}=\avrd{u}_{\ominus}$, problem \eqref{eq:averaged_f_weak} turns out to find $\ud \in H^1(\Lambda)$ such that
 \begin{equation}\label{eq:1Ddirneu_weak}
- (d_s \ud, d_s \ud)_{\Lambda,|\mathcal{D}|} 
+ (d_s \ud, d_s \vd)_{\Lambda,|\mathcal{D}|} 
 +(\ud, \vd)_{\Lambda, |\D|}
@@
 \end{equation*} 
-Then, we make the following modelling assumptions:
-\begin{description}
-\item[A2] we identify the domain $\Omega_{\oplus}$ with the entire $\Omega$, 
+Then, we make the following modelling assumption:
+we identify the domain $\Omega_{\oplus}$ with the entire $\Omega$, 
 and we correspondingly omit the subscript $\oplus$ to the functions defined on $\Omega_{\oplus}$,
@@
 \end{equation*}
-\end{description}
 Therefore, we obtain 
@@
 
-\subsubsection*{Problem 1 (3D-1D-3D)}
-Let $\langle \cdot , \cdot \rangle_\Gamma$ denote the duality pairing between 
-$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$. The problem consists to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac12}(\Gamma )$, such that
+\subsubsection*{Problem 1 (3D-2D-1D)}
+Find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac12}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
 \begin{subequations}\label{eq:problem1}
@@
 &(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
-+ \langle T v  - \mathcal{U}_E \vd, \lambda \rangle_\Gamma
++ \langle \trace v  - \ext \vd, \lambda \rangle_\Gamma &&
 \\
 \nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
+&\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
+\quad &&\forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)\,,
 \\
-&   \langle T u - \mathcal{U}_E \ud , \mu \rangle_\Gamma = 0
-\quad \forall \mu \in H^{-\frac12}(\Gamma)\,.
+& \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0
+\quad && \forall \mu \in H^{-\frac12}(\Gamma)\,.
 \end{align}
 \end{subequations}
-Here, $T:H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ denotes the trace operator on $\Gamma$ and $\mathcal{U}_E: H^1_0(\Lambda) \rightarrow H^1_{0}(\Gamma)$ denotes the uniform extension from $\Lambda$ to $\Gamma$.
-The idea is then to couple a 3D PDE with a 1D one, using a Lagrange multiplier space defined on a 2D surface that surrounds the 1D manifold.\\
-
-%Here, $\Pi_1: H^1_0(\Omega) \rightarrow H^{\frac12}_{00}(\Gamma)$
-%and $\Pi_2: H^1_0(\Lambda) \rightarrow H^{\frac12}_{00}(\Gamma)$
-%and we remark that $\Sigma$ may be considered as a virtual surface
-%not necessarily of the same size as the underlying physical structure that is modeled.  
-%The $\Pi_1$ and $\Pi_2$ operators may be defined in terms of the averaging operators above, but may also be realized in terms of e.g.
-Green functions (I don't know if this is a good idea).
-Furthermore,  $\Gamma$ may be discretized in terms of facets neighboring $\Lambda$ and may as such not be represented as a separate structure in the implementation.
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-Now, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-3D to a 3D-1D-1D formulation. 
-To this purpose, let us write the lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
+This coupled problem is classifies as 3D-2D-1D because the unknowns $u,\lambda,\ud$ belong to 
+$\Omega \subset \R^3,\, \Gamma \subset \R^2,\, \Lambda \subset \R$, respectively.
+Then, we apply a topological model reduction of the interface conditions, namely we go from a 3D-2D-1D formulation
+involving sub-problems on $\Omega$ and $\Lambda$ and coupling operators defined on $\Gamma$
+to a 3D-1D-1D formulation where the coupling terms are set on $\Lambda$. 
+To this purpose, let us write the Lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
 \begin{equation*}
@@
 
-Then, we make the following modelling assumptions:
-\begin{description}
-\item[A3] we assume that the product of fluctuations is small, namely
+Thanks to the additional assumption that the product of fluctuations is small, namely
 \begin{equation*}
@@
 \end{equation*}
-\end{description}
-and we obtain 
-\begin{equation*}
-(\nabla u ,\nabla v)_{\Omega} +(u,v)_{\Omega}+(\avrc \lambda, \avrc v)_{\Lambda , |\DD|}  =(f,v)_{\Omega},
-\end{equation*}
-which, combined with \eqref{eq:1Ddirneu_weak} leads to the second formulation of the reduced problem.
+the term $\left(\trace v, \lambda \right)_{\Gamma}$ becomes $\left( \mtrace v, \avrc{\lambda} \right)_{\Lambda, |\DD|}$, where $\mtrace$ denotes the composition of operators $\trace \circ \avrc{(\cdot)}$.
+Combined with \eqref{eq:1Ddirneu_weak}, this leads to the second formulation of the reduced problem.
 
-\subsection{Problem 2 (3D-1D-1D)}
-Let $\langle \cdot , \cdot \rangle_\Lambda$ denote the duality pairing between 
-$H^\frac12_{00}(\Lambda)$ and $H^{-\frac12}(\Lambda)$.
-The problem requires to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
+\subsubsection*{Problem 2 (3D-1D-1D)}
+Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
 \begin{subequations}\label{eq:problem2}
@@
 &(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
-+  \langle \avrc{T v} - \vd, \ld \rangle_{H^{-\frac12}(\Lambda), |\DD|} 
++  \langle \mtrace v - \vd, \ld \rangle_{\Lambda, |\DD|} &&
 \\
@@
 &\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
+\quad && \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)\,,
 \\
-&   \langle \avrc{T u} -   \ud, \md \rangle_{H^{-\frac12}(\Lambda),|\DD|} = 0
-\quad \forall \md \in H^{-\frac12}(\Lambda)\,.
+& \langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} = 0
+\quad &&\forall \md \in H^{-\frac12}(\Lambda)\,,
 \end{align}
 \end{subequations}
-We notice that all the integrals of the reduced problem are well defined because $u,v \in H^1_0(\Omega)$, 
-$Tu, \ Tv \in H^\frac12_{00}(\Gamma)$ and thus $\avrc{Tu},\avrc{Tv} \in H^\frac12_{00}(\Lambda)$, as shown in the following lemma.
-%More precisely, $\Pi_1 : H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda$ such that
-%$\Pi_1 u = \avrc{(u|_\Gamma)}$ is the combination between the trace on $\Gamma$ and the average on $\partial{\cal D}$.
-%The operator $\Pi_2: H^1_0(\Lambda) \rightarrow H^\frac12_{00}(\Lambda)$ is the injection form $H^1_0(\Lambda)$ and $H^\frac12_{00}(\Lambda)$.
+We notice that all the integrals of the reduced problem are well defined because 
+$\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$ as shown in Corollary \ref{corollary:H12norm}.
 
-\begin{lemma}\label{lemma:H12norm}
-{\color{red}TO DO: generalize to not uniform $\DD$} 
-When $\Gamma$ is a cylinder, if $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}\in H_{00}^{\frac 12}(\Lambda)$.
-Moreover, if $u\in H^{\frac 12}_{00}(\Gamma)$ is constant on each cross section, namely $u(s,\theta)=u(s)$, then
-\begin{equation*}
-\|u\|_{H^{\frac 12}_{00}(\Gamma)}=2\pi R \|u\|_{H^{\frac 12}_{00}(\Lambda)}.
-\end{equation*}
-\end{lemma}
-\begin{proof}
-Let us denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the laplacian on $\Gamma$, and with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $\Lambda$.
-In particular,
-\begin{align*}
-\phi _{ij}(s,\theta)=sin (i\pi s)\left( cos(j\theta)+ sin(j\theta) \right),\\
-\rho_{ij}=i\pi ^2+\frac{j^2}{R^2},\\
-\phi _{i}(s)=sin (i\pi s),\\
-\rho _i = i\pi ^2.
-\end{align*}
-It is easy to verify that 
-\begin{eqnarray}
-\label{null_int_eigenf}
-\int_0^{2\pi} \phi _{ij}(s,\theta)=0 \quad \forall j>0, \forall i \\
-\label{nonull_int_eigenf}
-\int_0^{2\pi} \phi _{ij}(s,\theta)= 2\pi R \, \sin(i \pi s) \quad \mbox{if } j=0, \forall i  .\\
-\end{eqnarray}
-Moreover we recall that $\phi_{i,j}(s,\theta)$ and $\phi _i(s)$ are orthogonal basis of $L^2(\Gamma)$ and $L^2(\Lambda)$ respectively. Therefore,
-\begin{multline*}
-\avrc{u}(s)=\frac{1}{2\pi R}\int_0^{2\pi} u(s,\theta)R\, d\theta
-= \frac{1}{2\pi R}\int_0^{2\pi} \sum_{i,j} a_{i,j} \phi_{i,j}(s,\theta) R\, d\theta
-\\= \frac{1}{2\pi R}\sum_{i,j} a_{i,j}\int_0^{2\pi}  \phi_{i,j}(s,\theta) R\, d\theta
-=  \sum_{i} a_{i,0} \phi_{i}(s).
-\end{multline*}
-From \cite[Lemma 4.11]{chandler2015interpolation} we have
-\begin{equation}\label{H12norm_Gamma}
-\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2,
-\text{ with }
-a_{ij}=\int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds.
-\end{equation}
-and 
-\begin{equation*}
-\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
-\text{ with }
-\avrc{a}_i=\int _0^1 \avrc{u}(s )\phi_{i}(s) ds.
-\end{equation*}
-
-Therefore, we have
-\begin{multline*}
-\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=
-\sum_{i=1}^{\infty}\left( 1+ i^2\pi^2\right)^{\frac 12}\left( \int_0^1 \avrc{u}(s) sin(i\pi s)\, ds \right)^2\\
-= \sum_{i=1}^{\infty} \left( 1+ i^2\pi^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^1 \sin(j\pi s) \sin(i\pi s) \, ds  \right)^2\\
-= \sum_{i=1}^{\infty} \frac 14 \left( 1+ i^2\pi^2\right)^{\frac 12}a_{i,0}^2\\
-\leq \sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ i^2\pi^2 + \frac{j^2}{R^2}\right)^{\frac 12} |a_{i,j}|^2 =\|u\|^2_{H^{\frac 12}(\Gamma)},
-\end{multline*}
-
-where we have used the fact that
-\begin{eqnarray*}
-&\int_0^1 \sin(i\pi s) \sin(j\pi s)\, ds=0 \quad \text{if $i\neq j$}\\
-&\int_0^1 \sin(i\pi s) \sin(j\pi s)\, ds=\frac 12 \quad \text{if $i =j$}.
-\end{eqnarray*}
-Moreover, in the case in which $u$ is constant on each cross section, from \eqref{H12norm_Gamma} we have
-\begin{multline*}
-\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2
-=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ i\pi ^2+\frac{j^2}{R^2}\right)^{\frac 12}\left( \int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds \right)^2\\
-=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ i\pi ^2+\frac{j^2}{R^2}\right)^{\frac 12}\left( \int _0^1 u(s) \int _0^{2\pi} \phi_{ij}\, R d\theta ds \right)^2,
-\end{multline*}
-and using \eqref{null_int_eigenf} and \eqref{nonull_int_eigenf}, we obtain
-\begin{multline*}
-\|u\|^2_{H^{\frac 12}(\Gamma)}=
-\sum_{i=1}^{\infty}\left( 1+ i\pi ^2\right)^{\frac 12}\left(\int _0^1 u(s )sin (i\pi s) 2\pi R ds\right)^2\\
-=4\pi ^2 R^2 \sum_{i=1}^{\infty}\left( 1+ \rho _i\right)^{\frac 12}|a_i|^2 = 4\pi ^2 R^2  \|u\|^2_{H^{\frac 12}(\Lambda)}.
-\end{multline*}
-\hspace*{0.9\textwidth} c.v.d.
-\end{proof}
-
-\begin{remark}
-The results of \eqref{lemma:H12norm}  can be generalized to the case of a  different geometry of $\Gamma$, for example a parallelepiped.  
-\end{remark}
-
-It is apparent that problems \eqref{eq:weak_dirneu} and \eqref{eq:red_dirneu} share the same mathematical structure.
-For this reason, the well-posedness of \eqref{eq:red_dirneu} can be studied in the framework of the classical theory of saddle point problems.
-
-%Assuming now that 
-%$\Pi_1: H^1(\Omega) \rightarrow H^{\frac12}(\Gamma)$ or $\Pi_2: H^1(\Gamma) \rightarrow H^{\frac12}(\Gamma)$ are isomorphisms in the sense that 
-%\[
-%\| \Pi_1 \|_{L(H^1(\Omega), H^{\frac12}(\Gamma))} \le C \mbox{, } 
-%\| \Pi_1^{-1} \|_{L(H^{\frac12}(\Gamma), H^1(\Omega))} \le 1/c,  
-%\]
-%and 
-%\[
-%\| \Pi_2 \|_{L(H^1(\Omega), H^{\frac12}(\Gamma))} \le C \mbox{, } 
-%\| \Pi_2^{-1} \|_{L(H^{\frac12}(\Gamma), H^1(\Omega))} \le 1/c .   
-%\]
-%We obtain the inf-sup condition as follows. Assume that $\Pi_1$ is an isomorphism then  
-%we may show the inf-sup conditioning by letting $\Pi_1 \hat u = M $ and $ \hat \ud = 0$ (i.e., we need the lower bound only for one
-%of the operators).  
-%\begin{eqnarray}
-%\sup_{u,\ud}\frac{
-%\langle \Pi_1 u - \Pi_2 \ud , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
-%}{(|u|_1^2 + |\ud|_1^2)^{1/2}} 
-%\ge \\ 
-%\frac{ \langle \Pi_1 \hat u - \Pi_2 \hat \ud , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
-%}{(|\hat u|_1^2 + |\hat \ud|_1^2)^{1/2}}  \ge \\
-%\frac{ \langle M , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
-%}{|\Pi_1^{-1} M |_{H^1(\Omega})} \ge \\ 
-%\frac{ \langle M , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
-%}{| M |_{H^\frac12(\Gamma)}} \ge \\ 
-%c | M |_{H^{-\frac12}(\Gamma)}  
-%\end{eqnarray}
-%I think the other Brezzi conditions also follows, but for the boundedness we
-%would need that both $\Pi_1$ and $\Pi_2$ are bounded. Not sure I am 
-%happy with the $\langle \cdot, \cdot \rangle$ notation and in particular not when we spesify the
-%spaces. I would rather just say that $(\cdot, \cdot)$ denotes both the $L_2$ inner product and the
-%duality pairing.  
-%If we find it useful we may also  
-%consider $\Pi_2: H^1(\Gamma) \rightarrow X(\Gamma)$ where $X$ may e.g. be $H^1$.  
-%If so, $L, M$ in $ H^{-\frac12}(\Gamma) \cap X(\Gamma)$
+The well-posedness of $\eqref{eq:problem1}$ and $\eqref{eq:problem2}$ 
+can be studied in the framework of the classical theory of saddle point problems as shown in the following.
 
@@
 \bibliography{3d1d_coupled}
+
+\appendix
+\input{appendix}
 \end{document}

### 2020-01-09 lm3d1d_vs1/infsup_discrete.tex
Paolo's revision sections 2-3

--- 2019-04-03 infsup_discrete.tex
@@
 being $W_h(\Gamma)$ the trace space of the functions in $X_h(\Omega)$, namely the space of the restrictions of the functions in $X_h(\Omega)$ to $\Gamma$. 
-Using the boundedness of the extension operator $E$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
+Using the boundedness of the extension operator $E$ from $H^{\frac 12}_0(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
 \begin{equation*}
@@
 \end{equation*}
-Consequently, using again the extension operator $E$ from $H^{\frac 12}(\Omega)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_h(\Omega)$, we obtain
+Consequently, using again the extension operator $E$ from $H^{\frac 12}_0(\Omega)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_h(\Omega)$, we obtain
 \begin{multline}
@@
 \nonumber
-&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + |{\cal D}(\avrd{g},{\vd}_h)_{L^2(\Lambda)}
+&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + |{\cal D}|(\avrd{g},{\vd}_h)_{L^2(\Lambda)}
 \quad \forall v_h \in X_{h,k}^0(\Omega), \ {\vd}_h \in X_{h,k}^0(\Lambda)
@@
 \begin{lemma}
-Let $P_h: H^{\frac 12}_{00} \longrightarrow W_{h,k}^0(\Gamma)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Gamma)$ by
+Let $P_h: H^{\frac 12}_{00}(\Gamma) \longrightarrow W_{h,k}^0(\Gamma)$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Gamma)$ by
 \begin{equation*}
@@
 \begin{proof}
-Let $M_h$ be in $W_{h,k}^0(\Gamma)$. From the continuous case, in particular from \eqref{inf_sup_traceop}, we have
+Let $M_h$ be in $W_{h,k}^0(\Gamma)$. From the continuous case, in particular from \eqref{infsup_traceop}, we have
 \begin{equation*}
@@
 \end{equation*}
-and by the trace inequality $\|T_{\Gamma}v\|_{H^\frac 12 (\Gamma)} \leq K_1 \|v\|_{H^1_0(\Omega)}$ (see \cite[7.56]{adams1975pure}), we obtain 
+and by the trace inequality $\|T_{\Gamma}v\|_{H^\frac 12 (\Gamma)} \leq K_1 \|v\|_{H^1(\Omega)}$ (see \cite[7.56]{adams1975pure}), we obtain 
 \begin{equation*}
@@
 It coincides with the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$ and satisfying homogeneous Dirichlet boundary condition.
+{\color{red} (Add assumptions..)}
 We choose $Q_h(\Lambda)=W_{h,k}^0(\Lambda)$, therefore we impose homogeneous Dirichlet boundary condition on $\Lambda \cap \partial \Omega$ also for the Lagrange multiplier.

### 2020-01-09 lm3d1d_vs2/3d1d_coupled_LM.tex
Paolo's revision sections 2-3

% SIAM Article Template
\documentclass[r]{siamart171218}
% Packages and macros go here
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{array}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{float}
\usepackage{fullpage}
\usepackage{color}
\usepackage{enumitem}  
\usepackage{epstopdf}
\usepackage{stmaryrd}
\usepackage{tikz, subfigure}

% Title. If the supplement option is on, then "Supplementary Material"
% is automatically inserted before the title.
%\title{On the weak coupling of 3D and 1D second order elliptic problems}
\title{Coupling PDEs on 3D-1D domains with Lagrange multipliers}

% Authors: full names plus addresses.
\author{Miroslav Kuchta, Federica Laurino, Kent-Andre Mardal, Paolo Zunino,\thanks{Authors are listed in alphabetical order}}

\begin{document}

\maketitle

% REQUIRED
\begin{abstract}
These are personal notes written to keep track of the developments on this topic, to be kept confidential.
\end{abstract}

% REQUIRED
\begin{keywords}
elliptic problems, high dimensionality gap, essential coupling conditions, Lagrange multipliers
\end{keywords}

% REQUIRED
\begin{AMS}
n.a.
\end{AMS}

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>

% definitions here

\def\ud{u_{\odot}}
\def\vd{v_{\odot}}
\def\ld{\lambda_{\odot}}
\def\md{\mu_{\odot}}
\def\lld{l_{\odot}}
\def\uf{u_{\ominus}}
\def\up{u_{\oplus}}
\def\eps{\epsilon}
\def\nn{\boldsymbol n}
\def\rr{\boldsymbol r}
\def\RR{\boldsymbol R}
\def\kk{\boldsymbol k}
\def\ss{\boldsymbol s}
\def\uu{\boldsymbol u}
\def\vv{\boldsymbol v}
\def\xx{\boldsymbol x}
\def\bu{\overline{u}}
\def\bv{\overline{v}}
\def\tu{\widetilde{u}}
\def\tv{\widetilde{v}}
\def\TT{\boldsymbol T}
\def\NN{\boldsymbol N}
\def\BB{\boldsymbol B}
\def\ttu{\widetilde{\widetilde{u}}}
\def\ttv{\widetilde{\widetilde{v}}}
\def\cv{\check{v}}
\def\mesh{{\cal T}^h}
\def\ball{{\cal B}}
\def\R{\mathbb{R}}
\def\D{\mathcal{D}}
\def\DD{\partial\mathcal{D}}
\def\trace{{\mathcal{T}_\Gamma}}
\def\mtrace{{\overline{\mathcal{T}}_\Lambda}}
\def\ext{\mathcal{E}_\Gamma}
\def\ide{\mathcal{I}}
\def\ii{\hat{\imath}}
\newcommand{\avrd}[1]{\overline{\overline{#1}}}
\newcommand{\avrc}[1]{\overline{#1}}
\newcommand{\refe}[1]{{#1}_{\mathrm{ref}}}

\newcommand{\vertiii}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 
    \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}{Property}[section]
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\section{Introduction}\label{sec:intro}

We address the geometrical configuration of the problem for a 3D coupled problem formulation based on from Dirichlet-Neumann interface conditions. Then, we apply a model reduction technique that transforms the problem into 3D-1D coupled PDEs. We develop and analyze a robust definition of the coupling operators form a 3D domain, $\Omega$, to 1D manifold, $\Lambda$, and vice versa. This is a non trivial objective because the standard trace operator form a domain $\Omega$ to a subset $\Lambda$ is not well posed if $\Lambda$ is a manifold of co-dimension two of $\Omega$.

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\section{Problem setting}\label{sec:setting}

Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set. Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Omega}_\ominus$ be the complementary set of the cylinder. We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Omega_\ominus$. We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$. We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Omega_\ominus$ and its boundary, respectively. 
%In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach. 
We also assume that $\Omega_\ominus$ crosses $\Omega$ from side to side and we call $\Gamma$ the lateral (cylindrical) surface of $\Omega_\ominus$, while the upper and lower side faces of $\Omega_\ominus$ belong to $\partial\Omega$. We refer to Figure \ref{fig1} for an illustration of the notation.

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{3D-1D-simple.png}
\end{center}
\caption{Geometrical setting of the problem}
\label{fig1}
\end{figure}

We consider the problem arising from \emph{Dirichlet-Neumann} conditions. 
It consists to find $\up,\uf$ s.t.:
\begin{subequations}\label{eq:dirneu}
\begin{align}
\label{eq:dirneu1}
- \Delta \up  + \up &= f  && \text{ in } \Omega_{\oplus},\\
\label{eq:dirneu2}
- \Delta \uf  + \uf &= g  && \text{ in } \Omega_\ominus,\\
\label{eq:dirneu3}
-\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
\label{eq:dirneu4}
\uf &= \up && \text{ on }  \Gamma,\\
\label{eq:dirneu5}
\up &= 0 && \text{ on } \partial \Omega\,.
\end{align}
\end{subequations}

The objective of this work is to derive and analyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Omega_\ominus$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$. This new problem setting will be called the \emph{reduced} problem. Form the mathematical standpoint it is more challenging than \eqref{eq:dirneu}, because it involves the coupling of 3D/1D elliptic problems.
For the model reduction process, we decompose integrals as follows, for any sufficiently regular function $w$,
\begin{equation*}
\int_{\Omega_\ominus} w d\omega 
= \int_\Lambda \int_{\mathcal{D}} w d\sigma ds
= \int_\Lambda |\mathcal{D}|\avrd{w} ds\,,
\quad
\int_{\Gamma} w d\sigma 
= \int_\Lambda \int_{\partial\mathcal{D}} w d\gamma ds
= \int_\Lambda  |\partial \mathcal{D}| \avrc{w} ds\,,
\end{equation*}
where $\avrd{w}, \ \avrc{w}$ denote the following mean values respectively,
\begin{equation*}
\avrd{w} = |\mathcal{D}|^{-1} \int_{\mathcal{D}} w d\sigma\,,
\quad
\avrc{w} = |\partial\mathcal{D}|^{-1} \int_{\partial\mathcal{D}} w d\gamma\,.
\end{equation*}

We apply the model reduction approach at the level of the variational formulation.
We start from the variational formulation of problem \eqref{eq:dirneu}, 
that is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus), \ \lambda \in H^{-\frac12}(\partial\Omega_\ominus)$ s.t.
\begin{subequations}\label{eq:weak_dirneu}
\begin{align}
&(u_\oplus,v_\oplus)_{H^1(\Omega_\oplus)} + (u_\ominus,v_\ominus)_{H^1(\Omega_\ominus)} 
+ \langle  v_\oplus - v_\ominus, \lambda \rangle_{H^{-\frac12}(\Gamma)} 
\\
\nonumber
&\qquad\qquad = (f,v_\oplus)_{L^2(\Omega_\oplus)} + (g,v_\ominus)_{L^2(\Omega_\ominus)}
\quad \forall v_\oplus \in H^1_{\partial\Omega}(\Omega_\oplus), \ v_\ominus \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus)
\\
& \langle u_\oplus - u_\ominus, \mu \rangle_{H^{-\frac12}(\Gamma)} = 0
\quad \forall  \mu \in H^{-\frac12}(\Gamma)\,,
\end{align}
\end{subequations}
where $\langle v, \mu \rangle_{H^{-\frac12}(\Gamma)}$ denotes the duality pairing between 
$ \mu \in H^{-\frac12}(\Gamma)$ and $v \in H^{\frac12}(\Gamma)$.
In this case, the additional variable $\lambda$ is equivalent to $\lambda  =  \nabla \uf \cdot \nn_\ominus$.

Using a model reduction approach based on averaging, we end up with two different formulations of a reduced problem
for the unknown $u$ defined on the entire 3D domain $\Omega$, coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$
and a Lagrange multiplier defined either on $\Gamma$ (problem 1) or on $\Lambda$ (problem 2). 
The scope of this work is to compare them, with the aim to determine which is the most suitable to set up a computational model for 3D-1D coupled PDEs.

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\subsection{Topological model reduction}
\subsubsection*{Model reduction of the problem on $\Omega_{\ominus}$}

We apply the averaging technique to equation \eqref{eq:dirneu2}. In particular, we consider an arbitrary portion $\mathcal{P}$ of the cylinder $\Omega_\ominus$, with lateral surface $\Gamma _{\mathcal{P}}$ and bounded by two perpendicular sections to $\Lambda$, namely $\mathcal{D}(s_1), \ \mathcal{D}(s_2)$ with $s_1<s_2$. We have,
\begin{multline*}
\int_{\mathcal{P}} -\Delta \uf + \uf d\omega =
-\int_{\partial \mathcal{P}} \nabla \uf \cdot \nn_{\ominus} \, d\sigma  + \int_{\mathcal{P}}\uf d\omega=
\\
 \int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma -  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma -  \int_{\Gamma_{\mathcal{P}}} \nabla \uf \cdot \nn_{\ominus} d\sigma +\int_{\mathcal{P}}\uf d\omega
\end{multline*}
By the fundamental theorem of integral calculus combined with the Reynolds transport Theorem, 
being $\nu$ the normal deformation of the boundary along $(0,S)$, we have,
\begin{equation*}
\begin{split}
\int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma -  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma 
&= -\int_{s_1}^{s_2} d_s \int_{\mathcal{D}(s)}  \partial_s \uf d\sigma ds
\\
&= -\int_{s_1}^{s_2} d_{ss}^2 \int_{\D(s)} u_{\ominus} \, d\sigma \, ds +  \int_{s_1}^{s_2} d_s \left( \int_{\DD(s)} \nu u_{\ominus} \, d\gamma \right) ds\,,
\end{split}
\end{equation*}
and assuming that $\D(s)$  can not change shape, we have
\begin{equation*}
\begin{split}
-\int_{s_1}^{s_2} d_{ss}^2 \int_{\D(s)} u_{\ominus} \, d\sigma \, ds + \int_{s_1}^{s_2} d_s \left( \int_{\DD(s)} \nu u_{\ominus} \, d\gamma \right)\, ds
&=-\int_{s_1}^{s_2} \left[d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) -  d_s(  \nu |\DD(s)| \avrc{u}_{\ominus} ) \right] \, ds
\\
&=-\int_{s_1}^{s_2} \left[d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) -  d_s\left(d_s(|\D(s)|) \avrc{u}_{\ominus} \right) \right] \, ds.
\end{split}
\end{equation*}
Moreover, we have
\begin{equation*}
\int_{\Gamma_{\mathcal{P}}} \nabla \uf \cdot \nn_{\ominus} d\sigma =  \int_{\Gamma_{\mathcal{P}}} \lambda \, d\sigma
=  \int_{s_1}^{s_2} \int_{\partial\mathcal{D}(s)} \lambda d\gamma \, ds 
= \int_{s_1}^{s_2} |\DD| \avrc{\lambda} \,ds\,.
\end{equation*}
From the combination of all the above terms with the right hand side, we obtain that the solution $\uf$ of \eqref{eq:dirneu2} satisfies,
\begin{equation*}
\int_{s_1}^{s_2} \left[ 
-d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) +  d_s\left(d_s(|\D(s)|) \avrc{u}_{\ominus}\right) + |\D(s)|\avrd{u}_{\ominus} 
- |\partial\mathcal{D}(s)| \avrc{\lambda} 
\right] \, ds = \int_{s_1}^{s_2} |\mathcal{D}(s)| \avrd{g}\, ds \,.
\end{equation*}
Since the choice of the points $s_1,s_2$ is arbitrary, we conclude that the following equation holds true,
\begin{equation}\label{eq:averaged_f}
-d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) +  d_s\left(d_s(|\D(s)|) \avrc{u}_{\ominus}\right) + |\D(s)|\avrd{u}_{\ominus} 
- |\partial\mathcal{D}(s)| \avrc{\lambda}
= |\mathcal{D}(s)| \avrd{g} \quad \text{on} \ \Lambda\,,
\end{equation}
which is complemented by the following conditions at the boundary of $\Lambda$,
\begin{equation}\label{eq:averaged_f_boundary}
|\D(s)| d_s \avrd{u}_{\ominus} = 0, \quad d_s |\D(s)| = 0, \quad \text{on} \quad s=0,S.
\end{equation}
Then, we consider variational formulation of the averaged equation \eqref{eq:averaged_f}.
After multiplication by a test function $\vd \in H^1(\Lambda)$, integration on $\Lambda$ and suitable application of integration by parts, we obtain,
\begin{multline*}
\int_\Lambda d_s (|\D(s)| \avrd{u}_{\ominus} ) d_s \vd \, ds - d_s (|\D(s)| \avrd{u}_{\ominus} ) \vd |_{s=0}^{s=S}
- \int_\Lambda (d_s |\D(s)|)\avrc{u}_{\ominus} d_s \vd \, ds + (d_s |\D(s)|) \avrc{u}_{\ominus} \vd |_{s=0}^{s=S}
\\
+\int_\Lambda |\D(s)| \avrd{u_\ominus} \vd - \int_\Lambda |\DD(s)| \avrc{\lambda} \vd \, ds
= \int_\Lambda |\D(s)| \avrd{g} V\, ds\,.
\end{multline*}
Using boundary conditions, 
the identity $d_s (|\D(s)| \avrd{u}_{\ominus} ) = |\D(s)| d_s \avrd{u}_{\ominus} + d_s (|\D(s)|) \avrd{u}_{\ominus}$
and reminding that $d_s |\D(s)|)/|\DD(s)| = \nu$,
we obtain,
\begin{equation}\label{eq:averaged_f_weak}
(d_s \avrd{u}_{\ominus}, d_s \vd )_{\Lambda,|\D|} 
+ ( \nu (\avrd{u}_{\ominus} - \avrc{u}_{\ominus}), d_s \vd)_{\Lambda,|\DD|} +(\avrd{u_\ominus}, \vd)_{\Lambda, |\D|}
- (\avrc{\lambda},\vd)_{\Lambda,|\DD|}
= (\avrd{g},V)_{\Lambda,|\D|}\,.
\end{equation}
where we have introduced the following weighted inner product notation,
\begin{equation*}
(\ud,\vd)_{\Lambda,w} = \int_0^S w(s) \ud(s) \vd(s) ds\,.
\end{equation*}
Let us now formulate the modelling assumption that allows us to reduce equation \eqref{eq:averaged_f_weak} to a solvable one-dimensional (1D) model.
More precisely, we assume that:
\begin{description}
\item[A1] the function $\uf$ has a \emph{uniform profile} on each cross section $\mathcal{D}(s)$, namely $\uf(r,s,t) = \ud(s)$.
\end{description}
Therefore, observing that $\ud=\avrc{u}_{\ominus}=\avrd{u}_{\ominus}$, problem \eqref{eq:averaged_f_weak} consists to find $\ud \in H^1(\Lambda)$ such that
\begin{equation}\label{eq:1Ddirneu_weak}
 (d_s \ud, d_s \vd)_{\Lambda,|\mathcal{D}|} 
+(\ud, \vd)_{\Lambda, |\D|}
-(\avrc{\lambda},\vd)_{\Lambda, |\DD|}
=  (\avrd{g},\vd)_{\Lambda, |\mathcal{D}|}
\quad \forall \vd \in H^1(\Lambda)\,.
\end{equation}

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\subsubsection*{Topological model reduction of the problem on $\Omega_{\oplus}$}
We focus here on the subproblem of \eqref{eq:dirneu1} related to $\Omega_{\oplus}$.
We multiply both sides of \eqref{eq:dirneu1} by a test function $v\in H^1_0(\Omega)$ and integrate on $\Omega_\oplus$. Integrating by parts and using boundary and interface conditions, we obtain
\begin{equation*}
\begin{split}
\int_{\Omega _{\oplus}}fv\,d\omega&=
\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\omega -\int _{\partial \Omega _{\oplus}}\nabla \up \cdot \nn_{\oplus} v\,d\sigma + \int_{\Omega_{\oplus}} \up v
\\
&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega -\int_{\Gamma} \nabla \up \cdot \nn_{\oplus} v + \int_{\Omega_{\oplus}} \up v
\\
&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega +\int_{\Gamma} \lambda v + \int_{\Omega_{\oplus}} \up v.
\end{split}
\end{equation*} 
Then, we make the following modelling assumptions:
\begin{description}
\item[A2] we identify the domain $\Omega_{\oplus}$ with the entire $\Omega$, 
and we correspondingly omit the subscript $\oplus$ to the functions defined on $\Omega_{\oplus}$,
namely
\begin{equation*}
\int_{\Omega_{\oplus}} u_\oplus\, d\omega \simeq \int_{\Omega} u\, d\omega\,.
\end{equation*}
\end{description}
Therefore, we obtain 
\begin{equation*}
(\nabla u ,\nabla v)_{\Omega} +(u,v)_{\Omega}+(\lambda, v)_{\Gamma}  =(f,v)_{\Omega}
\end{equation*}
and combining with \eqref{eq:1Ddirneu_weak} we obtain the first formulation of the reduced problem.

\subsubsection*{Problem 1 (3D-1D-3D)}
Let $\langle \cdot , \cdot \rangle_\Gamma$ denote the duality pairing between 
$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$. The problem consists to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac12}(\Gamma )$, such that
\begin{subequations}\label{eq:problem1}
\begin{align}
&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
+ \langle \trace v  - \ext \vd, \lambda \rangle_\Gamma
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
\\
&   \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0
\quad \forall \mu \in H^{-\frac12}(\Gamma)\,.
\end{align}
\end{subequations}
Here, $\trace:H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ denotes the trace operator from $\Omega$ to $\Gamma$ and $\ext: H^1_0(\Lambda) \rightarrow H^1_{0}(\Gamma)$ denotes the uniform extension from $\Lambda$ to $\Gamma$.

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
Now, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-2D formulation
involving sub-problems on $\Omega$ and $\Lambda$ and coupling operators defined on $\Gamma$
to a 3D-1D-1D formulation where the coupling terms are set on $\Lambda$. 
To this purpose, let us write the Lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
\begin{equation*}
\lambda=\avrc{\lambda}+\tilde{\lambda}, \qquad v=\avrc{v}+\tilde{v},
\quad \text{on} \ \partial\mathcal{D}(s)\,,
\end{equation*}
where $\avrc{\tilde{\lambda}}=\avrc{\tilde{v}}=0$. 
Therefore, the coupling term on $\Gamma$ can be decomposed as,
\begin{equation*}
\int_{\Gamma}\lambda v\, d\sigma
=\int _{\Lambda}  \int_{\partial\mathcal{D}(s)} (\avrc{\lambda}+\tilde{\lambda})(\avrc{v}+\tilde{v})d\gamma ds
= \int_{\Lambda}|\partial\mathcal{D}(s)| \avrc{\lambda}\avrc{v}\,ds+\int_{\Lambda}  \int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v}d\gamma ds\,.
\end{equation*}

Then, we make the following modelling assumptions:
\begin{description}
\item[A3] we assume that the product of fluctuations is small, namely
\begin{equation*}
\int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v} d\gamma \simeq 0\,
\end{equation*}
\end{description}
and we obtain 
\begin{equation*}
(\nabla u ,\nabla v)_{\Omega} +(u,v)_{\Omega}+(\avrc \lambda, \avrc v)_{\Lambda , |\DD|}  =(f,v)_{\Omega},
\end{equation*}
which, combined with \eqref{eq:1Ddirneu_weak} leads to the second formulation of the reduced problem.

\subsection{Problem 2 (3D-1D-1D)}
Let $\langle \cdot , \cdot \rangle_\Lambda$ denote the duality pairing between 
$H^\frac12_{00}(\Lambda)$ and $H^{-\frac12}(\Lambda)$.
The problem requires to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
\begin{subequations}\label{eq:problem2}
\begin{align}
&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
+  \langle \mtrace v - \vd, \ld \rangle_{H^{-\frac12}(\Lambda), |\DD|} 
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)\,,
\\
&   \langle \mtrace u -   \ud, \md \rangle_{H^{-\frac12}(\Lambda),|\DD|} = 0
\quad \forall \md \in H^{-\frac12}(\Lambda)\,,
\end{align}
\end{subequations}
where $\mtrace$ denotes the composition of operators $\trace \circ \avrc{(\cdot)}$.
We notice that all the integrals of the reduced problem are well defined because 
$\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$ as shown in the following lemma.

%\begin{lemma}\label{lemma:H12norm}
%{\color{red}TO DO: generalize to not uniform $\DD$} 
%When $\Gamma$ is a cylinder, if $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}\in H_{00}^{\frac 12}(\Lambda)$. Moreover, if $u\in H^{\frac 12}_{00}(\Gamma)$ is constant on each cross section, namely $u(s,\theta)=u(s)$, then 
%\begin{equation*}
%\|u\|_{H^{\frac 12}_{00}(\Gamma)}=2\pi R \|u\|_{H^{\frac 12}_{00}(\Lambda)}.
%\end{equation*}
%\end{lemma}
%\begin{proof}
%Let us denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the laplacian on $\Gamma$, and with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $\Lambda$. In particular,
%\begin{align*}
%\phi _{ij}(s,\theta)=sin (i\pi s)\left( cos(j\theta)+ sin(j\theta) \right),\\
%\rho_{ij}=i\pi ^2+\frac{j^2}{R^2},\\
%\phi _{i}(s)=sin (i\pi s),\\
%\rho _i = i\pi ^2.
%\end{align*}
%It is easy to verify that 
%\begin{eqnarray}
%\label{null_int_eigenf}
%\int_0^{2\pi} \phi _{ij}(s,\theta)=0 \quad \forall j>0, \forall i \\
%\label{nonull_int_eigenf}
%\int_0^{2\pi} \phi _{ij}(s,\theta)= 2\pi R \, \sin(i \pi s) \quad \mbox{if } j=0, \forall i  .\\
%\end{eqnarray}
%Moreover we recall that $\phi_{i,j}(s,\theta)$ and $\phi _i(s)$ are orthogonal basis of $L^2(\Gamma)$ and $L^2(\Lambda)$ respectively. Therefore,
%\begin{multline*}
%\avrc{u}(s)=\frac{1}{2\pi R}\int_0^{2\pi} u(s,\theta)R\, d\theta
%= \frac{1}{2\pi R}\int_0^{2\pi} \sum_{i,j} a_{i,j} \phi_{i,j}(s,\theta) R\, d\theta
%\\= \frac{1}{2\pi R}\sum_{i,j} a_{i,j}\int_0^{2\pi}  \phi_{i,j}(s,\theta) R\, d\theta
%=  \sum_{i} a_{i,0} \phi_{i}(s).
%\end{multline*}
%From \cite[Lemma 4.11]{chandler2015interpolation} we have
%\begin{equation}\label{H12norm_Gamma}
%\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2,
%\text{ with }
%a_{ij}=\int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds.
%\end{equation}
%and 
%\begin{equation*}
%\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
%\text{ with }
%\avrc{a}_i=\int _0^1 \avrc{u}(s )\phi_{i}(s) ds.
%\end{equation*}
%
%Therefore, we have
%\begin{multline*}
%\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=
%\sum_{i=1}^{\infty}\left( 1+ i^2\pi^2\right)^{\frac 12}\left( \int_0^1 \avrc{u}(s) sin(i\pi s)\, ds \right)^2\\
%= \sum_{i=1}^{\infty} \left( 1+ i^2\pi^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^1 \sin(j\pi s) \sin(i\pi s) \, ds  \right)^2\\
%= \sum_{i=1}^{\infty} \frac 14 \left( 1+ i^2\pi^2\right)^{\frac 12}a_{i,0}^2\\
%\leq \sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ i^2\pi^2 + \frac{j^2}{R^2}\right)^{\frac 12} |a_{i,j}|^2 =\|u\|^2_{H^{\frac 12}(\Gamma)},
%\end{multline*}
%
%where we have used the fact that
%\begin{eqnarray*}
%&\int_0^1 \sin(i\pi s) \sin(j\pi s)\, ds=0 \quad \text{if $i\neq j$}\\
%&\int_0^1 \sin(i\pi s) \sin(j\pi s)\, ds=\frac 12 \quad \text{if $i =j$}.
%\end{eqnarray*}
%Moreover, in the case in which $u$ is constant on each cross section, from \eqref{H12norm_Gamma} we have
%\begin{multline*}
%\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2
%=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ i\pi ^2+\frac{j^2}{R^2}\right)^{\frac 12}\left( \int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds \right)^2\\
%=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ i\pi ^2+\frac{j^2}{R^2}\right)^{\frac 12}\left( \int _0^1 u(s) \int _0^{2\pi} \phi_{ij}\, R d\theta ds \right)^2,
%\end{multline*}
%and using \eqref{null_int_eigenf} and \eqref{nonull_int_eigenf}, we obtain
%\begin{multline*}
%\|u\|^2_{H^{\frac 12}(\Gamma)}=
%\sum_{i=1}^{\infty}\left( 1+ i\pi ^2\right)^{\frac 12}\left(\int _0^1 u(s )sin (i\pi s) 2\pi R ds\right)^2\\
%=4\pi ^2 R^2 \sum_{i=1}^{\infty}\left( 1+ \rho _i\right)^{\frac 12}|a_i|^2 = 4\pi ^2 R^2  \|u\|^2_{H^{\frac 12}(\Lambda)}.
%\end{multline*}
%\hspace*{0.9\textwidth} c.v.d.
%\end{proof}
%\begin{remark}
%The results of \eqref{lemma:H12norm}  can be generalized to the case of a  different geometry of $\Gamma$, for example a parallelepiped.  
%\end{remark}

\begin{lemma}\label{lemma:H12norm}
Let $\Gamma$ be a tensor product domain, $\Gamma= (0,X) \times (0,Y)$. For any regular $u(x,y)$ in $\Gamma$, let $\avrc{u}(x)=\frac 1Y \int _0^Y u(x,y)\, dy$. Then, for any $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}(x)\in H_{00}^{\frac 12}((0,X))$. 
Moreover, if $u(x,y)\in H^{\frac 12}_{00}(\Gamma)$ is constant with respect to $y$, namely $u(x,y)=u(x)$, then 
\begin{equation*}
\|u\|_{H^{\frac 12}_{00}(\Gamma)}=Y \|u\|_{H^{\frac 12}_{00}(0,X)}.
\end{equation*}
\end{lemma}
\begin{proof}
Let us consider the eigenvalue problems for the Laplace operator on $\Gamma$ with homogeneous Dirichlet conditions at $x=0,\, X$ and periodic boundary conditions at $y=0,\, Y$ and on $(0,X)$ with homogeneous Dirichlet conditions. Let us denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the laplacian on $\Gamma$, and with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $(0,X)$. In particular,
\begin{align*}
\phi _{ij}(x,y)=\sin \left(\frac{i\pi x}{X}\right)\left( cos\left(\frac{j2\pi y}{Y}\right)+ sin	\left(\frac{j2\pi y}{Y}\right) \right),\\
\rho_{ij}=\left(\frac{i\pi}{X}\right) ^2+\left(\frac{j2\pi}{Y}\right)^2,\\
\phi _{i}(x)=\sin \left(\frac{i\pi x}{X}\right),\\
\rho _i = \left(\frac{i\pi}{X}\right) ^2.
\end{align*}
It is easy to verify that 
\begin{eqnarray}
\label{null_int_eigenf}
\int_0^{Y} \phi _{ij}(x,y)=0 \quad \forall j>0, \forall i \\
\label{nonull_int_eigenf}
\int_0^{Y} \phi _{ij}(x,y)= Y \, \sin\left(\frac{i\pi x}{X}\right) \quad \mbox{if } j=0, \forall i  .\\
\end{eqnarray}
Moreover we recall that $\phi_{i,j}(x,y)$ and $\phi _i(x)$ are orthogonal basis of $L^2(\Gamma)$ and $L^2(0,X)$ respectively. Therefore,
\begin{multline*}
\avrc{u}(x)=\frac{1}{Y}\int_0^{Y} u(x,y)\, dy
= \frac{1}{Y}\int_0^{Y} \sum_{i,j} a_{i,j} \phi_{i,j}(x,y) \, dy
\\= \frac{1}{Y}\sum_{i,j} a_{i,j}\int_0^{Y}  \phi_{i,j}(x,y) \, dy
=  \sum_{i} a_{i,0} \phi_{i}(x).
\end{multline*}
From \cite[Lemma 4.11]{chandler2015interpolation} we have
\begin{equation}\label{H12norm_Gamma}
\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2,
\text{ with }
a_{ij}=\int _0^X\int _0^{Y} u(x,y )\phi_{ij} (x,y)dy dx.
\end{equation}
and 
\begin{equation*}
\|\avrc{u}\|^2_{H^{\frac 12}(0,X)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
\text{ with }
\avrc{a}_i=\int _0^X \avrc{u}(x )\phi_{i}(x) dx.
\end{equation*}

Therefore, we have
\begin{multline*}
\|\avrc{u}\|^2_{H^{\frac 12}(0,X)}=
\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \int_0^X \avrc{u}(x) \sin\left(\frac{i\pi x}{X}\right)\, dx \right)^2\\
= \sum_{i=1}^{\infty} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^1 \sin\left(\frac{j\pi x}{X}\right) \sin\left(\frac{i\pi x}{X}\right) \, dx  \right)^2\\
= \sum_{i=1}^{\infty} \frac{X^2}{4} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}a_{i,0}^2\\
\leq \frac{X^2}{4}\sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12} |a_{i,j}|^2 =\frac{X^2}{4}\|u\|^2_{H^{\frac 12}(\Gamma)},
\end{multline*}

where we have used the fact that
\begin{eqnarray*}
&\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=0 \quad \text{if $i\neq j$}\\
&\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=\frac X2 \quad \text{if $i =j$}.
\end{eqnarray*}
Moreover, in the case in which $u$ is constant with respect to $y$, from \eqref{H12norm_Gamma} we have
\begin{multline*}
\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2\\
=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12}\left( \int _0^X\int _0^Y u(x,y )\phi_{ij}(x,y) \,dy\,dx \right)^2\\
=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12}\left( \int _0^X u(x) \int _0^Y \phi_{ij}(x,y)\,  dy dx \right)^2,
\end{multline*}
and using \eqref{null_int_eigenf} and \eqref{nonull_int_eigenf}, we obtain
\begin{multline*}
\|u\|^2_{H^{\frac 12}(\Gamma)}=
\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left(\int _0^X Yu(x)\, \sin\left(\frac{i\pi x}{X}\right) dx\right)^2\\
=Y^2 \sum_{i=1}^{\infty}\left( 1+ \rho _i\right)^{\frac 12}|a_i|^2 = Y^2  \|u\|^2_{H^{\frac 12}(0,X)}.
\end{multline*}
\end{proof}

\begin{corollary}
Let $\Gamma$ be the lateral surface of a prism with $N$ faces $\Gamma_i$, $i=1, \dots, N$, with $\Gamma_i=(0,X_i)\times(0,S)$. For any $u\in H^{\frac 12}_{00}(\Gamma)$, let $\avrc{u}(s)= \frac{1}{\sum_i{|X_i|}}\sum_{i=1}^N \int_0^{X_i} u(x,s)\, dx$. Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$.
\end{corollary}

\begin{corollary}
Let $\Gamma$ be the lateral surface of a cylinder of radius $R$. Let $u\in H^{\frac 12}_{00}(\Gamma)$ and let $\avrc{u}(s)= \frac{1}{2\pi R} \int_0^{2\pi} u(s,\theta)R\, d\theta$. Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$.
\end{corollary}

It is apparent that problems \eqref{eq:weak_dirneu} and \eqref{eq:red_dirneu} share the same mathematical structure.
For this reason, the well-posedness of \eqref{eq:red_dirneu} can be studied in the framework of the classical theory of saddle point problems.

%Assuming now that 
%$\Pi_1: H^1(\Omega) \rightarrow H^{\frac12}(\Gamma)$ or $\Pi_2: H^1(\Gamma) \rightarrow H^{\frac12}(\Gamma)$ are isomorphisms in the sense that 
%\[
%\| \Pi_1 \|_{L(H^1(\Omega), H^{\frac12}(\Gamma))} \le C \mbox{, } 
%\| \Pi_1^{-1} \|_{L(H^{\frac12}(\Gamma), H^1(\Omega))} \le 1/c,  
%\]
%and 
%\[
%\| \Pi_2 \|_{L(H^1(\Omega), H^{\frac12}(\Gamma))} \le C \mbox{, } 
%\| \Pi_2^{-1} \|_{L(H^{\frac12}(\Gamma), H^1(\Omega))} \le 1/c .   
%\]
%We obtain the inf-sup condition as follows. Assume that $\Pi_1$ is an isomorphism then  
%we may show the inf-sup conditioning by letting $\Pi_1 \hat u = M $ and $ \hat \ud = 0$ (i.e., we need the lower bound only for one
%of the operators).  
%\begin{eqnarray}
%\sup_{u,\ud}\frac{
%\langle \Pi_1 u - \Pi_2 \ud , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
%}{(|u|_1^2 + |\ud|_1^2)^{1/2}} 
%\ge \\ 
%\frac{ \langle \Pi_1 \hat u - \Pi_2 \hat \ud , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
%}{(|\hat u|_1^2 + |\hat \ud|_1^2)^{1/2}}  \ge \\
%\frac{ \langle M , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
%}{|\Pi_1^{-1} M |_{H^1(\Omega})} \ge \\ 
%\frac{ \langle M , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
%}{| M |_{H^\frac12(\Gamma)}} \ge \\ 
%c | M |_{H^{-\frac12}(\Gamma)}  
%\end{eqnarray}
%I think the other Brezzi conditions also follows, but for the boundedness we
%would need that both $\Pi_1$ and $\Pi_2$ are bounded. Not sure I am 
%happy with the $\langle \cdot, \cdot \rangle$ notation and in particular not when we spesify the
%spaces. I would rather just say that $(\cdot, \cdot)$ denotes both the $L_2$ inner product and the
%duality pairing.  
%If we find it useful we may also  
%consider $\Pi_2: H^1(\Gamma) \rightarrow X(\Gamma)$ where $X$ may e.g. be $H^1$.  
%If so, $L, M$ in $ H^{-\frac12}(\Gamma) \cap X(\Gamma)$

%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
%Analysis of the continuous problem 
\input{infsup_continuous}

%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
%Analysis of the discrete problem in the case in which the LM lives on the coarser mesh w.r.t the trace mesh deriving from the 3D mesh

%\input{infsup_discrete_coarserLM}

%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
%Analysis of the discrete problem in the case in which the LM lives on the the trace mesh deriving from the 3D mesh (conforming to the interface cylinder \Gamma)

\input{infsup_discrete_conformingLM}

%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
%Analysis of the discrete problem in the case in which we have a non conforming 3D mesh (just in the case of formulation 2 3D-1D-1D)

\input{unfitted_prob2}

%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>

\input{benchmark}
%-----------------
\bibliographystyle{siamplain}
\bibliography{3d1d_coupled}
\end{document}

### 2020-01-09 lm3d1d_vs2/unfitted_prob2.tex
Paolo's revision sections 2-3

\def\patch{\omega _j}
\subsection{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$}
We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_h$ cut the interface $\Gamma$. It is easy to understand that the formulation of Problem 2 is more suitable. 
{\color{red} Add more details, we can refer also to cutFEM (Burman, Massing etc.) explaining the limitation of that approach (network case for example).}\\
Therefore we focus on the analysis of Problem 2.

\subsubsection{Problem 2} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X_{h,0}^1(\Omega)$ and $X_{h,0}^1(\Lambda)$, see the previous subsection for the definition. Notice that in this case we suppose that the mesh sizes of the 3D mesh $\mathcal{T}^{\Omega}_h$ and the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different, in particular we suppose the 1D mesh is finer. Concerning the multiplier space, let $\mathcal{G}_h = \{K \in \mathcal{T}^{\Omega}_h: \, K\cap \Lambda \neq \emptyset\}$, namely the set of the 3D elements which intersect $\Lambda$, and let us define $Q_h=\{{\ld}_h : {\ld}_h \in P^0(K) \, \forall K \in \mathcal{G}_h\}$. We notice that we are extending the multiplier to the 3D elements: equivalenty we could have defined $\lambda_h$ as a piecewise constant function on $K\cap \Lambda$ for any $K \in \mathcal{G}_h$, but we use this trick so that we do not need to consider the 1D mesh given by the intersection of the elements of $\mathcal{G}_h$ with $\Lambda$. With this choice the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s({\ld}_h, {\md}_h)$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}. In particular, we build a new multiplier space $L_h$ for which the discrete inf-sup condition is fulfilled and we build a projection operator $\pi_L: Q_h \rightarrow L_h$ such that for any $[v, \vd] \in X $
\begin{equation}\label{condition_pi_L}
b([v, \vd], \lambda_h - \pi_L \lambda_h) \lesssim \vertiii{[v,\vd]}\|\lambda_h - \pi_L \lambda_h\|_{L_h},
\end{equation}
where for $X$ and $\vertiii{[\cdot, \cdot]}$ we use the definitions of section $3.2$ and $\|\cdot \|_{L_h}$ denotes a suitable discrete norm on $L_h$. Then, the following lemma holds
\begin{lemma}\cite[Lemma2.1]{burman2014}
Under the previous assumption, $\forall {\ld}_h \in Q_h$,
\begin{equation*}
\|{\ld}_h\|_{H^{-\frac 12}(\Lambda)} \lesssim \sup_{\substack{v_h \in X_{h,0}^1(\Omega)\\ {\vd}_h \in X_{h,0}^1(\Lambda)}} \frac{b([v_h, {\vd}_h], {\ld}_h)}{\vertiii{[v_h, {\vd}_h]}} + \|{\ld}_h - \pi_L {\ld}_h\|_{L_h}
\end{equation*}
\end{lemma}
 Based on this projection operator, we build the stabilization term $s({\ld}_h, {\md}_h)$ satisfying
 \begin{equation*}
 \|{\ld}_h- \pi_L {\ld}_h\|_{L_h} \lesssim s({\ld}_h, {\ld}_h)
\end{equation*}  and prove that $\forall [u_h, {\ud}_h]$, there exists $\xi_h([u_h, {\ud}_h]) \in Q_h$ s.t.
\begin{equation}\label{stab_coercivity}
a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h([u_h, {\ud}_h])) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) },
\end{equation}
\begin{equation}\label{stab_stability}
(s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) },
\end{equation}
being $\vertiii{[\cdot \, ,\, \cdot] }_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) }$ a suitable discrete norm (see \cite[section II]{burman2014}). \\

We recall that in the case of Problem 2, 
\begin{equation*}
b([u_h, {\ud}_h], {\ld}_h) = \left(\mtrace u_h - {\ud}_h, {\ld}_h\right)_{\Lambda,|\DD|}.
\end{equation*}
The construction of the inf-sup stable space $L_h$ is based on macro elements of diameter $H$, where $H$ is sufficiently larger than $h$. In particular, we assume that there exists positive constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$, with $c_h$ is sufficiently large. The space is constructed assembling the 3D elements of $\mathcal{G}_h$ into macro patches $ \patch $ such that {\color{red}$H \leq |\patch\cap \Lambda|\leq cH$}. Namely, $\patch=\cup _{i=0}^{M_j} K_i$, where $K_i \in \mathcal{G}_h$ and $M_j$ is uniformly bounded in $j$ by some $M\in \mathbb{N}$ and $H=\min_{j}|\patch\cap \Lambda|$. We assume that the interiors of the patches $\patch$ are  disjoint. We define 
\begin{equation*}
L_h=\left\{{\lld }_h: \, {\lld }_h\in P^0(\patch)\, \forall j \right\}.
\end{equation*}

%figure extended patch
\begin{figure}\label{fig:patch}
\center
\input{./graphics/ext_patch}
\caption{Extended patches $\omega_j$.}
\end{figure}

Moreover, we associate to each patch $\patch$ a shape-regular extended patch, still denoted by $\omega_j$ for notational simplicity, which is built adding to $\patch$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$ and we assume that the interiors of the new extended patches $\omega _j$ are still disjoint (see Figure \ref{fig:patch}). Here we are using the classical definition of shape-regularity, see for example \cite{MR2050138}, namely there exist a constant $C>0$ such that for any $\omega_j$, $\frac{\tilde{\rho}_j}{\bar{\rho}_j}\leq C$, being $\tilde{\rho}_j$ the diameter of $\omega_j$ and $\bar{\rho}_j$ the diameter of the largest ball that can be inscribed in $\omega_j$. The extended patches $\omega _j$ are built such that they fulfill the conditions meas$(\patch)=\mathcal{O}(H^3)$ and {\color{red}diam$(\Gamma_{\patch\cap \Lambda}\cap \omega_j)=O(H)$}, where $\Gamma_{\patch\cap \Lambda}$ is the portion of $\Gamma$ with centerline $\patch\cap \Lambda$. See Figure \ref{fig:gamma_generated} for a representation in the simple case in which $\omega _j$ is composed just by one tetrahedron. The latter assumption is required to ensure that the intersection of $\Gamma_{\patch\cap \Lambda}$ and $\omega_j$ is not too small and it will be needed later on to prove the inf-sup stability of the space $L_h$ in Lemma \ref{lemma:Lh_infsup}. We equipe the space $L_h$ with the discrete norm 
\begin{equation*}
\|\lld \|_{L_h} = \|\lld \|_{-\frac 12, h, \Lambda} = \|h^{\frac 12} \  \lld \|_{L^2(\Lambda)}.
\end{equation*}
As shown in \cite[Section III]{burman2014}, we can always choose $\pi_L$ as the $L_2$ orthogonal projection operator from $\Lambda_h$ to $L_h$ in order to satisfy \eqref{condition_pi_L} and then in practice replace it with any interpolation $\tilde{\pi}_L$ of $\Lambda_h$ in $L_h$. In particular, we define $\forall \lambda_h \in \Lambda_h$,
\begin{equation*}
\tilde{\pi}_L {\ld}_{ _{|\patch}} = N_j^{-1} \sum_{\substack{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset}} {\ld}_{|K_i} \qquad \text{for all $\omega_j$,} 
\end{equation*}
being $N_j$ the cardinality of the set $\{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset\}$. These choice leads to the following stabilization 
\begin{equation*}
s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
\end{equation*}
being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{G}_h$.

\begin{figure}\label{fig:gamma_generated}
\centering
\subfigure[$\Gamma_{\omega_j \cap \Lambda}$]
{
\input{./graphics/gamma_generated}
}
\qquad \qquad
\subfigure[ $\Gamma_{\omega_j \cap \Lambda} \cap \omega_j$]{
\input{./graphics/intersection}
}
\caption{$\Gamma_{\omega_j \cap \Lambda}$, the portion of $\Gamma$ generated by $\omega_j \cap \Lambda$ in (a) and the intersection between $\Gamma_{\omega_j \cap \Lambda}$ and $\omega_j$ in (b). Here for simplicity $\omega_j$ is represented as a single tetrahedron but actually it is a collection of tetrahedra as shown in Figure \ref{fig:patch}.}
\end{figure}
Thanks to the shape regularity of these extended patches, we have that the following discrete trace and Poincarè-type inequalites hold. More precisely, for any function $v\in H^1(\omega_j)$, 
\begin{equation}\label{discr_trace_ineq}
\|\trace v\|_{L^2(\Gamma\cap \omega_j)} \lesssim H^{-\frac 12} \|v\|_{L^2(\omega_j)}
\end{equation}
\begin{equation}\label{disc_poincare_ineq}
\|v- \mathcal{E}_{\patch} \pi_L\mtrace v\|_{L^2(\omega_j)} \leq c_P H \|\nabla v\|_{L^2(\omega_j)},
\end{equation}
%where $\pi_L$ is a projection operator onto piecewise constant functions on $\patch\cap \Lambda$. In particular, for any $w \in L^2(\Lambda)$, we define
where for any $w \in L^1(\Lambda)$, $ \mathcal{E}_{\patch}\pi_Lw \in L_h$ and with a little abuse of notation we denote as $\pi_L$ the operator
\begin{equation*}
\pi_Lw_{|\patch \cap \Lambda} =\frac{1}{|\Gamma_{\patch\cap \Lambda}|}\int_{\patch\cap \Lambda}|\DD| w\quad \forall j,
\end{equation*}   
whereas the operator $\mathcal{E}_{\patch}$ simply extends the constant $\pi_L\mtrace v_{|\patch \cap \Lambda}$ to $\omega _j$.
Moreover $\forall u_h \in X^1_{h,0}(\Omega)$ we have the following average inequality 
\begin{equation*}
\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| } \leq \sum _j \|\trace  u_h\|^2_{L^2(\omega_j\cap \Gamma)}.
\end{equation*}
Indeed, by the definition of $\mtrace$ and Jensen inequality, we have
\begin{multline*}
\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| }
= \sum _j\int_{\patch \cap \Lambda} |\DD| \mtrace u_h^2 
\\
= \int_{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \trace u_h \right)^2
\\
(\text{Jensen})\leq \int_{\Lambda} \int_{\DD} (\trace u_h)^2
= \int_{\Gamma} (\trace u_h)^2
\\
(\patch \cap \Gamma \text{ partition of } \Gamma)= \sum _j \int_{\patch \cap \Gamma} (\trace u_h)^2
= \sum _j \|\trace u_h\|^2_{L^2(\patch \cap \Gamma)}.
\end{multline*}

\begin{lemma}\label{lemma:Lh_infsup}
The space $L_h$ is inf-sup stable, namely $\forall {\lld}_h \in L_h$, $\exists \beta >0$ s.t.
\begin{equation*}
\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\lld} _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|{\lld}_h\|_{H^{-\frac 12}(\Lambda)}.
\end{equation*} 
and the constant is independent of the cuts. 
\end{lemma}
\begin{proof}
% We have to prove that $\exists \beta >0$ such that $\forall l_h \in L_h$,
%\begin{equation*}
%\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',1}^0(\Lambda)}} \frac{\left(\avrc{T v_h} - {\vd}_h, l _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|l_h\|_{H^{-\frac 12}(\Lambda)}.
%\end{equation*}
As in the continuous case, we can choose ${\vd}_h=0$ and we prove that
\begin{equation*} 
\sup_{v_h \in X_{h,0}^1(\Omega)} \frac{\left(\mtrace v_h ,{\lld}_h\right)_{\Lambda, |\DD|}}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|{\lld}_h\|_{H^{-\frac 12}(\Lambda)}.
\end{equation*} 
Proving the last inequality it is equivalent to find the Fortin operator $\pi_F: H^1_0(\Omega) \rightarrow X_{h,0}^1(\Omega)$, such that 
\begin{equation*}
\left(\mtrace v - \mtrace \pi _F v  , {\lld}_h\right)_{\Lambda, |\DD|}=0, \quad \forall v\in H^1_0(\Omega), \, {\lld}_h \in L_h
\end{equation*} 
and
\begin{equation*}
\|\pi_F v\|_{H^1(\Omega)}\lesssim \|v\|_{H^1(\Omega)}.
\end{equation*}

We define
\begin{equation*}
\pi_F v = I_h v + \sum _j \alpha _j \varphi _j \qquad \text{with }\alpha_j =\frac{\int_{\patch \cap \Lambda}|\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch \cap \Lambda}|\DD|\mtrace \varphi _j}
\end{equation*}
where $I_h: H^1(\Omega) \rightarrow X_{h,0}^1$ denotes an $H^1(\Omega)$-stable interpolant
and $\varphi_j \in X_{h,0}^1(\Omega)$ is such that supp$(\varphi_j)\subset \omega_j$, supp$(\trace \varphi _j) \subset \Gamma_{\patch\cap \Lambda}\cap \omega_j$, $\varphi_j =0$ on $\partial \omega _j$ and 
\begin{equation}\label{phi_properties}
 {\color{red}\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j=O(H)} \text{ and } \|\nabla \varphi _j\|_{L^2(\omega _j)}=O(1). 
\end{equation}
We notice that supp$(\trace \varphi_j) \subset \Gamma_{\patch\cap \Lambda}\cap \omega_j$ ensures that $\mtrace \varphi_j \subset \omega_j\cap \Lambda$. Therefore, since for construction the interiors of $\omega_j\cap \Lambda$  are disjoint and $\varphi _j = 0 $ on $\partial \omega_j$,  the functions $\mtrace \varphi_j\, \forall j$ have all disjoint supports. This construction is always possible since meas$(\patch) = \mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda} \cap \omega_j)=\mathcal{O}(H)$, provided $H$ is sufficiently larger that $h$. Indeed, this guarantees that the functions $\varphi _j$ and their traces $\trace \varphi _j$ have a sufficiently large support so that they can be built in order to satisfy \eqref{phi_properties}.
Then we have
\begin{multline*}
\left(\mtrace v - \mtrace \pi _F v  , {\lld}_h\right)_{\Lambda, |\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD |\left[ \mtrace v-\mtrace I_h v-\sum _i \alpha_i \mtrace \varphi _i \right]{\lld}_h \\
(\text{supp} (\mtrace \varphi _i )\subset \omega _i\cap \Lambda \, \forall i)  =\sum _j \int_{\patch\cap \Lambda}|\DD| \left[ \mtrace v-\mtrace I_h v-\alpha_j \mtrace \varphi _j \right]{\lld}_h\\
=\sum _j \int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\lld}_h - \frac{\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi _j} \int_{\patch\cap \Lambda} |\DD|\mtrace \varphi _j{\lld}_h\\ 
(\text{using $l_h$ constant on $\patch\cap \Lambda$})=0.
\end{multline*}
Concerning the continuity of $\pi_F$, we exploit the assumptions that the interiors of $\patch$ are disjoint and supp$(\varphi _j) \subset \patch$ and we have
\begin{multline*}
\|\nabla \pi_F v \|_{L^2(\Omega)} \leq \|\nabla I_h v\|_{L^2(\Omega)} + \left(\sum_j\alpha_j^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\right)^{\frac 12}\\
(\text{stability of }I_h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \left(\sum_j\alpha_j^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\right)^{\frac 12}
\end{multline*}
and for the second term 
\begin{multline*}
\sum_j \alpha_j ^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\leq
\\
\left(\text{using }\|\nabla \varphi _j\|_{{L^2(\omega_j)}}=O(1)\right) \lesssim  \sum_j \frac{\left(\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)\right)^2}{\left(\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j \right)^2}
\\
\left(\text{since }\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j=O(H)\right) \lesssim \frac {1}{H^2} \sum_j \left(\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_hv)\right)^2
\\
(\text{Jensen}) \lesssim  \frac {1}{H^2} \sum_j |\patch\cap \Lambda| \int_{\patch\cap \Lambda} |\DD|^2(\mtrace v-\mtrace I_h v)^2
\\
(\text{being }|\patch\cap \Lambda| \leq cH)\lesssim  \frac {1}{H} \sum_j \| \mtrace (v-I_h v)\|^2_{L^2(\patch\cap \Lambda), |\DD|}
\\
(\text{average inequality}) \lesssim  \frac {1}{H} \sum_j \| \trace(v-I_h v)\|^2_{L^2(\omega _j\cap \Gamma)}  
\\
\left(\text{trace inequality} \right)\lesssim  \frac {1}{H^2} \sum_j  \| v-I_h v\|^2_{L^2(\omega_j)} \lesssim  \frac {1}{H^2}  \| v-I_h v\|^2_{L^2(\Omega)} 
\\
(\text{approximation properties of }I_h)\lesssim \|\nabla  v\|^2_{L^2(\Omega)}
\end{multline*}
and the continuity of $\pi_F$ follows.
\end{proof}

%\subparagraph{Satisfaction of the assumptions of the 
%abstract analysis}
We choose the following discrete norm
\begin{equation*}
\vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_{h'}(\Lambda) }
= \|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|} + \|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|},
\end{equation*}
where $\|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|} = \|h^{-\frac 12} (\mtrace u_h - {\ud}_h)\|^2_{L^2(\Lambda), |\DD|} $. Then, we have the following lemma. 
\begin{lemma}
The inequalities \eqref{stab_coercivity} and \eqref{stab_stability} hold.
\end{lemma}
\begin{proof} 
Concerning the coercivity property \eqref{stab_coercivity}, we have to show that $\forall [u_h, {\ud}_h]$, there esists $\xi_h \in Q_h$ s.t.
\begin{multline*}
(u_h,u_h)_{H^1(\Omega)}+ ({\ud}_h, {\ud}_h)_{H^1(\Lambda), |\D|} +   (\mtrace u_h - {\ud}_h, \xi_h)_{\Lambda,|\DD|} \\
\geq \alpha_{\xi}(\|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|}+ \|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|}.
\end{multline*}
We choose 
\begin{equation*}
{\xi_h}_{|\patch\cap \Lambda}=\delta \frac 1H \pi_L(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}
\end{equation*}
and we recall that 
\begin{equation*}
\pi_L(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}=\frac{1}{|\Gamma_{\patch\cap \Lambda}|}\int_{\patch\cap \Lambda}|\DD| (\mtrace u_h- {\ud}_h).
\end{equation*} 
Actually, $\mathcal{E}_{\patch}\xi_h\in L_h \subset Q_h$. Then,
\begin{multline*}
\left( \mtrace u_h - {\ud}_h, \xi _h \right)_{\Lambda,|\DD|} 
= \sum_j \int_{\patch\cap \Lambda} |\DD|(\mtrace u_h - {\ud}_h)\xi_h
\\
(\text{definition of $\xi_h$})= \delta \frac{1}{H}\sum_j \pi_L( \mtrace u_h - {\ud}_h)\int_{\patch\cap \Lambda} |\DD|(\mtrace u_h - {\ud}_h)
\\
= \delta \frac{1}{H} \sum_j \int_{\patch\cap \Lambda}|\DD| (\pi_L( \mtrace u_h - {\ud}_h) )^2
\\
(\text{orthogonality of $\pi_L$}) = - \delta \frac{1}{H} \|(\pi_L-\mathcal{I})(\mtrace u_h - {\ud}_h)\|^2_{L^2(\patch\cap \Lambda),|\DD|} + \delta \frac{1}{H} \|\mtrace u_h - {\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|}
\\ 
\geq -2\delta \frac 1H \sum_j \|(\pi_L - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda), |\DD|}
-2 \delta \frac 1H \sum_j \|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|}
\\ 
+ \delta \frac 1H \sum_j \|\mtrace u_h-{\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|}. 
\end{multline*}
For the first term we have
\begin{multline*}
\sum _j  \|(\pi_L - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} =\sum _j \int _{\patch \cap \Lambda} |\DD| (\pi_L \mtrace u_h- \mtrace u_h)^2
\\
(\text{Average inequality)} \leq \sum _j  \int_{\omega _j \cap \Gamma} (\ext \pi_L \mtrace u_h -\trace u_h)^2 
\\
(\text{trace inequality}) \leq \sum _j  \frac 1H \int_{\omega_j}(\mathcal{E}_{\patch} \pi_L \mtrace u_h - u_h)^2 
\\ 
(\text{Poincare, see \cite[Corollary B.65]{MR2050138}})\leq \sum _j  H c_P ^2 \|\nabla u_h\|^2_{L^2(\omega _j)}.
\end{multline*}
For the second term we have
\begin{multline*}
\sum _j \|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD| (\pi_L {\ud}_h -{\ud}_h)^2
\\
(\text{Poincare, \cite[Corollary B.65]{MR2050138}})\lesssim \sum _j  H^2 c_P^2 \int_{\patch\cap \Lambda} |\DD|(\nabla {\ud}_h)^2
\\
(\text{since $H$ is fixed, we can find a constant s.t. } H|\DD| \lesssim |\D|) \lesssim \sum _j H c_P^2  \int_{\patch\cap \Lambda} |\D|(\nabla {\ud}_h)^2 
\\
\lesssim \sum _j H c_P^2  \|\nabla {\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\D|}.
\end{multline*}
%{\color{red} N.B. we are using a kind of weigthed Poincare inequality, check... I think it should work because I can do something like this
%\begin{multline*}
%\int_{\patch \cap \Lambda} |\DD| u^2 \leq 
%max |\DD| \int_{\patch \cap \Lambda} u^2 \leq
%max |\DD| \int_{\patch \cap \Lambda} (\nabla u)^2 =
%\frac{max |\DD|}{min|\DD|} min|\DD| \int_{\patch \cap \Lambda} (\nabla u)^2 \leq\\
%\frac{max |\DD|}{min|\DD|}  \int_{\patch \cap \Lambda} |\DD| (\nabla u)^2 
%\end{multline*}
%}\\
Therefore, we obtain
\begin{multline*}
a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h([u_h, {\ud}_h]))
\geq \\
(1-2\delta c_P^2) \|\nabla u_h\|^2_{L^2(\Omega)} + (1- 2\delta c_P^2) \|\nabla {\ud}_h\|^2_{L^2(\Lambda), |\D|}
+\delta c_H  \|\mtrace u_h-{\ud}_h\|^2_{\frac 12,h,\Lambda, |\DD|}
\end{multline*}
and choosing $\delta=\frac{1}{4c_P^2}$ we obtain the coercivity inequality.\\
Concerning the stability inequality \eqref{stab_stability}, the proof is analogous to the one in \cite{burman2014}.
\end{proof}

\begin{remark}
We notice that if we choose $Q_h=X_{h',0}^1(\Lambda)$, the constant in the inf-sup inequality  \eqref{eq:infsup_discrete} depends on the mesh size $h'$. Indeed,
\begin{multline}
\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\lld} _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}}
\geq \sup_{\substack{{\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(- {\vd}_h, {\lld} _h\right)_{\Lambda, |\DD|}}{\|{\vd}_h\|_{H^1(\Lambda)}}
\geq \frac{{\|\lld} _h\|^2_{L^2(\Lambda)}}{\|{\vd}_h\|_{H^1(\Lambda)}} \\
( \text{inverse inequality} )\geq \frac{{h'}^2}{c_I} \|{\lld}_h\|_{L^2(\Lambda)}
\geq  \frac{{h'}^2}{c_I} \|{\lld}_h\|_{H^{-\frac 12},(\Lambda)}
\end{multline}
being $c_I$ the constant in the inverse inequality
\begin{equation*}
\|{\lld}_h\|_{H^1(\Lambda)} \leq \frac{c_I} {{h'}^2} \|{\lld}_h\|_{L^2(\Lambda)}. 
\end{equation*}
\end{remark}

### 2020-01-09 lm3d1d_vs3/3d1d_coupled_LM.tex
Paolo's revision sections 2-3

--- 2020-01-09 lm3d1d_vs2/3d1d_coupled_LM.tex
@@
 Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set.
-Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Omega}_\ominus$ be the complementary set of the cylinder.
-We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Omega_\ominus$.
+Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and let $\Omega_\oplus = \Omega \setminus \overline{\Omega}_\ominus$ be the complementary set of the cylinder.
+We also introduce the set $\Lambda$, a 1D manifold that represents the centerline of $\Omega_\ominus$.
 We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$.
-We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Omega_\ominus$ and its boundary, respectively.
+We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Omega_\ominus$ and its boundary, respectively, and we assume that $\min |\D (s)| >0$, where $|\D (s)|$ is the measure of $\D (s)$.
 %In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach. 
@@
 Let $u\in H^{\frac 12}_{00}(\Gamma)$ and let $\avrc{u}(s)= \frac{1}{2\pi R} \int_0^{2\pi} u(s,\theta)R\, d\theta$.
-Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$.
+Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$ and there exists a constant $C_\Gamma$ such that
+\begin{equation*}
+\|\avrc{u}\|_{H^{\frac 12}(0,S)} \leq C_\Gamma \|u\|_{H^{\frac 12}(\Gamma)}.
+\end{equation*}
 \end{corollary}
 
-It is apparent that problems \eqref{eq:weak_dirneu} and \eqref{eq:red_dirneu} share the same mathematical structure.
-For this reason, the well-posedness of \eqref{eq:red_dirneu} can be studied in the framework of the classical theory of saddle point problems.
+\begin{corollary}
+Let $\Gamma$ be the lateral surface of a generalized cylinder, being $\DD(s)$ the boundary of the cross section and $\Lambda$ its centerline.
+Let $u\in H^{\frac 12}_{00}(\Gamma)$ and let $\avrc{u}(s)= \frac{1}{|\DD(s)|} \int_{\DD} u \,d\gamma$.
+Then $\avrc{u}\in H^{\frac 12}_{00}(\Lambda)$  and there exists a constant $C_\Gamma$ such that
+\begin{equation*}
+\|\avrc{u}\|_{H^{\frac 12}(\Lambda), |\DD|} \leq C_\Gamma \|u\|_{H^{\frac 12}(\Gamma)}.
+\end{equation*}
+\end{corollary}
+
+The well-posedness of $\eqref{eq:problem1}$ and $\eqref{eq:problem2}$ can be studied in the framework of the classical theory of saddle point problems as shown in the following.
+
+%It is apparent that problems \eqref{eq:weak_dirneu} and \eqref{eq:red_dirneu} share the same mathematical structure.
+%For this reason, the well-posedness of \eqref{eq:red_dirneu} can be studied in the framework of the classical theory of saddle point problems.
 

### 2020-01-09 lm3d1d_vs3/benchmark.tex
Paolo's revision sections 2-3

--- 2019-10-20 lm3d1d_vs1/3d1d_coupled_LM.tex
@@
-% SIAM Article Template
-\documentclass[r]{siamart171218}
-% Packages and macros go here
-\usepackage[english]{babel}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{array}
-\usepackage{graphicx}
-\usepackage{epsfig}
-\usepackage{float}
-\usepackage{fullpage}
-\usepackage{color}
-\usepackage{enumitem}  
-\usepackage{epstopdf}
-\usepackage{stmaryrd}
-
-% Title. If the supplement option is on, then "Supplementary Material"
-% is automatically inserted before the title.
-%\title{On the weak coupling of 3D and 1D second order elliptic problems}
-\title{Coupling PDEs on 3D-1D domains with Lagrange multipliers}
-
-% Authors: full names plus addresses.
-\author{Miroslav Kuchta, Federica Laurino, Kent-Andre Mardal, Paolo Zunino,\thanks{Authors are listed in alphabetical order}}
-
-\begin{document}
-
-\maketitle
-
-% REQUIRED
-\begin{abstract}
-These are personal notes written to keep track of the developments on this topic, to be kept confidential.
-\end{abstract}
-
-% REQUIRED
-\begin{keywords}
-elliptic problems, high dimensionality gap, essential coupling conditions, Lagrange multipliers
-\end{keywords}
-
-% REQUIRED
-\begin{AMS}
-n.a.
-\end{AMS}
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-
-% definitions here
-
-\def\ud{u_{\odot}}
-\def\udh{u_{\odot, h}}
-\def\vd{v_{\odot}}
-\def\uf{u_{\ominus}}
-\def\up{u_{\oplus}}
-\def\eps{\epsilon}
-\def\nn{\boldsymbol n}
-\def\rr{\boldsymbol r}
-\def\RR{\boldsymbol R}
-\def\kk{\boldsymbol k}
-\def\ss{\boldsymbol s}
-\def\uu{\boldsymbol u}
-\def\vv{\boldsymbol v}
-\def\xx{\boldsymbol x}
-\def\bu{\overline{u}}
-\def\bv{\overline{v}}
-\def\tu{\widetilde{u}}
-\def\tv{\widetilde{v}}
-\def\TT{\boldsymbol T}
-\def\NN{\boldsymbol N}
-\def\BB{\boldsymbol B}
-\def\ttu{\widetilde{\widetilde{u}}}
-\def\ttv{\widetilde{\widetilde{v}}}
-\def\cv{\check{v}}
-\def\mesh{{\cal T}^h}
-\def\ball{{\cal B}}
-\def\R{\mathbb{R}}
-\def\D{\mathcal{D}}
-\def\DD{\partial\mathcal{D}}
-\def\trace{\overline{\mathcal{R}}}
-\def\ext{\mathcal{E}}
-\def\ide{\mathcal{I}}
-\def\ii{\hat{\imath}}
-\newcommand{\avrd}[1]{\overline{\overline{#1}}}
-\newcommand{\avrc}[1]{\overline{#1}}
-\newcommand{\refe}[1]{{#1}_{\mathrm{ref}}}
-\newcommand{\norm}[1]{\lVert{#1}\rVert}
-
-\newcommand{\vertiii}[1]{{\left\vert\kern-0.25ex\left\vert\kern-0.25ex\left\vert #1 
-    \right\vert\kern-0.25ex\right\vert\kern-0.25ex\right\vert}}
-
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{prop}{Property}[section]
-\theoremstyle{remark}
-\newtheorem{remark}{Remark}[section]
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\section{Introduction}\label{sec:intro}
-
-We address the geometrical configuration of the problem for a 3D coupled problem formulation based on from Dirichlet-Neumann interface conditions.
-Then, we apply a model reduction technique that transforms the problem into 3D-1D coupled PDEs.
-We develop and analyze a robust definition of the coupling operators form a 3D domain, $\Omega$, to 1D manifold, $\Lambda$, and vice versa.
-This is a non trivial objective because the standard trace operator form a domain $\Omega$ to a subset $\Lambda$ is not well posed if $\Lambda$ is a manifold of co-dimension two of $\Omega$.
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\section{Problem setting}\label{sec:setting}
-
-Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set.
-Let $\Sigma$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Sigma}$ be the complementary set of the cylinder.
-We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Sigma$.
-We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$.
-We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Sigma$ and its boundary, respectively.
-In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach.
-We also assume that $\Sigma$ crosses $\Omega$ from side to side and we call $\Gamma$ the lateral (cylindrical) surface of $\Sigma$, while the upper and lower side faces of $\Sigma$ belong to $\partial\Omega$.
-We refer to Figure \ref{fig1} for an illustration of the notation.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.5\textwidth]{3D-1D-simple.png}
-\end{center}
-\caption{Geometrical setting of the problem}
-\label{fig1}
-\end{figure}
-
-We consider the problem arising from \emph{Dirichlet-Neumann} conditions. 
-It consists to find $\up,\uf$ s.t.:
-\begin{subequations}\label{eq:dirneu}
-\begin{align}
-\label{eq:dirneu1}
-- \Delta \up  + \up &= f  && \text{ in } \Omega_{\oplus},\\
-\label{eq:dirneu2}
-- \Delta \uf  + \uf &= g  && \text{ in } \Sigma,\\
-\label{eq:dirneu3}
--\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
-\label{eq:dirneu4}
-\uf &= \up && \text{ on }  \Gamma,\\
-\label{eq:dirneu5}
-\up &= 0 && \text{ on } \partial \Omega\,.
-\end{align}
-\end{subequations}
-
-The objective of this work is to derive and alalyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Sigma$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$.
-This new problem setting will be called the \emph{reduced} problem.
-Form the mathematical standpoint it is more challenging than \eqref{eq:dirneu}, because it involves the coupling of 3D/1D elliptic problems.
-For the model reduction process, we decompose integrals as follows, for any sufficiently regular function $w$,
-\begin{equation*}
-\int_\Sigma w d\omega 
-= \int_\Lambda \int_{\mathcal{D}} w d\sigma ds
-= \int_\Lambda |\mathcal{D}|\avrd{w} ds\,,
-\quad
-\int_{\Gamma} w d\sigma 
-= \int_\Lambda \int_{\partial\mathcal{D}} w d\gamma ds
-= \int_\Lambda  |\partial \mathcal{D}| \avrc{w} ds\,,
-\end{equation*}
-where $\avrd{w}, \ \avrc{w}$ denote the following mean values respectively,
-\begin{equation*}
-\avrd{w} = |\mathcal{D}|^{-1} \int_{\mathcal{D}} w d\sigma\,,
-\quad
-\avrc{w} = |\partial\mathcal{D}|^{-1} \int_{\partial\mathcal{D}} w d\gamma\,.
-\end{equation*}
-
-We apply the model reduction approach at the level of the variational formulation.
-We start from the variational formulation of problem \eqref{eq:dirneu}, 
-that is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Sigma\setminus\Gamma}(\Sigma), \ \lambda \in H^{-\frac12}(\partial\Sigma)$ s.t.
-\begin{subequations}\label{eq:weak_dirneu}
-\begin{align}
-&(u_\oplus,v_\oplus)_{H^1(\Omega_\oplus)} + (u_\ominus,v_\ominus)_{H^1(\Sigma)} 
-+ \langle v_\ominus - v_\oplus, \lambda \rangle_{H^{-\frac12}(\Gamma)} 
-\\
-\nonumber
-&\qquad\qquad = (f,v_\oplus)_{L^2(\Omega_\oplus)} + (g,v_\ominus)_{L^2(\Sigma)}
-\quad \forall v_\oplus \in H^1_{\partial\Omega}(\Omega_\oplus), \ v_\ominus \in H^1_{\partial\Sigma\setminus\Gamma}(\Sigma)
-\\
-& \langle u_\ominus - u_\oplus, \mu \rangle_{H^{-\frac12}(\Gamma)} = 0
-\quad \forall  \mu \in H^{-\frac12}(\Gamma)\,,
-\end{align}
-\end{subequations}
-where $\langle v, \mu \rangle_{H^{-\frac12}(\Gamma)}$ denotes the duality pairing between 
-$ \mu \in H^{-\frac12}(\Gamma)$ and $v \in H^{\frac12}(\Gamma)$.
-In this case, the additional variable $\lambda$ is equivalent to $\lambda  = - \nabla \uf \cdot \nn_\ominus$.
-
-Using the averaging tools for the model reduction approach, we end up with a reduced problem
-for the unknown $u$ defined on the entire 3D domain $\Omega$, coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$
-and a Lagrange multiplier $L$ defined on $\Lambda$. In the reduced problem the multiplier assumes the following interpretation,
-\begin{equation*}
-L = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \nabla \uf \cdot \nn_\ominus
-   = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \lambda \,.
-\end{equation*}
-
-We consider two alternative formulations. The scope of this work is to compare them, 
-with the aim to determine which is the most suitable as a computational model based on 3D-1D coupled PDEs.
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\subsection{Problem 1}
-The idea is to couple a 3D PDE with a 1D one, using a Lagrange multiplier space defined on a 2D surface that surrounds the 1D manifold.
-Let $\langle \cdot , \cdot \rangle_\Gamma$ denote the duality pairing between 
-$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$.
-The problem consists to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ L \in H^{-\frac12}(\Gamma )$, such that
-\begin{subequations}\label{eq:problem1}
-\begin{align}
-&(u,v)_{H^1(\Omega)} + |{\cal D}|(\ud,\vd)_{H^1(\Lambda)} 
-+ \langle \Pi_1 v  - \Pi_2 \vd, L \rangle_\Gamma
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
-\\
-&   \langle \Pi_1 u - \Pi_2 \ud , M \rangle_\Gamma = 0
-\quad \forall M \in H^{-\frac12}(\Gamma)\,.
-\end{align}
-\end{subequations}
-Here, $\Pi_1: H^1_0(\Omega) \rightarrow H^{\frac12}_{00}(\Gamma)$
-and $\Pi_2: H^1_0(\Lambda) \rightarrow H^{\frac12}_{00}(\Gamma)$
-and we remark that $\Sigma$ may be considered as a virtual surface
-not necessarily of the same size as the underlying physical structure that is modeled.  
-The $\Pi_1$ and $\Pi_2$ operators may be defined in terms of the averaging operators above, but may also be realized in terms of e.g.
-Green functions (I don't know if this is a good idea).
-Furthermore,  $\Gamma$ may be discretized in terms of facets neighboring $\Lambda$ and may as such not be represented as a separate structure in the implementation.
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\subsection{Problem 2}
-Another form of the reduced problem uses Lagrange multipliers defined directly on the 1D manifold.
-In this case, $\langle \cdot , \cdot \rangle_\Lambda$ denotes the duality pairing between 
-$H^\frac12_{00}(\Lambda)$ and $H^{-\frac12}(\Lambda)$.
-The problem requires to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ L \in H^{-\frac12}(\Lambda)$, such that
-\begin{subequations}\label{eq:problem2}
-\begin{align}
-&(u,v)_{H^1(\Omega)} + |{\cal D}|(\ud,\vd)_{H^1(\Lambda)} 
-+ |\partial {\cal D}| \langle \Pi_1 v - \Pi_2 \vd, L \rangle_{H^{-\frac12}(\Lambda)} 
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},V)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
-\\
-&  |\partial {\cal D}| \langle \Pi_1 u -  \Pi_2 \ud, M \rangle_{H^{-\frac12}(\Lambda)} = 0
-\quad \forall M \in H^{-\frac12}(\Lambda)\,.
-\end{align}
-\end{subequations}
-We notice that all the integrals of the reduced problem are well defined because $u,v \in H^1_0(\Omega)$, 
-$u,v|_{\Gamma} \in H^\frac12_{00}(\Gamma)$ and thus $\avrc{u},\avrc{v} \in H^\frac12_{00}(\Lambda)$.
-More precisely, $\Pi_1 : H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda$ such that
-$\Pi_1 u = \avrc{(u|_\Gamma)}$ is the combination between the trace on $\Gamma$ and the average on $\partial{\cal D}$.
-The operator $\Pi_2: H^1_0(\Lambda) \rightarrow H^\frac12_{00}(\Lambda)$ is the injection form $H^1_0(\Lambda)$ and $H^\frac12_{00}(\Lambda)$.
-It is apparent that problems \eqref{eq:weak_dirneu} and \eqref{eq:red_dirneu} share the same mathematical structure.
-For this reason, the well-posedness of \eqref{eq:red_dirneu} can be studied in the framework of the classical theory of saddle point problems.
-
-%Assuming now that 
-%$\Pi_1: H^1(\Omega) \rightarrow H^{\frac12}(\Gamma)$ or $\Pi_2: H^1(\Gamma) \rightarrow H^{\frac12}(\Gamma)$ are isomorphisms in the sense that 
-%\[
-%\| \Pi_1 \|_{L(H^1(\Omega), H^{\frac12}(\Gamma))} \le C \mbox{, } 
-%\| \Pi_1^{-1} \|_{L(H^{\frac12}(\Gamma), H^1(\Omega))} \le 1/c,  
-%\]
-%and 
-%\[
-%\| \Pi_2 \|_{L(H^1(\Omega), H^{\frac12}(\Gamma))} \le C \mbox{, } 
-%\| \Pi_2^{-1} \|_{L(H^{\frac12}(\Gamma), H^1(\Omega))} \le 1/c .   
-%\]
-%We obtain the inf-sup condition as follows. Assume that $\Pi_1$ is an isomorphism then  
-%we may show the inf-sup conditioning by letting $\Pi_1 \hat u = M $ and $ \hat \ud = 0$ (i.e., we need the lower bound only for one
-%of the operators).  
-%\begin{eqnarray}
-%\sup_{u,\ud}\frac{
-%\langle \Pi_1 u - \Pi_2 \ud , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
-%}{(|u|_1^2 + |\ud|_1^2)^{1/2}} 
-%\ge \\ 
-%\frac{ \langle \Pi_1 \hat u - \Pi_2 \hat \ud , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
-%}{(|\hat u|_1^2 + |\hat \ud|_1^2)^{1/2}}  \ge \\
-%\frac{ \langle M , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
-%}{|\Pi_1^{-1} M |_{H^1(\Omega})} \ge \\ 
-%\frac{ \langle M , M \rangle_{(H^{\frac12}(\Gamma), H^{-\frac12}(\Gamma))} 
-%}{| M |_{H^\frac12(\Gamma)}} \ge \\ 
-%c | M |_{H^{-\frac12}(\Gamma)}  
-%\end{eqnarray}
-%I think the other Brezzi conditions also follows, but for the boundedness we
-%would need that both $\Pi_1$ and $\Pi_2$ are bounded. Not sure I am 
-%happy with the $\langle \cdot, \cdot \rangle$ notation and in particular not when we spesify the
-%spaces. I would rather just say that $(\cdot, \cdot)$ denotes both the $L_2$ inner product and the
-%duality pairing.  
-%If we find it useful we may also  
-%consider $\Pi_2: H^1(\Gamma) \rightarrow X(\Gamma)$ where $X$ may e.g. be $H^1$.  
-%If so, $L, M$ in $ H^{-\frac12}(\Gamma) \cap X(\Gamma)$
-
-\input{infsup}
-
-\input{infsup_discrete}
-
 \section{A benchmark problem with analytical solution}
@@
 &\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda).
+\quad \forall v \in H^1_0(\Omega), \vd \in H^1(\Lambda).
 \\
 \end{align*}
-Since $L=\avrc{\lambda}=0$ and \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d}
+Since $\ld=\avrc{\lambda}=0$ and \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d}
 satisfies \eqref{benchm_1d}, we have that
@@
   \begin{center}
-    \includegraphics[width=0.5\textwidth]{./conform_mesh.pdf}
+    \includegraphics[width=0.5\textwidth]{./graphics/conform_mesh.pdf}
     \caption{$\Lambda$ and $\Gamma$ conforming discretization of $\Omega$
-      used for \eqref{eq:problem1_simple}. For \eqref{eq:problem2_simple}
-      only conformity to $\Lambda$ is needed.
+      used for \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}.
     }
@@
 here prevents the use direct solvers. Therefore iterative solvers were necessary.
+We plot the numerical solution of problem \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} in
+Figure \ref{fig:sol_benchm1} and \ref{fig:sol_benchm2}, respectively.
+
+\begin{figure}
+\centering
+\includegraphics[width = 0.9\textwidth]{./graphics/mfs_LM2d}
+\caption{Numerical solution of problem \eqref{eq:problem1_simple}: functions $u_h$ and $\udh$ on the left and the Lagrance multiplier $\lambda_h$ on the right.}\label{fig:sol_benchm1}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width = 0.9\textwidth]{./graphics/mfs_LM1d}
+\caption{Numerical solution of problem \eqref{eq:problem2_simple}: functions $u_h$ and $\udh$ on the left and the Lagrance multiplier ${\ld}_h$ on the right.}\label{fig:sol_benchm2}
+\end{figure}
 
@@
 
-\textbf{Some plots of the solutions}
+{\color{red}
+\begin{remark} In the following some observations:\\
 
-%\eqref{benchm_sol3d}-\eqref{benchm_sol1d}
+\begin{itemize}
+\item \textbf{How do we compute the norm $\|\cdot \|_{H^{-\frac 12}}$ in Table \ref{tab:error_conform}?} The norm $\|\cdot \|_{H^{-\frac 12}}$ has been computed using a decomposition based on eigenvalues and eigenfuctions of $\Delta ^{-\frac 12}$.\\
 
-%% \begin{remark}
-%% Let us notice that the 3D solution \eqref{benchm_sol3d} is such that $\avrc{u}=0$.
-Therefore in \eqref{benchmark} it is like we are solving two separated problems, one in $\Omega$ and the other on $\Lambda$.
-%% \end{remark}
-%% \begin{remark}
-%% It would be interesting to make a comparison between the solution of the fully coupled 3D-3D problem \eqref{eq:dirneu} (also in the simplified case of type \eqref{eq:dirneu_simple}) and the solution of the reduced problems \eqref{eq:problem1} and \eqref{eq:problem2}.
-%% Therefore, we could set the values of the data of the problem such that the reduced formulation becomes non-trivial and fully coupled.
-%% Then, we will solve both the original and reduced problem to observe the differences in the solutions and the values of the Lagrange multiplier.
-%% \end{remark}
+\item \textbf{Why $\lambda _h \neq \lambda$?} Since $\lambda = 0 \in Q_h$, we would expect $\lambda _h = \lambda$.
+However, first of all we suspect that for the approximation error an estimate similar to \cite[(11.26)]{steinbach2007numerical} holds, reported in the following
+\begin{equation*}
+\|u-u_h\|^2_{H^1} + \|\lambda - \lambda_h\|^2_{H^{-\frac 12}} \leq c_1 h^2|u|^2_{H^2} + c_2 h^3\|\lambda_h\|^2_{H^1_{pw}},
+\end{equation*}
+where $\|\cdot \|_{H^1_{pw}}$ is the broken $H^1$ norm. 
+So the error on the LM depends on the error on the solution.
+We suspect that if for example $u$ and $\ud$ are $P_2$ functions and we use a $P_2$ approximation (therefore $u = u_h$ and $\ud = \udh$), also $\lambda = \lambda_h$.\\
 
-\input{unfitted}
-%-----------------
-\bibliographystyle{siamplain}
-\bibliography{3d1d_coupled}
-\end{document}
+\item \textbf{Why the error is larger close to edges, especially in Figure \ref{fig:sol_benchm1}?} 
+We suspect that the reasoning for why the error is larger close to edges and corner vertices is that the multiplier is
+related to $\nabla u \cdot \boldsymbol{n}$ and the normal in the corner or on the z-aligned edges in the figure is not well-defined. Btw, the oscillations are smaller if we impose Neumann
+bcs on z min and max surfaces of $\Omega$ (the rest has Dirichlet).
+\end{itemize}
+\end{remark}
+}

### 2020-01-09 lm3d1d_vs3/infsup_discrete_conformingLM.tex
Paolo's revision sections 2-3

--- 2019-07-08 infsup_discrete_conformingLM.tex
@@
 \section{Finite element approximation}
+In this section we consider the discretization of Problem 1 and 2 by means of the finite element method.
+We address two main challenges; first we aim to identify a suitable approximation space for the Lagrange multiplier and to analyze the stability of the discrete saddle point problem; second we aim to derive a stable discretization method that uses indepent and conforming computational meshes for $\Omega$, $\Gamma$ and $\Lambda$.
+Let us introduce a shape-regular triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{h}$ of $\Lambda$.
+We analyze two different cases: the one in which the 3D mesh is conforming to the interface $\Gamma$, namely the set of the intersections of the 3D elements of $\mathcal{T}^{\Omega}_h$ with $\Gamma$ is constituted by facets of such elements, and the non conforming case, namely the interface $\Gamma$ cuts the mesh arbitrarly.
 The discrete equivalent of \eqref{eq:saddle-point} reads as finding $u_h\in X_h\subset X$, $\lambda_h\in Q_h\subset Q$ s.t.
@@
 
-\begin{corollary}{\cite[Theorem 2.42]{MR2050138}}
+\begin{corollary}{\cite[Theorem 2.42]{MR2050138}}Let $a(\cdot, \cdot)$ and $b(\cdot, \cdot)$ be continuous bilinear forms. 
 Problem \eqref{eq:saddle-point_discrete} is well-posed if and only if 
@@
 
-Let us introduce a shape-regular triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{h}$ of $\Lambda$. 
-We analyze two different cases: the one in which the 3D mesh is conforming to the interface $\Gamma$, namely the set of the intersections of the 3D elements of $\mathcal{T}^{\Omega}_h$ with $\Gamma$ is constituted by facets of such elements, and the non conforming case, namely the interface $\Gamma$ cuts the mesh arbitrarly.
-
 \subsection{$\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}
@@
 More precisely we require that the intersection of $\mathcal{T}^{\Omega}_h$ and $\Gamma$ is made of entire faces of elemets $K \in \mathcal{T}^{\Omega}_h$.
-Furthermore we also set a restriction between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$.
-We want that the intersection of $\Gamma$ with any orthogonal plane to $\Lambda$ that crosses $\Lambda$ at the nodes of $\mathcal{T}^{\Lambda}_h$, consists of entire edges of $\mathcal{T}^{\Omega}_h$.
+Furthermore, we also set a restriction between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$.
+We assume that $\Lambda$ is a piecewise linear manifold.
+We want that the intersection of $\Gamma$ with any orthogonal plane to $\Lambda$ that crosses $\Lambda$ at the internal nodes of $\mathcal{T}^{\Lambda}_h$, consists of entire edges of $\mathcal{T}^{\Omega}_h$.
 Namely the intersection of $\Gamma$ with orthogonal planes to $\Lambda$ is conformal with $\mathcal{T}^{\Lambda}_h$.
@@
 The space $Q_h$ must be suitably chosen such that \eqref{eq:infsup_discrete} holds.
-Let us denote with $W_{h,0}^k(\Gamma) \subset H^{\frac 12}_{00}(\Gamma)$ the trace space of functions running in $X_{h,0}^k(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$.
-We choose $Q_h=W_{h,0}^k(\Gamma)$, therefore we impose homogeneous Dirichlet boundary condition on $\partial \Omega$ also for the Lagrange multiplier.
+Let $Q_h$ be the trace space of functions running in $X_{h,0}^k(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$.As a result, $Q_h=X_{h,0}^k(\Gamma)$.
+Therefore we impose homogeneous Dirichlet boundary condition on $\partial \Omega$ also for the Lagrange multiplier.
 For this choice of $Q_h$ we can prove the well-posedness of the discrete problem, as shown in the following.
@@
 \end{equation*}
-Let $R_h: H^1_0(\Omega) \rightarrow X_{h,0}^k(\Omega)$ be a quasi interpolation operator satisfying 
+Let $R_h: H^1_0(\Omega) \rightarrow X_{h,0}^k(\Omega)$ be a quasi interpolation operator (such as the Scott-Zhang operator) satisfying 
 \begin{equation*}
@@
 and we have
-\begin{multline}
+\begin{multline}\label{eq_conformity}
 \gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)} 
@@
 Therefore the inf-sup condition $\eqref{inf_sup_discrete_prob1}$ holds with $\beta_{h,1} = \gamma \|\mathcal{E}_{\Omega}\|^{-1} C_R^{-1} $.
+We notice that in \eqref{eq_conformity} we exploit the fact that the operator $\trace R_h  \mathcal{E}_{\Omega}$ coincides with the identity on the space $Q_h$, thanks to the conformity of $\mathcal{T}^{\Omega}_h$ to the interface $\Gamma$.
 \end{proof}
 
-\begin{remark} We notice that to prove the result in Lemma \ref{lemma:trspace_infsup} (and then the discrete inf-sup condition)  basically we need a projection operator $P_h: H^{\frac 12}_{00} \longrightarrow W_{h,0}^k(\Gamma)$ orthogonal in the multiplier space $Q_h$, namely such that $\langle P_h v, \mu_h \rangle = \langle v, \mu_h \rangle, \, \forall \mu_h \in Q_h$, and continuous in $H^{\frac 12}(\Gamma)$.
+%\begin{remark} We notice that to prove the result in Lemma \ref{lemma:trspace_infsup} (and then the discrete inf-sup condition)  basically we need a projection operator $P_h: H^{\frac 12}_{00} \longrightarrow W_{h,0}^k(\Gamma)$ orthogonal in the multiplier space $Q_h$, namely such that $\langle P_h v, \mu_h \rangle = \langle v, \mu_h \rangle, \, \forall \mu_h \in Q_h$, and continuous in $H^{\frac 12}(\Gamma)$.
 Therefore, in principle different choices than $Q_h=W_{h,0}^k(\Gamma)$ could be considered if we can build an operator $P_h$ satisfying these properties.
 In \cite{belgacem1999mortar} such operator $P_h$  is built for a particular choice of $Q_h$ but it is not clear how to prove the $H^1$-stability inequality (and consequently the $H^{\frac 12 }$-stability) with a constant independent of the mesh size $h$.
-\end{remark}
+%\end{remark}
 
@@
 
-We introduce the space
-$W_{h,0}^k(\Lambda) \subset H^{\frac 12} _{00} (\Lambda)$, which is the averaged trace space of functions running in $H^1_0(\Omega)$.
-It coincides with the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$ and satisfying homogeneous Dirichlet boundary condition.
-We choose $Q_h=W_{h,0}^k(\Lambda)$, therefore we impose homogeneous Dirichlet boundary condition on $\Lambda \cap \partial \Omega$ also for the Lagrange multiplier.
+%We introduce the space
+%$W_{h,0}^k(\Lambda) \subset H^{\frac 12} _{00} (\Lambda)$, which is the averaged trace space of functions running in $X_{h,0}^k(\Omega)$.
+It coincides with the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$ and satisfying homogeneous Dirichlet boundary condition, namely $X_{h,0}^k(\Lambda)$.
+We choose $Q_h=X_{h,0}^k(\Lambda)$, therefore we impose homogeneous Dirichlet boundary condition on $\Lambda \cap \partial \Omega$ also for the Lagrange multiplier.
 With this choice for $Q_h$, we can prove the well-posedness of the discrete problem.
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma:prob1_orthproj}
 Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
@@
 \end{lemma}
-
+The proofs are equivalent ot the ones of Lemmas \ref{lemma:prob1_orthproj} and \ref{lemma:trspace_infsup}.
 \begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds, namely 
@@
 \begin{multline}
-\gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \leq 
-\sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} 
+\gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \leq 
+\sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} 
 \\
-=  \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|\ext q_h\|_{H^{\frac 12}(\Gamma)}} 
-\leq \|\mathcal{E}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|\mathcal{E}_{\Omega} \ext q_h\|_{H^1(\Omega)}} 
+=  \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda,|\DD|}} {\|\ext q_h\|_{H^{\frac 12}(\Gamma)}} 
+\leq \|\mathcal{E}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\|\mathcal{E}_{\Omega} \ext q_h\|_{H^1(\Omega)}} 
 \\
-\leq \|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|R_h \mathcal{E}_{\Omega} \ext q_h\|_{H^1(\Omega)}}
+\leq \|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\|R_h \mathcal{E}_{\Omega} \ext q_h\|_{H^1(\Omega)}}
 \\ 
-=  \|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle 	\mtrace R_h \mathcal{E}_{\Omega} \ext q_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|R_h \mathcal{E}_{\Omega} \ext w_h\|_{H^1(\Omega)}}
+=  \|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle 	\mtrace R_h \mathcal{E}_{\Omega} \ext q_h, {\md}_h \rangle _{\Lambda,|\DD|}} {\|R_h \mathcal{E}_{\Omega} \ext w_h\|_{H^1(\Omega)}}
 \\
-\leq \|\mathcal{E}_{\Omega}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \mtrace v_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|v_h\|_{H^1(\Omega)}}. 
+\leq \|\mathcal{E}_{\Omega}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \mtrace v_h, {\md}_h \rangle _{\Lambda,|\DD|}} {\|v_h\|_{H^1(\Omega)}}. 
 \end{multline}
-
+Also in this case to prove the disrete inf-sup condition we exploit the conformity of the meshes on $\Omega$, $\Gamma$ and $\Lambda$ and the fact that the operator $\mtrace R_h \mathcal{E}_{\Omega} \ext$ coincides with the identity if applied to functions in $Q_h$.
 \end{proof}

### 2020-02-28 3d1d_coupled_LM.tex
Updates from Overleaf

@@
 
+\newcommand{\kent}[1]{{\color{blue}#1}}
 \newcommand{\miro}[1]{{\color{cyan}#1}}
@@
 
-We address the geometrical configuration of the problem for a 3D coupled problem formulation based on from Dirichlet-Neumann interface conditions.
+In this paper we will consider a 3D-1D coupled problem described by the following equations: 
+\begin{subequations}
+\label{eq:pde}
+\begin{align}
+\label{eq:pde1}
+  -\Delta u + u + \lambda \delta_{\Lambda} &= f &\mbox{ in } \Omega,\\
+\label{eq:pde2}
+-\Delta \ud + \ud - \lambda &= g &\mbox{ on } \Lambda,\\
+\label{eq:coupling}
+T_\Lambda u - v  &=  h &\mbox{ on } \Lambda . 
+\end{align}
+\end{subequations}
+Here, $u$ and $\ud$ are the unknown scalar fields,  $\lambda$ is the Lagrange multiplier,  $\Omega$ is a bounded domain in $\R^3$, whereas $\Lambda \subset \Omega$ is a 1D structure. 
+The term $p\delta_{\Lambda}$ is a Dirac measure such that 
+$\int_{\Omega}p(x)\delta_{\Lambda}v(x)\,\mathrm{d}x=\int_{\Lambda}p(t)v(t) \,\mathrm{d}t$
+for a continuous function $v$.
+
+From a mathematical point of view, the challenge involved in problem \eqref{eq:pde} is that neither $T_\Lambda$ nor $\delta_\Lambda$ are well defined.
+That is, traces of co-dimension one are well defined, while here we face traces of co-dimension two, mapping 3D functions to 1D functions.
+Similarly, Dirac delta functions are well defined on measures of one lower dimension, but not two.
+Several studies \cite{DAngelo,..} have remedied the well-posedness by weakening the solution concept.
+The approach naturally leads to non-symmetric formulations.
+An alternative approach is to decompose the solution into smooth and non-smooth components, where the non-smooth component may be represented in terms of Greens functions, and then consider the well-posedness of the smooth component~\cite{Peaceman1983531,secomb2004green}.
+Both of these approaches have successfully be analyzed in a discrete setting and implemented~\cite{}.
+
+The mathematical problem is motivated by the fact that many problems in geophysics and bio-mechanics are characterized by slender cylindrical structures coupled to larger 3D body, where the characteristic transverse length scale of the slender structure is many orders of magnitude smaller than the longitudinal length scale.
+For example, in geophysical applications the radius of wells are often of the order of 10 cm while the length may be several kilometers~\cite{gjerde2019singularity}.
+Similarly, in applications involving the blood flow and oxygen transport of the micro-circulation the capillary radius is a few microns, while simulations are often performed on mm to cm scale, with thousands of vessels~\cite{berg2020modelling,fang2008oxygen,gould2017capillary}.
+Finally, in neuro-science applications a neuron has with a few microns, while  its length is much longer.
+For examples motor neurons may be as long as a meter.
+Hence,  at least 4 orders of magnitude in difference in transverse and longitudinal direction is common in both geo-physics, bio-mechanics and neuro-science.
+Meshes dictated by resolving the transverse length scale in 3D would then possibly lead to the order of $10^{12}$ degrees of freedom.
+Even if adaptive and strongly anisotropic meshes are allowed for, the computations quickly become demanding if many slender structures and their interactions are under study.
+If the quantity of interest is the far field impact caused by processes in the slender structures, the high resolution involved in the near field of the slender structure may not be needed.
+
+In this work we propose to analyze the problem in terms of an intermediate problem, posed either explicitly or implicitly. The intermediate problem reads, 
+\begin{subequations}
+\label{inteq:pde}
+\begin{align}
+\label{inteq:pde1}
+  -\Delta u + u + \lambda \delta_{\Lambda} &= f &\mbox{ in } \Omega,\\
+\label{inteq:pde2}
+-\Delta \ud + \ud - E' \lambda  &= g &\mbox{ on } \Lambda,\\
+\label{inteq:coupling}
+T_\Gamma u - E_\Gamma v  &=  h &\mbox{ on } \Gamma
+\end{align}
+\end{subequations}
+where $\Gamma \subset \Omega$ is a 2D surface corresponding to $\Lambda$
+and $E$ is an extension operator from $\Lambda$ to $\Gamma$. 
+\kent{check consistency with notation}
+
+Detail the approach and result a bit.
+\kent{either here or later, something like the below}
+The setting of this paper is quite
+similar to~\cite{laurino_m2an}, but for completeness and the readers convenience we repeat some basic derivations.
+
+%We address the geometrical configuration of the problem for a 3D coupled problem formulation based on from Dirichlet-Neumann interface conditions.
 Then, we apply a model reduction technique that transforms the problem into 3D-1D coupled PDEs.
@@
 % >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\section{Problem setting}\label{sec:setting}
+\section{Preliminaries}\label{sec:setting}
 
-In this section we fist provide the main notation and definitions to set up the problem.
-In particular, we address the geometry of the domain, which is equivalent to the one addressed in previous works of the authors \cite{laurino_m2an},
-and we define the functional spaces and related operators necessary for a rigorous problem formulation and analysis.
-Finally, the section ends with the formal derivation of the problem, 
-based on averaging techniques applied to a fully three-dimensional model in the geometrical setting defined before.
+%In this preliminary section we fist provide the main notation and definitions to set up the problem.
+%In particular, we address the geometry of the domain, which is equivalent to the one addressed in previous works of the authors \cite{laurino_m2an},
+%and we define the functional spaces and related operators necessary for a rigorous problem formulation and analysis.
+%Finally, the section ends with the formal derivation of the problem, 
+%based on averaging techniques applied to a fully three-dimensional model in the geometrical setting defined before.
 
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\subsection{Geometry of the problem}
-The domain is denoted as $\Omega$ is convex and composed by two parts, 
+%\subsection{Geometry of the problem}
+The domain is denoted as $\Omega\in \RR^3 $ is convex and composed by two parts, 
 $\Omega_{\ominus}$ and $\Omega_{\oplus}:=\Omega\setminus\overline{\Omega}_{\ominus}$. 
@@
 We refer to Figure \ref{fig1} for a sketch of the domains.
+Let $\mathcal{D}(s) = [x(r,t),y(r,t)]: (0,R(s))\times(0,T(s)) \rightarrow \R^2$ be a parametrization of the cross section, while 
+$|\cdot|$ denote the Lebesgue measure of a set, i.e. $|D(0)|$ is the cross-sectional area of the bottom of the cylinder.
 
-Let $\TT,\NN,\BB$ be the Frenet frame related to the curve.
-Let $\mathcal{D}(s) = [x(r,t),y(r,t)]: (0,R(s))\times(0,T(s)) \rightarrow \R^2$ be a parametrization of the cross section.
-Let us assume that $\mathcal{D}(s)$ is convex for any $s \in (0,S)$. The cross section can change size along $\Lambda$ but not shape.
-Let us also parametrize the boundary of the cross section as $\partial\mathcal{D}(s) = [\partial x(r,t),\partial y(r,t)]: (0,R(s))\times(0,T(s)) \rightarrow \R^2$,
-and let us assume that $\partial\mathcal{D}(s)$ is a piecewise $\mathcal{C}^2$-regular curve.
-Then, the generalized cylinder $\Omega_{\ominus}$ can be defined as follows
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.5\textwidth]{domain.pdf}
+\end{center}
+\caption{Geometrical setting of the problem}
+\label{fig1}
+\end{figure}
+
+%Let $\TT,\NN,\BB$ be the Frenet frame related to the curve.
+%Let $\mathcal{D}(s) = [x(r,t),y(r,t)]: (0,R(s))\times(0,T(s)) \rightarrow \R^2$ be a parametrization of the cross section.
+%Let us assume that $\mathcal{D}(s)$ is convex for any $s \in (0,S)$. The cross section can change size along $\Lambda$ but not shape.
+%Let us also parametrize the boundary of the cross section as $\partial\mathcal{D}(s) = [\partial %x(r,t),\partial y(r,t)]: (0,R(s))\times(0,T(s)) %\rightarrow \R^2$,
+%and let us assume that $\partial\mathcal{D}(s)$ is a %piecewise $\mathcal{C}^2$-regular curve.
+%Then, the generalized cylinder $\Omega_{\ominus}$ %can be defined as follows
+%\begin{equation*}
+%\Omega_{\ominus} = \{ \boldsymbol \lambda(s) + %x(r,t) \NN(s) + y(r,t) \BB(s), \ r \in (0,R(s)),\ s %\in (0,S), \ t \in (0,T(s))\}\,,
+%\end{equation*}
+%and the lateral boundary is
+%\begin{equation*}
+%\Gamma = \{ \boldsymbol \lambda(s) + \partial x(r,t) %\NN(s) + \partial y(r,t) \BB(s), \ r \in (0,R(s)),\ %s \in (0,S), \ t \in (0,T(s))\}\,.
+%\end{equation*}
+%Let $|\cdot|$ denote the Lebesgue measure of a set. %If $|\mathcal{D}(0)|, \ |\mathcal{D}(S)| >0$ then %$\Omega_{\ominus}$ has \emph{top} and \emph{bottom} %boundaries,
+%which belong to $\partial\Omega$.
+
+This work is based on the assumption that \emph{the transversal diameter of $\Omega_{\ominus}$ is small compared to the diameter of $\Omega$}. 
+Let $d= \max_{s \in (0,S)} \mathrm{diam}(\D(s))$ be the largest diameter of the cross sections of $\Omega_{\ominus}$, that is the transversal diameter of $\Omega_{\ominus}$.
+The central assumption of this work is that $d \ll \mathrm{diam}(\Omega)$.
+Let us now scale the domains $\Omega$ and $\Omega_{\ominus}$.
+Let $\chi_{\Omega}(\xx) = \xx / \mathrm{diam}(\Omega)$ be a scaling function and let be $\Omega_\chi = \chi_{\Omega}(\Omega), \ {\Omega_{\ominus}}_\chi =  \chi_{\Omega}(\Omega_{\ominus})$ be the scaled domains.
+The previous assumption implies that for the scaled domains $\epsilon = d_\chi = d/\mathrm{diam}(\Omega)$
+is such that $0 < \epsilon \ll 1$. For simplicity of notation, and without loss of generality, form now on we will implicitly refer to the scaled domains dropping the subindex $\chi$.
+\kent{this is a good explanatory paragraph, but not sure we use the notation introduced}
+
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+%\subsection{Functional setting and preliminary results}
+
+Let $D$ be a generic regular bounded domain in $\R^3$. 
+Let $X$ be a Hilbert space defined on $D$.
+Let $(\cdot,\cdot)_X$ denote the inner product of $X$.
+Let $(\cdot,\cdot)_L^2(D)$,  $(\cdot,\cdot)_D$ or simply $(\cdot,\cdot)$ be the $L^2(D)$ inner product on $D$.
+For the 1D domain $\Lambda$ we will frequently use
+weighted $L^2$ inner products, denoted as follows
 \begin{equation*}
-\Omega_{\ominus} = \{ \boldsymbol \lambda(s) + x(r,t) \NN(s) + y(r,t) \BB(s), \ r \in (0,R(s)),\ s \in (0,S), \ t \in (0,T(s))\}\,,
+(\ud,\vd)_{\Lambda,w} = \int_0^S w(s) \ud(s) \vd(s) ds\,.
 \end{equation*}
-and the lateral boundary is
-\begin{equation*}
-\Gamma = \{ \boldsymbol \lambda(s) + \partial x(r,t) \NN(s) + \partial y(r,t) \BB(s), \ r \in (0,R(s)),\ s \in (0,S), \ t \in (0,T(s))\}\,.
-\end{equation*}
-Let $|\cdot|$ denote the Lebesgue measure of a set. If $|\mathcal{D}(0)|, \ |\mathcal{D}(S)| >0$ then $\Omega_{\ominus}$ has \emph{top} and \emph{bottom} boundaries,
-which belong to $\partial\Omega$.
+Given an Hilbert space $X$ and its dual $X^*$, the duality pairing between the two is denoted as $\langle\cdot,\cdot\rangle$.
+When needed, the integration weights will be also applied to the duality product.
+\kent{I think we use weighted H1 as well.}
 
-Thanks to the  geometrical structure of the generalized cylinder, 
+We will use the standard notation $H^q(D)$ to denote the Sobolev space of functions on $D$ with all derivatives up to the order $q$ in $L^2(D)$.
+The corresponding norm is $\|\cdot\|_{H^q(D)}$ and the seminorm is $\vert\cdot\vert_{H^q(D)}$.
+The space $H^q_0(D)$ represents the closure in $H^q(D)$ of smooth functions with compact support in $D$.
+
+Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. 
+We denote with $\mathcal{T}: H^q(D) \rightarrow H^{q-\frac12}(\Sigma)$ the trace operator from $D$ to $\Sigma$.
+For the purpose of this work we will extensively use traces on $\Gamma$ of functions defined on $\Omega$. Such operator will be denoted with $\trace$. 
+Fractional Sobolev spaces arising from the application of the trace operator are particularly important in this work.
+For example the trace space on $\Gamma$ of $H^1_0(\Omega)$ will be be extensively used for this study.
+We denote this space as $H^{\frac12}_{00}(\Gamma) = \trace H^1_0(\Omega)$.
+It can be interpreted as the subspace of $H^{\frac12}(\Gamma)$ of functions with continuous extension by zero outside $\Gamma$.
+We remark that $(H^{\frac12}_{00}(D))^* = H^{-\frac12}(D)$ with $D=\Gamma,\Lambda$.
+
+Due to the  geometrical structure of the generalized cylinder, 
 for any sufficiently regular function $w$ we decompose integrals as follows
@@
 
-This work is based on the assumption that \emph{the transversal diameter of $\Omega_{\ominus}$ is small compared to the diameter of $\Omega$}. 
-Let $d= \max_{s \in (0,S)} \mathrm{diam}(\D(s))$ be the largest diameter of the cross sections of $\Omega_{\ominus}$, that is the transversal diameter of $\Omega_{\ominus}$.
-The central assumption of this work is that $d \ll \mathrm{diam}(\Omega)$.
-Let us now scale the domains $\Omega$ and $\Omega_{\ominus}$.
-Let $\chi_{\Omega}(\xx) = \xx / \mathrm{diam}(\Omega)$ be a scaling function and let be $\Omega_\chi = \chi_{\Omega}(\Omega), \ {\Omega_{\ominus}}_\chi =  \chi_{\Omega}(\Omega_{\ominus})$ be the scaled domains.
-The previous assumption implies that for the scaled domains $\epsilon = d_\chi = d/\mathrm{diam}(\Omega)$
-is such that $0 < \epsilon \ll 1$. For simplicity of notation, and without loss of generality, form now on we will implicitly refer to the scaled domains dropping the subindex $\chi$.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.5\textwidth]{3D-1D-simple.png}
-\end{center}
-\caption{Geometrical setting of the problem}
-\label{fig1}
-\end{figure}
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\subsection{Functional setting and preliminary results}
-
-Let $D$ be a generic regular bounded domain in $\R^3$. 
-Let $X$ be a Hilbert space defined on $D$.
-Let $(\cdot,\cdot)_X$ denote the inner product of $X$.
-Let $(\cdot,\cdot)_L^2(D)$,  $(\cdot,\cdot)_D$ or simply $(\cdot,\cdot)$ be the $L^2(D)$ inner product on $D$.
-For the domain $\Lambda$ we will use the following notation for the weighted inner product,
-\begin{equation*}
-(\ud,\vd)_{\Lambda,w} = \int_0^S w(s) \ud(s) \vd(s) ds\,.
-\end{equation*}
-Given an Hilbert space $X$ and its dual $X^*$, the duality pairing between the two is denoted as $\langle\cdot,\cdot\rangle$.
-When needed, the integration weights will be also applied to the duality product.
-
-We will use the standard notation $H^q(D)$ to denote the Sobolev space of functions on $D$ with all derivatives up to the order $q$ in $L^2(D)$.
-The corresponding norm is $\|\cdot\|_{H^q(D)}$ and the seminorm is $\vert\cdot\vert_{H^q(D)}$.
-The space $H^q_0(D)$ represents the closure in $H^q(D)$ of smooth functions with compact support in $D$.
-
-Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. 
-We denote with $\mathcal{T}: H^q(D) \rightarrow H^{q-\frac12}(\Sigma)$ the trace operator from $D$ to $\Sigma$.
-For the purpose of this work we will extensively use traces on $\Gamma$ of functions defined on $\Omega$. Such operator will be denoted with $\trace$. 
 The operator obtained form the combination of the average operator $\avrc{(\cdot)}$ with the trace on $\Gamma$ will be denoted with $\mtrace = \avrc{(\cdot)} \circ \trace$,
 as it maps functions on $\Omega$ to functions on $\Lambda$.
-
-Fractional Sobolev spaces arising from the application of the trace operator are particularly important in this work.
-For example the trace space on $\Gamma$ of $H^1_0(\Omega)$ will be be extensively used for this study.
-We denote this space as $H^{\frac12}_{00}(\Gamma) = \trace H^1_0(\Omega)$.
-It can be interpreted as the subspace of $H^{\frac12}(\Gamma)$ of functions with continuous extension by zero outside $\Gamma$.
-We remark that $(H^{\frac12}_{00}(D))^* = H^{-\frac12}(D)$ with $D=\Gamma,\Lambda$.
 We will see later that functions belonging to $H^{\frac12}_{00}(\Lambda)$ are generated from the application of $\mtrace$ to $H^1_0(\Omega)$.
@@
 % >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\subsection{Topological model reduction}
+
 \subsection{Problem formulation}
@@
 
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\subsection{Topological model reduction}
 \subsubsection*{Model reduction of the problem on $\Omega_{\ominus}$}

### 2020-02-28 infsup.tex
typos
Discrete inf-sup same mesh for sol and mult
Updates from Overleaf

@@
 Substituting in the previous inequalities we obtain
-\begin{equation*}
+\begin{equation}\label{infsup_traceop}
 \sup _{v\in H^1_0(\Omega)} \frac{ \langle \Pi_1 v, M \rangle_\Gamma}{\|v\|_{H^1(\Omega)}}
@@
 = \|E\|^{-1} \|M\|_{H^{-\frac 12}(\Gamma)},
-\end{equation*}
+\end{equation}
 where in the last inequality we exploited the fact that $H^{-\frac 12}(\Gamma)=(H^{\frac 12 }_{00}(\Gamma))^*$.
@@
 \begin{equation*}
-\sup _{v\in H^1_0(\Omega),\, V \in H^1_0(\Lambda)} \frac{ \langle  \Pi_1 V - \Pi_2 v, M \rangle_\Lambda}{\sqrt{\|v\|^2_{H^1(\Omega)}+\|V \|^2_{H^1(\Lambda)}}}
+\sup _{v\in H^1_0(\Omega),\, V \in H^1_0(\Lambda)} \frac{ \langle  \Pi_1 V - \Pi_2 v, M \rangle_\Lambda}{\sqrt{\|v\|^2_{H^1(\Omega)}+|\D| \|V \|^2_{H^1(\Lambda)}}}
 \geq \beta \sup_{q\in H^{\frac 12}(\Lambda)}\frac{\langle q, M\rangle_\Lambda}{\|q\|_{H^{\frac 12}(\Lambda)}}.
@@
 \begin{equation*}
-\sup _{v\in H^1_0(\Omega),\, V \in H^1_0(\Lambda)} \frac{ \langle  \Pi_1 V - \Pi_2 v, M \rangle_\Lambda}{\sqrt{\|v\|^2_{H^1(\Omega)}+\|V \|^2_{H^1(\Lambda)}}}
+\sup _{v\in H^1_0(\Omega),\, V \in H^1_0(\Lambda)} \frac{ \langle  \Pi_1 V - \Pi_2 v, M \rangle_\Lambda}{\sqrt{\|v\|^2_{H^1(\Omega)}+|\D|\|V \|^2_{H^1(\Lambda)}}}
 \geq \sup _{v\in H^1_0(\Omega)} \frac{ \langle \Pi_2 v, M \rangle_\Lambda}{\|v\|_{H^1(\Omega)}}. 

### 2020-02-28 infsup_discrete_coarserLM.tex
Updates from Overleaf

--- 2019-03-05 infsup_discrete.tex
@@
 c_S \|M_H\|_{H^{-\frac 12}(\Gamma)} \leq 
-\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} \qquad \forall M_H \in Q_H(\Gamma),
+\sup_{w_h \in W_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} \qquad \forall M_H \in Q_H(\Gamma),
 \end{equation}
-being $X_h(\Gamma)$ the trace space of the functions in $X_h(\Omega)$, namely the space of the restrictions of the functions in $X_h(\Omega)$ to $\Gamma$. 
-Using the boundedness of the extension operator $E$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
+being $W_h(\Gamma)$ the trace space of the functions in $X_h(\Omega)$, namely the space of the restrictions of the functions in $X_h(\Omega)$ to $\Gamma$. 
+Using the boundedness of the extension operator $E$ from $H^{\frac 12}_0(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
 \begin{equation*}
-\sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} 
+\sup_{w_h \in W_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|w_h\|_{H^{\frac 12}(\Gamma)}} 
 \leq 
-\|E\| \sup_{w_h \in X_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|E w_h\|_{H^1(\Omega)}}.
+\|E\| \sup_{w_h \in W_h(\Gamma)} \frac{ \langle w_h, M_H \rangle _{\Gamma} } {\|E w_h\|_{H^1(\Omega)}}.
 \end{equation*}
-Let $R_h: H^1(\Omega) \rightarrow X_h(\Omega)$ be a quasi interpolation operator satisfying 
+Let $R_h: H^1_0(\Omega) \rightarrow X_h(\Omega)$ be a quasi interpolation operator satisfying 
 \begin{equation*}
-\|R_h v\|_{H^1(\Omega)} \leq c_R \|v\|_{H^1(\Omega)} \qquad \forall v \in H^1(\Omega).
+\|R_h v\|_{H^1(\Omega)} \leq C_R \|v\|_{H^1(\Omega)} \qquad \forall v \in H^1_0(\Omega).
 \end{equation*}
@@
 \end{equation*}
-Consequently, using again the extension operator $E$ from $H^{\frac 12}(\Omega)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1(\Omega)$ to $X_h(\Omega)$, we obtain
+Consequently, using again the extension operator $E$ from $H^{\frac 12}_0(\Omega)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_h(\Omega)$, we obtain
 \begin{multline}
 c_{S_2} \|M_H\|_{H^{-\frac 12}(\Lambda)} \leq 
-\sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle_{\Lambda} } {\|w_h\|_{H^{\frac 12}(\Lambda)}} 
+\sup_{w_h \in W_h(\Lambda)} \frac{ \langle w_h, M_H \rangle_{\Lambda} } {\|w_h\|_{H^{\frac 12}(\Lambda)}} 
 \\
-\leq |\DD|^{-1} \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda}} {\|\mathcal{U}_E w_h\|_{H^{\frac 12}(\Gamma)}} 
-\leq |\DD|^{-1}\|E\| \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|E \mathcal{U}_E w_h\|_{H^1(\Omega)}} 
+\leq |\DD| \sup_{w_h \in W_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda}} {\|\mathcal{U}_E w_h\|_{H^{\frac 12}(\Gamma)}} 
+\leq |\DD| \|E\| \sup_{w_h \in W_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|E \mathcal{U}_E w_h\|_{H^1(\Omega)}} 
 \\
-\leq |\DD|^{-1}\|E\| C_R \sup_{w_h \in X_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
+\leq |\DD|\|E\| C_R \sup_{w_h \in W_h(\Lambda)} \frac{ \langle w_h, M_H \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
 \\ 
-=  |\DD|^{-1}\|E\| C_R \sup_{w_h \in X_h(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E w_h, M_H \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
+=  |\DD| \|E\| C_R \sup_{w_h \in W_h(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E w_h, M_H \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
 \\
-\leq |\DD|^{-1}\|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi _2  v_h, M_H \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
+\leq |\DD| \|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi _2  v_h, M_H \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
 \end{multline}
-Therefore, \eqref{inf_sup_discrete_prob2} holds with $\gamma_2=  c_{S_2} |\DD| \|E\|^{-1} C_R^{-1}$
+Therefore, \eqref{inf_sup_discrete_prob2} holds with $\gamma_2=  c_{S_2} |\DD|^{-1} \|E\|^{-1} C_R^{-1}$
 \end{proof}

### 2020-02-28 infsup_discrete_conformingLM.tex
Updates from Overleaf

@@
 \section{Finite element approximation}
+In this section we consider the discretization of Problem 1 and 2 by means of the finite element method.
+We address two main challenges; first we aim to identify a suitable approximation space for the Lagrange multiplier and to analyze the stability of the discrete saddle point problem; second we aim to derive a stable discretization method that uses independent computational meshes for $\Omega$, $\Gamma$ and $\Lambda$.
+Let us introduce a shape-regular triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{h}$ of $\Lambda$.
+We analyze two different cases: the one in which the 3D mesh is conforming to the interface $\Gamma$, namely the set of the intersections of the 3D elements of $\mathcal{T}^{\Omega}_h$ with $\Gamma$ is constituted by facets of such elements, and the non conforming case, namely the interface $\Gamma$ cuts the mesh arbitrarily.
 The discrete equivalent of \eqref{eq:saddle-point} reads as finding $u_h\in X_h\subset X$, $\lambda_h\in Q_h\subset Q$ s.t.
@@
 Let $B_h: Q'_h \longrightarrow Q_h$ be the operator induced by $b$ such that $\langle B_h v_h,\mu _h\rangle_{Q'_h,Q_h} = b(v_h,\mu _h)$.
-The well posedness of such problem is governed by the classical inf-sup theory in Banach spaces. The main result is reported below.
+The well posedness of such problem is governed by the classical result reported below.
 
-\begin{corollary}{\cite[Theorem 2.42]{MR2050138}}
+\begin{corollary}{\cite[Theorem 2.42]{MR2050138}}Let $a(\cdot, \cdot)$ and $b(\cdot, \cdot)$ be continuous bilinear forms. 
 Problem \eqref{eq:saddle-point_discrete} is well-posed if and only if 
-\begin{equation}\label{BNB1_discrete}
-\exists \alpha_h >0 :\, \inf_{u_h\in ker(B_h)}\sup_{v_h\in ker(B_h)} \frac{a(u_h,v_h)}{\|u_h\|_{X}\|v_h\|_{X}}\geq \alpha_h
-\end{equation}
-and 
-\begin{equation}\label{eq:infsup_discrete}
-\exists \beta_h >0:\,\inf_{\mu_h\in Q_h}\sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}\|\mu_h\|_{Q}}\geq \beta_h .
-\end{equation}
+\begin{align}\label{BNB1_discrete}
+& \exists \alpha_h >0 : && \inf_{u_h\in ker(B_h)}\sup_{v_h\in ker(B_h)} \frac{a(u_h,v_h)}{\|u_h\|_{X}\|v_h\|_{X}}\geq \alpha_h\,,
+\\
+\label{eq:infsup_discrete}
+ &\exists \beta_h >0: &&\inf_{\mu_h\in Q_h}\sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}\|\mu_h\|_{Q}}\geq \beta_h\, .
+\end{align}
 \end{corollary}
 This corollary is the discrete counterpart of Theorem \ref{th:bnb} where at the discrete level condition \eqref{BNB1_discrete} implies both of \eqref{BNB1}.
-Conversely, \eqref{eq:infsup_discrete} does not follow from the conformity of the finte element spaces and it must be analysed independetly of \eqref{eq:infsup}.
+We remark that \eqref{eq:infsup_discrete} does not follow from the conformity of the finte element spaces and it must be analysed independetly of \eqref{eq:infsup}.
 Let us notice that for both problem 1 and problem 2 the bilinear form $a(\cdot, \cdot)$ is coercive as stated in Lemmas \eqref{lemma:prob1_coercivity} and \eqref{lemma:prob2_coercivity}.
@@
 
-Let us introduce a shape-regular triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{h}$ of $\Lambda$. 
-We analyze two different cases: the one in which the 3D mesh is conforming to the interface $\Gamma$, namely the set of the intersections of the 3D elements of $\mathcal{T}^{\Omega}_h$ with $\Gamma$ is constituted by facets of such elements, and the non conforming case, namely the interface $\Gamma$ cuts the mesh arbitrarly.
-
 \subsection{$\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}
  We first analyze the case in which the 3D mesh is conforming to the interface $\Gamma$.
-With this aim, we define conformity conditions between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$ with $\Gamma$.
-More precisely we require that the intersection of $\mathcal{T}^{\Omega}_h$ and $\Gamma$ is made of entire faces of elemets $K \in \mathcal{T}^{\Omega}_h$.
-Furthermore we also set a restriction between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$.
-We want that the intersection of $\Gamma$ with any orthogonal plane to $\Lambda$ that crosses $\Lambda$ at the nodes of $\mathcal{T}^{\Lambda}_h$, consists of entire edges of $\mathcal{T}^{\Omega}_h$.
-Namely the intersection of $\Gamma$ with orthogonal planes to $\Lambda$ is conformal with $\mathcal{T}^{\Lambda}_h$.
+As conformity conditions between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$ with $\Gamma$ , we require that the intersection of $\mathcal{T}^{\Omega}_h$ and $\Gamma$ is made of entire faces of elemets $K \in \mathcal{T}^{\Omega}_h$.
+Furthermore, we also set a restriction between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$.
+We assume that $\Lambda$ is a piecewise linear manifold.
+We want that the intersection of $\Gamma$ with any orthogonal plane to $\Lambda$ that crosses $\Lambda$ at the internal nodes of $\mathcal{T}^{\Lambda}_h$, consists of entire edges of $\mathcal{T}^{\Omega}_h$.
+
 \subsubsection{Problem 1}
 We denote by $X_{h,0}^k(\Omega)\subset H^1_0(\Omega)$, with $k>0$, the conforming finite element space of continuous piecewise polynomials of degree $k$ defined on $\Omega$ satisfying homogeneous Dirichlet conditions on the boundary and by $X_{h,0}^k(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$, satisfying homogeneous Dirichlet conditions on $\Lambda \cap \partial \Omega$.
-%Moreover, $Q_{h}$ denotes a suitable trial space for the lagrange multiplier $\lambda_h$.
-In particular, $Q_h \subset H^{-\frac12}(\Gamma )$ in the case of Problem 1 and $Q_h \subset H^{-\frac12}(\Lambda)$ in the case of Problem 2.
-Problem 1 consists to find $u_h \in X_{h,0}^k (\Omega) ,\, {\ud}_h \in X_{h,0}^k(\Lambda) ,\, \lambda_h \in Q_h \subset H^{-\frac12}(\Gamma )$, such that
+
+The discrete version of Problem 1 is:
+find $u_h \in X_{h,0}^k (\Omega) ,\, {\ud}_h \in X_{h,0}^k(\Lambda) ,\, \lambda_h \in Q_h \subset H^{-\frac12}(\Gamma )$, such that
 \begin{subequations}
@@
 &(u_h,v_h)_{H^1(\Omega)} + ({\ud}_h,{\vd}_h)_{H^1(\Lambda),|\D|} 
-+ \langle \trace v_h  - \mathcal{E}_{\Lambda} {\vd}_h, \lambda_h \rangle_\Gamma 
++ \langle \trace v_h  - \mathcal{E}_{\Lambda} {\vd}_h, \lambda_h \rangle_\Gamma &&
 \\
 \nonumber
-&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda),|\D|}
-\quad \forall v_h \in X_{h,0}^k(\Omega), \ {\vd}_h \in X_{h,0}^k(\Lambda)
+&\qquad= (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda),|\D|}
+\quad && \forall v_h \in X_{h,0}^k(\Omega), \ {\vd}_h \in X_{h,0}^k(\Lambda)
 \\
 &   \langle \trace u_h - \mathcal{E}_{\Lambda} {\ud}_h , \mu_h \rangle_\Gamma = 0
-\quad \forall \mu_h \in Q_h\,,
+\quad && \forall \mu_h \in Q_h\,,
 \end{align}
@@
 The space $Q_h$ must be suitably chosen such that \eqref{eq:infsup_discrete} holds.
-Let us denote with $W_{h,0}^k(\Gamma) \subset H^{\frac 12}_{00}(\Gamma)$ the trace space of functions running in $X_{h,0}^k(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$.
-We choose $Q_h=W_{h,0}^k(\Gamma)$, therefore we impose homogeneous Dirichlet boundary condition on $\partial \Omega$ also for the Lagrange multiplier.
-For this choice of $Q_h$ we can prove the well-posedness of the discrete problem, as shown in the following.
+Let $Q_h$ be the trace space of $X_{h,0}^k(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$.
+As a result, $Q_h=X_{h,0}^k(\Gamma) \subset H^\frac12_{00}(\Gamma)$.
+Therefore we impose homogeneous Dirichlet boundary condition on $\partial \Omega$ also for the Lagrange multiplier.
+For this choice of $Q_h$ we prove the well-posedness of the discrete problem, as shown in the following.
 
-\begin{lemma}
-Let $P_h: H^{\frac 12}_{00}(\Gamma) \longrightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Gamma)$ by
+\begin{lemma}\label{lemma:prob1_orthproj}
+Let $P_h: H^{\frac 12}_{00}(\Gamma) \rightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Gamma)$ by
 \begin{equation*}
@@
 \begin{equation}\label{continuity_projoper}
-\|P_h v\|_{H^{\frac 12}(\Gamma)} \leq C \|v\|_{H^{\frac 12}(\Gamma)},
+\|P_h v\|_{H^{\frac 12}_{00}(\Gamma)} \leq C \|v\|_{H^{\frac 12}_{00}(\Gamma)},
 \end{equation}
@@
 We prove that $P_h$ is continuous on $L^2(\Gamma)$ and on $H^1_0(\Gamma)$ following \cite[Section 1.6.3]{MR2050138}.
-Then, the inequality \eqref{continuity_projoper} can be dirived by Hilbertian interpolation.
-For the $L^2$-continuity, we exploit the fact that, from the definition of $P_h$,
-\begin{equation*}
-(v-P_h v,P_h v)_{\Gamma}=0.
-\end{equation*} 
+Then, the inequality \eqref{continuity_projoper} can be derived by interpolation between spaces, since $H^\frac12_{00}(\Gamma)$ can be seen as the interpolation space between $L^2(\Gamma)$ and $H^1_0(\Gamma)$.
+For the $L^2$-continuity, we exploit the fact that, from the definition of $P_h$, $(v-P_h v,P_h v)_{\Gamma}=0$.
 Therefore, by Pythagoras identity,
@@
 Let us now consider $v\in H^1_0(\Gamma)$.The Scott-Zhang interpolation operator $SZ_h$ from $H^1_0(\Gamma)$ to $Q_h$ satisfies the following inequalities,
-\begin{equation}\label{SZ_stability}
-\|SZ_h v\|_{H^1(\Gamma)} \leq C_1 \|v\|_{H^1(\Gamma)}
-\end{equation} 
-\begin{equation}\label{SZ_approx}
-\|v -SZ_h v \|_{L^2(\Gamma)}\leq C_2 h \|v\|_{H^1(\Gamma)}.
-\end{equation}
+\begin{align}
+\label{SZ_stability}
+\|SZ_h v\|_{H^1(\Gamma)} &\leq C_1 \|v\|_{H^1(\Gamma)}
+\\
+\label{SZ_approx}
+\|v -SZ_h v \|_{L^2(\Gamma)} &\leq C_2 h \|v\|_{H^1(\Gamma)}.
+\end{align}
 Therefore, using \eqref{SZ_stability},
@@
 \end{equation*}
-from which we obtain the continuity in $H^1_0(\Gamma)$.\\
+from which we obtain the continuity in $H^1_0(\Gamma)$.
 \end{proof}
@@
 \begin{equation*}
-\sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , \mu_h \rangle}{ \|q_h\|_{H^{\frac 12}(\Gamma)}} \geq \gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)}.
+\sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , \mu_h \rangle}{ \|q_h\|_{H^{\frac 12}_{00}(\Gamma)}} \geq \gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)}.
 \end{equation*} 
@@
 \begin{equation*}
-\|\mathcal{E}_\Omega\|^{-1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{\|v\|_{H^1(\Omega)}} 
+\|\mathcal{H}_\Omega\|^{-1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{\|v\|_{H^1(\Omega)}} 
 \end{equation*}
@@
 \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{\|v\|_{H^1(\Omega)}}
-\leq C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{ \|\trace v\|_{H^{\frac 12}(\Gamma)}}.
+\leq C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{ \|\trace v\|_{H^{\frac 12}_{00}(\Gamma)}}.
 \end{equation*}
 By the definition of $P_h$ and \eqref{continuity_projoper} 
-\begin{equation*}
-\begin{split}
-C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{ \|\trace v\|_{H^{\frac 12}(\Gamma)}}&= C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(\trace v) , \mu_h \rangle}{ \|\trace v\|_{H^{\frac 12}(\Gamma)}}\\
-&\leq  C_T C \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(\trace v) , \mu_h \rangle}{ \|P_h(\trace v)\|_{H^{\frac 12}(\Gamma)}}\\
-&= C_T C \sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , \mu_h \rangle}{  \|q_h\|_{H^{\frac 12}(\Gamma)}}.
-\end{split}
-\end{equation*}
+\begin{multline*}
+C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{ \|\trace v\|_{H^{\frac 12}_{00}(\Gamma)}}= C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(\trace v) , \mu_h \rangle}{ \|\trace v\|_{H^{\frac 12}_{00}(\Gamma)}}
+\\
+\leq  C_T C \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(\trace v) , \mu_h \rangle}{ \|P_h(\trace v)\|_{H^{\frac 12}_{00}(\Gamma)}}
+= C_T C \sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , \mu_h \rangle}{  \|q_h\|_{H^{\frac 12}_{00}(\Gamma)}}.
+\end{multline*}
 \end{proof}
 
-\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds, namely 
+\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds true, namely 
 $\exists \beta_{h,1} >0$ s.t.
@@
 
-Using Lemma \ref{lemma:trspace_infsup} and the boundedness of the armonic extension operator $\mathcal{E}_{\Omega}$ from $H^{\frac 12}_{00}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
+Using Lemma \ref{lemma:trspace_infsup} and the boundedness of the harmonic extension operator $\mathcal{H}_\Omega$ from $H^{\frac 12}_{00}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
 \begin{equation*}
-\gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq  \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|q_h\|_{H^{\frac 12}(\Gamma)}} 
+\gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq  \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|q_h\|_{H^{\frac 12}_{00}(\Gamma)}} 
 \leq 
-\|\mathcal{E}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{E}_\Omega q_h\|_{H^1(\Omega)}} .
+\|\mathcal{H}_\Omega\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{H}_\Omega q_h\|_{H^1(\Omega)}} .
 \end{equation*}
-Let $R_h: H^1_0(\Omega) \rightarrow X_{h,0}^k(\Omega)$ be a quasi interpolation operator satisfying 
+Let $R_h: H^1_0(\Omega) \rightarrow X_{h,0}^k(\Omega)$ be a quasi interpolation operator (such as the Scott-Zhang operator) satisfying 
 \begin{equation*}
@@
 \begin{equation*}
-\|\mathcal{E}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{E}_{\Omega}q_h\|_{H^1(\Omega)}} 
+\|\mathcal{H}_\Omega\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{H}_\Omega q_h\|_{H^1(\Omega)}} 
 \leq
-\|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|R_h \mathcal{E}_{\Omega} q_h\|_{H^1(\Omega)}}
+\|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|R_h \mathcal{H}_{\Omega} q_h\|_{H^1(\Omega)}}
 \end{equation*}
 and we have
-\begin{multline}
+\begin{multline}\label{eq_conformity}
 \gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)} 
 \leq 
-\sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|q_h\|_{H^{\frac 12}(\Gamma)}} 
+\sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|q_h\|_{H^{\frac 12}_{00}(\Gamma)}} 
 \leq
-\|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{E}_{\Omega} q_h\|_{H^1(\Gamma)}}
+\|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{H}_{\Omega} q_h\|_{H^1(\Gamma)}}
 \\
 =
-\|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle \trace R_h  \mathcal{E}_{\Omega}q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{E}_{\Omega} q_h\|_{H^1(\Omega)}} 
-\leq \|\mathcal{E}_{\Omega}\| C_R \sup_{v_h \in X_{h,k}(\Omega)} \frac{ \langle \trace v_h, \mu_h \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
+\|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle \trace R_h  \mathcal{H}_{\Omega}q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{H}_{\Omega} q_h\|_{H^1(\Omega)}} 
+\leq \|\mathcal{H}_{\Omega}\| C_R \sup_{v_h \in X_{h,k}(\Omega)} \frac{ \langle \trace v_h, \mu_h \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
 \end{multline}
-Therefore the inf-sup condition $\eqref{inf_sup_discrete_prob1}$ holds with $\beta_{h,1} = \gamma \|\mathcal{E}_{\Omega}\|^{-1} C_R^{-1} $.
+Therefore the inf-sup condition $\eqref{inf_sup_discrete_prob1}$ holds with $\beta_{h,1} = \gamma \|\mathcal{H}_{\Omega}\|^{-1} C_R^{-1} $.
+We notice that in \eqref{eq_conformity} we exploit the fact that the operator $\trace R_h  \mathcal{H}_{\Omega}$ coincides with the identity on the space $Q_h$, thanks to the conformity of $\mathcal{T}^{\Omega}_h$ to the interface $\Gamma$.
 \end{proof}
 
-\begin{remark} We notice that to prove the result in Lemma \ref{lemma:trspace_infsup} (and then the discrete inf-sup condition)  basically we need a projection operator $P_h: H^{\frac 12}_{00} \longrightarrow W_{h,0}^k(\Gamma)$ orthogonal in the multiplier space $Q_h$, namely such that $\langle P_h v, \mu_h \rangle = \langle v, \mu_h \rangle, \, \forall \mu_h \in Q_h$, and continuous in $H^{\frac 12}(\Gamma)$.
+%\begin{remark} We notice that to prove the result in Lemma \ref{lemma:trspace_infsup} (and then the discrete inf-sup condition)  basically we need a projection operator $P_h: H^{\frac 12}_{00} \longrightarrow W_{h,0}^k(\Gamma)$ orthogonal in the multiplier space $Q_h$, namely such that $\langle P_h v, \mu_h \rangle = \langle v, \mu_h \rangle, \, \forall \mu_h \in Q_h$, and continuous in $H^{\frac 12}(\Gamma)$.
 Therefore, in principle different choices than $Q_h=W_{h,0}^k(\Gamma)$ could be considered if we can build an operator $P_h$ satisfying these properties.
 In \cite{belgacem1999mortar} such operator $P_h$  is built for a particular choice of $Q_h$ but it is not clear how to prove the $H^1$-stability inequality (and consequently the $H^{\frac 12 }$-stability) with a constant independent of the mesh size $h$.
-\end{remark}
+%\end{remark}
 
 \subsubsection{Problem 2}
-This problem requires to find  $u_h \in X_{h,0}^k(\Omega) ,\ {\ud}_h \in X_{h,0}^k(\Lambda), \ {\ld}_h \in Q_h \subset H^{-\frac12}(\Lambda)$, such that
+We aim to find  $u_h \in X_{h,0}^k(\Omega) ,\ {\ud}_h \in X_{h,0}^k(\Lambda), \ {\ld}_h \in Q_h \subset H^{-\frac12}(\Lambda)$, such that
 \begin{subequations}
@@
 
-%**** uniform \DD
-%\begin{lemma}
-%Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
-%\begin{equation*}
-%(P_h v , \psi)_\Lambda= (v, \psi)_\Lambda \qquad \forall \psi \in Q_h.  
-%\end{equation*} 
-%Then, $P_h$ is continuous on $H^{\frac 12}_{00}(\Lambda)$, namely
-%\begin{equation*}
-%\|P_h v\|_{H^{\frac 12}_{00}(\Lambda)} \leq C \|v\|_{H^{\frac 12}_{00}(\Lambda)},
-%\end{equation*}
-%where $C$ is a positive constant independent of $h$.
-%\end{lemma}
-%
-%\begin{lemma}\label{infsup_avr_trspace}
-%There exist a constant $\gamma >0$ such that
-%\begin{equation*}
-%\sup_{\substack{q_h \in W_{h,0}^k(\Lambda)}} \frac{\langle q_h , \mu_h \rangle}{ \|q_h\|_{H^{\frac 12}(\Lambda)}} \geq \gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall \mu_h \in Q_h.
-%\end{equation*} 
-%\end{lemma}
-%
-%\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds, namely 
-%$\exists \beta_{h,2} >0$ s.t.
-%\begin{equation}
-%\inf_{\mu_h \in Q_h} 
-%\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)} }\frac{\langle \mtrace v_h -  {\vd}_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\vertiii{[v_h, {\vd}_h]} \|{\md}_h\|_{H^{-\frac 12 }(\Lambda)} }
-%\geq \beta_{h,2}. 
-%\end{equation}
-%\end{theorem}
-%\begin{proof}
-%Let ${\md}_h$ be arbitrarly chosen in $Q_h$. Again, we choose ${\vd}_h =0$, so that the proof reduces to show that there exists $\beta_{h,2}$ such that
-%\begin{equation*}
-%\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \mtrace v_h , {\md}_h \rangle _{\Lambda,|\DD|} } {\|v_h\|_{H^1(\Omega)} }\geq \beta_{h,2} \|{\md}_h\|_{H^{-\frac 12}(\Lambda)}\ \qquad \forall {\md}_h \in Q_h.
-%\end{equation*}
-%Let us denote with $\ext$ the uniform extension operator from $\Lambda$ to $\Gamma$. Using Lemma \ref{H12norm_Gamma}, we easily have for any $w \in H^{\frac 12}(\Lambda)$,\\
-%{\color{red} TO DO: generalize to non constant $\DD$}
-%\begin{equation*}
-%\|\mathcal{U}_E w\|_{H^{\frac 12}(\Gamma)}=|\DD| \|w\|_{H^{\frac 12}(\Lambda)}.
-%\end{equation*}
-%Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $E$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
-%\begin{multline}
-%\gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \leq 
-%\sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
-%\\
-%= |\DD| \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
-%\leq |\DD|\|E\| \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda} } {\|E \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
-%\\
-%\leq |\DD|\|E\| C_R \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle q_h, \mu_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
-%\\ 
-%=  |\DD|\|E\| C_R \sup_{q_h \in W_{h,0}^k(\Lambda)} \frac{ \langle \Pi _1  R_h E \mathcal{U}_E q_h, \mu_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E w_h\|_{H^1(\Omega)}}
-%\\
-%\leq |\DD|\|E\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \Pi _2  v_h, \mu_h \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
-%\end{multline}
-%
-%%\begin{equation*}
-%%\|\mathcal{U}_E w\|_{H^{\frac 12}(\Gamma)}\lesssim \|w\|_{H^{\frac 12}(\Lambda)}.
-%%\end{equation*}
-%%Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{E}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
-%%\begin{multline}
-%%\gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \leq 
-%%\sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle_{\Lambda} } {\|q_h\|_{H^{\frac 12}(\Lambda)}} 
-%%\\
-%%\lesssim \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda}} {\|\mathcal{U}_E q_h\|_{H^{\frac 12}(\Gamma)}} 
-%%\lesssim \|\mathcal{E}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda} } {\|\mathcal{E} \mathcal{U}_E q_h\|_{H^1(\Omega)}} 
-%%\\
-%%\lesssim \|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda} } {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
-%%\\ 
-%%\lesssim\|\mathcal{E}\| C_R \sup_{q_h \in Q_h} \frac{ \langle \avrc{TR_h E \mathcal{U}_E q_h}, {\md}_h \rangle _{\Lambda}} {\|R_h E \mathcal{U}_E q_h\|_{H^1(\Omega)}}
-%%\\
-%%\lesssim\|\mathcal{E}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \avrc{T v_h}, {\md}_h \rangle _{\Lambda}} {\|v_h\|_{H^1(\Omega)}}. 
-%%\end{multline}
-%
-%\end{proof}
-%
-
-%*******************extension to non uniform $|\DD|$
-
-\begin{lemma}
+\begin{lemma}\label{lemma:prob2_orthproj}
 Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
@@
 \begin{equation*}
-\|P_h v\|_{H^{\frac 12}(\Lambda),|\DD|} \leq C \|v\|_{H^{\frac 12}(\Lambda),|\DD|},
+\|P_h v\|_{H^{\frac 12}_{00}(\Lambda),|\DD|} \leq C \|v\|_{H^{\frac 12}_{00}(\Lambda),|\DD|},
 \end{equation*}
@@
 \begin{equation*}
-\sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , {\md}_h \rangle_{\Lambda, |\DD|}}{ \|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} \geq \gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall {\md}_h \in Q_h.
+\sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , {\md}_h \rangle_{\Lambda, |\DD|}}{ \|q_h\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}} \geq \gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall {\md}_h \in Q_h.
 \end{equation*} 
 \end{lemma}
+
+The proofs follow the ones of Lemmas \ref{lemma:prob1_orthproj} and \ref{lemma:trspace_infsup} with the only difference that the arguments are applied to $\Lambda$ instead of $\Gamma$.
 
@@
 \begin{proof}
-Let ${\md}_h$ be arbitrarly chosen in $Q_h$. Again, we choose ${\vd}_h =0$, so that the proof reduces to show that there exists $\beta_{h,2}$ such that
+ Again, we choose ${\vd}_h =0$, so that the proof reduces to show that there exists $\beta_{h,2}$ such that
 \begin{equation*}
@@
 \end{equation*}
-From Lemma \ref{lemma:H12norm} and its corollaries, for any $w \in H^{\frac 12}(\Lambda)$,
-\begin{equation*}
-\|\ext w\|_{H^{\frac 12}(\Gamma)}= \|w\|_{H^{\frac 12}(\Lambda),|\DD|}.
-\end{equation*}
+From Lemma \ref{lemma:H12norm} and its corollaries, for any $w \in H^{\frac 12}(\Lambda) \ 
+\|\ext w\|_{H^{\frac 12}_{00}(\Gamma)}= \|w\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}$.
 
-Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{E}_{\Omega}$ from $H^{\frac 12}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
+Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{H}_{\Omega}$ from $H^{\frac 12}_{00}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
 \begin{multline}
-\gamma \|\mu_h\|_{H^{-\frac 12}(\Lambda)} \leq 
-\sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}(\Lambda),|\DD|}} 
+\gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \leq 
+\sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}} 
+%
+=  \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda,|\DD|}} {\|\ext q_h\|_{H^{\frac 12}_{00}(\Gamma)}} 
+\leq \|\mathcal{H}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\|\mathcal{H}_{\Omega} \ext q_h\|_{H^1(\Omega)}} 
 \\
-=  \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|\ext q_h\|_{H^{\frac 12}(\Gamma)}} 
-\leq \|\mathcal{E}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|\mathcal{E}_{\Omega} \ext q_h\|_{H^1(\Omega)}} 
+\leq \|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\|R_h \mathcal{H}_{\Omega} \ext q_h\|_{H^1(\Omega)}}
+%
+=  \|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle 	\mtrace R_h \mathcal{H}_{\Omega} \ext q_h, {\md}_h \rangle _{\Lambda,|\DD|}} {\|R_h \mathcal{H}_{\Omega} \ext w_h\|_{H^1(\Omega)}}
 \\
-\leq \|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Lambda,|\DD|} } {\|R_h \mathcal{E}_{\Omega} \ext q_h\|_{H^1(\Omega)}}
-\\ 
-=  \|\mathcal{E}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle 	\mtrace R_h \mathcal{E}_{\Omega} \ext q_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|R_h \mathcal{E}_{\Omega} \ext w_h\|_{H^1(\Omega)}}
-\\
-\leq \|\mathcal{E}_{\Omega}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \mtrace v_h, \mu_h \rangle _{\Lambda,|\DD|}} {\|v_h\|_{H^1(\Omega)}}. 
+\leq \|\mathcal{H}_{\Omega}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \mtrace v_h, {\md}_h \rangle _{\Lambda,|\DD|}} {\|v_h\|_{H^1(\Omega)}}. 
 \end{multline}
-
+Also in this case to prove the disrete inf-sup condition we exploit the conformity of the meshes on $\Omega$, $\Gamma$ and $\Lambda$ and the fact that the operator $\mtrace R_h \mathcal{H}_{\Omega} \ext$ coincides with the identity if applied to functions in $Q_h$.
 \end{proof}

### 2020-02-28 solver/solver.tex
work on A1
update
Updates from Overleaf

@@
 
+\newtheorem{example}{Example}[section]
+
 \section{Introduction}\label{sec:intro}
@@
     &\int_{\Omega}\nabla u\cdot \nabla v\,\mathrm{d}x &\phantom{+\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v}} &+\epsilon\int_{\Gamma} p v\,\mathrm{d}s &= \int_{\Omega}f v\,\mathrm{d}x \quad &\forall v\in V,\\
-    &\phantom{\int_{\Omega}\nabla u\cdot \nabla v} &+{\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v} + \hat{u}\hat{v}\,\mathrm{d}x} &-\int_{\Gamma} p\hat{v}\,\mathrm{d}s &= \int_{\Gamma}\hat{f}\hat{v}\,\mathrm{d}s \quad &\forall \hat{v}\in \hat{V},\\
+    &\phantom{\int_{\Omega}\nabla u\cdot \nabla v} &+{\int_{\Gamma}\nabla \hat{u}\cdot \nabla \hat{v} + \hat{u}\hat{v}\,\mathrm{d}s} &-\int_{\Gamma} p\hat{v}\,\mathrm{d}s &= \int_{\Gamma}\hat{f}\hat{v}\,\mathrm{d}s \quad &\forall \hat{v}\in \hat{V},\\
     &\epsilon\int_{\Gamma}u q\,\mathrm{d}s &-\int_{\Gamma}\hat{u}q\,\mathrm{d}s &\phantom{-\int{\Gamma}q\hat{v}} &= \int_{\Gamma}h q\,\mathrm{d}s \quad &\forall q\in Q.
@@
   \mathcal{A} = \begin{pmatrix}
-    -\Delta_{\Omega} & & -\epsilon T^{\prime}\\
+    -\Delta_{\Omega} & & \epsilon T^{\prime}\\
     & -\Delta_{\Gamma} + I & -I\\
-    -\epsilon T & -I & \\
+    \epsilon T & -I & \\
   \end{pmatrix} =
@@
   Unless specified otherwise all the experiments are done on $\Omega$ a unit square
-  triangulated in $2N^2$ isosceles triangles. MinRes iterations are always started
-  from a random initial vector and terminate one the relative preconditioned residual
+  triangulated into $2N^2$ isosceles triangles. MinRes iterations are always started
+  from a random initial vector and terminate once the relative preconditioned residual
   norm is reduced by factor $10^{8}$. Condition numbers of the preconditioned problem
-  are computed by direct solvers, i.e. from the full spectrum.
+  are computed by direct solver, i.e. from the full spectrum.
 } of the preconditioned problem for
@@
 
-\section{Preconditioning coupled problem}\label{sec:coupled}
-\input{coupled}
+\section{Preconditioning 2$d$ coupled problem}\label{sec:coupled2d}
+\input{coupled2d}
+
+\section{Preconditioning 3$d$ coupled problem}\label{sec:coupled2d}
+\input{coupled3d}
 

### 2020-02-28 unfitted_prob2.tex
Updates from Overleaf

@@
 \def\patch{\omega _j}
-\subsection{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$} \label{sec:unfit2}
-We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_h$ cut the interface $\Gamma$. The formulation of Problem 2 is more suitable for this purpose. 
+\subsection{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$ and $\Lambda$} \label{sec:unfit2}
+We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_h$ do not conform with the surface $\Gamma$ nor with $\Lambda$. In this case, the 3D-1D-1D
+formulation, namely Problem 2, is more suitable. 
 %{\color{red} Add more details, we can refer also to cutFEM (Burman, Massing etc.) explaining the limitation of that approach (network case for example).}\\
-Therefore we focus on the analysis of Problem 2.
+Therefore we focus on the analysis of this discretization approach for Problem 2 solely.
 
-\subsubsection{Problem 2} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X_{h,0}^1(\Omega)$ and $X_{h,0}^1(\Lambda)$.
-Notice that in this case we assume that the mesh sizes of the 3D mesh $\mathcal{T}^{\Omega}_h$ and the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different, in particular we assume the 1D mesh is finer.
-Concerning the multiplier space, let $\mathcal{G}_h = \{K \in \mathcal{T}^{\Omega}_h: \, K\cap \Lambda \neq \emptyset\}$, namely $\mathcal{G}_h$ is the set of the 3D elements which intersect $\Lambda$.
+\subsubsection{Problem 2} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X_h = X_{h,0}^1(\Omega) \times X_{h^\prime,0}^1(\Lambda)$.
+With little abuse of notation, we assume that the characteristic mesh size of the 3D mesh $\mathcal{T}^{\Omega}_h$ and the one of the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different.
+Concerning the multiplier space, let $\mathcal{G}_h = \{K \in \mathcal{T}^{\Omega}_h: \, K\cap \Lambda \neq \emptyset\}$, be the set of the 3D elements that intersect $\Lambda$.
 Then we define $Q_h=\{{\ld}_h : {\ld}_h \in P^0(K) \, \forall K \in \mathcal{G}_h\}$.
-We notice that we are extending the multiplier to the 3D elements so that we do not need to consider the 1D mesh given by the intersection of the elements of $\mathcal{T}^{\Omega}_h$ with $\mathcal{T}^{\Lambda}_{h'}$.
-With this choice of multipliers the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s({\ld}_h, {\md}_h)$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}.
-The stabilization operator is based on a new multiplier space $L_H$ for which the discrete inf-sup condition is fulfilled and a projection operator $\pi_L: Q_h \rightarrow L_H$ such that for any $[v, \vd] \in X $
-\begin{equation}\label{condition_pi_L}
-b([v, \vd], {\ld}_h - \pi_L {\ld}_h) \lesssim \vertiii{[v,\vd]}\|{\ld}_h - \pi_L {\ld}_h\|_{L_H},
-\end{equation}
-where for $X$ and $\vertiii{[\cdot, \cdot]}$ we use the definitions of section $3.2$ and $\|\cdot \|_{L_H}$ denotes a suitable discrete norm on $L_H$.
-Then, the following relaxed form of the inf-sup condition is satisfied,
-\begin{lemma}\cite[Lemma2.1]{burman2014}
-Under the previous assumption, $\forall {\ld}_h \in Q_h$,
-\begin{equation*}
-\|{\ld}_h\|_{H^{-\frac 12}(\Lambda)} \lesssim \sup_{\substack{v_h \in X_{h,0}^1(\Omega)\\ {\vd}_h \in X_{h,0}^1(\Lambda)}} \frac{b([v_h, {\vd}_h], {\ld}_h)}{\vertiii{[v_h, {\vd}_h]}} + \|{\ld}_h - \pi_L {\ld}_h\|_{L_H}.
-\end{equation*}
-\end{lemma}
- Based on this projection operator, we build the stabilization term $s({\ld}_h, {\md}_h)$ satisfying
- \begin{equation*}
- \|{\ld}_h- \pi_L {\ld}_h\|_{L_H} \lesssim s({\ld}_h, {\ld}_h)
-\end{equation*}  and prove that $\forall [u_h, {\ud}_h]$, there exists a function $\xi_h\in Q_h$ depending on $[u_h, {\ud}_h]$, namely $\xi_h=\xi_h([u_h, {\ud}_h])$, s.t.
-\begin{equation}\label{stab_coercivity}
-a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) },
-\end{equation}
-\begin{equation}\label{stab_stability}
-(s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) },
-\end{equation}
-being $\vertiii{[\cdot \, ,\, \cdot] }_{X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda) }$ a suitable discrete norm.
-Then, the final objective of this section is to prove that the stabilized version of the 3D-1D-1D problem, precisely,
+We notice that the multiplier functions are defined on the 3D elements.
+With little abuse of notation, we denote with $Q_h$ also the restriction to $\Lambda$ of the space of piecewise constant functions defined in 3D.
+As a result, we have $Q_h \subset L^2(\Lambda) \subset H^{-\frac12}(\Lambda)$.
+With this choice of multipliers the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s({\ld}_h, {\md}_h): \ Q_h \times Q_h \rightarrow \mathbb{R}$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}.
+The objective of this section is to analyze the stabilized version of the 3D-1D-1D problem: find $[u_h, {\ud}_h] \in X_h$ and ${\ld}_h \in Q_h$ such that
 \begin{multline}\label{eq:prob2_stabilized}
 a([u_h, {\ud}_h], [v_h, {\vd}_h]) +
-b([v_h, {\vd}_h], {\ld}_h) +\\
-b([u_h, {\ud}_h], {\md}_h) 
-- s({\ld}_h, {\md}_h) = c(v_h) + d({\md}_h)\\
-  \qquad \forall [v_h, {\vd}_h] \in {X_{h,0}^1(\Omega)\times X_{h,0}^1(\Lambda), \, \forall \md}_h \in Q_h
+b([v_h, {\vd}_h], {\ld}_h)
++ b([u_h, {\ud}_h], {\md}_h)
+- s({\ld}_h, {\md}_h) 
+= c(v_h) + d({\md}_h)\\
+  \quad \forall [v_h, {\vd}_h] \in X_h, \,
+  \forall {\md}_h \in Q_h\,.
 \end{multline}
-is well posed.
-%\begin{lemma}\cite[Lemma2.3]{burman2014}
-%Under the previous assumptions, system \eqref{eq:prob2_stabilized} admits a unique solution $\{[u_h, {\ud}_h], {\ld}_h \}$.
-%\end{lemma}
-In what follows we discuss the definition of the space $L_H$, the projector $\pi_L$ and the stabilization operator such that lemmas 2.1 and 2.3 of \cite{burman2014} can be applied to problem \eqref{eq:prob2_stabilized}.
+The idea of the stabilization strategy proposed in \cite{burman2014}
+is to identify a new multiplier space $Q_H$, which is never implemented in practice, such that inf-sup stability with $X_h$ holds true.
+Then, the stabilization operator is designed to control the distance between $Q_h$ and $Q_H$ trough the following inequality
+\begin{equation*}
+    \|{\md}_h - \pi_H {\md}_h\|_{Q_H} \leq C s_h({\md}_h, {\md}_h)\,,
+\end{equation*}
+being $\pi_H$ a suitable projection operator $Q_h \rightarrow Q_H$.
+Applying the results obtained in \cite{burman2014} we will show that the well posedness of problem \eqref{eq:prob2_stabilized} is governed by the following lemma.
+\begin{lemma}[Lemma 2.3 of \cite{burman2014}]\label{lemma23burman}
+\begin{enumerate}
+    \item If the $b(\cdot,\cdot),\, X_h,Q_H \rightarrow \R$ is inf-sup stable.
+    \item If the stabilization operator $s_h(\cdot,\cdot),\, Q_H,Q_H \rightarrow \R$ is such that
+    \begin{equation*}
+        \beta \|{\md}_h\|_{H^{-\frac12}(\Lambda)} \leq \sup\limits_{v_h \in X_h} \frac{b(v_h,{\md}_h}{\vertiii{v_h})} + s_h({\md}_h, {\md}_h), \quad \forall {\md}_h \in Q_h\,.
+    \end{equation*}
+    \item If for any $[v_h, {\vd}_h]$ there exists a function $\xi_h\in Q_h$ depending on $[v_h, {\vd}_h]$, namely $\xi_h=\xi_h([v_h, {\vd}_h])$, s.t.
+\begin{gather}
+\label{stab_coercivity}
+a([v_h, {\vd}_h],[v_h, {\vd}_h] ) + b([v_h, {\vd}_h], \xi_h) \geq \alpha_\xi \vertiii{[v_h, {\vd}_h]}_{X_h}\,,
+\\
+\label{stab_stability}
+(s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[v_h, {\vd}_h]}_{X_h}\,,
+\end{gather}
+being $\vertiii{[\cdot \, ,\, \cdot] }_{X_h}$ a suitable discrete norm. 
+\end{enumerate}
+Then, problem \eqref{eq:prob2_stabilized} admits a unique solution.
+\end{lemma}
+For the proof of this result we remand the reader to Lemma 2.3 of \cite{burman2014}.
+In the reminder of this section we show how to find a multiplier space $Q_H$ and a stabilization operator $s_h$ such that all the assumptions of lemma \ref{lemma23burman} are satisfied.
+
+% The stabilization operator is based on a new multiplier space $Q_H$, for which the discrete inf-sup condition is fulfilled, and a projection operator $\pi_H: Q_h \rightarrow Q_H$ such that for any $[v, \vd] \in X $
+% \begin{equation}\label{condition_pi_L}
+% b([v, \vd], {\ld}_h - \pi_H {\ld}_h) \leq C \vertiii{[v,\vd]}\|{\ld}_h - \pi_H {\ld}_h\|_{Q_H},
+% \end{equation}
+% where for $X$ and $\vertiii{[\cdot, \cdot]}$ we use the definitions of section $3.2$ and $\|\cdot \|_{Q_H}$ denotes a suitable discrete norm on $Q_H$.
+Then, the following relaxed form of the inf-sup condition is satisfied,
+% \begin{lemma}\cite[Lemma2.1]{burman2014}\label{lemma_burman2014}
+% If the multiplier space $Q_H$ is inf-sup stable and the operator $\pi_H: Q_h \rightarrow Q_H$ satisfies \eqref{condition_pi_L}, then for any ${\ld}_h \in Q_h$ it holds,
+% \begin{equation*}
+% \|{\ld}_h\|_{H^{-\frac 12}(\Lambda)} \lesssim \sup_{\substack{v_h \in X_{h,0}^1(\Omega)\\ {\vd}_h \in X_{h^\prime,0}^1(\Lambda)}} \frac{b([v_h, {\vd}_h], {\ld}_h)}{\vertiii{[v_h, {\vd}_h]}} + \|{\ld}_h - \pi_H {\ld}_h\|_{Q_H}.
+% \end{equation*}
+% \end{lemma}
+%  Based on this projection operator, we build the stabilization term $s({\ld}_h, {\md}_h)$ satisfying
+%  \begin{equation}\label{condition_pi_L_bis}
+%  \|{\ld}_h- \pi_H {\ld}_h\|_{Q_H} C \leq s({\ld}_h, {\ld}_h)
+% \end{equation} and prove that for any $[u_h, {\ud}_h]$ there exists a function $\xi_h\in Q_h$ depending on $[u_h, {\ud}_h]$, namely $\xi_h=\xi_h([u_h, {\ud}_h])$, s.t.
+% \begin{equation}\label{stab_coercivity}
+% a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) },
+% \end{equation}
+% \begin{equation}\label{stab_stability}
+% (s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) },
+% \end{equation}
+% being $\vertiii{[\cdot \, ,\, \cdot] }_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) }$ a suitable discrete norm.
+
+The first step consists of showing
+that there exists a discrete space $Q_H$ that satisfies the first assumption of \ref{lemma23burman}. 
 We recall that in the case of Problem 2, 
 \begin{equation*}
-b([u_h, {\ud}_h], {\ld}_h) = \left(\mtrace u_h - {\ud}_h, {\ld}_h\right)_{\Lambda,|\DD|}.
+b([u_h, {\vd}_h], {\md}_h) = \left(\mtrace v_h - {\vd}_h, {\md}_h\right)_{\Lambda,|\DD|}.
 \end{equation*}
-The construction of the inf-sup stable space $L_H$ is based on macro elements of diameter $H$, where $H$ is sufficiently large.
-In particular, we assume that there exists positive constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$.
+The construction of the inf-sup stable space $Q_H$ is based on macro elements of diameter $H$, where $H$ is sufficiently large.
+In particular, we assume that there exists positive constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$, being $h$ the mesh characteristic size of $\mathcal{T}_h^\Omega$.
 The space is constructed assembling the 3D elements of $\mathcal{G}_h$ into macro patches $ \patch $ such that $H \leq |\patch\cap \Lambda|\leq cH$, with $c\geq 1$.
@@
 \begin{equation*}
-L_H=\left\{{\lld }_H: \, {\lld }_H\in P^0(\patch)\, \forall j \right\}.
+Q_H=\left\{{\md }_H: \, {\md }_H\in P^0(\patch)\, \forall j \right\}.
 \end{equation*}
+As previously pointed out for $Q_h$, we denote with $Q_H$ also the restriction of the multiplier space to $\Lambda$, namely say $Q_H \subset L^2(\Lambda) \subset H^{-\frac12}(\Lambda)$.
 
@@
 The extended patches $\omega _j$ are built such that they fulfill the conditions meas$(\patch)=\mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda}\cap \omega_j)=\mathcal{O}(H)$, where $\Gamma_{\patch\cap \Lambda}$ is the portion of $\Gamma$ with centerline $\patch\cap \Lambda$.
-See Figure \ref{fig:gamma_generated} for a representation in the simple case in which $\omega _j$ is composed just by one tetrahedron.
-The latter assumption is required to ensure that the intersection of $\Gamma_{\patch\cap \Lambda}$ and $\omega_j$ is not too small and it will be needed later on to prove the inf-sup stability of the space $L_H$ in Lemma \ref{lemma:Lh_infsup}.
-We introduce the following discrete norms
-\begin{equation*}
-\|\, \lambda \,\|_{\pm \frac 12, h, \Lambda} = \|h^{\mp\frac 12} \lambda\|_{L^2(\Lambda)},
-\end{equation*}
-recalling that $h$ is the mesh size of $\mathcal{T}^\Omega_{h}$. We equipe the space $X_h(\Omega)\times X_{h'}(\Lambda)$ with the discrete norm
-\begin{equation*}
-\vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_{h'}(\Lambda) }
-= \|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|} + \|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|},
-\end{equation*}
-and the space $L_H$ with the norm 
-\begin{equation*}
-\|{\lld}_H \|_{L_H} = \|{\lld}_H \|_{-\frac 12, h, \Lambda}.
-\end{equation*}
-As shown in \cite[Section III]{burman2014}, we can always choose $\pi_L$ as the $L_2$ orthogonal projection operator from $\Lambda_h$ to $L_H$ in order to satisfy \eqref{condition_pi_L} and then in practice replace it with any interpolation $\tilde{\pi}_L$ of $\Lambda_h$ in $L_H$.
-In particular, we define $\forall \lambda_h \in \Lambda_h$,
-\begin{equation*}
-\tilde{\pi}_L {\ld}_{ _{|\patch}} = M^{-1} \sum_{\substack{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset}} {\ld}_{|K_i} \qquad \text{for all $\omega_j$,} 
-\end{equation*}
-being $M$ the cardinality of the set $\{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset\}$. These choices lead to the following stabilization 
-\begin{equation}\label{eq:stab}
-s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
-\end{equation}
-being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{G}_h$.
+The latter assumption is required to ensure that the intersection of $\Gamma_{\patch\cap \Lambda}$ and $\omega_j$ is not too small and it will be needed later on to prove the inf-sup stability of the space $Q_H$ in Lemma \ref{lemma:Lh_infsup}.
+A representation of this construction in the simple case in which $\omega _j$ is composed just by one tetrahedron is shown in Figure \ref{fig:gamma_generated}.
+
+% As shown in \cite[Section III]{burman2014}, we can always choose $\pi_H$ as the $L_2$ orthogonal projection operator from $\Lambda_h$ to $Q_H$ in order to satisfy \eqref{condition_pi_L} and then in practice replace it with any interpolation $\tilde{\pi}_L$ of $\Lambda_h$ in $Q_H$.
+In particular, for any $\lambda_h \in \Lambda_h$ we define,
+% \begin{equation*}
+% \tilde{\pi}_L {\ld}_{ _{|\patch}} = M_j^{-1} \sum_{\substack{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset}} {\ld}_{|K_i} \qquad \text{for all $\omega_j$,} 
+% \end{equation*}
+% being $M_j$ the cardinality of the set $\{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset\}$. These choices lead to the following stabilization 
+% \begin{equation}\label{eq:stab}
+% s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
+% \end{equation}
+% being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{G}_h$.
 
@@
 \end{figure}
-Thanks to the shape regularity of these extended patches, we have that the following discrete trace and Poincarè-type inequalites hold. More precisely, for any function $v\in H^1(\omega_j)$, 
+
+Thanks to the shape regularity of these extended patches, we have that the following discrete trace inequality holds true for any function $v\in H^1(\omega_j)$, 
 \begin{equation}\label{discr_trace_ineq}
@@
 \end{equation}
-\begin{equation}\label{disc_poincare_ineq}
-\|v- \mathcal{E}_{\patch} \pi_L\mtrace v\|_{L^2(\omega_j)} \leq c_P H \|\nabla v\|_{L^2(\omega_j)}.
-\end{equation}
-%where $\pi_L$ is a projection operator onto piecewise constant functions on $\patch\cap \Lambda$. In particular, for any $w \in L^2(\Lambda)$, we define
-For any $w \in L^2(\Lambda)$ we have that $ \mathcal{E}_{\patch}\pi_Lw \in L_H$, where with a little abuse of notation we denote as $\pi_L$ the operator
-\begin{equation}\label{eq:projector}
-\pi_Lw_{|\patch \cap \Lambda} =\frac{1}{|\Gamma_{\patch\cap \Lambda}|}\int_{\patch\cap \Lambda}|\DD| w\quad \forall j,
-\end{equation}   
-whereas the operator $\mathcal{E}_{\patch}$ simply extends the constant $\pi_L\mtrace v_{|\patch \cap \Lambda}$ to $\omega _j$.
-Moreover $\forall u_h \in X^1_{h,0}(\Omega)$ we have the following average inequality 
-%\begin{equation*}
-%\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| } \leq \sum _j \|\trace  u_h\|^2_{L^2(\omega_j\cap \Gamma)}.
-%\end{equation*}
-which is a consequence of the definition of $\mtrace$ and Jensen inequality,
+Moreover $\forall u_h \in X^1_{h,0}(\Omega)$ we have the following average inequality, which is a consequence of the definition of $\mtrace$ and Jensen inequality,
 \begin{multline}\label{eq:avrg_ineq}
@@
 \end{multline}
-To prove that \eqref{eq:prob2_stabilized} is well posed, we proceed through three main steps.
-The first step consists of showing that the space $L_H$ is inf-sup stable.
-This result is addressed in the following lemma.
+
+We are now ready to prove that the space $Q_H$ is inf-sup stable. 
 \begin{lemma}\label{lemma:Lh_infsup}
-The space $L_H$ is inf-sup stable, namely $\forall {\lld}_H \in L_H$, $\exists \beta >0$ s.t.
+The space $Q_H$ is inf-sup stable, namely $\forall {\md}_H \in Q_H$, $\exists \beta >0$ s.t.
 \begin{equation*}
-\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\lld} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|{\lld}_H\|_{H^{-\frac 12}(\Lambda)}.
+\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\md} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|{\md}_H\|_{H^{-\frac 12}(\Lambda)}.
 \end{equation*} 
 \end{lemma}
+
 \begin{proof}
-% We have to prove that $\exists \beta >0$ such that $\forall l_h \in L_h$,
-%\begin{equation*}
-%\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',1}^0(\Lambda)}} \frac{\left(\avrc{T v_h} - {\vd}_h, l _h\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|l_h\|_{H^{-\frac 12}(\Lambda)}.
-%\end{equation*}
 As in the continuous case, we can choose ${\vd}_h=0$ and we prove that
 \begin{equation*} 
-\sup_{v_h \in X_{h,0}^1(\Omega)} \frac{\left(\mtrace v_h ,{\lld}_H\right)_{\Lambda, |\DD|}}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|{\lld}_H\|_{H^{-\frac 12}(\Lambda)}.
+\sup_{v_h \in X_{h,0}^1(\Omega)} \frac{\left(\mtrace v_h ,{\md}_H\right)_{\Lambda, |\DD|}}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|{\md}_H\|_{H^{-\frac 12}(\Lambda)}.
 \end{equation*} 
 Proving the last inequality it is equivalent to find the Fortin operator $\pi_F: H^1_0(\Omega) \rightarrow X_{h,0}^1(\Omega)$, such that 
-\begin{equation*}
-\left(\mtrace v - \mtrace \pi _F v  , {\lld}_H\right)_{\Lambda, |\DD|}=0, \quad \forall v\in H^1_0(\Omega), \, {\lld}_H \in L_H
-\end{equation*} 
-and
-\begin{equation}\label{eq:cont_Fortin}
-\|\pi_F v\|_{H^1(\Omega)}\lesssim \|v\|_{H^1(\Omega)}.
-\end{equation}
+\begin{gather}
+\left(\mtrace v - \mtrace \pi _F v  , {\md}_H\right)_{\Lambda, |\DD|}=0, \quad \forall v\in H^1_0(\Omega), \, {\md}_H \in Q_H\,,
+\\
+\label{eq:cont_Fortin}
+\|\pi_F v\|_{H^1(\Omega)}\lesssim \|v\|_{H^1(\Omega)}\,.
+\end{gather}
 
@@
 \begin{multline*}
-\left(\mtrace v - \mtrace \pi _F v  , {\lld}_H\right)_{\Lambda, |\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD |\left[ \mtrace v-\mtrace I_h v-\sum _i \alpha_i \mtrace \varphi _i \right]{\lld}_H \\
-(\text{supp} (\mtrace \varphi _i )\subset \omega _i\cap \Lambda \, \forall i)  =\sum _j \int_{\patch\cap \Lambda}|\DD| \left[ \mtrace v-\mtrace I_h v-\alpha_j \mtrace \varphi _j \right]{\lld}_H\\
-=\sum _j \int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\lld}_H - \frac{\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi _j} \int_{\patch\cap \Lambda} |\DD|\mtrace \varphi _j{\lld}_H\\
-(\text{using ${\lld}_H$ constant on $\patch\cap \Lambda$})=0.
+\left(\mtrace v - \mtrace \pi _F v  , {\md}_H\right)_{\Lambda, |\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD |\left[ \mtrace v-\mtrace I_h v-\sum _i \alpha_i \mtrace \varphi _i \right]{\md}_H \\
+(\text{supp} (\mtrace \varphi _i )\subset \omega _i\cap \Lambda \, \forall i)  =\sum _j \int_{\patch\cap \Lambda}|\DD| \left[ \mtrace v-\mtrace I_h v-\alpha_j \mtrace \varphi _j \right]{\md}_H\\
+=\sum _j \int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\md}_H - \frac{\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi _j} \int_{\patch\cap \Lambda} |\DD|\mtrace \varphi _j{\md}_H\\
+(\text{using ${\md}_H$ constant on $\patch\cap \Lambda$})=0.
 \end{multline*}
@@
 
-%\subparagraph{Satisfaction of the assumptions of the 
-%abstract analysis}
+For the second assumption of lemma \ref{lemma23burman}, we recall that the bilinear form $b(v_h,{\md}_h)$ is continuous in the norms $\vertiii{v_h},\,\|{\md}_h\|_{L^2(\Lambda)}$. 
+Using lemma \ref{lemma:Lh_infsup}, it is straightforward to prove that there exists a constant $\beta$ such that
+\begin{equation}\label{relax_infsup}
+\beta \|{\md}_h\|_{H^{-\frac12}(\Lambda)} \leq \sup\limits_{v_h \in X_h} \frac{b(v_h,{\md}_h)}{\vertiii{v_h}} + \|{\md}_h-\pi_H {\md}_h\|_{L^2(\Lambda)}, \quad \forall {\md}_h \in Q_h\,.
+\end{equation}
+We define $\pi_H = \sum_j \pi_H^j$, where $\pi_H^j$ is the operator
+\begin{equation}\label{eq:projector}
+\pi_H^j w_{|\patch \cap \Lambda} =\frac{1}{|\Gamma_{\patch\cap \Lambda}|}\int_{\patch\cap \Lambda}|\DD| w\quad \forall j,
+\end{equation}   
+ Then, for any $w \in L^2(\Lambda)$ the following Poincarè inequality holds true, see for example \cite[Corollary B.65]{MR2050138},
+\begin{equation}\label{disc_poincare_ineq}
+\|w - \pi_H w\|_{L^2(\omega_j\cap\Lambda),|\DD|} \leq c_P H \|\partial_s w\|_{L^2(\omega_j\cap\Lambda),|\DD|}\,.
+\end{equation}
+We consider the following stabilization operator
+\begin{equation}\label{eq:stab}
+s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
+\end{equation}
+being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{G}_h$.
+Then, we use the result of \cite{burman2014}, Section III to show that
+\begin{equation*}
+    \|{\md}_h-\pi_H {\md}_h\|_{L^2(\Lambda)} \leq C s({\md}_h, {\md}_h)\,,
+\end{equation*}
+which combined with \eqref{relax_infsup} shows that the second assumption of lemma \ref{lemma23burman} holds true.
 
-The second step of the stability analysis of the stabilized 3D-1D-1D scheme, namely  \eqref{eq:prob2_stabilized}, consists of showing that \eqref{stab_coercivity} and \eqref{stab_stability} are satisfied.
-In particular, we consider the projection operator defined in \eqref{eq:projector} and the stabilization operator \eqref{eq:stab}.
-Also, the function $\xi_h([u_h, {\ud}_h])$ is defined as follows
+The third step of the analysis consists of showing that \eqref{stab_coercivity} and \eqref{stab_stability} are satisfied. 
+We introduce the following discrete norms
 \begin{equation*}
-{\xi_h}_{|\patch\cap \Lambda}=\delta \frac 1H \pi_L(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}.
+\|\, \lambda \,\|_{\pm \frac 12, h, \Lambda} = \|h^{\mp\frac 12} \lambda\|_{L^2(\Lambda)},
+\end{equation*}
+recalling that $h$ is the mesh size of $\mathcal{T}^\Omega_{h}$. We equip the space $X_h$ with the discrete norm
+\begin{equation*}
+\vertiii{[u_h, {\ud}_h]}^2_{X_h}
+= \|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|} + \|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|},
+\end{equation*}
+and the space $Q_H$ with the $L^2$ norm 
+$\|{\md}_H \|_{Q_H} = \|{\md}_H \|_{L^2(\Lambda)}$.
+
+Also, the function $\xi_h([v_h, {\vd}_h]) \in Q_H \subset Q_h \subset L^2(\Lambda)$ is defined as follows
+\begin{equation*}
+{\xi_h}_{|\patch\cap \Lambda}=\frac{\delta}{H} \pi_H(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}.
 \end{equation*}
@@
 \begin{lemma}
-The inequalities \eqref{stab_coercivity} and \eqref{stab_stability} are satisfied (under the previous assumptions).
+Given $\pi_H,\ s_h(\cdot,\cdot), \ \xi_h$ defined above, the inequalities \eqref{stab_coercivity} and \eqref{stab_stability} are satisfied.
 \end{lemma}
 \begin{proof} 
-Concerning the coercivity property \eqref{stab_coercivity}, we have to show that $\forall [u_h, {\ud}_h]$, there esists $\xi_h \in Q_h$ s.t.
+Concerning the coercivity property \eqref{stab_coercivity}, we show that $\forall [u_h, {\ud}_h]$, there exists $\xi_h \in Q_h$ s.t.
 \begin{equation*}
-(u_h,u_h)_{H^1(\Omega)}+ ({\ud}_h, {\ud}_h)_{H^1(\Lambda), |\D|} +   (\mtrace u_h - {\ud}_h, \xi_h)_{\Lambda,|\DD|} \geq \alpha_{\xi}\vertiii{[u_h, {\ud}_h]}^2_{X_h(\Omega)\times X_{h'}(\Lambda) }.
+(u_h,u_h)_{H^1(\Omega)}+ ({\ud}_h, {\ud}_h)_{H^1(\Lambda), |\D|} +   (\mtrace u_h - {\ud}_h, \xi_h)_{\Lambda,|\DD|} \geq \alpha_{\xi}\vertiii{[u_h, {\ud}_h]}^2_{X_h}.
 \end{equation*}
-Using the definitions of $\pi_L$ and $\xi_h([u_h, {\ud}_h])$ previously presented and recalling that $\mathcal{E}_{\patch}\xi_h\in L_H \subset Q_h$, we obtain
+Using the definitions of $\pi_H$ and $\xi_h([u_h, {\ud}_h])$ previously presented and recalling that $\xi_h\in Q_H \subset Q_h$, we obtain
 \begin{multline*}
@@
 \\
-(\text{definition of $\xi_h$})= \delta \frac{1}{H}\sum_j \pi_L( \mtrace u_h - {\ud}_h)\int_{\patch\cap \Lambda} |\DD|(\mtrace u_h - {\ud}_h)
+(\text{definition of $\xi_h$})= \frac{\delta}{H}\sum_j \pi_H^j( \mtrace u_h - {\ud}_h)\int_{\patch\cap \Lambda} |\DD|(\mtrace u_h - {\ud}_h)
 \\
-\left(|\Gamma_{\omega_j \cap \Lambda}| = \int_{\omega_j \cap \Lambda}|\DD|\right)= \delta \frac{1}{H} \sum_j \int_{\patch\cap \Lambda}|\DD| (\pi_L( \mtrace u_h - {\ud}_h) )^2
+\left(|\Gamma_{\omega_j \cap \Lambda}| = \int_{\omega_j \cap \Lambda}|\DD|\right)= \frac{\delta}{H} \sum_j \int_{\patch\cap \Lambda}|\DD| (\pi_H( \mtrace u_h - {\ud}_h) )^2
+= \frac{\delta}{H}\sum_j \|\pi_H( \mtrace u_h - {\ud}_h)\|_{L^2(\patch\cap \Lambda),|\DD|}
 \\
-(\text{orthogonality of $\pi_L$}) = - \delta \frac{1}{H} \|(\pi_L-\mathcal{I})(\mtrace u_h - {\ud}_h)\|^2_{L^2(\patch\cap \Lambda),|\DD|} + \delta \frac{1}{H} \|\mtrace u_h - {\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|}
+(\text{orthogonality of $\pi_H$}) = \frac{\delta}{H} \sum_j \left( \|\mtrace u_h - {\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} - \|(\pi_H-\mathcal{I})(\mtrace u_h - {\ud}_h)\|^2_{L^2(\patch\cap \Lambda),|\DD|} \right)
 \\ 
-\geq -2\delta \frac 1H \sum_j \|(\pi_L - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda), |\DD|}
--2 \delta \frac 1H \sum_j \|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|}
+\geq \frac{\delta}{H} \sum_j \left(
+\|\mtrace u_h-{\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|}
+- \|(\pi_H - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda), |\DD|}
+- \|(\pi_H - \mathcal{I}){\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} \right). 
+\end{multline*}
+For the second term we apply the additional assumption that the operators $\mtrace$ and $\partial_s$ commute. This is true if the cross section $\D$ does not depend on the arclength $s$.
+Then, we use the Poincar\'e inequality \eqref{disc_poincare_ineq}, the average inequality \eqref{eq:avrg_ineq} and the trace inequality \eqref{discr_trace_ineq} to show that,
+\begin{multline*}
+\sum _j  \|(\pi_H - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} 
+\leq C_P^2 H^2 \sum _j \|\partial_s \mtrace u_h\|_{L^2(\patch\cap \Lambda),|\DD|}^2
+= C_P^2 H^2 \sum _j \|\mtrace \partial_s  u_h\|_{L^2(\patch\cap \Lambda),|\DD|}^2
 \\
-+ \delta \frac 1H \sum_j \|\mtrace u_h-{\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|}. 
+\leq C H^2 \sum _j \|\trace \partial_s u_h\|_{L^2(\omega _j \cap \Gamma)}^2
+\leq C H \sum _j \|\nabla u_h\|_{L^2(\omega _j)}^2.
 \end{multline*}
-For the first term, we introduce the uniform extension operator  $\mathcal{E}_{\Gamma}$ from $\omega_j \cap \Lambda$ to the subset of $\Gamma$ with centerline $\omega_j \cap \Lambda$ and we have
+% old version, wrong
+% \begin{multline*}
+% \sum _j  \|(\pi_H - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} =\sum _j \int _{\patch \cap \Lambda} |\DD| (\pi_H \mtrace u_h- \mtrace u_h)^2
+% \\
+% (\text{Average inequality \eqref{eq:avrg_ineq}}) \leq \sum _j  \int_{\omega _j \cap \Gamma} (\ext \pi_H \mtrace u_h -\trace u_h)^2 
+% \\
+% (\text{trace inequality \eqref{discr_trace_ineq}}) \leq \sum _j  \frac 1H \int_{\omega_j}(\mathcal{E}_{\patch} \pi_H \mtrace u_h - u_h)^2 
+% \\ 
+% (\text{Poincare, see \cite[Corollary B.65]{MR2050138}})\leq \sum _j  H c_P ^2 \|\nabla u_h\|^2_{L^2(\omega _j)}.
+% \end{multline*}
+For the third term we proceed similarly,
 \begin{multline*}
-\sum _j  \|(\pi_L - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} =\sum _j \int _{\patch \cap \Lambda} |\DD| (\pi_L \mtrace u_h- \mtrace u_h)^2
+\sum _j \|(\pi_H - \mathcal{I}){\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} \leq C_P^2 H^2 \sum _j \|\partial_s {\ud}_h\|_{L^2(\patch\cap \Lambda),|\DD|}^2
 \\
-(\text{Average inequality \eqref{eq:avrg_ineq}}) \leq \sum _j  \int_{\omega _j \cap \Gamma} (\ext \pi_L \mtrace u_h -\trace u_h)^2 
-\\
-(\text{trace inequality \eqref{discr_trace_ineq}}) \leq \sum _j  \frac 1H \int_{\omega_j}(\mathcal{E}_{\patch} \pi_L \mtrace u_h - u_h)^2 
-\\ 
-(\text{Poincare, see \cite[Corollary B.65]{MR2050138}})\leq \sum _j  H c_P ^2 \|\nabla u_h\|^2_{L^2(\omega _j)}.
-\end{multline*}
-For the second term we have
-\begin{multline*}
-\sum _j \|(\pi_L - \mathcal{I}){\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD| (\pi_L {\ud}_h -{\ud}_h)^2
-\\
-(\text{Poincare, \cite[Corollary B.65]{MR2050138}})\lesssim \sum _j  H^2 c_P^2 \int_{\patch\cap \Lambda} |\DD|(\nabla {\ud}_h)^2
-\\
-(\text{since $H$ is fixed, we can find a constant s.t. } H|\DD| \lesssim |\D|) \lesssim \sum _j H c_P^2  \int_{\patch\cap \Lambda} |\D|(\nabla {\ud}_h)^2 
-\\
-\lesssim \sum _j H c_P^2  \|\nabla {\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\D|}.
+(\text{since $H$ is fixed, we can find a constant s.t. } H|\DD| \lesssim |\D|) C H \sum _j \|\partial_s {\ud}_h\|_{L^2(\patch\cap \Lambda),|\D|}^2.
 \end{multline*}
@@
 \geq \\
-(1-2\delta c_P^2) \|\nabla u_h\|^2_{L^2(\Omega)} + (1- 2\delta c_P^2) \|\nabla {\ud}_h\|^2_{L^2(\Lambda), |\D|}
+(1-\delta C) \|\nabla u_h\|^2_{L^2(\Omega)} + (1- \delta C) \|\partial_s {\ud}_h\|^2_{L^2(\Lambda), |\D|}
 +\delta c_H  \|\mtrace u_h-{\ud}_h\|^2_{\frac 12,h,\Lambda, |\DD|}
 \end{multline*}
-and choosing $\delta=\frac{1}{4c_P^2}$ we obtain the desired inequality.\\
-Concerning the stability inequality \eqref{stab_stability}, the proof is analogous to the one in \cite{burman2014}.
+and choosing $\delta=\frac{1}{2C}$ we obtain the desired inequality.\\
+Concerning inequality \eqref{stab_stability}, the proof is analogous to the one in \cite{burman2014}.
 \end{proof}
 
-\begin{remark}
-We notice that if we choose $Q_h=X_{h',0}^1(\Lambda)$, the constant in the inf-sup inequality  \eqref{eq:infsup_discrete} depends on the mesh size $h'$. Indeed,
-\begin{multline}
-\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\lld} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}}
-\geq \sup_{\substack{{\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(- {\vd}_h, {\lld} _H\right)_{\Lambda, |\DD|}}{\|{\vd}_h\|_{H^1(\Lambda)}}
-\geq \frac{{\|\lld} _H\|^2_{L^2(\Lambda)}}{\|{\vd}_h\|_{H^1(\Lambda)}} \\
-( \text{inverse inequality} )\geq \frac{{h'}^2}{c_I} \|{\lld}_H\|_{L^2(\Lambda)}
-\geq  \frac{{h'}^2}{c_I} \|{\lld}_H\|_{H^{-\frac 12},(\Lambda)}
-\end{multline}
-being $c_I$ the constant in the inverse inequality
-\begin{equation*}
-\|{\lld}_H\|_{H^1(\Lambda)} \leq \frac{c_I} {{h'}^2} \|{\lld}_H\|_{L^2(\Lambda)}. 
-\end{equation*}
-\end{remark}
+% \begin{remark}
+% We notice that if we choose $Q_h=X_{h',0}^1(\Lambda)$, the constant in the inf-sup inequality  \eqref{eq:infsup_discrete} depends on the mesh size $h'$. Indeed,
+% \begin{multline}
+% \sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\md} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}}
+% \geq \sup_{\substack{{\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(- {\vd}_h, {\md} _H\right)_{\Lambda, |\DD|}}{\|{\vd}_h\|_{H^1(\Lambda)}}
+% \geq \frac{{\|\md} _H\|^2_{L^2(\Lambda)}}{\|{\vd}_h\|_{H^1(\Lambda)}} \\
+% ( \text{inverse inequality} )\geq \frac{{h'}^2}{c_I} \|{\md}_H\|_{L^2(\Lambda)}
+% \geq  \frac{{h'}^2}{c_I} \|{\md}_H\|_{H^{-\frac 12},(\Lambda)}
+% \end{multline}
+% being $c_I$ the constant in the inverse inequality
+% \begin{equation*}
+% \|{\md}_H\|_{H^1(\Lambda)} \leq \frac{c_I} {{h'}^2} \|{\md}_H\|_{L^2(\Lambda)}. 
+% \end{equation*}
+% \end{remark}

### 2020-02-28 benchmark.tex
Paolo's revision sections 2-3
merge tables

@@
 %%   %%%
-\begin{minipage}[b]{0.35\linewidth}
+\begin{minipage}[c]{0.35\linewidth}
  \centering
  \includegraphics[width=\textwidth]{graphics/conform_mesh.pdf}
- \vspace{-20pt}
+ \vspace{20pt}
+ \includegraphics[width=\textwidth]{graphics/nonconform_mesh.pdf} 
+ \vspace{-40pt}
  \captionof{figure}{
+   (Top)
 $\Lambda$ and $\Gamma$ conforming discretization of $\Omega$
    used for \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}.
+   (Bottom) Sample discretization of the benchmark geometry in the non-conforming case. 
  }
@@
 \hspace{2pt}
-\begin{minipage}[b]{0.63\textwidth}
+\begin{minipage}[c]{0.63\textwidth}
   \scriptsize{
@@
     \begin{tabular}{l|llll}
-      \toprule
+\hline
+\multicolumn{5}{c}{\textcolor{blue!40!white}{$\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}}\\
+\hline
     $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\lambda-\lambda_h}_{-\tfrac{1}{2},\Gamma}$ & $\norm{\lambda-\lambda_h}_{0,\Gamma}$\\
@@
 64 & 2.2E-1(1.00) & 3.1E-2(1.00) & 8.6E-3(2.00) &4.2E-2(1.68) \\
-\midrule
+\hline
 $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-u_{\odot, h^{\prime}}}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{-\tfrac{1}{2}, \Lambda}$ & $\norm{\ld-\ldh}_{0, \Lambda}$\\
@@
 128 & 1.1E-1(1.00) & 1.6E-2(1.00) & 4.1E-5(2.01) & 7.4E-5(2.00)\\
-\bottomrule
+\hline
+\multicolumn{5}{c}{\textcolor{red!50!white}{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$}}\\
+%    \begin{tabular}{l|lll}
+\hline
+    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & \multicolumn{2}{c}{$\norm{\ld-\ldh}_{0,\Lambda}$}\\
+      \hline
+5   & 2.6E0(--)    & 2.3E-1(--)   & \multicolumn{2}{c}{1.7E-1(--)} \\ 
+9   & 1.5E0(0.84)  & 9.4E-2(1.42) & \multicolumn{2}{c}{7.1E-2(1.36)}\\
+17  & 8.1E-1(0.94) & 4.3E-2(1.18) & \multicolumn{2}{c}{2.9E-2(1.37)}\\
+33  & 4.2E-1(0.98) & 2.1E-2(1.06) & \multicolumn{2}{c}{7.9E-3(1.91)}\\
+65  & 2.1E-1(0.99) & 1.1E-2(1.02) & \multicolumn{2}{c}{2.6E-3(1.64)}\\
+129 & 1.1E-1(1.00) & 5.2E-3(1.01) & \multicolumn{2}{c}{8.5E-4(1.61)}\\
+\hline
     \end{tabular}
@@
   }
-  \captionof{table}{Error convergence of \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}
-    on a benchmark problem \eqref{benchmark}. Continuous linear Lagrange
-    elements are used.
+  \captionof{table}{Error convergence on a benchmark problem \eqref{benchmark}.
+    (Top) problem \eqref{eq:problem1_simple}, (middle) \eqref{eq:problem2_simple} wity
+    conforming disretization and (bottom) \eqref{eq:problem2_simple} in case
+    $\mathcal{T}^{\Omega}_h$ does not conform to $\Lambda$. Continuous linear Lagrange
+    elements are used for $u_h$, $\udh$ and $u_{\odot, h^{\prime}}$ and $\ldh$ in
+    conforming case, while in nonconforming case $\ldh$ is piecewise constant
+    on elements of $\mathcal{G}_h$.
   }
@@
 We plot the numerical solution of problem \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} in
-Figure \ref{fig:sol_benchm1} and \ref{fig:sol_benchm2}, respectively.
+Figure \ref{fig:sol_benchm1}.
 
@@
 \centering
-\includegraphics[width = 0.9\textwidth]{./graphics/mfs_LM2d}
-\caption{Numerical solution of problem \eqref{eq:problem1_simple}: functions $u_h$ and $\udh$ on the left and the Lagrance multiplier $\lambda_h$ on the right.}\label{fig:sol_benchm1}
+\includegraphics[width = 0.6\textwidth]{./graphics/mfs_LM2d}
+\includegraphics[width = 0.3\textwidth]{./graphics/mfs_LM1d_crop}
+\caption{Numerical solution of problem \eqref{eq:problem1_simple} and
+  \eqref{eq:problem2_simple}. (Left) function $u_h$, $\udh$ (practically identical
+  in both problems). (Middle) Lagrange multiplier for \eqref{eq:problem1_simple}
+  and (right) for \eqref{eq:problem2_simple}.}
+\label{fig:sol_benchm1}
 \end{figure}
 
-\begin{figure}
-\centering
-\includegraphics[width = 0.9\textwidth]{./graphics/mfs_LM1d}
-\caption{Numerical solution of problem \eqref{eq:problem2_simple}: functions $u_h$ and $\udh$ on the left and the Lagrance multiplier ${\ld}_h$ on the right.}\label{fig:sol_benchm2}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width = 0.9\textwidth]{./graphics/mfs_LM1d}
+%\caption{Numerical solution of problem \eqref{eq:problem2_simple}:
+%  functions $u_h$ and $\udh$ on the left and the Lagrance multiplier
+%  ${\ld}_h$ on the right.}\label{fig:sol_benchm2}
+%\end{figure}
 
@@
 lying on $\Lambda$. Further we let $h^{\prime}=h/3$ in $\mathcal{T}^{\Lambda}_{h^{\prime}}$,
-cf. Figure \ref{fig:unfit}.
+cf. Figure \ref{fig:mesh}.
 
-Using discretization in terms of $P_1$-$P_1$-$P_0$ element Table \ref{tab:error_unfit}
+Using discretization in terms of $P_1$-$P_1$-$P_0$ element Table \ref{tab:error_conform}
 lists the error of the stabilized formulation of \eqref{eq:problem2}. A linear
@@
 
-\begin{table}
+%% \begin{table}
+%% %%   %%%
+%% \begin{minipage}[b]{0.35\linewidth}
+%%  \centering
+%%  \includegraphics[width=\textwidth]{graphics/nonconform_mesh.pdf}
+%%  \vspace{-20pt}
+%%  \captionof{figure}{
+%%    Sample discretization of the benchmark geometry in the non-conforming case. 
+%%  }
+%% \label{fig:unfit}
+%% \end{minipage}
+%% \hspace{2pt}
 %% %%%
-\begin{minipage}[b]{0.35\linewidth}
- \centering
- \includegraphics[width=\textwidth]{graphics/nonconform_mesh.pdf}
- \vspace{-20pt}
- \captionof{figure}{
-   Sample discretization of the benchmark geometry in the non-conforming case. 
- }
-\label{fig:unfit}
-\end{minipage}
-\hspace{2pt}
-%%%
-    \begin{minipage}[b]{0.62\linewidth}
-      %%%
-  \scriptsize{
-  \begin{center}
-    \begin{tabular}{l|lll}
-      \toprule
-    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{0,\Lambda}$\\
-      \hline
-5   & 2.6E0(--)    & 2.3E-1(--)   & 1.7E-1(--) \\ 
-9   & 1.5E0(0.84)  & 9.4E-2(1.42) & 7.1E-2(1.36)\\
-17  & 8.1E-1(0.94) & 4.3E-2(1.18) & 2.9E-2(1.37)\\
-33  & 4.2E-1(0.98) & 2.1E-2(1.06) & 7.9E-3(1.91)\\
-65  & 2.1E-1(0.99) & 1.1E-2(1.02) & 2.6E-3(1.64)\\
-129 & 1.1E-1(1.00) & 5.2E-3(1.01) & 8.5E-4(1.61)\\
-\bottomrule
-    \end{tabular}
-  \end{center}    
-}    
-  \captionof{table}{
-    Error convergence of \eqref{eq:problem2_simple} on a benchmark problem \eqref{benchmark} in case
-    $\mathcal{T}^{\Omega}_h$ does not conform to $\Lambda$.}
-  \label{tab:error_unfit}    
-  \end{minipage}
-\end{table}
+%%     \begin{minipage}[b]{0.62\linewidth}
+%%       %%%
+%%   \scriptsize{
+%%   \begin{center}
+%%     \begin{tabular}{l|lll}
+%%       \toprule
+%%     $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{0,\Lambda}$\\
+%%       \hline
+%% 5   & 2.6E0(--)    & 2.3E-1(--)   & 1.7E-1(--) \\ 
+%% 9   & 1.5E0(0.84)  & 9.4E-2(1.42) & 7.1E-2(1.36)\\
+%% 17  & 8.1E-1(0.94) & 4.3E-2(1.18) & 2.9E-2(1.37)\\
+%% 33  & 4.2E-1(0.98) & 2.1E-2(1.06) & 7.9E-3(1.91)\\
+%% 65  & 2.1E-1(0.99) & 1.1E-2(1.02) & 2.6E-3(1.64)\\
+%% 129 & 1.1E-1(1.00) & 5.2E-3(1.01) & 8.5E-4(1.61)\\
+%% \bottomrule
+%%     \end{tabular}
+%%   \end{center}    
+%% }    
+%%   \captionof{table}{
+%%     Error convergence of \eqref{eq:problem2_simple} on a benchmark problem \eqref{benchmark} in case
+%%     $\mathcal{T}^{\Omega}_h$ does not conform to $\Lambda$.}
+%%   \label{tab:error_unfit}    
+%%   \end{minipage}
+%% \end{table}
 
 \subsection{Comparison}
-In Tables \ref{tab:error_conform}, \ref{tab:error_unfit} one can observe that 
+In Tables \ref{tab:error_conform}, \ref{tab:error_conform} one can observe that 
 all the formulations yield practically identically accurate approximations of $u$.
@@
     \begin{tabular}{l|lll|lll|lll|ll}
-      \toprule
+      %\toprule
+      \hline
       \multirow{2}{*}{$l$} & \multicolumn{3}{c|}{\eqref{eq:problem1}} & \multicolumn{3}{c|}{\eqref{eq:problem2}} & \multicolumn{3}{c|}{ Stabilized \eqref{eq:problem2}} & \multicolumn{2}{c}{\eqref{benchm_3d}}\\
@@
       6 & -- & --    & --    & 17 & 28.77 & --   & 507 & 832.90 & --    &6 & 7.75  \\
-      \bottomrule
+      \hline
+      %\bottomrule
     \end{tabular}
@@
 
-%\begin{remark}
-%Let us notice that the 3D solution \eqref{benchm_sol3d} is such that $\avrc{u}=0$.
-Therefore in \eqref{benchmark} it is like we are solving two separated problems, one in $\Omega$ and the other on $\Lambda$.
+%{\color{red}
+%\begin{remark} In the following some observations:\\
+%
+%\begin{itemize}
+%\item \textbf{How do we compute the norm $\|\cdot \|_{H^{-\frac 12}}$ in Table \ref{tab:error_conform}?} The norm $\|\cdot \|_{H^{-\frac 12}}$ has been computed using a decomposition based on eigenvalues and eigenfuctions of $\Delta ^{-\frac 12}$.\\
+%
+%\item \textbf{Why $\lambda _h \neq \lambda$?} Since $\lambda = 0 \in Q_h$, we would expect $\lambda _h = \lambda$.
+However, first of all we suspect that for the approximation error an estimate similar to \cite[(11.26)]{steinbach2007numerical} holds, reported in the following
+%\begin{equation*}
+%\|u-u_h\|^2_{H^1} + \|\lambda - \lambda_h\|^2_{H^{-\frac 12}} \leq c_1 h^2|u|^2_{H^2} + c_2 h^3\|\lambda_h\|^2_{H^1_{pw}},
+%\end{equation*}
+%where $\|\cdot \|_{H^1_{pw}}$ is the broken $H^1$ norm. 
+%So the error on the LM depends on the error on the solution.
+We suspect that if for example $u$ and $\ud$ are $P_2$ functions and we use a $P_2$ approximation (therefore $u = u_h$ and $\ud = \udh$), also $\lambda = \lambda_h$.\\
+%
+%\item \textbf{Why the error is larger close to edges, especially in Figure \ref{fig:sol_benchm1}?} 
+%We suspect that the reasoning for why the error is larger close to edges and corner vertices is that the multiplier is
+%related to $\nabla u \cdot \boldsymbol{n}$ and the normal in the corner or on the z-aligned edges in the figure is not well-defined. Btw, the oscillations are smaller if we impose Neumann
+%bcs on z min and max surfaces of $\Omega$ (the rest has Dirichlet).
+%\end{itemize}
 %\end{remark}
-%\begin{remark}
-%It would be interesting to make a comparison between the solution of the fully coupled 3D-3D problem \eqref{eq:dirneu} (also in the simplified case of type \eqref{eq:dirneu_simple}) and the solution of the reduced problems \eqref{eq:problem1} and \eqref{eq:problem2}.
-%Therefore, we could set the values of the data of the problem such that the reduced formulation becomes non-trivial and fully coupled.
-%Then, we will solve both the original and reduced problem to observe the differences in the solutions and the values of the Lagrange multiplier.
-%\end{remark}
+%}

### 2020-02-28 graphics/domain.tex
merge tables

\documentclass{standalone}

\usepackage{tikz}
\usetikzlibrary{shapes, snakes, patterns, arrows}
\usetikzlibrary{calc}
\usepackage{pgfplots}
\usepgfplotslibrary{fillbetween}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}

\begin{document}
\begin{tikzpicture}

% Omega
\draw[] (0, 2) ellipse (2. and 0.5);
\draw (-2.,2) -- (-2.,-2);
\draw (-2.,-2) arc (180:360:2. and 0.5);
\draw [dashed] (-2.,-2) arc (180:360:2. and -0.5);
\draw (2.,-2) -- (2., 2);
% Top whole
\draw[blue, thick] (-0.75, 2) ellipse (0.6 and 0.15);
% Bottom whole
\draw[blue, thick] (0.75, -2) ellipse (0.6 and 0.15);
% Auxliary middle surface
\draw [dashed, thin](-2., 0) arc (180:360:2. and 0.5);
\draw [dashed, thin] (-2.,0) arc (180:360:2. and -0.5);

\fill[pattern color=cyan, pattern=north east lines] (0.5, 0) ellipse (0.5 and 0.125);
\node [cyan, below right, fill=white, opacity=0.8] at (0.5, 0.0) {$\mathcal{D}(s)$};

\node[mark size=1.5pt, color=red] at (0.5, 0.0) {\pgfuseplotmark{*}};

% Walls of gamma
\draw [blue, thick, name path global = topleft] plot [smooth, tension=1] coordinates { (-1.35,2) (-0.6, 1) (0,0)};
\draw [blue, thick, name path global = botleft] plot [smooth, tension=1] coordinates { (0,0) (0.125, -1) (0.15,-2)};

\draw [blue, thick, name path global = topright] plot [smooth, tension=1] coordinates { (-0.15,2) (0.5, 1) (1.0,0)};
\draw [blue, thick, name path global = botright] plot [smooth, tension=1] coordinates { (1.0,0) (1.25, -1) (1.35,-2)};

%\fill [gray, opacity=0.5] (-1.25,0) -- (-1.25,-3.5) arc (180:360:1.25 and 0.5) -- (1.25,0) arc (0:180:1.25 and -0.5);

\tikzfillbetween[of=topleft and topright]{blue!40!white, opacity=0.2};
\tikzfillbetween[of=botleft and botright]{blue!40!white, opacity=0.2};
\fill[blue!40!white, opacity=0.2] (-1.35, 2) arc (180:360:0.6 and -0.15) -- (-0.75, 2);
\fill[blue!40!white, opacity=0.2] (0.15, -2) arc (180:360:0.6 and 0.15) -- (-0.15, -2);
\node[blue, fill=white, opacity=0.7, above] at (1.15, -2) {$\Omega_{\ominus}$};

% Curve
\draw [very thick, red] plot [smooth, tension=1] coordinates { (-0.75,2) (0.5, 0) (0.75,-2)};
\node[red, fill=white, opacity=0.7] at (0.075, 1) {$\Lambda$};

\node[] at (-0.5, -1) {$\Omega_{\oplus}$};

\node[blue] at (0.75, 1) {$\Gamma$};

%\fill [white!50!blue, opacity=0.5] (-1.,0) -- (-1.,-3.5) arc (180:360:1. and 0.3) -- (1., 1) arc (0:180:1. and -0.3);
%% % Outer guy
%% \draw (0,0) ellipse (1.25 and 0.5);
%% \draw (-1.25,0) -- (-1.25,-3.5);
%% \draw (-1.25,-3.5) arc (180:360:1.25 and 0.5);
%% \draw [dashed] (-1.25,-3.5) arc (180:360:1.25 and -0.5);
%% \draw (1.25,-3.5) -- (1.25,0);  
%% \fill [gray, opacity=0.5] (-1.25,0) -- (-1.25,-3.5) arc (180:360:1.25 and 0.5) -- (1.25,0) arc (0:180:1.25 and -0.5);
%% %
%% \draw [red, thick] (0, -3.5, 0) -- (0, 1.7);
%% \node [right, blue] at (0, 1.7) {$\vec{n}$};
%% \node [right] at (0, -1.5) {$\Lambda$};
%% %
%% \node [below, gray] at (0, -4) {$\Omega$};
%% %
%% \node [right, blue] at (0, 1) {$y$};
%% \draw [very thick, blue, ->] (0, 1) -- (0, 1.5);

%% \node [right, blue] at (1, 1) {$\mathcal{C}_R(y)$};
%% \draw [dashed] (0, 1) -- (-1, 1);
%% \node [above] at (-1, 1.1) {$R$};
%% \node[mark size=1.5pt, color=blue] at (0, 1) {\pgfuseplotmark{*}};
% Middle whole
\draw [very thick, cyan] (0, 0) arc (180:360:0.5 and 0.125);
\draw [very thick, dashed, cyan] (0,0) arc (180:360:0.5 and -0.125);
\node [left, cyan] at (0, 0) {$\partial\mathcal{D}(s)$};

%\node[left] at (0, -2) {$\partial\Omega$};
%\node[right] at (0, 2) {$\partial\Omega$};
%\node[right] at (2, 1) {$\partial\Omega$};

\end{tikzpicture}
\end{document}

### 2020-02-28 3d1d_coupled_LM.tex
fig next to eqs in intro

@@
 
-In this paper we will consider a 3D-1D coupled problem described by the following equations: 
+In this paper we will consider a 3D-1D coupled problem described by the following equations:\\
+\begin{minipage}{0.5\textwidth}
 \begin{subequations}
@@
 \end{subequations}
+\end{minipage}
+%
+\begin{minipage}{0.45\textwidth}
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=0.6\textwidth]{domain.pdf}
+\end{center}
+\caption{Geometrical setting of the problem}
+\label{fig1}
+\end{figure}
+\end{minipage}\\
 Here, $u$ and $\ud$ are the unknown scalar fields,  $\lambda$ is the Lagrange multiplier,  $\Omega$ is a bounded domain in $\R^3$, whereas $\Lambda \subset \Omega$ is a 1D structure. 
@@
 $|\cdot|$ denote the Lebesgue measure of a set, i.e. $|D(0)|$ is the cross-sectional area of the bottom of the cylinder.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.5\textwidth]{domain.pdf}
-\end{center}
-\caption{Geometrical setting of the problem}
-\label{fig1}
-\end{figure}
 

### 2020-03-02 3d1d_coupled_LM.tex
Updates from Overleaf

@@
 In this paper we will consider a 3D-1D coupled problem described by the following equations:\\
-\begin{minipage}{0.5\textwidth}
 \begin{subequations}
@@
 \label{eq:pde2}
--\Delta \ud + \ud - \lambda &= g &\mbox{ on } \Lambda,\\
+ d_s^2 \ud + \ud - \lambda &= g &\mbox{ on } \Lambda,\\
 \label{eq:coupling}
-T_\Lambda u - v  &=  h &\mbox{ on } \Lambda . 
+\mathcal{T}_\Lambda u - v  &=  h &\mbox{ on } \Lambda . 
 \end{align}
 \end{subequations}
-\end{minipage}
 %
-\begin{minipage}{0.45\textwidth}
-\begin{figure}[H]
-\begin{center}
-\includegraphics[width=0.6\textwidth]{domain.pdf}
-\end{center}
-\caption{Geometrical setting of the problem}
-\label{fig1}
-\end{figure}
-\end{minipage}\\
-Here, $u$ and $\ud$ are the unknown scalar fields,  $\lambda$ is the Lagrange multiplier,  $\Omega$ is a bounded domain in $\R^3$, whereas $\Lambda \subset \Omega$ is a 1D structure. 
-The term $p\delta_{\Lambda}$ is a Dirac measure such that 
-$\int_{\Omega}p(x)\delta_{\Lambda}v(x)\,\mathrm{d}x=\int_{\Lambda}p(t)v(t) \,\mathrm{d}t$
-for a continuous function $v$.
+Here, $u$, $\ud$,  $\lambda$ are unknowns,  $\Omega$ is a bounded domain in $\R^3$, whereas $\Lambda \subset \Omega$ is a 1D structure
+parameterized in terms of $s$ and $d_s$ is the derivative with respect to $s$. 
+The term $\lambda\delta_{\Lambda}$ is a Dirac measure such that 
+$\int_{\Omega}\lambda(x)\delta_{\Lambda}v(x)\,\mathrm{d}x=\int_{\Lambda}\lambda(t)v(t) \,\mathrm{d}t$
+for a continuous function $v$ and $\mathcal{T}_\Lambda: \Omega\rightarrow\Lambda$ is a trace operator.
 
-From a mathematical point of view, the challenge involved in problem \eqref{eq:pde} is that neither $T_\Lambda$ nor $\delta_\Lambda$ are well defined.
-That is, traces of co-dimension one are well defined, while here we face traces of co-dimension two, mapping 3D functions to 1D functions.
-Similarly, Dirac delta functions are well defined on measures of one lower dimension, but not two.
-Several studies \cite{DAngelo,..} have remedied the well-posedness by weakening the solution concept.
+From a mathematical point of view, the challenge involved in problem \eqref{eq:pde} is that neither $\mathcal{T}_\Lambda$ nor $\delta_\Lambda$ are well defined. 
+That is, without extra regularity,  solutions of elliptic PDEs only have well defined traces of co-dimension one.
+Here, $\mathcal{T}_\Lambda$ is of co-dimension two, mapping functions defined on a domain in 3D to
+functions defined along a 1D curve.
+Similarly, Dirac delta functions are well defined on measures of co-dimension one, but not two.
+Several studies \cite{DAngelo,d2012finite,d2008coupling} have remedied the well-posedness by weakening the solution concept.
 The approach naturally leads to non-symmetric formulations.
@@
 Both of these approaches have successfully be analyzed in a discrete setting and implemented~\cite{}.
+Error estimates etc...
+Many more references can be mentioned.
+In this work we analyze an alternative approach, closely related to \cite{laurino_m2an}, where we exploit the fact that the $\Lambda$ is not strictly a 1D curve, but rather a very thin 3D structure with
+a cross-sectional area far below what we can resolve. With this additional assumption, we show that robustness with respect to the cross-sectional area can be restored.
 
-The mathematical problem is motivated by the fact that many problems in geophysics and bio-mechanics are characterized by slender cylindrical structures coupled to larger 3D body, where the characteristic transverse length scale of the slender structure is many orders of magnitude smaller than the longitudinal length scale.
+The mathematical problem is motivated by the fact that many problems in geo- and biophysics are characterized by slender cylindrical structures coupled to a larger 3D body, where the characteristic transverse length scale of the slender structure is many orders of magnitude smaller than the longitudinal length.
 For example, in geophysical applications the radius of wells are often of the order of 10 cm while the length may be several kilometers~\cite{gjerde2019singularity}.
 Similarly, in applications involving the blood flow and oxygen transport of the micro-circulation the capillary radius is a few microns, while simulations are often performed on mm to cm scale, with thousands of vessels~\cite{berg2020modelling,fang2008oxygen,gould2017capillary}.
-Finally, in neuro-science applications a neuron has with a few microns, while  its length is much longer.
-For examples motor neurons may be as long as a meter.
+Finally, in neuro-science applications a neuron has width of a few microns, while  its length is much longer.
+For example, an axon of a motor neurons may be as long as a meter.
 Hence,  at least 4 orders of magnitude in difference in transverse and longitudinal direction is common in both geo-physics, bio-mechanics and neuro-science.
@@
 Even if adaptive and strongly anisotropic meshes are allowed for, the computations quickly become demanding if many slender structures and their interactions are under study.
-If the quantity of interest is the far field impact caused by processes in the slender structures, the high resolution involved in the near field of the slender structure may not be needed.
+If the quantity of interest is the far field impact (relative to the transverse lengthscale) caused by processes in the slender structures, the high resolution involved in the near field of the slender structure may not be needed.
 
-In this work we propose to analyze the problem in terms of an intermediate problem, posed either explicitly or implicitly. The intermediate problem reads, 
+An intermediate problem, where the coupling between the 3D and 1D problems of \eqref{eq:pde} is a 2D surface, reads 
 \begin{subequations}
@@
 \label{inteq:pde2}
--\Delta \ud + \ud - E' \lambda  &= g &\mbox{ on } \Lambda,\\
+-d_s² \ud + \ud - E' \lambda  &= g &\mbox{ on } \Lambda,\\
 \label{inteq:coupling}
@@
 and $E$ is an extension operator from $\Lambda$ to $\Gamma$.
-\kent{check consistency with notation}
 
+\kent{
 Detail the approach and result a bit.
-\kent{either here or later, something like the below}
-The setting of this paper is quite
+Mention that some stuff is 
 similar to~\cite{laurino_m2an}, but for completeness and the readers convenience we repeat some basic derivations. 
+}
 
@@
 This is a non trivial objective because the standard trace operator form a domain $\Omega$ to a subset $\Lambda$ is not well posed if $\Lambda$ is a manifold of co-dimension two of $\Omega$.
+
+%This work is based on the assumption that \emph{the transversal diameter of $\Omega_{\ominus}$ is small compared to the diameter of $\Omega$}. 
+%Let $d= \max_{s \in (0,S)} \mathrm{diam}(\D(s))$ be the largest diameter of the cross sections of $\Omega_{\ominus}$, that is the transversal diameter of $\Omega_{\ominus}$.
+%The central assumption of this work is that $d \ll \mathrm{diam}(\Omega)$.
+%Let us now scale the domains $\Omega$ and $\Omega_{\ominus}$.
+%Let $\chi_{\Omega}(\xx) = \xx / \mathrm{diam}(\Omega)$ be a scaling function and let be $\Omega_\chi = \chi_{\Omega}(\Omega), \ {\Omega_{\ominus}}_\chi =  \chi_{\Omega}(\Omega_{\ominus})$ be the scaled domains.
+%The previous assumption implies that for the scaled domains $\epsilon = d_\chi = d/\mathrm{diam}(\Omega)$
+%is such that $0 < \epsilon \ll 1$. For simplicity of notation, and without loss of generality, form now on we will implicitly refer to the scaled domains dropping the subindex $\chi$.
+%\kent{this is a good explanatory paragraph, but not sure we use the notation introduced}
 
@@
 
-%\subsection{Geometry of the problem}
-The domain is denoted as $\Omega\in \RR^3 $ is convex and composed by two parts, 
+Let the domain $\Omega\in \R^3 $ be convex and composed of two parts, 
 $\Omega_{\ominus}$ and $\Omega_{\oplus}:=\Omega\setminus\overline{\Omega}_{\ominus}$. 
-Let $\Omega_{\ominus}$ be a \emph{generalized cylinder}, 
-that is the swept volume of a two dimensional set moved along a curve in the three-dimensional space, see for example \cite{MR1940257}.
-We also assume that $\Omega_{\ominus}$ crosses $\Omega$ from side to side, and we call $\Gamma$ the lateral surface of $\Omega_{\ominus}$, 
+Let 
+$\Omega_{\ominus}$ be a \emph{generalized cylinder}, c.f.  \cite{MR1940257}, 
+that is; the swept volume of a two dimensional set, $\partial D$, moved along a curve, $\Lambda$, in the three-dimensional domain, $\Omega$, see for Figure \ref{fig1} for an illustration. 
+In detail, the curve 
+$\Lambda = \{\boldsymbol \lambda(s), \ s\in(0,S)\}$,  where 
+$\boldsymbol \lambda(s) = [\xi(s), \tau(s), \zeta(s)], \ s\in(0,S)$ is a $\mathcal{C}^2$-regular curve in the three-dimensional domain $\Omega$.
+For simplicity, let us assume that $\|\boldsymbol \lambda^\prime(s)\|=1$ such that the arc-length and the coordinate $s$ coincide.
+Further, let $\mathcal{D}(s) = [x(r,t),y(r,t)]: (0,R(s))\times(0,T(s)) \rightarrow \R^2$ be a parametrization of the cross section
+and $\Gamma$ be the lateral surface of $\Omega_{\ominus}$, i.e.
+$\Gamma=\{ \ \partial D(s) \  | \ s \in \Gamma\}$,
 while the upper and lower faces of $\Omega_{\ominus}$ belong to $\partial\Omega$. 
-Let $\boldsymbol \lambda(s) = [\xi(s), \tau(s), \zeta(s)], \ s\in(0,S)$ be a $\mathcal{C}^2$-regular curve in the three-dimensional space.
-For simplicity, let us assume that $\|\boldsymbol \lambda^\prime(s)\|=1$ such that the arc-length and the coordinate $s$ coincide.
-Let $\Lambda = \{\boldsymbol \lambda(s), \ s\in(0,S)\}$ be the centerline of the cylinder. 
+We will assume that $\Omega_{\ominus}$ crosses $\Omega$ from si
+de to side.
 According to the geometrical setting, we will denote with $v,\,v_\oplus,\,v_\ominus,\,\vd$,
 functions defined on $\Omega,\,\Omega_{\oplus},\,\Omega_{\ominus},\,\Lambda$, respectively.
-We refer to Figure \ref{fig1} for a sketch of the domains.
-Let $\mathcal{D}(s) = [x(r,t),y(r,t)]: (0,R(s))\times(0,T(s)) \rightarrow \R^2$ be a parametrization of the cross section, while 
-$|\cdot|$ denote the Lebesgue measure of a set, i.e. $|D(0)|$ is the cross-sectional area of the bottom of the cylinder.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=0.3\textwidth]{domain.pdf}
+\end{center}
+\caption{Geometrical setting of the problem}
+\label{fig1}
+\end{figure}
 
@@
 
-This work is based on the assumption that \emph{the transversal diameter of $\Omega_{\ominus}$ is small compared to the diameter of $\Omega$}. 
-Let $d= \max_{s \in (0,S)} \mathrm{diam}(\D(s))$ be the largest diameter of the cross sections of $\Omega_{\ominus}$, that is the transversal diameter of $\Omega_{\ominus}$.
-The central assumption of this work is that $d \ll \mathrm{diam}(\Omega)$.
-Let us now scale the domains $\Omega$ and $\Omega_{\ominus}$.
-Let $\chi_{\Omega}(\xx) = \xx / \mathrm{diam}(\Omega)$ be a scaling function and let be $\Omega_\chi = \chi_{\Omega}(\Omega), \ {\Omega_{\ominus}}_\chi =  \chi_{\Omega}(\Omega_{\ominus})$ be the scaled domains.
-The previous assumption implies that for the scaled domains $\epsilon = d_\chi = d/\mathrm{diam}(\Omega)$
-is such that $0 < \epsilon \ll 1$. For simplicity of notation, and without loss of generality, form now on we will implicitly refer to the scaled domains dropping the subindex $\chi$.
-\kent{this is a good explanatory paragraph, but not sure we use the notation introduced}
-
 % >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
@@
 
-Let $D$ be a generic regular bounded domain in $\R^3$. 
-Let $X$ be a Hilbert space defined on $D$.
-Let $(\cdot,\cdot)_X$ denote the inner product of $X$.
-Let $(\cdot,\cdot)_L^2(D)$,  $(\cdot,\cdot)_D$ or simply $(\cdot,\cdot)$ be the $L^2(D)$ inner product on $D$.
-For the 1D domain $\Lambda$ we will frequently use
-weighted $L^2$ inner products, denoted as follows
-\begin{equation*}
-(\ud,\vd)_{\Lambda,w} = \int_0^S w(s) \ud(s) \vd(s) ds\,.
-\end{equation*}
-Given an Hilbert space $X$ and its dual $X^*$, the duality pairing between the two is denoted as $\langle\cdot,\cdot\rangle$.
-When needed, the integration weights will be also applied to the duality product.
-\kent{I think we use weighted H1 as well.}
-
+Let $D$ be a generic regular bounded domain in $\R^3$
+and $X$ be a Hilbert space defined on $D$ then  $(\cdot,\cdot)_X$ and $\|\cdot\|_X$ denote the inner product and norm of $X$, respectively.
+The duality pairing between the $X$ and its dual $X^*$ is denoted as $\langle\cdot,\cdot\rangle$.
+Let $(\cdot,\cdot)_{L^2(D)}$,  $(\cdot,\cdot)_D$ or simply $(\cdot,\cdot)$ be the $L^2(D)$ inner product on $D$.
 We will use the standard notation $H^q(D)$ to denote the Sobolev space of functions on $D$ with all derivatives up to the order $q$ in $L^2(D)$.
@@
 Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. 
-We denote with $\mathcal{T}: H^q(D) \rightarrow H^{q-\frac12}(\Sigma)$ the trace operator from $D$ to $\Sigma$.
-For the purpose of this work we will extensively use traces on $\Gamma$ of functions defined on $\Omega$. Such operator will be denoted with $\trace$. 
-Fractional Sobolev spaces arising from the application of the trace operator are particularly important in this work.
-For example the trace space on $\Gamma$ of $H^1_0(\Omega)$ will be be extensively used for this study.
-We denote this space as $H^{\frac12}_{00}(\Gamma) = \trace H^1_0(\Omega)$.
-It can be interpreted as the subspace of $H^{\frac12}(\Gamma)$ of functions with continuous extension by zero outside $\Gamma$.
-We remark that $(H^{\frac12}_{00}(D))^* = H^{-\frac12}(D)$ with $D=\Gamma,\Lambda$.
+We denote with $\mathcal{T}_\Sigma}: H^q(D) \rightarrow H^{q-\frac12}(\Sigma)$ the trace operator from $\Omega$ to $\Sigma$.
+Functions in $H^{\frac12}(\Sigma)$ with continuous extension by zero outside $\Sigma$ is denoted 
+$H^{\frac12}_{00}(\Sigma)$ and we remark that 
+$H^{\frac12}_{00}(\Sigma) = \mathcal{T}_\Sigma H^1_0(D)$
+and  $H^{-\frac12}(\Sigma) = (H^{\frac12}_{00}(\Sigma))^*$
 
-Due to the  geometrical structure of the generalized cylinder, 
-for any sufficiently regular function $w$ we decompose integrals as follows
-and we define the corresponding averages $\avrc{w},\,\avrd{w}$,
+We will frequently used inner products and norms that are weighted, such if $X$ is a Hilbert space and $w$ is a positive number, then the
+weighted inner product is denoted 
+\[
+(u,v)_{X,w} = (w \, u,  v)_X
+\]
+with a corresponding norm $\|\cdot\|_{X,w}$. Finally, 
+$|\cdot|$ denote the Lebesgue measure of a set, i.e. $|D(0)|$ is the cross-sectional area of the bottom of the cylinder.
+We will in the following assume that the cross-sectional area $D(s)$ is constant, but remark that this assumption is only made to simplify the notation. 
+\kent{I wrote this comment for simplicity. Otherwise, we need to be a bit more careful with the definition of the inner product above}
+
+Central in our analysis are the transverse averages $\avrc{w},\,\avrd{w}$ defined as, 
+\begin{gather*}
+\avrc{w}(s) = |\partial\mathcal{D}(s)|^{-1} \int_{\partial\mathcal{D}(s)} w d\gamma \quad \mbox{and} \quad 
+\avrd{w}(s) = |\mathcal{D}(s)|^{-1} \int_{\mathcal{D}(s)} w d\sigma, 
+\end{gather*}
+where $d\omega, \ d\sigma, \ d\gamma$ are the generic volume, surface and curvilinear Lebesgue measures.
+Clearly, 
 \begin{gather*}
@@
 = \int_\Lambda \int_{\mathcal{D}(s)} w d\sigma ds
-= \int_\Lambda |\mathcal{D}(s)|\avrd{w}(s) ds\,,
-\ \textrm{where} \ \avrd{w}(s) = |\mathcal{D}(s)|^{-1} \int_{\mathcal{D}(s)} w d\sigma\,,
-\\
+= \int_\Lambda |\mathcal{D}(s)|\avrd{w}(s) ds\, \ \mbox{and} \ 
 \int_{\partial\Omega_{\ominus}} w d\sigma 
 = \int_\Lambda \int_{\partial\mathcal{D}(s)} w d\gamma ds
-= \int_\Lambda  |\partial \mathcal{D}(s)| \avrc{w}(s) ds\,,
-\ \textrm{where} \ \avrc{w}(s) = |\partial\mathcal{D}(s)|^{-1} \int_{\partial\mathcal{D}(s)} w d\gamma\,,
+= \int_\Lambda  |\partial \mathcal{D}(s)| \avrc{w}(s) ds\,. 
 \end{gather*}
-being $d\omega, \ d\sigma, \ d\gamma$ the generic volume, surface and curvilinear Lebesgue measures.
 Analogously, for functions defined on $\Lambda$ and $\Omega_\ominus$ respectively, 
@@
 
-The operator obtained form the combination of the average operator $\avrc{(\cdot)}$ with the trace on $\Gamma$ will be denoted with $\mtrace = \avrc{(\cdot)} \circ \trace$,
+The operator obtained from a combination of the average operator $\avrc{(\cdot)}$ with the trace on $\Gamma$ will be denoted with $\mtrace = \avrc{(\cdot)} \circ \trace$,
 as it maps functions on $\Omega$ to functions on $\Lambda$.
-We will see later that functions belonging to $H^{\frac12}_{00}(\Lambda)$ are generated from the application of $\mtrace$ to $H^1_0(\Omega)$.
-
-In what follows we will also use the uniform extension to $\Omega_{\ominus}$ of functions defined on $\Lambda$.
-Namely, given $\vd(s)$ we define $\mathcal{E}_{\Omega_{\ominus}}$ as $\mathcal{E}_{\Omega_{\ominus}}\vd(s,r,t)=\vd(s)$.
-Then, taking the trace on $\Gamma$ of the extended function we obtain an extension map from $\Lambda$ to $\Gamma$, denoted as $\ext$.
-We observe that $\ext: H^\frac12_0(\Lambda) \rightarrow H^\frac12_{00}(\Gamma)$ satisfies the following property
+Further, let the extension operator $\mathcal{E}_{\Gamma}: H^{\frac12}_{00}(\Lambda) \rightarrow H^{\frac12}_{00}(\Gamma)$ be defined such that
+ $(\mathcal{E}_{\Omega_{\ominus}}\vd)(x)=\vd(s), \quad \forall x\in \partial D(s)$.
+Then, 
 \begin{equation}\label{eq:ext}
@@
 \end{equation} 
-which shows that the average and the uniform extension operator commute.
+which shows that the average and the uniform extension operator commute with the trace.
 
-From the theory of interpolation of Sobolev spaces we define the fractional norms $\|\cdot \|_{H^{\frac 12}_{00}(\Gamma)}$ and $\|\cdot \|_{H^{\frac 12}_{00}(\Lambda)}$ as functions of the eigenvalues and eigenfunctions of the Laplacian on $\Gamma$ and $\Lambda$ respectively, see for example \cite{MR0350177,MR2328004}.
-We denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the Laplacian on $\Gamma$ with homogeneous Dirichlet condition at the boundary.
+%From the theory of interpolation of Sobolev spaces we define the fractional norms $\|\cdot \|_{H^{\frac 12}_{00}(\Gamma)}$ and $\|\cdot \|_{H^{\frac 12}_{00}(\Lambda)}$ as functions of the eigenvalues and eigenfunctions of the Laplacian on $\Gamma$ and $\Lambda$ respectively, see for example \cite{MR0350177,MR2328004}.
+%We denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the Laplacian on $\Gamma$ with homogeneous Dirichlet condition at the boundary.
 Then, the norms of $H^{\frac 12}_{00}(\Gamma),\,H^{\frac 12}_{00}(\Lambda)$ and the corresponding dual norms are defined as
-\begin{equation}\label{eq:fracnorm_gamma}
-\|u\|_{H^{\frac 12}_{00}(\Gamma)}=\left(\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2\right)^{\frac 12}
-\ \text{with} \ a_{ij}=\left( u,\phi _{ij} \right)_{\Gamma};
-\quad
-\| v \|_{H^{-\frac 12}(\Gamma)} = \sup_{u\in H^{\frac 12}_{00}(\Gamma)}\frac{\langle u, v \rangle_\Gamma}{\|u\|_{H^{\frac 12}_{00}(\Gamma)}}\,.
-\end{equation}
-Similarly, denoting with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the Laplacian on $\Lambda$ with homogenous Dirichlet boundary conditions, if $u \in H^{\frac 12}(\Lambda)$ we have
-\begin{equation}\label{eq:fracnorm_lambda}
-\|u\|_{H^{\frac 12}_{00}(\Lambda)}=\left(\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|a_i|^2\right)^{\frac 12}
-\ \text{with} \ a_i=\left(u, \phi _i \right)_{\Lambda};
-\quad
-\| v \|_{H^{-\frac 12}(\Lambda)} = \sup_{u\in H^{\frac 12}_{00}(\Lambda)}\frac{\langle u, v \rangle_\Lambda}{\|u\|_{H^{\frac 12}_{00}(\Lambda)}}\,.
-\end{equation}
-We define the equivalent weighted norm in $H^{\frac 12}_{00}(\Lambda)$ in the same way,
-\begin{equation}\label{eq:weightfracnorm}
-\|u\|_{H^{\frac 12}_{00}(\Lambda), |\DD|}=\left(\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|a_i|^2\right)^{\frac 12},
-\ \text{with} a_i=\left(u, \phi _i \right)_{\Lambda, |\DD|};
-\quad
-\| v \|_{H^{-\frac 12}(\Lambda)} = \sup_{u\in H^{\frac 12}_{00}(\Lambda)}\frac{\langle u, v \rangle_{\Lambda, |\DD|}}{\|u\|_{H^{\frac 12}_{00}(\Lambda), |\DD|}}\,.
-\end{equation}
+%\begin{equation}\label{eq:fracnorm_gamma}
+%\|u\|_{H^{\frac 12}_{00}(\Gamma)}=\left(\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2\right)^{\frac 12}
+%\ \text{with} \ a_{ij}=\left( u,\phi _{ij} \right)_{\Gamma};
+%\quad
+%\| v \|_{H^{-\frac 12}(\Gamma)} = \sup_{u\in H^{\frac 12}_{00}(\Gamma)}\frac{\langle u, v \rangle_\Gamma}{\|u\|_{H^{\frac 12}_{00}(\Gamma)}}\,.
+%\end{equation}
 
-We conclude this section with the analysis of a fundamental property for the problem formulation that we will address.
-It consists in the characterization of the regularity of the operator $\mtrace$.
-More precisely we aim to show that $\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$.
-This is a consequence of the following lemma.
+%We define the equivalent weighted norm in $H^{\frac 12}_{00}(\Lambda)$ in the same way,
+%\begin{equation}\label{eq:weightfracnorm}
+%\|u\|_{H^{\frac 12}_{00}(\Lambda), |\DD|}=\left(\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|a_i|^2\right)^{\frac 12},
+%\ \text{with} a_i=\left(u, \phi _i \right)_{\Lambda, |\DD|};
+%\quad
+%\| v \|_{H^{-\frac 12}(\Lambda)} = \sup_{u\in H^{\frac 12}_{00}(\Lambda)}\frac{\langle u, v \rangle_{\Lambda, |\DD|}}{\|u\|_{H^{\frac 12}_{00}(\Lambda), |\DD|}}\,.
+%\end{equation}
 
-\input{preliminary_results.tex}
+With the above notation we are now able to formulate the precise weak formulations of the problems 
+\eqref{eq:pde} and \eqref{inteq:pde}. 
+The weak formulation of \eqref{eq:pde}, which we will call the \textbf{Problem 3D-1D-1D} reads: 
+Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
+\begin{subequations}\label{eq:problem2}
+\begin{align}
+&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
++  \langle \mtrace v - \vd, \ld \rangle_{\Lambda, |\DD|} &&
+\\
+\nonumber
+&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
+\quad && \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)\,,
+\\
+& \langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} = 0
+\quad &&\forall \md \in H^{-\frac12}(\Lambda)\,,
+\end{align}
+\end{subequations}
+Furthermore, the weak formulation of \eqref{inteq:pde}, refered to as \textbf{Problem 3D-1D-2D}, reads: 
+Find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac12}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
+\begin{subequations}\label{eq:problem1}
+\begin{align}
+&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
++ \langle \trace v  - \ext \vd, \lambda \rangle_\Gamma &&
+\\
+\nonumber
+&\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
+\quad &&\forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)\,,
+\\
+& \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0
+\quad && \forall \mu \in H^{-\frac12}(\Gamma)\,.
+\end{align}
+\end{subequations}
 
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\section{Derivation of the model} \\
+Below we detail the steps performed in order to formulate \ref{eq:problem1} and \ref{eq:problem2} precisely. 
+The derivations are similar~\cite{laurino_m2an},  but here we derive the system including the Lagrange multiplier.
 
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 \subsection{Topological model reduction}
 
-\subsection{Problem formulation}
 We consider the problem arising from \emph{Dirichlet-Neumann} conditions. Find $\up,\uf$ s.t.:
@@
 
-We observe that the coupling constraints defined on $\Gamma$ involve \emph{essential}-type conditions.
-To address such conditions at the level of the variational formulation, we adopt the method of Lagrange multipliers,
-which has been widely used for this purpose since the origin of the finite element method, \cite{MR359352}.
-We remark that this case is substantially different from the one previously addressed in \cite{laurino_m2an}.
+We observe that the coupling constraints defined on $\Gamma$ involve essential or strong conditions.
+The strong conditions will, however, be enforced weakly by using the method of Lagrange multipliers~\cite{MR359352}.
+%We remark that this case is substantially different from the one previously addressed in \cite{laurino_m2an}.
 
@@
 We end up with two different formulations of a reduced problem for the unknown $u$ defined on the entire 3D domain $\Omega$, 
-coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$ and a Lagrange multiplier defined either on $\Gamma$ (problem 1) or on $\Lambda$ (problem 2). 
+coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$ and a Lagrange multiplier defined either on $\Gamma$ (Problem 3D-1D-2D) or on $\Lambda$ (Problem 3D-1D-1D). 
 The scope of this work is to analyze and compare the two alternatives,
@@
 
-\subsubsection*{Problem 1 (3D-2D-1D)}
+Hence, we have obtained the Problem 3D-1D-2D, equation 
+\eqref{eq:problem1}: \\
 Find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac12}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
-\begin{subequations}\label{eq:problem1}
-\begin{align}
+\begin{subequations}
+\begin{align*}
 &(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
@@
 \quad && \forall \mu \in H^{-\frac12}(\Gamma)\,.
-\end{align}
+\end{align*}
 \end{subequations}
-This coupled problem is classifies as 3D-2D-1D because the unknowns $u,\lambda,\ud$ belong to 
+This coupled problem is classifies as 3D-1D-2D because the unknowns $u,\lambda,\ud$ belong to 
 $\Omega \subset \R^3,\, \Gamma \subset \R^2,\, \Lambda \subset \R$, respectively.
-Then, we apply a topological model reduction of the interface conditions, namely we go from a 3D-2D-1D formulation
+Then, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-2D formulation
 involving sub-problems on $\Omega$ and $\Lambda$ and coupling operators defined on $\Gamma$
@@
 
-\subsubsection*{Problem 2 (3D-1D-1D)}
+Hence, we have derived the Problem 3D-1D-1D, equation \eqref{eq:problem2}: \\ 
 Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
-\begin{subequations}\label{eq:problem2}
-\begin{align}
+\begin{subequations}
+\begin{align*}
 &(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
@@
 \quad &&\forall \md \in H^{-\frac12}(\Lambda)\,,
-\end{align}
+\end{align*}
 \end{subequations}
@@
 can be studied in the framework of the classical theory of saddle point problems as shown in the following.
+
+We conclude this section with the analysis of a fundamental property for the problem formulation that we will address.
+It consists in the characterization of the regularity of the operator $\mtrace$.
+More precisely we aim to show that $\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$.
+This is a consequence of the following lemma.
+
+\input{preliminary_results.tex}
 

### 2020-03-02 infsup_discrete_conformingLM.tex
Updates from Overleaf

@@
 \section{Finite element approximation}
-In this section we consider the discretization of Problem 1 and 2 by means of the finite element method.
+In this section we consider the discretization of the Problems 3D-1D-2D and 3D-1D-1D by means of the finite element method.
 We address two main challenges; first we aim to identify a suitable approximation space for the Lagrange multiplier and to analyze the stability of the discrete saddle point problem; second we aim to derive a stable discretization method that uses independent computational meshes for $\Omega$, $\Gamma$ and $\Lambda$.
@@
 \end{eqnarray}
-Let $B_h: Q'_h \longrightarrow Q_h$ be the operator induced by $b$ such that $\langle B_h v_h,\mu _h\rangle_{Q'_h,Q_h} = b(v_h,\mu _h)$.
-The well posedness of such problem is governed by the classical result reported below.
-
-\begin{corollary}{\cite[Theorem 2.42]{MR2050138}}Let $a(\cdot, \cdot)$ and $b(\cdot, \cdot)$ be continuous bilinear forms. 
-Problem \eqref{eq:saddle-point_discrete} is well-posed if and only if 
+This discrete problem is well-posed if the \eqref{BNB1}-\eqref{BNB4} conditions applies to $X_h$ and $Q_h$. Since $X_h\subset X$ and $Q_h\subset Q$,  
+\eqref{BNB1}-\eqref{BNB3} follows immediately and only the inf-sup condition needs consideration.  We summarize this in the Corollary below. 
+\begin{corollary}{\cite[Theorem 2.42]{MR2050138}}\\
+Let
+$X_h \subset X$, $Q_h \subset Q$, $a(\cdot, \cdot)$ and $b(\cdot, \cdot)$ satisfy the conditions  \eqref{BNB1}-\eqref{BNB3} then  
+the problem \eqref{eq:saddle-point_discrete} is well-posed if 
+the discrete counterpart of \eqref{BNB4} is satisfied, ie., 
+there exists a $\beta_h>0$ such that
 \begin{align}\label{BNB1_discrete}
-& \exists \alpha_h >0 : && \inf_{u_h\in ker(B_h)}\sup_{v_h\in ker(B_h)} \frac{a(u_h,v_h)}{\|u_h\|_{X}\|v_h\|_{X}}\geq \alpha_h\,,
-\\
 \label{eq:infsup_discrete}
- &\exists \beta_h >0: &&\inf_{\mu_h\in Q_h}\sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}\|\mu_h\|_{Q}}\geq \beta_h\, .
+ \sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}}\geq \beta_h |\mu_h\|_{Q}\, .
 \end{align}
 \end{corollary}
-This corollary is the discrete counterpart of Theorem \ref{th:bnb} where at the discrete level condition \eqref{BNB1_discrete} implies both of \eqref{BNB1}.
-We remark that \eqref{eq:infsup_discrete} does not follow from the conformity of the finte element spaces and it must be analysed independetly of \eqref{eq:infsup}.
-Let us notice that for both problem 1 and problem 2 the bilinear form $a(\cdot, \cdot)$ is coercive as stated in Lemmas \eqref{lemma:prob1_coercivity} and \eqref{lemma:prob2_coercivity}.
-Consequently, \eqref{BNB1_discrete} is automatically satisfied, being $\alpha_h$ the coercivity constant.\\
 
@@
  We first analyze the case in which the 3D mesh is conforming to the interface $\Gamma$.
-As conformity conditions between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$ with $\Gamma$ , we require that the intersection of $\mathcal{T}^{\Omega}_h$ and $\Gamma$ is made of entire faces of elemets $K \in \mathcal{T}^{\Omega}_h$.
+As conformity conditions between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$ with $\Gamma$ , we require that the intersection of $\mathcal{T}^{\Omega}_h$ and $\Gamma$ is made of entire faces of elements $K \in \mathcal{T}^{\Omega}_h$.
 Furthermore, we also set a restriction between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$.
@@
 
-\subsubsection{Problem 1}
+\subsubsection{Problem 3D-1D-2D}
 We denote by $X_{h,0}^k(\Omega)\subset H^1_0(\Omega)$, with $k>0$, the conforming finite element space of continuous piecewise polynomials of degree $k$ defined on $\Omega$ satisfying homogeneous Dirichlet conditions on the boundary and by $X_{h,0}^k(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$, satisfying homogeneous Dirichlet conditions on $\Lambda \cap \partial \Omega$.
@@
 
-\subsubsection{Problem 2}
+\subsubsection{Problem 3D-1D-1D}
 We aim to find  $u_h \in X_{h,0}^k(\Omega) ,\ {\ud}_h \in X_{h,0}^k(\Lambda), \ {\ld}_h \in Q_h \subset H^{-\frac12}(\Lambda)$, such that

### 2020-03-02 unfitted_prob2.tex
Updates from Overleaf

@@
 We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_h$ do not conform with the surface $\Gamma$ nor with $\Lambda$. In this case, the 3D-1D-1D
-formulation, namely Problem 2, is more suitable. 
+formulation, namely Problem 3D-1D-1D, is more suitable. 
 %{\color{red} Add more details, we can refer also to cutFEM (Burman, Massing etc.) explaining the limitation of that approach (network case for example).}\\
@@
 
-\subsubsection{Problem 2} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X_h = X_{h,0}^1(\Omega) \times X_{h^\prime,0}^1(\Lambda)$.
+\subsubsection{Problem 3D-1D-1D} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X_h = X_{h,0}^1(\Omega) \times X_{h^\prime,0}^1(\Lambda)$.
 With little abuse of notation, we assume that the characteristic mesh size of the 3D mesh $\mathcal{T}^{\Omega}_h$ and the one of the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different.
@@
 \end{lemma}
-For the proof of this result we remand the reader to Lemma 2.3 of \cite{burman2014}.
-In the reminder of this section we show how to find a multiplier space $Q_H$ and a stabilization operator $s_h$ such that all the assumptions of lemma \ref{lemma23burman} are satisfied.
+For the proof of this result we remind the reader to Lemma 2.3 of \cite{burman2014}.
+In the remainder of this section we show how to find a multiplier space $Q_H$ and a stabilization operator $s_h$ such that all the assumptions of lemma \ref{lemma23burman} are satisfied.
 

### 2020-03-02 3d1d_coupled_LM.tex
fix complilation issues

@@
 \label{inteq:pde2}
--d_s² \ud + \ud - E' \lambda  &= g &\mbox{ on } \Lambda,\\
+-d_s^2 \ud + \ud - E' \lambda  &= g &\mbox{ on } \Lambda,\\
 \label{inteq:coupling}
@@
 Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. 
-We denote with $\mathcal{T}_\Sigma}: H^q(D) \rightarrow H^{q-\frac12}(\Sigma)$ the trace operator from $\Omega$ to $\Sigma$.
-Functions in $H^{\frac12}(\Sigma)$ with continuous extension by zero outside $\Sigma$ is denoted 
-$H^{\frac12}_{00}(\Sigma)$ and we remark that 
-$H^{\frac12}_{00}(\Sigma) = \mathcal{T}_\Sigma H^1_0(D)$
-and  $H^{-\frac12}(\Sigma) = (H^{\frac12}_{00}(\Sigma))^*$
+We denote with $\mathcal{T}_\Sigma: H^q(D) \rightarrow H^{q-\frac 1 2}(\Sigma)$ the trace operator from $\Omega$ to $\Sigma$.
+Functions in $H^{\frac 1 2}(\Sigma)$ with continuous extension by zero outside $\Sigma$ is denoted 
+$H^{\frac 1 2}_{00}(\Sigma)$ and we remark that 
+$H^{\frac 1 2}_{00}(\Sigma) = \mathcal{T}_\Sigma H^1_0(D)$
+and  $H^{-\frac 1 2}(\Sigma) = (H^{\frac 1 2}_{00}(\Sigma))^*$
 
@@
 as it maps functions on $\Omega$ to functions on $\Lambda$.
-Further, let the extension operator $\mathcal{E}_{\Gamma}: H^{\frac12}_{00}(\Lambda) \rightarrow H^{\frac12}_{00}(\Gamma)$ be defined such that
+Further, let the extension operator $\mathcal{E}_{\Gamma}: H^{\frac 1 2}_{00}(\Lambda) \rightarrow H^{\frac 1 2}_{00}(\Gamma)$ be defined such that
  $(\mathcal{E}_{\Omega_{\ominus}}\vd)(x)=\vd(s), \quad \forall x\in \partial D(s)$.
@@
 The weak formulation of \eqref{eq:pde}, which we will call the \textbf{Problem 3D-1D-1D} reads: 
-Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
+Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac 1 2}(\Lambda)$, such that
 \begin{subequations}\label{eq:problem2}
@@
 & \langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} = 0
-\quad &&\forall \md \in H^{-\frac12}(\Lambda)\,,
+\quad &&\forall \md \in H^{-\frac 1 2}(\Lambda)\,,
 \end{align}
@@
 Furthermore, the weak formulation of \eqref{inteq:pde}, refered to as \textbf{Problem 3D-1D-2D}, reads: 
-Find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac12}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
+Find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac 1 2}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
 \begin{subequations}\label{eq:problem1}
@@
 & \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0
-\quad && \forall \mu \in H^{-\frac12}(\Gamma)\,.
+\quad && \forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
 \end{align}
@@
 
-\section{Derivation of the model} \\
+\section{Derivation of the model}
 Below we detail the steps performed in order to formulate \ref{eq:problem1} and \ref{eq:problem2} precisely. 
@@
 The variational formulation of problem \eqref{eq:dirneu}
-is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus), \ \lambda \in H^{-\frac12}(\partial\Omega_\ominus)$ s.t.
+is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus), \ \lambda \in H^{-\frac 1 2}(\partial\Omega_\ominus)$ s.t.
 \begin{subequations}\label{eq:weak_dirneu}
@@
 & \langle u_\oplus - u_\ominus, \mu \rangle_{\Gamma} = 0
-\quad \forall  \mu \in H^{-\frac12}(\Gamma)\,,
+\quad \forall  \mu \in H^{-\frac 1 2}(\Gamma)\,,
 \end{align}
 \end{subequations}
-%where $\langle v, \mu \rangle_{H^{-\frac12}(\Gamma)}$ denotes the duality pairing between 
-%$ \mu \in H^{-\frac12}(\Gamma)$ and $v \in H^{\frac12}(\Gamma)$.
+%where $\langle v, \mu \rangle_{H^{-\frac 1 2}(\Gamma)}$ denotes the duality pairing between 
+%$ \mu \in H^{-\frac 1 2}(\Gamma)$ and $v \in H^{\frac 1 2}(\Gamma)$.
 In this case, $\lambda$ is the Lagrange multiplier and it is equivalent to $\nabla \uf \cdot \nn_\ominus$.
@@
 \eqref{eq:problem1}: \\
-Find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac12}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
+Find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac 1 2}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
 \begin{subequations}
@@
 & \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0
-\quad && \forall \mu \in H^{-\frac12}(\Gamma)\,.
+\quad && \forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
 \end{align*}
@@
 Hence, we have derived the Problem 3D-1D-1D, equation \eqref{eq:problem2}: \\ 
-Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
+Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac 1 2}(\Lambda)$, such that
 \begin{subequations}
@@
 & \langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} = 0
-\quad &&\forall \md \in H^{-\frac12}(\Lambda)\,,
+\quad &&\forall \md \in H^{-\frac 1 2}(\Lambda)\,,
 \end{align*}
@@
 We notice that all the integrals of the reduced problem are well defined because 
-$\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$ as shown in Corollary \ref{corollary:H12norm}.
+$\mtrace: H^1_0(\Omega) \rightarrow H^\frac 1 2_{00}(\Lambda)$ as shown in Corollary \ref{corollary:H12norm}.
 
@@
 It consists in the characterization of the regularity of the operator $\mtrace$.
-More precisely we aim to show that $\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$.
+More precisely we aim to show that $\mtrace: H^1_0(\Omega) \rightarrow H^\frac 1 2_{00}(\Lambda)$.
 This is a consequence of the following lemma.

### 2020-03-14 3d1d_coupled_LM.tex
Updates from Overleaf

@@
 \usepackage{float}
-\usepackage{fullpage}
+%\usepackage{fullpage}
 \usepackage{color}
@@
 \usepackage{stmaryrd}
+\usepackage{standalone}
 \usepackage{tikz, subfigure}
+
+\usetikzlibrary{shapes, snakes, patterns, arrows}
+\usetikzlibrary{calc}
+\usepackage{pgfplots}
+\usepgfplotslibrary{fillbetween}
+
 \usepackage{booktabs}  % for tables
@@
 
-In this paper we will consider a 3D-1D coupled problem described by the following equations:\\
+In this study we consider coupled partial differential equations on domains with mixed dimensionality, in particular we address the  3D-1D case.
+The mathematical structure of such problems can be represented by the following formal equations:
 \begin{subequations}
@@
 \end{subequations}
-%
+Problem \eqref{eq:pde} can be described as an example of \emph{mixed dimensional PDEs}.
 Here, $u$, $\ud$,  $\lambda$ are unknowns,  $\Omega$ is a bounded domain in $\R^3$, whereas $\Lambda \subset \Omega$ is a 1D structure
@@
 $\int_{\Omega}\lambda(x)\delta_{\Lambda}v(x)\,\mathrm{d}x=\int_{\Lambda}\lambda(t)v(t) \,\mathrm{d}t$
-for a continuous function $v$ and $\mathcal{T}_\Lambda: \Omega\rightarrow\Lambda$ is a trace operator.
+for a continuous function $v$ and $\mathcal{T}_\Lambda: \Omega\rightarrow\Lambda$ is a suitable restriction operator from 3D to 1D.
 
-From a mathematical point of view, the challenge involved in problem \eqref{eq:pde} is that neither $\mathcal{T}_\Lambda$ nor $\delta_\Lambda$ are well defined. 
-That is, without extra regularity,  solutions of elliptic PDEs only have well defined traces of co-dimension one.
-Here, $\mathcal{T}_\Lambda$ is of co-dimension two, mapping functions defined on a domain in 3D to
-functions defined along a 1D curve.
-Similarly, Dirac delta functions are well defined on measures of co-dimension one, but not two.
-Several studies \cite{DAngelo,d2012finite,d2008coupling} have remedied the well-posedness by weakening the solution concept.
-The approach naturally leads to non-symmetric formulations.
-An alternative approach is to decompose the solution into smooth and non-smooth components, where the non-smooth component may be represented in terms of Greens functions, and then consider the well-posedness of the smooth component~\cite{Peaceman1983531,secomb2004green}.
-Both of these approaches have successfully be analyzed in a discrete setting and implemented~\cite{}.
-Error estimates etc...
-Many more references can be mentioned.
-In this work we analyze an alternative approach, closely related to \cite{laurino_m2an}, where we exploit the fact that the $\Lambda$ is not strictly a 1D curve, but rather a very thin 3D structure with
-a cross-sectional area far below what we can resolve. With this additional assumption, we show that robustness with respect to the cross-sectional area can be restored.
-
-The mathematical problem is motivated by the fact that many problems in geo- and biophysics are characterized by slender cylindrical structures coupled to a larger 3D body, where the characteristic transverse length scale of the slender structure is many orders of magnitude smaller than the longitudinal length.
-For example, in geophysical applications the radius of wells are often of the order of 10 cm while the length may be several kilometers~\cite{gjerde2019singularity}.
-Similarly, in applications involving the blood flow and oxygen transport of the micro-circulation the capillary radius is a few microns, while simulations are often performed on mm to cm scale, with thousands of vessels~\cite{berg2020modelling,fang2008oxygen,gould2017capillary}.
+Using models based on mixed dimensional PDEs is motivated by the fact that many problems in geo- and biophysics are characterized by slender cylindrical structures coupled to a larger 3D body, where the characteristic transverse length scale of the slender structure is many orders of magnitude smaller than the longitudinal length.
+For example, in geophysical applications the radius of wells are often of the order of 10 cm while the length may be several kilometers~\cite{Peaceman1978183, Peaceman1983531}.
+Similarly, in applications involving the blood flow and oxygen transport of the micro-circulation the capillary radius is a few microns, while simulations are often performed on mm to cm scale, with thousands of vessels~\cite{berg2020modelling,fang2008oxygen,gould2017capillary, secomb2004green}.
 Finally, in neuro-science applications a neuron has width of a few microns, while  its length is much longer.
@@
 Even if adaptive and strongly anisotropic meshes are allowed for, the computations quickly become demanding if many slender structures and their interactions are under study.
-If the quantity of interest is the far field impact (relative to the transverse lengthscale) caused by processes in the slender structures, the high resolution involved in the near field of the slender structure may not be needed.
 
-An intermediate problem, where the coupling between the 3D and 1D problems of \eqref{eq:pde} is a 2D surface, reads 
-\begin{subequations}
-\label{inteq:pde}
-\begin{align}
-\label{inteq:pde1}
-  -\Delta u + u + \lambda \delta_{\Lambda} &= f &\mbox{ in } \Omega,\\
-\label{inteq:pde2}
--d_s^2 \ud + \ud - E' \lambda  &= g &\mbox{ on } \Lambda,\\
-\label{inteq:coupling}
-T_\Gamma u - E_\Gamma v  &=  h &\mbox{ on } \Gamma
-\end{align}
-\end{subequations}
-where $\Gamma \subset \Omega$ is a 2D surface corresponding to $\Lambda$
-and $E$ is an extension operator from $\Lambda$ to $\Gamma$.
+From a mathematical standpoint, the challenge involved in problem \eqref{eq:pde} is that neither $\mathcal{T}_\Lambda$ nor $\delta_\Lambda$ are well defined.
+That is, without extra regularity,  solutions of elliptic PDEs only have well defined traces of co-dimension one.
+Here, $\mathcal{T}_\Lambda$ is of co-dimension two, mapping functions defined on a domain in 3D to functions defined along a 1D curve.
+The challenge of coupling PDEs on domains with high dimensionality gap has recently attracted the attention of many researchers.
+The sequence of works by D'Angelo, \cite{DAngelo,d2012finite,d2008coupling} have remedied the well-posedness by weakening the solution concept.
+The approach naturally leads to non-symmetric formulations.
+An alternative approach is to decompose the solution into smooth and non-smooth components, where the non-smooth component may be represented in terms of Green functions, and then consider the well-posedness of the smooth component \cite{gjerde2019singularity}.
+The numerical approximation of such equations has been also studied in a series of works.
+The consistent derivation of numerical approximations schemes for PDEs in mixed dimension is addressed in \cite{Nordbotten}.
+Concerning approximability,  elliptic equations with Dirac sources represent an effective prototype case that has been addressed in \cite{Bertoluzza201897,koppl2016local,koppl2014optimal}, where the optimal a-priori error estimates for the finite element approximation are derived.
+Furthermore, the interplay between the mathematical structure of the problem and solvers, as well as preconditioners for its discretization has been studied in details  in \cite{Kuchta2016B962} for the solution of 1D differential equations embedded in 2D, and more recently extended to the 3D-1D case in \cite{KMM2}.
 
-\kent{
-Detail the approach and result a bit.
-Mention that some stuff is 
-similar to~\cite{laurino_m2an}, but for completeness and the readers convenience we repeat some basic derivations. 
-}
+Stemming from this literature, in this work we adopt and analyze a different approach, closely related to \cite{KVWZ,laurino_m2an}.
+That is, we exploit the fact that the $\Lambda$ is not strictly a 1D curve, but rather a very thin 3D structure with a cross-sectional area far below what can be resolved.
+With this additional assumption, we show that robustness with respect to the cross-sectional area can be restored.
+The major novelty with respect to the previous works is that we address essential type coupling conditions, namely Dirichlet-Neumann conditions, rather than natural type ones, such as the Neumann-Robin or Robin-Robin cases.
+These coupling conditions pose additional difficulties as the conditions
+are not a natural part of the weak formulation of the problem.
+We overcome this difficulty by  resorting to a weak formulation of the Dirichlet-Neumann coupling conditions across dimensions by using Lagrange multipliers.
 
-%We address the geometrical configuration of the problem for a 3D coupled problem formulation based on from Dirichlet-Neumann interface conditions.
-Then, we apply a model reduction technique that transforms the problem into 3D-1D coupled PDEs.
-We develop and analyze a robust definition of the coupling operators form a 3D domain, $\Omega$, to 1D manifold, $\Lambda$, and vice versa.
-This is a non trivial objective because the standard trace operator form a domain $\Omega$ to a subset $\Lambda$ is not well posed if $\Lambda$ is a manifold of co-dimension two of $\Omega$.
-
-%This work is based on the assumption that \emph{the transversal diameter of $\Omega_{\ominus}$ is small compared to the diameter of $\Omega$}. 
-%Let $d= \max_{s \in (0,S)} \mathrm{diam}(\D(s))$ be the largest diameter of the cross sections of $\Omega_{\ominus}$, that is the transversal diameter of $\Omega_{\ominus}$.
-%The central assumption of this work is that $d \ll \mathrm{diam}(\Omega)$.
-%Let us now scale the domains $\Omega$ and $\Omega_{\ominus}$.
-%Let $\chi_{\Omega}(\xx) = \xx / \mathrm{diam}(\Omega)$ be a scaling function and let be $\Omega_\chi = \chi_{\Omega}(\Omega), \ {\Omega_{\ominus}}_\chi =  \chi_{\Omega}(\Omega_{\ominus})$ be the scaled domains.
-%The previous assumption implies that for the scaled domains $\epsilon = d_\chi = d/\mathrm{diam}(\Omega)$
-%is such that $0 < \epsilon \ll 1$. For simplicity of notation, and without loss of generality, form now on we will implicitly refer to the scaled domains dropping the subindex $\chi$.
-%\kent{this is a good explanatory paragraph, but not sure we use the notation introduced}
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 \section{Preliminaries}\label{sec:setting}
-
-%In this preliminary section we fist provide the main notation and definitions to set up the problem.
-%In particular, we address the geometry of the domain, which is equivalent to the one addressed in previous works of the authors \cite{laurino_m2an},
-%and we define the functional spaces and related operators necessary for a rigorous problem formulation and analysis.
-%Finally, the section ends with the formal derivation of the problem, 
-%based on averaging techniques applied to a fully three-dimensional model in the geometrical setting defined before.
 
@@
 while the upper and lower faces of $\Omega_{\ominus}$ belong to $\partial\Omega$. 
-We will assume that $\Omega_{\ominus}$ crosses $\Omega$ from si
-de to side.
+We assume that $\Omega_{\ominus}$ crosses $\Omega$ from side to side.
 According to the geometrical setting, we will denote with $v,\,v_\oplus,\,v_\ominus,\,\vd$,
@@
 \begin{center}
-\includegraphics[width=0.3\textwidth]{domain.pdf}
+\includegraphics[width=0.25\textwidth,angle=-90]{./graphics/domain.tex}
 \end{center}
@@
 \end{figure}
+\kent{I think the symbols in the Figure should be bigger}
 
-%Let $\TT,\NN,\BB$ be the Frenet frame related to the curve.
-%Let $\mathcal{D}(s) = [x(r,t),y(r,t)]: (0,R(s))\times(0,T(s)) \rightarrow \R^2$ be a parametrization of the cross section.
-%Let us assume that $\mathcal{D}(s)$ is convex for any $s \in (0,S)$. The cross section can change size along $\Lambda$ but not shape.
-%Let us also parametrize the boundary of the cross section as $\partial\mathcal{D}(s) = [\partial %x(r,t),\partial y(r,t)]: (0,R(s))\times(0,T(s)) %\rightarrow \R^2$,
-%and let us assume that $\partial\mathcal{D}(s)$ is a %piecewise $\mathcal{C}^2$-regular curve.
-%Then, the generalized cylinder $\Omega_{\ominus}$ %can be defined as follows
-%\begin{equation*}
-%\Omega_{\ominus} = \{ \boldsymbol \lambda(s) + %x(r,t) \NN(s) + y(r,t) \BB(s), \ r \in (0,R(s)),\ s %\in (0,S), \ t \in (0,T(s))\}\,,
-%\end{equation*}
-%and the lateral boundary is
-%\begin{equation*}
-%\Gamma = \{ \boldsymbol \lambda(s) + \partial x(r,t) %\NN(s) + \partial y(r,t) \BB(s), \ r \in (0,R(s)),\ %s \in (0,S), \ t \in (0,T(s))\}\,.
-%\end{equation*}
-%Let $|\cdot|$ denote the Lebesgue measure of a set. %If $|\mathcal{D}(0)|, \ |\mathcal{D}(S)| >0$ then %$\Omega_{\ominus}$ has \emph{top} and \emph{bottom} %boundaries,
-%which belong to $\partial\Omega$.
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-%\subsection{Functional setting and preliminary results}
-
-Let $D$ be a generic regular bounded domain in $\R^3$
-and $X$ be a Hilbert space defined on $D$ then  $(\cdot,\cdot)_X$ and $\|\cdot\|_X$ denote the inner product and norm of $X$, respectively.
+Let $D$ be a generic regular bounded domain in $\R^3$ and $X$ be a Hilbert space defined on $D$ then  $(\cdot,\cdot)_X$ and $\|\cdot\|_X$ denote the inner product and norm of $X$, respectively.
 The duality pairing between the $X$ and its dual $X^*$ is denoted as $\langle\cdot,\cdot\rangle$.
 Let $(\cdot,\cdot)_{L^2(D)}$,  $(\cdot,\cdot)_D$ or simply $(\cdot,\cdot)$ be the $L^2(D)$ inner product on $D$.
-We will use the standard notation $H^q(D)$ to denote the Sobolev space of functions on $D$ with all derivatives up to the order $q$ in $L^2(D)$.
+We use the standard notation $H^q(D)$ to denote the Sobolev space of functions on $D$ with all derivatives up to the order $q$ in $L^2(D)$.
 The corresponding norm is $\|\cdot\|_{H^q(D)}$ and the seminorm is $\vert\cdot\vert_{H^q(D)}$.
@@
 
-We will frequently used inner products and norms that are weighted, such if $X$ is a Hilbert space and $w$ is a positive number, then the
+We will frequently use inner products and norms that are weighted, such that if $X$ is a Hilbert space and $w$ is a positive integrable function, then the
 weighted inner product is denoted 
@@
 \]
-with a corresponding norm $\|\cdot\|_{X,w}$. Finally, 
-$|\cdot|$ denote the Lebesgue measure of a set, i.e. $|D(0)|$ is the cross-sectional area of the bottom of the cylinder.
-We will in the following assume that the cross-sectional area $D(s)$ is constant, but remark that this assumption is only made to simplify the notation. 
-\kent{I wrote this comment for simplicity. Otherwise, we need to be a bit more careful with the definition of the inner product above}
-
+\kent{
+I think we need to be careful when we write this. A reader may believe
+that 
+\[
+(u,v)_{1,w} = (\nabla (w \, u),  \nabla v)_1
+\]
+I will fix this, but I'd like a chat first.
+}
+with a corresponding norm $\|\cdot\|_{X,w}$.
+Finally, $|\cdot|$ denote the Lebesgue measure of a set, i.e.
+$|D(0)|$ is the cross-sectional area of the bottom of the cylinder.
+In the following we assume that the cross-sectional area $\mathcal{D}(s)$ is constant, namely $\mathcal{D}(s)=\mathcal{D}$, but remark that this assumption is only made to simplify the notation.
 Central in our analysis are the transverse averages $\avrc{w},\,\avrd{w}$ defined as,
@@
 = \int_\Lambda \int_{\mathcal{D}(s)} w d\sigma ds
-= \int_\Lambda |\mathcal{D}(s)|\avrd{w}(s) ds\, \ \mbox{and} \ 
+= \int_\Lambda |\mathcal{D}(s)|\avrd{w}(s) ds\, 
+\\
 \int_{\partial\Omega_{\ominus}} w d\sigma 
@@
 Analogously, for functions defined on $\Lambda$ and $\Omega_\ominus$ respectively, 
-we define as $d_s$ and $\partial_s$ the ordinary and partial derivative with respect to the arclength.
+we let  $d_s$ and $\partial_s$ be the ordinary and partial derivative with respect to the arclength.
 
-The operator obtained from a combination of the average operator $\avrc{(\cdot)}$ with the trace on $\Gamma$ will be denoted with $\mtrace = \avrc{(\cdot)} \circ \trace$,
-as it maps functions on $\Omega$ to functions on $\Lambda$.
-Further, let the extension operator $\mathcal{E}_{\Gamma}: H^{\frac 1 2}_{00}(\Lambda) \rightarrow H^{\frac 1 2}_{00}(\Gamma)$ be defined such that
- $(\mathcal{E}_{\Omega_{\ominus}}\vd)(x)=\vd(s), \quad \forall x\in \partial D(s)$.
-Then, 
+The operator obtained from a combination of the average operator $\avrc{(\cdot)}$ with the trace on $\Gamma$ will be denoted with $\mtrace = \avrc{(\cdot)} \circ \trace$, as it maps functions on $\Omega$ to functions on $\Lambda$.
+Further, let the extension operator $\mathcal{E}_{\Gamma}: H^{\frac 1 2}_{00}(\Lambda) \rightarrow H^{\frac 1 2}_{00}(\Gamma)$ be defined such that $(\mathcal{E}_{\Omega_{\ominus}}\vd)(x)=\vd(s)$, for any $x\in \DD(s)$.
+Then, the following identity shows that the transversal uniform extension operator is the inverse of the transversal average.
+
 \begin{equation}\label{eq:ext}
@@
 \end{equation}
-which shows that the average and the uniform extension operator commute with the trace.
 
@@
 
-With the above notation we are now able to formulate the precise weak formulations of the problems 
-\eqref{eq:pde} and \eqref{inteq:pde}. 
-The weak formulation of \eqref{eq:pde}, which we will call the \textbf{Problem 3D-1D-1D} reads: 
-Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac 1 2}(\Lambda)$, such that
+With the above notation we are now able to formulate the precise weak formulations of the problems \eqref{eq:pde} and \eqref{inteq:pde}.
+The weak formulation of \eqref{eq:pde}, which we will call the \textbf{Problem 3D-1D-1D} reads:  Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac 1 2}(\Lambda)$, such that
 \begin{subequations}\label{eq:problem2}
 \begin{align}
-&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
-+  \langle \mtrace v - \vd, \ld \rangle_{\Lambda, |\DD|} &&
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
-\quad && \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)\,,
-\\
-& \langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} = 0
-\quad &&\forall \md \in H^{-\frac 1 2}(\Lambda)\,,
-\end{align}
-\end{subequations}
-Furthermore, the weak formulation of \eqref{inteq:pde}, refered to as \textbf{Problem 3D-1D-2D}, reads: 
-Find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac 1 2}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
-\begin{subequations}\label{eq:problem1}
-\begin{align}
-&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
-+ \langle \trace v  - \ext \vd, \lambda \rangle_\Gamma &&
-\\
-\nonumber
-&\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
-\quad &&\forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)\,,
-\\
-& \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0
-\quad && \forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
+(u,v)_{H^1(\Omega)} 
++  \langle \mtrace v, \ld \rangle_{\Lambda, |\DD|} &= 
+(f,v)_{L^2(\Omega)} &\forall v \in H^1_0(\Omega)\, ,\\
+(\ud,\vd)_{H^1(\Lambda),|\D|} - \langle  \vd, \ld \rangle_{\Lambda, |\DD|} 
+&=  (\avrd{g},V)_{L^2(\Lambda),|\D|}
+&\forall \vd \in H^1_0(\Lambda)\, ,\\
+\langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} &= 0
+&\forall \md \in H^{-\frac 1 2}(\Lambda)\,,
 \end{align}
@@
 
-\section{Derivation of the model}
-Below we detail the steps performed in order to formulate \ref{eq:problem1} and \ref{eq:problem2} precisely. 
-The derivations are similar~\cite{laurino_m2an},  but here we derive the system including the Lagrange multiplier.
-
-\subsection{Topological model reduction}
-
-We consider the problem arising from \emph{Dirichlet-Neumann} conditions. Find $\up,\uf$ s.t.:
-\begin{subequations}\label{eq:dirneu}
+In addition to the 3D-1D-1D problem we will also consider an 
+intermediate problem where the 3D and 1D problems are coupled at an
+intermediate 2D surface  encapsulating the 1D structure. The strong form is:  
+\begin{subequations}
+\label{inteq:pde}
 \begin{align}
-\label{eq:dirneu1}
-- \Delta \up  + \up &= f  && \text{ in } \Omega_{\oplus},\\
-\label{eq:dirneu2}
-- \Delta \uf  + \uf &= g  && \text{ in } \Omega_\ominus,\\
-\label{eq:dirneu3}
--\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
-\label{eq:dirneu4}
-\uf &= \up && \text{ on }  \Gamma,\\
-\label{eq:dirneu5}
-\up &= 0 && \text{ on } \partial \Omega\,.
+\label{inteq:pde1}
+  -\Delta u + u + \lambda \delta_{\Lambda} &= f &\mbox{ in } \Omega,\\ 
+\label{inteq:pde2}
+ d_s^2 \ud + \ud - \lambda &= g &\mbox{ on } \Lambda,\\
+\label{inteq:coupling}
+\mathcal{T}_\Lambda u - v  &=  h &\mbox{ on } \Gamma . 
 \end{align}
@@
 
-We observe that the coupling constraints defined on $\Gamma$ involve essential or strong conditions.
-The strong conditions will, however, be enforced weakly by using the method of Lagrange multipliers~\cite{MR359352}.
-%We remark that this case is substantially different from the one previously addressed in \cite{laurino_m2an}.
-
-The variational formulation of problem \eqref{eq:dirneu}
-is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus), \ \lambda \in H^{-\frac 1 2}(\partial\Omega_\ominus)$ s.t.
-\begin{subequations}\label{eq:weak_dirneu}
+The corresponding weak formulation of \eqref{inteq:pde}, refered to as the \textbf{Problem 3D-1D-2D}, reads: 
+Find $u \in H^1_0(\Omega), \ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac 1 2}(\Gamma ) $ such that
+\begin{subequations}\label{eq:problem1}
 \begin{align}
-&(u_\oplus,v_\oplus)_{H^1(\Omega_\oplus)} + (u_\ominus,v_\ominus)_{H^1(\Omega_\ominus)} 
-+ \langle  v_\oplus - v_\ominus, \lambda \rangle_{\Gamma} 
+(u,v)_{H^1(\Omega)} + \langle \trace v, \lambda \rangle_\Gamma &= (f,v)_{L^2(\Omega)} &\forall v \in H^1_0(\Omega)\, ,
 \\
-\nonumber
-&\qquad\qquad = (f,v_\oplus)_{L^2(\Omega_\oplus)} + (g,v_\ominus)_{L^2(\Omega_\ominus)}
-\quad \forall v_\oplus \in H^1_{\partial\Omega}(\Omega_\oplus), \ v_\ominus \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus)
-\\
-& \langle u_\oplus - u_\ominus, \mu \rangle_{\Gamma} = 0
-\quad \forall  \mu \in H^{-\frac 1 2}(\Gamma)\,,
+ (\ud,\vd)_{H^1(\Lambda),|\D|}  -  \langle \ext \vd, \lambda \rangle_\Gamma
+&=  (\avrd{g},\vd)_{L^2(\Lambda),|\D|} &\forall\vd \in H^1(\Lambda)\, ,\\
+\langle \trace u - \ext \ud , \mu \rangle_\Gamma &= 0 &\forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
 \end{align}
 \end{subequations}
-%where $\langle v, \mu \rangle_{H^{-\frac 1 2}(\Gamma)}$ denotes the duality pairing between 
-%$ \mu \in H^{-\frac 1 2}(\Gamma)$ and $v \in H^{\frac 1 2}(\Gamma)$.
-In this case, $\lambda$ is the Lagrange multiplier and it is equivalent to $\nabla \uf \cdot \nn_\ominus$.
-
-The objective of this work is to derive and analyze a simplified version of problem \eqref{eq:weak_dirneu}, where the domain $\Omega_\ominus$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$.
-This new problem setting will be called the \emph{reduced} problem.
-Form the mathematical standpoint it is more challenging than \eqref{eq:weak_dirneu}, because it involves the coupling of 3D/1D elliptic problems.
-We end up with two different formulations of a reduced problem for the unknown $u$ defined on the entire 3D domain $\Omega$, 
-coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$ and a Lagrange multiplier defined either on $\Gamma$ (Problem 3D-1D-2D) or on $\Lambda$ (Problem 3D-1D-1D). 
-The scope of this work is to analyze and compare the two alternatives,
-with the aim to determine which is the most suitable to set up a computational model for 3D-1D PDEs coupled with Dirichlet-Neumann constraint.
-
-\subsubsection*{Model reduction of the problem on $\Omega_{\ominus}$}
-
-We apply the averaging technique to equation \eqref{eq:dirneu2}.
-In particular, we consider an arbitrary portion $\mathcal{P}$ of the cylinder $\Omega_\ominus$, with lateral surface $\Gamma _{\mathcal{P}}$ and bounded by two perpendicular sections to $\Lambda$, namely $\mathcal{D}(s_1), \ \mathcal{D}(s_2)$ with $s_1<s_2$.
-We have,
-\begin{multline*}
-\int_{\mathcal{P}} -\Delta \uf + \uf d\omega =
--\int_{\partial \mathcal{P}} \nabla \uf \cdot \nn_{\ominus} \, d\sigma  + \int_{\mathcal{P}}\uf d\omega=
-\\
- \int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma -  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma -  \int_{\Gamma_{\mathcal{P}}} \nabla \uf \cdot \nn_{\ominus} d\sigma +\int_{\mathcal{P}}\uf d\omega
-\end{multline*}
-By the fundamental theorem of integral calculus combined with the Reynolds transport Theorem, 
-being $\nu$ the normal deformation of the boundary along $(0,S)$, we have,
-\begin{equation*}
-\begin{split}
-\int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma -  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma 
-&= -\int_{s_1}^{s_2} d_s \int_{\mathcal{D}(s)}  \partial_s \uf d\sigma ds
-\\
-&= -\int_{s_1}^{s_2} d_{ss}^2 \int_{\D(s)} u_{\ominus} \, d\sigma \, ds +  \int_{s_1}^{s_2} d_s \left( \int_{\DD(s)} \nu u_{\ominus} \, d\gamma \right) ds\,,
-\end{split}
-\end{equation*}
-and assuming that $\D(s)$  can not change shape, we have
-\begin{equation*}
-\begin{split}
--\int_{s_1}^{s_2} d_{ss}^2 \int_{\D(s)} u_{\ominus} \, d\sigma \, ds + \int_{s_1}^{s_2} d_s \left( \int_{\DD(s)} \nu u_{\ominus} \, d\gamma \right)\, ds
-&=-\int_{s_1}^{s_2} \left[d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) -  d_s(  \nu |\DD(s)| \avrc{u}_{\ominus} ) \right] \, ds
-\\
-&=-\int_{s_1}^{s_2} \left[d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) -  d_s\left(d_s(|\D(s)|) \avrc{u}_{\ominus} \right) \right] \, ds.
-\end{split}
-\end{equation*}
-Moreover, we have
-\begin{equation*}
-\int_{\Gamma_{\mathcal{P}}} \nabla \uf \cdot \nn_{\ominus} d\sigma =  \int_{\Gamma_{\mathcal{P}}} \lambda \, d\sigma
-=  \int_{s_1}^{s_2} \int_{\partial\mathcal{D}(s)} \lambda d\gamma \, ds 
-= \int_{s_1}^{s_2} |\DD| \avrc{\lambda} \,ds\,.
-\end{equation*}
-From the combination of all the above terms with the right hand side, we obtain that the solution $\uf$ of \eqref{eq:dirneu2} satisfies,
-\begin{equation*}
-\int_{s_1}^{s_2} \left[ 
--d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) +  d_s\left(d_s(|\D(s)|) \avrc{u}_{\ominus}\right) + |\D(s)|\avrd{u}_{\ominus} 
-- |\partial\mathcal{D}(s)| \avrc{\lambda} 
-\right] \, ds = \int_{s_1}^{s_2} |\mathcal{D}(s)| \avrd{g}\, ds \,.
-\end{equation*}
-Since the choice of the points $s_1,s_2$ is arbitrary, we conclude that the following equation holds true,
-\begin{equation}\label{eq:averaged_f}
--d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) +  d_s\left(d_s(|\D(s)|) \avrc{u}_{\ominus}\right) + |\D(s)|\avrd{u}_{\ominus} 
-- |\partial\mathcal{D}(s)| \avrc{\lambda}
-= |\mathcal{D}(s)| \avrd{g} \quad \text{on} \ \Lambda\,,
-\end{equation}
-which is complemented by the following conditions at the boundary of $\Lambda$,
-\begin{equation}\label{eq:averaged_f_boundary}
-|\D(s)| d_s \avrd{u}_{\ominus} = 0, \quad d_s |\D(s)| = 0, \quad \text{on} \quad s=0,S.
-\end{equation}
-Then, we consider variational formulation of the averaged equation \eqref{eq:averaged_f}.
-After multiplication by a test function $\vd \in H^1(\Lambda)$, integration on $\Lambda$ and suitable application of integration by parts, we obtain,
-\begin{multline*}
-\int_\Lambda d_s (|\D(s)| \avrd{u}_{\ominus} ) d_s \vd \, ds - d_s (|\D(s)| \avrd{u}_{\ominus} ) \vd |_{s=0}^{s=S}
-- \int_\Lambda (d_s |\D(s)|)\avrc{u}_{\ominus} d_s \vd \, ds + (d_s |\D(s)|) \avrc{u}_{\ominus} \vd |_{s=0}^{s=S}
-\\
-+\int_\Lambda |\D(s)| \avrd{u}_\ominus \vd - \int_\Lambda |\DD(s)| \avrc{\lambda} \vd \, ds
-= \int_\Lambda |\D(s)| \avrd{g} V\, ds\,.
-\end{multline*}
-Using boundary conditions, 
-the identity $d_s (|\D(s)| \avrd{u}_{\ominus} ) = |\D(s)| d_s \avrd{u}_{\ominus} + d_s (|\D(s)|) \avrd{u}_{\ominus}$
-and reminding that $d_s |\D(s)|)/|\DD(s)| = \nu$,
-we obtain,
-\begin{equation}\label{eq:averaged_f_weak}
-(d_s \avrd{u}_{\ominus}, d_s \vd )_{\Lambda,|\D|} 
-+ ( \nu (\avrd{u}_{\ominus} - \avrc{u}_{\ominus}), d_s \vd)_{\Lambda,|\DD|} +(\avrd{u}_\ominus, \vd)_{\Lambda, |\D|}
-- (\avrc{\lambda},\vd)_{\Lambda,|\DD|}
-= (\avrd{g},V)_{\Lambda,|\D|}\,.
-\end{equation}
-Let us now formulate the modelling assumption that allows us to reduce equation \eqref{eq:averaged_f_weak} to a solvable one-dimensional (1D) model.
-More precisely, we assume that the function $\uf$ has a \emph{uniform profile} on each cross section $\mathcal{D}(s)$, namely $\uf(r,s,t) = \ud(s)$.
-Therefore, observing that $\ud=\avrc{u}_{\ominus}=\avrd{u}_{\ominus}$, problem \eqref{eq:averaged_f_weak} turns out to find $\ud \in H^1(\Lambda)$ such that
-\begin{equation}\label{eq:1Ddirneu_weak}
- (d_s \ud, d_s \vd)_{\Lambda,|\mathcal{D}|} 
-+(\ud, \vd)_{\Lambda, |\D|}
--(\avrc{\lambda},\vd)_{\Lambda, |\DD|}
-=  (\avrd{g},\vd)_{\Lambda, |\mathcal{D}|}
-\quad \forall \vd \in H^1(\Lambda)\,.
-\end{equation}
-
-% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-\subsubsection*{Topological model reduction of the problem on $\Omega_{\oplus}$}
-We focus here on the subproblem of \eqref{eq:dirneu1} related to $\Omega_{\oplus}$.
-We multiply both sides of \eqref{eq:dirneu1} by a test function $v\in H^1_0(\Omega)$ and integrate on $\Omega_\oplus$. Integrating by parts and using boundary and interface conditions, we obtain
-\begin{equation*}
-\begin{split}
-\int_{\Omega _{\oplus}}fv\,d\omega&=
-\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\omega -\int _{\partial \Omega _{\oplus}}\nabla \up \cdot \nn_{\oplus} v\,d\sigma + \int_{\Omega_{\oplus}} \up v
-\\
-&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega -\int_{\Gamma} \nabla \up \cdot \nn_{\oplus} v + \int_{\Omega_{\oplus}} \up v
-\\
-&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega +\int_{\Gamma} \lambda v + \int_{\Omega_{\oplus}} \up v.
-\end{split}
-\end{equation*} 
-Then, we make the following modelling assumption:
-we identify the domain $\Omega_{\oplus}$ with the entire $\Omega$, 
-and we correspondingly omit the subscript $\oplus$ to the functions defined on $\Omega_{\oplus}$,
-namely
-\begin{equation*}
-\int_{\Omega_{\oplus}} u_\oplus\, d\omega \simeq \int_{\Omega} u\, d\omega\,.
-\end{equation*}
-Therefore, we obtain 
-\begin{equation*}
-(\nabla u ,\nabla v)_{\Omega} +(u,v)_{\Omega}+(\lambda, v)_{\Gamma}  =(f,v)_{\Omega}
-\end{equation*}
-and combining with \eqref{eq:1Ddirneu_weak} we obtain the first formulation of the reduced problem.
-
-Hence, we have obtained the Problem 3D-1D-2D, equation 
-\eqref{eq:problem1}: \\
-Find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac 1 2}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
-\begin{subequations}
-\begin{align*}
-&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
-+ \langle \trace v  - \ext \vd, \lambda \rangle_\Gamma &&
-\\
-\nonumber
-&\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
-\quad &&\forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)\,,
-\\
-& \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0
-\quad && \forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
-\end{align*}
-\end{subequations}
-This coupled problem is classifies as 3D-1D-2D because the unknowns $u,\lambda,\ud$ belong to 
-$\Omega \subset \R^3,\, \Gamma \subset \R^2,\, \Lambda \subset \R$, respectively.
-Then, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-2D formulation
-involving sub-problems on $\Omega$ and $\Lambda$ and coupling operators defined on $\Gamma$
-to a 3D-1D-1D formulation where the coupling terms are set on $\Lambda$. 
-To this purpose, let us write the Lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
-\begin{equation*}
-\lambda=\avrc{\lambda}+\tilde{\lambda}, \qquad v=\avrc{v}+\tilde{v},
-\quad \text{on} \ \partial\mathcal{D}(s)\,,
-\end{equation*}
-where $\avrc{\tilde{\lambda}}=\avrc{\tilde{v}}=0$. 
-Therefore, the coupling term on $\Gamma$ can be decomposed as,
-\begin{equation*}
-\int_{\Gamma}\lambda v\, d\sigma
-=\int _{\Lambda}  \int_{\partial\mathcal{D}(s)} (\avrc{\lambda}+\tilde{\lambda})(\avrc{v}+\tilde{v})d\gamma ds
-= \int_{\Lambda}|\partial\mathcal{D}(s)| \avrc{\lambda}\avrc{v}\,ds+\int_{\Lambda}  \int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v}d\gamma ds\,.
-\end{equation*}
-
-Thanks to the additional assumption that the product of fluctuations is small, namely
-\begin{equation*}
-\int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v} d\gamma \simeq 0\,
-\end{equation*}
-the term $\left(\trace v, \lambda \right)_{\Gamma}$ becomes $\left( \mtrace v, \avrc{\lambda} \right)_{\Lambda, |\DD|}$, where $\mtrace$ denotes the composition of operators $\trace \circ \avrc{(\cdot)}$.
-Combined with \eqref{eq:1Ddirneu_weak}, this leads to the second formulation of the reduced problem.
-
-Hence, we have derived the Problem 3D-1D-1D, equation \eqref{eq:problem2}: \\ 
-Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac 1 2}(\Lambda)$, such that
-\begin{subequations}
-\begin{align*}
-&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
-+  \langle \mtrace v - \vd, \ld \rangle_{\Lambda, |\DD|} &&
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
-\quad && \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)\,,
-\\
-& \langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} = 0
-\quad &&\forall \md \in H^{-\frac 1 2}(\Lambda)\,,
-\end{align*}
-\end{subequations}
-We notice that all the integrals of the reduced problem are well defined because 
-$\mtrace: H^1_0(\Omega) \rightarrow H^\frac 1 2_{00}(\Lambda)$ as shown in Corollary \ref{corollary:H12norm}.
-
-The well-posedness of $\eqref{eq:problem1}$ and $\eqref{eq:problem2}$ 
-can be studied in the framework of the classical theory of saddle point problems as shown in the following.
 
@@
 
-\input{preliminary_results.tex}
+\begin{lemma}\label{lemma:H12norm}
+Let $\Gamma$ be a tensor product domain, $\Gamma= (0,X) \times (0,Y)$.
+For any regular $u(x,y)$ in $\Gamma$, let $\avrc{u}(x)=\frac 1Y \int _0^Y u(x,y)\, dy$.
+Then, for any $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}(x)\in H_{00}^{\frac 12}((0,X))$.
+Moreover, if $u(x,y)\in H^{\frac 12}_{00}(\Gamma)$ is constant with respect to $y$, namely $u(x,y)=u(x)$, then 
+\begin{equation*}
+\|u\|_{H^{\frac 12}_{00}(\Gamma)}=Y \|u\|_{H^{\frac 12}_{00}(0,X)}.
+\end{equation*}
+\end{lemma}
+The proof of \label{lemma:H12norm} is based on the representation of fractional norms in terms of the spectrum of the Laplace operator and subsequent standard arguments in harmonic analysis.
+The full proof is reported in the appendix for the sake of clarity.
+
+%\begin{corollary}
+%Let $\Gamma$ be the lateral surface of a prism with $N$ faces $\Gamma_i$, $i=1, \dots, N$, with $\Gamma_i=(0,X_i)\times(0,S)$.
+For any $u\in H^{\frac 12}_{00}(\Gamma)$, let $\avrc{u}(s)= \frac{1}{\sum_i{|X_i|}}\sum_{i=1}^N \int_0^{X_i} u(x,s)\, dx$.
+Then $\avrc{u}\in H^{\frac 12}_{00}(0,S )$ {\color{red} and there exists a constant $C_\Gamma$ such that
+%\begin{equation*}
+%\|\avrc{u}\|_{H^{\frac 12}(0,S)} \leq C_\Gamma \|u\|_{H^{\frac 12}(\Gamma)}.
+%\end{equation*}
+%}
+%\end{corollary}
+
+%\begin{corollary}
+%Let $\Gamma$ be the lateral surface of a cylinder of radius $R$.
+Let $u\in H^{\frac 12}_{00}(\Gamma)$ and let $\avrc{u}(s)= \frac{1}{2\pi R} \int_0^{2\pi} u(s,\theta)R\, d\theta$.
+Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$ and there exists a constant $C_\Gamma$ such that
+%\begin{equation*}
+%\|\avrc{u}\|_{H^{\frac 12}(0,S)} \leq C_\Gamma \|u\|_{H^{\frac 12}(\Gamma)}.
+%\end{equation*}
+%\end{corollary}
+
+Under the geometric assumptions stated above for $\Omega,\,\Gamma,\,\Lambda$, Lemma \ref{lemma:H12norm} implies the following result.
+\begin{corollary}\label{corollary:H12norm}
+If $u\in H^{\frac 12}_{00}(\Gamma)$ then $\avrc{u}\in H^{\frac 12}_{00}(\Lambda)$ and there exists a constant $C_\Gamma$ such that
+\begin{equation*}
+\|\avrc{u}\|_{H^{\frac 12}_{00}(\Lambda), |\DD|} \leq C_\Gamma \|u\|_{H^{\frac 12}_{00}(\Gamma)}.
+\end{equation*}
+\kent{Here, $C_\Gamma$ is bounded independently of $D(s)$.} 
+\end{corollary}
 
@@
 %Analysis of the continuous problem 
-\input{infsup_continuous}
+\section{Saddle-point problem analysis}
+Let $a: X \times X \rightarrow \mathbb{R}$ and $b: X\times Q \rightarrow \mathbb{R}$ be bilinear forms. Let us consider a general saddle point problem of the form: find $u\in X$, $\lambda\in Q$ s.t.
+\begin{eqnarray}\label{eq:saddle-point}
+\begin{aligned}
+a(u,v)+b(v,\lambda)&=c(v),\quad &\forall v\in X,\\
+b(u,\mu)&=d(\mu), \quad &\forall \mu\in Q.
+\end{aligned}
+\end{eqnarray}
+%We denote with $A$ and $B$ the operators associated to the bilinear forms $a$ and $b$, namely $A: X \longrightarrow X'$ with $\langle Au,v\rangle _{X',X} = a(u,v)$ and $B: X \longrightarrow Q'$ with $\langle Bv,\mu\rangle_{Q',Q} = b(v,\mu)$.
+Problem \eqref{eq:saddle-point} embraces problems 1 and 2 described before.
+The Brezzi conditions \cite{MR365287} ensure that the problem \eqref{eq:saddle-point} is well-posed.
+For our purpose here, we use the following relaxed version of the Brezzi conditions:  
+\begin{theorem}{}\label{th:bnb}
+Problem \eqref{eq:saddle-point} is well posed if the following conditions are satisfied
+\begin{align}\label{BNB1}
+a(u,u) &\ge \alpha \|u\|^2_{X}, & u\in X\\
+\label{BNB2}
+a(u,v) &\le C \|u\|_{X}\|v\|_{X}, & u,v \in X\\
+\label{BNB3}
+b(u,\mu) &\ge D \|u\|_{X} \|\mu\|_{Q}, & u\in X, \mu\in Q\\
+\label{BNB4}
+\sup_{v\in X} \frac{b(v,\mu)}{\|v\|_{X}} &\geq \beta\|\mu\|_{Q}, & \mu \in Q .\\
+\end{align}
+Here $\alpha$, $\beta$, $C$, and $D$ are positive numbers. 
+\end{theorem} 
+Here, the coercivity condition \eqref{BNB1} applies to $X$, which is a relaxation of Brezzi's original conditions.
 
 %>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-%Analysis of the discrete problem in the case in which the LM lives on the coarser mesh w.r.t the trace mesh deriving from the 3D mesh
+\subsection{Problem 3D-1D-2D}
+We aim to find $u \in H^1_0(\Omega),\ \ud \in H_0^1(\Lambda), \ \lambda \in H^{-\frac12}(\Gamma )$,
+solutions of \eqref{eq:saddle-point}, where
+\begin{align*}
+a([u, \ud], [v, \vd])&= (u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|}
+\\
+b([v, \vd], \mu)&= \langle \trace v - \ext \vd , \mu \rangle_\Gamma
+\\
+c([v,\vd])&= (f,v)_{L^2(\Omega)} + (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
+\\
+d(\mu)&=0
+\end{align*}
+We prove that the conditions of Theorem \ref{th:bnb} are fullfilled choosing 
+$X=H^1_0(\Omega) \times H^1_0(\Lambda)$, $Q=H^{-\frac 12}(\Gamma)$, where $X$  is equipped with the norm $\vertiii{[u,\ud ]}^2=\|u\|^2_{H^1(\Omega)} + \|\ud\|^2_{H^1(\Lambda),|\D|}$.
+\kent{We should state somewhere that $H^1$ and its weighted space are the same in 
+the sense of set, but that we the parameter dependent norm makes up a cleaner analysis}
+\begin{lemma}\label{lemma:prob1_boundedness} 
+The Problem 3D-1D-2D is well-posed.
+\end{lemma}
+\begin{proof}
+We need to establish the four Brezzi conditions. 
+The bilinear form $a(\cdot \ , \ \cdot)$ is clearly bounded and coersive since 
+\begin{equation*}
+a([u, \ud], [v, \vd]) = (u,v)_{H^1(\Omega)} + (\ud, \vd)_{H^1(\Lambda), |\D|}.
+\end{equation*}
+Furthermore, the bilinear form $b(\cdot \ , \ \cdot)$ is bounded because
+\begin{multline*}
+b([v, \vd], \mu)= \langle \trace v - \ext \vd , \mu \rangle_\Gamma 
+\leq \|\trace v - \ext \vd\|_{H^{\frac 12}_{00}(\Gamma)}\|\mu\|_{H^{-\frac 12}(\Gamma)}\\
+\leq \left(\|\trace v\|_{H^{\frac 12}_{00}(\Gamma)} + \|\ext \vd\|_{H^{\frac 12}_{00}(\Gamma)}\right)\|\mu\|_{H^{-\frac 12}(\Gamma)}
+\leq \left(C_T \|v\|_{H^1(\Omega)} + \|\ext \vd\|_{H^1(\Gamma)}\right)\|\mu\|_{H^{-\frac 12}(\Gamma)}\\
+\leq \left(C_T \|v\|_{H^1(\Omega)} + \left(\frac{\max |\DD|}{\min |\D|}\right)^{\frac 12} \|\vd\|_{H^1(\Lambda),|\D|}\right)\|\mu\|_{H^{-\frac 12}(\Gamma)}\\
+\leq \left( C_T + \left(\frac{\max |\DD|}{\min |\D|}\right)^{\frac 12}\right) \vertiii{[v,\vd]}\|\mu\|_{H^{-\frac 12}(\Gamma)}
+\end{multline*}
 
-%\input{infsup_discrete_coarserLM}
+\kent{In the proof of the boundedness above we first
+go $H^{1/2}\rightarrow H^1$. Then $\Gamma\rightarrow\Lambda$. Is this what we want
+? Relation to Corr 2.2 is clearer if we go the other way. Also, if we go the other
+way it is less clear to me that we end up with the $\frac{\max \partial D}{\min D}}$ term. }
 
-%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-%Analysis of the discrete problem in the case in which the LM lives on the the trace mesh deriving from the 3D mesh (conforming to the interface cylinder \Gamma)
+To show the inf-sup condition, we will employ a harmonic extension operator. 
+We denote with $\mathcal{H}_\Omega$ the harmonic extension operator defined is $\mathcal{H}_\Omega \xi = v$ where $v$ is the weak solution of
+\begin{equation}\label{eq:harmonic}
+-\Delta v=0 \ \text{in} \ \Omega,
+\quad
+v=0 \ \text{on} \ \partial \Omega,
+\quad
+v=\xi \ \text{on} \ \Gamma. 
+\end{equation}
+The boundedness/stability of this operator ensures that there exists $\| \mathcal{H}_\Omega \| \in \mathbb{R}$ such that
+$\|v \|_{H^1(\Omega)}\leq \|\mathcal{H}_\Omega\| \|\xi \|_{H^{\frac 12}_{00}(\Gamma)}$.
 
-\input{infsup_discrete_conformingLM}
+The inf-sup inequality is fulfilled, that is; 
+we choose $\vd \in H^1_0(\Lambda)$ such that $\ext\vd =0$. Therefore,
+\begin{equation*}
+\sup _{\substack{v\in H^1_0(\Omega),\\ \vd \in H^1_0(\Lambda)}} \frac{ \langle \trace v  - \ext \vd, \mu\rangle_\Gamma}{\vertiii{[v, \vd]}} 
+\geq \sup _{v\in H^1_0(\Omega)} \frac{ \langle \trace v, \mu \rangle_\Gamma}{\|v\|_{H^1(\Omega)}}.
+\end{equation*}
+We notice that the trace operator is surjective from $H^1_0(\Omega)$ to $H^{\frac12}_{00}(\Gamma)$. Indeed, $\forall \xi \in H^{\frac 12}_{00}(\Gamma)$, 
+we  can find $v=\mathcal{H}_\Omega \xi$ solution of \eqref{eq:harmonic}. Using the stability of the harmonic extension we obtain
+\begin{equation}\label{infsup_traceop}
+\sup _{v\in H^1_0(\Omega)} \frac{ \langle \trace v, \mu \rangle_\Gamma}{\|v\|_{H^1(\Omega)}}
+\geq  \sup _{\xi \in H^{\frac 12}_{00}(\Gamma )} \frac{ \langle \xi , \mu \rangle_\Gamma}{\|\mathcal{H}_\Omega\| \|\xi\|_{H^{\frac 12}_{00}(\Gamma)}}
+= \|\mathcal{H}_\Omega\|^{-1} \|\mu\|_{H^{-\frac 12}(\Gamma)},
+\end{equation}
+where in the last inequality we exploited the fact that $H^{-\frac 12}(\Gamma)=(H^{\frac 12 }_{00}(\Gamma))^*$. 
+\end{proof}
+
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\subsection{Problem 3D-1D-1D}
+We aim to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$,
+solution of \eqref{eq:saddle-point} with
+\begin{align*}
+a([u, \ud], [v, \vd])&= (u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|}
+\\
+b([v, \vd], \md)&=  \langle  \mtrace v - \vd, \md \rangle_{\Lambda, |\DD|} 
+\\
+c([v,\vd])&= (f,v)_{L^2(\Omega)} + (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
+\\
+d(\md)&=0
+\end{align*}
+
+We prove that the hypotesis of  Theorem \ref{th:bnb} are fulfilled with the following spaces $X=H^1_0(\Omega) \times H^1_0(\Lambda)$, $Q=H^{-\frac 12}(\Lambda)$.
+Let us consider $X$ equipped again with the norm $\vertiii{[\cdot,\cdot ]}$ and  
+$Q$ equipped with the norm $\|\cdot \|_{H^{-\frac 12}(\Lambda),|\DD|}$.
+Then, we have the following lemmas.
+\begin{lemma}
+The Problem 3D-1D-1D is well-posed.
+\end{lemma}
+\begin{proof}
+Again, 
+\begin{equation*}
+a([u, \ud], [v, \vd]) = (u,v)_{H^1(\Omega)} + (\ud, \vd)_{H^1(\Lambda), |\D|}.
+\end{equation*}
+The bound on $b(\cdot \ , \ \cdot)$ is established as
+\begin{multline*}
+b([v, \vd], \md)=  \langle  \mtrace v - \vd, \md \rangle_{\Lambda, |\DD|} 
+\leq \|\mtrace v - \vd\|_{H^{\frac 12 }_{00}(\Lambda), |\DD|}\|\md\|_{H^{-\frac 12}(\Lambda),|\DD|}\\
+\leq \left(\|\mtrace v\|_{H^{\frac 12 }_{00}(\Lambda), |\DD|}+\|\vd\|_{H^{\frac 12 }_{00}(\Lambda), |\DD|}\right)\|\md\|_{H^{-\frac 12}(\Lambda),|\DD|}\\
+\leq \left(C_\Gamma \|\trace v\|_{H^{\frac 12 }_{00}(\Gamma)}+ \|\vd\|_{H^1(\Lambda), |\DD|}\right)\|\md\|_{H^{-\frac 12}(\Lambda),|\DD|} \\
+\leq \left(C_\Gamma C_T\|v\|_{H^1(\Omega)}+ \left(\frac{\max |\DD|}{\min |\D|}\right)^{\frac 12} \|\vd\|_{H^1(\Lambda), |\D|}\right) \|\md\|_{H^{-\frac 12}(\Lambda),|\DD|} \\
+\leq  \left( C_\Gamma C_T + \left(\frac{\max |\DD|}{\min |\D|}\right)^{\frac 12} \right) \vertiii{[v,\vd]}\|\md\|_{H^{-\frac 12}(\Lambda),|\DD|}.
+\end{multline*} 
+The inf-sup condition holds. 
+We choose $\vd=0$ and we obtain
+\begin{equation*}
+\sup _{\substack{v\in H^1_0(\Omega),\\ \vd \in H^1_0(\Lambda)}} \frac{ \langle \mtrace v - \vd, \md \rangle_{\Lambda,|\DD|}}{\vertiii{[v,\vd]}}
+\geq \sup _{v\in H^1_0(\Omega)} \frac{ \langle \mtrace v, \md \rangle_{\Lambda,|\DD|}}{\|v\|_{H^1(\Omega)}}. 
+\end{equation*}
+
+For any $q \in H^{\frac 12}_{00}(\Lambda)$, we consider its uniform extension to $\Gamma$ named as $\ext q$
+and then we consider the harmonic extension $v=\mathcal{H}_\Omega \ext q\in H^1_0(\Omega)$. It follows that $\mtrace v=q$. Therefore, 
+\begin{equation*}
+\sup _{v\in H^1_0(\Omega)}  \langle \mtrace v, \md \rangle_{\Lambda,|\DD|} \geq\sup_{q \in H^{\frac 12}_{00}(\Lambda)} \langle q, \md  \rangle_{\Lambda,|\DD|}\,.
+\end{equation*}
+Moreover, using Lemma \ref{lemma:H12norm} we obtain
+\begin{equation*}
+\|v\|_{H^1_0(\Omega)}\leq \|\mathcal{H}_\Omega\| \|\ext q\|_{H^{\frac 12}_{00}(\Gamma)}  = \|\mathcal{H}_\Omega\| \|q\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}.
+\end{equation*}
+ Therefore,
+\begin{align*}
+\sup _{v\in H^1_0(\Omega)} \frac{ \langle \mtrace v, \md \rangle_{\Lambda,|\DD|}}{\|v\|_{H^1(\Omega)}}
+\geq \sup _{q\in H^{\frac 12}_{00}(\Lambda)} \frac{ \langle q, \md \rangle_{\Lambda,|\DD|}}{\|v\|_{H^1(\Omega)}}
+\geq \frac{1}{\|\mathcal{H}_\Omega\|} \sup _{q\in H^{\frac 12}_{00}(\Lambda)} \frac{ \langle q, \md \rangle_{\Lambda,|\DD|}}{\|q\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}} 
+= \frac{1}{\|\mathcal{H}_\Omega\|} \|\md\|_{H^{-\frac 12}(\Lambda),|\DD|}.
+\end{align*}
+\end{proof}
 
@@
 
-\input{unfitted_prob2}
+\section{Finite element approximation}
+In this section we consider the discretization of the Problems 3D-1D-2D and 3D-1D-1D by means of the finite element method.
+We address two main challenges; first we aim to identify a suitable approximation space for the Lagrange multiplier and to analyze the stability of the discrete saddle point problem; second we aim to derive a stable discretization method that uses independent computational meshes for $\Omega$, $\Gamma$ and $\Lambda$.
+Let us introduce a shape-regular triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{h}$ of $\Lambda$.
+We analyze two different cases: the one in which the 3D mesh is conforming to the interface $\Gamma$, namely the set of the intersections of the 3D elements of $\mathcal{T}^{\Omega}_h$ with $\Gamma$ is constituted by facets of such elements, and the non conforming case, namely the interface $\Gamma$ cuts the mesh arbitrarily.
+The discrete equivalent of \eqref{eq:saddle-point} reads as finding $u_h\in X_h\subset X$, $\lambda_h\in Q_h\subset Q$ s.t.
+\begin{eqnarray}\label{eq:saddle-point_discrete}
+\begin{cases}
+a(u_h,v_h)+b(v_h,\lambda_h)=c(v_h)\quad &\forall v_h\in X_h\\
+b(u_h,\mu_h)=d(\mu_h) \quad &\forall \mu_h\in Q_h.
+\end{cases}
+\end{eqnarray}
+This discrete problem is well-posed if the \eqref{BNB1}-\eqref{BNB4} conditions applies to $X_h$ and $Q_h$. Since $X_h\subset X$ and $Q_h\subset Q$,  
+\eqref{BNB1}-\eqref{BNB3} follows immediately and only the inf-sup condition needs consideration.  We summarize this in the Corollary below. 
+\begin{corollary}{\cite[Theorem 2.42]{MR2050138}}\\
+Let
+$X_h \subset X$, $Q_h \subset Q$, $a(\cdot, \cdot)$ and $b(\cdot, \cdot)$ satisfy the conditions  \eqref{BNB1}-\eqref{BNB3} then  
+the problem \eqref{eq:saddle-point_discrete} is well-posed if 
+the discrete counterpart of \eqref{BNB4} is satisfied, ie., 
+there exists a $\beta_h>0$ such that
+\begin{align}
+\label{eq:infsup_discrete}
+ \sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}}\geq \beta_h |\mu_h\|_{Q}\, .
+\end{align}
+\end{corollary}
+
+\subsection{$\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}
+ We first analyze the case in which the 3D mesh is conforming to the interface $\Gamma$.
+As conformity conditions between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$ with $\Gamma$ , we require that the intersection of $\mathcal{T}^{\Omega}_h$ and $\Gamma$ is made of entire faces of elements $K \in \mathcal{T}^{\Omega}_h$.
+Furthermore, we also set a restriction between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$.
+We assume that $\Lambda$ is a piecewise linear manifold.
+We want that the intersection of $\Gamma$ with any orthogonal plane to $\Lambda$ that crosses $\Lambda$ at the internal nodes of $\mathcal{T}^{\Lambda}_h$, consists of entire edges of $\mathcal{T}^{\Omega}_h$.
+
+\subsubsection{Problem 3D-1D-2D}
+We denote by $X_{h,0}^k(\Omega)\subset H^1_0(\Omega)$, with $k>0$, the conforming finite element space of continuous piecewise polynomials of degree $k$ defined on $\Omega$ satisfying homogeneous Dirichlet conditions on the boundary and by $X_{h,0}^k(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$, satisfying homogeneous Dirichlet conditions on $\Lambda \cap \partial \Omega$.
+
+The discrete version of Problem 1 is:
+find $u_h \in X_{h,0}^k (\Omega) ,\, {\ud}_h \in X_{h,0}^k(\Lambda) ,\, \lambda_h \in Q_h \subset H^{-\frac12}(\Gamma )$, such that
+\begin{subequations}
+\begin{align}
+&(u_h,v_h)_{H^1(\Omega)} + ({\ud}_h,{\vd}_h)_{H^1(\Lambda),|\D|} 
++ \langle \trace v_h  - \mathcal{E}_{\Lambda} {\vd}_h, \lambda_h \rangle_\Gamma &&
+\\
+\nonumber
+&\qquad= (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda),|\D|}
+\quad && \forall v_h \in X_{h,0}^k(\Omega), \ {\vd}_h \in X_{h,0}^k(\Lambda)
+\\
+&   \langle \trace u_h - \mathcal{E}_{\Lambda} {\ud}_h , \mu_h \rangle_\Gamma = 0
+\quad && \forall \mu_h \in Q_h\,,
+\end{align}
+\end{subequations}
+The space $Q_h$ must be suitably chosen such that \eqref{eq:infsup_discrete} holds.
+Let $Q_h$ be the trace space of $X_{h,0}^k(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$.
+As a result, $Q_h=X_{h,0}^k(\Gamma) \subset H^\frac12_{00}(\Gamma)$.
+Therefore we impose homogeneous Dirichlet boundary condition on $\partial \Omega$ also for the Lagrange multiplier.
+For this choice of $Q_h$ we prove the well-posedness of the discrete problem, as shown in the following.
+
+\begin{lemma}\label{lemma:prob1_orthproj}
+Let $P_h: H^{\frac 12}_{00}(\Gamma) \rightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Gamma)$ by
+\begin{equation*}
+(P_h v , \psi_h)_\Gamma= (v, \psi_h)_\Gamma \qquad \forall \psi_h \in Q_h.  
+\end{equation*} 
+Then, $P_h$ is continuous on $H^{\frac 12}_{00}(\Gamma)$, namely
+\begin{equation}\label{continuity_projoper}
+\|P_h v\|_{H^{\frac 12}_{00}(\Gamma)} \leq C \|v\|_{H^{\frac 12}_{00}(\Gamma)},
+\end{equation}
+where $C$ is a positive constant independent of $h$.
+\end{lemma}
+\begin{proof}
+We prove that $P_h$ is continuous on $L^2(\Gamma)$ and on $H^1_0(\Gamma)$ following \cite[Section 1.6.3]{MR2050138}.
+Then, the inequality \eqref{continuity_projoper} can be derived by interpolation between spaces, since $H^\frac12_{00}(\Gamma)$ can be seen as the interpolation space between $L^2(\Gamma)$ and $H^1_0(\Gamma)$.
+For the $L^2$-continuity, we exploit the fact that, from the definition of $P_h$, $(v-P_h v,P_h v)_{\Gamma}=0$.
+Therefore, by Pythagoras identity,
+\begin{equation*}
+\|v\|^2_{L^2(\Gamma)} = \|v-P_h v\|_{L^2(\Gamma)}^2 + \|P_h v\|_{L^2(\Gamma)}^2 \geq \|P_h v\|^2 _{L^2(\Gamma)}.
+\end{equation*}
+Let us now consider $v\in H^1_0(\Gamma)$.The Scott-Zhang interpolation operator $SZ_h$ from $H^1_0(\Gamma)$ to $Q_h$ satisfies the following inequalities,
+\begin{align}
+\label{SZ_stability}
+\|SZ_h v\|_{H^1(\Gamma)} &\leq C_1 \|v\|_{H^1(\Gamma)}
+\\
+\label{SZ_approx}
+\|v -SZ_h v \|_{L^2(\Gamma)} &\leq C_2 h \|v\|_{H^1(\Gamma)}.
+\end{align}
+Therefore, using \eqref{SZ_stability},
+\begin{equation*}
+\begin{split}
+\|\nabla P_h v\|_{L^2(\Gamma)} 
+&\leq \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + \|\nabla SZ_h v\|_{L^2(\Gamma)}\\
+&\leq  \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
+\end{split}
+\end{equation*}
+and by using the inverse inequality we obtain
+\begin{equation*}
+\begin{split}
+\|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
+&\leq \frac{C_3}{h} \|P_h v - SZ_h v\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
+&= \frac{C_3}{h} \|P_h (v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
+&\leq  \text{ (Stability of $P_h$ in $L^2$) } \frac{C_3}{h} \|v - SZ_h v\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
+&\leq \text{ (using \eqref{SZ_approx}) } \frac{C_3}{h} C_2 h  \| v\|_{H^1(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
+&\leq (C_2 C_3 +C_1) \|v\|_{H^1(\Gamma)},
+\end{split}
+\end{equation*}
+from which we obtain the continuity in $H^1_0(\Gamma)$.
+\end{proof}
+\begin{lemma}\label{lemma:trspace_infsup} 
+There exists a constant $\gamma >0$ such that for any $\mu_h\in Q_h$
+\begin{equation*}
+\sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , \mu_h \rangle}{ \|q_h\|_{H^{\frac 12}_{00}(\Gamma)}} \geq \gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)}.
+\end{equation*} 
+\end{lemma}
+\begin{proof}
+Let $\mu_h$ be in $Q_h$. From the continuous case, in particular from \eqref{infsup_traceop}, we have
+\begin{equation*}
+\|\mathcal{H}_\Omega\|^{-1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{\|v\|_{H^1(\Omega)}} 
+\end{equation*}
+and by the trace inequality $\|\trace v\|_{H^\frac 12 (\Gamma)} \leq C_T \|v\|_{H^1(\Omega)}$ (see \cite[7.56]{adams1975pure}), we obtain 
+\begin{equation*}
+\sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{\|v\|_{H^1(\Omega)}}
+\leq C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{ \|\trace v\|_{H^{\frac 12}_{00}(\Gamma)}}.
+\end{equation*}
+By the definition of $P_h$ and \eqref{continuity_projoper} 
+\begin{multline*}
+C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{ \|\trace v\|_{H^{\frac 12}_{00}(\Gamma)}}= C_T \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(\trace v) , \mu_h \rangle}{ \|\trace v\|_{H^{\frac 12}_{00}(\Gamma)}}
+\\
+\leq  C_T C \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(\trace v) , \mu_h \rangle}{ \|P_h(\trace v)\|_{H^{\frac 12}_{00}(\Gamma)}}
+= C_T C \sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , \mu_h \rangle}{  \|q_h\|_{H^{\frac 12}_{00}(\Gamma)}}.
+\end{multline*}
+\end{proof}
+
+\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds true, namely 
+$\exists \beta_{h,1} >0$ s.t.
+\begin{equation}\label{inf_sup_discrete_prob1}
+\inf_{\mu_h \in Q_h} 
+\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)}} \frac{ \langle \trace v_h - \ext {\vd}_h, \mu_h \rangle _{\Gamma}} {\vertiii{[v_h, {\vd} _h]} \|\mu_h\|_{H^{-\frac 12 }(\Gamma)}}
+\geq \beta_{h,1}. 
+\end{equation}
+\end{theorem}
+
+\begin{proof}
+Let $\mu_h \in Q_h$. As in the continuos case, we choose ${\vd}_h =0$ and we have
+\begin{equation*}
+\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)}} \frac{ \langle \trace v_h - \ext {\vd}_h, \mu_h \rangle _{\Gamma}} {\vertiii{[v_h,  {\vd}_h]}}
+\geq \sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \trace v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}}.
+\end{equation*}
+
+Therefore, we want to prove that there exists $\beta_{h,1}$ such that
+\begin{equation*}
+\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \trace v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}} \geq \beta_{h,1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \qquad \forall \mu_h \in Q_h.
+\end{equation*}
+
+Using Lemma \ref{lemma:trspace_infsup} and the boundedness of the harmonic extension operator $\mathcal{H}_\Omega$ from $H^{\frac 12}_{00}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
+\begin{equation*}
+\gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq  \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|q_h\|_{H^{\frac 12}_{00}(\Gamma)}} 
+\leq 
+\|\mathcal{H}_\Omega\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{H}_\Omega q_h\|_{H^1(\Omega)}} .
+\end{equation*}
+Let $R_h: H^1_0(\Omega) \rightarrow X_{h,0}^k(\Omega)$ be a quasi interpolation operator (such as the Scott-Zhang operator) satisfying 
+\begin{equation*}
+\|R_h v\|_{H^1(\Omega)} \leq C_R \|v\|_{H^1(\Omega)} \qquad \forall v \in H^1_0(\Omega).
+\end{equation*}
+Therefore, we obtain 
+\begin{equation*}
+\|\mathcal{H}_\Omega\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|\mathcal{H}_\Omega q_h\|_{H^1(\Omega)}} 
+\leq
+\|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|R_h \mathcal{H}_{\Omega} q_h\|_{H^1(\Omega)}}
+\end{equation*}
+and we have
+\begin{multline}\label{eq_conformity}
+\gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)} 
+\leq 
+\sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|q_h\|_{H^{\frac 12}_{00}(\Gamma)}} 
+\leq
+\|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{H}_{\Omega} q_h\|_{H^1(\Gamma)}}
+\\
+=
+\|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle \trace R_h  \mathcal{H}_{\Omega}q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{H}_{\Omega} q_h\|_{H^1(\Omega)}} 
+\leq \|\mathcal{H}_{\Omega}\| C_R \sup_{v_h \in X_{h,k}(\Omega)} \frac{ \langle \trace v_h, \mu_h \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
+\end{multline}
+Therefore the inf-sup condition $\eqref{inf_sup_discrete_prob1}$ holds with $\beta_{h,1} = \gamma \|\mathcal{H}_{\Omega}\|^{-1} C_R^{-1} $.
+We notice that in \eqref{eq_conformity} we exploit the fact that the operator $\trace R_h  \mathcal{H}_{\Omega}$ coincides with the identity on the space $Q_h$, thanks to the conformity of $\mathcal{T}^{\Omega}_h$ to the interface $\Gamma$.
+\end{proof}
+
+%\begin{remark} We notice that to prove the result in Lemma \ref{lemma:trspace_infsup} (and then the discrete inf-sup condition)  basically we need a projection operator $P_h: H^{\frac 12}_{00} \longrightarrow W_{h,0}^k(\Gamma)$ orthogonal in the multiplier space $Q_h$, namely such that $\langle P_h v, \mu_h \rangle = \langle v, \mu_h \rangle, \, \forall \mu_h \in Q_h$, and continuous in $H^{\frac 12}(\Gamma)$.
+Therefore, in principle different choices than $Q_h=W_{h,0}^k(\Gamma)$ could be considered if we can build an operator $P_h$ satisfying these properties.
+In \cite{belgacem1999mortar} such operator $P_h$  is built for a particular choice of $Q_h$ but it is not clear how to prove the $H^1$-stability inequality (and consequently the $H^{\frac 12 }$-stability) with a constant independent of the mesh size $h$.
+%\end{remark}
+
+\subsubsection{Problem 3D-1D-1D}
+We aim to find  $u_h \in X_{h,0}^k(\Omega) ,\ {\ud}_h \in X_{h,0}^k(\Lambda), \ {\ld}_h \in Q_h \subset H^{-\frac12}(\Lambda)$, such that
+\begin{subequations}
+\begin{align}\label{eq:prob2_discrete}
+&(u_h,v_h)_{H^1(\Omega)} + ({\ud}_h,{\vd}_h)_{H^1(\Lambda), |{\cal D}|} 
++  \langle  \mtrace v_h -  {\vd}_h, {\ld}_h \rangle_{\Lambda, |\DD|} 
+\\
+\nonumber
+&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda), |{\cal D}|}
+\quad \forall v_h \in X_h(\Omega), \ {\vd}_h \in X_h(\Lambda)
+\\
+&  \langle \mtrace u_h - {\ud}_h, {\md}_h \rangle_{\Lambda,| \DD| } = 0
+\quad \forall {\md}_h \in Q_h\,.
+\end{align}
+\end{subequations}
+
+%We introduce the space
+%$W_{h,0}^k(\Lambda) \subset H^{\frac 12} _{00} (\Lambda)$, which is the averaged trace space of functions running in $X_{h,0}^k(\Omega)$.
+It coincides with the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$ and satisfying homogeneous Dirichlet boundary condition, namely $X_{h,0}^k(\Lambda)$.
+We choose $Q_h=X_{h,0}^k(\Lambda)$, therefore we impose homogeneous Dirichlet boundary condition on $\Lambda \cap \partial \Omega$ also for the Lagrange multiplier.
+With this choice for $Q_h$, we can prove the well-posedness of the discrete problem.
+In particular, following the same steps as for Problem 1, we can prove the following results.
+
+\begin{lemma}\label{lemma:prob2_orthproj}
+Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
+\begin{equation*}
+(P_h v , \psi)_{\Lambda,|\DD|}= (v, \psi)_{\Lambda , |\DD|} \qquad \forall \psi \in Q_h.  
+\end{equation*} 
+Then, $P_h$ is continuous on $H^{\frac 12}_{00}(\Lambda)$, namely
+\begin{equation*}
+\|P_h v\|_{H^{\frac 12}_{00}(\Lambda),|\DD|} \leq C \|v\|_{H^{\frac 12}_{00}(\Lambda),|\DD|},
+\end{equation*}
+where $C$ is a positive constant independent of $h$.
+\end{lemma}
+
+\begin{lemma}\label{infsup_avr_trspace}
+There exist a constant $\gamma >0$ such that
+\begin{equation*}
+\sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , {\md}_h \rangle_{\Lambda, |\DD|}}{ \|q_h\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}} \geq \gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall {\md}_h \in Q_h.
+\end{equation*} 
+\end{lemma}
+
+The proofs follow the ones of Lemmas \ref{lemma:prob1_orthproj} and \ref{lemma:trspace_infsup} with the only difference that the arguments are applied to $\Lambda$ instead of $\Gamma$.
+
+\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds, namely 
+$\exists \beta_{h,2} >0$ s.t.
+\begin{equation}
+\inf_{\mu_h \in Q_h} 
+\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)} }\frac{\langle \mtrace v_h -  {\vd}_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\vertiii{[v_h, {\vd}_h]} \|{\md}_h\|_{H^{-\frac 12 }(\Lambda)} }
+\geq \beta_{h,2}. 
+\end{equation}
+\end{theorem}
+\begin{proof}
+ Again, we choose ${\vd}_h =0$, so that the proof reduces to show that there exists $\beta_{h,2}$ such that
+\begin{equation*}
+\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \mtrace v_h , {\md}_h \rangle _{\Lambda,|\DD|} } {\|v_h\|_{H^1(\Omega)} }\geq \beta_{h,2} \|{\md}_h\|_{H^{-\frac 12}(\Lambda)}\ \qquad \forall {\md}_h \in Q_h.
+\end{equation*}
+From Lemma \ref{lemma:H12norm} and its corollaries, for any $w \in H^{\frac 12}(\Lambda) \ 
+\|\ext w\|_{H^{\frac 12}_{00}(\Gamma)}= \|w\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}$.
+
+Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{H}_{\Omega}$ from $H^{\frac 12}_{00}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
+\begin{multline}
+\gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \leq 
+\sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}} 
+%
+=  \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda,|\DD|}} {\|\ext q_h\|_{H^{\frac 12}_{00}(\Gamma)}} 
+\leq \|\mathcal{H}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\|\mathcal{H}_{\Omega} \ext q_h\|_{H^1(\Omega)}} 
+\\
+\leq \|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\|R_h \mathcal{H}_{\Omega} \ext q_h\|_{H^1(\Omega)}}
+%
+=  \|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle 	\mtrace R_h \mathcal{H}_{\Omega} \ext q_h, {\md}_h \rangle _{\Lambda,|\DD|}} {\|R_h \mathcal{H}_{\Omega} \ext w_h\|_{H^1(\Omega)}}
+\\
+\leq \|\mathcal{H}_{\Omega}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \mtrace v_h, {\md}_h \rangle _{\Lambda,|\DD|}} {\|v_h\|_{H^1(\Omega)}}. 
+\end{multline}
+Also in this case to prove the disrete inf-sup condition we exploit the conformity of the meshes on $\Omega$, $\Gamma$ and $\Lambda$ and the fact that the operator $\mtrace R_h \mathcal{H}_{\Omega} \ext$ coincides with the identity if applied to functions in $Q_h$.
+\end{proof}
+
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\def\patch{\omega _j}
+\subsection{$\mathcal{T}^{\Omega}_\mathbb{H}$ non conforming to $\Gamma$ and $\Lambda$} \label{sec:unfit2}
+We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_\mathcal{h}$,
+$\mathcal{T}^{\Omega}_\mathfrak{H}$,
+$\mathcal{T}^{\Omega}_\mathbf{H}$
+$\mathcal{T}^{\Omega}_\mathfrak{h}$do not conform with the surface $\Gamma$ nor with $\Lambda$. In this case, the 3D-1D-1D
+formulation, namely Problem 3D-1D-1D, is more suitable. 
+%{\color{red} Add more details, we can refer also to cutFEM (Burman, Massing etc.) explaining the limitation of that approach (network case for example).}\\
+Therefore we focus on the analysis of this discretization approach for Problem 2 solely.
+
+\subsubsection{Problem 3D-1D-1D} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X_h = X_{h,0}^1(\Omega) \times X_{h^\prime,0}^1(\Lambda)$.
+With little abuse of notation, we assume that the characteristic mesh size of the 3D mesh $\mathcal{T}^{\Omega}_h$ and the one of the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different.
+Concerning the multiplier space, let $\mathcal{G}_h = \{K \in \mathcal{T}^{\Omega}_h: \, K\cap \Lambda \neq \emptyset\}$, be the set of the 3D elements that intersect $\Lambda$.
+Then we define $Q_h=\{{\ld}_h : {\ld}_h \in P^0(K) \, \forall K \in \mathcal{G}_h\}$.
+We notice that the multiplier functions are defined on the 3D elements.
+With little abuse of notation, we denote with $Q_h$ also the restriction to $\Lambda$ of the space of piecewise constant functions defined in 3D.
+As a result, we have $Q_h \subset L^2(\Lambda) \subset H^{-\frac12}(\Lambda)$.
+With this choice of multipliers the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s({\ld}_h, {\md}_h): \ Q_h \times Q_h \rightarrow \mathbb{R}$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}.
+The objective of this section is to analyze the stabilized version of the 3D-1D-1D problem: find $[u_h, {\ud}_h] \in X_h$ and ${\ld}_h \in Q_h$ such that
+\begin{multline}\label{eq:prob2_stabilized}
+a([u_h, {\ud}_{\mathfrak{h}}], [v_h, {\vd}_h]) +
+b([v_h, {\vd}_h], {\ld}_h)
++ b([u_h, {\ud}_h], {\md}_h)
+- s({\ld}_h, {\md}_h) 
+= c(v_h) + d({\md}_h)\\
+  \quad \forall [v_h, {\vd}_h] \in X_h, \,
+  \forall {\md}_h \in Q_h\,.
+\end{multline}
+The idea of the stabilization strategy proposed in \cite{burman2014}
+is to identify a new multiplier space $Q_H$, which is never implemented in practice, such that inf-sup stability with $X_h$ holds true.
+Then, the stabilization operator is designed to control the distance between $Q_h$ and $Q_H$ trough the following inequality
+\begin{equation*}
+    \|{\md}_h - \pi_H {\md}_h\|_{Q_H} \leq C s_h({\md}_h, {\md}_h)\,,
+\end{equation*}
+being $\pi_H$ a suitable projection operator $Q_h \rightarrow Q_H$.
+Applying the results obtained in \cite{burman2014} we will show that the well posedness of problem \eqref{eq:prob2_stabilized} is governed by the following lemma.
+\begin{lemma}[Lemma 2.3 of \cite{burman2014}]\label{lemma23burman}
+\begin{enumerate}
+    \item If the $b(\cdot,\cdot),\, X_h,Q_H \rightarrow \R$ is inf-sup stable.
+    \item If the stabilization operator $s_h(\cdot,\cdot),\, Q_H,Q_H \rightarrow \R$ is such that
+    \begin{equation*}
+        \beta \|{\md}_h\|_{H^{-\frac12}(\Lambda)} \leq \sup\limits_{v_h \in X_h} \frac{b(v_h,{\md}_h}{\vertiii{v_h})} + s_h({\md}_h, {\md}_h), \quad \forall {\md}_h \in Q_h\,.
+    \end{equation*}
+    \item If for any $[v_h, {\vd}_h]$ there exists a function $\xi_h\in Q_h$ depending on $[v_h, {\vd}_h]$, namely $\xi_h=\xi_h([v_h, {\vd}_h])$, s.t.
+\begin{gather}
+\label{stab_coercivity}
+a([v_h, {\vd}_h],[v_h, {\vd}_h] ) + b([v_h, {\vd}_h], \xi_h) \geq \alpha_\xi \vertiii{[v_h, {\vd}_h]}_{X_h}\,,
+\\
+\label{stab_stability}
+(s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[v_h, {\vd}_h]}_{X_h}\,,
+\end{gather}
+being $\vertiii{[\cdot \, ,\, \cdot] }_{X_h}$ a suitable discrete norm. 
+\end{enumerate}
+Then, problem \eqref{eq:prob2_stabilized} admits a unique solution.
+\end{lemma}
+For the proof of this result we remind the reader to Lemma 2.3 of \cite{burman2014}.
+In the remainder of this section we show how to find a multiplier space $Q_H$ and a stabilization operator $s_h$ such that all the assumptions of lemma \ref{lemma23burman} are satisfied.
+
+% The stabilization operator is based on a new multiplier space $Q_H$, for which the discrete inf-sup condition is fulfilled, and a projection operator $\pi_H: Q_h \rightarrow Q_H$ such that for any $[v, \vd] \in X $
+% \begin{equation}\label{condition_pi_L}
+% b([v, \vd], {\ld}_h - \pi_H {\ld}_h) \leq C \vertiii{[v,\vd]}\|{\ld}_h - \pi_H {\ld}_h\|_{Q_H},
+% \end{equation}
+% where for $X$ and $\vertiii{[\cdot, \cdot]}$ we use the definitions of section $3.2$ and $\|\cdot \|_{Q_H}$ denotes a suitable discrete norm on $Q_H$.
+Then, the following relaxed form of the inf-sup condition is satisfied,
+% \begin{lemma}\cite[Lemma2.1]{burman2014}\label{lemma_burman2014}
+% If the multiplier space $Q_H$ is inf-sup stable and the operator $\pi_H: Q_h \rightarrow Q_H$ satisfies \eqref{condition_pi_L}, then for any ${\ld}_h \in Q_h$ it holds,
+% \begin{equation*}
+% \|{\ld}_h\|_{H^{-\frac 12}(\Lambda)} \lesssim \sup_{\substack{v_h \in X_{h,0}^1(\Omega)\\ {\vd}_h \in X_{h^\prime,0}^1(\Lambda)}} \frac{b([v_h, {\vd}_h], {\ld}_h)}{\vertiii{[v_h, {\vd}_h]}} + \|{\ld}_h - \pi_H {\ld}_h\|_{Q_H}.
+% \end{equation*}
+% \end{lemma}
+%  Based on this projection operator, we build the stabilization term $s({\ld}_h, {\md}_h)$ satisfying
+%  \begin{equation}\label{condition_pi_L_bis}
+%  \|{\ld}_h- \pi_H {\ld}_h\|_{Q_H} C \leq s({\ld}_h, {\ld}_h)
+% \end{equation} and prove that for any $[u_h, {\ud}_h]$ there exists a function $\xi_h\in Q_h$ depending on $[u_h, {\ud}_h]$, namely $\xi_h=\xi_h([u_h, {\ud}_h])$, s.t.
+% \begin{equation}\label{stab_coercivity}
+% a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) },
+% \end{equation}
+% \begin{equation}\label{stab_stability}
+% (s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) },
+% \end{equation}
+% being $\vertiii{[\cdot \, ,\, \cdot] }_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) }$ a suitable discrete norm.
+
+The first step consists of showing
+that there exists a discrete space $Q_H$ that satisfies the first assumption of \ref{lemma23burman}. 
+We recall that in the case of Problem 2, 
+\begin{equation*}
+b([u_h, {\vd}_h], {\md}_h) = \left(\mtrace v_h - {\vd}_h, {\md}_h\right)_{\Lambda,|\DD|}.
+\end{equation*}
+The construction of the inf-sup stable space $Q_H$ is based on macro elements of diameter $H$, where $H$ is sufficiently large.
+In particular, we assume that there exists positive constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$, being $h$ the mesh characteristic size of $\mathcal{T}_h^\Omega$.
+The space is constructed assembling the 3D elements of $\mathcal{G}_h$ into macro patches $ \patch $ such that $H \leq |\patch\cap \Lambda|\leq cH$, with $c\geq 1$.
+Let $M_j$ be the number of elements of the patch $\omega_j$, namely, $\patch=\cup _{i=0}^{M_j} K_i$, where $K_i \in \mathcal{G}_h$, $M_j$ is uniformly bounded in $j$ by some $M\in \mathbb{N}$ and $H=\min_{j}|\patch\cap \Lambda|$.
+We assume that the interiors of the patches $\patch$ are  disjoint.
+We define
+\begin{equation*}
+Q_H=\left\{{\md }_H: \, {\md }_H\in P^0(\patch)\, \forall j \right\}.
+\end{equation*}
+As previously pointed out for $Q_h$, we denote with $Q_H$ also the restriction of the multiplier space to $\Lambda$, namely say $Q_H \subset L^2(\Lambda) \subset H^{-\frac12}(\Lambda)$.
+
+%figure extended patch
+\begin{figure}\label{fig:patch}
+\center
+\input{./graphics/ext_patch}
+\caption{Extended patches $\omega_j$.}
+\end{figure}
+
+Moreover, we associate to each patch $\patch$ a shape-regular extended patch, still denoted by $\omega_j$ for notational simplicity, which is built adding to $\patch$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$ and we assume that the interiors of the new extended patches $\omega _j$ are still disjoint (see Figure \ref{fig:patch}).
+Here we are using the classical definition of shape-regularity, see for example \cite{MR2050138}, namely there exist a constant $C>0$ such that for any $\omega_j$, $\frac{\tilde{\rho}_j}{\bar{\rho}_j}\leq C$, being $\tilde{\rho}_j$ the diameter of $\omega_j$ and $\bar{\rho}_j$ the diameter of the largest ball that can be inscribed in $\omega_j$.
+The extended patches $\omega _j$ are built such that they fulfill the conditions meas$(\patch)=\mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda}\cap \omega_j)=\mathcal{O}(H)$, where $\Gamma_{\patch\cap \Lambda}$ is the portion of $\Gamma$ with centerline $\patch\cap \Lambda$.
+The latter assumption is required to ensure that the intersection of $\Gamma_{\patch\cap \Lambda}$ and $\omega_j$ is not too small and it will be needed later on to prove the inf-sup stability of the space $Q_H$ in Lemma \ref{lemma:Lh_infsup}.
+A representation of this construction in the simple case in which $\omega _j$ is composed just by one tetrahedron is shown in Figure \ref{fig:gamma_generated}.
+
+% As shown in \cite[Section III]{burman2014}, we can always choose $\pi_H$ as the $L_2$ orthogonal projection operator from $\Lambda_h$ to $Q_H$ in order to satisfy \eqref{condition_pi_L} and then in practice replace it with any interpolation $\tilde{\pi}_L$ of $\Lambda_h$ in $Q_H$.
+In particular, for any $\lambda_h \in \Lambda_h$ we define,
+% \begin{equation*}
+% \tilde{\pi}_L {\ld}_{ _{|\patch}} = M_j^{-1} \sum_{\substack{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset}} {\ld}_{|K_i} \qquad \text{for all $\omega_j$,} 
+% \end{equation*}
+% being $M_j$ the cardinality of the set $\{i: \ K_i \in \mathcal{G}_h, \  K_i \cap \omega_j \neq \emptyset\}$. These choices lead to the following stabilization 
+% \begin{equation}\label{eq:stab}
+% s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
+% \end{equation}
+% being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{G}_h$.
+
+\begin{figure}\label{fig:gamma_generated}
+\centering
+\subfigure[$\Gamma_{\omega_j \cap \Lambda}$]
+{
+\input{./graphics/gamma_generated}
+}
+\qquad \qquad
+\subfigure[ $\Gamma_{\omega_j \cap \Lambda} \cap \omega_j$]{
+\input{./graphics/intersection}
+}
+\caption{$\Gamma_{\omega_j \cap \Lambda}$, the portion of $\Gamma$ generated by $\omega_j \cap \Lambda$ in (a) and the intersection between $\Gamma_{\omega_j \cap \Lambda}$ and $\omega_j$ in (b).
+Here for simplicity $\omega_j$ is represented as a single tetrahedron but actually it is a collection of tetrahedra as shown in Figure \ref{fig:patch}.}
+\end{figure}
+
+Thanks to the shape regularity of these extended patches, we have that the following discrete trace inequality holds true for any function $v\in H^1(\omega_j)$, 
+\begin{equation}\label{discr_trace_ineq}
+\|\trace v\|_{L^2(\Gamma\cap \omega_j)} \lesssim H^{-\frac 12} \|v\|_{L^2(\omega_j)}
+\end{equation}
+Moreover $\forall u_h \in X^1_{h,0}(\Omega)$ we have the following average inequality, which is a consequence of the definition of $\mtrace$ and Jensen inequality,
+\begin{multline}\label{eq:avrg_ineq}
+\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| }
+= \sum _j\int_{\patch \cap \Lambda} |\DD| \mtrace u_h^2 
+= \int_{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \trace u_h \right)^2
+\leq \int_{\Lambda} \int_{\DD} (\trace u_h)^2
+\\
+= \int_{\Gamma} (\trace u_h)^2
+= \sum _j \int_{\patch \cap \Gamma} (\trace u_h)^2
+= \sum _j \|\trace u_h\|^2_{L^2(\patch \cap \Gamma)}.
+\end{multline}
+
+We are now ready to prove that the space $Q_H$ is inf-sup stable. 
+\begin{lemma}\label{lemma:Lh_infsup}
+The space $Q_H$ is inf-sup stable, namely $\forall {\md}_H \in Q_H$, $\exists \beta >0$ s.t.
+\begin{equation*}
+\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\md} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|{\md}_H\|_{H^{-\frac 12}(\Lambda)}.
+\end{equation*} 
+\end{lemma}
+
+\begin{proof}
+As in the continuous case, we can choose ${\vd}_h=0$ and we prove that
+\begin{equation*} 
+\sup_{v_h \in X_{h,0}^1(\Omega)} \frac{\left(\mtrace v_h ,{\md}_H\right)_{\Lambda, |\DD|}}{\|v_h\|_{H^1(\Omega)}} \geq \beta \|{\md}_H\|_{H^{-\frac 12}(\Lambda)}.
+\end{equation*} 
+Proving the last inequality it is equivalent to find the Fortin operator $\pi_F: H^1_0(\Omega) \rightarrow X_{h,0}^1(\Omega)$, such that 
+\begin{gather}
+\left(\mtrace v - \mtrace \pi _F v  , {\md}_H\right)_{\Lambda, |\DD|}=0, \quad \forall v\in H^1_0(\Omega), \, {\md}_H \in Q_H\,,
+\\
+\label{eq:cont_Fortin}
+\|\pi_F v\|_{H^1(\Omega)}\lesssim \|v\|_{H^1(\Omega)}\,.
+\end{gather}
+
+We define
+\begin{equation*}
+\pi_F v = I_h v + \sum _j \alpha _j \varphi _j \qquad \text{with }\alpha_j =\frac{\int_{\patch \cap \Lambda}|\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch \cap \Lambda}|\DD|\mtrace \varphi _j}
+\end{equation*}
+where $I_h: H^1(\Omega) \rightarrow X_{h,0}^1$ denotes an $H^1(\Omega)$-stable interpolant
+and $\varphi_j \in X_{h,0}^1(\Omega)$ is such that supp$(\varphi_j)\subset \omega_j$, supp$(\trace \varphi _j) \subset \Gamma_{\patch\cap \Lambda}\cap \omega_j$, $\varphi_j =0$ on $\partial \omega _j$ and
+\begin{equation}\label{phi_properties}
+\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j=\mathcal{O}(H) \text{ and } \|\nabla \varphi _j\|_{L^2(\omega _j)}=\mathcal{O}(1). 
+\end{equation}
+We notice that supp$(\trace \varphi_j) \subset \Gamma_{\patch\cap \Lambda}\cap \omega_j$ ensures that $\mtrace \varphi_j \subset \omega_j\cap \Lambda$.
+Therefore, since for construction the interiors of $\omega_j\cap \Lambda$  are disjoint and $\varphi _j = 0 $ on $\partial \omega_j$,  the functions $\mtrace \varphi_j\, \forall j$ have all disjoint supports.
+This construction is always possible since meas$(\patch) = \mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda} \cap \omega_j)=\mathcal{O}(H)$, provided $H$ is sufficiently larger that $h$.
+Indeed, this guarantees that the functions $\varphi _j$ and their traces $\trace \varphi _j$ have a sufficiently large support so that they can be built in order to satisfy \eqref{phi_properties}.
+Then we have
+\begin{multline*}
+\left(\mtrace v - \mtrace \pi _F v  , {\md}_H\right)_{\Lambda, |\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD |\left[ \mtrace v-\mtrace I_h v-\sum _i \alpha_i \mtrace \varphi _i \right]{\md}_H \\
+(\text{supp} (\mtrace \varphi _i )\subset \omega _i\cap \Lambda \, \forall i)  =\sum _j \int_{\patch\cap \Lambda}|\DD| \left[ \mtrace v-\mtrace I_h v-\alpha_j \mtrace \varphi _j \right]{\md}_H\\
+=\sum _j \int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\md}_H - \frac{\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi _j} \int_{\patch\cap \Lambda} |\DD|\mtrace \varphi _j{\md}_H\\
+(\text{using ${\md}_H$ constant on $\patch\cap \Lambda$})=0.
+\end{multline*}
+Concerning the continuity of $\pi_F$, we exploit the assumptions that the interiors of $\patch$ are disjoint and supp$(\varphi _j) \subset \patch$ and we have
+\begin{multline*}
+\|\nabla \pi_F v \|_{L^2(\Omega)} \leq \|\nabla I_h v\|_{L^2(\Omega)} + \left(\sum_j\alpha_j^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\right)^{\frac 12}\\
+(\text{stability of }I_h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \left(\sum_j\alpha_j^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\right)^{\frac 12}
+\end{multline*}
+and for the second term 
+\begin{multline*}
+\sum_j \alpha_j ^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\leq
+\\
+\left(\text{using }\|\nabla \varphi _j\|_{{L^2(\omega_j)}}=\mathcal{O}(1)\right) \lesssim  \sum_j \frac{\left(\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)\right)^2}{\left(\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j \right)^2}
+\\
+\left(\text{since }\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j=O(H)\right) \lesssim \frac {1}{H^2} \sum_j \left(\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_hv)\right)^2
+\\
+(\text{Jensen}) \lesssim  \frac {1}{H^2} \sum_j |\patch\cap \Lambda| \int_{\patch\cap \Lambda} |\DD|^2(\mtrace v-\mtrace I_h v)^2
+\\
+(\text{being }|\patch\cap \Lambda| \leq cH)\lesssim  \frac {1}{H} \sum_j \| \mtrace (v-I_h v)\|^2_{L^2(\patch\cap \Lambda), |\DD|}
+\\
+(\text{average inequality \eqref{eq:avrg_ineq}} ) \lesssim  \frac {1}{H} \sum_j \| \trace(v-I_h v)\|^2_{L^2(\omega _j\cap \Gamma)}  
+\\
+\left(\text{trace inequality \eqref{discr_trace_ineq}} \right)\lesssim  \frac {1}{H^2} \sum_j  \| v-I_h v\|^2_{L^2(\omega_j)} \lesssim  \frac {1}{H^2}  \| v-I_h v\|^2_{L^2(\Omega)} 
+\\
+(\text{approximation properties of }I_h)\lesssim \|\nabla  v\|^2_{L^2(\Omega)}
+\end{multline*}
+and the continuity of $\pi_F$ follows.
+We notice that the constant in the inequality \eqref{eq:cont_Fortin} is independent of how $\Lambda$  is cut by the elements of the mesh $\mathcal{T}_h^{\Omega}$.
+\end{proof}
+
+For the second assumption of lemma \ref{lemma23burman}, we recall that the bilinear form $b(v_h,{\md}_h)$ is continuous in the norms $\vertiii{v_h},\,\|{\md}_h\|_{L^2(\Lambda)}$. 
+Using lemma \ref{lemma:Lh_infsup}, it is straightforward to prove that there exists a constant $\beta$ such that
+\begin{equation}\label{relax_infsup}
+\beta \|{\md}_h\|_{H^{-\frac12}(\Lambda)} \leq \sup\limits_{v_h \in X_h} \frac{b(v_h,{\md}_h)}{\vertiii{v_h}} + \|{\md}_h-\pi_H {\md}_h\|_{L^2(\Lambda)}, \quad \forall {\md}_h \in Q_h\,.
+\end{equation}
+We define $\pi_H = \sum_j \pi_H^j$, where $\pi_H^j$ is the operator
+\begin{equation}\label{eq:projector}
+\pi_H^j w_{|\patch \cap \Lambda} =\frac{1}{|\Gamma_{\patch\cap \Lambda}|}\int_{\patch\cap \Lambda}|\DD| w\quad \forall j,
+\end{equation}   
+ Then, for any $w \in L^2(\Lambda)$ the following Poincarè inequality holds true, see for example \cite[Corollary B.65]{MR2050138},
+\begin{equation}\label{disc_poincare_ineq}
+\|w - \pi_H w\|_{L^2(\omega_j\cap\Lambda),|\DD|} \leq c_P H \|\partial_s w\|_{L^2(\omega_j\cap\Lambda),|\DD|}\,.
+\end{equation}
+We consider the following stabilization operator
+\begin{equation}\label{eq:stab}
+s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
+\end{equation}
+being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{G}_h$.
+Then, we use the result of \cite{burman2014}, Section III to show that
+\begin{equation*}
+    \|{\md}_h-\pi_H {\md}_h\|_{L^2(\Lambda)} \leq C s({\md}_h, {\md}_h)\,,
+\end{equation*}
+which combined with \eqref{relax_infsup} shows that the second assumption of lemma \ref{lemma23burman} holds true.
+
+The third step of the analysis consists of showing that \eqref{stab_coercivity} and \eqref{stab_stability} are satisfied. 
+We introduce the following discrete norms
+\begin{equation*}
+\|\, \lambda \,\|_{\pm \frac 12, h, \Lambda} = \|h^{\mp\frac 12} \lambda\|_{L^2(\Lambda)},
+\end{equation*}
+recalling that $h$ is the mesh size of $\mathcal{T}^\Omega_{h}$. We equip the space $X_h$ with the discrete norm
+\begin{equation*}
+\vertiii{[u_h, {\ud}_h]}^2_{X_h}
+= \|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|} + \|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|},
+\end{equation*}
+and the space $Q_H$ with the $L^2$ norm 
+$\|{\md}_H \|_{Q_H} = \|{\md}_H \|_{L^2(\Lambda)}$.
+
+Also, the function $\xi_h([v_h, {\vd}_h]) \in Q_H \subset Q_h \subset L^2(\Lambda)$ is defined as follows
+\begin{equation*}
+{\xi_h}_{|\patch\cap \Lambda}=\frac{\delta}{H} \pi_H(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}.
+\end{equation*}
+Then the following result holds true. 
+\begin{lemma}
+Given $\pi_H,\ s_h(\cdot,\cdot), \ \xi_h$ defined above, the inequalities \eqref{stab_coercivity} and \eqref{stab_stability} are satisfied.
+\end{lemma}
+\begin{proof} 
+Concerning the coercivity property \eqref{stab_coercivity}, we show that $\forall [u_h, {\ud}_h]$, there exists $\xi_h \in Q_h$ s.t.
+\begin{equation*}
+(u_h,u_h)_{H^1(\Omega)}+ ({\ud}_h, {\ud}_h)_{H^1(\Lambda), |\D|} +   (\mtrace u_h - {\ud}_h, \xi_h)_{\Lambda,|\DD|} \geq \alpha_{\xi}\vertiii{[u_h, {\ud}_h]}^2_{X_h}.
+\end{equation*}
+Using the definitions of $\pi_H$ and $\xi_h([u_h, {\ud}_h])$ previously presented and recalling that $\xi_h\in Q_H \subset Q_h$, we obtain
+\begin{multline*}
+\left( \mtrace u_h - {\ud}_h, \xi _h \right)_{\Lambda,|\DD|} 
+= \sum_j \int_{\patch\cap \Lambda} |\DD|(\mtrace u_h - {\ud}_h)\xi_h
+\\
+(\text{definition of $\xi_h$})= \frac{\delta}{H}\sum_j \pi_H^j( \mtrace u_h - {\ud}_h)\int_{\patch\cap \Lambda} |\DD|(\mtrace u_h - {\ud}_h)
+\\
+\left(|\Gamma_{\omega_j \cap \Lambda}| = \int_{\omega_j \cap \Lambda}|\DD|\right)= \frac{\delta}{H} \sum_j \int_{\patch\cap \Lambda}|\DD| (\pi_H( \mtrace u_h - {\ud}_h) )^2
+= \frac{\delta}{H}\sum_j \|\pi_H( \mtrace u_h - {\ud}_h)\|_{L^2(\patch\cap \Lambda),|\DD|}
+\\
+(\text{orthogonality of $\pi_H$}) = \frac{\delta}{H} \sum_j \left( \|\mtrace u_h - {\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} - \|(\pi_H-\mathcal{I})(\mtrace u_h - {\ud}_h)\|^2_{L^2(\patch\cap \Lambda),|\DD|} \right)
+\\ 
+\geq \frac{\delta}{H} \sum_j \left(
+\|\mtrace u_h-{\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|}
+- \|(\pi_H - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda), |\DD|}
+- \|(\pi_H - \mathcal{I}){\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} \right). 
+\end{multline*}
+For the second term we apply the additional assumption that the operators $\mtrace$ and $\partial_s$ commute. This is true if the cross section $\D$ does not depend on the arclength $s$.
+Then, we use the Poincar\'e inequality \eqref{disc_poincare_ineq}, the average inequality \eqref{eq:avrg_ineq} and the trace inequality \eqref{discr_trace_ineq} to show that,
+\begin{multline*}
+\sum _j  \|(\pi_H - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} 
+\leq C_P^2 H^2 \sum _j \|\partial_s \mtrace u_h\|_{L^2(\patch\cap \Lambda),|\DD|}^2
+= C_P^2 H^2 \sum _j \|\mtrace \partial_s  u_h\|_{L^2(\patch\cap \Lambda),|\DD|}^2
+\\
+\leq C H^2 \sum _j \|\trace \partial_s u_h\|_{L^2(\omega _j \cap \Gamma)}^2
+\leq C H \sum _j \|\nabla u_h\|_{L^2(\omega _j)}^2.
+\end{multline*}
+% old version, wrong
+% \begin{multline*}
+% \sum _j  \|(\pi_H - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} =\sum _j \int _{\patch \cap \Lambda} |\DD| (\pi_H \mtrace u_h- \mtrace u_h)^2
+% \\
+% (\text{Average inequality \eqref{eq:avrg_ineq}}) \leq \sum _j  \int_{\omega _j \cap \Gamma} (\ext \pi_H \mtrace u_h -\trace u_h)^2 
+% \\
+% (\text{trace inequality \eqref{discr_trace_ineq}}) \leq \sum _j  \frac 1H \int_{\omega_j}(\mathcal{E}_{\patch} \pi_H \mtrace u_h - u_h)^2 
+% \\ 
+% (\text{Poincare, see \cite[Corollary B.65]{MR2050138}})\leq \sum _j  H c_P ^2 \|\nabla u_h\|^2_{L^2(\omega _j)}.
+% \end{multline*}
+For the third term we proceed similarly,
+\begin{multline*}
+\sum _j \|(\pi_H - \mathcal{I}){\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} \leq C_P^2 H^2 \sum _j \|\partial_s {\ud}_h\|_{L^2(\patch\cap \Lambda),|\DD|}^2
+\\
+(\text{since $H$ is fixed, we can find a constant s.t. } H|\DD| \lesssim |\D|) C H \sum _j \|\partial_s {\ud}_h\|_{L^2(\patch\cap \Lambda),|\D|}^2.
+\end{multline*}
+%{\color{red} N.B. we are using a kind of weigthed Poincare inequality, check... I think it should work because I can do something like this
+%\begin{multline*}
+%\int_{\patch \cap \Lambda} |\DD| u^2 \leq 
+%max |\DD| \int_{\patch \cap \Lambda} u^2 \leq
+%max |\DD| \int_{\patch \cap \Lambda} (\nabla u)^2 =
+%\frac{max |\DD|}{min|\DD|} min|\DD| \int_{\patch \cap \Lambda} (\nabla u)^2 \leq\\
+%\frac{max |\DD|}{min|\DD|}  \int_{\patch \cap \Lambda} |\DD| (\nabla u)^2 
+%\end{multline*}
+%}\\
+Therefore, we obtain
+\begin{multline*}
+a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h([u_h, {\ud}_h]))
+\geq \\
+(1-\delta C) \|\nabla u_h\|^2_{L^2(\Omega)} + (1- \delta C) \|\partial_s {\ud}_h\|^2_{L^2(\Lambda), |\D|}
++\delta c_H  \|\mtrace u_h-{\ud}_h\|^2_{\frac 12,h,\Lambda, |\DD|}
+\end{multline*}
+and choosing $\delta=\frac{1}{2C}$ we obtain the desired inequality.\\
+Concerning inequality \eqref{stab_stability}, the proof is analogous to the one in \cite{burman2014}.
+\end{proof}
+
+% \begin{remark}
+% We notice that if we choose $Q_h=X_{h',0}^1(\Lambda)$, the constant in the inf-sup inequality  \eqref{eq:infsup_discrete} depends on the mesh size $h'$. Indeed,
+% \begin{multline}
+% \sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\md} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}}
+% \geq \sup_{\substack{{\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(- {\vd}_h, {\md} _H\right)_{\Lambda, |\DD|}}{\|{\vd}_h\|_{H^1(\Lambda)}}
+% \geq \frac{{\|\md} _H\|^2_{L^2(\Lambda)}}{\|{\vd}_h\|_{H^1(\Lambda)}} \\
+% ( \text{inverse inequality} )\geq \frac{{h'}^2}{c_I} \|{\md}_H\|_{L^2(\Lambda)}
+% \geq  \frac{{h'}^2}{c_I} \|{\md}_H\|_{H^{-\frac 12},(\Lambda)}
+% \end{multline}
+% being $c_I$ the constant in the inverse inequality
+% \begin{equation*}
+% \|{\md}_H\|_{H^1(\Lambda)} \leq \frac{c_I} {{h'}^2} \|{\md}_H\|_{L^2(\Lambda)}. 
+% \end{equation*}
+% \end{remark}
 
 %>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\section{A benchmark problem with analytical solution}
 
-\input{benchmark}
-%-----------------
+Let $\Omega=[0,1]^3$, $\Lambda=\{x=\tfrac{1}{2}\}\times \{y=\tfrac{1}{2}\} \times [0,1] $
+and $\Omega_{\ominus}=[\tfrac{1}{4}, \tfrac{3}{4}]\times [\tfrac{1}{4}, \tfrac{3}{4}]\times [0, 1]$.
+%Finally we let $\DD$ be the cross section of the virtual interface $\Gamma=\partial \Sigma$.
+As a benchmark for the two formulations we consider the following coupled problems
+%
+\begin{subequations}\label{benchmark}
+\begin{align}
+\label{benchm_3d}
+-\Delta u=f \quad &\text{in $\Omega$},\\
+\label{benchm_1d}
+-d_{zz}^2 \ud =g \quad &\text{on $\Lambda$},\\
+u=u_b \quad &\text{on $\partial \Omega$},
+\end{align}
+\end{subequations}
+where for formulation \eqref{eq:problem1} the mix-dimensional coupling constraint reads
+\begin{equation}
+  \label{eq:couple_1}
+\trace{u} - \ext{\ud} = q_1\quad\text{ on }\Gamma,
+\end{equation}
+while for \eqref{eq:problem2} we set
+\begin{equation}
+    \label{eq:couple_2}
+\avrc{u} - \ud = q_2\quad\text{ on }\Lambda.
+\end{equation}
+%
+In \eqref{benchmark}-\eqref{eq:couple_2} the right-hand sides shall be defined as 
+\begin{eqnarray*}
+  &f=8\pi ^2 \sin (2\pi x) \sin (2\pi y),\quad &g={\pi ^2}\sin \left({\pi z}\right),\quad u_b=\sin (2\pi x) \sin (2\pi y),\\
+  &q_1=\sin (2\pi x) \sin (2\pi y) - \sin \left({\pi z}\right),\quad &q_2=-\sin \left({\pi z}\right).
+\end{eqnarray*}
+
+The exact solution of \eqref{benchmark}, regardless of the coupling constraint,
+is given by
+%
+\begin{eqnarray}
+\label{benchm_sol3d}
+u=\sin (2\pi x) \sin (2\pi y),\\
+\label{benchm_sol1d}
+%\ud=1+\exp(-z).
+\ud=\sin \left({\pi z}\right).
+\end{eqnarray}
+%
+Let us notice that $\ud$ satisfies homogeneous Dirichlet conditions at the boundary of $\Lambda$.
+Moreover, the solution \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfies on $\Gamma$ the relation
+\begin{equation}\label{benchm_flux}
+L=\nabla u \cdot \textbf{n}_{\oplus}=d_z \ud n_{\oplus,z}=0,
+\end{equation}
+with $n_{\oplus,z}$ the $z-$component of the normal unit vector to $\Gamma$.
+
+We prove that \eqref{benchmark} is solution of \eqref{eq:problem2} in the
+simplified case in which the starting 3D-3D problem is
+\begin{subequations}\label{eq:dirneu_simple}
+\begin{align}
+- \Delta \up  &= f  && \text{ in } \Omega_{\oplus},\\
+- \Delta \uf &= g  && \text{ in } \Omega_{\ominus},\\
+-\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
+\uf - \up &= q_i  && \text{ on }  \Gamma,\\
+\up &= h && \text{ on } \partial \Omega.
+\end{align}
+\end{subequations}
+instead of \eqref{eq:dirneu}. Therefore the reduced problems in \eqref{eq:problem1} and
+\eqref{eq:problem2} become respectively
+%
+\begin{subequations}\label{eq:problem1_simple}
+\begin{align}
+\label{eq:problem1_simple_eq1}
+&(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
++ \langle \trace{v}  - \ext{\vd}, \lambda \rangle_\Gamma
+\\
+\nonumber
+&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
+\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
+\\
+\label{eq:problem1_simple_eq2}
+&   \langle \trace{u} - \ext{\ud} , \mu \rangle_\Gamma =  \langle q_1 , \mu \rangle_\Gamma
+\quad \forall \mu \in H^{-\frac12}(\Gamma)
+\end{align}
+\end{subequations}
+and
+\begin{subequations}\label{eq:problem2_simple}
+  \begin{align}
+    \label{eq:problem2_simple_eq1}
+&(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
++ |{\partial \cal D}| \langle \avrc{v} - \vd, \ld \rangle_{H^{-\frac12}(\Lambda)} 
+\\
+\nonumber
+&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g}, \vd)_{L^2(\Lambda)}
+\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
+\\
+\label{eq:problem2_simple_eq2}
+&  |\partial {\cal D}| \langle \avrc{u} -  \ud, \md \rangle_{H^{-\frac12}(\Lambda)} =
+|\partial {\cal D}| \langle \avrc{q_2}, \md \rangle_{H^{-\frac12}(\Lambda)}
+\quad \forall \md \in H^{-\frac12}(\Lambda)\,.
+\end{align}
+\end{subequations}
+
+Let us prove that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is the solution of
+\eqref{eq:problem2_simple}. Using the integration by part formula and homogeneous
+boundary conditions on $\Omega$ and $\Lambda$, from \eqref{eq:problem2_simple_eq1} we have
+\begin{align*}
+&-(\Delta u, v)_{L^2(\Omega)} - |{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)} 
++ |{\cal D}|\langle \avrc{v}  - \vd, \ld \rangle_\Lambda
+\\
+\nonumber
+&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
+\quad \forall v \in H^1_0(\Omega), \vd \in H^1(\Lambda).
+\\
+\end{align*}
+Since $\ld=\avrc{L}=0$ and \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d}
+satisfies \eqref{benchm_1d}, we have that
+\begin{align*}
+-(\Delta u, v)_{L^2(\Omega)} =  (f,v)_{L^2(\Omega)}, \\
+-|{\partial \cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)},
+\end{align*}
+Thus \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfy \eqref{eq:problem2_simple_eq1}.
+The fact that the solution satisfy \eqref{eq:problem2_simple_eq2} follows from \eqref{eq:couple_2}.
+
+We can prove in a similar way that \eqref{benchm_sol3d}-\eqref{benchm_sol1d}, with $\lambda=L=0$
+satisfy \eqref{eq:problem1_simple}. Note in particular that $q_1$ is such that
+$\trace{u} - \ext{\ud} = q_1$ on $\Gamma$.
+
+\subsection{Numerical experiments. $\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}\label{sec:experiment_conform}
+Using the benchmark problem \eqref{benchmark} we now investigate convergence
+properties of the two formulations. To this end we consider a \emph{uniform} mesh
+of $\mathcal{T}^{\Omega}_h$ of $\Omega$ consisting of tetrahedra with diameter $h$.
+Further, the discretization shall be geometrically \emph{conforming} to both $\Lambda$
+and $\Gamma$ such that the meshes $\mathcal{T}^{\Gamma}_h$, $\mathcal{T}^{\Lambda}_h$
+are made up of facets and edges of $\mathcal{T}^{\Omega}_h$ respectively, cf. Figure \ref{fig:mesh}
+for illustration.
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.45\textwidth]{graphics/conform_mesh.tex}
+ \includegraphics[width=0.45\textwidth]{graphics/nonconform_mesh.tex} 
+ \captionof{figure}{
+   (Top)
+$\Lambda$ and $\Gamma$ conforming discretization of $\Omega$
+   used for \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}.
+   (Bottom) Sample discretization of the benchmark geometry in the non-conforming case. 
+ }
+\label{fig:mesh}
+\end{figure}
+
+\begin{table}
+  \scriptsize{
+  \begin{center}
+    \begin{tabular}{l|llll}
+\hline
+\multicolumn{5}{c}{\textcolor{blue!40!white}{$\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}}\\
+\hline
+    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\lambda-\lambda_h}_{-\tfrac{1}{2},\Gamma}$ & $\norm{\lambda-\lambda_h}_{0,\Gamma}$\\
+      \hline
+4  & 3.4E0(--)    & 5.3E-1(--)   & 2.9E0(--)    &8.7E0(--)    \\
+8  & 1.7E0(0.99)  & 2.6E-1(1.06) & 6.1E-1(2.25) &1.9E0(2.21)  \\
+16 & 8.7E-1(0.99) & 1.3E-1(1.02) & 1.4E-1(2.13) &4.7E-1(1.99) \\
+32 & 4.4E-1(1.00) & 6.3E-2(1.00) & 3.4E-2(2.03) &1.3E-1(1.80) \\
+64 & 2.2E-1(1.00) & 3.1E-2(1.00) & 8.6E-3(2.00) &4.2E-2(1.68) \\
+\hline
+$h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-u_{\odot h^{\prime}}}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{-\tfrac{1}{2}, \Lambda}$ & $\norm{\ld-\ldh}_{0, \Lambda}$\\
+\hline
+4   & 3.1E0(--)    & 5.4E-1(--)   & 4.4E-2(--)   & 7.8E-2(--)  \\
+8   & 1.7E0(0.87)  & 2.6E-1(1.06) & 1.1E-2(2.01) & 1.9E-2(2.01)\\
+16  & 8.6E-1(0.96) & 1.3E-1(1.02) & 2.7E-3(2.01) & 4.8E-3(2.02)\\
+32  & 4.4E-1(0.99) & 6.3E-2(1.00) & 6.7E-4(2.01) & 1.2E-3(2.01)\\
+64  & 2.2E-1(1.00) & 3.1E-2(1.00) & 1.7E-4(2.01) & 3.0E-4(2.01)\\
+128 & 1.1E-1(1.00) & 1.6E-2(1.00) & 4.1E-5(2.01) & 7.4E-5(2.00)\\
+\hline
+\multicolumn{5}{c}{\textcolor{red!50!white}{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$}}\\
+%    \begin{tabular}{l|lll}
+\hline
+    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & \multicolumn{2}{c}{$\norm{\ld-\ldh}_{0,\Lambda}$}\\
+      \hline
+5   & 2.6E0(--)    & 2.3E-1(--)   & \multicolumn{2}{c}{1.7E-1(--)} \\ 
+9   & 1.5E0(0.84)  & 9.4E-2(1.42) & \multicolumn{2}{c}{7.1E-2(1.36)}\\
+17  & 8.1E-1(0.94) & 4.3E-2(1.18) & \multicolumn{2}{c}{2.9E-2(1.37)}\\
+33  & 4.2E-1(0.98) & 2.1E-2(1.06) & \multicolumn{2}{c}{7.9E-3(1.91)}\\
+65  & 2.1E-1(0.99) & 1.1E-2(1.02) & \multicolumn{2}{c}{2.6E-3(1.64)}\\
+129 & 1.1E-1(1.00) & 5.2E-3(1.01) & \multicolumn{2}{c}{8.5E-4(1.61)}\\
+\hline
+    \end{tabular}
+  \end{center}    
+  }
+  \captionof{table}{Error convergence on a benchmark problem \eqref{benchmark}.
+    (Top) problem \eqref{eq:problem1_simple}, (middle) \eqref{eq:problem2_simple} with
+    conforming discretization and (bottom) \eqref{eq:problem2_simple} in case
+    $\mathcal{T}^{\Omega}_h$ does not conform to $\Lambda$. Continuous linear Lagrange
+    elements are used for $u_h$, $\udh$ and $u_{\odot h^{\prime}}$ and $\ldh$ in
+    conforming case, while in nonconforming case $\ldh$ is piecewise constant
+    on elements of $\mathcal{G}_h$.
+  }
+  \label{tab:error_conform}
+\end{table}
+
+Considering inf-sup stable discretization in terms of continuous linear Lagrange
+($P_1$) elements (for all the spaces), Table \ref{tab:error_conform}
+lists the errors of formulations \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}
+on the benchmark problem. It can be seen that the error in $u$ and $\ud$ in $H^1$ norm
+converges linearly (as can be expected due to $P_1$ element discretization).
+Moreover, the error of the Lagrange multiplier approximation in $H^{-1/2}$ norm
+decreases quadratically. In the light of $P_1$ discretization this rate appears
+superconvergent. We speculate that the result is due to the fact that the
+exact solution is particularly simple, $\lambda=\ld=0$.
+%In case of the results for
+%\eqref{eq:problem1_simple} the rate can also be due to the fact that the
+%error is interpolated into the same finite element space as the approximation $Q_h$.
+We remark that for $u$ and $\ud$ the error is interpolated into the finite element space of
+piecewise quadratic \emph{discontinous} functions. For \eqref{eq:problem2_simple} we
+evaluate the fractional norm and interpolate the error using piecewise continuous
+cubic functions. 
+%This is due to the fact that evaluating the fractional norm in higher order spaces
+%for on $\Gamma$ is prohibitively costly. 
+For the sake of comparison with non-conforming formulation of \eqref{eq:problem2} from
+\S\ref{sec:unfit2} Table \ref{tab:error_conform} also
+lists the error of the Lagrange multiplier in the $L^2$ norm. Here, quadratic convergence is observed
+for \eqref{eq:problem2_simple}. For \eqref{eq:problem1_simple} the rate is between 1.5 and 2.
+
+We plot the numerical solution of problem \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} in
+Figure \ref{fig:sol_benchm1}.
+
+\begin{figure}
+\centering
+\includegraphics[width = 0.6\textwidth]{./graphics/mfs_LM2d}
+\includegraphics[width = 0.3\textwidth]{./graphics/mfs_LM1d_crop}
+\caption{Numerical solution of problem \eqref{eq:problem1_simple} and
+  \eqref{eq:problem2_simple}. (Left) functions $u_h$, $\udh$ (practically identical
+  in both problems). (Middle) Lagrange multiplier for \eqref{eq:problem1_simple}
+  and (right) for \eqref{eq:problem2_simple}.}
+\label{fig:sol_benchm1}
+\end{figure}
+
+%\begin{figure}
+%\centering
+%\includegraphics[width = 0.9\textwidth]{./graphics/mfs_LM1d}
+%\caption{Numerical solution of problem \eqref{eq:problem2_simple}:
+%  functions $u_h$ and $\udh$ on the left and the Lagrance multiplier
+%  ${\ld}_h$ on the right.}\label{fig:sol_benchm2}
+%\end{figure}
+
+\subsection{Numerical experiments. $\mathcal{T}^{\Omega}_h$ non-conforming to $\Gamma$}\label{sec:experiment_nonconform}
+Using benchmark problem \eqref{benchmark} we consider \eqref{eq:problem2} in the
+setting of \S \ref{sec:unfit2}. To this end we let $\mathcal{T}^{\Omega}_h$ be a uniform
+mesh of $\Omega$ such that no cell $\mathcal{T}^{\Omega}_h$ has any edge
+lying on $\Lambda$. Further we let $h^{\prime}=h/3$ in $\mathcal{T}^{\Lambda}_{h^{\prime}}$,
+cf. Figure \ref{fig:mesh}.
+
+Using discretization in terms of $P_1$-$P_1$-$P_0$ element Table \ref{tab:error_conform}
+lists the error of the stabilized formulation of \eqref{eq:problem2}. A linear
+convergence in the $H^1$ norm can be observed in the error of $u$ and $\ud$. We
+remark that the norms were computed as in \S\ref{sec:experiment_conform}. For simplicity
+the convergence of the multiplier is measured in the $L^2$ norm rather then the $H^{-1/2}(\Gamma)$
+norm used in the analysis. Then, convergence exceeding order 1.5 can be observed, however,
+the rates are rather unstable.
+
+%% \begin{table}
+%% %%   %%%
+%% \begin{minipage}[b]{0.35\linewidth}
+%%  \centering
+%%  \includegraphics[width=\textwidth]{graphics/nonconform_mesh.pdf}
+%%  \vspace{-20pt}
+%%  \captionof{figure}{
+%%    Sample discretization of the benchmark geometry in the non-conforming case. 
+%%  }
+%% \label{fig:unfit}
+%% \end{minipage}
+%% \hspace{2pt}
+%% %%%
+%%     \begin{minipage}[b]{0.62\linewidth}
+%%       %%%
+%%   \scriptsize{
+%%   \begin{center}
+%%     \begin{tabular}{l|lll}
+%%       \toprule
+%%     $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{0,\Lambda}$\\
+%%       \hline
+%% 5   & 2.6E0(--)    & 2.3E-1(--)   & 1.7E-1(--) \\ 
+%% 9   & 1.5E0(0.84)  & 9.4E-2(1.42) & 7.1E-2(1.36)\\
+%% 17  & 8.1E-1(0.94) & 4.3E-2(1.18) & 2.9E-2(1.37)\\
+%% 33  & 4.2E-1(0.98) & 2.1E-2(1.06) & 7.9E-3(1.91)\\
+%% 65  & 2.1E-1(0.99) & 1.1E-2(1.02) & 2.6E-3(1.64)\\
+%% 129 & 1.1E-1(1.00) & 5.2E-3(1.01) & 8.5E-4(1.61)\\
+%% \bottomrule
+%%     \end{tabular}
+%%   \end{center}    
+%% }    
+%%   \captionof{table}{
+%%     Error convergence of \eqref{eq:problem2_simple} on a benchmark problem \eqref{benchmark} in case
+%%     $\mathcal{T}^{\Omega}_h$ does not conform to $\Lambda$.}
+%%   \label{tab:error_unfit}    
+%%   \end{minipage}
+%% \end{table}
+
+\subsection{Comparison}
+In Tables \ref{tab:error_conform}, \ref{tab:error_conform} one can observe that 
+all the formulations yield practically identically accurate approximations of $u$.
+Further, compared to the conforming case, the stabilized formulation \eqref{eq:problem2}
+results in a greater accuracy of $u_{\odot h}$ as the underlying mesh $\mathcal{T}^{\Lambda}_{h}$ is
+here finer. Due to the different definitions in the three formulations, comparision of the Lagrange
+multiplier convergence is not straightforward. We therefore limit ourselves to a
+comment that in the $L^2$ norm all the formulations yield faster than linear convergence.
+
+In order to discuss solution cost of the formulations we consider 
+the resulting preconditioned linear systems. In particular, we shall compare
+spectral condition numbers and the time to convergence of the preconditioned
+minimal residual (MinRes) solver with the with stopping criterion requiring
+the relative preconditioned residual norm to be less than $10^{-8}$. We remark
+that we shall ignore the setup cost of the preconditioner.
+
+Following operator preconditioning technique \cite{mardal2011preconditioning} we
+propose as preconditioners for \eqref{eq:problem1} and \eqref{eq:problem2} in the
+conforming case the (approximate) Riesz mapping with respect to the inner products of
+the spaces in which the two formulations were proved to be well posed.
+In particular, the preconditioner for the Lagrange multiplier relies on
+(the inverse of) the fractional Laplacian $-\Delta^{-1/2}$ on $\Gamma$ for
+\eqref{eq:problem1_simple} and $\Lambda$ for \eqref{eq:problem2_simple}.
+A detailed analysis of the preconditioners will be presented in a separate
+work. We remark that in both cases the fractional Laplacian was here realized
+by spectral decomposition \cite{kuchta2016preconditioners}.
+
+For the unfitted stabilized \eqref{eq:problem2} the Lagrange multiplier preconditioner
+uses a Riesz map with respect to the inner product due to $L^2(\mathcal{G}_h)$ and
+the stabilization \eqref{eq:stab}, i.e.
+\[
+({\ld}_h, {\md}_h) \mapsto \sum _{K\in \mathcal{G}_h}\int_{K}{\ld}_h {\md}_h + \sum _{K\in \mathcal{G}_h} \int_{\partial K \setminus \partial \mathcal{G}_h} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket.
+\]
+This simple choice does not yield bounded
+iterations. However, establishing a robust precondtioner in this case 
+is beyond the scope of the paper and shall be pursued in the future works.
+
+In Table \ref{tab:cost} we compare solution time, number of iterations and
+condition numbers of the (linear systems due to the) three formulations.
+Let us first note that the proposed preconditioners for \eqref{eq:problem1} and
+\eqref{eq:problem2} in the conforming case seem robust with respect to discretization
+parameter as the iteration counts and condition numbers are bounded in $h$.
+We then see that the solution time for \eqref{eq:problem1_simple} is about 2 times
+longer compared to \eqref{eq:problem2_simple} which is about 4 times more expensive
+than the solution of the Poisson problem \eqref{benchm_3d}. This is in addition to the
+higher setup costs of the preconditioner which in our implementation involve solving
+an eigenvalue problem for the fractional Laplacian. Therefore it is advantageous to keep
+the multiplier space as small as possible. We remark that the missing
+results for \eqref{eq:problem1_simple} in Table \ref{tab:cost} and \ref{tab:error_conform}
+are due to the memory limitations which we encounter when solving the eigenvalue problem
+for the Laplacian, which for finest mesh involves cca 32 thousand eigenvalues, cf. Appendix \ref{sec:appendix}.
+%
+
+Due to the missing proper preconditioner for the Lagrange multiplier block the
+number of iterations in the third, unfitted formulation can be seen to approximatly
+double on refinement.
+
+\begin{table}
+  \scriptsize{
+  \begin{center}
+    \begin{tabular}{l|lll|lll|lll|ll}
+      %\toprule
+      \hline
+      \multirow{2}{*}{$l$} & \multicolumn{3}{c|}{\eqref{eq:problem1}} & \multicolumn{3}{c|}{\eqref{eq:problem2}} & \multicolumn{3}{c|}{ Stabilized \eqref{eq:problem2}} & \multicolumn{2}{c}{\eqref{benchm_3d}}\\
+      \cline{2-12}
+      & \# & $T\left[s\right]$ & $\kappa$ & \# & $T\left[s\right]$ & $\kappa$ & \# & $T\left[s\right]$ & $\kappa$ & \# & $T\left[s\right]$\\
+      \hline
+      1 & 20 & 0.03  & 15.56 & 9  & 0.02  & 3.04 & 21  & 0.01   & 9.70  &3 & $<0.01$\\ 
+      2 & 35 & 0.06  & 16.28 & 17 & 0.03  & 4.67 & 31  & 0.03   & 15.87 &4 & $<0.01$\\ 
+      3 & 38 & 0.14  & 16.64 & 22 & 0.06  & 6.25 & 53  & 0.15   & 32.93 &5 & 0.01   \\ 
+      4 & 39 & 1.70  & 16.75 & 24 & 0.89  & 7.03 & 110 & 4.54   & 61.48 &5 & 0.12   \\ 
+      5 & 38 & 12.04 & 16.78 & 20 & 5.21  & 5.02 & 232 & 59.43  & 94.25 &5 & 0.90  \\ 
+      6 & -- & --    & --    & 17 & 28.77 & --   & 507 & 832.90 & --    &6 & 7.75  \\
+      \hline
+      %\bottomrule
+    \end{tabular}
+    \end{center}
+    }
+  \caption{Cost comparison of the formulations across refinement levels $l$.
+    Number of Krylov (preconditioned conjugate gradient for \eqref{benchm_3d},
+    MinRes otherwise) iterations and the conditioned number of the preconditioned
+    problem is denoted by $\#$ and $\kappa$ respectively. Time till convergence
+    of the iterative solver (excluding the setup) is shown as $T$. 
+  }
+\label{tab:cost}
+\end{table}
+
+%{\color{red}
+%\begin{remark} In the following some observations:\\
+%
+%\begin{itemize}
+%\item \textbf{How do we compute the norm $\|\cdot \|_{H^{-\frac 12}}$ in Table \ref{tab:error_conform}?} The norm $\|\cdot \|_{H^{-\frac 12}}$ has been computed using a decomposition based on eigenvalues and eigenfuctions of $\Delta ^{-\frac 12}$.\\
+%
+%\item \textbf{Why $\lambda _h \neq \lambda$?} Since $\lambda = 0 \in Q_h$, we would expect $\lambda _h = \lambda$.
+However, first of all we suspect that for the approximation error an estimate similar to \cite[(11.26)]{steinbach2007numerical} holds, reported in the following
+%\begin{equation*}
+%\|u-u_h\|^2_{H^1} + \|\lambda - \lambda_h\|^2_{H^{-\frac 12}} \leq c_1 h^2|u|^2_{H^2} + c_2 h^3\|\lambda_h\|^2_{H^1_{pw}},
+%\end{equation*}
+%where $\|\cdot \|_{H^1_{pw}}$ is the broken $H^1$ norm. 
+%So the error on the LM depends on the error on the solution.
+We suspect that if for example $u$ and $\ud$ are $P_2$ functions and we use a $P_2$ approximation (therefore $u = u_h$ and $\ud = \udh$), also $\lambda = \lambda_h$.\\
+%
+%\item \textbf{Why the error is larger close to edges, especially in Figure \ref{fig:sol_benchm1}?} 
+%We suspect that the reasoning for why the error is larger close to edges and corner vertices is that the multiplier is
+%related to $\nabla u \cdot \boldsymbol{n}$ and the normal in the corner or on the z-aligned edges in the figure is not well-defined. Btw, the oscillations are smaller if we impose Neumann
+%bcs on z min and max surfaces of $\Omega$ (the rest has Dirichlet).
+%\end{itemize}
+%\end{remark}
+%}
+
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 \bibliographystyle{siamplain}

### 2020-03-14 appendix.tex
Paolo's revision sections 2-3
merge tables
Updates from Overleaf

@@
-\section{System sizes in benchmark formulations}\label{sec:appendix}
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\section{Derivation of the model}
+Below we detail the steps performed in order to formulate \ref{eq:problem1} and \ref{eq:problem2} precisely. 
+The derivations are similar~\cite{laurino_m2an},  but here we derive the system including the Lagrange multiplier.
+
+\subsection{Topological model reduction}
+
+We consider the problem arising from \emph{Dirichlet-Neumann} conditions. Find $\up,\uf$ s.t.:
+\begin{subequations}\label{eq:dirneu}
+\begin{align}
+\label{eq:dirneu1}
+- \Delta \up  + \up &= f  && \text{ in } \Omega_{\oplus},\\
+\label{eq:dirneu2}
+- \Delta \uf  + \uf &= g  && \text{ in } \Omega_\ominus,\\
+\label{eq:dirneu3}
+-\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
+\label{eq:dirneu4}
+\uf &= \up && \text{ on }  \Gamma,\\
+\label{eq:dirneu5}
+\up &= 0 && \text{ on } \partial \Omega\,.
+\end{align}
+\end{subequations}
+
+We observe that the coupling constraints defined on $\Gamma$ involve essential or strong conditions.
+The strong conditions will, however, be enforced weakly by using the method of Lagrange multipliers~\cite{MR359352}.
+%We remark that this case is substantially different from the one previously addressed in \cite{laurino_m2an}.
+
+The variational formulation of problem \eqref{eq:dirneu}
+is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus), \ \lambda \in H^{-\frac 1 2}(\partial\Omega_\ominus)$ s.t.
+\begin{subequations}\label{eq:weak_dirneu}
+\begin{align}
+&(u_\oplus,v_\oplus)_{H^1(\Omega_\oplus)} + (u_\ominus,v_\ominus)_{H^1(\Omega_\ominus)} 
++ \langle  v_\oplus - v_\ominus, \lambda \rangle_{\Gamma} 
+\\
+\nonumber
+&\qquad\qquad = (f,v_\oplus)_{L^2(\Omega_\oplus)} + (g,v_\ominus)_{L^2(\Omega_\ominus)}
+\quad \forall v_\oplus \in H^1_{\partial\Omega}(\Omega_\oplus), \ v_\ominus \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus)
+\\
+& \langle u_\oplus - u_\ominus, \mu \rangle_{\Gamma} = 0
+\quad \forall  \mu \in H^{-\frac 1 2}(\Gamma)\,,
+\end{align}
+\end{subequations}
+%where $\langle v, \mu \rangle_{H^{-\frac 1 2}(\Gamma)}$ denotes the duality pairing between 
+%$ \mu \in H^{-\frac 1 2}(\Gamma)$ and $v \in H^{\frac 1 2}(\Gamma)$.
+In this case, $\lambda$ is the Lagrange multiplier and it is equivalent to $\nabla \uf \cdot \nn_\ominus$.
+
+The objective of this work is to derive and analyze a simplified version of problem \eqref{eq:weak_dirneu}, where the domain $\Omega_\ominus$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$.
+This new problem setting will be called the \emph{reduced} problem.
+Form the mathematical standpoint it is more challenging than \eqref{eq:weak_dirneu}, because it involves the coupling of 3D/1D elliptic problems.
+We end up with two different formulations of a reduced problem for the unknown $u$ defined on the entire 3D domain $\Omega$, 
+coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$ and a Lagrange multiplier defined either on $\Gamma$ (Problem 3D-1D-2D) or on $\Lambda$ (Problem 3D-1D-1D). 
+The scope of this work is to analyze and compare the two alternatives,
+with the aim to determine which is the most suitable to set up a computational model for 3D-1D PDEs coupled with Dirichlet-Neumann constraint.
+
+\subsubsection*{Model reduction of the problem on $\Omega_{\ominus}$}
+
+We apply the averaging technique to equation \eqref{eq:dirneu2}.
+In particular, we consider an arbitrary portion $\mathcal{P}$ of the cylinder $\Omega_\ominus$, with lateral surface $\Gamma _{\mathcal{P}}$ and bounded by two perpendicular sections to $\Lambda$, namely $\mathcal{D}(s_1), \ \mathcal{D}(s_2)$ with $s_1<s_2$.
+We have,
+\begin{multline*}
+\int_{\mathcal{P}} -\Delta \uf + \uf d\omega =
+-\int_{\partial \mathcal{P}} \nabla \uf \cdot \nn_{\ominus} \, d\sigma  + \int_{\mathcal{P}}\uf d\omega=
+\\
+ \int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma -  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma -  \int_{\Gamma_{\mathcal{P}}} \nabla \uf \cdot \nn_{\ominus} d\sigma +\int_{\mathcal{P}}\uf d\omega
+\end{multline*}
+By the fundamental theorem of integral calculus combined with the Reynolds transport Theorem, 
+being $\nu$ the normal deformation of the boundary along $(0,S)$, we have,
+\begin{equation*}
+\begin{split}
+\int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma -  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma 
+&= -\int_{s_1}^{s_2} d_s \int_{\mathcal{D}(s)}  \partial_s \uf d\sigma ds
+\\
+&= -\int_{s_1}^{s_2} d_{ss}^2 \int_{\D(s)} u_{\ominus} \, d\sigma \, ds +  \int_{s_1}^{s_2} d_s \left( \int_{\DD(s)} \nu u_{\ominus} \, d\gamma \right) ds\,,
+\end{split}
+\end{equation*}
+and assuming that $\D(s)$  can not change shape, we have
+\begin{equation*}
+\begin{split}
+-\int_{s_1}^{s_2} d_{ss}^2 \int_{\D(s)} u_{\ominus} \, d\sigma \, ds + \int_{s_1}^{s_2} d_s \left( \int_{\DD(s)} \nu u_{\ominus} \, d\gamma \right)\, ds
+&=-\int_{s_1}^{s_2} \left[d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) -  d_s(  \nu |\DD(s)| \avrc{u}_{\ominus} ) \right] \, ds
+\\
+&=-\int_{s_1}^{s_2} \left[d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) -  d_s\left(d_s(|\D(s)|) \avrc{u}_{\ominus} \right) \right] \, ds.
+\end{split}
+\end{equation*}
+Moreover, we have
+\begin{equation*}
+\int_{\Gamma_{\mathcal{P}}} \nabla \uf \cdot \nn_{\ominus} d\sigma =  \int_{\Gamma_{\mathcal{P}}} \lambda \, d\sigma
+=  \int_{s_1}^{s_2} \int_{\partial\mathcal{D}(s)} \lambda d\gamma \, ds 
+= \int_{s_1}^{s_2} |\DD| \avrc{\lambda} \,ds\,.
+\end{equation*}
+From the combination of all the above terms with the right hand side, we obtain that the solution $\uf$ of \eqref{eq:dirneu2} satisfies,
+\begin{equation*}
+\int_{s_1}^{s_2} \left[ 
+-d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) +  d_s\left(d_s(|\D(s)|) \avrc{u}_{\ominus}\right) + |\D(s)|\avrd{u}_{\ominus} 
+- |\partial\mathcal{D}(s)| \avrc{\lambda} 
+\right] \, ds = \int_{s_1}^{s_2} |\mathcal{D}(s)| \avrd{g}\, ds \,.
+\end{equation*}
+Since the choice of the points $s_1,s_2$ is arbitrary, we conclude that the following equation holds true,
+\begin{equation}\label{eq:averaged_f}
+-d_{ss}^2 (|\D(s)|\avrd{u}_{\ominus}) +  d_s\left(d_s(|\D(s)|) \avrc{u}_{\ominus}\right) + |\D(s)|\avrd{u}_{\ominus} 
+- |\partial\mathcal{D}(s)| \avrc{\lambda}
+= |\mathcal{D}(s)| \avrd{g} \quad \text{on} \ \Lambda\,,
+\end{equation}
+which is complemented by the following conditions at the boundary of $\Lambda$,
+\begin{equation}\label{eq:averaged_f_boundary}
+|\D(s)| d_s \avrd{u}_{\ominus} = 0, \quad d_s |\D(s)| = 0, \quad \text{on} \quad s=0,S.
+\end{equation}
+Then, we consider variational formulation of the averaged equation \eqref{eq:averaged_f}.
+After multiplication by a test function $\vd \in H^1(\Lambda)$, integration on $\Lambda$ and suitable application of integration by parts, we obtain,
+\begin{multline*}
+\int_\Lambda d_s (|\D(s)| \avrd{u}_{\ominus} ) d_s \vd \, ds - d_s (|\D(s)| \avrd{u}_{\ominus} ) \vd |_{s=0}^{s=S}
+- \int_\Lambda (d_s |\D(s)|)\avrc{u}_{\ominus} d_s \vd \, ds + (d_s |\D(s)|) \avrc{u}_{\ominus} \vd |_{s=0}^{s=S}
+\\
++\int_\Lambda |\D(s)| \avrd{u}_\ominus \vd - \int_\Lambda |\DD(s)| \avrc{\lambda} \vd \, ds
+= \int_\Lambda |\D(s)| \avrd{g} V\, ds\,.
+\end{multline*}
+Using boundary conditions, 
+the identity $d_s (|\D(s)| \avrd{u}_{\ominus} ) = |\D(s)| d_s \avrd{u}_{\ominus} + d_s (|\D(s)|) \avrd{u}_{\ominus}$
+and reminding that $d_s |\D(s)|)/|\DD(s)| = \nu$,
+we obtain,
+\begin{equation}\label{eq:averaged_f_weak}
+(d_s \avrd{u}_{\ominus}, d_s \vd )_{\Lambda,|\D|} 
++ ( \nu (\avrd{u}_{\ominus} - \avrc{u}_{\ominus}), d_s \vd)_{\Lambda,|\DD|} +(\avrd{u}_\ominus, \vd)_{\Lambda, |\D|}
+- (\avrc{\lambda},\vd)_{\Lambda,|\DD|}
+= (\avrd{g},V)_{\Lambda,|\D|}\,.
+\end{equation}
+Let us now formulate the modelling assumption that allows us to reduce equation \eqref{eq:averaged_f_weak} to a solvable one-dimensional (1D) model.
+More precisely, we assume that the function $\uf$ has a \emph{uniform profile} on each cross section $\mathcal{D}(s)$, namely $\uf(r,s,t) = \ud(s)$.
+Therefore, observing that $\ud=\avrc{u}_{\ominus}=\avrd{u}_{\ominus}$, problem \eqref{eq:averaged_f_weak} turns out to find $\ud \in H^1(\Lambda)$ such that
+\begin{equation}\label{eq:1Ddirneu_weak}
+ (d_s \ud, d_s \vd)_{\Lambda,|\mathcal{D}|} 
++(\ud, \vd)_{\Lambda, |\D|}
+-(\avrc{\lambda},\vd)_{\Lambda, |\DD|}
+=  (\avrd{g},\vd)_{\Lambda, |\mathcal{D}|}
+\quad \forall \vd \in H^1(\Lambda)\,.
+\end{equation}
+
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\subsubsection*{Topological model reduction of the problem on $\Omega_{\oplus}$}
+We focus here on the subproblem of \eqref{eq:dirneu1} related to $\Omega_{\oplus}$.
+We multiply both sides of \eqref{eq:dirneu1} by a test function $v\in H^1_0(\Omega)$ and integrate on $\Omega_\oplus$. Integrating by parts and using boundary and interface conditions, we obtain
+\begin{equation*}
+\begin{split}
+\int_{\Omega _{\oplus}}fv\,d\omega&=
+\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\omega -\int _{\partial \Omega _{\oplus}}\nabla \up \cdot \nn_{\oplus} v\,d\sigma + \int_{\Omega_{\oplus}} \up v
+\\
+&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega -\int_{\Gamma} \nabla \up \cdot \nn_{\oplus} v + \int_{\Omega_{\oplus}} \up v
+\\
+&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega +\int_{\Gamma} \lambda v + \int_{\Omega_{\oplus}} \up v.
+\end{split}
+\end{equation*} 
+Then, we make the following modelling assumption:
+we identify the domain $\Omega_{\oplus}$ with the entire $\Omega$, 
+and we correspondingly omit the subscript $\oplus$ to the functions defined on $\Omega_{\oplus}$,
+namely
+\begin{equation*}
+\int_{\Omega_{\oplus}} u_\oplus\, d\omega \simeq \int_{\Omega} u\, d\omega\,.
+\end{equation*}
+Therefore, we obtain 
+\begin{equation*}
+(\nabla u ,\nabla v)_{\Omega} +(u,v)_{\Omega}+(\lambda, v)_{\Gamma}  =(f,v)_{\Omega}
+\end{equation*}
+and combining with \eqref{eq:1Ddirneu_weak} we obtain the first formulation of the reduced problem.
+
+Hence, we have obtained the Problem 3D-1D-2D, equation 
+\eqref{eq:problem1}: \\
+Find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac 1 2}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
+\begin{subequations}
+\begin{align*}
+&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
++ \langle \trace v  - \ext \vd, \lambda \rangle_\Gamma &&
+\\
+\nonumber
+&\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
+\quad &&\forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)\,,
+\\
+& \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0
+\quad && \forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
+\end{align*}
+\end{subequations}
+This coupled problem is classifies as 3D-1D-2D because the unknowns $u,\lambda,\ud$ belong to 
+$\Omega \subset \R^3,\, \Gamma \subset \R^2,\, \Lambda \subset \R$, respectively.
+Then, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-2D formulation
+involving sub-problems on $\Omega$ and $\Lambda$ and coupling operators defined on $\Gamma$
+to a 3D-1D-1D formulation where the coupling terms are set on $\Lambda$. 
+To this purpose, let us write the Lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
+\begin{equation*}
+\lambda=\avrc{\lambda}+\tilde{\lambda}, \qquad v=\avrc{v}+\tilde{v},
+\quad \text{on} \ \partial\mathcal{D}(s)\,,
+\end{equation*}
+where $\avrc{\tilde{\lambda}}=\avrc{\tilde{v}}=0$. 
+Therefore, the coupling term on $\Gamma$ can be decomposed as,
+\begin{equation*}
+\int_{\Gamma}\lambda v\, d\sigma
+=\int _{\Lambda}  \int_{\partial\mathcal{D}(s)} (\avrc{\lambda}+\tilde{\lambda})(\avrc{v}+\tilde{v})d\gamma ds
+= \int_{\Lambda}|\partial\mathcal{D}(s)| \avrc{\lambda}\avrc{v}\,ds+\int_{\Lambda}  \int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v}d\gamma ds\,.
+\end{equation*}
+
+Thanks to the additional assumption that the product of fluctuations is small, namely
+\begin{equation*}
+\int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v} d\gamma \simeq 0\,
+\end{equation*}
+the term $\left(\trace v, \lambda \right)_{\Gamma}$ becomes $\left( \mtrace v, \avrc{\lambda} \right)_{\Lambda, |\DD|}$, where $\mtrace$ denotes the composition of operators $\trace \circ \avrc{(\cdot)}$.
+Combined with \eqref{eq:1Ddirneu_weak}, this leads to the second formulation of the reduced problem.
+
+Hence, we have derived the Problem 3D-1D-1D, equation \eqref{eq:problem2}: \\ 
+Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac 1 2}(\Lambda)$, such that
+\begin{subequations}
+\begin{align*}
+&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
++  \langle \mtrace v - \vd, \ld \rangle_{\Lambda, |\DD|} &&
+\\
+\nonumber
+&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
+\quad && \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)\,,
+\\
+& \langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} = 0
+\quad &&\forall \md \in H^{-\frac 1 2}(\Lambda)\,,
+\end{align*}
+\end{subequations}
+We notice that all the integrals of the reduced problem are well defined because 
+$\mtrace: H^1_0(\Omega) \rightarrow H^\frac 1 2_{00}(\Lambda)$ as shown in Corollary \ref{corollary:H12norm}.
+
+% The well-posedness of $\eqref{eq:problem1}$ and $\eqref{eq:problem2}$ 
+% can be studied in the framework of the classical theory of saddle point problems as shown in the following.
+
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\section{Proof of Lemma \ref{lemma:H12norm}.}
+
+\begin{proof}
+Let us consider the eigenvalue problems for the Laplace operator on $\Gamma$ with homogeneous Dirichlet conditions at $x=0,\, X$ and periodic boundary conditions at $y=0,\, Y$.
+Let us also consider the Laplace eigenproblem on $(0,X)$ with homogeneous Dirichlet conditions.
+Let us denote as $\phi _{ij}(x,y)$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the Laplacian on $\Gamma$, and with $\phi _i(x)$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $(0,X)$.
+In particular,
+\begin{align*}
+&\phi _{ij}(x,y)=\sin \left(\frac{i\pi x}{X}\right)\left( \cos\left(\frac{j2\pi y}{Y}\right)+ \sin\left(\frac{j2\pi y}{Y}\right) \right),\quad
+&&\rho_{ij}=\left(\frac{i\pi}{X}\right) ^2+\left(\frac{j2\pi}{Y}\right)^2,
+\\
+&\phi _{i}(x)=\sin \left(\frac{i\pi x}{X}\right),\quad
+&&\rho _i = \left(\frac{i\pi}{X}\right) ^2.
+\end{align*}
+
+Further, we have
+the following concrete representation of the fractional norms, 
+\begin{equation}\label{eq:fracnorm_lambda}
+\|u\|_{H^{\frac 12}_{00}(\Lambda)}=\left(\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|a_i|^2\right)^{\frac 12}
+\ \text{with} \ a_i=\left(u, \phi _i \right)_{\Lambda};
+\quad
+\| v \|_{H^{-\frac 12}(\Lambda)} = \sup_{u\in H^{\frac 12}_{00}(\Lambda)}\frac{\langle u, v \rangle_\Lambda}{\|u\|_{H^{\frac 12}_{00}(\Lambda)}}\,.
+\end{equation}
+\kent{also the other}
+
+It is easy to verify that 
+\begin{equation}\label{int_eigenf}
+\int_0^{Y} \phi _{ij}(x,y)=0 \quad \forall j>0, \forall i\,,
+\quad
+\int_0^{Y} \phi _{ij}(x,y)= Y \, \sin\left(\frac{i\pi x}{X}\right) \quad \mbox{if } j=0, \forall i  .
+\end{equation}
+Moreover we recall that $\phi_{i,j}(x,y)$ and $\phi _i(x)$ form an orthogonal basis of $L^2(\Gamma)$ and $L^2(0,X)$ respectively. Therefore,
+\begin{equation*}
+\avrc{u}(x)=\frac{1}{Y}\int_0^{Y} u(x,y)\, dy
+= \frac{1}{Y}\int_0^{Y} \sum_{i,j} a_{i,j} \phi_{i,j}(x,y) \, dy
+= \frac{1}{Y}\sum_{i,j} a_{i,j}\int_0^{Y}  \phi_{i,j}(x,y) \, dy
+=  \sum_{i} a_{i,0} \phi_{i}(x).
+\end{equation*}
+
+From \eqref{eq:fracnorm_lambda} we have
+\begin{multline*}
+\|\avrc{u}\|^2_{H^{\frac 12}_{00}(0,X)}
+=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}a_i^2
+=\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \int_0^X \avrc{u}(x) \sin\left(\frac{i\pi x}{X}\right)\, dx \right)^2
+\\
+= \sum_{i=1}^{\infty} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^X \sin\left(\frac{j\pi x}{X}\right) \sin\left(\frac{i\pi x}{X}\right) \, dx  \right)^2
+= \sum_{i=1}^{\infty} \frac{X^2}{4} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}a_{i,0}^2
+\\
+\leq \frac{X^2}{4}\sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ \left(\frac{i\pi}{X}\right)^2 
++ \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12} |a_{i,j}|^2 =\frac{X^2}{4}\|u\|^2_{H^{\frac 12}_{00}(\Gamma)},
+\end{multline*}
+where we have used the fact that
+\begin{equation*}
+\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=0 \quad \text{if $i\neq j$}
+\quad
+\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=\frac X2 \quad \text{if $i =j$}
+\end{equation*}
+and we have applied \eqref{eq:fracnorm_gamma} in the last equality.
+Moreover, in the case in which $u$ is constant with respect to $y$, we have
+\begin{multline*}
+\|u\|^2_{H^{\frac 12}_{00}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2
+=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12}\left( \int _0^X\int _0^Y u(x,y )\phi_{ij}(x,y) \right)^2
+\\
+=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12}\left( \int _0^X u(x) \int _0^Y \phi_{ij}(x,y) \right)^2,
+\end{multline*}
+and using \eqref{int_eigenf} we obtain
+\begin{equation*}
+\|u\|^2_{H^{\frac 12}_{00}(\Gamma)}=
+\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left(\int _0^X Yu(x)\, \sin\left(\frac{i\pi x}{X}\right)\right)^2
+=Y^2 \sum_{i=1}^{\infty}\left( 1+ \rho _i\right)^{\frac 12}|a_i|^2 = Y^2  \|u\|^2_{H^{\frac 12}_{00}(0,X)}.
+\end{equation*}
+\end{proof}
+
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\section{System sizes in benchmark formulations} \label{sec:appendix}
 Below we list dimensions of the finite element spaces used to discretize
@@
     \begin{tabular}{l|lll|lll|lll}
-      \toprule
+      %\toprule
+      \hline
       \multirow{2}{*}{$l$} & \multicolumn{3}{c|}{\eqref{eq:problem1}} & \multicolumn{3}{c|}{\eqref{eq:problem2}} & \multicolumn{3}{c}{ Stabilized \eqref{eq:problem2}}\\
@@
      6& --     & -- & -    & 2146689 & 129 & 129 & 2180100 & 385 & 768 \\
-      \bottomrule
+     %\bottomrule
+     \hline
     \end{tabular}

### 2020-03-14 3d1d_coupled_LM.tex
update 5

@@
 Concerning approximability,  elliptic equations with Dirac sources represent an effective prototype case that has been addressed in \cite{Bertoluzza201897,koppl2016local,koppl2014optimal}, where the optimal a-priori error estimates for the finite element approximation are derived.
-Furthermore, the interplay between the mathematical structure of the problem and solvers, as well as preconditioners for its discretization has been studied in details  in \cite{Kuchta2016B962} for the solution of 1D differential equations embedded in 2D, and more recently extended to the 3D-1D case in \cite{KMM2}.
+Furthermore, the interplay between the mathematical structure of the problem and solvers, as well as preconditioners for its discretization has been studied in details  in \cite{kuchta2016preconditioners} for the solution of 1D differential equations embedded in 2D, and more recently extended to the 3D-1D case in \cite{KMM2}.
 
@@
  \centering
- \includegraphics[width=0.45\textwidth]{graphics/conform_mesh.tex}
- \includegraphics[width=0.45\textwidth]{graphics/nonconform_mesh.tex} 
+ \includegraphics[width=0.45\textwidth]{graphics/conform_mesh.pdf}
+ \includegraphics[width=0.45\textwidth]{graphics/nonconform_mesh.pdf} 
  \captionof{figure}{
@@
 \subsection{Comparison}
-In Tables \ref{tab:error_conform}, \ref{tab:error_conform} one can observe that 
+In Tables \ref{tab:error_conform} one can observe that 
 all the formulations yield practically identically accurate approximations of $u$.
@@
 
-For the unfitted stabilized \eqref{eq:problem2} the Lagrange multiplier preconditioner
+For the unfitted stabilized formulation \eqref{eq:problem2} the Lagrange multiplier preconditioner
 uses a Riesz map with respect to the inner product due to $L^2(\mathcal{G}_h)$ and
@@
 This simple choice does not yield bounded
-iterations. However, establishing a robust precondtioner in this case 
+iterations. However, establishing a robust preconditioner in this case 
 is beyond the scope of the paper and shall be pursued in the future works.
@@
 than the solution of the Poisson problem \eqref{benchm_3d}. This is in addition to the
-higher setup costs of the preconditioner which in our implementation involve solving
+higher setup costs of the preconditioner, which in our implementation involve solving
 an eigenvalue problem for the fractional Laplacian. Therefore it is advantageous to keep
 the multiplier space as small as possible. We remark that the missing
-results for \eqref{eq:problem1_simple} in Table \ref{tab:cost} and \ref{tab:error_conform}
-are due to the memory limitations which we encounter when solving the eigenvalue problem
+results for \eqref{eq:problem1_simple} in Table \ref{tab:cost} are due to the
+memory limitations encountered when solving the eigenvalue problem
 for the Laplacian, which for finest mesh involves cca 32 thousand eigenvalues, cf. Appendix \ref{sec:appendix}.
@@
 Due to the missing proper preconditioner for the Lagrange multiplier block the
-number of iterations in the third, unfitted formulation can be seen to approximatly
+number of iterations in the third, unfitted formulation can be seen to approximately
 double on refinement.
@@
   \caption{Cost comparison of the formulations across refinement levels $l$.
-    Number of Krylov (preconditioned conjugate gradient for \eqref{benchm_3d},
-    MinRes otherwise) iterations and the conditioned number of the preconditioned
+    Number of Krylov  terations (preconditioned conjugate gradient for \eqref{benchm_3d},
+    MinRes otherwise) and the condition number of the preconditioned
     problem is denoted by $\#$ and $\kappa$ respectively. Time till convergence

### 2020-03-30 3d1d_coupled_LM.tex
Updates from Overleaf

@@
 \usepackage{tikz, subfigure}
-
-\usetikzlibrary{shapes, snakes, patterns, arrows}
+\usepackage{yfonts}
+
+\usetikzlibrary{shapes, patterns, arrows}
 \usetikzlibrary{calc}
@@
 \usepgfplotslibrary{fillbetween}
+\pgfplotsset{compat=1.16}
 
@@
 \newcommand{\miro}[1]{{\color{cyan}#1}}
+\newcommand{\paolo}[1]{{\color{magenta}#1}}
 % Title. If the supplement option is on, then "Supplementary Material"
@@
 \def\udh{u_{\odot h}}
+\def\udfh{u_{\odot \fkh}}
 \def\vdh{v_{\odot h}}
+\def\vdfh{v_{\odot \fkh}}
 \def\ldh{\lambda_{\odot h}}
 \def\md{\mu_{\odot}}
+\def\mdh{\mu_{\odot h}}
 \def\lld{l_{\odot}}
@@
 \def\ii{\hat{\imath}}
+\def\fkh{\mathfrak{h}}
 \newcommand{\avrd}[1]{\overline{\overline{#1}}}
@@
 Using models based on mixed dimensional PDEs is motivated by the fact that many problems in geo- and biophysics are characterized by slender cylindrical structures coupled to a larger 3D body, where the characteristic transverse length scale of the slender structure is many orders of magnitude smaller than the longitudinal length.
-For example, in geophysical applications the radius of wells are often of the order of 10 cm while the length may be several kilometers~\cite{Peaceman1978183, Peaceman1983531}.
+For example, in geophysical applications the radii of wells are often of the order of 10 cm while the length may be several kilometers~\cite{Peaceman1978183, Peaceman1983531}.
 Similarly, in applications involving the blood flow and oxygen transport of the micro-circulation the capillary radius is a few microns, while simulations are often performed on mm to cm scale, with thousands of vessels~\cite{berg2020modelling,fang2008oxygen,gould2017capillary, secomb2004green}.
@@
 The approach naturally leads to non-symmetric formulations.
-An alternative approach is to decompose the solution into smooth and non-smooth components, where the non-smooth component may be represented in terms of Green functions, and then consider the well-posedness of the smooth component \cite{gjerde2019singularity}.
+An alternative approach is to decompose the solution into smooth and non-smooth components, where the non-smooth component may be represented in terms of Green's functions, and then consider the well-posedness of the smooth component \cite{gjerde2019singularity}.
 The numerical approximation of such equations has been also studied in a series of works.
-The consistent derivation of numerical approximations schemes for PDEs in mixed dimension is addressed in \cite{Nordbotten}.
+The consistent derivation of numerical approximation schemes for PDEs in mixed dimension is addressed in \cite{Nordbotten}.
 Concerning approximability,  elliptic equations with Dirac sources represent an effective prototype case that has been addressed in \cite{Bertoluzza201897,koppl2016local,koppl2014optimal}, where the optimal a-priori error estimates for the finite element approximation are derived.
@@
 Stemming from this literature, in this work we adopt and analyze a different approach, closely related to \cite{KVWZ,laurino_m2an}.
-That is, we exploit the fact that the $\Lambda$ is not strictly a 1D curve, but rather a very thin 3D structure with a cross-sectional area far below what can be resolved.
+That is, we exploit the fact that $\Lambda$ is not strictly a 1D curve, but rather a very thin 3D structure with a cross-sectional area far below from what can be resolved.
 With this additional assumption, we show that robustness with respect to the cross-sectional area can be restored.
@@
 
-Let the domain $\Omega\in \R^3 $ be convex and composed of two parts, 
+Let the domain $\Omega\subset \R^3 $ be convex and composed of two parts, 
 $\Omega_{\ominus}$ and $\Omega_{\oplus}:=\Omega\setminus\overline{\Omega}_{\ominus}$. 
@@
 $\Omega_{\ominus}$ be a \emph{generalized cylinder}, c.f.  \cite{MR1940257}, 
-that is; the swept volume of a two dimensional set, $\partial D$, moved along a curve, $\Lambda$, in the three-dimensional domain, $\Omega$, see for Figure \ref{fig1} for an illustration. 
+that is; the swept volume of a two dimensional set, $\partial\mathcal{D}$, moved along a curve, $\Lambda$, in the three-dimensional domain, $\Omega$, see for Figure \ref{fig1} for an illustration. 
 In detail, the curve 
@@
 and $\Gamma$ be the lateral surface of $\Omega_{\ominus}$, i.e.
-$\Gamma=\{ \ \partial D(s) \  | \ s \in \Gamma\}$,
+$\Gamma=\{ \ \partial \mathcal{D}(s) \  | \ s \in \Gamma\}$,
 while the upper and lower faces of $\Omega_{\ominus}$ belong to $\partial\Omega$. 
@@
 
-\begin{figure}[H]
-\begin{center}
-\includegraphics[width=0.25\textwidth,angle=-90]{./graphics/domain.tex}
-\end{center}
-\caption{Geometrical setting of the problem}
-\label{fig1}
-\end{figure}
-\kent{I think the symbols in the Figure should be bigger}
-
-Let $D$ be a generic regular bounded domain in $\R^3$ and $X$ be a Hilbert space defined on $D$ then  $(\cdot,\cdot)_X$ and $\|\cdot\|_X$ denote the inner product and norm of $X$, respectively.
+Let $D$ be a generic regular bounded domain in $\R^3$ and $X$ be a Hilbert space defined on $D$. Then  $(\cdot,\cdot)_X$ and $\|\cdot\|_X$ denote the inner product and norm of $X$, respectively.
 The duality pairing between the $X$ and its dual $X^*$ is denoted as $\langle\cdot,\cdot\rangle$.
@@
 
-Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. 
-We denote with $\mathcal{T}_\Sigma: H^q(D) \rightarrow H^{q-\frac 1 2}(\Sigma)$ the trace operator from $\Omega$ to $\Sigma$.
-Functions in $H^{\frac 1 2}(\Sigma)$ with continuous extension by zero outside $\Sigma$ is denoted 
+Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. We denote with $\mathcal{T}_\Sigma: H^q(D) \rightarrow H^{q-\frac 1 2}(\Sigma)$ the trace operator from $\Omega$ to $\Sigma$.
+The space of functions in $H^{\frac 1 2}(\Sigma)$ with continuous extension by zero outside $\Sigma$ is denoted 
 $H^{\frac 1 2}_{00}(\Sigma)$ and we remark that 
@@
 
-We will frequently use inner products and norms that are weighted, such that if $X$ is a Hilbert space and $w$ is a positive integrable function, then the
-weighted inner product is denoted 
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=0.35\textwidth,angle=-90]{./graphics/domain.tex}
+\end{center}
+\caption{Geometrical setting of the problem}
+\label{fig1}
+\end{figure}
+
+\kent{
+We will frequently use inner products and norms that are weighted. The
+$L_2$ and $H^1$ inner products
+weighted by a scalar function 
+$w$, which is positive almost everywhere,
+are defined as 
+follows
+\begin{eqnarray*}
+%(u,v)_{\Gamma, w} = 
+(u,v)_{L^2(\Omega), w} &=& 
+\int_{\Omega} w \, u \, v d\omega \\
+%(u,v)_{\Gamma, w} = 
+(u,v)_{H^1(\Omega), w} &=& 
+\int_{\Omega}  w \, u \, v d\omega
++ \int_{\Omega} w \, \nabla u \cdot \nabla v d\omega
+\end{eqnarray*}
+whereas a weighted fractional
+space \miro{$H^s(\Gamma; w)$} is defined in terms of the interpolation of the corresponding weighted spaces. 
+That is, let $S$ denote the
+Riesz map such that 
+for $u, v \in H^1(\Gamma)$ we have 
 \[
-(u,v)_{X,w} = (w \, u,  v)_X
+(S u,v)_{H^1(\Gamma),w} = (u,v)_{L^2(\Gamma), w}.
 \]
-\kent{
-I think we need to be careful when we write this. A reader may believe
-that 
+Then $S$ is a compact self-adjoint operator. 
+Assuming that $\{\lambda_k\}_k$ is the set of eigenvalues, 
+$\{\phi_k\}_k$ the set of eigenvectors orthonormal with respect to the inner 
+product $(\cdot, \cdot)_{L^2(\Gamma), w}$ and $u\in H^1(\Gamma)$ can be expressed 
+as $u=\sum_k c_k \phi_k$ 
+then
 \[
-(u,v)_{1,w} = (\nabla (w \, u),  \nabla v)_1
+\|u\|^2_{H^s(\Gamma), w} = \sum \lambda_k^{-1} c_k^2 .   
 \]
-I will fix this, but I'd like a chat first.
+The space $H_{00}^s(\Gamma; w)$ is defined analogously, but with $S$ above defined in terms of the $H^1_0$ inner product. 
+The weighted spaces equal the corresponding non-weighted spaces as sets, but their norms are different. \miro{Not sure about the last sentence.}
  }
-with a corresponding norm $\|\cdot\|_{X,w}$.
  Finally, $|\cdot|$ denote the Lebesgue measure of a set, i.e.
-$|D(0)|$ is the cross-sectional area of the bottom of the cylinder.
+$|\mathcal{D}(0)|$ is the cross-sectional area of the bottom of the cylinder.
 In the following we assume that the cross-sectional area $\mathcal{D}(s)$ is constant, namely $\mathcal{D}(s)=\mathcal{D}$, but remark that this assumption is only made to simplify the notation.
@@
 The operator obtained from a combination of the average operator $\avrc{(\cdot)}$ with the trace on $\Gamma$ will be denoted with $\mtrace = \avrc{(\cdot)} \circ \trace$, as it maps functions on $\Omega$ to functions on $\Lambda$.
-Further, let the extension operator $\mathcal{E}_{\Gamma}: H^{\frac 1 2}_{00}(\Lambda) \rightarrow H^{\frac 1 2}_{00}(\Gamma)$ be defined such that $(\mathcal{E}_{\Omega_{\ominus}}\vd)(x)=\vd(s)$, for any $x\in \DD(s)$.
-Then, the following identity shows that the transversal uniform extension operator is the inverse of the transversal average.
-
+Further, let the extension operator $\mathcal{E}_{\Gamma}: H^{\frac 1 2}_{00}(\Lambda) \rightarrow H^{\frac 1 2}_{00}(\Gamma)$ be defined such that $(\mathcal{E}_{\miro{\Gamma}}\vd)(x)=\vd(s)$, for any $x\in \DD(s)$.
+Then, the following identity shows that the transversal uniform extension operator is the inverse of the transversal average,
 \begin{equation}\label{eq:ext}
@@
 = \int _{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \trace u \, d\gamma \right) \vd \, ds 
-= \langle \trace u, \ext \vd\rangle_{\Gamma}\,,
+= \langle \trace u, \ext \vd\rangle_{\Gamma}\,.
 \end{equation}
@@
 (\ud,\vd)_{H^1(\Lambda),|\D|} - \langle  \vd, \ld \rangle_{\Lambda, |\DD|} 
-&=  (\avrd{g},V)_{L^2(\Lambda),|\D|}
+&=  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
 &\forall \vd \in H^1_0(\Lambda)\, ,\\
 \langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} &= 0
-&\forall \md \in H^{-\frac 1 2}(\Lambda)\,,
+&\forall \md \in H^{-\frac 1 2}(\Lambda)\,.
 \end{align}
@@
 intermediate problem where the 3D and 1D problems are coupled at an
-intermediate 2D surface  encapsulating the 1D structure. The strong form is:  
+intermediate 2D surface  encapsulating the 1D structure. The strong form is \miro{The strong form does not seem correct}:  
 \begin{subequations}
@@
 \end{subequations}
-
-The corresponding weak formulation of \eqref{inteq:pde}, refered to as the \textbf{Problem 3D-1D-2D}, reads: 
+The corresponding weak formulation of \eqref{inteq:pde}, referred to as the \textbf{Problem 3D-1D-2D}, reads: 
 Find $u \in H^1_0(\Omega), \ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac 1 2}(\Gamma ) $ such that
@@
 
-We conclude this section with the analysis of a fundamental property for the problem formulation that we will address.
-It consists in the characterization of the regularity of the operator $\mtrace$.
+We conclude this section with the analysis of a fundamental property for the problem formulation that we will address, namely, the characterization of the regularity of the operator $\mtrace$.
 More precisely we aim to show that $\mtrace: H^1_0(\Omega) \rightarrow H^\frac 1 2_{00}(\Lambda)$.
@@
 For any regular $u(x,y)$ in $\Gamma$, let $\avrc{u}(x)=\frac 1Y \int _0^Y u(x,y)\, dy$.
-Then, for any $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}(x)\in H_{00}^{\frac 12}((0,X))$.
+Then, for any $u\in H_{00}^{\frac 12}(\Gamma)$, $\avrc{u}(x)\in H_{00}^{\frac 12}((0,X))$.
 Moreover, if $u(x,y)\in H^{\frac 12}_{00}(\Gamma)$ is constant with respect to $y$, namely $u(x,y)=u(x)$, then 
@@
 \end{lemma}
-The proof of \label{lemma:H12norm} is based on the representation of fractional norms in terms of the spectrum of the Laplace operator and subsequent standard arguments in harmonic analysis.
+The proof of \ref{lemma:H12norm} is based on the representation of fractional norms in terms of the spectrum of the Laplace operator and subsequent standard arguments in harmonic analysis.
 The full proof is reported in the appendix for the sake of clarity.
@@
 
-%\begin{corollary}
-%Let $\Gamma$ be the lateral surface of a cylinder of radius $R$.
+% \begin{corollary}
+% Let $\Gamma$ be the lateral surface of a cylinder of radius $R$.
 Let $u\in H^{\frac 12}_{00}(\Gamma)$ and let $\avrc{u}(s)= \frac{1}{2\pi R} \int_0^{2\pi} u(s,\theta)R\, d\theta$.
 Then $\avrc{u}\in H^{\frac 12}_{00}(0,S)$ and there exists a constant $C_\Gamma$ such that
-%\begin{equation*}
-%\|\avrc{u}\|_{H^{\frac 12}(0,S)} \leq C_\Gamma \|u\|_{H^{\frac 12}(\Gamma)}.
-%\end{equation*}
-%\end{corollary}
+% \begin{equation*}
+% \|\avrc{u}\|_{H^{\frac 12}(0,S)} \leq C_\Gamma \|u\|_{H^{\frac 12}(\Gamma)}.
+% \end{equation*}
+% \end{corollary}
 
@@
 \end{equation*}
-\kent{Here, $C_\Gamma$ is bounded independently of $D(s)$.} 
+\kent{Here, $C_\Gamma$ is bounded independently of $\mathcal{D}(s)$.} 
 \end{corollary}
@@
 \begin{aligned}
-a(u,v)+b(v,\lambda)&=c(v),\quad &\forall v\in X,\\
-b(u,\mu)&=d(\mu), \quad &\forall \mu\in Q.
+a(u,v)+b(v,\lambda)&=c(v), &\forall v\in X,\\
+b(u,\mu)&=d(\mu), &\forall \mu\in Q.
 \end{aligned}
@@
 \begin{align}\label{BNB1}
-a(u,u) &\ge \alpha \|u\|^2_{X}, & u\in X\\
+a(u,u) &\ge \alpha \|u\|^2_{X}, & u\in X,\\
 \label{BNB2}
-a(u,v) &\le C \|u\|_{X}\|v\|_{X}, & u,v \in X\\
+a(u,v) &\le C \|u\|_{X}\|v\|_{X}, & u,v \in X,\\
 \label{BNB3}
-b(u,\mu) &\ge D \|u\|_{X} \|\mu\|_{Q}, & u\in X, \mu\in Q\\
+b(u,\mu) &\ge D \|u\|_{X} \|\mu\|_{Q}, & u\in X, \mu\in Q,\\
 \label{BNB4}
-\sup_{v\in X} \frac{b(v,\mu)}{\|v\|_{X}} &\geq \beta\|\mu\|_{Q}, & \mu \in Q .\\
+\sup_{v\in X} \frac{b(v,\mu)}{\|v\|_{X}} &\geq \beta\|\mu\|_{Q}, & \mu \in Q .
 \end{align}
@@
 \begin{align*}
-a([u, \ud], [v, \vd])&= (u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|}
-\\
-b([v, \vd], \mu)&= \langle \trace v - \ext \vd , \mu \rangle_\Gamma
-\\
-c([v,\vd])&= (f,v)_{L^2(\Omega)} + (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
-\\
-d(\mu)&=0
+a([u, \ud], [v, \vd])&= (u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|},
+\\
+b([v, \vd], \mu)&= \langle \trace v - \ext \vd , \mu \rangle_\Gamma,
+\\
+c([v,\vd])&= (f,v)_{L^2(\Omega)} + (\avrd{g},\vd)_{L^2(\Lambda),|\D|},
+\\
+d(\mu)&=0.
 \end{align*}
-We prove that the conditions of Theorem \ref{th:bnb} are fullfilled choosing 
+We prove that the conditions of Theorem \ref{th:bnb} are fulfilled choosing 
 $X=H^1_0(\Omega) \times H^1_0(\Lambda)$, $Q=H^{-\frac 12}(\Gamma)$, where $X$  is equipped with the norm $\vertiii{[u,\ud ]}^2=\|u\|^2_{H^1(\Omega)} + \|\ud\|^2_{H^1(\Lambda),|\D|}$.
-\kent{We should state somewhere that $H^1$ and its weighted space are the same in 
-the sense of set, but that we the parameter dependent norm makes up a cleaner analysis}
+
 \begin{lemma}\label{lemma:prob1_boundedness} 
@@
 We need to establish the four Brezzi conditions. 
-The bilinear form $a(\cdot \ , \ \cdot)$ is clearly bounded and coersive since 
-\begin{equation*}
-a([u, \ud], [v, \vd]) = (u,v)_{H^1(\Omega)} + (\ud, \vd)_{H^1(\Lambda), |\D|}.
+The bilinear form $a(\cdot \ , \ \cdot)$ is clearly bounded and coercive since 
+for $u=\ud$, $v=\vd$
+\begin{equation*}
+a([u, \ud], [v, \vd]) 
+= (u,v)_{H^1(\Omega)} + (\ud, \vd)_{H^1(\Lambda), |\D|}
+= \|u\|^2_{H^1(\Omega)} + \|\ud\|^2_{H^1(\Lambda),|\D|}.
 \end{equation*}
 Furthermore, the bilinear form $b(\cdot \ , \ \cdot)$ is bounded because
-\begin{multline*}
-b([v, \vd], \mu)= \langle \trace v - \ext \vd , \mu \rangle_\Gamma 
+\begin{align*}
+b([v, \vd], \mu)&= \langle \trace v - \ext \vd , \mu \rangle_\Gamma
+% \langle \trace v, \mu\rangle_\Gamma - \langle D\ext \vd , D^{-1}\mu \rangle_\Gamma=
 \leq \|\trace v - \ext \vd\|_{H^{\frac 12}_{00}(\Gamma)}\|\mu\|_{H^{-\frac 12}(\Gamma)}\\
-\leq \left(\|\trace v\|_{H^{\frac 12}_{00}(\Gamma)} + \|\ext \vd\|_{H^{\frac 12}_{00}(\Gamma)}\right)\|\mu\|_{H^{-\frac 12}(\Gamma)}
-\leq \left(C_T \|v\|_{H^1(\Omega)} + \|\ext \vd\|_{H^1(\Gamma)}\right)\|\mu\|_{H^{-\frac 12}(\Gamma)}\\
-\leq \left(C_T \|v\|_{H^1(\Omega)} + \left(\frac{\max |\DD|}{\min |\D|}\right)^{\frac 12} \|\vd\|_{H^1(\Lambda),|\D|}\right)\|\mu\|_{H^{-\frac 12}(\Gamma)}\\
-\leq \left( C_T + \left(\frac{\max |\DD|}{\min |\D|}\right)^{\frac 12}\right) \vertiii{[v,\vd]}\|\mu\|_{H^{-\frac 12}(\Gamma)}
-\end{multline*}
-
-\kent{In the proof of the boundedness above we first
-go $H^{1/2}\rightarrow H^1$. Then $\Gamma\rightarrow\Lambda$. Is this what we want
-? Relation to Corr 2.2 is clearer if we go the other way. Also, if we go the other
-way it is less clear to me that we end up with the $\frac{\max \partial D}{\min D}}$ term. }
-
-To show the inf-sup condition, we will employ a harmonic extension operator. 
-We denote with $\mathcal{H}_\Omega$ the harmonic extension operator defined is $\mathcal{H}_\Omega \xi = v$ where $v$ is the weak solution of
-\begin{equation}\label{eq:harmonic}
--\Delta v=0 \ \text{in} \ \Omega,
-\quad
-v=0 \ \text{on} \ \partial \Omega,
-\quad
-v=\xi \ \text{on} \ \Gamma. 
-\end{equation}
-The boundedness/stability of this operator ensures that there exists $\| \mathcal{H}_\Omega \| \in \mathbb{R}$ such that
-$\|v \|_{H^1(\Omega)}\leq \|\mathcal{H}_\Omega\| \|\xi \|_{H^{\frac 12}_{00}(\Gamma)}$.
+&\leq \left(\|\trace v\|_{H^{\frac 12}_{00}(\Gamma)} + \|\ext \vd\|_{H^{\frac 12}_{00}(\Gamma)}\right)\|\mu\|_{H^{-\frac 12}(\Gamma)} \\
+&\leq \left(C_T \|v\|_{H^1(\Omega)} + \|\ext \vd\|_{H^1(\Gamma)}\right)\|\mu\|_{H^{-\frac 12}(\Gamma)}\\
+&\leq \left(C_T \|v\|_{H^1(\Omega)} + \left(\frac{\max |\DD|}{\min |\D|}\right)^{\frac 12} \|\vd\|_{H^1(\Lambda),|\D|}\right)\|\mu\|_{H^{-\frac 12}(\Gamma)}\\
+&\leq \left( C_T + \left(\frac{\max |\DD|}{\min |\D|}\right)^{\frac 12}\right) \vertiii{[v,\vd]}\|\mu\|_{H^{-\frac 12}(\Gamma)}.
+\end{align*}
+
+\paolo{
+To show the inf-sup condition, we will employ $\mathcal{H}_\Omega$ 
+a lifting operator from $H^{1/2}_{00}(\Gamma)$ to $H^1(\Omega)$.
+Using the results of \cite{sauter1999extension} about extension operators for domains having small geometric details (see also \cite{laurino_m2an} for a direct application to this case) there exists a lifting operator $\mathcal{H}_\Omega$ from $H^{1/2}_{00}(\Gamma)$ to $H^1(\Omega)$ such that $\mathcal{H}_\Omega \xi = v$ for any $\xi \in H^{1/2}_{00}(\Gamma)$ with $v\in H^1(\Omega)$ and the boundedness/stability of this operator ensures that there exists
+$\| \mathcal{H}_\Omega \| \in \mathbb{R}$ such that
+$\|v \|_{H^1(\Omega)}\leq \|\mathcal{H}_\Omega\| \|\xi \|_{H^{1/2}_{00}(\Gamma)}$
+where $\| \mathcal{H}_\Omega \|$ is a constant independent the (minimal) radius of $\Gamma$.
+}
+
+% $\|v \|_{H^1(\Omega)}\leq \|\mathcal{H}_\Omega\| \|\xi \|_{H^{\frac 12}_{00}(\Gamma)}$. 
+% is $\mathcal{H}_\Omega \xi = v$ where $v$ is the weak solution of
+% \begin{equation}\label{eq:harmonic}
+% -\Delta v=0 \ \text{in} \ \Omega,
+% \quad
+% v=0 \ \text{on} \ \partial \Omega,
+% \quad
+% v=\xi \ \text{on} \ \Gamma. 
+% \end{equation}
+% The boundedness/stability of this operator ensures that there exists $\| \mathcal{H}_\Omega \| \in \mathbb{R}$ such that
+% $\|v \|_{H^1(\Omega)}\leq \|\mathcal{H}_\Omega\| \|\xi \|_{H^{\frac 12}_{00}(\Gamma)}$.
 
@@
 We notice that the trace operator is surjective from $H^1_0(\Omega)$ to $H^{\frac12}_{00}(\Gamma)$. Indeed, $\forall \xi \in H^{\frac 12}_{00}(\Gamma)$, 
-we  can find $v=\mathcal{H}_\Omega \xi$ solution of \eqref{eq:harmonic}. Using the stability of the harmonic extension we obtain
+we  can find $v=\mathcal{H}_\Omega \xi$. Using the stability of the harmonic extension we obtain
 \begin{equation}\label{infsup_traceop}
@@
 \begin{align*}
-a([u, \ud], [v, \vd])&= (u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|}
-\\
-b([v, \vd], \md)&=  \langle  \mtrace v - \vd, \md \rangle_{\Lambda, |\DD|} 
-\\
-c([v,\vd])&= (f,v)_{L^2(\Omega)} + (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
-\\
-d(\md)&=0
+a([u, \ud], [v, \vd])&= (u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|},
+\\
+b([v, \vd], \md)&=  \langle  \mtrace v - \vd, \md \rangle_{\Lambda, |\DD|},
+\\
+c([v,\vd])&= (f,v)_{L^2(\Omega)} + (\avrd{g},\vd)_{L^2(\Lambda),|\D|},
+\\
+d(\md)&=0.
 \end{align*}
@@
 The inf-sup condition holds. 
-We choose $\vd=0$ and we obtain
+We choose $\vd=0$ and obtain
 \begin{equation*}
@@
 \end{equation*}
- Therefore,
-\begin{align*}
+ Therefore, we conclude the proof with the following inequalities,
+\begin{multline*}
 \sup _{v\in H^1_0(\Omega)} \frac{ \langle \mtrace v, \md \rangle_{\Lambda,|\DD|}}{\|v\|_{H^1(\Omega)}}
 \geq \sup _{q\in H^{\frac 12}_{00}(\Lambda)} \frac{ \langle q, \md \rangle_{\Lambda,|\DD|}}{\|v\|_{H^1(\Omega)}}
+\\
 \geq \frac{1}{\|\mathcal{H}_\Omega\|} \sup _{q\in H^{\frac 12}_{00}(\Lambda)} \frac{ \langle q, \md \rangle_{\Lambda,|\DD|}}{\|q\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}} 
 = \frac{1}{\|\mathcal{H}_\Omega\|} \|\md\|_{H^{-\frac 12}(\Lambda),|\DD|}.
-\end{align*}
+\end{multline*}
 \end{proof}
@@
 In this section we consider the discretization of the Problems 3D-1D-2D and 3D-1D-1D by means of the finite element method.
-We address two main challenges; first we aim to identify a suitable approximation space for the Lagrange multiplier and to analyze the stability of the discrete saddle point problem; second we aim to derive a stable discretization method that uses independent computational meshes for $\Omega$, $\Gamma$ and $\Lambda$.
-Let us introduce a shape-regular triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{h}$ of $\Lambda$.
-We analyze two different cases: the one in which the 3D mesh is conforming to the interface $\Gamma$, namely the set of the intersections of the 3D elements of $\mathcal{T}^{\Omega}_h$ with $\Gamma$ is constituted by facets of such elements, and the non conforming case, namely the interface $\Gamma$ cuts the mesh arbitrarily.
+We address two main challenges; first we aim to identify a suitable approximation space for the Lagrange multiplier and to analyze the stability of the discrete saddle point problem; second we aim to derive a stable discretization method that uses independent computational meshes for $\Omega$ and $\Lambda$, not necessarily conforming to $\Gamma$.
+Let us introduce a shape-regular triangulation $\mathcal{T}^{\Omega}_h$ of $\Omega$ and an admissible partition $\mathcal{T}^{\Lambda}_{\fkh}$ of $\Lambda$.
+We analyze two different cases: the conforming case, where compatibility constraints are satisfied by $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_{h}$ with respect to $\Gamma$ and consequently $h=\fkh$; and the non conforming case, where it is possible to choose $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_{\fkh}$ arbitrarily.
+
 The discrete equivalent of \eqref{eq:saddle-point} reads as finding $u_h\in X_h\subset X$, $\lambda_h\in Q_h\subset Q$ s.t.
 \begin{eqnarray}\label{eq:saddle-point_discrete}
-\begin{cases}
-a(u_h,v_h)+b(v_h,\lambda_h)=c(v_h)\quad &\forall v_h\in X_h\\
-b(u_h,\mu_h)=d(\mu_h) \quad &\forall \mu_h\in Q_h.
-\end{cases}
+\begin{aligned}
+a(u_h,v_h)+b(v_h,\lambda_h)&=c(v_h) &&\forall v_h\in X_h,\\
+b(u_h,\mu_h)&=d(\mu_h) &&\forall \mu_h\in Q_h,
+\end{aligned}
 \end{eqnarray}
+where with little abuse of notation we use $h$ as the sub-index for all the discretization spaces.
 This discrete problem is well-posed if the \eqref{BNB1}-\eqref{BNB4} conditions applies to $X_h$ and $Q_h$. Since $X_h\subset X$ and $Q_h\subset Q$,  
-\eqref{BNB1}-\eqref{BNB3} follows immediately and only the inf-sup condition needs consideration.  We summarize this in the Corollary below. 
+\eqref{BNB1}-\eqref{BNB3} follow immediately and only the inf-sup condition needs consideration.  We summarize this proposition in the Corollary below. 
 \begin{corollary}{\cite[Theorem 2.42]{MR2050138}}\\
@@
 the problem \eqref{eq:saddle-point_discrete} is well-posed if 
-the discrete counterpart of \eqref{BNB4} is satisfied, ie., 
-there exists a $\beta_h>0$ such that
+the discrete counterpart of \eqref{BNB4} is satisfied, i.e.
+there exists a constant $\beta_h>0$ such that
 \begin{align}
 \label{eq:infsup_discrete}
- \sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}}\geq \beta_h |\mu_h\|_{Q}\, .
+ \sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}}\geq \beta_h \|\mu_h\|_{Q}\, .
 \end{align}
@@
 
-\subsection{$\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}
- We first analyze the case in which the 3D mesh is conforming to the interface $\Gamma$.
-As conformity conditions between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$ with $\Gamma$ , we require that the intersection of $\mathcal{T}^{\Omega}_h$ and $\Gamma$ is made of entire faces of elements $K \in \mathcal{T}^{\Omega}_h$.
-Furthermore, we also set a restriction between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_h$.
+\subsection{Analysis of the case where $\mathcal{T}^{\Omega}_h$ conforms to $\mathcal{T}^{\Lambda}_\fkh$ and to $\Gamma$}
+As conformity conditions between $\mathcal{T}^{\Omega}_h$, $\mathcal{T}^{\Lambda}_\fkh$ and $\Gamma$, we require that the intersection of $\mathcal{T}^{\Omega}_h$ and $\Gamma$ is made of entire faces of elements $K \in \mathcal{T}^{\Omega}_h$.
+Furthermore, we also set a restriction between $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_\fkh$.
 We assume that $\Lambda$ is a piecewise linear manifold.
-We want that the intersection of $\Gamma$ with any orthogonal plane to $\Lambda$ that crosses $\Lambda$ at the internal nodes of $\mathcal{T}^{\Lambda}_h$, consists of entire edges of $\mathcal{T}^{\Omega}_h$.
+We want that the intersection of $\Gamma$ with any orthogonal plane to $\Lambda$ that crosses $\Lambda$ at the internal nodes of $\mathcal{T}^{\Lambda}_\fkh$, consists of entire edges of $\mathcal{T}^{\Omega}_h$.
+As a result of the latter condition we have $h=\fkh$.
+For this reason, we denote as $\mathcal{T}^{\Lambda}_h$ the mesh on $\Lambda$
+from now on throughout this section.
 
@@
 We denote by $X_{h,0}^k(\Omega)\subset H^1_0(\Omega)$, with $k>0$, the conforming finite element space of continuous piecewise polynomials of degree $k$ defined on $\Omega$ satisfying homogeneous Dirichlet conditions on the boundary and by $X_{h,0}^k(\Lambda)\subset H^1_0(\Lambda)$ the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$, satisfying homogeneous Dirichlet conditions on $\Lambda \cap \partial \Omega$.
-
-The discrete version of Problem 1 is:
+The space $Q_h$ must be suitably chosen such that \eqref{eq:infsup_discrete} holds.
+Let $Q_h$ be the trace space of $X_{h,0}^k(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$.
+As a result, $Q_h=X_{h,0}^k(\Gamma) \subset H^\frac12_{00}(\Gamma)$.
+The discrete version of the 3D-1D-2D problem is:
 find $u_h \in X_{h,0}^k (\Omega) ,\, {\ud}_h \in X_{h,0}^k(\Lambda) ,\, \lambda_h \in Q_h \subset H^{-\frac12}(\Gamma )$, such that
@@
 &(u_h,v_h)_{H^1(\Omega)} + ({\ud}_h,{\vd}_h)_{H^1(\Lambda),|\D|}
-+ \langle \trace v_h  - \mathcal{E}_{\Lambda} {\vd}_h, \lambda_h \rangle_\Gamma &&
++ \langle \trace v_h  - \mathcal{E}_{\Lambda} {\vd}_h, \lambda_h \rangle_\Gamma
 \\
 \nonumber
-&\qquad= (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda),|\D|}
-\quad && \forall v_h \in X_{h,0}^k(\Omega), \ {\vd}_h \in X_{h,0}^k(\Lambda)
-\\
-&   \langle \trace u_h - \mathcal{E}_{\Lambda} {\ud}_h , \mu_h \rangle_\Gamma = 0
-\quad && \forall \mu_h \in Q_h\,,
+&\quad = (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda),|\D|} 
+\quad \forall v_h \in X_{h,0}^k(\Omega), \ {\vd}_h \in X_{h,0}^k(\Lambda)\,,
+\\
+&\langle \trace u_h - \mathcal{E}_{\Lambda} {\ud}_h , \mu_h \rangle_\Gamma = 0
+\quad \forall \mu_h \in Q_h\,.
 \end{align}
 \end{subequations}
-The space $Q_h$ must be suitably chosen such that \eqref{eq:infsup_discrete} holds.
-Let $Q_h$ be the trace space of $X_{h,0}^k(\Omega)$, namely the space of continuous piecewise polynomials of degree $k$ defined on $\Gamma$ which satisfy homogeneous Dirichlet conditions on $\partial \Omega$.
-As a result, $Q_h=X_{h,0}^k(\Gamma) \subset H^\frac12_{00}(\Gamma)$.
-Therefore we impose homogeneous Dirichlet boundary condition on $\partial \Omega$ also for the Lagrange multiplier.
-For this choice of $Q_h$ we prove the well-posedness of the discrete problem, as shown in the following.
+In what follows we analyze the well-posedness of the discrete problem. 
+From now on, $C$ denotes a generic constant independent of the mesh size.
 
@@
 Let $P_h: H^{\frac 12}_{00}(\Gamma) \rightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Gamma)$ by
-\begin{equation*}
-(P_h v , \psi_h)_\Gamma= (v, \psi_h)_\Gamma \qquad \forall \psi_h \in Q_h.  
-\end{equation*} 
+$(P_h v , \psi_h)_\Gamma= (v, \psi_h)_\Gamma$ for any $\psi_h \in Q_h$.
 Then, $P_h$ is continuous on $H^{\frac 12}_{00}(\Gamma)$, namely
-\begin{equation}\label{continuity_projoper}
-\|P_h v\|_{H^{\frac 12}_{00}(\Gamma)} \leq C \|v\|_{H^{\frac 12}_{00}(\Gamma)},
-\end{equation}
-where $C$ is a positive constant independent of $h$.
+$\|P_h v\|_{H^{\frac 12}_{00}(\Gamma)} \leq C \|v\|_{H^{\frac 12}_{00}(\Gamma)}$.
 \end{lemma}
+
 \begin{proof}
-We prove that $P_h$ is continuous on $L^2(\Gamma)$ and on $H^1_0(\Gamma)$ following \cite[Section 1.6.3]{MR2050138}.
-Then, the inequality \eqref{continuity_projoper} can be derived by interpolation between spaces, since $H^\frac12_{00}(\Gamma)$ can be seen as the interpolation space between $L^2(\Gamma)$ and $H^1_0(\Gamma)$.
+We show that $P_h$ is continuous on $L^2(\Gamma)$ and on $H^1_0(\Gamma)$ following \cite[Section 1.6.3]{MR2050138}.
+Then, Lemma \ref{lemma:prob1_orthproj} can be proved by interpolation between spaces, since $H^\frac12_{00}(\Gamma)$ can be seen as the interpolation space between $L^2(\Gamma)$ and $H^1_0(\Gamma)$.
 For the $L^2$-continuity, we exploit the fact that, from the definition of $P_h$, $(v-P_h v,P_h v)_{\Gamma}=0$.
@@
 \end{equation*}
-Let us now consider $v\in H^1_0(\Gamma)$.The Scott-Zhang interpolation operator $SZ_h$ from $H^1_0(\Gamma)$ to $Q_h$ satisfies the following inequalities,
+Let us now consider $v\in H^1_0(\Gamma)$. The Scott-Zhang interpolation operator $SZ_h$ from $H^1_0(\Gamma)$ to $Q_h$ satisfies the following inequalities,
 \begin{align}
 \label{SZ_stability}
-\|SZ_h v\|_{H^1(\Gamma)} &\leq C_1 \|v\|_{H^1(\Gamma)}
+\|SZ_h v\|_{H^1(\Gamma)} &\leq C_1 \|v\|_{H^1(\Gamma)},
 \\
@@
 \end{align}
-Therefore, using \eqref{SZ_stability},
-\begin{equation*}
-\begin{split}
+Therefore, using \eqref{SZ_stability}, \eqref{SZ_approx}, 
+the $L^2$ stability of $P_h$ and the inverse inequality, we obtain,
+\begin{multline*}
 \|\nabla P_h v\|_{L^2(\Gamma)} 
-&\leq \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + \|\nabla SZ_h v\|_{L^2(\Gamma)}\\
-&\leq  \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
-\end{split}
-\end{equation*}
-and by using the inverse inequality we obtain
-\begin{equation*}
-\begin{split}
-\|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
-&\leq \frac{C_3}{h} \|P_h v - SZ_h v\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
-&= \frac{C_3}{h} \|P_h (v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
-&\leq  \text{ (Stability of $P_h$ in $L^2$) } \frac{C_3}{h} \|v - SZ_h v\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
-&\leq \text{ (using \eqref{SZ_approx}) } \frac{C_3}{h} C_2 h  \| v\|_{H^1(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}\\
-&\leq (C_2 C_3 +C_1) \|v\|_{H^1(\Gamma)},
-\end{split}
-\end{equation*}
+\leq \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + \|\nabla SZ_h v\|_{L^2(\Gamma)}
+\\
+\leq  \|\nabla (P_h v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
+% \leq \frac{C_3}{h} \|P_h v - SZ_h v\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
+= \frac{C_3}{h} \|P_h (v - SZ_h v)\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
+\\
+\leq \frac{C_3}{h} \|v - SZ_h v\|_{L^2(\Gamma)} + C_1\|v\|_{H^1(\Gamma)}
+\leq (C_2 C_3 +C_1) \|v\|_{H^1(\Gamma)},
+\end{multline*}
 from which we obtain the continuity in $H^1_0(\Gamma)$.
 \end{proof}
+
 \begin{lemma}\label{lemma:trspace_infsup} 
@@
 \end{lemma}
+
 \begin{proof}
-Let $\mu_h$ be in $Q_h$. From the continuous case, in particular from \eqref{infsup_traceop}, we have
+From the continuous case, in particular from \eqref{infsup_traceop}, we have
 \begin{equation*}
 \|\mathcal{H}_\Omega\|^{-1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \leq \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle \trace v , \mu_h \rangle}{\|v\|_{H^1(\Omega)}} 
+\quad \forall \mu_h \in Q_h,
 \end{equation*}
@@
 \end{equation*}
-By the definition of $P_h$ and \eqref{continuity_projoper} 
+Using Lemma \ref{lemma:prob1_orthproj} we obtain,
 \begin{multline*}
@@
 \\
-\leq  C_T C \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(\trace v) , \mu_h \rangle}{ \|P_h(\trace v)\|_{H^{\frac 12}_{00}(\Gamma)}}
-= C_T C \sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , \mu_h \rangle}{  \|q_h\|_{H^{\frac 12}_{00}(\Gamma)}}.
+\leq  C \sup_{\substack{v \in H^1_0(\Omega)}} \frac{\langle P_h(\trace v) , \mu_h \rangle}{ \|P_h(\trace v)\|_{H^{\frac 12}_{00}(\Gamma)}}
+= C \sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , \mu_h \rangle}{  \|q_h\|_{H^{\frac 12}_{00}(\Gamma)}}.
 \end{multline*}
@@
 
-\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds true, namely 
-$\exists \beta_{h,1} >0$ s.t.
+\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds true, 
+namely there exists a positive constant $\beta_{h,1}$ such that,
 \begin{equation}\label{inf_sup_discrete_prob1}
@@
 \begin{proof}
-Let $\mu_h \in Q_h$. As in the continuos case, we choose ${\vd}_h =0$ and we have
+As in the continuos case, we choose ${\vd}_h =0$ and we have
 \begin{equation*}
@@
 \end{equation*}
-
-Therefore, we want to prove that there exists $\beta_{h,1}$ such that
-\begin{equation*}
-\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \trace v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}} \geq \beta_{h,1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \qquad \forall \mu_h \in Q_h.
-\end{equation*}
-
+% Therefore, we want to prove that there exists $\beta_{h,1}$ such that
+% \begin{equation*}
+% \sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \trace v_h, \mu_h \rangle _{\Gamma} } {\|v_h\|_{H^1(\Omega)}} \geq \beta_{h,1} \|\mu_h\|_{H^{-\frac 12}(\Gamma)} \qquad \forall \mu_h \in Q_h.
+% \end{equation*}
 Using Lemma \ref{lemma:trspace_infsup} and the boundedness of the harmonic extension operator $\mathcal{H}_\Omega$ from $H^{\frac 12}_{00}(\Gamma)$ to $H^1_0(\Omega)$ introduced in the previous section, we have
@@
 Let $R_h: H^1_0(\Omega) \rightarrow X_{h,0}^k(\Omega)$ be a quasi interpolation operator (such as the Scott-Zhang operator) satisfying 
-\begin{equation*}
-\|R_h v\|_{H^1(\Omega)} \leq C_R \|v\|_{H^1(\Omega)} \qquad \forall v \in H^1_0(\Omega).
-\end{equation*}
+$\|R_h v\|_{H^1(\Omega)} \leq C_R \|v\|_{H^1(\Omega)}$ for any  $v \in H^1_0(\Omega)$.
 Therefore, we obtain 
@@
 \leq
-\|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|R_h \mathcal{H}_{\Omega} q_h\|_{H^1(\Omega)}}
-\end{equation*}
-and we have
-\begin{multline}\label{eq_conformity}
+\|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, \mu_h \rangle _{\Gamma} } {\|R_h \mathcal{H}_{\Omega} q_h\|_{H^1(\Omega)}}\,.
+\end{equation*}
+Now we use the conformity of $\mathcal{T}^{\Omega}_h$ to the interface $\Gamma$
+to guarantee that the operator $\trace R_h  \mathcal{H}_{\Omega}$ coincides with the identity on the space $Q_h$. Then, for any $q_h \in Q_h$ we have $q_h = \trace R_h  \mathcal{H}_{\Omega} q_h$
+and owing to this property we obtain the following inequality, which proves the thesis with $\beta_{h,1} = \gamma \|\mathcal{H}_{\Omega}\|^{-1} C_R^{-1}$,
+\begin{multline*}
 \gamma \|\mu_h\|_{H^{-\frac 12}(\Gamma)} 
@@
 \|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle \trace R_h  \mathcal{H}_{\Omega}q_h, \mu_h \rangle_{\Gamma} } {\|R_h \mathcal{H}_{\Omega} q_h\|_{H^1(\Omega)}} 
-\leq \|\mathcal{H}_{\Omega}\| C_R \sup_{v_h \in X_{h,k}(\Omega)} \frac{ \langle \trace v_h, \mu_h \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}. 
-\end{multline}
-Therefore the inf-sup condition $\eqref{inf_sup_discrete_prob1}$ holds with $\beta_{h,1} = \gamma \|\mathcal{H}_{\Omega}\|^{-1} C_R^{-1} $.
-We notice that in \eqref{eq_conformity} we exploit the fact that the operator $\trace R_h  \mathcal{H}_{\Omega}$ coincides with the identity on the space $Q_h$, thanks to the conformity of $\mathcal{T}^{\Omega}_h$ to the interface $\Gamma$.
+\leq \|\mathcal{H}_{\Omega}\| C_R \sup_{v_h \in X_{h,k}(\Omega)} \frac{ \langle \trace v_h, \mu_h \rangle_{\Gamma} } {\|v_h\|_{H^1(\Omega)}}\,. 
+\end{multline*}
 \end{proof}
@@
 \subsubsection{Problem 3D-1D-1D}
-We aim to find  $u_h \in X_{h,0}^k(\Omega) ,\ {\ud}_h \in X_{h,0}^k(\Lambda), \ {\ld}_h \in Q_h \subset H^{-\frac12}(\Lambda)$, such that
+In this case, we use the same spaces $X_{h,0}^k(\Omega)$, $X_{h,0}^k(\Lambda)$ defined previously.
+For the multiplier space we choose $Q_h=X_{h,0}^k(\Lambda)$, therefore we impose homogeneous Dirichlet boundary condition on $\Lambda \cap \partial \Omega$ also for the Lagrange multiplier. 
+We aim to find  $u_h \in X_{h,0}^k(\Omega) ,\ {\ud}_h \in X_{h,0}^k(\Lambda), \ \ldh \in Q_h \subset H^{-\frac12}(\Lambda)$, such that
 \begin{subequations}
@@
 &(u_h,v_h)_{H^1(\Omega)} + ({\ud}_h,{\vd}_h)_{H^1(\Lambda), |{\cal D}|} 
-+  \langle  \mtrace v_h -  {\vd}_h, {\ld}_h \rangle_{\Lambda, |\DD|} 
++  \langle  \mtrace v_h -  {\vd}_h, \ldh \rangle_{\Lambda, |\DD|} 
 \\
 \nonumber
-&\qquad\qquad= (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda), |{\cal D}|}
-\quad \forall v_h \in X_h(\Omega), \ {\vd}_h \in X_h(\Lambda)
-\\
-&  \langle \mtrace u_h - {\ud}_h, {\md}_h \rangle_{\Lambda,| \DD| } = 0
-\quad \forall {\md}_h \in Q_h\,.
+&\quad = (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda), |{\cal D}|}
+\quad \forall v_h \in X_h(\Omega), \ {\vd}_h \in X_h(\Lambda)\,,
+\\
+& \langle \mtrace u_h - {\ud}_h, \mdh \rangle_{\Lambda,| \DD| } = 0
+\quad \forall \mdh \in Q_h\,.
 \end{align}
 \end{subequations}
-
-%We introduce the space
-%$W_{h,0}^k(\Lambda) \subset H^{\frac 12} _{00} (\Lambda)$, which is the averaged trace space of functions running in $X_{h,0}^k(\Omega)$.
-It coincides with the space of continuous piecewise polynomials of degree $k$ defined on $\Lambda$ and satisfying homogeneous Dirichlet boundary condition, namely $X_{h,0}^k(\Lambda)$.
-We choose $Q_h=X_{h,0}^k(\Lambda)$, therefore we impose homogeneous Dirichlet boundary condition on $\Lambda \cap \partial \Omega$ also for the Lagrange multiplier.
-With this choice for $Q_h$, we can prove the well-posedness of the discrete problem.
-In particular, following the same steps as for Problem 1, we can prove the following results.
+Below we address the well-posedness of the 3D-1D-1D discrete problem with this alternative choice of multiplier space.
 
 \begin{lemma}\label{lemma:prob2_orthproj}
-Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by
-\begin{equation*}
-(P_h v , \psi)_{\Lambda,|\DD|}= (v, \psi)_{\Lambda , |\DD|} \qquad \forall \psi \in Q_h.  
-\end{equation*} 
+Let $P_h: H^{\frac 12}_{00}(\Lambda) \longrightarrow Q_h$ be the orthogonal projection operator defined  for any $v \in H^{\frac 12}_{00}(\Lambda)$ by $(P_h v , \psi)_{\Lambda,|\DD|}= (v, \psi)_{\Lambda , |\DD|} \qquad \forall \psi \in Q_h$.
 Then, $P_h$ is continuous on $H^{\frac 12}_{00}(\Lambda)$, namely
-\begin{equation*}
-\|P_h v\|_{H^{\frac 12}_{00}(\Lambda),|\DD|} \leq C \|v\|_{H^{\frac 12}_{00}(\Lambda),|\DD|},
-\end{equation*}
-where $C$ is a positive constant independent of $h$.
+$\|P_h v\|_{H^{\frac 12}_{00}(\Lambda),|\DD|} \leq C \|v\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}$.
 \end{lemma}
@@
 \begin{lemma}\label{infsup_avr_trspace}
-There exist a constant $\gamma >0$ such that
-\begin{equation*}
-\sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , {\md}_h \rangle_{\Lambda, |\DD|}}{ \|q_h\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}} \geq \gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \qquad \forall {\md}_h \in Q_h.
+There exist a constant $\gamma >0$ such that for any $\mu_h \in Q_h$,
+\begin{equation*}
+\sup_{\substack{q_h \in Q_h}} \frac{\langle q_h , \mdh \rangle_{\Lambda, |\DD|}}{ \|q_h\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}} \geq \gamma \|\mdh\|_{H^{-\frac 12}(\Lambda)}\,.
 \end{equation*} 
@@
 
-The proofs follow the ones of Lemmas \ref{lemma:prob1_orthproj} and \ref{lemma:trspace_infsup} with the only difference that the arguments are applied to $\Lambda$ instead of $\Gamma$.
-
-\begin{theorem}[Discrete inf-sup] The inequality \eqref{eq:infsup_discrete} holds, namely 
-$\exists \beta_{h,2} >0$ s.t.
+The proofs of these Lemmas follow the ones of Lemmas \ref{lemma:prob1_orthproj} and \ref{lemma:trspace_infsup} with the only difference that the arguments are applied to $\Lambda$ instead of $\Gamma$.
+
+\begin{theorem}[Discrete inf-sup] 
+The inequality \eqref{eq:infsup_discrete} holds, 
+namely there exists a positive constant $\beta_{h,2}$ such that,
 \begin{equation}
 \inf_{\mu_h \in Q_h} 
-\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)} }\frac{\langle \mtrace v_h -  {\vd}_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\vertiii{[v_h, {\vd}_h]} \|{\md}_h\|_{H^{-\frac 12 }(\Lambda)} }
+\sup_{\substack{v_h \in X_{h,0}^k(\Omega),\\ {\vd}_h \in X_{h,0}^k(\Lambda)} }\frac{\langle \mtrace v_h -  {\vd}_h, \mdh \rangle _{\Lambda,|\DD|} } {\vertiii{[v_h, {\vd}_h]} \|\mdh\|_{H^{-\frac 12 }(\Lambda)} }
 \geq \beta_{h,2}. 
@@
 \begin{proof}
- Again, we choose ${\vd}_h =0$, so that the proof reduces to show that there exists $\beta_{h,2}$ such that
-\begin{equation*}
-\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \mtrace v_h , {\md}_h \rangle _{\Lambda,|\DD|} } {\|v_h\|_{H^1(\Omega)} }\geq \beta_{h,2} \|{\md}_h\|_{H^{-\frac 12}(\Lambda)}\ \qquad \forall {\md}_h \in Q_h.
-\end{equation*}
-From Lemma \ref{lemma:H12norm} and its corollaries, for any $w \in H^{\frac 12}(\Lambda) \ 
-\|\ext w\|_{H^{\frac 12}_{00}(\Gamma)}= \|w\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}$.
-
-Consequently, from Lemma \ref{infsup_avr_trspace}, using again the extension operator $\mathcal{H}_{\Omega}$ from $H^{\frac 12}_{00}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$, we obtain
-\begin{multline}
-\gamma \|{\md}_h\|_{H^{-\frac 12}(\Lambda)} \leq 
-\sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}} 
-%
-=  \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda,|\DD|}} {\|\ext q_h\|_{H^{\frac 12}_{00}(\Gamma)}} 
-\leq \|\mathcal{H}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\|\mathcal{H}_{\Omega} \ext q_h\|_{H^1(\Omega)}} 
-\\
-\leq \|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle q_h, {\md}_h \rangle _{\Lambda,|\DD|} } {\|R_h \mathcal{H}_{\Omega} \ext q_h\|_{H^1(\Omega)}}
-%
-=  \|\mathcal{H}_{\Omega}\| C_R \sup_{q_h \in Q_h} \frac{ \langle 	\mtrace R_h \mathcal{H}_{\Omega} \ext q_h, {\md}_h \rangle _{\Lambda,|\DD|}} {\|R_h \mathcal{H}_{\Omega} \ext w_h\|_{H^1(\Omega)}}
-\\
-\leq \|\mathcal{H}_{\Omega}\| C_R \sup_{v_h \in X_h(\Omega)} \frac{ \langle \mtrace v_h, {\md}_h \rangle _{\Lambda,|\DD|}} {\|v_h\|_{H^1(\Omega)}}. 
-\end{multline}
-Also in this case to prove the disrete inf-sup condition we exploit the conformity of the meshes on $\Omega$, $\Gamma$ and $\Lambda$ and the fact that the operator $\mtrace R_h \mathcal{H}_{\Omega} \ext$ coincides with the identity if applied to functions in $Q_h$.
+ Again, we choose ${\vd}_h =0$, so that the proof reduces to showing that there exists $\beta_{h,2}$ such that
+\begin{equation*}
+\sup_{v_h \in X_{h,0}^k(\Omega)} \frac{ \langle \mtrace v_h , \mdh \rangle _{\Lambda,|\DD|} } {\|v_h\|_{H^1(\Omega)} }\geq \beta_{h,2} \|\mdh\|_{H^{-\frac 12}(\Lambda)} 
+\quad \forall \mdh \in Q_h.
+\end{equation*}
+For any $w \in H^{\frac 12}(\Lambda)$, Lemma \ref{lemma:H12norm} ensures that 
+$\|\ext w\|_{H^{\frac 12}_{00}(\Gamma)} = \|w\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}$.
+As in the previous case, we use the extension operator $\mathcal{H}_{\Omega}$ from $H^{\frac 12}_{00}(\Gamma)$ to $H^1_0(\Omega)$ and the quasi interpolation operator $R_h$ from $H^1_0(\Omega)$ to $X_{h,0}^k(\Omega)$.
+Then, we exploit the conformity of the meshes on $\Omega$, $\Gamma$ and $\Lambda$ and the fact that the operator $\mtrace R_h \mathcal{H}_{\Omega} \ext$ coincides with the identity if applied to functions in $Q_h$.
+As a result, from Lemma \ref{infsup_avr_trspace}, we obtain the following inequality
+\begin{multline*}
+\gamma \|\mdh\|_{H^{-\frac 12}(\Lambda)} \leq 
+\sup_{q_h \in Q_h} \frac{ \langle q_h, \mdh \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}} 
+=  \sup_{q_h \in Q_h} \frac{ \langle q_h, \mdh \rangle _{\Lambda,|\DD|}} {\|\ext q_h\|_{H^{\frac 12}_{00}(\Gamma)}} 
+\\
+\leq \|\mathcal{H}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mdh \rangle _{\Lambda,|\DD|} } {\|\mathcal{H}_{\Omega} \ext q_h\|_{H^1(\Omega)}} 
+\leq C_R\|\mathcal{H}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mdh \rangle _{\Lambda,|\DD|} } {\|R_h \mathcal{H}_{\Omega} \ext q_h\|_{H^1(\Omega)}}
+\\
+=  C_R\|\mathcal{H}_{\Omega}\|\sup_{q_h \in Q_h} \frac{ \langle \mtrace R_h \mathcal{H}_{\Omega} \ext q_h, \mdh \rangle _{\Lambda,|\DD|}} {\|R_h \mathcal{H}_{\Omega} \ext w_h\|_{H^1(\Omega)}}
+\leq C_R\|\mathcal{H}_{\Omega}\| \sup_{v_h \in X_{h,0}^k} \frac{ \langle \mtrace v_h, \mdh \rangle _{\Lambda,|\DD|}} {\|v_h\|_{H^1(\Omega)}}\,,
+\end{multline*}
+that concludes the proof with $\beta_{h,2} = \gamma \|\mathcal{H}_{\Omega}\|^{-1} C_R^{-1}$.
 \end{proof}
@@
 \def\patch{\omega _j}
-\subsection{$\mathcal{T}^{\Omega}_\mathbb{H}$ non conforming to $\Gamma$ and $\Lambda$} \label{sec:unfit2}
-We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_\mathcal{h}$,
-$\mathcal{T}^{\Omega}_\mathfrak{H}$,
-$\mathcal{T}^{\Omega}_\mathbf{H}$
-$\mathcal{T}^{\Omega}_\mathfrak{h}$do not conform with the surface $\Gamma$ nor with $\Lambda$. In this case, the 3D-1D-1D
-formulation, namely Problem 3D-1D-1D, is more suitable. 
-%{\color{red} Add more details, we can refer also to cutFEM (Burman, Massing etc.) explaining the limitation of that approach (network case for example).}\\
-Therefore we focus on the analysis of this discretization approach for Problem 2 solely.
-
-\subsubsection{Problem 3D-1D-1D} We consider for the solutions $u_h$ and ${\ud}_h$ the spaces $X_h = X_{h,0}^1(\Omega) \times X_{h^\prime,0}^1(\Lambda)$.
-With little abuse of notation, we assume that the characteristic mesh size of the 3D mesh $\mathcal{T}^{\Omega}_h$ and the one of the 1D mesh $\mathcal{T}^{\Lambda}_{h'}$ are different.
+\subsection{Analysis of the case where $\mathcal{T}^{\Omega}_h$ and $\mathcal{T}^{\Lambda}_\fkh$ do not conform to $\Gamma$} \label{sec:unfit2}
+We analyze now the case in which the elements of the 3D mesh $\mathcal{T}^{\Omega}_h$
+do not conform with the surface $\Gamma$ nor with $\Lambda$. 
+As the 3D-1D-1D formulation is more suitable for this purpose,
+we solely focus on the analysis of the discrete version of Problem 3D-1D-1D.
+
+\subsubsection{Problem 3D-1D-1D} 
+Let $u_h \in X_{h,0}^1(\Omega)$ be the approximation of the 3D problem
+and let $\udfh \in X_{\fkh,0}^1(\Lambda)$ the one of the 1D problem.
+In contrast to the conforming case, 
+here we limit the analysis to the case of piecewise-linear finite elements. 
+With little abuse of notation, we use the sub-index $h$ for the product space 
+$X_h = X_{h,0}^1(\Omega) \times X_{\fkh,0}^1(\Lambda)$.
 Concerning the multiplier space, let $\mathcal{G}_h = \{K \in \mathcal{T}^{\Omega}_h: \, K\cap \Lambda \neq \emptyset\}$, be the set of the 3D elements that intersect $\Lambda$.
-Then we define $Q_h=\{{\ld}_h : {\ld}_h \in P^0(K) \, \forall K \in \mathcal{G}_h\}$.
+Then we define $Q_h=\{\ldh : \ldh \in P^0(K) \, \forall K \in \mathcal{G}_h\}$.
 We notice that the multiplier functions are defined on the 3D elements.
-With little abuse of notation, we denote with $Q_h$ also the restriction to $\Lambda$ of the space of piecewise constant functions defined in 3D.
+Again with a little abuse of notation, we denote with $Q_h$ also the restriction to $\Lambda$ of the space of piecewise constant functions defined in 3D.
 As a result, we have $Q_h \subset L^2(\Lambda) \subset H^{-\frac12}(\Lambda)$.
-With this choice of multipliers the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s({\ld}_h, {\md}_h): \ Q_h \times Q_h \rightarrow \mathbb{R}$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}.
-The objective of this section is to analyze the stabilized version of the 3D-1D-1D problem: find $[u_h, {\ud}_h] \in X_h$ and ${\ld}_h \in Q_h$ such that
+However, with this choice of multipliers the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s(\ldh, \mdh): \ Q_h \times Q_h \rightarrow \mathbb{R}$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}.
+The objective of this section is to analyze the stabilized version of the 3D-1D-1D problem: find $[u_h, {\ud}_h] \in X_h$ and $\ldh \in Q_h$ such that
 \begin{multline}\label{eq:prob2_stabilized}
-a([u_h, {\ud}_{\mathfrak{h}}], [v_h, {\vd}_h]) +
-b([v_h, {\vd}_h], {\ld}_h)
-+ b([u_h, {\ud}_h], {\md}_h)
-- s({\ld}_h, {\md}_h) 
-= c(v_h) + d({\md}_h)\\
-  \quad \forall [v_h, {\vd}_h] \in X_h, \,
-  \forall {\md}_h \in Q_h\,.
+a([u_h, \udfh], [v_h, \vdfh]) +
+b([v_h, \vdfh], \ldh)
++ b([u_h, \udfh], \mdh)
+\\
+- s_h(\ldh, \mdh) 
+= c(v_h) + d(\mdh)
+  \quad \forall [v_h, \vdfh] \in X_h, \,
+  \forall \mdh \in Q_h\,.
 \end{multline}
@@
 is to identify a new multiplier space $Q_H$, which is never implemented in practice, such that inf-sup stability with $X_h$ holds true.
-Then, the stabilization operator is designed to control the distance between $Q_h$ and $Q_H$ trough the following inequality
-\begin{equation*}
-    \|{\md}_h - \pi_H {\md}_h\|_{Q_H} \leq C s_h({\md}_h, {\md}_h)\,,
+Then, the stabilization operator is designed to control the distance between $Q_h$ and $Q_H$ through the following inequality
+\begin{equation*}
+    \|\mdh - \pi_H \mdh\|_{Q_H} \leq C s_h(\mdh, \mdh)\,,
 \end{equation*}
 being $\pi_H$ a suitable projection operator $Q_h \rightarrow Q_H$.
-Applying the results obtained in \cite{burman2014} we will show that the well posedness of problem \eqref{eq:prob2_stabilized} is governed by the following lemma.
+Applying the results obtained in \cite{burman2014}, the well posedness of problem \eqref{eq:prob2_stabilized} is governed by the following lemma.
 \begin{lemma}[Lemma 2.3 of \cite{burman2014}]\label{lemma23burman}
@@
     \item If the $b(\cdot,\cdot),\, X_h,Q_H \rightarrow \R$ is inf-sup stable.
-    \item If the stabilization operator $s_h(\cdot,\cdot),\, Q_H,Q_H \rightarrow \R$ is such that
-    \begin{equation*}
-        \beta \|{\md}_h\|_{H^{-\frac12}(\Lambda)} \leq \sup\limits_{v_h \in X_h} \frac{b(v_h,{\md}_h}{\vertiii{v_h})} + s_h({\md}_h, {\md}_h), \quad \forall {\md}_h \in Q_h\,.
-    \end{equation*}
-    \item If for any $[v_h, {\vd}_h]$ there exists a function $\xi_h\in Q_h$ depending on $[v_h, {\vd}_h]$, namely $\xi_h=\xi_h([v_h, {\vd}_h])$, s.t.
+    \item If the stabilization operator $s_h(\cdot,\cdot),\, Q_h,Q_h \rightarrow \R$ is such that
+    \begin{equation*}
+        \beta \|\mdh\|_{H^{-\frac12}(\Lambda)} \leq \sup\limits_{v_h \in X_h} \frac{b(v_h,\mdh)}{\vertiii{v_h}} + s_h(\mdh, \mdh), \quad \forall \mdh \in Q_h\,.
+    \end{equation*}
+    \item If for any $[v_h, \vdfh] \in X_h$ there exists a function $\xi_h\in Q_h$ depending on $[v_h, \vdfh]$, namely $\xi_h=\xi_h([v_h, \vdfh])$, s.t.
 \begin{gather}
 \label{stab_coercivity}
-a([v_h, {\vd}_h],[v_h, {\vd}_h] ) + b([v_h, {\vd}_h], \xi_h) \geq \alpha_\xi \vertiii{[v_h, {\vd}_h]}_{X_h}\,,
+a([v_h, \vdfh],[v_h, \vdfh] ) + b([v_h, \vdfh], \xi_h) \geq \alpha_\xi \vertiii{[v_h, \vdfh]}_{X_h}\,,
 \\
 \label{stab_stability}
-(s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[v_h, {\vd}_h]}_{X_h}\,,
+(s_h(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[v_h, \vdfh]}_{X_h}\,,
 \end{gather}
@@
 \end{lemma}
-For the proof of this result we remind the reader to Lemma 2.3 of \cite{burman2014}.
-In the remainder of this section we show how to find a multiplier space $Q_H$ and a stabilization operator $s_h$ such that all the assumptions of lemma \ref{lemma23burman} are satisfied.
+For the proof of this result we refer the reader to Lemma 2.3 of \cite{burman2014}.
+In the remainder of this section, we show how to find a multiplier space $Q_H$ and a stabilization operator $s_h$ such that all the assumptions of Lemma \ref{lemma23burman} are satisfied.
 
@@
 % \begin{equation}\label{condition_pi_L}
-% b([v, \vd], {\ld}_h - \pi_H {\ld}_h) \leq C \vertiii{[v,\vd]}\|{\ld}_h - \pi_H {\ld}_h\|_{Q_H},
+% b([v, \vd], \ldh - \pi_H \ldh) \leq C \vertiii{[v,\vd]}\|\ldh - \pi_H \ldh\|_{Q_H},
 % \end{equation}
@@
 % \begin{lemma}\cite[Lemma2.1]{burman2014}\label{lemma_burman2014}
-% If the multiplier space $Q_H$ is inf-sup stable and the operator $\pi_H: Q_h \rightarrow Q_H$ satisfies \eqref{condition_pi_L}, then for any ${\ld}_h \in Q_h$ it holds,
+% If the multiplier space $Q_H$ is inf-sup stable and the operator $\pi_H: Q_h \rightarrow Q_H$ satisfies \eqref{condition_pi_L}, then for any $\ldh \in Q_h$ it holds,
 % \begin{equation*}
-% \|{\ld}_h\|_{H^{-\frac 12}(\Lambda)} \lesssim \sup_{\substack{v_h \in X_{h,0}^1(\Omega)\\ {\vd}_h \in X_{h^\prime,0}^1(\Lambda)}} \frac{b([v_h, {\vd}_h], {\ld}_h)}{\vertiii{[v_h, {\vd}_h]}} + \|{\ld}_h - \pi_H {\ld}_h\|_{Q_H}.
+% \|\ldh\|_{H^{-\frac 12}(\Lambda)} \lesssim \sup_{\substack{v_h \in X_{h,0}^1(\Omega)\\ \vdfh \in X_{h^\prime,0}^1(\Lambda)}} \frac{b([v_h, \vdfh], \ldh)}{\vertiii{[v_h, \vdfh]}} + \|\ldh - \pi_H \ldh\|_{Q_H}.
 % \end{equation*}
 % \end{lemma}
-%  Based on this projection operator, we build the stabilization term $s({\ld}_h, {\md}_h)$ satisfying
+%  Based on this projection operator, we build the stabilization term $s(\ldh, \mdh)$ satisfying
 %  \begin{equation}\label{condition_pi_L_bis}
-%  \|{\ld}_h- \pi_H {\ld}_h\|_{Q_H} C \leq s({\ld}_h, {\ld}_h)
-% \end{equation} and prove that for any $[u_h, {\ud}_h]$ there exists a function $\xi_h\in Q_h$ depending on $[u_h, {\ud}_h]$, namely $\xi_h=\xi_h([u_h, {\ud}_h])$, s.t.
+%  \|\ldh- \pi_H \ldh\|_{Q_H} C \leq s(\ldh, \ldh)
+% \end{equation} and prove that for any $[u_h, \udfh]$ there exists a function $\xi_h\in Q_h$ depending on $[u_h, \udfh]$, namely $\xi_h=\xi_h([u_h, \udfh])$, s.t.
 % \begin{equation}\label{stab_coercivity}
-% a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h) \geq \alpha_\xi \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) },
+% a([u_h, \udfh],[u_h, \udfh] ) + b([u_h, \udfh], \xi_h) \geq \alpha_\xi \vertiii{[u_h, \udfh]}_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) },
 % \end{equation}
 % \begin{equation}\label{stab_stability}
-% (s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[u_h, {\ud}_h]}_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) },
+% (s(\xi_{h}, \xi_{h}))^{\frac 12} \leq c_s \vertiii{[u_h, \udfh]}_{X_{h,0}^1(\Omega)\times X_{h^\prime,0}^1(\Lambda) },
 % \end{equation}
@@
 The first step consists of showing
-that there exists a discrete space $Q_H$ that satisfies the first assumption of \ref{lemma23burman}. 
-We recall that in the case of Problem 2, 
-\begin{equation*}
-b([u_h, {\vd}_h], {\md}_h) = \left(\mtrace v_h - {\vd}_h, {\md}_h\right)_{\Lambda,|\DD|}.
+that there exists a discrete space $Q_H$ that satisfies the first assumption of Lemma \ref{lemma23burman}. 
+We recall that in the case of Problem 3D-1D-1D, 
+\begin{equation*}
+b([u_h, \vdfh], \mdh) = \left(\mtrace v_h - \vdfh, \mdh\right)_{\Lambda,|\DD|}.
 \end{equation*}
 The construction of the inf-sup stable space $Q_H$ is based on macro elements of diameter $H$, where $H$ is sufficiently large.
-In particular, we assume that there exists positive constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$, being $h$ the mesh characteristic size of $\mathcal{T}_h^\Omega$.
-The space is constructed assembling the 3D elements of $\mathcal{G}_h$ into macro patches $ \patch $ such that $H \leq |\patch\cap \Lambda|\leq cH$, with $c\geq 1$.
-Let $M_j$ be the number of elements of the patch $\omega_j$, namely, $\patch=\cup _{i=0}^{M_j} K_i$, where $K_i \in \mathcal{G}_h$, $M_j$ is uniformly bounded in $j$ by some $M\in \mathbb{N}$ and $H=\min_{j}|\patch\cap \Lambda|$.
-We assume that the interiors of the patches $\patch$ are  disjoint.
-We define
-\begin{equation*}
-Q_H=\left\{{\md }_H: \, {\md }_H\in P^0(\patch)\, \forall j \right\}.
-\end{equation*}
+In particular, we assume that there exists positive constants $c_h$ and $c_H$ such that $c_h h\leq H \leq c_H^{-1}h$.
+The space is constructed assembling the 3D elements of $\mathcal{G}_h$ into macro patches $ \patch $ such that $H \leq |\patch\cap \Lambda|\leq cH$ with $H=\min_{j}|\patch\cap \Lambda|$ and $c\geq 1$.
+Let $M_j$ be the number of elements of the patch $\omega_j$, namely, $\patch=\cup _{i=0}^{M_j} K_i$, where $K_i \in \mathcal{G}_h$.
+We assume that $M_j$ is uniformly bounded in $j$ by some $M\in \mathbb{N}$ and that the interiors of the patches $\patch$ are  disjoint.
+We define $Q_H$ as the space of piecewise-constant functions on the patches, namely
+$Q_H=\left\{{\md }_H: \, {\md }_H\in P^0(\patch)\, \forall j \right\}$.
 As previously pointed out for $Q_h$, we denote with $Q_H$ also the restriction of the multiplier space to $\Lambda$, namely say $Q_H \subset L^2(\Lambda) \subset H^{-\frac12}(\Lambda)$.
-
 %figure extended patch
-\begin{figure}\label{fig:patch}
-\center
-\input{./graphics/ext_patch}
-\caption{Extended patches $\omega_j$.}
-\end{figure}
-
-Moreover, we associate to each patch $\patch$ a shape-regular extended patch, still denoted by $\omega_j$ for notational simplicity, which is built adding to $\patch$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$ and we assume that the interiors of the new extended patches $\omega _j$ are still disjoint (see Figure \ref{fig:patch}).
-Here we are using the classical definition of shape-regularity, see for example \cite{MR2050138}, namely there exist a constant $C>0$ such that for any $\omega_j$, $\frac{\tilde{\rho}_j}{\bar{\rho}_j}\leq C$, being $\tilde{\rho}_j$ the diameter of $\omega_j$ and $\bar{\rho}_j$ the diameter of the largest ball that can be inscribed in $\omega_j$.
-The extended patches $\omega _j$ are built such that they fulfill the conditions meas$(\patch)=\mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda}\cap \omega_j)=\mathcal{O}(H)$, where $\Gamma_{\patch\cap \Lambda}$ is the portion of $\Gamma$ with centerline $\patch\cap \Lambda$.
+%\begin{figure}\label{fig:patch}
+%\center
+%\input{./graphics/ext_patch}
+%\caption{Extended patches $\omega_j$.}
+%\end{figure}
+Moreover, we associate to each patch $\patch$ a shape-regular extended patch (using the classical definition of shape-regularity, see for example \cite{MR2050138}), still denoted by $\omega_j$ for notational simplicity, which is built adding to $\patch$ a sufficient number of elements of $\mathcal{T}_h^{\Omega}$ and we assume that the interiors of the new extended patches $\omega _j$ are still disjoint (see Figure \ref{fig:gamma_generated}).
+The extended patches $\omega _j$ are built such that they fulfill the conditions meas$(\patch)=\mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda}\cap \omega_j)=\mathcal{O}(H)$ ($\mathcal{O}(X)$ means $cX \leq \mathcal{O}(X) \leq CX$), where $\Gamma_{\patch\cap \Lambda}$ is the portion of $\Gamma$ with centerline $\patch\cap \Lambda$.
 The latter assumption is required to ensure that the intersection of $\Gamma_{\patch\cap \Lambda}$ and $\omega_j$ is not too small and it will be needed later on to prove the inf-sup stability of the space $Q_H$ in Lemma \ref{lemma:Lh_infsup}.
 A representation of this construction in the simple case in which $\omega _j$ is composed just by one tetrahedron is shown in Figure \ref{fig:gamma_generated}.
+Thanks to the shape regularity of these extended patches, the following discrete trace inequality holds true for any function $v\in H^1(\omega_j)$, 
+\begin{equation}\label{discr_trace_ineq}
+\|\trace v\|_{L^2(\Gamma\cap \omega_j)} \leq C H^{-\frac 12} \|v\|_{L^2(\omega_j)}
+\end{equation}
+Moreover, $\forall u_h \in X^1_{h,0}(\Omega)$ we have the following average inequality, 
+which is a consequence of the definition of $\mtrace$ and Jensen inequality,
+\begin{multline}\label{eq:avrg_ineq}
+\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| }
+= \int_{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \trace u_h \right)^2
+\\
+\leq \int_{\Lambda} \int_{\DD} (\trace u_h)^2
+= \int_{\Gamma} (\trace u_h)^2
+= \sum _j \int_{\patch \cap \Gamma} (\trace u_h)^2
+= \sum _j \|\trace u_h\|^2_{L^2(\patch \cap \Gamma)}.
+\end{multline}
 
@@
 % \begin{equation}\label{eq:stab}
-% s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
+% s(\ldh, \mdh)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket \ldh \rrbracket \llbracket \mdh \rrbracket,
 % \end{equation}
-% being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{G}_h$.
+% being $\llbracket \ldh \rrbracket$ the jump of $\ldh$ across the internal faces of $\mathcal{G}_h$.
+
+%\begin{figure}\label{fig:patch}
+%\center
+%\input{./graphics/ext_patch}
+%\caption{Extended patches $\omega_j$.}
+%\end{figure}
 
@@
 \centering
-\subfigure[$\Gamma_{\omega_j \cap \Lambda}$]
-{
-\input{./graphics/gamma_generated}
-}
-\qquad \qquad
-\subfigure[ $\Gamma_{\omega_j \cap \Lambda} \cap \omega_j$]{
-\input{./graphics/intersection}
-}
-\caption{$\Gamma_{\omega_j \cap \Lambda}$, the portion of $\Gamma$ generated by $\omega_j \cap \Lambda$ in (a) and the intersection between $\Gamma_{\omega_j \cap \Lambda}$ and $\omega_j$ in (b).
-Here for simplicity $\omega_j$ is represented as a single tetrahedron but actually it is a collection of tetrahedra as shown in Figure \ref{fig:patch}.}
+\includegraphics[width=0.32\textwidth]{./graphics/ext_patch.tex}
+\includegraphics[width=0.32\textwidth]{./graphics/gamma_generated}
+\includegraphics[width=0.32\textwidth]{./graphics/intersection}
+\caption{
+(Left) Extended patches $\omega_j$. (Middle)
+$\Gamma_{\omega_j \cap \Lambda}$, the portion of $\Gamma$ generated by $\omega_j \cap \Lambda$.
+(Right) the intersection between $\Gamma_{\omega_j \cap \Lambda}$ and $\omega_j$.
+Here for simplicity $\omega_j$ is represented as a single tetrahedron but actually it is a collection of tetrahedra as shown in left panel.}
 \end{figure}
-
-Thanks to the shape regularity of these extended patches, we have that the following discrete trace inequality holds true for any function $v\in H^1(\omega_j)$, 
-\begin{equation}\label{discr_trace_ineq}
-\|\trace v\|_{L^2(\Gamma\cap \omega_j)} \lesssim H^{-\frac 12} \|v\|_{L^2(\omega_j)}
-\end{equation}
-Moreover $\forall u_h \in X^1_{h,0}(\Omega)$ we have the following average inequality, which is a consequence of the definition of $\mtrace$ and Jensen inequality,
-\begin{multline}\label{eq:avrg_ineq}
-\sum _j \|\mtrace u_h\|^2_{L^2(\patch \cap \Lambda),|\DD| }
-= \sum _j\int_{\patch \cap \Lambda} |\DD| \mtrace u_h^2 
-= \int_{\Lambda} |\DD| \left( \frac{1}{|\DD|} \int_{\DD} \trace u_h \right)^2
-\leq \int_{\Lambda} \int_{\DD} (\trace u_h)^2
-\\
-= \int_{\Gamma} (\trace u_h)^2
-= \sum _j \int_{\patch \cap \Gamma} (\trace u_h)^2
-= \sum _j \|\trace u_h\|^2_{L^2(\patch \cap \Gamma)}.
-\end{multline}
 
@@
 \begin{lemma}\label{lemma:Lh_infsup}
-The space $Q_H$ is inf-sup stable, namely $\forall {\md}_H \in Q_H$, $\exists \beta >0$ s.t.
-\begin{equation*}
-\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\md} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}} \geq \beta \|{\md}_H\|_{H^{-\frac 12}(\Lambda)}.
+The space $Q_H$ is inf-sup stable, 
+namely there exists $\beta >0$ such that
+\begin{equation*}
+\sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ \vdfh \in X_{\fkh,0}^1(\Lambda)}} \frac{\left(\mtrace v_h - \vdfh, {\md} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, \vdfh]}} \geq \beta \|{\md}_H\|_{H^{-\frac 12}(\Lambda)} \quad \forall {\md}_H \in Q_H.
 \end{equation*} 
@@
 \begin{proof}
-As in the continuous case, we can choose ${\vd}_h=0$ and we prove that
+We choose $\vdfh=0$ and we prove that
 \begin{equation*} 
@@
 \end{equation*} 
-Proving the last inequality it is equivalent to find the Fortin operator $\pi_F: H^1_0(\Omega) \rightarrow X_{h,0}^1(\Omega)$, such that 
+Proving the last inequality is equivalent to finding the Fortin operator $\pi_F: H^1_0(\Omega) \rightarrow X_{h,0}^1(\Omega)$, such that 
 \begin{gather}
@@
 \label{eq:cont_Fortin}
-\|\pi_F v\|_{H^1(\Omega)}\lesssim \|v\|_{H^1(\Omega)}\,.
+\|\pi_F v\|_{H^1(\Omega)} \leq C \|v\|_{H^1(\Omega)}\,.
 \end{gather}
@@
 \end{equation*}
-where $I_h: H^1(\Omega) \rightarrow X_{h,0}^1$ denotes an $H^1(\Omega)$-stable interpolant
+where $I_h: H^1(\Omega) \rightarrow X_{h,0}^1(\Omega)$ denotes an $H^1(\Omega)$-stable interpolant
 and $\varphi_j \in X_{h,0}^1(\Omega)$ is such that supp$(\varphi_j)\subset \omega_j$, supp$(\trace \varphi _j) \subset \Gamma_{\patch\cap \Lambda}\cap \omega_j$, $\varphi_j =0$ on $\partial \omega _j$ and
@@
 We notice that supp$(\trace \varphi_j) \subset \Gamma_{\patch\cap \Lambda}\cap \omega_j$ ensures that $\mtrace \varphi_j \subset \omega_j\cap \Lambda$.
-Therefore, since for construction the interiors of $\omega_j\cap \Lambda$  are disjoint and $\varphi _j = 0 $ on $\partial \omega_j$,  the functions $\mtrace \varphi_j\, \forall j$ have all disjoint supports.
-This construction is always possible since meas$(\patch) = \mathcal{O}(H^3)$ and diam$(\Gamma_{\patch\cap \Lambda} \cap \omega_j)=\mathcal{O}(H)$, provided $H$ is sufficiently larger that $h$.
-Indeed, this guarantees that the functions $\varphi _j$ and their traces $\trace \varphi _j$ have a sufficiently large support so that they can be built in order to satisfy \eqref{phi_properties}.
-Then we have
+Therefore, since the interiors of $\omega_j\cap \Lambda$  are disjoint and $\varphi _j = 0 $ on $\partial \omega_j$,  the functions $\mtrace \varphi_j\, \forall j$ have all disjoint supports.
+Provided $H$ is sufficiently larger that $h$, the functions $\varphi _j$ and their traces $\trace \varphi _j$ have a sufficiently large support thanks to the fact that $\mathrm{meas}(\patch) = \mathcal{O}(H^3)$ and $\mathrm{diam}(\Gamma_{\patch\cap \Lambda} \cap \omega_j)=\mathcal{O}(H)$.
+Owing to these properties it is possible to satisfy \eqref{phi_properties}. 
+Then, using the properties of $\varphi_j$ we have
 \begin{multline*}
 \left(\mtrace v - \mtrace \pi _F v  , {\md}_H\right)_{\Lambda, |\DD|} = \sum _j \int_{\patch\cap \Lambda} |\DD |\left[ \mtrace v-\mtrace I_h v-\sum _i \alpha_i \mtrace \varphi _i \right]{\md}_H \\
-(\text{supp} (\mtrace \varphi _i )\subset \omega _i\cap \Lambda \, \forall i)  =\sum _j \int_{\patch\cap \Lambda}|\DD| \left[ \mtrace v-\mtrace I_h v-\alpha_j \mtrace \varphi _j \right]{\md}_H\\
-=\sum _j \int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\md}_H - \frac{\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi _j} \int_{\patch\cap \Lambda} |\DD|\mtrace \varphi _j{\md}_H\\
-(\text{using ${\md}_H$ constant on $\patch\cap \Lambda$})=0.
+=\sum _j \int_{\patch\cap \Lambda}|\DD| \left[ \mtrace v-\mtrace I_h v-\alpha_j \mtrace \varphi _j \right]{\md}_H
+\\
+% =\sum _j \left[\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\md}_H - \frac{\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)}{\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi _j} \int_{\patch\cap \Lambda} |\DD|\mtrace \varphi _j{\md}_H\right]
+% \\ 
+=\sum _j \left[\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\md}_H
+-[\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace  I_h v) {\md}_H \right]=0.
 \end{multline*}
-Concerning the continuity of $\pi_F$, we exploit the assumptions that the interiors of $\patch$ are disjoint and supp$(\varphi _j) \subset \patch$ and we have
+Concerning the continuity of $\pi_F$, we exploit the assumptions that the interiors of $\patch$ are disjoint, $\mathrm{supp}(\varphi _j) \subset \patch$ and the $H^1$-stability of $I_h$ to show that
+\begin{equation*}
+\|\nabla \pi_F v \|_{L^2(\Omega)} 
+% \leq \|\nabla I_h v\|_{L^2(\Omega)} + \left(\sum_j\alpha_j^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\right)^{\frac 12}
+\leq C \|\nabla  v\|_{L^2(\Omega)} + \left(\sum_j\alpha_j^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\right)^{\frac 12}\,.
+\end{equation*}
+For the second term,
+using that $\|\nabla \varphi _j\|_{{L^2(\omega_j)}}=\mathcal{O}(1)$, 
+$\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j=\mathcal{O}(H)$ and that
+$|\patch\cap \Lambda| \leq cH$,
+exploiting Jensen's, average inequality \eqref{eq:avrg_ineq} 
+and trace inequality \eqref{discr_trace_ineq},
+and finally applying the approximation properties of $I_h$,
+the following upper bound holds true,
 \begin{multline*}
-\|\nabla \pi_F v \|_{L^2(\Omega)} \leq \|\nabla I_h v\|_{L^2(\Omega)} + \left(\sum_j\alpha_j^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\right)^{\frac 12}\\
-(\text{stability of }I_h)\lesssim   \|\nabla  v\|_{L^2(\Omega)} + \left(\sum_j\alpha_j^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\right)^{\frac 12}
+\sum_j \alpha_j ^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}
+\leq C \sum_j \frac{\left(\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)\right)^2}{\left(\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j \right)^2}
+\\
+% \leq \frac {C}{H^2} \sum_j \left(\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_hv)\right)^2
+\leq \frac {C}{H^2} \sum_j |\patch\cap \Lambda| \int_{\patch\cap \Lambda} |\DD|^2(\mtrace v-\mtrace I_h v)^2
+\\
+\leq \frac {C}{H} \sum_j \| \mtrace (v-I_h v)\|^2_{L^2(\patch\cap \Lambda), |\DD|}
+\leq \frac {C}{H} \sum_j \| \trace(v-I_h v)\|^2_{L^2(\omega _j\cap \Gamma)}  
+\\
+\leq \frac {C}{H^2} \sum_j  \| v-I_h v\|^2_{L^2(\omega_j)} 
+\leq C \frac {1}{H^2}  \| v-I_h v\|^2_{L^2(\Omega)} 
+\leq C \|\nabla  v\|^2_{L^2(\Omega)}
 \end{multline*}
-and for the second term 
-\begin{multline*}
-\sum_j \alpha_j ^2\|\nabla \varphi _j\|^2_{L^2(\omega_j)}\leq
-\\
-\left(\text{using }\|\nabla \varphi _j\|_{{L^2(\omega_j)}}=\mathcal{O}(1)\right) \lesssim  \sum_j \frac{\left(\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_h v)\right)^2}{\left(\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j \right)^2}
-\\
-\left(\text{since }\int_{\patch\cap \Lambda}|\DD|\mtrace \varphi_j=O(H)\right) \lesssim \frac {1}{H^2} \sum_j \left(\int_{\patch\cap \Lambda} |\DD| (\mtrace v-\mtrace I_hv)\right)^2
-\\
-(\text{Jensen}) \lesssim  \frac {1}{H^2} \sum_j |\patch\cap \Lambda| \int_{\patch\cap \Lambda} |\DD|^2(\mtrace v-\mtrace I_h v)^2
-\\
-(\text{being }|\patch\cap \Lambda| \leq cH)\lesssim  \frac {1}{H} \sum_j \| \mtrace (v-I_h v)\|^2_{L^2(\patch\cap \Lambda), |\DD|}
-\\
-(\text{average inequality \eqref{eq:avrg_ineq}} ) \lesssim  \frac {1}{H} \sum_j \| \trace(v-I_h v)\|^2_{L^2(\omega _j\cap \Gamma)}  
-\\
-\left(\text{trace inequality \eqref{discr_trace_ineq}} \right)\lesssim  \frac {1}{H^2} \sum_j  \| v-I_h v\|^2_{L^2(\omega_j)} \lesssim  \frac {1}{H^2}  \| v-I_h v\|^2_{L^2(\Omega)} 
-\\
-(\text{approximation properties of }I_h)\lesssim \|\nabla  v\|^2_{L^2(\Omega)}
-\end{multline*}
-and the continuity of $\pi_F$ follows.
-We notice that the constant in the inequality \eqref{eq:cont_Fortin} is independent of how $\Lambda$  is cut by the elements of the mesh $\mathcal{T}_h^{\Omega}$.
+that is the $H^1$-stability of $\pi_F$. We notice that the constant in the inequality \eqref{eq:cont_Fortin} is independent of how $\Lambda$  cuts the elements of the mesh $\mathcal{T}_h^{\Omega}$.
 \end{proof}
 
-For the second assumption of lemma \ref{lemma23burman}, we recall that the bilinear form $b(v_h,{\md}_h)$ is continuous in the norms $\vertiii{v_h},\,\|{\md}_h\|_{L^2(\Lambda)}$. 
-Using lemma \ref{lemma:Lh_infsup}, it is straightforward to prove that there exists a constant $\beta$ such that
+For the second assumption of Lemma \ref{lemma23burman}, we recall that $b(v_h,\mdh)$ is continuous in the norms $\vertiii{v_h},\,\|\mdh\|_{L^2(\Lambda)}$. 
+Using Lemma \ref{lemma:Lh_infsup}, and in particular the existence of a Fortin projector,
+there exists a constant $\beta$ such that 
+(the proof is \miro{analogous} to the one of Lemma 2.1 in \cite{burman2014})
 \begin{equation}\label{relax_infsup}
-\beta \|{\md}_h\|_{H^{-\frac12}(\Lambda)} \leq \sup\limits_{v_h \in X_h} \frac{b(v_h,{\md}_h)}{\vertiii{v_h}} + \|{\md}_h-\pi_H {\md}_h\|_{L^2(\Lambda)}, \quad \forall {\md}_h \in Q_h\,.
+\beta \|\mdh\|_{H^{-\frac12}(\Lambda)} \leq \sup\limits_{v_h \in X_h} \frac{b(v_h,\mdh)}{\vertiii{v_h}} + \|\mdh-\pi_H \mdh\|_{L^2(\Lambda)}, \quad \forall \mdh \in Q_h\,.
 \end{equation}
-We define $\pi_H = \sum_j \pi_H^j$, where $\pi_H^j$ is the operator
+We define $\pi_H = \sum_j \pi_H^j\,: L^2(\Lambda) \rightarrow Q_H$, 
+where $\pi_H^j$ is the operator
 \begin{equation}\label{eq:projector}
-\pi_H^j w_{|\patch \cap \Lambda} =\frac{1}{|\Gamma_{\patch\cap \Lambda}|}\int_{\patch\cap \Lambda}|\DD| w\quad \forall j,
+\pi_H^j w_{|\patch \cap \Lambda} =\frac{1}{|\Gamma_{\patch\cap \Lambda}|}\int_{\patch\cap \Lambda}|\DD| w\quad \forall j.
 \end{equation}   
- Then, for any $w \in L^2(\Lambda)$ the following Poincarè inequality holds true, see for example \cite[Corollary B.65]{MR2050138},
+Since $\cup_j \omega_j \cap \Lambda  = \Lambda$ and $\omega_j \cap \Lambda$ are not overlapping,
+we obtain that $\pi_H$ is an orthogonal projection, namely $(w-\pi_H w,\pi_H w)=0$.
+Moreover, for any $w \in L^2(\Lambda)$ the following Poincarè inequality holds true, see for example \cite[Corollary B.65]{MR2050138},
 \begin{equation}\label{disc_poincare_ineq}
-\|w - \pi_H w\|_{L^2(\omega_j\cap\Lambda),|\DD|} \leq c_P H \|\partial_s w\|_{L^2(\omega_j\cap\Lambda),|\DD|}\,.
+\|w - \pi_H w\|_{L^2(\omega_j\cap\Lambda),|\DD|} \leq C_P H \|\partial_s w\|_{L^2(\omega_j\cap\Lambda),|\DD|}\,.
 \end{equation}
@@
 \begin{equation}\label{eq:stab}
-s({\ld}_h, {\md}_h)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket,
+s_h(\ldh, \mdh)= \sum _{K\in \mathcal{G}_{h}} \int_{\partial K\setminus \partial \mathcal{G}_{h}} h \llbracket \ldh \rrbracket \llbracket \mdh \rrbracket,
 \end{equation}
-being $\llbracket {\ld}_h \rrbracket$ the jump of ${\ld}_h$ across the internal faces of $\mathcal{G}_h$.
+being $\llbracket \ldh \rrbracket$ the jump of $\ldh$ across the internal faces of $\mathcal{G}_h$.
 Then, we use the result of \cite{burman2014}, Section III to show that
 \begin{equation*}
-    \|{\md}_h-\pi_H {\md}_h\|_{L^2(\Lambda)} \leq C s({\md}_h, {\md}_h)\,,
-\end{equation*}
-which combined with \eqref{relax_infsup} shows that the second assumption of lemma \ref{lemma23burman} holds true.
+    \|\mdh-\pi_H \mdh\|_{L^2(\Lambda)} \leq C s_h(\mdh, \mdh)\,,
+\end{equation*}
+which combined with \eqref{relax_infsup} shows that the second assumption of Lemma \ref{lemma23burman} holds true.
 
@@
 \begin{equation*}
-\vertiii{[u_h, {\ud}_h]}^2_{X_h}
-= \|u_h\|^2_{H^1(\Omega)}+\|{\ud}_h\|^2_{H^1(\Lambda),|\D|} + \|\mtrace u_h - {\ud}_h\|^2_{\frac 12, h, \Lambda, |\DD|},
-\end{equation*}
-and the space $Q_H$ with the $L^2$ norm 
-$\|{\md}_H \|_{Q_H} = \|{\md}_H \|_{L^2(\Lambda)}$.
-
-Also, the function $\xi_h([v_h, {\vd}_h]) \in Q_H \subset Q_h \subset L^2(\Lambda)$ is defined as follows
-\begin{equation*}
-{\xi_h}_{|\patch\cap \Lambda}=\frac{\delta}{H} \pi_H(\mtrace u_h-{\ud}_h)_{|\patch \cap \Lambda}.
-\end{equation*}
-Then the following result holds true. 
+\vertiii{[u_h, \udfh]}^2_{X_h}
+= \|u_h\|^2_{H^1(\Omega)}+\|\udfh\|^2_{H^1(\Lambda),|\D|} + \|\mtrace u_h - \udfh\|^2_{\frac 12, h, \Lambda, |\DD|},
+\end{equation*}
+and the space $Q_H$ with the $L^2$ norm $\|{\md}_H \|_{L^2(\Lambda)}$.
+
+Also, the function $\xi_h([v_h, \vdfh]) \in Q_H \subset Q_h \subset L^2(\Lambda)$ is defined as follows
+\begin{equation*}
+{\xi_h}_{|\patch\cap \Lambda}=\frac{\delta}{H} \pi_H(\mtrace u_h-\udfh)_{|\patch \cap \Lambda}.
+\end{equation*}
+where $\delta$ is an arbitrarily small parameter. Then the following result holds true. 
 \begin{lemma}
-Given $\pi_H,\ s_h(\cdot,\cdot), \ \xi_h$ defined above, the inequalities \eqref{stab_coercivity} and \eqref{stab_stability} are satisfied.
+Given $\pi_H,\ s_h(\cdot,\cdot), \ \xi_h$ defined above, 
+choosing $\delta$ small enough,
+the inequalities \eqref{stab_coercivity} and \eqref{stab_stability} are satisfied.
 \end{lemma}
 \begin{proof} 
-Concerning the coercivity property \eqref{stab_coercivity}, we show that $\forall [u_h, {\ud}_h]$, there exists $\xi_h \in Q_h$ s.t.
-\begin{equation*}
-(u_h,u_h)_{H^1(\Omega)}+ ({\ud}_h, {\ud}_h)_{H^1(\Lambda), |\D|} +   (\mtrace u_h - {\ud}_h, \xi_h)_{\Lambda,|\DD|} \geq \alpha_{\xi}\vertiii{[u_h, {\ud}_h]}^2_{X_h}.
-\end{equation*}
-Using the definitions of $\pi_H$ and $\xi_h([u_h, {\ud}_h])$ previously presented and recalling that $\xi_h\in Q_H \subset Q_h$, we obtain
+Concerning the coercivity property \eqref{stab_coercivity}, we show that $\forall [u_h, \udfh]$, there exists $\xi_h \in Q_h$ such that,
+\begin{equation*}
+(u_h,u_h)_{H^1(\Omega)}+ (\udfh, \udfh)_{H^1(\Lambda), |\D|} +   (\mtrace u_h - \udfh, \xi_h)_{\Lambda,|\DD|} \geq \alpha_{\xi}\vertiii{[u_h, \udfh]}^2_{X_h}.
+\end{equation*}
+Using the definitions of $\pi_H$ and $\xi_h([u_h, \udfh])$ previously presented and recalling that $\xi_h\in Q_H \subset Q_h$, we obtain
 \begin{multline*}
-\left( \mtrace u_h - {\ud}_h, \xi _h \right)_{\Lambda,|\DD|} 
-= \sum_j \int_{\patch\cap \Lambda} |\DD|(\mtrace u_h - {\ud}_h)\xi_h
-\\
-(\text{definition of $\xi_h$})= \frac{\delta}{H}\sum_j \pi_H^j( \mtrace u_h - {\ud}_h)\int_{\patch\cap \Lambda} |\DD|(\mtrace u_h - {\ud}_h)
-\\
-\left(|\Gamma_{\omega_j \cap \Lambda}| = \int_{\omega_j \cap \Lambda}|\DD|\right)= \frac{\delta}{H} \sum_j \int_{\patch\cap \Lambda}|\DD| (\pi_H( \mtrace u_h - {\ud}_h) )^2
-= \frac{\delta}{H}\sum_j \|\pi_H( \mtrace u_h - {\ud}_h)\|_{L^2(\patch\cap \Lambda),|\DD|}
-\\
-(\text{orthogonality of $\pi_H$}) = \frac{\delta}{H} \sum_j \left( \|\mtrace u_h - {\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} - \|(\pi_H-\mathcal{I})(\mtrace u_h - {\ud}_h)\|^2_{L^2(\patch\cap \Lambda),|\DD|} \right)
+\left( \mtrace u_h - \udfh, \xi _h \right)_{\Lambda,|\DD|} 
+% = \sum_j \int_{\patch\cap \Lambda} |\DD|(\mtrace u_h - \udfh)\xi_h
+= \frac{\delta}{H}\sum_j \pi_H^j( \mtrace u_h - \udfh)\int_{\patch\cap \Lambda} |\DD|(\mtrace u_h - \udfh)
+\\
+= \frac{\delta}{H} \sum_j \int_{\patch\cap \Lambda}|\DD| (\pi_H( \mtrace u_h - \udfh) )^2
+= \frac{\delta}{H}\sum_j \|\pi_H( \mtrace u_h - \udfh)\|_{L^2(\patch\cap \Lambda),|\DD|}^2
+\\
+= \frac{\delta}{H} \sum_j \left( \|\mtrace u_h - \udfh\|^2_{L^2(\patch\cap \Lambda),|\DD|} - \|(\pi_H-\mathcal{I})(\mtrace u_h - \udfh)\|^2_{L^2(\patch\cap \Lambda),|\DD|} \right) 
 \\ 
 \geq \frac{\delta}{H} \sum_j \left(
-\|\mtrace u_h-{\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|}
-- \|(\pi_H - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda), |\DD|}
-- \|(\pi_H - \mathcal{I}){\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} \right). 
+\|\mtrace u_h-\udfh\|^2_{L^2(\patch\cap \Lambda),|\DD|}
+- \|(\pi_H - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda), |\DD|} \right.
+\\
+\left.- \|(\pi_H - \mathcal{I})\udfh\|^2_{L^2(\patch\cap \Lambda),|\DD|} \right). 
 \end{multline*}
-For the second term we apply the additional assumption that the operators $\mtrace$ and $\partial_s$ commute. This is true if the cross section $\D$ does not depend on the arclength $s$.
+Now, we seek for an upper bound of the second and third (negative) terms of the last inequality.
+For the second term, we apply the additional assumption that the operators $\mtrace$ and $\partial_s$ commute. This is true if the cross section $\D$ does not depend on the arclength $s$.
 Then, we use the Poincar\'e inequality \eqref{disc_poincare_ineq}, the average inequality \eqref{eq:avrg_ineq} and the trace inequality \eqref{discr_trace_ineq} to show that,
@@
 \sum _j  \|(\pi_H - \mathcal{I})\mtrace u_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} 
-\leq C_P^2 H^2 \sum _j \|\partial_s \mtrace u_h\|_{L^2(\patch\cap \Lambda),|\DD|}^2
-= C_P^2 H^2 \sum _j \|\mtrace \partial_s  u_h\|_{L^2(\patch\cap \Lambda),|\DD|}^2
+% \leq C_P^2 H^2 \sum _j \|\partial_s \mtrace u_h\|_{L^2(\patch\cap \Lambda),|\DD|}^2
+\leq C_P^2 H^2 \sum _j \|\mtrace \partial_s  u_h\|_{L^2(\patch\cap \Lambda),|\DD|}^2
 \\
@@
 % \end{multline*}
-For the third term we proceed similarly,
+\paolo{For the third term we observe that since $H \lesssim 1$, there exists a constant $C$ 
+such that $C_P^2 H|\DD| \leq C |\D|$. As a result, the following upper bound holds true,
 \begin{multline*}
-\sum _j \|(\pi_H - \mathcal{I}){\ud}_h\|^2_{L^2(\patch\cap \Lambda),|\DD|} \leq C_P^2 H^2 \sum _j \|\partial_s {\ud}_h\|_{L^2(\patch\cap \Lambda),|\DD|}^2
-\\
-(\text{since $H$ is fixed, we can find a constant s.t. } H|\DD| \lesssim |\D|) C H \sum _j \|\partial_s {\ud}_h\|_{L^2(\patch\cap \Lambda),|\D|}^2.
+\sum _j \|(\pi_H - \mathcal{I})\udfh\|^2_{L^2(\patch\cap \Lambda),|\DD|} \leq C_P^2 H^2 \sum _j \|\partial_s \udfh\|_{L^2(\patch\cap \Lambda),|\DD|}^2
+\\
+\leq C_P^2 H \frac{\max |\DD|}{\min |\D|} \sum _j \|\partial_s \udfh\|_{L^2(\patch\cap \Lambda),|\D|}^2.
 \end{multline*}
@@
 %}\\
-Therefore, we obtain
+Combining the last three inequalities, reminding that $c_h h\leq H \leq c_H^{-1}h$, 
+we obtain
 \begin{multline*}
-a([u_h, {\ud}_h],[u_h, {\ud}_h] ) + b([u_h, {\ud}_h], \xi_h([u_h, {\ud}_h]))
-\geq \\
-(1-\delta C) \|\nabla u_h\|^2_{L^2(\Omega)} + (1- \delta C) \|\partial_s {\ud}_h\|^2_{L^2(\Lambda), |\D|}
-+\delta c_H  \|\mtrace u_h-{\ud}_h\|^2_{\frac 12,h,\Lambda, |\DD|}
+a([u_h, \udfh],[u_h, \udfh] ) + b([u_h, \udfh], \xi_h([u_h, \udfh]))
+\geq (1-\delta C) \|\nabla u_h\|^2_{L^2(\Omega)} 
+\\
++ \left(1- \delta C_P^2 \frac{\max |\DD|}{\min |\D|}\right) \|\partial_s \udfh\|^2_{L^2(\Lambda), |\D|}
++\delta c_H  \|\mtrace u_h-\udfh\|^2_{\frac 12,h,\Lambda, |\DD|}
 \end{multline*}
-and choosing $\delta=\frac{1}{2C}$ we obtain the desired inequality.\\
+and choosing $\delta=\frac{1}{2}\min\left[C^{-1}, \left(C_P^2 \frac{\max |\DD|}{\min |\D|}\right)^{-1}\right]$ we obtain the desired inequality.}\\
 Concerning inequality \eqref{stab_stability}, the proof is analogous to the one in \cite{burman2014}.
@@
 % \begin{multline}
-% \sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ {\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - {\vd}_h, {\md} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, {\vd}_h]}}
-% \geq \sup_{\substack{{\vd}_h \in X_{h',0}^1(\Lambda)}} \frac{\left(- {\vd}_h, {\md} _H\right)_{\Lambda, |\DD|}}{\|{\vd}_h\|_{H^1(\Lambda)}}
-% \geq \frac{{\|\md} _H\|^2_{L^2(\Lambda)}}{\|{\vd}_h\|_{H^1(\Lambda)}} \\
+% \sup_{\substack{v_h \in X_{h,0}^1(\Omega),\\ \vdfh \in X_{h',0}^1(\Lambda)}} \frac{\left(\mtrace v_h - \vdfh, {\md} _H\right)_{\Lambda, |\DD|}}{\vertiii{[v_h, \vdfh]}}
+% \geq \sup_{\substack{\vdfh \in X_{h',0}^1(\Lambda)}} \frac{\left(- \vdfh, {\md} _H\right)_{\Lambda, |\DD|}}{\|\vdfh\|_{H^1(\Lambda)}}
+% \geq \frac{{\|\md} _H\|^2_{L^2(\Lambda)}}{\|\vdfh\|_{H^1(\Lambda)}} \\
 % ( \text{inverse inequality} )\geq \frac{{h'}^2}{c_I} \|{\md}_H\|_{L^2(\Lambda)}
@@
 \uf - \up &= q_i  && \text{ on }  \Gamma,\\
-\up &= h && \text{ on } \partial \Omega.
+\up &= h && \text{ on } \partial \Omega,
 \end{align}
@@
  \captionof{figure}{
-   (Top)
+   (Left)
 $\Lambda$ and $\Gamma$ conforming discretization of $\Omega$
    used for \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}.
-   (Bottom) Sample discretization of the benchmark geometry in the non-conforming case. 
+   (Right) Sample discretization of the benchmark geometry in the non-conforming case. 
  }
@@
 \hline
-\multicolumn{5}{c}{\textcolor{blue!40!white}{$\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}}\\
+\multicolumn{5}{c}{\textcolor{blue}{$\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}}\\
 \hline
@@
 \hline
-\multicolumn{5}{c}{\textcolor{red!50!white}{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$}}\\
+\multicolumn{5}{c}{\textcolor{red}{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$}}\\
 %    \begin{tabular}{l|lll}
@@
 %  functions $u_h$ and $\udh$ on the left and the Lagrance multiplier
-%  ${\ld}_h$ on the right.}\label{fig:sol_benchm2}
+%  $\ldh$ on the right.}\label{fig:sol_benchm2}
 %\end{figure}
@@
 \[
-({\ld}_h, {\md}_h) \mapsto \sum _{K\in \mathcal{G}_h}\int_{K}{\ld}_h {\md}_h + \sum _{K\in \mathcal{G}_h} \int_{\partial K \setminus \partial \mathcal{G}_h} h \llbracket {\ld}_h \rrbracket \llbracket {\md}_h \rrbracket.
+(\ldh, \mdh) \mapsto \sum _{K\in \mathcal{G}_h}\int_{K}\ldh \mdh + \sum _{K\in \mathcal{G}_h} \int_{\partial K \setminus \partial \mathcal{G}_h} h \llbracket \ldh \rrbracket \llbracket \mdh \rrbracket.
 \]
@@
   \caption{Cost comparison of the formulations across refinement levels $l$.
-    Number of Krylov  terations (preconditioned conjugate gradient for \eqref{benchm_3d},
+    Number of Krylov  iterations (preconditioned conjugate gradient for \eqref{benchm_3d},
     MinRes otherwise) and the condition number of the preconditioned
@@
 
+\newpage
+
 \appendix

### 2020-03-30 appendix.tex
Updates from Overleaf

--- 2019-12-07 appendix.tex
@@
-\section{System sizes in benchmark formulations}\label{sec:appendix}
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+
+\section{Derivation of the model}
+This section provides a rigorous derivation of 3D-1D-2D problem \eqref{eq:problem2} and 3D-1D-1D problem \eqref{eq:problem1}. 
+The steps are similar to the derivation presented in \cite{laurino_m2an}, 
+however, here the coupling conditions are different,
+giving rise to coupled problems featuring Lagrange multipliers. 
+Precisely, the starting point is the problem arising from \emph{Dirichlet-Neumann} conditions. 
+Find $\up,\uf$ s.t.:
+\begin{subequations}\label{eq:dirneu}
+\begin{align}
+\label{eq:dirneu1}
+- \Delta \up  + \up &= f  && \text{ in } \Omega_{\oplus},\\
+\label{eq:dirneu2}
+- \Delta \uf  + \uf &= g  && \text{ in } \Omega_\ominus,\\
+\label{eq:dirneu3}
+-\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
+\label{eq:dirneu4}
+\uf &= \up && \text{ on }  \Gamma,\\
+\label{eq:dirneu5}
+\up &= 0 && \text{ on } \partial \Omega\,.
+\end{align}
+\end{subequations}
+The coupling constraints defined on $\Gamma$ involve essential or strong conditions.
+Such conditions will be enforced weakly by using the method of Lagrange multipliers~\cite{MR359352}. Then, the variational formulation of problem \eqref{eq:dirneu}
+is to find $\up \in H^1_{\partial\Omega}(\Omega_\oplus), \ \uf \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus), \ \lambda \in H^{-\frac 1 2}(\Gamma)$ s.t.
+\begin{subequations}\label{eq:weak_dirneu}
+\begin{align}
+&(u_\oplus,v_\oplus)_{H^1(\Omega_\oplus)} + (u_\ominus,v_\ominus)_{H^1(\Omega_\ominus)} 
++ \langle  v_\oplus - v_\ominus, \lambda \rangle_{\Gamma} 
+\\
+\nonumber
+&\quad = (f,v_\oplus)_{L^2(\Omega_\oplus)} + (g,v_\ominus)_{L^2(\Omega_\ominus)}
+\quad \forall v_\oplus \in H^1_{\partial\Omega}(\Omega_\oplus), \ v_\ominus \in H^1_{\partial\Omega_\ominus\setminus\Gamma}(\Omega_\ominus),
+\\
+& \langle u_\oplus - u_\ominus, \mu \rangle_{\Gamma} = 0
+\quad \forall  \mu \in H^{-\frac 1 2}(\Gamma)\,.
+\end{align}
+\end{subequations}
+%where $\langle v, \mu \rangle_{H^{-\frac 1 2}(\Gamma)}$ denotes the duality pairing between 
+%$ \mu \in H^{-\frac 1 2}(\Gamma)$ and $v \in H^{\frac 1 2}(\Gamma)$.
+where $\lambda$ is the Lagrange multiplier and it is equivalent to $\nabla \uf \cdot \nn_\ominus$.
+
+\subsubsection*{Model reduction of the problem on $\Omega_{\ominus}$}
+
+We apply the averaging technique to equation \eqref{eq:dirneu2}.
+In particular, we consider an arbitrary portion $\mathcal{P}$ of the cylinder $\Omega_\ominus$, with lateral surface $\Gamma _{\mathcal{P}}$ and bounded by two perpendicular sections to $\Lambda$, namely $\mathcal{D}(s_1), \ \mathcal{D}(s_2)$ with $s_1<s_2$.
+We have,
+\begin{multline*}
+\int_{\mathcal{P}} -\Delta \uf + \uf d\omega =
+-\int_{\partial \mathcal{P}} \nabla \uf \cdot \nn_{\ominus} \, d\sigma  + \int_{\mathcal{P}}\uf d\omega=
+\\
+ \int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma -  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma -  \int_{\Gamma_{\mathcal{P}}} \nabla \uf \cdot \nn_{\ominus} d\sigma +\int_{\mathcal{P}}\uf d\omega
+\end{multline*}
+By the fundamental theorem of integral calculus 
+\begin{equation*}
+\int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma -  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma 
+= -\int_{s_1}^{s_2} d_s \int_{\mathcal{D}(s)}  \partial_s \uf d\sigma ds
+= -\int_{s_1}^{s_2} d_s \left( |\mathcal{D}(s)| \avrd{\partial_s \uf} \right)
+\end{equation*}
+Moreover, we have
+\begin{equation*}
+\int_{\Gamma_{\mathcal{P}}} \nabla \uf \cdot \nn_{\ominus} d\sigma =  \int_{\Gamma_{\mathcal{P}}} \lambda \, d\sigma
+=  \int_{s_1}^{s_2} \int_{\partial\mathcal{D}(s)} \lambda d\gamma \, ds 
+= \int_{s_1}^{s_2} |\DD| \avrc{\lambda} \,ds\,.
+\end{equation*}
+From the combination of all the above terms with the right hand side, we obtain that the solution $\uf$ of \eqref{eq:dirneu2} satisfies,
+\begin{equation*}
+\int_{s_1}^{s_2} \left[ 
+-d_s (|\D(s)|\avrd{\partial_s \uf}) + |\D(s)|\avrd{u}_{\ominus} 
+- |\partial\mathcal{D}(s)| \avrc{\lambda} - |\mathcal{D}(s)| \avrd{g}
+\right]\, ds = 0.
+\end{equation*}
+Since the choice of the points $s_1,s_2$ is arbitrary, we conclude that the following equation holds true,
+\begin{equation}\label{eq:averaged_f}
+-d_s (|\D(s)|\avrd{\partial_s \uf}) + |\D(s)|\avrd{u}_{\ominus} 
+- |\partial\mathcal{D}(s)| \avrc{\lambda}
+= |\mathcal{D}(s)| \avrd{g} \quad \text{on} \ \Lambda\,,
+\end{equation}
+which is complemented by the following conditions at the boundary of $\Lambda$,
+\begin{equation}\label{eq:averaged_f_boundary}
+|\D(s)| \avrd{\partial_s \uf}= 0, \quad \text{on} \quad s=0,S.
+\end{equation}
+Then, we consider variational formulation of the averaged equation \eqref{eq:averaged_f}.
+After multiplication by a test function $\vd \in H^1(\Lambda)$, integration on $\Lambda$ and suitable application of integration by parts, we obtain,
+\begin{multline*}
+\int_\Lambda |\D(s)| \avrd{\partial_s \uf} d_s \vd \, ds - (|\D(s)| \avrd{\partial_s \uf}) \vd |_{s=0}^{s=S}- \int_\Lambda |\DD(s)| \avrc{\lambda} \vd \, ds
++\int_\Lambda |\D(s)| \avrd{u}_\ominus \vd 
+\\
+= \int_\Lambda |\D(s)| \avrd{g} V\, ds\,.
+\end{multline*}
+Using boundary conditions, we obtain,
+\begin{equation}\label{eq:averaged_f_weak}
+  (\avrd{\partial_s \uf}, d_s \vd )_{\Lambda,|\D|} 
++ (\avrd{u}_\ominus, \vd)_{\Lambda, |\D|}
+- (\avrc{\lambda},\vd)_{\Lambda,|\DD|}
+= (\avrd{g},V)_{\Lambda,|\D|}\,.
+\end{equation}
+Let us now formulate the modelling assumption that allows us to reduce equation \eqref{eq:averaged_f_weak} to a solvable one-dimensional (1D) model.
+More precisely, we assume that the function $\uf$ has a \emph{uniform profile} on each cross section $\mathcal{D}(s)$, namely $\uf(r,s,t) = \ud(s)$.
+Therefore, observing that $\ud=\avrc{u}_{\ominus}=\avrd{u}_{\ominus}$, 
+and that $\avrd{\partial_s \uf} = \avrd{\partial_s \ud} = d_s \ud$,
+problem \eqref{eq:averaged_f_weak} turns out to find $\ud \in H^1(\Lambda)$ such that
+\begin{equation}\label{eq:1Ddirneu_weak}
+ (d_s \ud, d_s \vd)_{\Lambda,|\mathcal{D}|} 
++(\ud, \vd)_{\Lambda, |\D|}
+-(\avrc{\lambda},\vd)_{\Lambda, |\DD|}
+=  (\avrd{g},\vd)_{\Lambda, |\mathcal{D}|}
+\quad \forall \vd \in H^1(\Lambda)\,.
+\end{equation}
+
+% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\subsubsection*{Topological model reduction of the problem on $\Omega_{\oplus}$}
+We focus here on the subproblem of \eqref{eq:dirneu1} related to $\Omega_{\oplus}$.
+We multiply both sides of \eqref{eq:dirneu1} by a test function $v\in H^1_0(\Omega)$ and integrate on $\Omega_\oplus$. Integrating by parts and using boundary and interface conditions, we obtain
+\begin{equation*}
+\begin{split}
+\int_{\Omega _{\oplus}}fv\,d\omega&=
+\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\omega -\int _{\partial \Omega _{\oplus}}\nabla \up \cdot \nn_{\oplus} v\,d\sigma + \int_{\Omega_{\oplus}} \up v
+\\
+&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega -\int_{\Gamma} \nabla \up \cdot \nn_{\oplus} v + \int_{\Omega_{\oplus}} \up v
+\\
+&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega +\int_{\Gamma} \lambda v + \int_{\Omega_{\oplus}} \up v.
+\end{split}
+\end{equation*} 
+Then, we make the following modelling assumption:
+we identify the domain $\Omega_{\oplus}$ with the entire $\Omega$, 
+and we correspondingly omit the subscript $\oplus$ to the functions defined on $\Omega_{\oplus}$,
+namely
+\begin{equation*}
+\int_{\Omega_{\oplus}} u_\oplus\, d\omega \simeq \int_{\Omega} u\, d\omega\,.
+\end{equation*}
+Therefore, we obtain 
+\begin{equation*}
+(\nabla u ,\nabla v)_{\Omega} +(u,v)_{\Omega}+(\lambda, v)_{\Gamma}  =(f,v)_{\Omega}
+\end{equation*}
+and combining with \eqref{eq:1Ddirneu_weak} we obtain the first formulation of the reduced problem.
+
+Hence, we have obtained the Problem 3D-2D-1D, equation 
+\eqref{eq:problem1}:
+Find $u \in H^1_0(\Omega), \ \lambda \in H^{-\frac 1 2}(\Gamma ),\ \ud \in H^1_0(\Lambda)$, such that
+\begin{subequations}
+\begin{align*}
+&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
++ \langle \trace v  - \ext \vd, \lambda \rangle_\Gamma &&
+\\
+\nonumber
+&\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}\,,
+\quad &&\forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)\,,
+\\
+& \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0\,,
+\quad && \forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
+\end{align*}
+\end{subequations}
+This coupled problem is classified as 3D-2D-1D because the unknowns $u,\lambda,\ud$ belong to 
+$\Omega \subset \R^3,\, \Gamma \subset \R^2,\, \Lambda \subset \R$, respectively.
+Then, we apply a topological model reduction of the interface conditions, namely we go from a 3D-2D-1D formulation
+involving sub-problems on $\Omega$ and $\Lambda$ and coupling operators defined on $\Gamma$
+to a 3D-1D-1D formulation where the coupling terms are set on $\Lambda$. 
+To this purpose, let us write the Lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
+\begin{equation*}
+\lambda=\avrc{\lambda}+\tilde{\lambda}, \qquad v=\avrc{v}+\tilde{v},
+\quad \text{on} \ \partial\mathcal{D}(s)\,,
+\end{equation*}
+where $\avrc{\tilde{\lambda}}=\avrc{\tilde{v}}=0$. 
+Therefore, the coupling term on $\Gamma$ can be decomposed as,
+\begin{equation*}
+\int_{\Gamma}\lambda v\, d\sigma
+=\int _{\Lambda}  \int_{\partial\mathcal{D}(s)} (\avrc{\lambda}+\tilde{\lambda})(\avrc{v}+\tilde{v})d\gamma ds
+= \int_{\Lambda}|\partial\mathcal{D}(s)| \avrc{\lambda}\avrc{v}\,ds+\int_{\Lambda}  \int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v}d\gamma ds\,.
+\end{equation*}
+Thanks to the additional assumption that the product of fluctuations is small,
+\begin{equation*}
+\int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v} d\gamma \simeq 0\,
+\end{equation*}
+the term $\left(\trace v, \lambda \right)_{\Gamma}$ becomes $\left( \mtrace v, \avrc{\lambda} \right)_{\Lambda, |\DD|}$, where $\mtrace$ denotes the composition of operators $\avrc{(\cdot)}\circ \trace$.
+Combined with \eqref{eq:1Ddirneu_weak}, this leads to the 3D-1D-1D formulation of the reduced problem, namely equation \eqref{eq:problem2}:
+find $u \in H^1_0(\Omega)$, $\ud \in H^1_0(\Lambda)$, $\ld \in H^{-\frac 1 2}(\Lambda)$, such that
+\begin{subequations}
+\begin{align*}
+&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
++  \langle \mtrace v - \vd, \ld \rangle_{\Lambda, |\DD|} &&
+\\
+\nonumber
+&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}\,,
+\quad && \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)\,,
+\\
+& \langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} = 0\,,
+\quad &&\forall \md \in H^{-\frac 1 2}(\Lambda)\,.
+\end{align*}
+\end{subequations}
+% We notice that all the integrals of the reduced problem are well defined because 
+% $\mtrace: H^1_0(\Omega) \rightarrow H^\frac 1 2_{00}(\Lambda)$ as shown in Corollary \ref{corollary:H12norm}.
+
+% The well-posedness of $\eqref{eq:problem1}$ and $\eqref{eq:problem2}$ 
+% can be studied in the framework of the classical theory of saddle point problems as shown in the following.
+
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\section{Proof of Lemma \ref{lemma:H12norm}}
+
+\begin{proof}
+Let us consider the eigenvalue problems for the Laplace operator on $\Gamma$ with homogeneous Dirichlet conditions at $x=0,\, X$ and periodic boundary conditions at $y=0,\, Y$.
+Let us also consider the Laplace eigenproblem on $(0,X)$ with homogeneous Dirichlet conditions.
+Let us denote as $\phi _{ij}(x,y)$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the Laplacian on $\Gamma$, and with $\phi _i(x)$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $(0,X)$.
+In particular,
+\begin{align*}
+&\phi _{ij}(x,y)=\sin \left(\frac{i\pi x}{X}\right)\left( \cos\left(\frac{j2\pi y}{Y}\right)+ \sin\left(\frac{j2\pi y}{Y}\right) \right),\quad
+&&\rho_{ij}=\left(\frac{i\pi}{X}\right) ^2+\left(\frac{j2\pi}{Y}\right)^2,
+\\
+&\phi _{i}(x)=\sin \left(\frac{i\pi x}{X}\right),\quad
+&&\rho _i = \left(\frac{i\pi}{X}\right) ^2.
+\end{align*}
+
+Further, we have
+the following concrete representation of the fractional norms, 
+\begin{equation}\label{eq:fracnorm_lambda}
+\begin{aligned}
+&\|u\|_{H^{\frac 12}_{00}(\Lambda)}=\left(\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|a_i|^2\right)^{\frac 12},\\
+&\|u\|_{H^{\frac 12}_{00}(\Gamma)}=
+\sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ \left(\frac{i\pi}{X}\right)^2 
++ \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12} |a_{i,j}|^2
+\end{aligned}
+\end{equation} 
+with $a_i=\left(u, \phi _i \right)_{\Lambda}$ and $a_{ij}=\left( u, \phi_{ij}\right)_{\Gamma}$.
+It is easy to verify that 
+\begin{equation}\label{int_eigenf}
+\int_0^{Y} \phi _{ij}(x,y)=0 \quad \forall j>0, \forall i\,,
+\quad
+\int_0^{Y} \phi _{ij}(x,y)= Y \, \sin\left(\frac{i\pi x}{X}\right) \quad \mbox{if } j=0, \forall i  .
+\end{equation}
+Moreover we recall that $\phi_{i,j}(x,y)$ and $\phi _i(x)$ form an orthogonal basis of $L^2(\Gamma)$ and $L^2(0,X)$ respectively. Therefore,
+\begin{equation*}
+\avrc{u}(x)=\frac{1}{Y}\int_0^{Y} u(x,y)\, dy
+%= \frac{1}{Y}\int_0^{Y} \sum_{i,j} a_{i,j} \phi_{i,j}(x,y) \, dy
+= \frac{1}{Y}\sum_{i,j} a_{i,j}\int_0^{Y}  \phi_{i,j}(x,y) \, dy
+=  \sum_{i} a_{i,0} \phi_{i}(x).
+\end{equation*}
+
+Let $C=C(X)=\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}$. Then,  
+from \eqref{eq:fracnorm_lambda} we have $\|\avrc{u}\|^2_{H^{\frac 12}_{00}(0,X)}
+=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}a_i^2=$
+\begin{equation*}
+\begin{split}
+=&C\left( \int_0^X \avrc{u}(x) \sin\left(\frac{i\pi x}{X}\right)\, dx \right)^2
+= C\left( \sum_{j=1}^\infty a_{j,0}\int_0^X \sin\left(\frac{j\pi x}{X}\right) \sin\left(\frac{i\pi x}{X}\right) \, dx  \right)\\
+=& \sum_{i=1}^{\infty} \frac{X^2}{4} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}a_{i,0}^2
+\leq \frac{X^2}{4}\sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ \left(\frac{i\pi}{X}\right)^2 
++ \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12} |a_{i,j}|^2\\ =&\frac{X^2}{4}\|u\|^2_{H^{\frac 12}_{00}(\Gamma)},
+\end{split}
+\end{equation*}
+where we have used the orthogonality property
+\begin{equation*}
+\int_0^X \sin\left(\frac{i\pi x}{X}\right) \sin\left(\frac{j\pi x}{X}\right)\, dx=\begin{cases} 0 & i\neq j\\
+\frac X 2 & i = j\\
+\end{cases}
+\end{equation*}
+and we have applied \eqref{eq:fracnorm_lambda} in the last equality.
+Moreover, in the case in which $u$ is constant with respect to $y$, we have
+\begin{equation*}
+    \begin{aligned}
+&\|u\|^2_{H^{\frac 12}_{00}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2\\
+&=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12}\left( \int _0^X\int _0^Y u(x,y )\phi_{ij}(x,y) \right)^2
+\\
+&=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left(  1+ \left(\frac{i\pi}{X}\right)^2 + \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12}\left( \int _0^X u(x) \int _0^Y \phi_{ij}(x,y) \right)^2,
+\end{aligned}
+\end{equation*}
+and using \eqref{int_eigenf} we obtain
+\begin{equation*}
+\begin{aligned}
+\|u\|^2_{H^{\frac 12}_{00}(\Gamma)}
+&=\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}\left(\int _0^X Yu(x)\, \sin\left(\frac{i\pi x}{X}\right)\right)^2\\
+&=Y^2 \sum_{i=1}^{\infty}\left( 1+ \rho _i\right)^{\frac 12}|a_i|^2 = Y^2  \|u\|^2_{H^{\frac 12}_{00}(0,X)}.
+\end{aligned}
+\end{equation*}
+\end{proof}
+
+%>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+\section{System sizes in benchmark formulations} \label{sec:appendix}
 Below we list dimensions of the finite element spaces used to discretize
 formualations \eqref{eq:problem1}, \eqref{eq:problem2} and stabilized
-\eqref{eq:problem2} on different levels of refinement.
+\eqref{eq:problem2} on different levels of refinement. The number of 
+degrees of freedom in subspace $W_{i, h}$ is denote as $\lvert W_{i, h}\rvert$. 
+We recall that the discrete spaces in the respected formulations 
+are $X^1_{h, 0}(\Omega)\times X^1_{h, 0}(\Lambda)\times Q_h(\Gamma)$,
+      $X^1_{h, 0}(\Omega)\times X^1_{h, 0}(\Lambda)\times Q_h(\Lambda)$,
+      and 
+      $X^1_{h, 0}(\Omega)\times X^1_{h^{\prime}, 0}(\Lambda)\times Q_h(\mathcal{G}_h)$.
 
@@
     \begin{tabular}{l|lll|lll|lll}
-      \toprule
+      %\toprule
+      \hline
       \multirow{2}{*}{$l$} & \multicolumn{3}{c|}{\eqref{eq:problem1}} & \multicolumn{3}{c|}{\eqref{eq:problem2}} & \multicolumn{3}{c}{ Stabilized \eqref{eq:problem2}}\\
       \cline{2-10}
-      & $\lvert X^1_{h, 0}(\Omega) \rvert$ & $\lvert X^1_{h, 0}(\Lambda) \rvert$ & $\lvert Q_h(\Gamma) \rvert$ &
-      $\lvert X^1_{h, 0}(\Omega) \rvert$ & $\lvert X^1_{h, 0}(\Lambda) \rvert$ & $\lvert Q_h(\Lambda) \rvert$ &
-      $\lvert X^1_{h, 0}(\Omega) \rvert$ & $\lvert X^1_{h^{\prime}, 0}(\Lambda) \rvert$ & $\lvert Q_h(\mathcal{G}_h) \rvert$\\
+       & $\lvert W_{1, h}\rvert$  & $\lvert W_{2, h}\rvert$ & $\lvert W_{3, h}\rvert$ 
+       & $\lvert W_{1, h}\rvert$  & $\lvert W_{2, h}\rvert$ & $\lvert W_{3, h}\rvert$
+       & $\lvert W_{1, h}\rvert$  & $\lvert W_{2, h}\rvert$ & $\lvert W_{3, h}\rvert$\\
+      %& $\lvert X^1_{h, 0}(\Omega) \rvert$ & $\lvert X^1_{h, 0}(\Lambda) \rvert$ & $\lvert Q_h(\Gamma) \rvert$ &
+      %$\lvert X^1_{h, 0}(\Omega) \rvert$ & $\lvert X^1_{h, 0}(\Lambda) \rvert$ & $\lvert Q_h(\Lambda) \rvert$ &
+      %$\lvert X^1_{h, 0}(\Omega) \rvert$ & $\lvert X^1_{h^{\prime}, 0}(\Lambda) \rvert$ & $\lvert Q_h(\mathcal{G}_h) \rvert$\\
       \hline
@@
      4& 35937  & 33 & 2112 & 35937   & 33  & 33  & 38148   & 97  & 192 \\
-     5& 274625 & 65 & 8320 & 274625  & 65  & 65  & 283140  & 193 & 384 \\
-     6& --     & -- & -    & 2146689 & 129 & 129 & 2180100 & 385 & 768 \\
-      \bottomrule
+     5& 275K & 65 & 8320 & 275K  & 65  & 65  & 283K  & 193 & 384 \\
+     6& --     & -- & -    & 2.15M & 129 & 129 & 2.18M & 385 & 768 \\
+     %\bottomrule
+     \hline
     \end{tabular}

### 2020-03-30 3d1d_coupled_LM.tex

@@
 \hline
-    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & $\norm{\lambda-\lambda_h}_{-\tfrac{1}{2},\Gamma}$ & $\norm{\lambda-\lambda_h}_{0,\Gamma}$\\
+    $h^{-1}$ & $\norm{u-u_h}_{H^1(\Omega)}$ & $\norm{\ud-\udh}_{H^1(\Lambda)}$ & $\norm{\lambda-\lambda_h}_{H^{-1/2}(\Gamma)}$ & $\norm{\lambda-\lambda_h}_{L^2(\Gamma)}$\\
       \hline
@@
 \hline
-$h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-u_{\odot h^{\prime}}}_{1, \Lambda}$ & $\norm{\ld-\ldh}_{-\tfrac{1}{2}, \Lambda}$ & $\norm{\ld-\ldh}_{0, \Lambda}$\\
+$h^{-1}$ & $\norm{u-u_h}_{H^1(\Omega)}$ & $\norm{\ud-u_{\odot}}_{H^1(\Lambda)}$ & $\norm{\ld-\ldh}_{H^{-1/2}(\Lambda)}$ & $\norm{\ld-\ldh}_{L^2(\Lambda)}$\\
 \hline
@@
 \hline
-    $h^{-1}$ & $\norm{u-u_h}_{1, \Omega}$ & $\norm{\ud-\udh}_{1, \Lambda}$ & \multicolumn{2}{c}{$\norm{\ld-\ldh}_{0,\Lambda}$}\\
+    $h^{-1}$ & $\norm{u-u_h}_{H^1(\Omega)}$ & $\norm{\ud-u_{\odot\mathfrak{h}}}_{H^1(\Lambda)}$ & \multicolumn{2}{c}{$\norm{\ld-\ldh}_{L^2(\mathcal{G}_h)}$}\\
       \hline
@@
     $\mathcal{T}^{\Omega}_h$ does not conform to $\Lambda$. Continuous linear Lagrange
-    elements are used for $u_h$, $\udh$ and $u_{\odot h^{\prime}}$ and $\ldh$ in
+    elements are used for $u_h$, $\udh$ and $u_{\odot \mathfrak{h}}$ and $\ldh$ in
     conforming case, while in nonconforming case $\ldh$ is piecewise constant

### 2020-03-30 appendix.tex
MK sweep

@@
 
-Hence, we have obtained the Problem 3D-2D-1D, equation 
+Hence, we have obtained the Problem 3D-1D-2D, equation 
 \eqref{eq:problem1}:
@@
 \end{subequations}
-This coupled problem is classified as 3D-2D-1D because the unknowns $u,\lambda,\ud$ belong to 
-$\Omega \subset \R^3,\, \Gamma \subset \R^2,\, \Lambda \subset \R$, respectively.
-Then, we apply a topological model reduction of the interface conditions, namely we go from a 3D-2D-1D formulation
+This coupled problem is classified as 3D-1D-2D because the unknowns $u$, $\ud$, $\lambda$ belong to 
+$\Omega \subset \R^3$, $\Lambda \subset \R$ and $\Gamma \subset \R^2$ respectively.
+Then, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-2D formulation
 involving sub-problems on $\Omega$ and $\Lambda$ and coupling operators defined on $\Gamma$
@@
 Let us also consider the Laplace eigenproblem on $(0,X)$ with homogeneous Dirichlet conditions.
-Let us denote as $\phi _{ij}(x,y)$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the Laplacian on $\Gamma$, and with $\phi _i(x)$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $(0,X)$.
+Let us denote as $\phi _{ij}(x,y)$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the Laplacian on $\Gamma$, and with $\phi _i(x)$ and $\rho _i$ the eigenfunctions and the eigenvalues of the Laplacian on $(0,X)$.
 In particular,
@@
       and 
-      $X^1_{h, 0}(\Omega)\times X^1_{h^{\prime}, 0}(\Lambda)\times Q_h(\mathcal{G}_h)$.
+      $X^1_{h, 0}(\Omega)\times X^1_{\mathfrak{h}, 0}(\Lambda)\times Q_h(\mathcal{G}_h)$.
 
@@
        & $\lvert W_{1, h}\rvert$  & $\lvert W_{2, h}\rvert$ & $\lvert W_{3, h}\rvert$
-       & $\lvert W_{1, h}\rvert$  & $\lvert W_{2, h}\rvert$ & $\lvert W_{3, h}\rvert$\\
+       & $\lvert W_{1, h}\rvert$  & $\lvert W_{2, \mathfrak{h}}\rvert$ & $\lvert W_{3, h}\rvert$\\
       %& $\lvert X^1_{h, 0}(\Omega) \rvert$ & $\lvert X^1_{h, 0}(\Lambda) \rvert$ & $\lvert Q_h(\Gamma) \rvert$ &

### 2020-04-06 3d1d_coupled_LM.tex
MK sweep
Arxiv-ed version

@@
 
-\newcommand{\kent}[1]{{\color{blue}#1}}
-\newcommand{\miro}[1]{{\color{cyan}#1}}
-\newcommand{\paolo}[1]{{\color{magenta}#1}}
+\newcommand{\kent}[1]{{\color{black}#1}}
+\newcommand{\miro}[1]{{\color{black}#1}}
+\newcommand{\paolo}[1]{{\color{black}#1}}
 % Title. If the supplement option is on, then "Supplementary Material"
@@
 %\title{On the weak coupling of 3D and 1D second order elliptic problems}
-\title{Coupling PDEs on 3D-1D domains with Lagrange multipliers}
+% \title{Coupling PDEs on 3D-1D domains\\ with Lagrange multipliers}
+\title{Analysis and approximation of mixed-dimensional PDEs on 3D-1D domains coupled with Lagrange multipliers}
 
 % Authors: full names plus addresses.
-\author{Miroslav Kuchta, Federica Laurino, Kent-Andre Mardal, Paolo Zunino,\thanks{Authors are listed in alphabetical order}}
+\author{M.
+Kuchta\thanks{Simula Research Laboratory, Oslo, Norway (\email{miroslav@simula.no})}\and F.
+Laurino\thanks{MOX, Department of Mathematics, Politecnico di Milano, Italy (\email{federica.laurino@polimi.it})} \and K.A.
+Mardal\footnotemark[1]$^{\;,}$\thanks{University of Oslo, Department of Mathematics (\email{kent-and@math.uio.no})} \and P.
+Zunino\thanks{MOX, Department of Mathematics, Politecnico di Milano, Italy (\email{paolo.zunino@polimi.it}), Corresponding Author}}
 
@@
 \begin{abstract}
-Manuscript in preparation, to be kept confidential.
+Coupled partial differential equations defined on domains with different dimensionality are usually called mixed dimensional PDEs.
+We address mixed dimensional PDEs on three-dimensional (3D) and one-dimensional domains, giving rise to a 3D-1D coupled problem.
+Such problem poses several challenges from the standpoint of existence of solutions and numerical approximation.
+For the coupling conditions across dimensions, we consider the combination of essential and natural conditions, basically the combination of Dirichlet and Neumann conditions.
+To ensure a meaningful formulation of such conditions, we use the Lagrange multiplier method, suitably adapted to the mixed dimensional case.
+The well posedness of the resulting saddle point problem is analyzed.
+Then, we address the numerical approximation of the problem in the framework of the finite element method.
+The discretization of the Lagrange multiplier space is the main challenge.
+Several options are proposed, analyzed and compared, with the purpose to determine a good balance between the mathematical properties of the discrete problem and flexibility of implementation of the numerical scheme.
+The results are supported by evidence based on numerical experiments.
 \end{abstract}
@@
 \begin{keywords}
-elliptic problems, high dimensionality gap, essential coupling conditions, Lagrange multipliers
+mixed dimensional PDEs, finite elemet approximation, essential coupling conditions, Lagrange multipliers
 \end{keywords}
@@
 \label{eq:coupling}
-\mathcal{T}_\Lambda u - v  &=  h &\mbox{ on } \Lambda . 
+\mathcal{T}_\Lambda u - \ud  &=  \paolo{q} &\mbox{ on } \Lambda . 
 \end{align}
@@
 We overcome this difficulty by  resorting to a weak formulation of the Dirichlet-Neumann coupling conditions across dimensions by using Lagrange multipliers.
+
+\paolo{Although the focus of the present work is mostly about analysis and approximation of the proposed approach, we stress that it aims to build the mathematical foundations to tackle various applications involving 3D-1D mixed dimensional PDEs, such as FSI of slender bodies \cite{Mori2019887}, microcirculation and lymphatics \cite{Possenti2019101,Vinje2019}, subsurface flow models with wells \cite{Cerroni2019} and the electrical activity of neurons.}
 
@@
 We assume that $\Omega_{\ominus}$ crosses $\Omega$ from side to side.
+ \paolo{Finally, $|\cdot|$ denotes the Lebesgue measure of a set, e.g. $|\mathcal{D}(s)|$ is the cross-sectional area of the cylinder. In general, $|\D(s)|$ must be strictly positive and bounded.}
 According to the geometrical setting, we will denote with $v,\,v_\oplus,\,v_\ominus,\,\vd$,
@@
 
-Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. We denote with $\mathcal{T}_\Sigma: H^q(D) \rightarrow H^{q-\frac 1 2}(\Sigma)$ the trace operator from $\Omega$ to $\Sigma$.
+Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. We denote with $\mathcal{T}_\Sigma: H^q(D) \rightarrow H^{q-\frac 1 2}(\Sigma)$ the trace operator from \kent{$D$} to $\Sigma$.
 The space of functions in $H^{\frac 1 2}(\Sigma)$ with continuous extension by zero outside $\Sigma$ is denoted 
@@
 weighted by a scalar function 
-$w$, which is positive almost everywhere,
+$w$, which is strictly positive and bounded almost everywhere,
 are defined as 
 follows
-\begin{eqnarray*}
+\begin{equation*}
 %(u,v)_{\Gamma, w} = 
-(u,v)_{L^2(\Omega), w} &=& 
-\int_{\Omega} w \, u \, v d\omega \\
+(u,v)_{L^2(\Omega), w} = 
+\int_{\Omega} w \, u \, v d\omega \ \mbox{   and   } \
 %(u,v)_{\Gamma, w} = 
-(u,v)_{H^1(\Omega), w} &=& 
+(u,v)_{H^1(\Omega), w} = 
 \int_{\Omega}  w \, u \, v d\omega
 + \int_{\Omega} w \, \nabla u \cdot \nabla v d\omega
-\end{eqnarray*}
+\end{equation*}
 whereas a weighted fractional
 space \miro{$H^s(\Gamma; w)$} is defined in terms of the interpolation of the corresponding weighted spaces. 
-That is, let $S$ denote the
-Riesz map such that 
+For the norm of such spaces, we introduce 
+the Riesz map $S$ such that 
 for $u, v \in H^1(\Gamma)$ we have 
@@
 Assuming that $\{\lambda_k\}_k$ is the set of eigenvalues, 
-$\{\phi_k\}_k$ the set of eigenvectors orthonormal with respect to the inner 
+$\{\phi_k\}_k$ the set of eigenvectors of $S$ 
+orthonormal with respect to the inner 
 product $(\cdot, \cdot)_{L^2(\Gamma), w}$ and $u\in H^1(\Gamma)$ can be expressed 
@@
 \[
-\|u\|^2_{H^s(\Gamma), w} = \sum \lambda_k^{-1} c_k^2 .   
+\|u\|^2_{H^s(\Gamma), w} = \sum_k \lambda_k^{-s} c_k^2 .   
 \]
 The space $H_{00}^s(\Gamma; w)$ is defined analogously, but with $S$ above defined in terms of the $H^1_0$ inner product.
-The weighted spaces equal the corresponding non-weighted spaces as sets, but their norms are different. \miro{Not sure about the last sentence.}
+Owing to the positivity and boundedness of $w$ the weighted spaces equal the corresponding non-weighted spaces as sets, but their norms are different.
  }
- Finally, $|\cdot|$ denote the Lebesgue measure of a set, i.e.
-$|\mathcal{D}(0)|$ is the cross-sectional area of the bottom of the cylinder.
-In the following we assume that the cross-sectional area $\mathcal{D}(s)$ is constant, namely $\mathcal{D}(s)=\mathcal{D}$, but remark that this assumption is only made to simplify the notation.
+
 Central in our analysis are the transverse averages $\avrc{w},\,\avrd{w}$ defined as, 
@@
 
-With the above notation we are now able to formulate the precise weak formulations of the problems \eqref{eq:pde} and \eqref{inteq:pde}.
-The weak formulation of \eqref{eq:pde}, which we will call the \textbf{Problem 3D-1D-1D} reads:  Find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac 1 2}(\Lambda)$, such that
+\kent{With the above notation we are now able to formulate the precise weak formulations of the problems \eqref{eq:pde}, which we will call the \textbf{Problem 3D-1D-1D}. The problem} reads:
+\paolo{given $f\in L^2(\Omega), \ g \in L^2(\Omega_{\ominus}), \ q \in H^\frac12_{00}(\Gamma)$}
+find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac 1 2}(\Lambda)$, such that
 \begin{subequations}\label{eq:problem2}
 \begin{align}
+\label{eq:problem2a}
 (u,v)_{H^1(\Omega)} 
 +  \langle \mtrace v, \ld \rangle_{\Lambda, |\DD|} &= 
-(f,v)_{L^2(\Omega)} &\forall v \in H^1_0(\Omega)\, ,\\
+(f,v)_{L^2(\Omega)} &\forall v \in H^1_0(\Omega)\, ,
+\\
+\label{eq:problem2b}
 (\ud,\vd)_{H^1(\Lambda),|\D|} - \langle  \vd, \ld \rangle_{\Lambda, |\DD|} 
 &=  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
-&\forall \vd \in H^1_0(\Lambda)\, ,\\
-\langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} &= 0
+&\forall \vd \in H^1_0(\Lambda)\, ,
+\\
+\label{eq:problem2c}
+\langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} 
+&= \paolo{\langle \avrc{q},\md\rangle_{\Lambda,|\DD|}}
 &\forall \md \in H^{-\frac 1 2}(\Lambda)\,.
@@
 intermediate problem where the 3D and 1D problems are coupled at an
-intermediate 2D surface  encapsulating the 1D structure. The strong form is \miro{The strong form does not seem correct}:  
+intermediate 2D surface  encapsulating the 1D structure. The strong form is:  
+\paolo{
 \begin{subequations}
@@
 \label{inteq:pde1}
-  -\Delta u + u + \lambda \delta_{\Lambda} &= f &\mbox{ in } \Omega,\\ 
+  -\Delta u + u + \lambda \delta_{\Gamma} &= f &\mbox{ in } \Omega,\\ 
 \label{inteq:pde2}
- d_s^2 \ud + \ud - \lambda &= g &\mbox{ on } \Lambda,\\
+ d_s^2 \ud + \ud -  \avrc{\lambda} &= \avrd{g} &\mbox{ on } \Lambda,\\
 \label{inteq:coupling}
-\mathcal{T}_\Lambda u - v  &=  h &\mbox{ on } \Gamma . 
+\mathcal{T}_\Gamma u - \mathcal{E}_\Gamma \ud  &=  q &\mbox{ on } \Gamma . 
 \end{align}
 \end{subequations}
+}
 The corresponding weak formulation of \eqref{inteq:pde}, referred to as the \textbf{Problem 3D-1D-2D}, reads: 
-Find $u \in H^1_0(\Omega), \ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac 1 2}(\Gamma ) $ such that
+\paolo{given $f\in L^2(\Omega), \ g \in L^2(\Omega_{\ominus}), \ q \in H^\frac12_{00}(\Gamma)$}
+find $u \in H^1_0(\Omega), \ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac 1 2}(\Gamma ) $ such that
 \begin{subequations}\label{eq:problem1}
@@
  (\ud,\vd)_{H^1(\Lambda),|\D|}  -  \langle \ext \vd, \lambda \rangle_\Gamma
-&=  (\avrd{g},\vd)_{L^2(\Lambda),|\D|} &\forall\vd \in H^1(\Lambda)\, ,\\
-\langle \trace u - \ext \ud , \mu \rangle_\Gamma &= 0 &\forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
+&=  (\avrd{g},\vd)_{L^2(\Lambda),|\D|} &\forall\vd \in H^1(\Lambda)\, ,
+\\
+\langle \trace u - \ext \ud , \mu \rangle_\Gamma 
+&= \paolo{\langle q,\md\rangle_\Gamma} 
+&\forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
 \end{align}
@@
 \begin{corollary}\label{corollary:H12norm}
-If $u\in H^{\frac 12}_{00}(\Gamma)$ then $\avrc{u}\in H^{\frac 12}_{00}(\Lambda)$ and there exists a constant $C_\Gamma$ such that
+If $u\in H^{\frac 12}_{00}(\Gamma)$ then $\avrc{u}\in H^{\frac 12}_{00}(\Lambda)$ and there exists a constant $C_\Gamma$, \paolo{bounded independently of $\D$ and $\DD$, such that}
 \begin{equation*}
@@
 \end{equation*}
-\kent{Here, $C_\Gamma$ is bounded independently of $\mathcal{D}(s)$.} 
 \end{corollary}
+\paolo{
+Furthermore, from the
+above Corollary, it is clear that
+$\mtrace: H^1_0(\Omega) \rightarrow H^\frac 1 2_{00}(\Lambda)$.
+}
 
@@
 \\
-d(\mu)&=0.
+d(\mu)&=\paolo{\langle q,\mu\rangle_\Gamma}.
 \end{align*}
@@
 \paolo{
-To show the inf-sup condition, we will employ $\mathcal{H}_\Omega$ 
-a lifting operator from $H^{1/2}_{00}(\Gamma)$ to $H^1(\Omega)$.
-Using the results of \cite{sauter1999extension} about extension operators for domains having small geometric details (see also \cite{laurino_m2an} for a direct application to this case) there exists a lifting operator $\mathcal{H}_\Omega$ from $H^{1/2}_{00}(\Gamma)$ to $H^1(\Omega)$ such that $\mathcal{H}_\Omega \xi = v$ for any $\xi \in H^{1/2}_{00}(\Gamma)$ with $v\in H^1(\Omega)$ and the boundedness/stability of this operator ensures that there exists
+To show the inf-sup condition, we will employ  
+a lifting operator,  
+$\mathcal{H}_\Omega$,
+from $H^{1/2}_{00}(\Gamma)$ to $H^1(\Omega)$.
+In \cite{sauter1999extension} 
+it is established that extension operators for domains having small geometric details (see also \cite{laurino_m2an} for a direct application to this case) there exists a lifting operator $\mathcal{H}_\Omega$ from $H^{1/2}_{00}(\Gamma)$ to $H^1(\Omega)$ such that $\mathcal{H}_\Omega \xi = v$ for any $\xi \in H^{1/2}_{00}(\Gamma)$ with $v\in H^1(\Omega)$.
+Further, for this operator   there exists
 $\| \mathcal{H}_\Omega \| \in \mathbb{R}$ such that
@@
 \\
-d(\md)&=0.
+d(\md)&=\paolo{\langle \avrc{q},\md\rangle_{\Lambda,|\DD|}}.
 \end{align*}
@@
 \label{eq:infsup_discrete}
- \sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}}\geq \beta_h \|\mu_h\|_{Q}\, .
+ \sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}}\geq \beta_h \|\mu_h\|_{Q}\,, \kent{\quad \forall \mu_h \in Q_h.}
 \end{align}
@@
 \\
-&\langle \trace u_h - \mathcal{E}_{\Lambda} {\ud}_h , \mu_h \rangle_\Gamma = 0
+&\langle \trace u_h - \mathcal{E}_{\Lambda} {\ud}_h , \mu_h \rangle_\Gamma 
+= \paolo{\langle q,\mu_h \rangle_\Gamma}
 \quad \forall \mu_h \in Q_h\,.
@@
 \end{subequations}
-In what follows we analyze the well-posedness of the discrete problem. 
+In what follows, we analyze the well-posedness of the discrete problem. 
 From now on, $C$ denotes a generic constant independent of the mesh size.
@@
 to guarantee that the operator $\trace R_h  \mathcal{H}_{\Omega}$ coincides with the identity on the space $Q_h$. Then, for any $q_h \in Q_h$ we have $q_h = \trace R_h  \mathcal{H}_{\Omega} q_h$
-and owing to this property we obtain the following inequality, which proves the thesis with $\beta_{h,1} = \gamma \|\mathcal{H}_{\Omega}\|^{-1} C_R^{-1}$,
+and owing to this property we obtain the following inequality, which proves the condition, with $\beta_{h,1} = \gamma \|\mathcal{H}_{\Omega}\|^{-1} C_R^{-1}$,
 \begin{multline*}
@@
 \nonumber
-&\quad = (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda), |{\cal D}|}
+&\quad = (f,v_h)_{L^2(\Omega)} + (\avrd{g},{\vd}_h)_{L^2(\Lambda),|\D|}
 \quad \forall v_h \in X_h(\Omega), \ {\vd}_h \in X_h(\Lambda)\,,
 \\
-& \langle \mtrace u_h - {\ud}_h, \mdh \rangle_{\Lambda,| \DD| } = 0
+& \langle \mtrace u_h - {\ud}_h, \mdh \rangle_{\Lambda,| \DD| } 
+= \paolo{\langle \avrc{q},\mdh \rangle_{\Lambda,|\DD|}}
 \quad \forall \mdh \in Q_h\,.
@@
 As a result, from Lemma \ref{infsup_avr_trspace}, we obtain the following inequality
-\begin{multline*}
-\gamma \|\mdh\|_{H^{-\frac 12}(\Lambda)} \leq 
+\begin{align*}
+\gamma \|\mdh\|_{H^{-\frac 12}(\Lambda)} &\leq 
 \sup_{q_h \in Q_h} \frac{ \langle q_h, \mdh \rangle_{\Lambda,|\DD|} } {\|q_h\|_{H^{\frac 12}_{00}(\Lambda),|\DD|}} 
@@
 \\
-\leq \|\mathcal{H}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mdh \rangle _{\Lambda,|\DD|} } {\|\mathcal{H}_{\Omega} \ext q_h\|_{H^1(\Omega)}} 
+&\leq \|\mathcal{H}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mdh \rangle _{\Lambda,|\DD|} } {\|\mathcal{H}_{\Omega} \ext q_h\|_{H^1(\Omega)}} 
 \leq C_R\|\mathcal{H}_{\Omega}\| \sup_{q_h \in Q_h} \frac{ \langle q_h, \mdh \rangle _{\Lambda,|\DD|} } {\|R_h \mathcal{H}_{\Omega} \ext q_h\|_{H^1(\Omega)}}
 \\
-=  C_R\|\mathcal{H}_{\Omega}\|\sup_{q_h \in Q_h} \frac{ \langle \mtrace R_h \mathcal{H}_{\Omega} \ext q_h, \mdh \rangle _{\Lambda,|\DD|}} {\|R_h \mathcal{H}_{\Omega} \ext w_h\|_{H^1(\Omega)}}
-\leq C_R\|\mathcal{H}_{\Omega}\| \sup_{v_h \in X_{h,0}^k} \frac{ \langle \mtrace v_h, \mdh \rangle _{\Lambda,|\DD|}} {\|v_h\|_{H^1(\Omega)}}\,,
-\end{multline*}
+&=  C_R\|\mathcal{H}_{\Omega}\|\sup_{q_h \in Q_h} \frac{ \langle \mtrace R_h \mathcal{H}_{\Omega} \ext q_h, \mdh \rangle _{\Lambda,|\DD|}} {\|R_h \mathcal{H}_{\Omega} \ext w_h\|_{H^1(\Omega)}} \\
+&\leq C_R\|\mathcal{H}_{\Omega}\| \sup_{v_h \in X_{h,0}^k} \frac{ \langle \mtrace v_h, \mdh \rangle _{\Lambda,|\DD|}} {\|v_h\|_{H^1(\Omega)}}\,,
+\end{align*}
 that concludes the proof with $\beta_{h,2} = \gamma \|\mathcal{H}_{\Omega}\|^{-1} C_R^{-1}$.
@@
 However, with this choice of multipliers the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s(\ldh, \mdh): \ Q_h \times Q_h \rightarrow \mathbb{R}$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}.
-The objective of this section is to analyze the stabilized version of the 3D-1D-1D problem: find $[u_h, {\ud}_h] \in X_h$ and $\ldh \in Q_h$ such that
+The objective of this section is to analyze the stabilized version of the 3D-1D-1D problem: find $[u_h, \kent{\udfh]} \in X_h$ and $\ldh \in Q_h$ such that
 \begin{multline}\label{eq:prob2_stabilized}
@@
 Thanks to the shape regularity of these extended patches, the following discrete trace inequality holds true for any function $v\in H^1(\omega_j)$, 
+\paolo{
 \begin{equation}\label{discr_trace_ineq}
-\|\trace v\|_{L^2(\Gamma\cap \omega_j)} \leq C H^{-\frac 12} \|v\|_{L^2(\omega_j)}
+\|\trace v\|_{L^2(\Gamma\cap \omega_j)} \leq C_I H^{-\frac 12} \|v\|_{L^2(\omega_j)}
 \end{equation}
+}
 Moreover, $\forall u_h \in X^1_{h,0}(\Omega)$ we have the following average inequality, 
-which is a consequence of the definition of $\mtrace$ and Jensen inequality,
+which is a consequence of the definition of $\mtrace$, Jensen inequality, \kent{and the fact that the patches are disjoint}
 \begin{multline}\label{eq:avrg_ineq}
@@
 \end{multline}
+%\kent{Earlier in the paper we always specified the measure, ds, dx etc}
 
@@
 Owing to these properties it is possible to satisfy \eqref{phi_properties}. 
-Then, using the properties of $\varphi_j$ we have
+\kent{Then, by construction,}
 \begin{multline*}
@@
 $|\patch\cap \Lambda| \leq cH$,
-exploiting Jensen's, average inequality \eqref{eq:avrg_ineq} 
+\kent{exploiting Jensen's average inequality} \eqref{eq:avrg_ineq} 
 and trace inequality \eqref{discr_trace_ineq},
 and finally applying the approximation properties of $I_h$,
-the following upper bound holds true,
+the following upper bound holds true
+\paolo{(where all the constants have been condensed into $C$),}
 \begin{multline*}
@@
 
-For the second assumption of Lemma \ref{lemma23burman}, we recall that $b(v_h,\mdh)$ is continuous in the norms $\vertiii{v_h},\,\|\mdh\|_{L^2(\Lambda)}$. 
+For the second assumption of Lemma \ref{lemma23burman}, we recall that $b(v_h,\mdh)$ is continuous \kent{with respect to the norms} $\vertiii{v_h},\,\|\mdh\|_{L^2(\Lambda)}$. 
 Using Lemma \ref{lemma:Lh_infsup}, and in particular the existence of a Fortin projector,
@@
 For the second term, we apply the additional assumption that the operators $\mtrace$ and $\partial_s$ commute. This is true if the cross section $\D$ does not depend on the arclength $s$.
+\paolo{
 Then, we use the Poincar\'e inequality \eqref{disc_poincare_ineq}, the average inequality \eqref{eq:avrg_ineq} and the trace inequality \eqref{discr_trace_ineq} to show that,
@@
 \\
-\leq C H^2 \sum _j \|\trace \partial_s u_h\|_{L^2(\omega _j \cap \Gamma)}^2
-\leq C H \sum _j \|\nabla u_h\|_{L^2(\omega _j)}^2.
+\leq C_P^2 H^2 \sum _j \|\trace \partial_s u_h\|_{L^2(\omega _j \cap \Gamma)}^2
+\leq C_P^2 C_I^2 H \sum _j \|\nabla u_h\|_{L^2(\omega _j)}^2.
 \end{multline*}
@@
 % \end{multline*}
-\paolo{For the third term we observe that since $H \lesssim 1$, there exists a constant $C$ 
-such that $C_P^2 H|\DD| \leq C |\D|$. As a result, the following upper bound holds true,
+% \kent{Is it $C_P$}
+% \paolo{For the third term we observe that since $H \lesssim 1$, there exists a constant $C$ 
+% such that $C_P^2 H|\DD| \leq C |\D|$.
+For the third term, the following upper bound holds true,
 \begin{multline*}
@@
 \\
-\leq C_P^2 H \frac{\max |\DD|}{\min |\D|} \sum _j \|\partial_s \udfh\|_{L^2(\patch\cap \Lambda),|\D|}^2.
+\leq C_P^2 H^2 \frac{\max |\DD|}{\min |\D|} \sum _j \|\partial_s \udfh\|_{L^2(\patch\cap \Lambda),|\D|}^2.
 \end{multline*}
@@
 a([u_h, \udfh],[u_h, \udfh] ) + b([u_h, \udfh], \xi_h([u_h, \udfh]))
-\geq (1-\delta C) \|\nabla u_h\|^2_{L^2(\Omega)} 
-\\
-+ \left(1- \delta C_P^2 \frac{\max |\DD|}{\min |\D|}\right) \|\partial_s \udfh\|^2_{L^2(\Lambda), |\D|}
+\geq (1-\delta C_P^2 C_I^2) \|\nabla u_h\|^2_{L^2(\Omega)} 
+\\
++ \left(1- \delta C_P^2 H \frac{\max |\DD|}{\min |\D|}\right) \|\partial_s \udfh\|^2_{L^2(\Lambda), |\D|}
 +\delta c_H  \|\mtrace u_h-\udfh\|^2_{\frac 12,h,\Lambda, |\DD|}
 \end{multline*}
-and choosing $\delta=\frac{1}{2}\min\left[C^{-1}, \left(C_P^2 \frac{\max |\DD|}{\min |\D|}\right)^{-1}\right]$ we obtain the desired inequality.}\\
-Concerning inequality \eqref{stab_stability}, the proof is analogous to the one in \cite{burman2014}.
+and choosing $\delta=\frac{1}{2}\min\left[(C_P^2 C_I^2)^{-1}, \left(C_P^2 H \frac{\max |\DD|}{\min |\D|}\right)^{-1}\right]$ we obtain the desired inequality.
+Concerning inequality \eqref{stab_stability}, the proof is analogous to the one in \cite{burman2014}.}
 \end{proof}
@@
 \label{benchm_1d}
--d_{zz}^2 \ud =g \quad &\text{on $\Lambda$},\\
+-d_{zz}^2 \ud =\avrd{g} \quad &\text{on $\Lambda$},\\
 u=u_b \quad &\text{on $\partial \Omega$},
@@
     \label{eq:couple_2}
-\avrc{u} - \ud = q_2\quad\text{ on }\Lambda.
+\avrc{u} - \ud = \avrc{q}_2\quad\text{ on }\Lambda.
 \end{equation}
@@
 \begin{eqnarray*}
-  &f=8\pi ^2 \sin (2\pi x) \sin (2\pi y),\quad &g={\pi ^2}\sin \left({\pi z}\right),\quad u_b=\sin (2\pi x) \sin (2\pi y),\\
-  &q_1=\sin (2\pi x) \sin (2\pi y) - \sin \left({\pi z}\right),\quad &q_2=-\sin \left({\pi z}\right).
+  &f=8\pi ^2 \sin (2\pi x) \sin (2\pi y),\quad &\avrd{g}={\pi ^2}\sin \left({\pi z}\right),\quad u_b=\sin (2\pi x) \sin (2\pi y),\\
+  &q_1=\sin (2\pi x) \sin (2\pi y) - \sin \left({\pi z}\right),\quad &\avrc{q}_2=-\sin \left({\pi z}\right).
 \end{eqnarray*}
@@
 %
-\begin{eqnarray}
-\label{benchm_sol3d}
-u=\sin (2\pi x) \sin (2\pi y),\\
-\label{benchm_sol1d}
+\begin{equation}
+\label{benchm_sol3d-1d}
+u=\sin (2\pi x) \sin (2\pi y),
+\quad
 %\ud=1+\exp(-z).
 \ud=\sin \left({\pi z}\right).
-\end{eqnarray}
+\end{equation}
 %
 Let us notice that $\ud$ satisfies homogeneous Dirichlet conditions at the boundary of $\Lambda$.
-Moreover, the solution \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfies on $\Gamma$ the relation
+Moreover, the solution \eqref{benchm_sol3d-1d} satisfies on $\Gamma$ the relation
 \begin{equation}\label{benchm_flux}
-L=\nabla u \cdot \textbf{n}_{\oplus}=d_z \ud n_{\oplus,z}=0,
+\nabla u \cdot \textbf{n}_{\oplus}=d_z \ud n_{\oplus,z}=0,
 \end{equation}
@@
 
-We prove that \eqref{benchmark} is solution of \eqref{eq:problem2} in the
-simplified case in which the starting 3D-3D problem is
-\begin{subequations}\label{eq:dirneu_simple}
-\begin{align}
-- \Delta \up  &= f  && \text{ in } \Omega_{\oplus},\\
-- \Delta \uf &= g  && \text{ in } \Omega_{\ominus},\\
--\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
-\uf - \up &= q_i  && \text{ on }  \Gamma,\\
-\up &= h && \text{ on } \partial \Omega,
-\end{align}
-\end{subequations}
-instead of \eqref{eq:dirneu}. Therefore the reduced problems in \eqref{eq:problem1} and
-\eqref{eq:problem2} become respectively
-%
-\begin{subequations}\label{eq:problem1_simple}
-\begin{align}
-\label{eq:problem1_simple_eq1}
-&(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
-+ \langle \trace{v}  - \ext{\vd}, \lambda \rangle_\Gamma
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
-\\
-\label{eq:problem1_simple_eq2}
-&   \langle \trace{u} - \ext{\ud} , \mu \rangle_\Gamma =  \langle q_1 , \mu \rangle_\Gamma
-\quad \forall \mu \in H^{-\frac12}(\Gamma)
-\end{align}
-\end{subequations}
-and
-\begin{subequations}\label{eq:problem2_simple}
-  \begin{align}
-    \label{eq:problem2_simple_eq1}
-&(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
-+ |{\partial \cal D}| \langle \avrc{v} - \vd, \ld \rangle_{H^{-\frac12}(\Lambda)} 
-\\
-\nonumber
-&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g}, \vd)_{L^2(\Lambda)}
-\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
-\\
-\label{eq:problem2_simple_eq2}
-&  |\partial {\cal D}| \langle \avrc{u} -  \ud, \md \rangle_{H^{-\frac12}(\Lambda)} =
-|\partial {\cal D}| \langle \avrc{q_2}, \md \rangle_{H^{-\frac12}(\Lambda)}
-\quad \forall \md \in H^{-\frac12}(\Lambda)\,.
-\end{align}
-\end{subequations}
-
-Let us prove that \eqref{benchm_sol3d}-\eqref{benchm_sol1d} is the solution of
-\eqref{eq:problem2_simple}. Using the integration by part formula and homogeneous
-boundary conditions on $\Omega$ and $\Lambda$, from \eqref{eq:problem2_simple_eq1} we have
+% in the case in which the starting 3D-3D problem is
+% \begin{subequations}\label{eq:dirneu_simple}
+% \begin{align}
+% - \Delta \up  &= f  && \text{ in } \Omega_{\oplus},\\
+% - \Delta \uf &= g  && \text{ in } \Omega_{\ominus},\\
+% -\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
+% \uf - \up &= q_i  && \text{ on }  \Gamma,\\
+% \up &= \paolo{u_b} && \text{ on } \partial \Omega,
+% \end{align}
+% \end{subequations}
+% Therefore the reduced problems in \eqref{eq:problem1} and
+% \eqref{eq:problem2} become respectively
+% %
+% \begin{subequations}\label{eq:problem1_simple}
+% \begin{align}
+% \label{eq:problem1_simple_eq1}
+% &(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
+% + \langle \trace{v}  - \ext{\vd}, \lambda \rangle_\Gamma
+% \\
+% \nonumber
+% &\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
+% \quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
+% \\
+% \label{eq:problem1_simple_eq2}
+% &   \langle \trace{u} - \ext{\ud} , \mu \rangle_\Gamma =  \langle q_1 , \mu \rangle_\Gamma
+% \quad \forall \mu \in H^{-\frac12}(\Gamma)
+% \end{align}
+% \end{subequations}
+% % and
+% \begin{subequations}\label{eq:problem2_simple}
+%   \begin{align}
+%     \label{eq:problem2_simple_eq1}
+% &(\nabla u,\nabla v)_{L^2(\Omega)} + |{\cal D}|(d_s \ud,d_s \vd)_{L^2(\Lambda)} 
+% + |{\partial \cal D}| \langle \avrc{v} - \vd, \ld \rangle_{H^{-\frac12}(\Lambda)} 
+% \\
+% \nonumber
+% &\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g}, \vd)_{L^2(\Lambda)}
+% \quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
+% \\
+% \label{eq:problem2_simple_eq2}
+% &  |\partial {\cal D}| \langle \avrc{u} -  \ud, \md \rangle_{H^{-\frac12}(\Lambda)} =
+% |\partial {\cal D}| \langle \avrc{q_2}, \md \rangle_{H^{-\frac12}(\Lambda)}
+% \quad \forall \md \in H^{-\frac12}(\Lambda)\,.
+% \end{align}
+% \end{subequations}
+
+\paolo{We prove that the solution of \eqref{benchmark} is equivalent to the one of \eqref{eq:problem2}.}
+Precisely, we prove that \eqref{benchm_sol3d-1d} is the solution of
+\eqref{eq:problem2}. Using the integration by part formula and homogeneous
+boundary conditions on $\Omega$ and $\Lambda$, from \eqref{eq:problem2} we have
 \begin{align*}
@@
 \quad \forall v \in H^1_0(\Omega), \vd \in H^1(\Lambda).
-\\
 \end{align*}
-Since $\ld=\avrc{L}=0$ and \eqref{benchm_sol3d} satisfies \eqref{benchm_3d} and \eqref{benchm_sol1d}
-satisfies \eqref{benchm_1d}, we have that
+Since $\ld=0$ and the first of \eqref{benchm_sol3d-1d} satisfies \eqref{benchm_3d} and the second satisfies \eqref{benchm_1d}, we have that
 \begin{align*}
--(\Delta u, v)_{L^2(\Omega)} =  (f,v)_{L^2(\Omega)}, \\
--|{\partial \cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)},
+-(\Delta u, v)_{L^2(\Omega)} =  (f,v)_{L^2(\Omega)}, 
+\\
+-|{\partial \cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}.
 \end{align*}
-Thus \eqref{benchm_sol3d}-\eqref{benchm_sol1d} satisfy \eqref{eq:problem2_simple_eq1}.
-The fact that the solution satisfy \eqref{eq:problem2_simple_eq2} follows from \eqref{eq:couple_2}.
-
-We can prove in a similar way that \eqref{benchm_sol3d}-\eqref{benchm_sol1d}, with $\lambda=L=0$
-satisfy \eqref{eq:problem1_simple}. Note in particular that $q_1$ is such that
+Thus \eqref{benchm_sol3d-1d} satisfy equations \eqref{eq:problem2a}, \eqref{eq:problem2b}.
+The fact that the solution satisfy \eqref{eq:problem2c} follows from \eqref{eq:couple_2}.
+
+We can prove in a similar way that \eqref{benchm_sol3d-1d}, with $\lambda=0$
+satisfy \eqref{eq:problem1}. Note in particular that $q_1$ is such that
 $\trace{u} - \ext{\ud} = q_1$ on $\Gamma$.
@@
  \includegraphics[width=0.45\textwidth]{graphics/nonconform_mesh.pdf} 
+ \vspace{-10pt}
  \captionof{figure}{
@@
 $\Lambda$ and $\Gamma$ conforming discretization of $\Omega$
-   used for \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}.
-   (Right) Sample discretization of the benchmark geometry in the non-conforming case. 
+   used for \eqref{eq:problem1} and \eqref{eq:problem2}.
+   (Right) Sample discretization of the benchmark geometry in the non-conforming case for \eqref{eq:problem2}. 
  }
@@
 \hline
-\multicolumn{5}{c}{\textcolor{blue}{$\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$}}\\
+\multicolumn{5}{c}{\textcolor{blue}{$\mathcal{T}^{\Omega}_h$ conforming to $\Gamma$, $\Lambda$}}\\
 \hline
@@
 \hline
-\multicolumn{5}{c}{\textcolor{red}{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$}}\\
+\multicolumn{5}{c}{\textcolor{red}{$\mathcal{T}^{\Omega}_h$ non conforming to $\Gamma$, $\Lambda$}}\\
 %    \begin{tabular}{l|lll}
@@
   \captionof{table}{Error convergence on a benchmark problem \eqref{benchmark}.
-    (Top) problem \eqref{eq:problem1_simple}, (middle) \eqref{eq:problem2_simple} with
-    conforming discretization and (bottom) \eqref{eq:problem2_simple} in case
-    $\mathcal{T}^{\Omega}_h$ does not conform to $\Lambda$. Continuous linear Lagrange
+    (Top) problem \eqref{eq:problem1}, (middle) \eqref{eq:problem2} with
+    conforming discretization and (bottom) \eqref{eq:problem2} in case
+    $\mathcal{T}^{\Omega}_h$ does not conform to $\Lambda$ using 
+    stabilized formulation \eqref{eq:prob2_stabilized}. Continuous linear Lagrange
     elements are used for $u_h$, $\udh$ and $u_{\odot \mathfrak{h}}$ and $\ldh$ in
@@
 ($P_1$) elements (for all the spaces), Table \ref{tab:error_conform}
-lists the errors of formulations \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple}
+lists the errors of formulations \eqref{eq:problem1} and \eqref{eq:problem2}
 on the benchmark problem. It can be seen that the error in $u$ and $\ud$ in $H^1$ norm
@@
 We remark that for $u$ and $\ud$ the error is interpolated into the finite element space of
-piecewise quadratic \emph{discontinous} functions. For \eqref{eq:problem2_simple} we
+piecewise quadratic \emph{discontinous} functions. For \eqref{eq:problem2} we
 evaluate the fractional norm and interpolate the error using piecewise continuous
@@
 lists the error of the Lagrange multiplier in the $L^2$ norm. Here, quadratic convergence is observed
-for \eqref{eq:problem2_simple}. For \eqref{eq:problem1_simple} the rate is between 1.5 and 2.
-
-We plot the numerical solution of problem \eqref{eq:problem1_simple} and \eqref{eq:problem2_simple} in
+for \eqref{eq:problem2}. For \eqref{eq:problem1} the rate is between 1.5 and 2.
+
+We plot the numerical solution of problem \eqref{eq:problem1} and \eqref{eq:problem2} in
 Figure \ref{fig:sol_benchm1}.
@@
 \includegraphics[width = 0.3\textwidth]{./graphics/mfs_LM1d_crop}
-\caption{Numerical solution of problem \eqref{eq:problem1_simple} and
-  \eqref{eq:problem2_simple}. (Left) functions $u_h$, $\udh$ (practically identical
-  in both problems). (Middle) Lagrange multiplier for \eqref{eq:problem1_simple}
-  and (right) for \eqref{eq:problem2_simple}.}
+\vspace{-10pt}
+\caption{Numerical solution of problem \eqref{eq:problem1} and
+  \eqref{eq:problem2}. (Left) functions $u_h$, $\udh$ (practically identical
+  in both problems). (Middle) Lagrange multiplier for \eqref{eq:problem1}
+  and (right) for \eqref{eq:problem2}.}
 \label{fig:sol_benchm1}
@@
 mesh of $\Omega$ such that no cell $\mathcal{T}^{\Omega}_h$ has any edge
-lying on $\Lambda$. Further we let $h^{\prime}=h/3$ in $\mathcal{T}^{\Lambda}_{h^{\prime}}$,
+lying on $\Lambda$. Further we let $\mathfrak{h}=h/3$ in $\mathcal{T}^{\Lambda}_{\mathfrak{h}}$,
 cf. Figure \ref{fig:mesh}.
@@
 comment that in the $L^2$ norm all the formulations yield faster than linear convergence.
-
+%
 In order to discuss solution cost of the formulations we consider 
@@
 that we shall ignore the setup cost of the preconditioner.
-
+%
 Following operator preconditioning technique \cite{mardal2011preconditioning} we
@@
 (the inverse of) the fractional Laplacian $-\Delta^{-1/2}$ on $\Gamma$ for
-\eqref{eq:problem1_simple} and $\Lambda$ for \eqref{eq:problem2_simple}.
+\eqref{eq:problem1} and $\Lambda$ for \eqref{eq:problem2}.
 A detailed analysis of the preconditioners will be presented in a separate
@@
 by spectral decomposition \cite{kuchta2016preconditioners}.
-
+%
 For the unfitted stabilized formulation \eqref{eq:problem2} the Lagrange multiplier preconditioner
@@
 is beyond the scope of the paper and shall be pursued in the future works.
-
+%
 In Table \ref{tab:cost} we compare solution time, number of iterations and
@@
 parameter as the iteration counts and condition numbers are bounded in $h$.
-We then see that the solution time for \eqref{eq:problem1_simple} is about 2 times
-longer compared to \eqref{eq:problem2_simple} which is about 4 times more expensive
+We then see that the solution time for \eqref{eq:problem1} is about 2 times
+longer compared to \eqref{eq:problem2} which is about 4 times more expensive
 than the solution of the Poisson problem \eqref{benchm_3d}. This is in addition to the
@@
 the multiplier space as small as possible. We remark that the missing
-results for \eqref{eq:problem1_simple} in Table \ref{tab:cost} are due to the
+results for \eqref{eq:problem1} in Table \ref{tab:cost} are due to the
 memory limitations encountered when solving the eigenvalue problem
@@
 %
-
 Due to the missing proper preconditioner for the Lagrange multiplier block the

### 2020-04-06 appendix.tex
Arxiv-ed version

@@
 \section{Derivation of the model}
-This section provides a rigorous derivation of 3D-1D-2D problem \eqref{eq:problem2} and 3D-1D-1D problem \eqref{eq:problem1}. 
+This section provides a rigorous derivation of 3D-1D-1D problem \eqref{eq:problem2} and 3D-1D-2D problem \eqref{eq:problem1}. 
 The steps are similar to the derivation presented in \cite{laurino_m2an}, 
@@
 - \Delta \uf  + \uf &= g  && \text{ in } \Omega_\ominus,\\
+\label{eq:dirneu4}
+\up - \uf &= q && \text{ on }  \Gamma,\\
 \label{eq:dirneu3}
--\nabla \uf \cdot \nn_{\ominus} &= -\nabla \up \cdot \nn_{\ominus}  && \text{ on } \Gamma,\\
-\label{eq:dirneu4}
-\uf &= \up && \text{ on }  \Gamma,\\
+\nabla\left( \up - \uf \right) \cdot \nn_{\oplus} &=0  && \text{ on } \Gamma,\\
 \label{eq:dirneu5}
@@
 =  \int_{s_1}^{s_2} \int_{\partial\mathcal{D}(s)} \lambda d\gamma \, ds 
-= \int_{s_1}^{s_2} |\DD| \avrc{\lambda} \,ds\,.
+= \int_{s_1}^{s_2} |\DD(s)| \avrc{\lambda} \,ds\,.
 \end{equation*}
@@
 \int_{\Omega _{\oplus}}fv\,d\omega&=
-\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\omega -\int _{\partial \Omega _{\oplus}}\nabla \up \cdot \nn_{\oplus} v\,d\sigma + \int_{\Omega_{\oplus}} \up v
+\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\omega -\int _{\partial \Omega _{\oplus}}\nabla \up \cdot \nn_{\oplus} v\,d\sigma + \int_{\Omega_{\oplus}} \up v \,d\omega
 \\
-&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega -\int_{\Gamma} \nabla \up \cdot \nn_{\oplus} v + \int_{\Omega_{\oplus}} \up v
+&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\omega -\int_{\Gamma} \nabla \up \cdot \nn_{\oplus} v\,d\sigma + \int_{\Omega_{\oplus}} \up v\,d\omega
 \\
-&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega +\int_{\Gamma} \lambda v + \int_{\Omega_{\oplus}} \up v.
+&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\omega +\int_{\Gamma} \lambda v\,d\sigma + \int_{\Omega_{\oplus}} \up v\,d\omega.
 \end{split}
@@
 \\
-& \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0\,,
+& \langle \trace u - \ext \ud , \mu \rangle_\Gamma 
+= \langle q, \mu \rangle_\Gamma\,,
 \quad && \forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
@@
 \end{subequations}
-This coupled problem is classified as 3D-1D-2D because the unknowns $u$, $\ud$, $\lambda$ belong to 
-$\Omega \subset \R^3$, $\Lambda \subset \R$ and $\Gamma \subset \R^2$ respectively.
+This coupled problem is classified as 3D-1D-2D because the unknowns $u$, $\ud$, $\lambda$ belong to $\Omega \subset \R^3$, $\Lambda \subset \R$ and $\Gamma \subset \R^2$ respectively.
 Then, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-2D formulation
@@
 \\
-& \langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} = 0\,,
+& \langle \mtrace u - \ud, \md \rangle_{\Lambda,|\DD|} 
+= \langle q, \md \rangle_\Gamma = \langle \avrc{q}, \md \rangle_{\Lambda,|\DD|} \,,
 \quad &&\forall \md \in H^{-\frac 1 2}(\Lambda)\,.
@@
 \end{subequations}
+
 % We notice that all the integrals of the reduced problem are well defined because 
 % $\mtrace: H^1_0(\Omega) \rightarrow H^\frac 1 2_{00}(\Lambda)$ as shown in Corollary \ref{corollary:H12norm}.
-
 % The well-posedness of $\eqref{eq:problem1}$ and $\eqref{eq:problem2}$ 
@@
 \begin{proof}
-Let us consider the eigenvalue problems for the Laplace operator on $\Gamma$ with homogeneous Dirichlet conditions at $x=0,\, X$ and periodic boundary conditions at $y=0,\, Y$.
+Let us consider the eigenvalue problem for the Laplace operator on $\Gamma$ with homogeneous Dirichlet conditions at $x=0,\, X$ and periodic boundary conditions at $y=0,\, Y$.
 Let us also consider the Laplace eigenproblem on $(0,X)$ with homogeneous Dirichlet conditions.
@@
 
-Further, we have
-the following concrete representation of the fractional norms, 
+We use here the following representation of the fractional norms, 
 \begin{equation}\label{eq:fracnorm_lambda}
@@
 
-Let $C=C(X)=\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}$. Then,  
-from \eqref{eq:fracnorm_lambda} we have $\|\avrc{u}\|^2_{H^{\frac 12}_{00}(0,X)}
-=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}a_i^2=$
-\begin{equation*}
-\begin{split}
-=&C\left( \int_0^X \avrc{u}(x) \sin\left(\frac{i\pi x}{X}\right)\, dx \right)^2
-= C\left( \sum_{j=1}^\infty a_{j,0}\int_0^X \sin\left(\frac{j\pi x}{X}\right) \sin\left(\frac{i\pi x}{X}\right) \, dx  \right)\\
-=& \sum_{i=1}^{\infty} \frac{X^2}{4} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}a_{i,0}^2
+Let the constant $C$ be equal to 
+$C=C(X)=\sum_{i=1}^{\infty}\left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}$. 
+Then,  from \eqref{eq:fracnorm_lambda} we have 
+\begin{multline*}
+\|\avrc{u}\|^2_{H^{\frac 12}_{00}(0,X)}
+=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}a_i^2
+\\
+=C\left( \int_0^X \avrc{u}(x) \sin\left(\frac{i\pi x}{X}\right)\, dx \right)^2
+= C\left( \sum_{j=1}^\infty a_{j,0}\int_0^X \sin\left(\frac{j\pi x}{X}\right) \sin\left(\frac{i\pi x}{X}\right) \, dx  \right)
+\\
+= \sum_{i=1}^{\infty} \frac{X^2}{4} \left( 1+ \left(\frac{i\pi}{X}\right)^2\right)^{\frac 12}a_{i,0}^2
 \leq \frac{X^2}{4}\sum_{i=1}^{\infty} \sum_{j=1}^{\infty}  \left( 1+ \left(\frac{i\pi}{X}\right)^2 
-+ \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12} |a_{i,j}|^2\\ =&\frac{X^2}{4}\|u\|^2_{H^{\frac 12}_{00}(\Gamma)},
-\end{split}
-\end{equation*}
++ \left(\frac{j2\pi}{Y}\right)^2\right)^{\frac 12} |a_{i,j}|^2
+\\ 
+=\frac{X^2}{4}\|u\|^2_{H^{\frac 12}_{00}(\Gamma)},
+\end{multline*}
 where we have used the orthogonality property
@@
 and we have applied \eqref{eq:fracnorm_lambda} in the last equality.
-Moreover, in the case in which $u$ is constant with respect to $y$, we have
+As a result of the previous inequality, we have proved the first statement of the Corollary, namely $u\in H^\frac12_{00}(\Gamma) \rightarrow \overline{u}\in H^\frac12_{00}(\Lambda)$.
+
+The second statement of the Corollary addresses the case of the function $u$ constant with respect to $y$. Precisely, we have
 \begin{equation*}
@@
 \section{System sizes in benchmark formulations} \label{sec:appendix}
-Below we list dimensions of the finite element spaces used to discretize
-formualations \eqref{eq:problem1}, \eqref{eq:problem2} and stabilized
+In Table \ref{tab:dof} we list dimensions of the finite element spaces used to discretize formualations \eqref{eq:problem1}, \eqref{eq:problem2} and stabilized
 \eqref{eq:problem2} on different levels of refinement. The number of 
 degrees of freedom in subspace $W_{i, h}$ is denote as $\lvert W_{i, h}\rvert$. 
-We recall that the discrete spaces in the respected formulations 
-are $X^1_{h, 0}(\Omega)\times X^1_{h, 0}(\Lambda)\times Q_h(\Gamma)$,
-      $X^1_{h, 0}(\Omega)\times X^1_{h, 0}(\Lambda)\times Q_h(\Lambda)$,
-      and 
-      $X^1_{h, 0}(\Omega)\times X^1_{\mathfrak{h}, 0}(\Lambda)\times Q_h(\mathcal{G}_h)$.
+We recall that the discrete spaces  
+are $X^1_{h, 0}(\Omega)\times X^1_{h, 0}(\Lambda)\times Q_h(\Gamma)$
+for the 3D-1D-2D problem \eqref{eq:problem1},
+$X^1_{h, 0}(\Omega)\times X^1_{h, 0}(\Lambda)\times Q_h(\Lambda)$
+for the 3D-1D-1D problem \eqref{eq:problem2}, and 
+$X^1_{h, 0}(\Omega)\times X^1_{\mathfrak{h}, 0}(\Lambda)\times Q_h(\mathcal{G}_h)$
+for the stabilized 3D-1D-1D problem.
 
+\begin{table}[h!]
 \begin{center}
@@
 \end{center}
+    \caption{Number of degrees of freedom of the discrete spaces used in the numerical experiments.}
+    \label{tab:dof}
+\end{table}

### 2020-04-07 arxiv/domain.tex
arxived

%\documentclass{standalone}

%\usepackage{tikz}
%\usetikzlibrary{shapes, snakes, patterns, arrows}
%\usetikzlibrary{calc}
%\usepackage{pgfplots}
%\usepgfplotslibrary{fillbetween}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage{amsfonts}

%\begin{document}
\begin{tikzpicture}

% Omega
\draw[] (0, 3) ellipse (2. and 0.5);
\draw (-2.,3) -- (-2.,-3);
\draw (-2.,-3) arc (180:360:2. and 0.5);
\draw [dashed] (-2.,-3) arc (180:360:2. and -0.5);
\draw (2.,-3) -- (2., 3);
% Top whole
\draw[blue, thick] (-0.75, 3) ellipse (0.6 and 0.15);
% Bottom whole
\draw[blue, thick] (0.75, -3) ellipse (0.6 and 0.15);
% Auxliary middle surface
\draw [dashed, thin](-2., 0) arc (180:360:2. and 0.5);
\draw [dashed, thin] (-2.,0) arc (180:360:2. and -0.5);

\fill[pattern color=cyan, pattern=north east lines] (0.5, 0) ellipse (0.5 and 0.125);
\node [cyan, below right, fill=white, opacity=0.8] at (0.6, 0.0) {\rotatebox{90}{\Large{$\mathcal{D}(s)$}}};

\node[mark size=1.5pt, color=red] at (0.5, 0.0) {\pgfuseplotmark{*}};

% Walls of gamma
\draw [blue, thick, name path global = topleft] plot [smooth, tension=1] coordinates { (-1.35,3) (-0.6, 1) (0,0)};
\draw [blue, thick, name path global = botleft] plot [smooth, tension=1] coordinates { (0,0) (0.125, -1) (0.15,-3)};

\draw [blue, thick, name path global = topright] plot [smooth, tension=1] coordinates { (-0.15,3) (0.5, 1) (1.0,0)};
\draw [blue, thick, name path global = botright] plot [smooth, tension=1] coordinates { (1.0,0) (1.25, -1) (1.35,-3)};

%\fill [gray, opacity=0.5] (-1.25,0) -- (-1.25,-3.5) arc (180:360:1.25 and 0.5) -- (1.25,0) arc (0:180:1.25 and -0.5);

\tikzfillbetween[of=topleft and topright]{blue!40!white, opacity=0.2};
\tikzfillbetween[of=botleft and botright]{blue!40!white, opacity=0.2};
\fill[blue!40!white, opacity=0.2] (-1.35, 3) arc (180:360:0.6 and -0.15) -- (-0.75, 3);
\fill[blue!40!white, opacity=0.2] (0.15, -3) arc (180:360:0.6 and 0.15) -- (-0.15, -3);
\node[blue, fill=white, opacity=0.7, above] at (1.15, -3) {\rotatebox{90}{\Large{$\Omega_{\ominus}$}}};

% Curve
\draw [very thick, red] plot [smooth, tension=0.2] coordinates { (-0.75,3) (-0.2, 1.5) (0.5, 0) (0.75,-3)};
\node[red, fill=white, opacity=0.7] at (0.075, 1) {\rotatebox{90}{\Large{$\Lambda$}}};

\node[] at (-0.5, -1.5) {\rotatebox{90}{\Large{$\Omega_{\oplus}$}}};

\node[blue] at (0.75, 1) {\rotatebox{90}{\Large{$\Gamma$}}};

\draw [very thick, cyan] (0, 0) arc (180:360:0.5 and 0.125);
\draw [very thick, dashed, cyan] (0,0) arc (180:360:0.5 and -0.125);
\node [left, cyan] at (0, 0) {\rotatebox{90}{\Large{$\partial\mathcal{D}(s)$}}};

\end{tikzpicture}
%\end{document}

### 2020-04-07 arxiv/intersection.tex
arxived

--- 2019-07-22 graphics/gamma_generated.tex
@@
 %\begin{document}
+\begin{tikzpicture}[scale=0.7, every node/.style={scale=0.7}]
 
-\begin{tikzpicture}[scale=0.7, every node/.style={scale=0.7}]
 \pgfmathsetmacro{\factor}{1/sqrt(2)};
 
+%tetrahedron
 \coordinate  (A) at (-2.5,1.5,-2.1*\factor);
@@
 
+%intersection
 \draw[dashed, very thick, purple, opacity=.4] (1, 3.05) ellipse (1.5 and 0.3);
 \draw[dashed, very thick, purple, opacity=.4] (1, -0.65) ellipse (1.5 and 0.3);
-
-\fill [purple, opacity=0.3]  (-0.5, -0.65) arc (180:360:1.5 and 0.3) -- (2.5, 3.05) arc (0:180:1.5 and -0.3);
-\node [font=\Large, right, purple] at (-2, 0) {$\Gamma_{\omega_j \cap \Lambda}$};
+\draw[dashed, very thick, purple, opacity=.4] (1, 1.5) ellipse (1.5 and 0.3);
+\fill [purple, opacity=0.3]  (2.5, -0.65) arc (360:280:1.5 and 0.3) -- (-0.5, 0.75) -- (-0.5, 2.55) -- (0.3, 2.8) arc (118:0:1.5 and -0.3);
+\node [font=\Large, right, purple] at (-2, -0.1) {$\Gamma_{\omega_j \cap \Lambda} \cap \omega_j$};
 

### 2020-09-04 reply_to_reviewers.tex

\documentclass{article}
\usepackage{fullpage}
\newenvironment{answer}{\begin{paragraph}{Answer:}}{\end{paragraph}\vspace{0.5cm}}

\title
{ Reply to the reviews of the manuscript:\\
\emph{Analysis and approximation of mixed-dimensional PDEs on 3D-1D domains coupled with Lagrange multipliers}\\
by M. Kuchta, F. Laurino, K.A. Mardal, P. Zunino.
}

\date{\today}

\begin{document}

\maketitle

First of all, we would like to thank the referees for their insightful comments. 
We believe that their observations have helped in delivering a substantially improved version of the original work,
as discussed in the following point by point reply to their remarks. 
For the sake of clarity, the main changes in the revised manuscript are reported in blue.

\vspace{1cm}

\section*{Reviewer \#1}

In the paper under review the authors study an example of mixed dimensional PDE, i.e. a 3D problem coupled with a 1D problem. Such problems naturally appear in various applications (e.g. biomedicine and geophysics) where slender cylindrical structures are coupled with larger 3D body. The main issue in the analysis of such problem is that trace is not well defined on set of co-dimension two for weak solutions. The authors circumvent this issue by exploiting the fact that the thin structure is not 1D curve, but rather a slender 3D structure. This leads to two formulation of the problems: 3D-1D-1D and 3D-1D-2D. The former is obtained from the latter by averaging procedure. Neumann (dynamic) coupling conditions are enforced by using a Lagrange multiplier. Well-posednes is proved for the continuous and the discrete version of the problem. Two different version of the discrete case are analyzed: the case when 3D and 1D mesh matches on the interface (the conforming case) and the case when the meshes do not necessarily match (the non-conforming case). Since the saddle point approach is used, the main technical step is to prove that inf-sup condition is satisfied. In the non-conforming case the stabilization operator is constructed in order to satisfy inf-sup condition. Finally, the comparison of the numerical solution with analytical solution for benchmark problem is presented.

The result presented in the paper are interesting and to the best of my knowledge correct. I recommend the paper for publication in the SINUM.
Remarks:
\begin{enumerate}
    \item Please explain what is unknown $\lambda$ in problem (1.1). I suggest including part of the Appendix from supplementary materials where $\lambda$ is introduces as a Langrange multiplier.
    \item Sectio 2, page 2 - $\Omega$ is open? Maybe replace "in detail" with "More precisely".
    \item P. 3. - Please provide references for $H^{1/2}_{00}$ and interpolation of weighted spaces. In addition, it would be instructive to provide an example for Riesz map S.
    \item p.4. (l145-l50) I suggest rewriting this paragraph. First, please refer to the exact result that you are using (from [22] or [28]) and define or refer to definition of "domains having small geometric details". Second, it is not necessary to define operator norm, but enough to say that norm of $H_{\Omega}$ is uniformly bounded.
    \item p4 l152. Is $H_{\Omega}$ harmonic extension? If so, please state this in previous paragraph.
    \item p8 l177-l184 - I suggest adding a figure that illustrate the assumptions on the conforming mesh.
    \item p9 (4.4) Reference for these properties of $SZ_h$
    \item p9, after (4.5) Do you mean inverse Poincare inequality?
    \item In statement of problem (5.1) include $\lambda$ and then say that one can construct explicit solution with $\lambda=0$.
\end{enumerate}

\section*{Reviewer \#2}

In the present contribution the authors discuss coupling of pde's
defined on domains of co-dimension 2. This case is more challenging
than the case of co-dimension 1 since the in the standard functional
spacesfor elliptic problems the weak solution does not
have enough regularity to make the coupling conditions between the
function in the 3D space and the function in the 1D space well
defined. Here the authors follow a natural approach proposed in previous
work that consists in introducing a cylindrical tube
around the 1D domain (which is physically justified, since the 1D
domain typically is an idealization of such a tubular region) and perform
the coupling of the two systems through lifting to the tupe or
averaging on the tube surface. This results in a global constrained
system where the coupling conditions are imposed using Lagrange
multipliers.
First wellposedness of the pde-systems is discussed and then numerical
discretization. Discrete spaces are introduces and stability
proven. Both a conforming setting and a non-conforming setting is
considered, where stabilization is introduced in the non-conforming
case.

This is an interesting contribution and I think that it is of
sufficient originality to be published in SINUM. However in its
present case the paper is a bit rough and can not be accepted. In particular the following
points should be carefully considered in a revised version.

\begin{enumerate}
\item The authors argue that meshing the fine scale slender domain is
  too costly. However from the present manuscript one can not deduce
  that the proposed method is less costly. Indeed it is not clear how
  fine the mesh needs to be in the vicinity of $\Lambda$. This depends
  on the curvature of $\Lambda$ and the radius $R$ of the generalized
  cylinder around it.
Note in particular that the constants in (3.2)-(3.8) may depend on
these quantities. Normally the wellposedness result of Thm 3.1 is
accompanied with a stability result quantifying the continuous
dependence of the problem. The authors should add this stability
result and for each model track the dependence of the stability
constant on the model parameters, at least the radius $R$ of the
slender domain.

Although no error estimates are given (and not required), the size of
the (inverse of the) stability constant generally gives an idea of how fine the
mesh needs to be in the vicinity of the lower dimensional domain. 
\item In the conforming case the mesh constraints impose that $h \sim R$
  it seems, this could be stated clearly. Is it considered an
  advantage of the non-conforming method that this is not imposed?
Is it still expected to be imposed for accuracy reasons? Please
discuss (taking into account the stability arguments of the previous
point). It would also be interesting to understand how the
conditioning of the system depends on the radius of the slender
domain. The academic numerical example does not give much information,
since there both in the conforming and the nonconforming case $R  \sim h$.
\item In the introduction the coupling conditions are presented as ``a
  combination of Dirichlet and Neumann conditions'', this is slightly
  obscure to me, since the later multiplier formalism simply imposes
  continuity of the primal variable. This could be made clearer.
\item Line 85: Typo in the definition of $\Gamma$.
\item Line 128: Appendix, what appendix? Please add in the revised version.
\item Corollary 2.2: Please add a two line proof showing how Lemma 2.1
  is applied.
\item Equation (3.4): The inequality should go the other way.
\item Line 150: ``independent OF the (minimal)...''
\item Line 178: Would it not be more realistic to introduce an
  approximation of $\Gamma$, $\Gamma_h$ that conforms to the mesh?
  Similarly you could introduce $\Lambda_h$ approximation of $\Lambda$
  that is a piecewise linear manifold.
\item Lemma 4.2: The proof is incomplete, please state clearly the
  interpolation results that you wish to apply (with reference) and
  how you obtain the desired bound using the weaker and stronger
  stabilities.
\item Lemma 4.3: Maybe $\gamma_h$ since you used $\beta_h$ in
  Corollary 4.1? Also in Lemma 4.6.
\item Proof of Theorem 4.4: The proof is incomplete, please provide a
  full proof of the claim on page 10, line -2 that the trace of the
  Scott-Zhang interpolant (how do you define S-Z here?) coincides with
  the identity.
\item Theorem 4.7: Why do you change the style of presentation of the
  inf-sup condition here?
\item Page 12, line 2: Please provide a full proof of the claim that
  the average of the S-Z interpolation of the harmonic extension
  coincides with the identity operator on $Q_h$.
\item Lemma 4.9, maybe subscript on $\beta$?
\item Page 20, In the comparison the accuracy of the Lagrange
  multiplier is discussed, but what is the physical significance of
  the multiplier, i.e. why should the reader be concerned of its
  accuracy, does it provide information that can not be obtained from
  the primal variables?
\item It should be easy to consider the same example but with a
  slender domain half as wide, to see how this affect accuracy and conditioning.
\end{enumerate}
\end{document}

### 2020-09-22 reply_to_reviewers.tex
Updates from Overleaf

@@
 \newenvironment{answer}{\begin{paragraph}{Answer:}}{\end{paragraph}\vspace{0.5cm}}
+\usepackage{xcolor}
+
+\newcommand{\fede}[1]{{\color{green!55!blue}#1}}
+\newcommand{\kent}[1]{{\color{red}#1}}
+\newcommand{\miro}[1]{{\color{blue}#1}}
+\newcommand{\paolo}[1]{{\color{magenta}#1}}
 
@@
     \item Please explain what is unknown $\lambda$ in problem (1.1). I suggest including part of the Appendix from supplementary materials where $\lambda$ is introduces as a Langrange multiplier.
-    \item Sectio 2, page 2 - $\Omega$ is open? Maybe replace "in detail" with "More precisely".
+    \item Sectio 2, page 2 - $\Omega$ is open? Maybe replace "in detail" with "More precisely".\\
+    \fede{The standard definition of domain is used, i.e. $\Omega$ is a open and connected set. For clarity, the definition has been added to the manuscript. }
     \item P. 3. - Please provide references for $H^{1/2}_{00}$ and interpolation of weighted spaces. In addition, it would be instructive to provide an example for Riesz map S.
@@
 First, please refer to the exact result that you are using (from [22] or [28]) and define or refer to definition of "domains having small geometric details".
-Second, it is not necessary to define operator norm, but enough to say that norm of $H_{\Omega}$ is uniformly bounded.
-    \item p4 l152. Is $H_{\Omega}$ harmonic extension? If so, please state this in previous paragraph.
+Second, it is not necessary to define operator norm, but enough to say that norm of $H_{\Omega}$ is uniformly bounded.\\
+    \fede{We thank the reviewer for the suggestion. In the revised manuscript, the extension operator has been replaced by the harmonic extension, therefore the reference to [28] is not needed.\\
+    WHAT DOES THE SECOND PART MEAN? }
+    \item p4 l152. Is $H_{\Omega}$ harmonic extension? If so, please state this in previous paragraph.\\
+    \fede{Yes, the definition has been added in the revised manuscript.}
     \item p8 l177-l184 - I suggest adding a figure that illustrate the assumptions on the conforming mesh.
-    \item p9 (4.4) Reference for these properties of $SZ_h$
-    \item p9, after (4.5) Do you mean inverse Poincare inequality?
-    \item In statement of problem (5.1) include $\lambda$ and then say that one can construct explicit solution with $\lambda=0$.
+    \item p9 (4.4) Reference for these properties of $SZ_h$\\
+    \fede{The reference has been added in the revised manuscript.\\
+
+    CHECK: LEMMA 1.130 FROM ERN AND GUERMOND. (4.4) IS OBTAINED FROM (i) WITH l=1, p=2, m=1. (4.5) IS OBTAINED FROM (ii) WITH l=1, p=2, m=0}
+    \item p9, after (4.5) Do you mean inverse Poincare inequality?\\
+    \fede{Yes it is a discrete inverse Poincare inequality.
+We adopt the terminology used in [Ern and Guermond, Ch.
+1.7] where these inequalities are more in general addressed as inverse inequalities.
+}
+    \item In statement of problem (5.1) include $\lambda$ and then say that one can construct explicit solution with $\lambda=0$.\\
+    \fede{The entire paragraph has been revised.
+Notice that $\lambda$ cannot be included in problem (5.1) because (5.1) is not the strong formulation of problems (2.2) and (2.4).
+It is only an auxiliary problem used to fabricate the weak solution of problems (2.2) and (2.4).}
 \end{enumerate}

### 2020-09-22 3d1d_LM_rev.tex
Updates from Overleaf

--- 2020-04-06 3d1d_coupled_LM.tex
@@
 
-\newcommand{\kent}[1]{{\color{black}#1}}
-\newcommand{\miro}[1]{{\color{black}#1}}
-\newcommand{\paolo}[1]{{\color{black}#1}}
+\newcommand{\fede}[1]{{\color{green!55!blue}#1}}
+\newcommand{\kent}[1]{{\color{red}#1}}
+\newcommand{\miro}[1]{{\color{blue}#1}}
+\newcommand{\paolo}[1]{{\color{magenta}#1}}
+
+% old commands: used for changes before review
+\newcommand{\kentold}[1]{{\color{black}#1}}
+\newcommand{\miroold}[1]{{\color{black}#1}}
+\newcommand{\paoloold}[1]{{\color{black}#1}}
+
 % Title. If the supplement option is on, then "Supplementary Material"
@@
 \label{eq:coupling}
-\mathcal{T}_\Lambda u - \ud  &=  \paolo{q} &\mbox{ on } \Lambda . 
+\mathcal{T}_\Lambda u - \ud  &=  \paoloold{q} &\mbox{ on } \Lambda . 
 \end{align}
@@
 
-\paolo{Although the focus of the present work is mostly about analysis and approximation of the proposed approach, we stress that it aims to build the mathematical foundations to tackle various applications involving 3D-1D mixed dimensional PDEs, such as FSI of slender bodies \cite{Mori2019887}, microcirculation and lymphatics \cite{Possenti2019101,Vinje2019}, subsurface flow models with wells \cite{Cerroni2019} and the electrical activity of neurons.}
+\paoloold{Although the focus of the present work is mostly about analysis and approximation of the proposed approach, we stress that it aims to build the mathematical foundations to tackle various applications involving 3D-1D mixed dimensional PDEs, such as FSI of slender bodies \cite{Mori2019887}, microcirculation and lymphatics \cite{Possenti2019101,Vinje2019}, subsurface flow models with wells \cite{Cerroni2019} and the electrical activity of neurons.}
 
@@
 \section{Preliminaries}\label{sec:setting}
-
-Let the domain $\Omega\subset \R^3 $ be convex and composed of two parts, 
+Let the domain $\Omega\subset \R^3 $\fede{, i.e. open and connected,} be convex and composed of two parts, 
 $\Omega_{\ominus}$ and $\Omega_{\oplus}:=\Omega\setminus\overline{\Omega}_{\ominus}$. 
@@
 that is; the swept volume of a two dimensional set, $\partial\mathcal{D}$, moved along a curve, $\Lambda$, in the three-dimensional domain, $\Omega$, see for Figure \ref{fig1} for an illustration. 
-In detail, the curve 
+\fede{More precisely}, the curve 
 $\Lambda = \{\boldsymbol \lambda(s), \ s\in(0,S)\}$,  where 
@@
 We assume that $\Omega_{\ominus}$ crosses $\Omega$ from side to side.
- \paolo{Finally, $|\cdot|$ denotes the Lebesgue measure of a set, e.g. $|\mathcal{D}(s)|$ is the cross-sectional area of the cylinder. In general, $|\D(s)|$ must be strictly positive and bounded.}
+ \paoloold{Finally, $|\cdot|$ denotes the Lebesgue measure of a set, e.g. $|\mathcal{D}(s)|$ is the cross-sectional area of the cylinder. In general, $|\D(s)|$ must be strictly positive and bounded.}
 According to the geometrical setting, we will denote with $v,\,v_\oplus,\,v_\ominus,\,\vd$,
@@
 
-Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. We denote with $\mathcal{T}_\Sigma: H^q(D) \rightarrow H^{q-\frac 1 2}(\Sigma)$ the trace operator from \kent{$D$} to $\Sigma$.
+Let $\Sigma$ be a Lipschitz co-dimension one subset of $D$. We denote with $\mathcal{T}_\Sigma: H^q(D) \rightarrow H^{q-\frac 1 2}(\Sigma)$ the trace operator from \kentold{$D$} to $\Sigma$.
 The space of functions in $H^{\frac 1 2}(\Sigma)$ with continuous extension by zero outside $\Sigma$ is denoted 
@@
 
-\kent{
+\kentold{
 We will frequently use inner products and norms that are weighted. The
@@
 whereas a weighted fractional
-space \miro{$H^s(\Gamma; w)$} is defined in terms of the interpolation of the corresponding weighted spaces. 
+space \miroold{$H^s(\Gamma; w)$} is defined in terms of the interpolation of the corresponding weighted spaces. 
 For the norm of such spaces, we introduce 
@@
 The operator obtained from a combination of the average operator $\avrc{(\cdot)}$ with the trace on $\Gamma$ will be denoted with $\mtrace = \avrc{(\cdot)} \circ \trace$, as it maps functions on $\Omega$ to functions on $\Lambda$.
-Further, let the extension operator $\mathcal{E}_{\Gamma}: H^{\frac 1 2}_{00}(\Lambda) \rightarrow H^{\frac 1 2}_{00}(\Gamma)$ be defined such that $(\mathcal{E}_{\miro{\Gamma}}\vd)(x)=\vd(s)$, for any $x\in \DD(s)$.
+Further, let the extension operator $\mathcal{E}_{\Gamma}: H^{\frac 1 2}_{00}(\Lambda) \rightarrow H^{\frac 1 2}_{00}(\Gamma)$ be defined such that $(\mathcal{E}_{\miroold{\Gamma}}\vd)(x)=\vd(s)$, for any $x\in \DD(s)$.
 Then, the following identity shows that the transversal uniform extension operator is the inverse of the transversal average,
@@
 
-\kent{With the above notation we are now able to formulate the precise weak formulations of the problems \eqref{eq:pde}, which we will call the \textbf{Problem 3D-1D-1D}. The problem} reads:
-\paolo{given $f\in L^2(\Omega), \ g \in L^2(\Omega_{\ominus}), \ q \in H^\frac12_{00}(\Gamma)$}
+\kentold{With the above notation we are now able to formulate the precise weak formulations of the problems \eqref{eq:pde}, which we will call the \textbf{Problem 3D-1D-1D}. The problem} reads:
+\paoloold{given $f\in L^2(\Omega), \ g \in L^2(\Omega_{\ominus}), \ q \in H^\frac12_{00}(\Gamma)$}
 find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac 1 2}(\Lambda)$, such that
@@
 \langle \mtrace u -   \ud, \md \rangle_{\Lambda,|\DD|} 
-&= \paolo{\langle \avrc{q},\md\rangle_{\Lambda,|\DD|}}
+&= \paoloold{\langle \avrc{q},\md\rangle_{\Lambda,|\DD|}}
 &\forall \md \in H^{-\frac 1 2}(\Lambda)\,.
@@
 intermediate 2D surface  encapsulating the 1D structure. The strong form is:  
-\paolo{
+\paoloold{
 \begin{subequations}
@@
 The corresponding weak formulation of \eqref{inteq:pde}, referred to as the \textbf{Problem 3D-1D-2D}, reads: 
-\paolo{given $f\in L^2(\Omega), \ g \in L^2(\Omega_{\ominus}), \ q \in H^\frac12_{00}(\Gamma)$}
+\paoloold{given $f\in L^2(\Omega), \ g \in L^2(\Omega_{\ominus}), \ q \in H^\frac12_{00}(\Gamma)$}
 find $u \in H^1_0(\Omega), \ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac 1 2}(\Gamma ) $ such that
@@
 \langle \trace u - \ext \ud , \mu \rangle_\Gamma 
-&= \paolo{\langle q,\md\rangle_\Gamma} 
+&= \paoloold{\langle q,\md\rangle_\Gamma} 
 &\forall \mu \in H^{-\frac 1 2}(\Gamma)\,.
@@
 \begin{corollary}\label{corollary:H12norm}
-If $u\in H^{\frac 12}_{00}(\Gamma)$ then $\avrc{u}\in H^{\frac 12}_{00}(\Lambda)$ and there exists a constant $C_\Gamma$, \paolo{bounded independently of $\D$ and $\DD$, such that}
+If $u\in H^{\frac 12}_{00}(\Gamma)$ then $\avrc{u}\in H^{\frac 12}_{00}(\Lambda)$ and there exists a constant $C_\Gamma$, \paoloold{bounded independently of $\D$ and $\DD$, such that}
 \begin{equation*}
@@
 \end{corollary}
-\paolo{
+\paoloold{
 Furthermore, from the
@@
 \\
-d(\mu)&=\paolo{\langle q,\mu\rangle_\Gamma}.
+d(\mu)&=\paoloold{\langle q,\mu\rangle_\Gamma}.
 \end{align*}
@@
 
-\paolo{
+\paoloold{
 To show the inf-sup condition, we will employ  
@@
 
+\fede{I THINK THE RESULT FROM [28] IS NOT WHAT WE NEED.
+IN [28] THEY BUILD AN EXTENSION OPERATOR FROM THE EXTERNAL DOMAIN TO THE SMALL INCLUSION.
+HERE WE NEED AN EXTENSION FROM THE BOUNDARY OF THE SMALL INCLUSION TO THE EXTERNAL DOMAIN, WHICH IS THE HARMONIC EXTENSION.
+FOR THIS OPERATOR, THE STABILITY CONSTANT SHOULD DEPEND ON THE RADIUS OF THE INCLUSION.
+\\
+
+To show the inf-sup condition, we will employ the harmonic extension $\mathcal{H}_\Omega$ from $H^{1/2}_{00}(\Gamma)$ to $H^1_0(\Omega)$ such that $\mathcal{H}_\Omega \xi = v$ for any $\xi \in H^{1/2}_{00}(\Gamma)$ with $v\in H^1_0(\Omega)$.
+The boundedness of this operator guarantees that there exists
+$\| \mathcal{H}_\Omega \| \in \mathbb{R}$ such that
+$\|v \|_{H^1(\Omega)}\leq \|\mathcal{H}_\Omega\| \|\xi \|_{H^{1/2}_{00}(\Gamma)}$.}
 % $\|v \|_{H^1(\Omega)}\leq \|\mathcal{H}_\Omega\| \|\xi \|_{H^{\frac 12}_{00}(\Gamma)}$. 
@@
 \\
-d(\md)&=\paolo{\langle \avrc{q},\md\rangle_{\Lambda,|\DD|}}.
+d(\md)&=\paoloold{\langle \avrc{q},\md\rangle_{\Lambda,|\DD|}}.
 \end{align*}
@@
 \label{eq:infsup_discrete}
- \sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}}\geq \beta_h \|\mu_h\|_{Q}\,, \kent{\quad \forall \mu_h \in Q_h.}
+ \sup_{v_h\in X_h} \frac{b(v_h,\mu_h)}{\|v_h\|_{X}}\geq \beta_h \|\mu_h\|_{Q}\,, \kentold{\quad \forall \mu_h \in Q_h.}
 \end{align}
@@
 &\langle \trace u_h - \mathcal{E}_{\Lambda} {\ud}_h , \mu_h \rangle_\Gamma 
-= \paolo{\langle q,\mu_h \rangle_\Gamma}
+= \paoloold{\langle q,\mu_h \rangle_\Gamma}
 \quad \forall \mu_h \in Q_h\,.
@@
 & \langle \mtrace u_h - {\ud}_h, \mdh \rangle_{\Lambda,| \DD| } 
-= \paolo{\langle \avrc{q},\mdh \rangle_{\Lambda,|\DD|}}
+= \paoloold{\langle \avrc{q},\mdh \rangle_{\Lambda,|\DD|}}
 \quad \forall \mdh \in Q_h\,.
@@
 However, with this choice of multipliers the problem is not inf-sup stable, therefore the idea is to add a stabilization term $s(\ldh, \mdh): \ Q_h \times Q_h \rightarrow \mathbb{R}$ to \eqref{eq:prob2_discrete} following the approach introduced in \cite{burman2014}.
-The objective of this section is to analyze the stabilized version of the 3D-1D-1D problem: find $[u_h, \kent{\udfh]} \in X_h$ and $\ldh \in Q_h$ such that
+The objective of this section is to analyze the stabilized version of the 3D-1D-1D problem: find $[u_h, \kentold{\udfh]} \in X_h$ and $\ldh \in Q_h$ such that
 \begin{multline}\label{eq:prob2_stabilized}
@@
 Thanks to the shape regularity of these extended patches, the following discrete trace inequality holds true for any function $v\in H^1(\omega_j)$, 
-\paolo{
+\paoloold{
 \begin{equation}\label{discr_trace_ineq}
@@
 Moreover, $\forall u_h \in X^1_{h,0}(\Omega)$ we have the following average inequality, 
-which is a consequence of the definition of $\mtrace$, Jensen inequality, \kent{and the fact that the patches are disjoint}
+which is a consequence of the definition of $\mtrace$, Jensen inequality, \kentold{and the fact that the patches are disjoint}
 \begin{multline}\label{eq:avrg_ineq}
@@
 \end{multline}
-%\kent{Earlier in the paper we always specified the measure, ds, dx etc}
+%\kentold{Earlier in the paper we always specified the measure, ds, dx etc}
 
@@
 Owing to these properties it is possible to satisfy \eqref{phi_properties}. 
-\kent{Then, by construction,}
+\kentold{Then, by construction,}
 \begin{multline*}
@@
 $|\patch\cap \Lambda| \leq cH$,
-\kent{exploiting Jensen's average inequality} \eqref{eq:avrg_ineq} 
+\kentold{exploiting Jensen's average inequality} \eqref{eq:avrg_ineq} 
 and trace inequality \eqref{discr_trace_ineq},
@@
 the following upper bound holds true
-\paolo{(where all the constants have been condensed into $C$),}
+\paoloold{(where all the constants have been condensed into $C$),}
 \begin{multline*}
@@
 
-For the second assumption of Lemma \ref{lemma23burman}, we recall that $b(v_h,\mdh)$ is continuous \kent{with respect to the norms} $\vertiii{v_h},\,\|\mdh\|_{L^2(\Lambda)}$. 
+For the second assumption of Lemma \ref{lemma23burman}, we recall that $b(v_h,\mdh)$ is continuous \kentold{with respect to the norms} $\vertiii{v_h},\,\|\mdh\|_{L^2(\Lambda)}$. 
 Using Lemma \ref{lemma:Lh_infsup}, and in particular the existence of a Fortin projector,
 there exists a constant $\beta$ such that 
-(the proof is \miro{analogous} to the one of Lemma 2.1 in \cite{burman2014})
+(the proof is \miroold{analogous} to the one of Lemma 2.1 in \cite{burman2014})
 \begin{equation}\label{relax_infsup}
@@
 For the second term, we apply the additional assumption that the operators $\mtrace$ and $\partial_s$ commute. This is true if the cross section $\D$ does not depend on the arclength $s$.
-\paolo{
+\paoloold{
 Then, we use the Poincar\'e inequality \eqref{disc_poincare_ineq}, the average inequality \eqref{eq:avrg_ineq} and the trace inequality \eqref{discr_trace_ineq} to show that,
@@
 % \end{multline*}
-% \kent{Is it $C_P$}
-% \paolo{For the third term we observe that since $H \lesssim 1$, there exists a constant $C$ 
+% \kentold{Is it $C_P$}
+% \paoloold{For the third term we observe that since $H \lesssim 1$, there exists a constant $C$ 
 % such that $C_P^2 H|\DD| \leq C |\D|$.
@@
 \section{A benchmark problem with analytical solution}
-
+\fede{Let $\Omega=[0,1]^3$, $\Lambda=\{x=\tfrac{1}{2}\}\times \{y=\tfrac{1}{2}\} \times [0,1] $
+and $\Omega_{\ominus}=[\tfrac{1}{4}, \tfrac{3}{4}]\times [\tfrac{1}{4}, \tfrac{3}{4}]\times [0, 1]$.
+As a benchmark for the two formulations \eqref{eq:problem1} and \eqref{eq:problem2} we consider the case in which the source terms are defined as
+\begin{equation*}
+f=8\pi ^2 \sin (2\pi x) \sin (2\pi y),\quad \avrd{g}={\pi ^2}\sin \left({\pi z}\right)
+\end{equation*}
+and the coupling constraints , denoted as $q_1$ for \eqref{eq:problem1} and $\avrc{q}_2$ for \eqref{eq:problem2}, are given by
+\begin{equation*}
+q_1=\sin (2\pi x) \sin (2\pi y) - \sin \left({\pi z}\right),\quad \avrc{q}_2=-\sin \left({\pi z}\right).
+\end{equation*}
+At the boundary $\partial \Omega$, non-homogeneous Dirichlet conditions are imposed 
+\begin{equation*}
+u=u_b \text{ on $\partial \Omega$ \quad with $u_b=\sin (2\pi x) \sin (2\pi y)$}.
+\end{equation*}
+Under these conditions, the solution of \eqref{eq:problem1} and \eqref{eq:problem2} is given by
+\begin{equation}
+\label{benchm_sol3d-1d_}
+u=\sin (2\pi x) \sin (2\pi y),
+\quad
+%\ud=1+\exp(-z).
+\ud=\sin \left({\pi z}\right),
+\quad
+\lambda = \ld = 0.
+\end{equation}
+We show that \eqref{benchm_sol3d-1d_} is solution of \eqref{eq:problem2}. We notice that, regardless the coupling constraints, $u$ and $\ud$ are solutions of the following coupled problem
+\begin{subequations}\label{benchmark_}
+\begin{align}
+\label{benchm_3d_}
+-\Delta u=f \quad &\text{in $\Omega$},\\
+\label{benchm_1d_}
+-d_{zz}^2 \ud =\avrd{g} \quad &\text{on $\Lambda$},\\
+u=u_b \quad &\text{on $\partial \Omega$}.
+\end{align}
+\end{subequations}
+Using the integration by part formula and homogeneous
+boundary conditions on $\Omega$ and $\Lambda$, from \eqref{eq:problem2} we have
+\begin{align*}
+&-(\Delta u, v)_{L^2(\Omega)} - |{\cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)} 
++ |{\cal D}|\langle \avrc{v}  - \vd, \ld \rangle_\Lambda
+\\
+\nonumber
+&\qquad\qquad= (f,v)_{L^2(\Omega)} + |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}
+\quad \forall v \in H^1_0(\Omega), \vd \in H^1(\Lambda).
+\end{align*}
+Since $\ld=0$ and the first of \eqref{benchm_sol3d-1d_} satisfies \eqref{benchm_3d_} and the second satisfies \eqref{benchm_1d_}, we have that
+\begin{align*}
+-(\Delta u, v)_{L^2(\Omega)} =  (f,v)_{L^2(\Omega)}, 
+\\
+-|{\partial \cal D}|(d^2_{ss} \ud, \vd)_{L^2(\Lambda)}  = |{\cal D}| (\avrd{g},\vd)_{L^2(\Lambda)}.
+\end{align*}
+Thus \eqref{benchm_sol3d-1d_} satisfy equations \eqref{eq:problem2a}, \eqref{eq:problem2b}.
+The fact that the solution satisfy \eqref{eq:problem2c} follows from \eqref{benchm_sol3d-1d_} and the definition of $\avrc{q}_2$.
+
+We can prove in a similar way that \eqref{benchm_sol3d-1d_}
+satisfies \eqref{eq:problem1}. Note in particular that $q_1$ is such that
+$\trace{u} - \ext{\ud} = q_1$ on $\Gamma$.\\
+}
 Let $\Omega=[0,1]^3$, $\Lambda=\{x=\tfrac{1}{2}\}\times \{y=\tfrac{1}{2}\} \times [0,1] $
@@
 % \uf - \up &= q_i  && \text{ on }  \Gamma,\\
-% \up &= \paolo{u_b} && \text{ on } \partial \Omega,
+% \up &= \paoloold{u_b} && \text{ on } \partial \Omega,
 % \end{align}
@@
 
-\paolo{We prove that the solution of \eqref{benchmark} is equivalent to the one of \eqref{eq:problem2}.}
+\paoloold{We prove that the solution of \eqref{benchmark} is equivalent to the one of \eqref{eq:problem2}.}
 Precisely, we prove that \eqref{benchm_sol3d-1d} is the solution of
@@
 \bibliographystyle{siamplain}
-\bibliography{3d1d_coupled}
+\bibliography{3d1d}
 

### 2020-09-22 reply_to_reviewers.tex
almost done rev1

@@
 \item Please explain what is unknown $\lambda$ in problem (1.1). I suggest including part of the Appendix from supplementary materials where $\lambda$ is introduces as a Langrange multiplier.
-    \item Sectio 2, page 2 - $\Omega$ is open? Maybe replace "in detail" with "More precisely".\\
+  \miro{
+    In the revised text we newly comment that $\lambda$ can be seen as a Lagrange multiplier related to
+    the coupling constraint and refer readers to the Supplementary material where the exact definition of
+    $\lambda$ is given.
+
+    Let us note that (1.1) is a ``template'' problem where we simply wish to illustrate
+    that the 3$D$ and the 1$D$ problems are coupled via $\lambda\delta_{\Gamma}$ where the strength
+    of the coupling, i.e. $\lambda$, is unknown. 
+    }
+    \item Section 2, page 2 - $\Omega$ is open? Maybe replace "in detail" with "More precisely".\\
     \fede{The standard definition of domain is used, i.e. $\Omega$ is a open and connected set. For clarity, the definition has been added to the manuscript. }
   \item P. 3. - Please provide references for $H^{1/2}_{00}$ and interpolation of weighted spaces. In addition, it would be instructive to provide an example for Riesz map S.
+    \miro{
+      \textit{We actually don't use $H^s$, only $H^s_{00}$. For this reason I'd like to
+      simplify the text and only discuss $-\Delta u=\lambda u$ on $H^1_0(\Gamma)$.
+      An advantage is that then the Riesz map is $-\Delta^{-1}$. I don't know if
+      in $H^s$ we can say that $(-\Delta+I)^{-1}$ is the Riesz map.}
+
+      \textit{
+        I included refences for $H^{1/2}_{00}$ and general interpolation in
+        Hilbert spaces.
+      }
+      The reference has been added in the revised manuscript. We have
+      also simplified the exposion: definition of the space $H^s$,
+      which was not used further in the analysis, was removed and only
+      the space $H^s_{00}$ is introduced. Per reviewer's suggestion the
+      relevant Riesz map, $-\Delta^{-1}$, is newly given in the text.
+      }
+
     \item p.4.
@@
   \item p8 l177-l184 - I suggest adding a figure that illustrate the assumptions on the conforming mesh.
+
+    \miro{
+      \textit{I modified the existing figure and the caption to highlight.
+        Is it sufficient?}
+      In the previous version we tried to illustrate the assumptions on the conforming
+      mesh with Figure 5.1. This figure has newly been modified to emphasize
+      correpondence of the cells of $\mathcal{T}^{\Lambda}_h$, $\mathcal{T}^{\Gamma}_h$ to
+      entities of $\mathcal{T}^{\Omega}_h$.
+      }
+
     \item p9 (4.4) Reference for these properties of $SZ_h$\\

### 2020-09-22 3d1d_LM_rev.tex
almost done rev1

@@
 \usepgfplotslibrary{fillbetween}
-\pgfplotsset{compat=1.16}
+%\pgfplotsset{compat=1.16}
 
@@
 for a continuous function $v$ and $\mathcal{T}_\Lambda: \Omega\rightarrow\Lambda$ is a suitable restriction operator from 3D to 1D.
+\miro{We remark that $\lambda$ can be viewed as a Lagrange multiplier associated with the
+  coupling constraint \eqref{eq:coupling}, see \S\ref{sec:derivation} for
+  detailed interpretation.
+}
 
@@
 Owing to the positivity and boundedness of $w$ the weighted spaces equal the corresponding non-weighted spaces as sets, but their norms are different.
+}
+
+\miro{
+We will frequently use inner products and norms that are weighted. The
+$L_2$ and $H^1$ inner products
+weighted by a scalar function 
+$w$, which is strictly positive and bounded almost everywhere,
+are defined as 
+follows
+\begin{equation*}
+%(u,v)_{\Gamma, w} = 
+(u,v)_{L^2(\Omega), w} = 
+\int_{\Omega} w \, u \, v d\omega \ \mbox{   and   } \
+%(u,v)_{\Gamma, w} = 
+(u,v)_{H^1(\Omega), w} = 
+\int_{\Omega}  w \, u \, v d\omega
++ \int_{\Omega} w \, \nabla u \cdot \nabla v d\omega
+\end{equation*}
+whereas a weighted fractional
+space \miroold{$H_{00}^s(\Gamma; w)$} is defined in terms of the interpolation
+of the corresponding weighted spaces (see \cite[ch. 2.1]{MR0350177}, \cite{chandler2015interpolation}). 
+For the norm of such spaces, we introduce 
+the Riesz map $S$ such that 
+for $u, v \in H_0^1(\Gamma)$ we have 
+\[
+\int_{\Omega} w \nabla\left(S u\right)\cdot\nabla vd\omega  = (u,v)_{L^2(\Gamma), w}.
+\]
+Then $S=-\Delta^{-1}$ is a compact self-adjoint operator. 
+Assuming that $\{\lambda_k\}_k$ is the set of eigenvalues, 
+$\{\phi_k\}_k$ the set of eigenvectors of $S$ 
+orthonormal with respect to the inner 
+product $(\cdot, \cdot)_{L^2(\Gamma), w}$ and $u\in H_0^1(\Gamma)$ can be expressed 
+as $u=\sum_k c_k \phi_k$ 
+then
+\[
+\|u\|^2_{H_{00}^s(\Gamma), w} = \sum_k \lambda_k^{-s} c_k^2 .   
+\]
+%The space $H_{00}^s(\Gamma; w)$ is defined analogously, but with $S$ above defined in terms of the $H^1_0$ inner product.
+Owing to the positivity and boundedness of $w$ the weighted spaces equal the corresponding non-weighted spaces as sets,
+but their norms are different.
 }
@@
    used for \eqref{eq:problem1} and \eqref{eq:problem2}.
+   Each cell of $\mathcal{T}^{\Gamma}_h$ (in blue, filled marker vertices) and $\mathcal{T}^{\Lambda}_h$ (in red, filled marker vertices)
+   is a facet, respectively edge, of $\mathcal{T}^{\Omega}_h$ (in black, empty square marker vertices).
    (Right) Sample discretization of the benchmark geometry in the non-conforming case for \eqref{eq:problem2}. 

### 2020-09-22 appendix.tex
almost done rev1

@@
 
-\section{Derivation of the model}
+\section{Derivation of the model}\label{sec:derivation}
 This section provides a rigorous derivation of 3D-1D-1D problem \eqref{eq:problem2} and 3D-1D-2D problem \eqref{eq:problem1}. 
